### 2021-11-23 src/ms.tex
showyourwork utils and paper

% Define document class
\documentclass[twocolumn]{aastex631}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\usepackage{amsmath}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\newcommand{\cosmic}{\texttt{COSMIC}}
\newcommand{\legwork}{\texttt{LEGWORK}}

\shorttitle{Applying a metallicity-dependent binary fraction to DWD formation}
\shortauthors{Thiele, Breivik, \& Sanderson}

% Begin!
\begin{document}

% Title
\title{Applying the metallicity-dependent binary fraction to double white dwarf formation: \\ Implications for LISA}

% Author list
\correspondingauthor{Sarah Thiele}
\email{sarahgthiele@gmail.com}

\author[0000-0001-7442-6926]{Sarah Thiele}
\affiliation{Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC, V6T 1Z1, Canada}
\affiliation{Canadian Institute for Theoretical Astrophysics, University
of Toronto, 60 St. George Street, Toronto, Ontario, M5S 1A7,
Canada}
\author[0000-0001-5228-6598]{Katelyn Breivik}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
\affiliation{Canadian Institute for Theoretical Astrophysics, University
of Toronto, 60 St. George Street, Toronto, Ontario, M5S 1A7,
Canada}
\author[0000-0003-3939-3297]{Robyn E. Sanderson}
\affiliation{Department of Physics and Astronomy, University of Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}

% Abstract with filler text
\begin{abstract}
   Short-period double white dwarf (DWD) binaries will be the most prolific source of gravitational waves (GWs) for the Laser Interferometer Space Antenna (LISA). Not only will tens of thousands of DWDs be individually resolved, but DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be the dominant contributor to a stochastic foreground caused by confusion from overlapping GW signals, limiting the detectability of individual sources of all kinds. The number of DWDs in the Milky Way strongly depends on the Galactic stellar binary fraction. Population modelling of Galactic DWDs typically assumes a standard binary fraction of $50\%$. However, recent observations have shown that the binary fraction of close ($P_{\text{orb}}$ $\leq 10^4$ days) solar-type stars exhibits a strong anti-correlation with metallicity. In this study we perform the first simulation of the Galactic DWD population observable by LISA which incorporates an empirically-derived metallicity-dependent binary fraction. We simulate DWDs using the binary population synthesis suite \cosmic\ and incorporate a metallicity-dependent star formation history to create a Galactic population of short-period DWDs. We compare two models: one which assumes a metallicity-dependent binary fraction, and one with a binary fraction of 50\%. We find that while metallicity impacts the evolution and intrinsic properties of our simulated DWD progenitor binaries, the LISA-resolvable populations of the two models remain roughly indistinguishable. However, the size of the total Galactic DWD population orbiting in the LISA frequency band is reduced by more than half when accounting for a metallicity-dependent binary fraction. This effect serves to lower the confusion foreground, effectively increasing the sensitivity for detecting all types of low-frequency LISA sources. We repeat our analysis for three different assumptions for Roche-lobe overflow interactions and find the population reduction to be robust when a metallicity-dependent binary fraction is assumed.

\end{abstract}

% Keywords
\keywords{Binary stars --- Stellar evolution --- GW astronomy}

\section{Introduction} \label{sec:intro}
Most stars in the Galaxy will end their lives as white dwarfs. Of the stars which are born with a binary companion, many will undergo interactions which bring the two stars closer together, eventually forming a close double white dwarf (DWD). Close DWDs, with orbital periods shorter than $\sim2.75\,\rm{hr}$ %\snotes{[close DWDs are defined to have $P_{\rm{orb}}\leq10^4$ days - are we noting 2.75 hrs for GW sources specifically? If so maybe we should reword this bit because it reads like it conflicts with the abstract?]},
%Katie: Close DWDs is a different classification than close binaries.
are the largest source by number of mHz gravitational waves (GWs) in the Galaxy \citep[e.g.,][]{LISAMissionProposal}. The Laser Interferometer Space Antenna (LISA) is expected to resolve at least $10^4$ individual DWD binaries in the Milky Way and will also observe GW emission from the entire Galactic DWD population through the unresolved foreground created by overlapping signals at sub-mHz frequencies \citep[e.g.,][]{Nelemans2001a, Ruiter2010, Nissanke2012, Yu2013, Korol2017, Lamberts2019, Breivik2020a}. The resolved population will enable the study of several important aspects of binary evolution like the strength of tides \citep{Valsecchi2012} and the stability of mass transfer in DWD systems \citep[e.g.,][]{Marsh2004, Shen2015, Gokhale2007, Sepinsky2014, Kremer2015} as well as provide a probe of Galactic structure \citep{Korol2019} and the Local Group \citep{Korol2018}. The shape and strength of the Galactic DWD foreground can also be used as a tool to study the structure of the Milky Way \citep{Benacquista2006, Breivik2020b} as well as the separation distribution of close DWDs \citep{Korol2021}.

When viewed strictly as a source of noise, the unresolved Galactic DWD foreground is the dominant noise source for LISA in the sub-mHz part of LISA's frequency range. This extra noise above the detector noise floor affects the detection of all other LISA sources including extreme mass ratio inspirals \citep[e.g.,][]{Berti2006, Barack2007, Babak2017, Moore2017}, merging black holes with masses between $10^4$--$10^7\,M_{\odot}$ \citep[e.g.,][]{Klein2016, Bellovary2019}, and cosmological GW backgrounds \citep[e.g.,][]{Bartolo2016, Caprini2016, Caldwell2019}. For sources which have signals buried by the Galactic DWD population, the foreground must be carefully analyzed and subtracted \citep[][]{Adams2014,Cornish2020,Littenberg2020,Boileau2021}. The number of resolved DWDs and the height of the unresolved DWD foreground are a direct consequence of the number of DWD progenitors which form and evolve over the Milky Way's history.

While the binary fraction remains approximately constant across a large metallicity range ($-1.5 \leq$ [Fe/H] $< 0.5$) for wide binaries, close OB stars, and the stellar Initial Mass Function (IMF) \citep{Moe2017, Moe2019}, the binary fraction for solar-type star systems with orbital period $P_{\text{orb}}\leq 10^4$ days (separation $a \leq 10$ AU) shows a strong anti-correlation with metallicity \citep[e.g.][]{Badenes2018, Moe2019, Mazzola2020, Price-Whelan2020}. Because close DWDs are the remnants of close, solar-type binary stars, this anti-correlation plays an important role in the formation, evolution, and characteristics of the DWD population that LISA will observe.

%These relatively close binaries are likely to form from fragmentation, accretion, and inward migration in protostellar disks. This is in contrast to wide binaries whose formation channels stem from fragmentation of molecular cores, which is generally unaffected by the opacity of the material. 
%This is depicted in the ``metallicity invariance" for the IMF and binary fraction beyond separations of 200 au for -1.0 $<$ [Fe/H] $<$ 0.5 of Mazzola et al. (2020). Within protostellar disks however, it has been shown through analytical models and hydrodynamic simulations that the probability of disk fragmentation decreases with increasing metallicity (Mazzola et al. 2020). Metal-poor cores are unable to radiate through molecular transitions as effectively, and so are generally hotter and must reach higher masses in order to collapse into disks, which instigates higher accretion rates and results in gravitational instability and thus fragmentation. Furthermore, if you decrease a disk’s metallicity and thus its optical depth, the mid-plane of the disk is able to radiate and cool more efficiently which encourages fragmentation. (Mazzola et al. 2020 and others).

%Numerically, the dominant sources for LISA will be DWDs from the Milky Way. There is an expectation that several tens of millions of detached DWDs will be present in the LISA band with about ten thousand of these to be individually resolvable  with $f_\text{GW} \geq 0.4$ mHz (Nelemans et al. 2001b). DWDs are nice systems to work with: a compact binary which emits continuously and near monochromatically GW signals in the source frame (LISA proposal REF), and of which the second harmonic of their signals can be measured with high accuracy. In general, higher frequency systems are louder and better characterized than low frequency counterparts. In fact, at low frequencies we find that the high number of DWDs begin to overlap in their signals, creating a stochastic background. This effective “confusion signal” arises for these low frequencies from having more than one DWD per frequency bin, $f_\text{bin} = 1 / t_\text{obs}$, where $t_\text{obs}$ is the length of observation time for the LISA mission, which we assume to be four years (LISA proposal REF).

%The science that the LISA mission will contribute to is diverse in scope. Specific to DWDs, the hope is to use the distribution of chirp masses and periods to constrain the impact of the common envelope, which drastically tightens the orbit of the systems (Toonen et al. 2014). A complete sample will also allow for direct comparison with the post-common envelope binaries, which have undergone only one episode of the common envelope (Rebassa-Mansergas et al. 2012). In some cases, the frequency derivative will be measurable and allow us to determine if mass transfer is happening (Breivik et al. 2018) and/or tidal interactions are deforming the white dwarfs.

%\subsection{The metallicity-dependent binary fraction}
To date, population synthesis studies of the Galactic population of close DWDs have either assumed a $100\%$ binary fraction or a $50\%$ binary fraction, such that for every three stars formed, two reside in a binary system \citep{Nelemans2001a, Yu2013, Korol2017, Lamberts2019}. In this study, we investigate the effects of a metallicity-dependent binary fraction on the formation and evolution of DWDs. To this end, we create synthetic present-day Milky Way-like galaxies of DWDs and specifically select systems with GW signals that may be observable by the space-based detector LISA. Throughout, we make comparisons between the standard assumption of a constant $50\%$ initial binary fraction (hereafter model F50) and one with a metallicity-dependent binary fraction (hereafter model FZ).

In Section \ref{sec:simulations} we discuss our binary evolution assumptions used in simulating DWD populations and detail the process to produce present-day synthetic Milky-Way-like galaxies. In Section \ref{sec:LISA_obs} we review the derivation of LISA detectability for circular DWD populations at mHz frequencies. In Section \ref{sec:results} we detail results showing how a metallicity-dependent binary fraction affects the formation and evolution of DWD populations assuming a fiducial set of binary evolution assumptions. In Section \ref{sec:LISA_met} we detail the metallicity dependence of the LISA DWD foreground and resolved population. Finally, we repeat our analysis for three sets of binary evolution assumptions to show a robust reduction of the size of the Galactic DWD foreground in LISA for populations simulated with a metallicity-dependent binary fraction in Section \ref{sec:model_compare} and conclude in Section \ref{sec:conclusions}.

\section{Simulating a Galactic DWD population}\label{sec:simulations}
In this section we describe the setup of our DWD simulations using the binary population synthesis suite \cosmic, and the process to scale these simulations to create Milky Way-like galaxies using the star formation history of galaxy \textbf{\textbf{m12i}} in the Latte suite of the FIRE-2 simulations \citep{Wetzel2016, Hopkins2018} and stellar positions assigned according to the the Ananke framework \citep{Sanderson2020}.

%The Latte suite of FIRE-2 cosmological zoom-in baryonic simulations of Milky Way-mass galaxies \citep{Wetzel2016}, part of the Feedback In Realistic Environments (FIRE) simulation project, were run using the Gizmo gravity plus hydrodynamics code in meshless finite-mass (MFM) mode \citep{Hopkins2015} and the FIRE-2 physics model \citep{Hopkins2018}. Synthetic Gaia DR2-like surveys of the Latte suite of FIRE-2 simulations were created via the Ananke framework \citep{Sanderson2020}.

\subsection{Binary population models}
\label{sec:bin_pop}
We simulate the evolution of DWD progenitor populations using \cosmic\footnote{https://cosmic-popsynth.github.io}, an open-source Python-based rapid binary population synthesis suite which employs single and binary star evolution using \texttt{SSE/BSE} \citep{Hurley2000, Hurley2002}. Several modifications have been added to \cosmic\ which incorporate updates for massive star evolution and binary interactions. For a detailed description of these modifications see \citet{Breivik2020a}. \cosmic\ has been used in several studies to examine the effects of binary evolution on binary populations from blue stragglers \citep{Leiner2021} and heartbeat stars \citep{Jayasinghe2021}, to white dwarf populations \citep{Kremer2017,Breivik2018,Kilic2021}, to merging compact object populations in isolated binaries \citep{Zevin2020b, Zevin2020a, Zevin2021, Wong2021, Mandhai2021} and in dynamical environments around super-massive black holes \citep{Stephan2019, Wang2021}. 
%Recently, \cosmic\ was integrated with the Cluster Monte Carlo (CMC) code to enable direct comparisons between isolated binary evolution and the evolution of stars in globular clusters \citep{Rodriguez2021}. Since this work considers the effects of the metallicity-dependence of the close isolated binary fraction, we leave direct comparisons to globular clusters to future work.

\cosmic\ is especially useful for efficient generation of large populations of compact binaries. Instead of choosing a fixed number of binary stars for each simulation, \cosmic\ iteratively simulates populations until parameter distributions of the binary population converge to a stable shape as more binaries are added. This process is quantified through the $match$ parameter inspired by matched filtering techniques \citep[e.g. Eq. 6 of ][]{Chatziioannou2017} defined as

\begin{equation}
   match = \frac{\sum_{k=1}^{N}P_{k,i}P_{k,i+1}}{\sqrt{\sum_{k=1}^{N}P_{k,i}P_{k,i}\sum_{k=1}^{N}P_{k,i+1}P_{k,i+1}}},
\end{equation}
where $P_{k,i}$ represents the height of bin $k$ on the $i\rm{th}$ iteration \citep{Breivik2020a}. In this study, we simulate binaries until $\log_{10}(1-match) \leq -5$ for the masses and orbital periods of each DWD population at the formation of the second WD. Since all DWD progenitor binaries simulated with \cosmic\ are circularized through mass transfer or tides before the second WD forms \citep[e.g.][]{Marsh2004, Gokhale2007, Sepinsky2014, Kremer2015}, we do not consider convergence of DWD eccentricities.

% I'm suggesting text above since we have a boiler-plate style that we use to stay consisten in the literature.
%Rather than evolving an initial binary population’s individual stars - a computationally expensive process - \cosmic\ uses Monte Carlo statistics to create fixed populations that would be expected based on parameters like SFH and the known processes within binary star evolution. In the \cosmic\ framework, binaries are initialized iteratively with zero age main sequence (ZAMS) binary parameters and tested against the final parameter distributions desired by the user until they match. The output of \cosmic\ contains enough information that a user can analyze both individual systems of interest as well as the overall population, from ZAMS until compact binary formation.

%In this study, we used \cosmic\ 's cosmic-pop package to create fixed populations of DWDs, keeping all parameters except DWD type and metallicity Z constant. The output fully describes the binary parameter distributions that result from our SFH and binary evolution model, coined BSEDict, which is specified in an inifile containing sections on filters, convergence, sampling, and BSE flags, which will be described below:

%\katie{Based on the restructuring I did, I think you should expand this paragraph to describe (1) since we are interested in a metallicity-dependent binary fraction, we simulate metallicity bins separately, (2) since the masses and orbital periods of each DWD type at formation span a wide range, we simulate them separately.}
%For a given metallicity, a fixed population of one million binaries was created for each DWD subtype (discussed in Section \ref{sec:ini}). 
%\katie{Is this true? I think we probably simulated more. We should talk about this today!}

%moved paragraph up here from below since it takes care of some of the things I suggested in the paragraph above!

The masses and orbital periods at the formation of the second-formed WD span a wide range depending on the WD binary component types, thus we consider four DWD combinations: two helium WDs (He + He), a carbon-oxygen WD orbiting a helium WDs (CO + He), two carbon-oxygen WDs (CO + CO), and an oxygen-neon orbiting helium, carbon-oxygen, or oxygen-neon WD (ONe + X). For each DWD type we simulate a grid of $15$ metallicities spaced uniformly in $\log_{10}(Z)$ between $Z=10^{-4}$ to $0.03$, to account for the limits of the \citet{Hurley2000} stellar evolution tracks employed in \cosmic. This results in a total of $60$ populations across all DWD types and metallicities. The output of \cosmic\ contains information limited to intrinsic binary properties like mass and orbital period. External parameters like Galactic position and orientation are assigned in a post-processing scheme which uses metallicity-dependent positions and ages from the Ananke framework of galaxy \textbf{m12i} from the Latte Suite of the FIRE simulations (see Section~\ref{sec:FIRE} for details).

%this is covered in my text above.
%We iteratively simulate binary populations until the distributions of the DWD masses and orbital period at the formation of the second-formed WD converge to a stable shape. Eccentricity does not need to be analyzed, as most DWDs are circularized by tidal forces (Marsh et al. 2004, Gokhale et al. 2007, Kremer et al. 2015/17), which also simplifies many calculations later on for GW evolution and GW signals.

We assume that the Zero Age Main Sequence (ZAMS) masses, orbital periods and eccentricities for each binary are independently distributed. We choose primary masses following \citet{Kroupa2001}, a flat mass ratio distribution \citep{Mazeh1992, Goldberg1994}, a log-uniform period distribution following Opik's Law, and a uniform eccentricity distribution following \cite{Geller2019}. We initialize all binaries with the same evolution time of $13.7\,\rm{Gyr}$ to capture all potential evolution within a Hubble time. We assume a $100\%$ binary fraction in our COSMIC simulations to reduce computation time and scale the simulations to models which assume a constant $50\%$ binary fraction (model F50) or a metallicity-dependent binary fraction (model FZ) in a post-processing scheme.

Since we are primarily interested in the effects of a metallicity-dependent binary fraction, we use a single set of assumptions for binary interactions. Our choices follow the \texttt{COSMIC} defaults described in \citet{Breivik2020a} except for the treatment of Roche-lobe overflow (RLO). The stability of RLO mass transfer is determined using critical mass ratios resulting from radius-mass exponents \citep{Webbink1985, Hurley2002}, where the critical mass ratio is defined as the ratio of the donor to accretor mass. We assume critical mass ratios following \citet{Claeys2014} which reduce the standard critical mass ratio assumptions from \citet{Hurley2002} for main sequence (MS) donors by $\sim50\%$ from $3$ to $1.6$ based on the models of \citet{deMink2007} and treat WD accretors separately following the models of \citet{Soberman1997}. We increase the mass loss rate from the donor following Equation 11 of \citet{Claeys2014}. The amount of mass lost during RLO from the donor is limited by the overflow factor of the donor radius to its Roche radius following \citet{Hurley2002}. The amount of mass accepted by the accretor is limited to $10$ times the accretor's mass divided by the accretor's thermal timescale. Finally, for RLO mass loss which becomes unstable and leads to common envelope evolution (CEE) we assume that the donor's binding energy is calculated according to the fits detailed in Appendix B of \citet{Claeys2014} and that orbital energy is deposited with $100\%$ efficiency into unbinding the common envelope ($\alpha=1$).

\subsection{Metallicity-dependent binary fraction}
We fit the results presented in \citet{Moe2019} using linear regression to obtain a piecewise relation between the metallicity, [Fe/H] and binary fraction $f_{\rm{b}}$ as

\[f_{\rm{b}}= \begin{cases} 
      - 0.0648 \cdot [\rm{Fe/H}] + 0.3356, & [\rm{Fe/H}]\leq -1.0 \numberthis \\
      -0.1977 \cdot [\rm{Fe/H}] + 0.2025, & [\rm{Fe/H}]> -1.0  
   \end{cases}
\]

\noindent We convert between [Fe/H] and metallicity Z, assuming all stars have solar abundance such that
\begin{equation}
\label{eq:metallicity}
    [\rm{Fe/H}] = \log_{10}\Big(\frac{Z}{Z_{\odot}}\Big),
\end{equation}
\noindent where we assume $Z_{\odot}=0.02$.

\subsection{A metallicity-dependent SFH: Convolving with the FIRE models}
\label{sec:FIRE}
%\katie{I think this paragraph gives a bit too much detail on FIRE. I think the only detail we need is (1) we use Galaxy m12i from the Latte Suite of the FIRE simulations and (2) Latte reproduces parts of the Milky Way (see Lamberts+2019 paper for this info)}
To create Milky Way-like galaxies which integrate the metallicity-dependent binary fraction, we use the metallicity-dependent ages and positions of galaxy \textbf{m12i} from the ``Latte" suite of the FIRE simulations \citep{Hopkins2015, Wetzel2016, Hopkins2018} to create synthetic, Milky Way-like DWD populations. %\sout{Specifically, the new “FIRE-2” code version was used, which updates the FIRE physics modules in the code GIZMO (Hopkins et al. 2018;  Gabyurov and Nitadori 2011; Hopkins 2015). This update leverages recent developments of mesh-free Godunov hydrodynamics methods, and incorporates updates to “cooling and recombination rates, gravitational force softening, and numerical feedback coupling” (Hopkins et al. 2018). The Latte suite is then run using Gizmo gravity, plus hydrodynamics code in meshless finite-mass (MFM) mode (Hopkins 2015) and the FIRE-2 physics model (Hopkins e al 2018)” $<$- citation}.

The \textbf{m12i} galaxy provides particle mass resolution of 7070 M$_\odot$ per star particle. Each star particle has an associated metallicity, position, and age, which is combined with the output of \cosmic\ to assign DWDs to each star particle by matching its metallicity to our \cosmic\ metallicity grid. The positions of each DWD are assigned using the Ananke framework since multiple DWD binaries can form within a single star particle. Specifically, we use an epanechnikov kernel where the kernel size is inversely proportional to the local density to assign the radial component of spherically symmetric offsets from the center of each star particle following \citet{Sanderson2020}.

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/sfh_vs_fb.pdf}
    \caption{The metallicity-dependent binary fraction for close solar-type binaries with P $< 10^4$ days (black) plotted against the logarithm of Z/Z$_\odot$, with scatter points denoting the location of the metallicity grid used in our \cosmic\ simulations. The secondary axis shows the amount of mass in stars formed within each metallicity bin from galaxy \textbf{m12i} of the ``Latte" suite in FIRE-2 simulations as a red histogram. The amount of stellar mass formed with super-solar metallicities dominates the distribution. Note that the primary axis shows $f_{\rm{b}}(Z)$ in linear scale, and the secondary axis shows amount of mass formed in log-scale. The opposing trends of these two distributions compete throughout this study.}
    \label{fig:sfh_vs_fb}
\end{figure}

The metallicity-dependent binary fraction is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid. %Plotted in black is the binary fraction as a function of metallicity. 
%The metallicity values chosen for our grid are shown as the scatter points. The red histogram depicts the total mass in stars formed for each metallicity bin within FIRE galaxy \textbf{m12i}, the Milky Way-like simulation used in this study which will be described further in Section \ref{sec:simulations}, as a function of metallicity. 
The binary fraction, $f_{\rm{b}}$, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly. These two opposing trends compete throughout this study along with the impact of metallicity on single star evolution to form the final numerical distribution of systems in our DWD populations.

Since our \cosmic\ simulations assume a binary fraction of $f_{\rm{b}} = 1$, we scale the amount of mass sampled at ZAMS required to produce our \cosmic-generated population of DWDs ($M_{\text{b,ZAMS}}$) to the proper amount of mass sampled in single and binary stars ($M_{\text{ZAMS,sim}}$) for each binary fraction and model. We do this by sampling single stars and primary masses of binary stars from the \cite{Kroupa2001} IMF and sampling secondary masses of the binary stars from a uniform mass distribution, where the number of binaries is determined by the binary fraction model (F50 or FZ). From this sample, we obtain the ratio of mass in single stars to the mass in binary stars as a function of the binary fraction, $R(f_{\rm{b}})$. For model F50, the ratio is a constant $R(f_{\rm{b}}) = 0.64$. For model FZ, the ratio increases from 0.68 at low metallicities to 3.17 at solar metallicity indicating less mass in binaries relative to single stars. The total amount of ZAMS mass in single and binary stars is then $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}} (1 + R(f_{\rm{b}}))$.

%We use these ratios to then determine the total amount of ZAMS mass sampled in single and binary stars. 
%This ratio can then be used to scale the total amount of ZAMS mass sampled in binary stars required to produce our simulated population from \cosmic\ to $M_{\rm{ZAMS,sim}}$, the total amount of ZAMS mass in single stars and binary systems required to produce the simulated population for a given binary fraction $f_{\rm{b}}$.

%For a given metallicity in our grid and a given DWD type of one compact object binary type, the general procedure to create the Milky Way like galaxy is as follows. We specify metallicity bin $i$ with metallicities Z $\in$ [Z$_{i-1}$, Z$_i$]. The number of DWDs per unit mass N$_{\text{DWD,}i}$ for the \katie{\sout{cosmic-pop} simulated \cosmic} population pop$_i$ with Z = Z$_i$ is found through:

%\begin{align*}
%    R_{m}(f_i) &= \frac{M_{\text{singles,}\odot}(f_i)}{M_\text{binaries,} \odot(f_i)} \numberthis \\
%    \\
%    M_{\text{tot,}i} &=  M_{\text{binaries,}i} \cdot (1 + R_m(f_i)) \numberthis \\
%    \\
%    N_{\text{DWD,}i} &= \frac{N_{\text{DWD, tot,}i}}{M_{\text{tot,}i}} \numberthis
%\end{align*}

%R$_m$ is the fraction of mass in single stars to mass in binary stars for binary fraction $f_i$. \katie{I wonder if we can rewrite these equations to be a bit less confusing; I think we should use Lamberts+2019 as a guide.} \katie{\sout{This is calculated ahead of time using the \cosmic\ independent sampler in the InitialBinaryTable class.} I think that this sentence should say that the scaling incorporates the same assumptions for primary and secondary mass distributions as are used in the simulated data.} One million DWD binaries are initialized at solar metallicity for a given binary fraction, along with the total mass in singles vs. binaries. M$_{{\rm{binaries, }}i}$ the mass in binaries of pop$_i$ (the total mass of the population, as they were run with f$_{\rm{b}}$ = 1.0). M$_{{\rm{binaries, }}i}$ is scaled using R$_m$ to find the total astronomical mass M$_{\rm{tot, Z}_i}$ of the population. N$_{{\rm{DWD, tot,}}i}$ is the total number of DWDs in pop$_i$.

Once we determine the total ZAMS mass required to produce our simulated population for a given metallicity, the number of DWDs formed per unit solar mass at metallicity $Z_i$ is
\begin{equation}
    n_{\rm{DWD}}(Z_i) = \frac{N_{\rm{DWD, sim}}(Z_i)}{M_{\rm{ZAMS, sim}}(Z_i)}.
\end{equation}

\noindent The number of DWD’s per \textbf{m12i} star particle at metallicity $Z_i$ is then
\begin{equation}
    N_{\rm{DWD},\star} (Z_i) = n_{\rm{DWD}}(Z_i)\, M_\star,
\end{equation}

\noindent where $M_\star = 7070\,M_\odot$ is the mass per \textbf{m12i} star particle. Since $N_{\rm{DWD},\star} (Z_i)$ is not an integer, we treat the decimal component as the probability that the star particle contains an extra DWD in addition to the integer number. For each star particle, we sample with replacement $N_{\rm{DWD},\star}(Z_i)$ DWDs from the corresponding simulated \cosmic\ population at that metallicity and assign the ZAMS birth time of each DWD to the formation time of the star particle. For most DWD types there is more than one DWD binary system assigned to each \textbf{m12i} star particle.

%Already covered above
%In order to ensure that each DWD position is unique, we assign positions inside the star particle following the Ananke framework which provides offsets from the star particle center.

%\katie{I think this should go later}This gives us a final distance $d$ to the sun for all the systems, and from this and other information, we can calculate parameters relevant to the LISA observatory like Amplitude Spectral Density (ASD), signal-to-noise ratio (SNR), chirps, chirp masses, etc, as discussed in the next section.

%This will be a floating point number. The integer component gives one number of DWDs to sample with replacement from the cosmic-pop output to apply to each FIRE star particle. The decimal component will be treated as a probability $p$ of a binary existing for that particle. We assign an additional DWD to each star particle with probability $p$. The DWDs now have metallicities, ages, and galactic positions.

%\katie{I think the presentation of the next couple of paragraphs is a bit out of order. What about presenting it in the order: (1) we evolve the DWDs from their formation time up to the present day using the Peters equations (2) we discard any systems which overflow their roche lobes.}

If the DWD formation time is less than the age of the star particle, we evolve the DWD over the remaining time between its formation and star particle age, $t_{\rm{evol}}$, to produce the present-day population. Once a DWD is formed, we assume that the binary evolves only due to the emission of GWs. Due to tidal effects and mass transfer between their progenitor binaries, all DWDs in our simulations are circular, thus eccentricity does not need to be considered. The orbital evolution over the time $t_{\rm{evol}}$ is then simply defined according to \citet{Peters1964} as
\begin{equation}
    a_f = (a_i - 4\beta t_\text{evol})^{1/4},
\end{equation}
where $a_i$ is the DWD separation at formation, and 
\begin{equation}
    \beta = \frac{64G^3}{5c^5} M_1M_2(M_1+M_2)
\end{equation}
is constant throughout DWD evolution \citep{Peters1964}.

We discard any DWDs for which the sum of their ZAMS birth time, given by the star particle formation time, and DWD formation time is larger than the age of the star particle since the system will not have evolved long enough to become a DWD at present. We further discard any DWDs for which the lower mass WD overflows it's Roche lobe before present day, because the outcomes of these interactions are highly uncertain and their treatment is outside the scope of this work \citep[e.g., ][]{Shen2015, Kremer2017}. The separation at which the lower mass WD overflows its Roche Lobe is defined as

\begin{equation}
    a_{\text{RLO,}\ell} = R_{\ell} \frac{0.6 q_{\ell}^{2/3} + \ln{(1+q_{\ell}^{1/3})}}{0.49 q_{\ell}^{2/3}}
\end{equation}
where $R_{\ell}$ is the radius of the lower mass WD and $q_{\ell} = M_{\ell}/M_{h}$ is the ratio of the lower- to higher-mass WD components. \citep{Eggleton1983}. 
We define the radius of a WD following \citet{Tout1997, Hurley2000} as
\begin{equation}
    R_{\rm{WD}} = \max\Bigg(R_\text{NS}, 0.0115\sqrt{\left(\frac{M_\text{Ch}}{M}\right)^{2/3}-\left(\frac{M}{M_\text{Ch}}\right)^{2/3}} \Bigg) 
\end{equation}
\noindent where $R_\text{NS} = 1.4\cdot 10^{-5}$ R$_\odot$ is the radius of a neutron star, $M_{\text{Ch}}=1.44$ M$_\odot$ is the Chandrasekhar limit for the mass of a stable WD, and $M$ is the mass of the DWD in solar masses.

For the non-discarded systems, we log the present-day separations from which the present-day orbital frequency $f_\text{orb}$ can be found using Kepler's third law. The GW frequency is then $f_\text{GW} = 2f_\text{orb}$.

%Following the creation of an initial population, certain systems are discarded. We discard any systems with formation times longer than their assigned age from their respective star particle since these systems won’t have formed a DWD by present day and would thus not be observable by LISA. The time from DWD formation until the time when the system merges, t$_{\text{merge}}$, is defined as 
%\begin{equation}
%    t_\text{merge} = \frac{a_i^4}{4 \beta}
%\end{equation}
%where $a_i$ is the DWD separation at formation, and 
%\begin{equation}
%    \beta = \frac{64G^3}{5c^5} M_1M_2(M_1+M_2)
%\end{equation}
%is constant throughout DWD evolution \citep{Peters1964}. The delay time of the %system, $t_\text{delay}$, is defined as the sum of the DWD formation time and t$_{\text{merge}}$. Systems are also discarded if the delay time is less than the FIRE age, since they would have merged before present day. Finally, we 
%We find the time corresponding to when} the system will reach separation $a = a_\text{RLOF,2}$ by inverting Eq.(12), and \textcolor{purple}{\sout{discarding systems with $t_\text{phys} + t_\text{RLOF} \leq t_\text{FIRE}$} discard systems that would overflow their Roche Lobe before present day according to their FIRE age}.

%For the non-discarded systems, we assume evolution occurs solely through the emission of gravitational radiation. Furthermore,

%We discard any sampled DWDs for which the sum of their ZAMS birth time given by the star particle and DWD formation time is larger than the age of the star particle. 
%since DWDs orbit mainly in the second harmonic, with negligible signal stemming from the others. Systems in the LISA band are defined to have $f_\text{GW} \in [10^{-4}, 1.0]$ Hz, although they may not be observable from Earth with LISA’s current sensitivity limits.

%\katie{I think we might want to leave photometric observations to a future paper}
%In order to investigate possible follow-up with photometric observations, we also calculate the bolometric magnitude of the DWD. To calculate the luminosity of the DWD, we utilize the modified Mestel cooling described in Hurley(2003):
%\begin{equation}
%    L_{\text{WD,}i} = %\frac{bM_iZ^{0.4}}{(A_i(t_\text{evol,i}+0.1))^x}
%\end{equation}
%where $M_i$ is the WD mass in solar masses and $Z$ is the metallicity of our specified metallicity bin. $A_i$ is the baryon number for the WD subtype. 4 corresponds to helium, 15 to carbon-oxygen and 17 to oxygen-neon. $t_\text{evol, i}$ is evolution time for WD component $i$ in Myr (i.e. $t_{\text{evol, 2}}$ = $t_{\text{evol}}$, but $t_{\text{evol,1}} = t_{\text{FIRE}}-t_{\text{phys,1}}$ where $t_{\text{phys,1}}$ must be retrieved from \cosmic\ at primary formation.). The values of $b$ and $x$ are dependent on this age:
%\begin{equation}
%x = \begin{cases} 
%     1.18 & t_\text{evol, i} < 9000.0\\
%      6.48 & t_\text{evol, i} \geq 9000.0
%   \end{cases}
%\end{equation}
%\begin{equation}
%b = \begin{cases} 
%      300 & t_\text{evol, i} < 9000.0\\
%      300(9000A)^{5/3} & t_\text{evol, i} \geq 9000.0 
%   \end{cases}
%\end{equation}
%We can then find the bolometric magnitude of the system using https://www.astro.princeton.edu/~gk/A403/
%constants.pdf and https://www.astro.keele.ac.uk/jkt/pubs/
%JKTeq-fluxsum.pdf:
%\begin{equation}
%    m_{\text{bol, tot}} = -2.5 \cdot \log_{10}(10^{-0.4m_1}+10^{-0.4m_2}),
%\end{equation}
%where the bolometric magnitude of each component $m_{i}$ is %given by:
%\begin{equation}
%    m_{i} = 4.8 - 2.5 \cdot %\log_{10}\left(\frac{L_i}{L_\odot}\right)
%\end{equation}

\section{LISA detectability}
\label{sec:LISA_obs}
We use \legwork\footnote{https://legwork.readthedocs.io} to determine the detectability of our simulated DWD populations for sources with GW frequencies $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$. \legwork\ calculates the position-, orientation-, and angle-averaged signal to noise ratio (SNR) for inspiraling GW sources closely following the derivations of \citet{Flanagan1998} and using the LISA noise power spectrum density (PSD) of \citet{Robson2019}.

To lowest order in the post-Newtonian expansion, the frequency evolution of circular orbits for quadrupole GW emission is defined as
\begin{equation}
    \Dot{f}_n = \frac{48n}{5\pi} \frac{(G\mathcal{M}_c)^{5/3}}{c^5} (2\pi f_\text{orb})^{11/3}.
\end{equation}
We classify DWDs as evolving, or ``chirping", when $\Dot{f}_n \geq 1/t_\text{obs}^2$. For evolving sources, the SNR is

\begin{equation}
   \langle \rho \rangle^2_{\text{circ,evol}} = \int_{f_0}^{f_1}df   \frac{h_{c}^2}{f^2S_n(f)}
\end{equation}

\noindent where $h_c$ is the characteristic strain of the system, $S_n(f)$ is the LISA sensitivity curve of \citet{Robson2019}, and the frequency limits are determined by the orbital evolution over the observation time, $T_{\rm{obs}}=4\,\rm{yr}$. The characteristic strain for %DWDs 
circular orbits is 
%only defined for the $n=2$ harmonic and is:
\begin{equation}
    h_{c}^2 = \frac{2^{2/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}},
\end{equation}
\noindent where $\mathcal{M}_c = (M_1M_2)^{3/5}/(M_1 + M_2)^{1/5}$ is the system's chirp mass, and $D_L$ is the systems luminosity distance which we assume to be the distance of each simulated DWD to the Sun.

For stationary sources, the SNR is modified due to the lack of observable orbital evolution as
\begin{equation}
    \rho_{\text{circ,stat}}^2 = \frac{h_{2}^2T_{\text{obs}}}{4 S_n(f_2)}
\end{equation}
with the observation time $T_{\text{obs}}$. Here, $h_2$ is strain amplitude of the source for the second orbital frequency harmonic
\begin{equation}
   h_2^2 = \frac{2^{22/3}}{5}\frac{(G\mathcal{M}_c)^{10/3}}{c^8D_L^2}(\pi f_\text{orb})^{4/3}.
\end{equation}
and is connected to the characteristic strain as
\begin{equation}
    h_2^2 = \frac{\dot{f}_{2}}{f_{\rm{orb}}^2} h_c^2.
\end{equation}

%$g(n,e)$ is the relative power of gravitational radiation at the nth harmonic taken from Peters and Mathews(1963). For $n=2$ this reduces to:
%\begin{equation}
%    h_2^2 = \frac{2^{22/3}}{5}\frac{(G\mathcal{M}_c)^{10/3}}{c^8D_L^2}(\pi f_\text{orb})^{4/3}
%\end{equation}
The amplitude spectral density for a stationary system is finally defined as $ASD = h_{2} \sqrt{T_\text{obs}}$, such that the SNR for stationary source is simply, $\rho \sim ASD/S_n$.

The Galactic foreground included in the \citet{Robson2019} LISA noise curve was generated using a different binary evolution code and set of model assumptions for DWD formation and evolution \citep{Toonen2012, Korol2017}. Thus, we use the detector curve only and generate an approximate foreground from each of our populations as follows. Instead of performing a full source subtraction algorithm \citep[e.g.][]{Littenberg2020}, which is out of the scope of this work, we calculate the PSD of the Galactic DWD population with a frequency resolution set by the LISA mission time as $1/T_{\rm{obs}}\sim1/4\,\rm{yr}^{-1}\sim8\times10^{-9}\,\rm{Hz}$. We then approximate the foreground as the running median of the PSD with a boxcar window with a width of $10^3$ frequency bins similar to \citet{Benacquista2006}. The Galactic DWD PSD is truncated near $10\,\rm{mHz}$ for both of our models because we remove all DWDs which experience Roche-lobe overflow. In order to smooth the effect of this truncation in our foreground, we fit each running median with fourth-order polynomials for GW frequencies up to $1\,\rm{mHz}$, thus allowing an approximation of the foreground PSD for higher frequencies. These fits are listed in Table~\ref{tbl:fits} where the polynomial is described as
\begin{equation}
\label{eq:fit}
    \log_{10}(\rm{confusion\ fit}/\rm{Hz}) = a\,x^4 + b\,x^3 + c\,x^2 + d\,x + e
\end{equation}
\noindent and $x=\log_{10}(f_{\rm{GW}}/\rm{Hz})$. We add the fitted polynomial of the PSD's running median to the LISA noise PSD to obtain a sensitivity curve for each model.

\begin{table}[]
    \centering
    \begin{tabular}{|c|c|c|c|c|c|}
       \hline
       model & a & b & c & d & e \\
       \hline
       \hline
       F50 & -223.5 & -189.8 & -76.8 & -14.0 & -1.0 \\
       \hline
       FZ & -558.5 & -575.4 & -243.1 & -45.8 & -3.2 \\
       \hline
    \end{tabular}
    \caption{Polynomial fitting coefficients for the confusion foreground fit of Equation~\ref{eq:fit} for each binary fraction model.}
    \label{tbl:fits}
\end{table}

\section{Metallicity effects on the formation and evolution of DWDs}\label{sec:results}

\subsection{DWD types and their formation channels}\label{sec:ini}
As discussed in Section\,\ref{sec:bin_pop}, we consider four DWD sub-types, which each contribute differently to LISA's GW signals: He + He, CO + He, CO + CO, and ONe + X. Each sub-type has a unique distribution in their formation times, initial masses, radii, and orbital periods stemming from variations in their evolution channels and their formation efficiency. Here we describe the general formation scenarios and population properties of Galactic close DWDs which may be observable by LISA.
%We thus simulated \cosmic \ DWD populations separately for each DWD type and metallicity value in order to identify variations in how each type is impacted differently by changes in metallicity. A key effect is that in general, lower metallicity stars have shorter MS lifetimes and smaller initial radii than high metallicity counterparts (https://arxiv.org/pdf/2001.10404.pdf). This is discussed in greater depth later in this section.

%The resulting DWD populations from \cosmic\ gives insight in to the impact that metallicity has on these systems upon their initial formation. The trends we see within these distributions can be better interpreted through the characteristics and evolutionary channels of each DWD type which are outlined below.

%He + He: (REF = https://iopscience.iop.org/article/
%10.1086/303686/fulltext/34537.text.html)
He WDs are unable to form through single star evolution within the lifetime of the Milky Way. Instead, they originate through interactions in close binary systems or binaries with large eccentricities. Because of this, He WDs are able to form with low component masses on order $\sim$ 0.1M$_\odot$, with the majority of He WDs in our simulations having masses between 0.2-0.5 M$_\odot$. 
%, which would be impossible through SSE within a Hubble time (REF). 
He + He DWDs form through evolution of close binary systems, during which their envelopes are both stripped through RLO and CE phase interactions before Helium ignition occurs. The two progenitor stars generally have masses $\lesssim 3 M_\odot$ which is lower than the progenitors of other DWD types. Our simulated He + He DWDs have an approximately constant distribution of formation times $\gtrsim$ 2.5 Gyr. Lastly, since the ZAMS separations are skewed towards shorter values, we also see that the resulting DWD separations are smaller on average than that of other DWD types.

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/form_eff.pdf}
    \caption{The DWD formation efficiency vs metallicity of DWD populations simulated with \cosmic. Each panel shows the formation efficiency for a given DWD type. The solid lines indicate the formation efficiency for model FZ which incorporates a metallicity-dependent binary fraction. The dashed lines indicate the formation efficiency for model F50, which assumes a constant binary fraction of $50\%$. The DWD formation efficiency drops by a factor of $4-5$ for model FZ and a factor of 2-5 for model F50. See Section~\ref{sec:formeff} for a careful description of the trends for each DWD type.}
    \label{fig:form_eff}
\end{figure*}

%CO + He: 
%(REF = https://www.researchgate.net/publ ication/231115182\_Helium\_and\_Carbon-Oxygen\_White\_ Dwarfs\_in\_Close\_Binaries)
A CO WD forms when a star is able to begin the helium burning process before its envelope is stripped. Thus to form a CO + He DWD, RLO and CE stages occur after one component experiences core helium burning, but before the other component can. Most close CO + He DWDs form in approximately 2 Gyr after ZAMS and with very short periods because the He WD is formed through the ejection of a common envelope which greatly reduces the orbital separation. Because of these short formation separations, many CO + He DWDs merge before the present day.
%(Lamberts) of $O$(hour), and may merge due to GW radiation by present day. Specifically, DWDs with sub-hour periods tend to merge in less than 10$^8$ years (REF). 
Due to their asymmetric mass distributions, they have lower chirp masses, but their shorter periods make them important candidates for LISA detection. 
%Possible formation channels of these short period CO + He DWDs are explored in (REF). The fate of the binary is dependent on the orbital period that results from the final CE phase before DWD formation.

%CO + CO:
%A CO WD forms when a star is able to begin helium burning before its envelope is stripped (Lamberts,  https://arxiv.org/pdf/2011.10439.pdf). 
To prevent the two stars' envelopes from being stripped before helium ignition, CO + CO DWDs typically form from progenitors in wider orbits, and the two components may have little to no interaction during their evolution from ZAMS to DWD. CO DWDs thus have a distribution in progenitor separation that extends to larger values than for other DWD types. Most need $> 0.3$ Gyr to form. These systems have component WD masses between $0.35$--$1.0\,M_\odot$ and make up the majority of the DWD population.

%ONe + X: (REF = https://arxiv.org/pdf/2011.10439.pdf)
ONe WDs are rare and typically form from massive progenitor stars which evolve through the asymptotic giant branch (AGB) phase, thus resulting in a higher mass WD. All ONe WDs in our \cosmic\ populations, e.g., have progenitor ZAMS masses above $4\,M_\odot$, and the resulting ONe WDs have a relatively flat distribution of masses from $1.05\,M_\odot$ up to the Chandrasekkhar limit of $1.4\,M_\odot$. Because an ONe WD can have a companion of any other WD type in our study, there is a spread in their distributions for separation, secondary mass, final orbital period, and formation time. In general, however, these systems result from wider separations to allow for the evolution of the ONe component without merging, e.g. all initial separations in our \cosmic \ populations have separations $\gtrsim 1.5\,R_\odot$. ONe + X DWDs can form on short timescales, as low as $30\,\rm{Myr}$ for the majority of high-metallicity systems.

\subsection{Metallicity-dependent trends in the formation efficiency of DWDs}\label{sec:formeff}
The number of DWDs formed per unit solar mass of ZAMS star formation, or DWD formation efficiency $\eta_{\rm{form}}(Z))$, varies with metallicity. Consequently, a metallicity-dependent binary fraction further impacts the efficiency of DWD formation within the Galaxy. Figure \ref{fig:form_eff} shows the DWD formation efficiency as a function of metallicity for each DWD type and for each of our binary fraction models. In general, the formation efficiency decreases with increasing metallicity. This effect is exaggerated for model FZ which assumes a binary fraction which also decreases with increasing metallicity.

%KB cut 28 sept 21
%This drop across metallicity is due to an increase in the number of merging systems before the formation of the DWD.
%The increased propensity for merging during binary interactions stems from variations in the star's intrinsic properties caused by the effect of metallicity on stellar evolution. A higher abundance of metals results in a cooler, dimmer star with a lower central temperature and that is less compact, leading to larger stellar radii and longer main sequence lifetimes. These changes further alter the timescales for Roche-lobe overflow interactions.

%Consider two stars of high and low metallicity but equal mass. The star with higher metal abundance will have a larger radius, and a higher fraction of mass in the convective envelope (which creates longer turnover timescales) of the star/less in the core. This in theory impacts the CE phase - there would be more envelope to eject, leading to a longer energy transfer times, longer CE phases, and thus more mergers. We will now detail the unique processes for each DWD type which leads to the drop in DWD formation efficiency. For many of the subtypes, the mechanisms behind and degree to which the DWD formation efficiency is impacted can be identified within subsets of their initial orbital period.
%\katie{I think we might want to shorten this previous paragraph a bit since we go into detail later on.}

For He + He DWDs, the sudden drop in formation efficiency near $\log(Z/Z_{\odot})=-1.0$, is generally caused by the timescale for which the initially more massive star in the DWD progenitor overflows it's Roche lobe. At lower metallicities, donors tend to fill their Roche lobes while they are still on the main sequence and the mass transfer remains stable. This is because, in our \cosmic\ models %\snotes{[in just our \cosmic\ models or astrophysically? or are we stating this is just for \cosmic\ to be safe?]}, 
% KB: yeah exactly -- to be safe
lower metallicity stars evolve faster than high-metallicity stars and have larger radii near the end of the MS. At higher metallicities, mass transfer is initiated when the donor has left the main sequence and the binary enters a common envelope evolution. The ZAMS orbital period leads to different specific evolutionary channels. For short-period systems with periods below $10~\rm{days}$, this leads to a stellar merger due to insufficient orbital energy to eject the envelope. Stellar mergers continue to dominate the evolutionary pathways of systems with intermediate orbital periods ($1 < \log_{10}(P_{\rm{orb}}/\rm{day}) < 2.5$). However, an additional growing number of merging systems arises with one WD component and one stellar companion, and systems which don't interact at all and thus do not form a He + He DWD. The distinction between the various scenarios in this intermediate orbital period range depends on the combination of their ZAMS masses and orbital periods. Finally, at wider initial periods $\log_{10}(\rm{P}) > 2.5$, the decrease in formation efficiency is dominated by systems which never interact and thus do not form a DWD before the present day.

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/CEsep.pdf}
    \caption{Average interaction separation, $\overline{\mathrm{a}}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type from model FZ. Solid lines show the average separation at the first RLO for binaries in each metallicity bin. The shaded regions show the $1\sigma$ spread around the mean within each metallicity bin. The average interaction separation increases with metallicity for every DWD type. The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts.} 
    %The initial radii of high-metallicity ZAMS stars is larger than their lower-metallicity counterparts but inflate less during their evolution, creating three cases: 1) stars with wider initial separations that do not shrink enough to evolve into the LISA band before present day or fail to interact at all since their radii never increase enough to interact, 2) systems which remain stable throughout their evolution and end up in the LISA band, which requires higher interaction separations to account for the larger radii and deeper convective envelopes which need to be ejected (i.e the separation must be large enough to allow for longer CE phases), and 3) systems which merge before present day either through interactions delayed until late in their evolution from radii which do not evolve much, causing unstable mass transfer, or through very close initial separations which merged during a CE phase before present. Only case (2) would result in successful systems shown here.}
    \label{fig:CEsep}
\end{figure*}

For short-period CO + He DWD progenitor binaries with orbital periods below $\sim30~\rm{days}$, the only channel for mergers before DWD formation is during a CE evolution. This channel is similar to the stellar merger channel for He + He DWDs, but due to higher-mass progenitors the CE evolution results in the binary component with a higher mass becoming a CO WD. At higher metallicities, the CO WD merges with its companion. Higher-metallicity progenitors have a larger fraction of their mass in the convective envelope when compared to lower-metallicity stars of the same mass \citep{Amard2019, Amard2020} Thus a CE phase with a higher-metallicity progenitor requires more orbital energy to eject the common envelope, causing a larger amount of orbital shrinking which results in a merger later in its binary evolution.

For CO + He DWD progenitor systems with intermediate orbital periods ($1.5\leq \log_{10}(P_{\rm{orb}}/\rm{day})< 2.5$) the mechanisms which impact formation efficiency are complex. The dominant way to lose CO + He DWDs is stellar mergers that occur during the second CE phase. For lower-metallicity systems, the second CE is successful, while the opposite is true for higher-metallicity systems. This is again because the envelope mass of the CE evolution donor at higher metallicity is larger than it would be at lower metallicity and thus requires more orbital energy to eject in the CE phase. This leads to shorter post-CE orbital periods after the first CE phase and hence mergers during the second phase.

If a lower-metallicity system forms a CO + He DWD and a higher-metallicity system does not, this is because the initially more massive binary component initiates a CE while on the giant branch (GB) instead of the AGB. This instead leaves behind a He WD with a stellar companion, which is the dominating scenario that restricts formation efficiency. There are a few edge cases where either a He + He DWD is formed instead, or when a CO WD and a stellar companion is formed and there has been very nearly but not quite enough time for a CO + He DWD to form.

Long-period binaries with $\log_{10}(P_{\rm{orb}}/\rm{day})>2.5$ also display complex scenarios that hinder CO + He DWD formation. In near-equal contributions, our \cosmic\ simulations produce either stellar mergers or stable non-DWD binaries at the end of the Hubble time. At these orbital periods, stellar mergers always occur with a CE phase between a stellar companion and a CO or He WD. Similar to binaries with shorter orbital periods, the mergers occur because of increased CE donor envelope masses at higher metallicities. A subdominant channel of stable He + He DWDs can also occur when a high-metallicity primary overflows it's Roche lobe while still on the GB and thus forms a He WD.

The decrease in the CO + CO DWD formation efficiency with increasing metallicity stems from different evolutionary channels which arise at the ZAMS orbital period boundary of $\log_{10}(P_{\rm{orb}}/\rm{day})\simeq3$. We find that for binaries with orbital periods below this boundary, the most common way that CO + CO DWDs form at lower metallicities but not at higher metallicities is through stellar mergers during a CE phase with a donor that is still on the GB. For lower-metallicity binaries, which evolve on faster timescales, the primaries enter CE evolution while on the AGB instead and the binary is able to survive. For binaries with orbital periods above the boundary, the vast majority of systems with wide initial orbits end up as stable binaries. The systems which don’t form a CO DWD at high metallicity do so because one or both of the binary components initiate a CE phase while still on the GB thus producing a CO + He or He + He DWD.

The strongest effect which hinders formations of higher-metallicity ONe + X DWDs is the strength of metallicity-dependent stellar winds assumed in our model \citep{Vink2001}. The strength of line-driven winds varies more strongly for the more massive ($\geq5\,\rm{M}_\odot$) progenitors of ONe WDs relative to the other lower mass WD progenitors. At higher metallicities, ONe WD progenitors can lose enough mass through winds such that they don't ignite their CO cores and thus leave behind a CO WD. Conversely, the lower-metallicity progenitors retain enough mass to cause carbon ignition and leave behind an ONe WD.

\subsection{Metallicity trends in DWD progenitor common envelope separation}\label{sec:CEsep}

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/lisa_nums.pdf}
    \caption{The number of LISA-band systems formed for each DWD type as a function of the base-10 logarithm of metallicity, normalized to solar value. The solid line shows the FZ population with a metallicity-dependent binary fraction incorporated, and the dashed line shows the F50 population for a standard binary fraction of 0.5. The LISA population of DWDs is dominated by stars with super-solar metallicities. This is true even for model FZ, which drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond Z$\simeq$Z$_\odot$. There is a double peak in the He + He population; the first peak is caused by the sharp drop in formation efficiency past Z$\simeq$0.1$Z_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
    \label{fig:lisa_nums}
\end{figure*}

All systems that end up radiating GWs in the LISA band have undergone at least one phase of CE evolution. For systems which experience a stable RLO mass transfer in the first interaction, the CE phase plays a key role in shrinking systems with initially wide separations to bring them into the LISA band.

Figure \ref{fig:CEsep} shows the average separation at the first instance of CE evolution, $a_{\text{CE}}$ of all DWD progenitors that result in systems orbiting in the LISA frequency band at present day, as a function of metallicity for each DWD type. The solid lines denote the average value, and the $1\sigma$ variance is shown in the surrounding shading. The average CE separation increases in general across metallicity. Higher-metallicity binaries will interact earlier in the binary's lifetime than a lower-metallicity binary of equal separation due to their relatively larger maximum radii. Since higher-metallicity binaries are also more likely to merge during CE interactions because of their relatively more massive donor envelopes, the DWDs which survive and eventually orbit in the LISA band originate from systems with higher interaction separations which allow their orbits to shrink significantly during CE phases without merging. This regulation plays a key role in smearing out any observable effects of a metallicity-dependent binary fraction in the population of DWDs observable by LISA.

\section{Metallicity Dependence of the LISA DWD Population}
\label{sec:LISA_met}

While metallicity impacts the intrinsic properties of our simulated DWD populations as described in Sections~\ref{sec:formeff} and \ref{sec:CEsep}, when we consider the present-day Galactic close DWDs we find that the population detectable by LISA changes only numerically. The number of DWDs in the LISA frequency band decreases by $\sim50\%$ when comparing model F50 to model FZ.

\begin{figure}
	\includegraphics[width=1\columnwidth]{figures/PSD.pdf}
    \caption{The PSD of the entire Galactic DWD GW foreground, summed over all metallicities and DWD types vs GW frequency for models FZ and F50. The vertical lines show the PSD where model F50 is shown in dark blue and model FZ is shown in light blue. The dashed lines show fits to the rolling boxcar median of width 1000 bins for each PSD (see \ref{sec:LISA_obs} for a discussion). A metallicity-dependent binary fraction (model FZ) yields fewer DWDs across all frequencies than a $50\%$ binary fraction (model F50) by roughly a factor of $2$. This produces a lower GW confusion foreground for frequencies with f$_{\rm{GW}}\leq\sim10^{-3}$ Hz.}
    \label{fig:PSD}
\end{figure}

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/LISA_SNR_FZ.pdf}
	\includegraphics[width=\textwidth]{figures/LISA_SNR_F50.pdf}
    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for each DWD type where the top row shows the population from model FZ and the bottom row shows the population from model F50. In each panel, the LISA sensitivity curve, including the confusion foreground for each model, is shown in black and the total population for each model is shown in grey. We find that each model qualitatively exhibits similar characteristics and that the only change is in the yield of resolved DWDs for each type based on the strength of the confusion foreground.}
    \label{fig:LISA_SNR}
\end{figure*}

Figure \ref{fig:lisa_nums} shows the number of DWDs orbiting with frequencies $f_{\rm{GW}} > 0.1\,\rm{mHz}$ against metallicity for each DWD type. The solid lines show DWDs from model FZ, and the dashed lines show DWDs from model F50. The He + CO, CO + CO, and ONe + X populations each have strong peaks in the number of DWDs near solar metallicity at which the majority of star formation in galaxy {\bf{m12i}} occurs. The largest contribution to the population comes from metallicities above $\sim$ 0.01Z$_\odot$. The discrepancy between the two binary fraction models is also the most significant above this threshold. When creating our DWD populations the DWD formation efficiency, number of \textbf{m12i} star particles, and binary fraction all compete. The amount of stars formed in \textbf{m12i} at higher metallicity values overwhelms the drop in DWD formation efficiency by multiple orders of magnitude, so this effect dominates when determining the number of stars initially sampled in the population for $f_{\rm{b}}$.

There are two peaks in the distribution of He + He DWDs. This occurs because near $Z\simeq 0.1Z_\odot$, the DWD formation efficiency transitions from near constant values to a sharp decrease (see Figure \ref{fig:form_eff}). However, for a drop in the formation efficiency by a factor of of $\sim$ six, the amount of star formation in galaxy \textbf{m12i} increases by more than an order of magnitude for supersolar metallicities. Above $Z=Z_\odot$ this overcompensates for the efficiency drop, producing the second peak.

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/Mc_vs_dist.pdf}
    \caption{The chirp mass vs distance for each DWD type is shown. Only systems with observable evolution in their GW frequency, i.e those which are chirping, and with SNR $>7$, are shown, since these are systems for which distance can be separated from chirp mass within their strain amplitude. Each panel shows one DWD type, summed over all metallicities. Model FZ is indicated with solid light blue contours, and model F50 is indicated with dark blue dashed contours respectively. Contours are shown at the $5^{\rm{th}}$, 25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$, and 95$^{\rm{th}}$ percentiles. Despite intrinsic changes to population properties induced by a metallicity-dependent binary fraction, and a reduction in the height of the DWD Galactic foreground the distributions are very similar.}
    \label{fig:Mc_vs_dist}
\end{figure*}

The reduced number of DWDs in model FZ relative to model F50 is also apparent in the GW power spectral density (PSD) LISA will observe. We show the GW PSD of each model, as well as the confusion estimate, in Figure~\ref{fig:PSD}. While model F50 (dark blue) and model FZ (light blue) produce several thousand large spikes in the PSD across LISA's frequency band, the overall foreground height, including the confusion, is larger for model F50. This is a direct consequence of the overall reduction in the size of the close DWD population in model FZ.

Similar to previous studies, we find that LISA will be able to resolve several thousand DWDs. Figure \ref{fig:LISA_SNR} shows the amplitude spectral density vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the top and bottom rows show results for models FZ and F50 respectively. For comparison, we also show the LISA sensitivity curve, including the 
modeled confusion foreground from each population in black, and the the entire population for each model in grey. Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models. The populations containing at least one He WD occupy the lower-ASD, higher-GW frequency region of parameter space compared to the total population, with CO + He DWDs having larger ASDs than the He + He DWD population. Conversely, DWD types without a He WD component tend to occupy the higher-ASD, lower-GW frequency region of parameter space. This difference is largely due to the formation scenario of DWDs containing a He WD, which form from the ejection of a common envelope created by the He WD progenitor. These lower mass progenitors overflow their Roche lobes at closer separations relative to the higher mass progenitors (e.g. Figure~\ref{fig:CEsep}) and thus also produce closer DWDs. While the distance to any one DWD strongly influences its ASD, DWD populations without a He WD component have, on average, higher ASDs due to their more massive WD components.

We note that while the height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 2 for model FZ relative to model F50, the number of resolved sources is not reduced to an equal degree. This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved. Between models FZ and F50, the number of resolvable systems with SNR $>7$ over all DWD types decreases by only $\sim14\%$.

The distance and chirp mass of DWDs which exhibit observable orbital evolution due to the emission of GWs during the LISA mission can be measured. This is because the chirp mass -- distance degeneracy in the observed strain can be broken with the observed GW frequency evolution, or chirp. Assuming a chirp resolution of $1/T_{\rm{obs}}^2 \sim 8\times10^{-9}\,\rm{Hz}^2$, we select the DWDs whose chirp masses and distances can be measured. Figure \ref{fig:Mc_vs_dist} shows the chirp mass vs the luminosity distance for each DWD type in this selected population. The contours show the $5^{\rm{th}}$, $25^{\rm{th}}$, $50^{\rm{th}}$, $75^{\rm{th}}$, and $95^{\rm{th}}$ percentiles for models FZ (light blue) and F50 (dark blue, dashed). Despite the reduction in the height of the confusion foreground when considering model FZ relative to F50, we find that LISA is unable to differentiate between the chirp mass -- distance distributions of the two models.

\section{Binary evolution assumption variations}
\label{sec:model_compare}

\begin{figure}
	\includegraphics[width=0.45\textwidth]{figures/model_comp.pdf}
    \caption{The top panel shows the Galactic DWD confusion fit vs GW frequency for different binary evolution assumption variations (colors) with model F50 shown in dashed lines and model FZ shown in solid lines. The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for model FZ to model F50 vs to number of DWDs orbiting in the LISA band for model F50 only. While both the height of the confusion foreground and number of LISA DWDs changes for each variation, the FZ models within each variation exhibit a constant reduction by a factor of two compared with the F50 models.}
    \label{fig:model_comp}
\end{figure}

In order to test the robustness of the reduction of the height of the Galactic DWD GW foreground when assuming a metallicity-dependent binary fraction, we repeat our analysis using three different binary evolution assumption variations. For each variation, we consider models FZ and F50 as done in the fiducial case described above. In variation $q3$, we vary the assumption for the critical mass ratios at which a RLO interaction remains stable or becomes unstable from our fiducial assumptions such that the critical mass ratio is increased to $3.0$ and thus allows stable mass transfer for more massive RLO donors. In variations $\alpha25$ and $\alpha5$, we modify the common envelope ejection efficiency to be either much less ($\alpha=0.25$) or more ($\alpha=5$) than in our fiducial assumption ($\alpha=1$). Larger common envelope ejection efficiencies lead to wider post-CE separations, while smaller ejection efficiencies either lead to closer post-CE separations or mergers where the envelope ejection fails.

In each variation, changing the binary evolution assumptions dramatically changes the formation and evolution of the DWD populations. These changes lead to large shifts in the overall number of close DWDs in our synthetic present-day Milky-Way-like galaxies. We find that the total number of DWDs with $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$ increases for both variations $q3$ and $\alpha5$. This is because there are fewer stellar mergers which occur before the formation of a DWD, thus allowing more systems to evolve due to GW emission and orbit in the LISA frequency band at present. Conversely, for variation $\alpha0.25$, we find that the number of DWDs orbiting with frequencies in the LISA band is drastically reduced. This is because of the highly inefficient use of orbital energy to eject the common envelope, thus producing more stellar mergers, or closer binaries which are more prone to future mergers.

Interestingly, when we compare the populations of each binary fraction model for our variations, we find that the number of close DWDs reduces by the constant factor of two as seen in our fiducial set of assumptions. This is illustrated in \ref{fig:model_comp}. The top panel shows the confusion foreground fits for each binary evolution variation (different colored lines) and for each binary fraction model where the solid lines show FZ models and dotted lines show F50 models. The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for the FZ models vs the F50 models for each variation. Even though the number of DWDs in the LISA band spans over two orders of magnitude, the ratio of FZ to F50, as well as the spectral shape of the confusion fit, stays fixed at a constant factor of two reduction. This suggests that assuming a metallicity-dependent binary fraction reduces the size of the Galactic close DWD population by a factor of $\sim$ two and the strength of the Galactic DWD GW foreground for LISA \emph{regardless of the chosen binary evolution model}.

\section{Conclusions}\label{sec:conclusions}
In this study, we have investigated the effects of assuming a metallicity-dependent binary fraction on the formation and evolution of the Galactic population of DWDs with a special focus on the implications for LISA. Based on our synthetic Milky-Way-like galaxy catalogs of DWDs, we find that applying a metallicity-dependent binary fraction changes the formation efficiency and evolutionary history of DWD populations. However, when considering the close DWD populations observable by LISA, we find that the only distinguishing features between models which assume a metallicity-dependent binary fraction (model FZ) and models which assume a flat $50\%$ binary fraction (model F50) are the population sizes and the strength of the Galactic DWD GW foreground. Models which assume a metallicity-dependent binary fraction produce Galactic DWD populations that are reduced by a factor of two relative to the standard model assumptions. This reduction extends to the height of the confusion foreground in the LISA data stream.

We extended our study to include three binary evolution assumption variations to investigate whether the DWD population reduction was robust to changes in assumptions for mass transfer stability and common envelope ejection efficiencies. While our binary evolution assumption variations change the size of the LISA-observable populations dramatically, the reduction in the size of the close Galactic DWD population and the height of the confusion foreground for models which assume a metallicity-dependent binary fraction is robust. An important consequence of a lower Galactic DWD confusion foreground is that relative to the total DWD population, more DWDs can be individually resolved because of the reduction in competing GW signals. While the number of DWDs radiating GWs in the LISA frequency band is reduced by a factor of two for model FZ relative to model F50, the number of resolved sources is less affected with a population-wide reduction of $14\%$. These results are far-reaching since the strength of the Galactic DWD confusion foreground has direct consequences on the detectability of all other LISA sources with small SNRs. An increase in resolution capability from the reduced confusion foreground can be extended to other galactic binaries that LISA will observe at these frequencies like those involving neutron stars and stellar-origin black holes, as well as other more exotic GW sources like merging supermassive black holes, extreme mass ratio inspirals, or cosmological GW backgrounds. Based on our results, we suggest that studies which employ fits to the confusion foreground based on population synthesis results consider reducing the strength of the Galactic foreground PSD by a factor of two.

\begin{acknowledgments}
The authors are grateful for helpful discussions with Carles Badenes, Christine Mazzola Daher, and the Gravitational Waves and Astronomical Data groups at the CCA.  S.T.\ was supported by an Undergraduate Student Research Award (USRA) at CITA from the Natural Sciences and Engineering Research Council of Canada (NSERC), Reference \# 498223. K.B.\ is grateful for support from the Jeffrey L. Bishop Fellowship. The Flatiron Institute is supported by the Simons Foundation.
\end{acknowledgments}

\section*{Data Availability}

All data and software required to reproduce our results will be shared through GitHub and Zenodo on acceptance of this manuscript.

\software{\texttt{astropy} \citep{astropy:2013, astropy:2018}; 
          \cosmic\ \citep{Breivik2020a};
          \legwork\ (legwork.readthedocs.io);
          \texttt{matplotlib}\ \citep{matplotlib}; 
          \texttt{numpy}\ \citep{numpy}; 
          \texttt{pandas}\ \citep{mckinney-proc-scipy-2010, reback2020pandas}; 
          \texttt{scipy}\ \citep{scipy}
          }

\bibliographystyle{aasjournal}
\bibliography{bib}{}

\end{document}

### 2021-11-23 src/figures/LISA_SNR.py
adding pipeline

@@ -1,0 +1,116 @@
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import astropy.units as u
+from legwork.visualisation import plot_sensitivity_curve
+from legwork import psd
+
+
+def plot_LISAcurves(model):
+    def func(x, a, b, c, d, e):
+        return a + b * x + c * x ** 2 + d * x ** 3 + e * x ** 4
+
+    def cosmic_confusion(f, L, t_obs=4 * u.yr, approximate_R=True, confusion_noise=None):
+        lisa_psd_no_conf = psd.power_spectral_density(
+            f, confusion_noise=None, t_obs=4 * u.yr
+        )
+        conf = 10 ** func(
+            x=np.log10(f.value), 
+            a=popt[0], 
+            b=popt[1], 
+            c=popt[2], 
+            d=popt[3], 
+            e=popt[4]
+        ) * t_obs.to(u.s)
+
+        psd_plus_conf = conf + lisa_psd_no_conf
+        return psd_plus_conf.to(u.Hz ** (-1))
+
+    resolved = pd.read_hdf("../data/results.hdf", key="resolved_DWDs_{}_{}".format(model, "fiducial"))
+    popt = pd.read_hdf("../data/results.hdf", key="conf_fit_DWDs_{}_{}".format(model, "fiducial"))
+    popt = popt.values.flatten()
+    
+    resolved_HeHe = resolved.loc[(resolved.kstar_1 == 10) & (resolved.kstar_2 == 10)]
+    resolved_COHe = resolved.loc[((resolved.kstar_1 == 11) & (resolved.kstar_2 == 10)) |
+                                 ((resolved.kstar_2 == 11) & (resolved.kstar_1 == 10))]
+    resolved_COCO = resolved.loc[(resolved.kstar_1 == 11) & (resolved.kstar_2 == 11)]
+    resolved_ONeX = resolved.loc[((resolved.kstar_1 == 12) & (resolved.kstar_2.isin([10,11,12]))) |
+                                 ((resolved.kstar_2 == 12) & (resolved.kstar_1.isin([10,11,12])))]
+    
+    t_obs = 4 * u.yr
+    
+    
+    psd_conf = psd.power_spectral_density(
+        f=np.linspace(1e-4, 1e-1, 1000000) * u.Hz, 
[…]

### 2021-11-23 src/figures/Mc_vs_dist.py

@@ -1,0 +1,133 @@
+from matplotlib.ticker import AutoMinorLocator
+import legwork.utils as utils
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import astropy.units as u
+import seaborn as sns
+
+model = "fiducial"
+
+resolved_dat_FZ = pd.read_hdf(
+   "../data/results.hdf", key="resolved_DWDs_{}_{}".format("FZ", model)
+)
+resolved_dat_FZ = resolved_dat_FZ.loc[resolved_dat_FZ.resolved_chirp == 1.0]
+
+resolved_dat_F50 = pd.read_hdf(
+    "../data/results.hdf", key="resolved_DWDs_{}_{}".format("F50", model)
+)
+resolved_dat_F50 = resolved_dat_F50.loc[resolved_dat_F50.resolved_chirp == 1.0]
+
+Heplot = resolved_dat_FZ.loc[
+    (resolved_dat_FZ.kstar_1 == 10) & (resolved_dat_FZ.kstar_2 == 10)
+]
+COHeplot = resolved_dat_FZ.loc[
+    ((resolved_dat_FZ.kstar_1 == 11) & (resolved_dat_FZ.kstar_2 == 10)) |
+    ((resolved_dat_FZ.kstar_2 == 11) & (resolved_dat_FZ.kstar_1 == 10))
+]
+COplot = resolved_dat_FZ.loc[
+    (resolved_dat_FZ.kstar_1 == 11) & (resolved_dat_FZ.kstar_2 == 11)
+]
+ONeplot = resolved_dat_FZ.loc[
+    ((resolved_dat_FZ.kstar_1 == 12) & (resolved_dat_FZ.kstar_2.isin([10, 11, 12]))) |
+    ((resolved_dat_FZ.kstar_2 == 12) & (resolved_dat_FZ.kstar_1.isin([10, 11, 12])))
+]
+
+
+Heplot_F50 = resolved_dat_F50.loc[
+    (resolved_dat_F50.kstar_1 == 10) & (resolved_dat_F50.kstar_2 == 10)
+]
+COHeplot_F50 = resolved_dat_F50.loc[
+    ((resolved_dat_F50.kstar_1 == 11) & (resolved_dat_F50.kstar_2 == 10)) |
+    ((resolved_dat_F50.kstar_2 == 11) & (resolved_dat_F50.kstar_1 == 10))
+]
+COplot_F50 = resolved_dat_F50.loc[
[…]

### 2021-11-23 src/figures/PSD.py

@@ -1,0 +1,98 @@
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import astropy.units as u
+
+
+def func(x, a, b, c, d, e):
+    return a + b * x + c * x ** 2 + d * x ** 3 + e * x ** 4
+
+model = "fiducial"
+colors = ["#add0ed", "#2b5d87", "#4288c2", "#17334a"]
+Tobs = 4 * u.yr
+
+power_dat_F50 = pd.read_hdf(
+    "../data/results.hdf", key="total_power_DWDs_{}_{}".format("F50", model)
+)
+popt_F50 = pd.read_hdf("../data/results.hdf",  key="conf_fit_DWDs_{}_{}".format("F50", model))
+popt_F50 = popt_F50.values.flatten()
+
+power_dat_FZ = pd.read_hdf(
+    "../data/results.hdf", key="total_power_DWDs_{}_{}".format("FZ", model)
+)
+popt_FZ = pd.read_hdf("../data/results.hdf", key="conf_fit_DWDs_{}_{}".format("FZ", model))
+popt_FZ = popt_FZ.values.flatten()
+
+conf_fit_FZ = (
+    10
+    ** func(
+        x=np.log10(np.linspace(1e-4, 1e-1, 100000)),
+        a=popt_FZ[0],
+        b=popt_FZ[1],
+        c=popt_FZ[2],
+        d=popt_FZ[3],
+        e=popt_FZ[4],
+    )
+    * Tobs.to(u.s).value
+)
+
+conf_fit_F50 = (
+    10
+    ** func(
+        x=np.log10(np.linspace(1e-4, 1e-1, 100000)),
+        a=popt_F50[0],
+        b=popt_F50[1],
+        c=popt_F50[2],
+        d=popt_F50[3],
+        e=popt_F50[4],
+    )
+    * Tobs.to(u.s).value
+)
+
+
+fig, (ax1) = plt.subplots(1, 1, figsize=(6, 4.2))
+plt.plot(
+    power_dat_F50.f_gw[::10],
+    power_dat_F50.strain_2[::10] * Tobs.to(u.s).value,
+    c=colors[1],
+    lw=1,
+    alpha=1,
+    rasterized=True,
+)
+plt.plot(
+    power_dat_FZ.f_gw[::10],
[…]

### 2021-11-23 src/figures/form_eff.py

@@ -1,0 +1,155 @@
+from matplotlib.ticker import AutoMinorLocator
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import utils
+
+'''
+Creates plot files with formation efficiency of DWDs. In order to
+run this, there must be already-existing LISA band files created with
+make_galaxy() at pathtoLband.
+    
+INPUTS
+----------------------
+pathtodat [str]: path to folder containing datfiles 
+pathtoLband [str]: path to folder containing LISA band files
+pathtosave [str]: path to folder to save formation efficiency information to
+    
+RETURNS
+----------------------
+No direct function outputs, but saves formation efficiency data for all
+DWD types and metallicity bins to files contained in pathtosave.
+'''
+met_arr = np.logspace(np.log10(1e-4), np.log10(0.03), 15)
+met_arr = np.round(met_arr, 8)
+met_arr = np.append(0.0, met_arr)
+Z_sun = 0.02
+kstar1_list = ['10', '11', '11', '12']
+kstar2_list = ['10', '10', '11', '10_12']
+labels = ['10_10', '11_10', '11_11', '12']
+pathtodat = "../data/"
+
+DWDeff = pd.read_hdf('../data/results.hdf', key='DWDeff_{}_{}'.format("FZ", "fiducial"))
+DWDeff05 = pd.read_hdf('../data/results.hdf', key='DWDeff_{}_{}'.format("F50", "fiducial"))
+
+effHe = DWDeff.He.values
+effCOHe = DWDeff.COHe.values
+effCO = DWDeff.CO.values
+effONe = DWDeff.ONe.values
+
+effHe05 = DWDeff05.He.values
+effCOHe05 = DWDeff05.COHe.values
+effCO05 = DWDeff05.CO.values
+effONe05 = DWDeff05.ONe.values
+
+fig, ax = plt.subplots(1, 4, figsize=(16, 4.5))
+ax[0].plot(
+    np.log10(met_arr[1:] / Z_sun),
+    effHe * 1e3,
+    color='xkcd:tomato red',
+    drawstyle='steps-mid',
+    lw=3,
+    label='FZ',
+    rasterized=True
+)
+
+ax[0].plot(
[…]

### 2021-11-23 src/figures/model_comp.py

@@ -1,0 +1,128 @@
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+import astropy.units as u
+
+models = ["log_uniform", "qcflag_4", "alpha_0.25", "alpha_5"]
+model_names = ["fiducial", "q3", "alpha25", "alpha5"]
+colors = sns.color_palette("mako", n_colors=len(models))
+
+Tobs = 4 * u.yr
+
+
+def func(x, a, b, c, d, e):
+    return a + b * x + c * x ** 2 + d * x ** 3 + e * x ** 4
+
+
+mosaic = """
+AA
+AA
+BB
+"""
+
+fig = plt.figure(figsize=(6, 8))
+ax_dict = fig.subplot_mosaic(mosaic)
+
+
+lisa_ratio = []
+n_lisa_F50_list = []
+
+popt_F50_list = []
+popt_FZ_list = []
+
+for model in model_names:
+    numsFZ = pd.read_hdf("../data/results.hdf", key="numLISA_30bins_{}_{}".format("FZ", model))
+    numsF50 = pd.read_hdf("../data/results.hdf", key="numLISA_30bins_{}_{}".format("F50", model))
+
+
+    popt_F50 = pd.read_hdf("../data/results.hdf", key="conf_fit_DWDs_{}_{}".format("F50", model))
+    popt_FZ = pd.read_hdf("../data/results.hdf", key="conf_fit_DWDs_{}_{}".format("FZ", model))
+
+    n_lisa_F50 = np.sum(numsF50.values.flatten())
+    n_lisa_FZ = np.sum(numsFZ.values.flatten())
+
+    lisa_ratio.append(n_lisa_FZ / n_lisa_F50)
+    n_lisa_F50_list.append(n_lisa_F50)
+
+    popt_F50 = popt_F50.values.flatten()
+    popt_FZ = popt_FZ.values.flatten()
+
+    popt_F50_list.append(popt_F50)
+    popt_FZ_list.append(popt_FZ)
+
+
+for popt_F50, popt_FZ, ii in zip(popt_F50_list, popt_FZ_list, range(len(popt_FZ_list))):
+    conf_fit_FZ = (
+        10
+        ** func(
+            x=np.log10(np.linspace(1e-4, 1e-1, 100000)),
+            a=popt_FZ[0],
+            b=popt_FZ[1],
+            c=popt_FZ[2],
[…]

### 2021-11-23 src/figures/pipeline.py

@@ -1,0 +1,56 @@
+#=========================================================================
+# This script creates LISA DWD galaxies across 15 metallicity bins,
+# incorporating the metallicity-dependent binary fraction as
+# discussed in Thiele et al. (2021).
+#
+# Authors: Sarah Thiele & Katelyn Breivik
+# Last updated: Oct 14th, 2021
+#=========================================================================
+
+import numpy as np
+from astropy import constants as const
+from astropy import units as u
+import astropy.coordinates as coords
+from astropy.time import Time
+import argparse
+import postproc as pp
+
+
+DWD_list = ['He_He', 'CO_He', 'CO_CO', 'ONe_X']
+dat_path = "../data/"
+FIRE_path = "../data/"
+models = ['fiducial', 'alpha25', 'alpha5', 'q3']
+interfile = False
+nproc = 4
+
+for model in models:
+    pp.save_full_galaxy(
+        DWD_list, dat_path, FIRE_path, dat_path, interfile, model, nproc
+    )
+    print('Gx done!')
+
+    if model == 'fiducial':
+        pp.get_formeff(
+            pathtodat=dat_path, pathtosave=dat_path
+        )
+    print('formation efficiency done')
+
+    pp.get_interactionsep_and_numLISA(
+        pathtodat=dat_path, pathtosave=dat_path, model=model, var=True
+    )
+    print('interaction sep FZ done')
+ 
+    pp.get_interactionsep_and_numLISA(
+        pathtodat=dat_path, pathtosave=dat_path, model=model, var=False
+    )
+    print('interaction sep F50 done')
+    
+    pp.get_resolvedDWDs(
+        dat_path, dat_path, var=True, model=model, window=1000
+    )
+    print('resolved FZ done')
+    pp.get_resolvedDWDs(
+        dat_path, dat_path, var=False, model=model, window=1000
+    )
+
+    print('resolved F50 done')

### 2021-11-23 src/figures/utils.py

@@ -1,0 +1,129 @@
+import numpy as np
+
+#===================================================================================
+# File and Organizing Functions:
+#===================================================================================
+
+def getfiles(kstar1, kstar2, model):
+    '''
+    Get the list of COSMIC dat files used to create 
+    DWD populations.
+    
+    INPUTS
+    ----------------------
+    kstar1 [10, 11, 12]: type of first WD
+    kstar2 [10, 11, 12]: type of second WD
+    model: model variation from 'fiducial', 'q3', 'alpha25', 'alpha5'
+    
+    RETURNS
+    ----------------------
+    filename_list [list, str]: list of files names
+    label [str]: DWD type label
+    '''
+    met_list = [0.0001, 0.00015029, 0.00022588, 0.00033948, 0.00051021, 
+                0.00076681, 0.00115245, 0.00173205, 0.00260314, 0.00391233, 
+                0.00587993, 0.0088371, 0.01328149, 0.01996108, 0.03]
+    
+    filename_list = []
+    for ii in range(len(met_list)):
+        fname = '{}_{}_{}_{}.h5'.format(model, kstar1, kstar2, ii)
+        filename_list.append(fname)
+        
+    if kstar1 == '12':
+        label='12'
+    else:
+        label='{}_{}'.format(kstar1, kstar2)
+        
+    return filename_list, label
+
+
+def Lband_files(kstar1, kstar2, model, var=True):
+    '''
+    Creates list of LISA band filenames for given DWD type.
+    
+    INPUTS
+    ----------------------
+    kstar1 [10, 11, 12]: type of first WD
+    kstar2 [10, 11, 12]: type of second WD
+    model ['fiducial', 'alpha25', 'alpha5', 'q3']: specifies binary evolution assumptions
+    var [bool]: if True, creates keys for FZ, else for F50
+    
+    RETURNS
+    ----------------------
+    files [list, str]: list of keys
+    '''
+    met_list = [0.0001, 0.00015029, 0.00022588, 0.00033948, 0.00051021, 
+                0.00076681, 0.00115245, 0.00173205, 0.00260314, 0.00391233, 
+                0.00587993, 0.0088371, 0.01328149, 0.01996108, 0.03]
+    if var:
+        var_list = [0.4847, 0.4732, 0.4618, 0.4503, 0.4388, 
[…]

### 2021-11-24 src/ms.tex
add in legwork citation

@@
 \label{sec:LISA_obs}
-We use \legwork\footnote{https://legwork.readthedocs.io} to determine the detectability of our simulated DWD populations for sources with GW frequencies $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$.
+We use \legwork\footnote{https://legwork.readthedocs.io} \citep{Wagg2021} to determine the detectability of our simulated DWD populations for sources with GW frequencies $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$.
 \legwork\ calculates the position-, orientation-, and angle-averaged signal to noise ratio (SNR) for inspiraling GW sources closely following the derivations of \citet{Flanagan1998} and using the LISA noise power spectrum density (PSD) of \citet{Robson2019}.
@@
           \cosmic\ \citep{Breivik2020a};
-          \legwork\ (legwork.readthedocs.io);
+          \legwork\ \citep{Wagg2021};
           \texttt{matplotlib}\ \citep{matplotlib}; 

### 2021-11-25 src/ms.tex
note interaction separation tank in intersep figure from binning, strip utils.py of Lband filename function.

--- 2021-11-23 src/ms.tex
@@
 The average interaction separation increases with metallicity for every DWD type.
-The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts.}
+The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts.
+The sharp drop of the CO + CO average at the highest-metallicity bin is due to binning effects of the figure: it only contains 115 systems, of which the majority stem from a single low-separation system which was sampled 94 times times during the simulation.}
     %The initial radii of high-metallicity ZAMS stars is larger than their lower-metallicity counterparts but inflate less during their evolution, creating three cases: 1) stars with wider initial separations that do not shrink enough to evolve into the LISA band before present day or fail to interact at all since their radii never increase enough to interact, 2) systems which remain stable throughout their evolution and end up in the LISA band, which requires higher interaction separations to account for the larger radii and deeper convective envelopes which need to be ejected (i.e the separation must be large enough to allow for longer CE phases), and 3) systems which merge before present day either through interactions delayed until late in their evolution from radii which do not evolve much, causing unstable mass transfer, or through very close initial separations which merged during a CE phase before present.

### 2021-11-25 src/figures/utils.py

@@ -26,7 +26,10 @@ def getfiles(kstar1, kstar2, model):
     
     filename_list = []
     for ii in range(len(met_list)):
-        fname = '{}_{}_{}_{}.h5'.format(model, kstar1, kstar2, ii)
+        if kstar1 == '12':
+            fname = '{}_12_10_12_{}.h5'.format(model, ii)
+        else:
+            fname = '{}_{}_{}_{}.h5'.format(model, kstar1, kstar2, ii)
         filename_list.append(fname)
         
     if kstar1 == '12':
@@ -35,42 +38,6 @@ def getfiles(kstar1, kstar2, model):
         label='{}_{}'.format(kstar1, kstar2)
         
     return filename_list, label
-
-
-def Lband_files(kstar1, kstar2, model, var=True):
-    '''
-    Creates list of LISA band filenames for given DWD type.
-    
-    INPUTS
-    ----------------------
-    kstar1 [10, 11, 12]: type of first WD
-    kstar2 [10, 11, 12]: type of second WD
-    model ['fiducial', 'alpha25', 'alpha5', 'q3']: specifies binary evolution assumptions
-    var [bool]: if True, creates keys for FZ, else for F50
-    
-    RETURNS
-    ----------------------
-    files [list, str]: list of keys
-    '''
-    met_list = [0.0001, 0.00015029, 0.00022588, 0.00033948, 0.00051021, 
-                0.00076681, 0.00115245, 0.00173205, 0.00260314, 0.00391233, 
-                0.00587993, 0.0088371, 0.01328149, 0.01996108, 0.03]
-    if var:
-        var_list = [0.4847, 0.4732, 0.4618, 0.4503, 0.4388, 
-                    0.4274, 0.4159, 0.4044, 0.3776, 0.3426, 
-                    0.3076, 0.2726, 0.2376, 0.2027, 0.1677]
-      
-        if kstar1 != '12':
-            files = ['Lband_{}_{}_{}_{}_{}.hdf'.format(kstar1, kstar2, int(met*1e5), int(var*1e5), model) for var, met in zip(var_list, met_list)]
-        else:
-            files = ['Lband_{}_{}_{}_{}.hdf'.format(kstar1, int(met*1e5), int(var*1e5), model) for var, met in zip(var_list, met_list)]
-    else:
-        if kstar1 != '12':
[…]

### 2021-11-25 src/ms.tex
adding in close binary caveat

@@
 
+Note that the average CE separation is close to the qualitative limit for close binaries of $P_{\rm{orb}}\gtrsim10^{4}\,\rm{day}$ for the CO + CO and ONe + X binaries.
+We investigated the fraction of close DWD progenitors which formed with orbital periods above this range for each DWD type.
+For the He + He DWDs, less than $10\%$ of all progenitors, regardless of metallicity originate in wide orbits.
+For CO + He population, the percentage increases from $10$--$15\%$ from low to high metallicities, and for the more massive CO + CO and ONe + X DWDs, the percentages increase from $15$--$25\%$ and $20$--$40\%$ respectively.
+This suggests that our application of the close binary fraction may not be valid over the entire range of the DWD progenitor population.
+However, since the relative sizes of CO + CO and ONe + X are small compared to the He + He and CO + He populations, we leave a further investigation of these effects to a future study.
+
 \section{Metallicity Dependence of the LISA DWD Population}

### 2021-11-26 src/ms.tex

@@
 Of the stars which are born with a binary companion, many will undergo interactions which bring the two stars closer together, eventually forming a close double white dwarf (DWD).
-Close DWDs, with orbital periods shorter than $\sim2.75\,\rm{hr}$ %\snotes{[close DWDs are defined to have $P_{\rm{orb}}\leq10^4$ days - are we noting 2.75 hrs for GW sources specifically?
-If so maybe we should reword this bit because it reads like it conflicts with the abstract?]},
-%Katie: Close DWDs is a different classification than close binaries.
-are the largest source by number of mHz gravitational waves (GWs) in the Galaxy \citep[e.g.,][]{LISAMissionProposal}.
+Close DWDs, with orbital periods shorter than $\sim2.75\,\rm{hr}$ are the largest source by number of mHz gravitational waves (GWs) in the Galaxy \citep[e.g.,][]{LISAMissionProposal}.
 The Laser Interferometer Space Antenna (LISA) is expected to resolve at least $10^4$ individual DWD binaries in the Milky Way and will also observe GW emission from the entire Galactic DWD population through the unresolved foreground created by overlapping signals at sub-mHz frequencies \citep[e.g.,][]{Nelemans2001a, Ruiter2010, Nissanke2012, Yu2013, Korol2017, Lamberts2019, Breivik2020a}.
@@
 Because close DWDs are the remnants of close, solar-type binary stars, this anti-correlation plays an important role in the formation, evolution, and characteristics of the DWD population that LISA will observe.
-
-%These relatively close binaries are likely to form from fragmentation, accretion, and inward migration in protostellar disks.
-This is in contrast to wide binaries whose formation channels stem from fragmentation of molecular cores, which is generally unaffected by the opacity of the material.
-%This is depicted in the ``metallicity invariance" for the IMF and binary fraction beyond separations of 200 au for -1.0 $<$ [Fe/H] $<$ 0.5 of Mazzola et al.
-(2020).
-Within protostellar disks however, it has been shown through analytical models and hydrodynamic simulations that the probability of disk fragmentation decreases with increasing metallicity (Mazzola et al.
-2020).
-Metal-poor cores are unable to radiate through molecular transitions as effectively, and so are generally hotter and must reach higher masses in order to collapse into disks, which instigates higher accretion rates and results in gravitational instability and thus fragmentation.
-Furthermore, if you decrease a disk’s metallicity and thus its optical depth, the mid-plane of the disk is able to radiate and cool more efficiently which encourages fragmentation.
-(Mazzola et al.
-2020 and others).
-
-%Numerically, the dominant sources for LISA will be DWDs from the Milky Way.
-There is an expectation that several tens of millions of detached DWDs will be present in the LISA band with about ten thousand of these to be individually resolvable  with $f_\text{GW} \geq 0.4$ mHz (Nelemans et al.
-2001b).
-DWDs are nice systems to work with: a compact binary which emits continuously and near monochromatically GW signals in the source frame (LISA proposal REF), and of which the second harmonic of their signals can be measured with high accuracy.
-In general, higher frequency systems are louder and better characterized than low frequency counterparts.
-In fact, at low frequencies we find that the high number of DWDs begin to overlap in their signals, creating a stochastic background.
-This effective “confusion signal” arises for these low frequencies from having more than one DWD per frequency bin, $f_\text{bin} = 1 / t_\text{obs}$, where $t_\text{obs}$ is the length of observation time for the LISA mission, which we assume to be four years (LISA proposal REF).
-
-%The science that the LISA mission will contribute to is diverse in scope.
-Specific to DWDs, the hope is to use the distribution of chirp masses and periods to constrain the impact of the common envelope, which drastically tightens the orbit of the systems (Toonen et al.
-2014).
-A complete sample will also allow for direct comparison with the post-common envelope binaries, which have undergone only one episode of the common envelope (Rebassa-Mansergas et al.
-2012).
-In some cases, the frequency derivative will be measurable and allow us to determine if mass transfer is happening (Breivik et al.
-2018) and/or tidal interactions are deforming the white dwarfs.
 
@@
 
-%The Latte suite of FIRE-2 cosmological zoom-in baryonic simulations of Milky Way-mass galaxies \citep{Wetzel2016}, part of the Feedback In Realistic Environments (FIRE) simulation project, were run using the Gizmo gravity plus hydrodynamics code in meshless finite-mass (MFM) mode \citep{Hopkins2015} and the FIRE-2 physics model \citep{Hopkins2018}.
-Synthetic Gaia DR2-like surveys of the Latte suite of FIRE-2 simulations were created via the Ananke framework \citep{Sanderson2020}.
-
 \subsection{Binary population models}
@@
 \cosmic\ has been used in several studies to examine the effects of binary evolution on binary populations from blue stragglers \citep{Leiner2021} and heartbeat stars \citep{Jayasinghe2021}, to white dwarf populations \citep{Kremer2017,Breivik2018,Kilic2021}, to merging compact object populations in isolated binaries \citep{Zevin2020b, Zevin2020a, Zevin2021, Wong2021, Mandhai2021} and in dynamical environments around super-massive black holes \citep{Stephan2019, Wang2021}.
-%Recently, \cosmic\ was integrated with the Cluster Monte Carlo (CMC) code to enable direct comparisons between isolated binary evolution and the evolution of stars in globular clusters \citep{Rodriguez2021}.
-Since this work considers the effects of the metallicity-dependence of the close isolated binary fraction, we leave direct comparisons to globular clusters to future work.
 
@@
 
-% I'm suggesting text above since we have a boiler-plate style that we use to stay consisten in the literature.
-%Rather than evolving an initial binary population’s individual stars - a computationally expensive process - \cosmic\ uses Monte Carlo statistics to create fixed populations that would be expected based on parameters like SFH and the known processes within binary star evolution.
-In the \cosmic\ framework, binaries are initialized iteratively with zero age main sequence (ZAMS) binary parameters and tested against the final parameter distributions desired by the user until they match.
-The output of \cosmic\ contains enough information that a user can analyze both individual systems of interest as well as the overall population, from ZAMS until compact binary formation.
-
-%In this study, we used \cosmic\ 's cosmic-pop package to create fixed populations of DWDs, keeping all parameters except DWD type and metallicity Z constant.
-The output fully describes the binary parameter distributions that result from our SFH and binary evolution model, coined BSEDict, which is specified in an inifile containing sections on filters, convergence, sampling, and BSE flags, which will be described below:
-
-%\katie{Based on the restructuring I did, I think you should expand this paragraph to describe (1) since we are interested in a metallicity-dependent binary fraction, we simulate metallicity bins separately, (2) since the masses and orbital periods of each DWD type at formation span a wide range, we simulate them separately.}
-%For a given metallicity, a fixed population of one million binaries was created for each DWD subtype (discussed in Section \ref{sec:ini}). 
-%\katie{Is this true? I think we probably simulated more. We should talk about this today!}
-
-%moved paragraph up here from below since it takes care of some of the things I suggested in the paragraph above!
-
 The masses and orbital periods at the formation of the second-formed WD span a wide range depending on the WD binary component types, thus we consider four DWD combinations: two helium WDs (He + He), a carbon-oxygen WD orbiting a helium WDs (CO + He), two carbon-oxygen WDs (CO + CO), and an oxygen-neon orbiting helium, carbon-oxygen, or oxygen-neon WD (ONe + X).
@@
 External parameters like Galactic position and orientation are assigned in a post-processing scheme which uses metallicity-dependent positions and ages from the Ananke framework of galaxy \textbf{m12i} from the Latte Suite of the FIRE simulations (see Section~\ref{sec:FIRE} for details).
-
-%this is covered in my text above.
-%We iteratively simulate binary populations until the distributions of the DWD masses and orbital period at the formation of the second-formed WD converge to a stable shape.
-Eccentricity does not need to be analyzed, as most DWDs are circularized by tidal forces (Marsh et al.
-2004, Gokhale et al.
-2007, Kremer et al.
-2015/17), which also simplifies many calculations later on for GW evolution and GW signals.
 
@@
 \label{sec:FIRE}
-%\katie{I think this paragraph gives a bit too much detail on FIRE.
-I think the only detail we need is (1) we use Galaxy m12i from the Latte Suite of the FIRE simulations and (2) Latte reproduces parts of the Milky Way (see Lamberts+2019 paper for this info)}
 To create Milky Way-like galaxies which integrate the metallicity-dependent binary fraction, we use the metallicity-dependent ages and positions of galaxy \textbf{m12i} from the ``Latte" suite of the FIRE simulations \citep{Hopkins2015, Wetzel2016, Hopkins2018} to create synthetic, Milky Way-like DWD populations.
-%\sout{Specifically, the new “FIRE-2” code version was used, which updates the FIRE physics modules in the code GIZMO (Hopkins et al.
-2018;  Gabyurov and Nitadori 2011; Hopkins 2015).
-This update leverages recent developments of mesh-free Godunov hydrodynamics methods, and incorporates updates to “cooling and recombination rates, gravitational force softening, and numerical feedback coupling” (Hopkins et al.
-2018).
-The Latte suite is then run using Gizmo gravity, plus hydrodynamics code in meshless finite-mass (MFM) mode (Hopkins 2015) and the FIRE-2 physics model (Hopkins e al 2018)” $<$- citation}.
 
@@
 The metallicity-dependent binary fraction is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid.
-%Plotted in black is the binary fraction as a function of metallicity.
-%The metallicity values chosen for our grid are shown as the scatter points.
-The red histogram depicts the total mass in stars formed for each metallicity bin within FIRE galaxy \textbf{m12i}, the Milky Way-like simulation used in this study which will be described further in Section \ref{sec:simulations}, as a function of metallicity.
 The binary fraction, $f_{\rm{b}}$, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly.
@@
 The total amount of ZAMS mass in single and binary stars is then $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}} (1 + R(f_{\rm{b}}))$.
-
-%We use these ratios to then determine the total amount of ZAMS mass sampled in single and binary stars. 
-%This ratio can then be used to scale the total amount of ZAMS mass sampled in binary stars required to produce our simulated population from \cosmic\ to $M_{\rm{ZAMS,sim}}$, the total amount of ZAMS mass in single stars and binary systems required to produce the simulated population for a given binary fraction $f_{\rm{b}}$.
-
-%For a given metallicity in our grid and a given DWD type of one compact object binary type, the general procedure to create the Milky Way like galaxy is as follows.
-We specify metallicity bin $i$ with metallicities Z $\in$ [Z$_{i-1}$, Z$_i$].
-The number of DWDs per unit mass N$_{\text{DWD,}i}$ for the \katie{\sout{cosmic-pop} simulated \cosmic} population pop$_i$ with Z = Z$_i$ is found through:
-
-%\begin{align*}
-%    R_{m}(f_i) &= \frac{M_{\text{singles,}\odot}(f_i)}{M_\text{binaries,} \odot(f_i)} \numberthis \\
-%    \\
-%    M_{\text{tot,}i} &=  M_{\text{binaries,}i} \cdot (1 + R_m(f_i)) \numberthis \\
-%    \\
-%    N_{\text{DWD,}i} &= \frac{N_{\text{DWD, tot,}i}}{M_{\text{tot,}i}} \numberthis
-%\end{align*}
-
-%R$_m$ is the fraction of mass in single stars to mass in binary stars for binary fraction $f_i$.
-\katie{I wonder if we can rewrite these equations to be a bit less confusing; I think we should use Lamberts+2019 as a guide.} \katie{\sout{This is calculated ahead of time using the \cosmic\ independent sampler in the InitialBinaryTable class.} I think that this sentence should say that the scaling incorporates the same assumptions for primary and secondary mass distributions as are used in the simulated data.} One million DWD binaries are initialized at solar metallicity for a given binary fraction, along with the total mass in singles vs.
-binaries.
-M$_{{\rm{binaries, }}i}$ the mass in binaries of pop$_i$ (the total mass of the population, as they were run with f$_{\rm{b}}$ = 1.0).
-M$_{{\rm{binaries, }}i}$ is scaled using R$_m$ to find the total astronomical mass M$_{\rm{tot, Z}_i}$ of the population.
-N$_{{\rm{DWD, tot,}}i}$ is the total number of DWDs in pop$_i$.
 
@@
 For most DWD types there is more than one DWD binary system assigned to each \textbf{m12i} star particle.
-
-%Already covered above
-%In order to ensure that each DWD position is unique, we assign positions inside the star particle following the Ananke framework which provides offsets from the star particle center.
-
-%\katie{I think this should go later}This gives us a final distance $d$ to the sun for all the systems, and from this and other information, we can calculate parameters relevant to the LISA observatory like Amplitude Spectral Density (ASD), signal-to-noise ratio (SNR), chirps, chirp masses, etc, as discussed in the next section.
-
-%This will be a floating point number.
-The integer component gives one number of DWDs to sample with replacement from the cosmic-pop output to apply to each FIRE star particle.
-The decimal component will be treated as a probability $p$ of a binary existing for that particle.
-We assign an additional DWD to each star particle with probability $p$.
-The DWDs now have metallicities, ages, and galactic positions.
-
-%\katie{I think the presentation of the next couple of paragraphs is a bit out of order.
-What about presenting it in the order: (1) we evolve the DWDs from their formation time up to the present day using the Peters equations (2) we discard any systems which overflow their roche lobes.}
 
@@
 
-%Following the creation of an initial population, certain systems are discarded.
-We discard any systems with formation times longer than their assigned age from their respective star particle since these systems won’t have formed a DWD by present day and would thus not be observable by LISA.
-The time from DWD formation until the time when the system merges, t$_{\text{merge}}$, is defined as
-%\begin{equation}
-%    t_\text{merge} = \frac{a_i^4}{4 \beta}
-%\end{equation}
-%where $a_i$ is the DWD separation at formation, and 
-%\begin{equation}
-%    \beta = \frac{64G^3}{5c^5} M_1M_2(M_1+M_2)
-%\end{equation}
-%is constant throughout DWD evolution \citep{Peters1964}.
-The delay time of the %system, $t_\text{delay}$, is defined as the sum of the DWD formation time and t$_{\text{merge}}$.
-Systems are also discarded if the delay time is less than the FIRE age, since they would have merged before present day.
-Finally, we
-%We find the time corresponding to when} the system will reach separation $a = a_\text{RLOF,2}$ by inverting Eq.(12), and \textcolor{purple}{\sout{discarding systems with $t_\text{phys} + t_\text{RLOF} \leq t_\text{FIRE}$} discard systems that would overflow their Roche Lobe before present day according to their FIRE age}.
-
-%For the non-discarded systems, we assume evolution occurs solely through the emission of gravitational radiation. Furthermore,
-
-%We discard any sampled DWDs for which the sum of their ZAMS birth time given by the star particle and DWD formation time is larger than the age of the star particle. 
-%since DWDs orbit mainly in the second harmonic, with negligible signal stemming from the others.
-Systems in the LISA band are defined to have $f_\text{GW} \in [10^{-4}, 1.0]$ Hz, although they may not be observable from Earth with LISA’s current sensitivity limits.
-
-%\katie{I think we might want to leave photometric observations to a future paper}
-%In order to investigate possible follow-up with photometric observations, we also calculate the bolometric magnitude of the DWD.
-To calculate the luminosity of the DWD, we utilize the modified Mestel cooling described in Hurley(2003):
-%\begin{equation}
-%    L_{\text{WD,}i} = %\frac{bM_iZ^{0.4}}{(A_i(t_\text{evol,i}+0.1))^x}
-%\end{equation}
-%where $M_i$ is the WD mass in solar masses and $Z$ is the metallicity of our specified metallicity bin.
-$A_i$ is the baryon number for the WD subtype.
-4 corresponds to helium, 15 to carbon-oxygen and 17 to oxygen-neon.
-$t_\text{evol, i}$ is evolution time for WD component $i$ in Myr (i.e.
-$t_{\text{evol, 2}}$ = $t_{\text{evol}}$, but $t_{\text{evol,1}} = t_{\text{FIRE}}-t_{\text{phys,1}}$ where $t_{\text{phys,1}}$ must be retrieved from \cosmic\ at primary formation.).
-The values of $b$ and $x$ are dependent on this age:
-%\begin{equation}
-%x = \begin{cases} 
-%     1.18 & t_\text{evol, i} < 9000.0\\
-%      6.48 & t_\text{evol, i} \geq 9000.0
-%   \end{cases}
-%\end{equation}
-%\begin{equation}
-%b = \begin{cases} 
-%      300 & t_\text{evol, i} < 9000.0\\
-%      300(9000A)^{5/3} & t_\text{evol, i} \geq 9000.0 
-%   \end{cases}
-%\end{equation}
-%We can then find the bolometric magnitude of the system using https://www.astro.princeton.edu/~gk/A403/
-%constants.pdf and https://www.astro.keele.ac.uk/jkt/pubs/
-%JKTeq-fluxsum.pdf:
-%\begin{equation}
-%    m_{\text{bol, tot}} = -2.5 \cdot \log_{10}(10^{-0.4m_1}+10^{-0.4m_2}),
-%\end{equation}
-%where the bolometric magnitude of each component $m_{i}$ is %given by:
-%\begin{equation}
-%    m_{i} = 4.8 - 2.5 \cdot %\log_{10}\left(\frac{L_i}{L_\odot}\right)
-%\end{equation}
-
 \section{LISA detectability}
@@
 circular orbits is 
-%only defined for the $n=2$ harmonic and is:
 \begin{equation}
@@
 
-%$g(n,e)$ is the relative power of gravitational radiation at the nth harmonic taken from Peters and Mathews(1963). For $n=2$ this reduces to:
-%\begin{equation}
-%    h_2^2 = \frac{2^{22/3}}{5}\frac{(G\mathcal{M}_c)^{10/3}}{c^8D_L^2}(\pi f_\text{orb})^{4/3}
-%\end{equation}
 The amplitude spectral density for a stationary system is finally defined as $ASD = h_{2} \sqrt{T_\text{obs}}$, such that the SNR for stationary source is simply, $\rho \sim ASD/S_n$.
@@
 Here we describe the general formation scenarios and population properties of Galactic close DWDs which may be observable by LISA.
-%We thus simulated \cosmic \ DWD populations separately for each DWD type and metallicity value in order to identify variations in how each type is impacted differently by changes in metallicity.
-A key effect is that in general, lower metallicity stars have shorter MS lifetimes and smaller initial radii than high metallicity counterparts (https://arxiv.org/pdf/2001.10404.pdf).
-This is discussed in greater depth later in this section.
 
-%The resulting DWD populations from \cosmic\ gives insight in to the impact that metallicity has on these systems upon their initial formation.
-The trends we see within these distributions can be better interpreted through the characteristics and evolutionary channels of each DWD type which are outlined below.
-
-%He + He: (REF = https://iopscience.iop.org/article/
-%10.1086/303686/fulltext/34537.text.html)
 He WDs are unable to form through single star evolution within the lifetime of the Milky Way.
@@
 Because of this, He WDs are able to form with low component masses on order $\sim$ 0.1M$_\odot$, with the majority of He WDs in our simulations having masses between 0.2-0.5 M$_\odot$.
-%, which would be impossible through SSE within a Hubble time (REF). 
 He + He DWDs form through evolution of close binary systems, during which their envelopes are both stripped through RLO and CE phase interactions before Helium ignition occurs.
@@
 
-%CO + He: 
-%(REF = https://www.researchgate.net/publ ication/231115182\_Helium\_and\_Carbon-Oxygen\_White\_ Dwarfs\_in\_Close\_Binaries)
 A CO WD forms when a star is able to begin the helium burning process before its envelope is stripped.
@@
 Because of these short formation separations, many CO + He DWDs merge before the present day.
-%(Lamberts) of $O$(hour), and may merge due to GW radiation by present day. Specifically, DWDs with sub-hour periods tend to merge in less than 10$^8$ years (REF). 
 Due to their asymmetric mass distributions, they have lower chirp masses, but their shorter periods make them important candidates for LISA detection.
-%Possible formation channels of these short period CO + He DWDs are explored in (REF).
-The fate of the binary is dependent on the orbital period that results from the final CE phase before DWD formation.
 
-%CO + CO:
-%A CO WD forms when a star is able to begin helium burning before its envelope is stripped (Lamberts,  https://arxiv.org/pdf/2011.10439.pdf). 
 To prevent the two stars' envelopes from being stripped before helium ignition, CO + CO DWDs typically form from progenitors in wider orbits, and the two components may have little to no interaction during their evolution from ZAMS to DWD.
@@
 
-%ONe + X: (REF = https://arxiv.org/pdf/2011.10439.pdf)
 ONe WDs are rare and typically form from massive progenitor stars which evolve through the asymptotic giant branch (AGB) phase, thus resulting in a higher mass WD.
@@
 
-%KB cut 28 sept 21
-%This drop across metallicity is due to an increase in the number of merging systems before the formation of the DWD.
-%The increased propensity for merging during binary interactions stems from variations in the star's intrinsic properties caused by the effect of metallicity on stellar evolution.
-A higher abundance of metals results in a cooler, dimmer star with a lower central temperature and that is less compact, leading to larger stellar radii and longer main sequence lifetimes.
-These changes further alter the timescales for Roche-lobe overflow interactions.
-
-%Consider two stars of high and low metallicity but equal mass.
-The star with higher metal abundance will have a larger radius, and a higher fraction of mass in the convective envelope (which creates longer turnover timescales) of the star/less in the core.
-This in theory impacts the CE phase - there would be more envelope to eject, leading to a longer energy transfer times, longer CE phases, and thus more mergers.
-We will now detail the unique processes for each DWD type which leads to the drop in DWD formation efficiency.
-For many of the subtypes, the mechanisms behind and degree to which the DWD formation efficiency is impacted can be identified within subsets of their initial orbital period.
-%\katie{I think we might want to shorten this previous paragraph a bit since we go into detail later on.}
-
 For He + He DWDs, the sudden drop in formation efficiency near $\log(Z/Z_{\odot})=-1.0$, is generally caused by the timescale for which the initially more massive star in the DWD progenitor overflows it's Roche lobe.
 At lower metallicities, donors tend to fill their Roche lobes while they are still on the main sequence and the mass transfer remains stable.
-This is because, in our \cosmic\ models %\snotes{[in just our \cosmic\ models or astrophysically?
-or are we stating this is just for \cosmic\ to be safe?]},
-% KB: yeah exactly -- to be safe
-lower metallicity stars evolve faster than high-metallicity stars and have larger radii near the end of the MS.
+This is because, in our \cosmic\ models lower metallicity stars evolve faster than high-metallicity stars and have larger radii near the end of the MS.
 At higher metallicities, mass transfer is initiated when the donor has left the main sequence and the binary enters a common envelope evolution.
@@
 The sharp drop of the CO + CO average at the highest-metallicity bin is due to binning effects of the figure: it only contains 115 systems, of which the majority stem from a single low-separation system which was sampled 94 times times during the simulation.}
-    %The initial radii of high-metallicity ZAMS stars is larger than their lower-metallicity counterparts but inflate less during their evolution, creating three cases: 1) stars with wider initial separations that do not shrink enough to evolve into the LISA band before present day or fail to interact at all since their radii never increase enough to interact, 2) systems which remain stable throughout their evolution and end up in the LISA band, which requires higher interaction separations to account for the larger radii and deeper convective envelopes which need to be ejected (i.e the separation must be large enough to allow for longer CE phases), and 3) systems which merge before present day either through interactions delayed until late in their evolution from radii which do not evolve much, causing unstable mass transfer, or through very close initial separations which merged during a CE phase before present.
-Only case (2) would result in successful systems shown here.}
     \label{fig:CEsep}
@@
 
-All data and software required to reproduce our results will be shared through GitHub and Zenodo on acceptance of this manuscript.
+All data and software required to reproduce our results are available through GitHub and Zenodo which are accessible through the icon links associated with our abstract and each figure.
 

### 2021-11-26 src/ms.tex
fixing some minor typos and shortening abstract

@@
 Not only will tens of thousands of DWDs be individually resolved, but DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be the dominant contributor to a stochastic foreground caused by confusion from overlapping GW signals, limiting the detectability of individual sources of all kinds.
-The number of DWDs in the Milky Way strongly depends on the Galactic stellar binary fraction.
-Population modelling of Galactic DWDs typically assumes a standard binary fraction of $50\%$.
+Population modeling of Galactic DWDs typically assumes a standard binary fraction of $50\%$.
 However, recent observations have shown that the binary fraction of close ($P_{\text{orb}}$ $\leq 10^4$ days) solar-type stars exhibits a strong anti-correlation with metallicity.
@@
 We use \legwork\footnote{https://legwork.readthedocs.io} \citep{Wagg2021} to determine the detectability of our simulated DWD populations for sources with GW frequencies $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$.
-\legwork\ calculates the position-, orientation-, and angle-averaged signal to noise ratio (SNR) for inspiraling GW sources closely following the derivations of \citet{Flanagan1998} and using the LISA noise power spectrum density (PSD) of \citet{Robson2019}.
+\legwork\ calculates the position-, orientation-, and angle-averaged signal to noise ratio (SNR) for inspiraling GW sources closely following the derivations of \citet{Flanagan1998} and using the LISA noise power spectral density (PSD) of \citet{Robson2019}.
 
@@
 
-The reduced number of DWDs in model FZ relative to model F50 is also apparent in the GW power spectral density (PSD) LISA will observe.
+The reduced number of DWDs in model FZ relative to model F50 is also apparent in the GW PSD LISA will observe.
 We show the GW PSD of each model, as well as the confusion estimate, in Figure~\ref{fig:PSD}.

### 2021-11-26 src/ms.tex
Update ms.tex

--- 2021-11-26 src/ms.tex
@@
 When viewed strictly as a source of noise, the unresolved Galactic DWD foreground is the dominant noise source for LISA in the sub-mHz part of LISA's frequency range.
-This extra noise above the detector noise floor affects the detection of all other LISA sources including extreme mass ratio inspirals \citep[e.g.,][]{Berti2006, Barack2007, Babak2017, Moore2017}, merging black holes with masses between $10^4$--$10^7\,M_{\odot}$ \citep[e.g.,][]{Klein2016, Bellovary2019}, and cosmological GW backgrounds \citep[e.g.,][]{Bartolo2016, Caprini2016, Caldwell2019}.
+This extra noise above the detector noise floor affects the detection of all other LISA sources including extreme mass ratio inspirals \citep[e.g.,][]{Berti2006, Barack2007, Babak2017, Moore2017}, merging black holes with masses between $10^4$--$10^7$ M$_{\odot}$ \citep[e.g.,][]{Klein2016, Bellovary2019}, and cosmological GW backgrounds \citep[e.g.,][]{Bartolo2016, Caprini2016, Caldwell2019}.
 For sources which have signals buried by the Galactic DWD population, the foreground must be carefully analyzed and subtracted \citep[][]{Adams2014,Cornish2020,Littenberg2020,Boileau2021}.
@@
 
-The masses and orbital periods at the formation of the second-formed WD span a wide range depending on the WD binary component types, thus we consider four DWD combinations: two helium WDs (He + He), a carbon-oxygen WD orbiting a helium WDs (CO + He), two carbon-oxygen WDs (CO + CO), and an oxygen-neon orbiting helium, carbon-oxygen, or oxygen-neon WD (ONe + X).
+The masses and orbital periods at the formation of the second-formed WD span a wide range depending on the WD binary component types, thus we consider four DWD combinations: two helium WDs (He + He), a carbon-oxygen WD orbiting a helium WD (CO + He), two carbon-oxygen WDs (CO + CO), and an oxygen-neon orbiting a helium, carbon-oxygen, or oxygen-neon WD (ONe + X).
 For each DWD type we simulate a grid of $15$ metallicities spaced uniformly in $\log_{10}(Z)$ between $Z=10^{-4}$ to $0.03$, to account for the limits of the \citet{Hurley2000} stellar evolution tracks employed in \cosmic.
@@
 The output of \cosmic\ contains information limited to intrinsic binary properties like mass and orbital period.
-External parameters like Galactic position and orientation are assigned in a post-processing scheme which uses metallicity-dependent positions and ages from the Ananke framework of galaxy \textbf{m12i} from the Latte Suite of the FIRE simulations (see Section~\ref{sec:FIRE} for details).
+External parameters like Galactic position and orientation are assigned in a post-processing scheme which uses metallicity-dependent positions and ages from the Ananke framework of galaxy \textbf{m12i} from the Latte Suite of the FIRE-2 simulations (see Section~\ref{sec:FIRE} for details).
 
@@
 
-\subsection{A metallicity-dependent SFH: Convolving with the FIRE models}
+\subsection{A metallicity-dependent SFH: Convolving with the FIRE-2 models}
 \label{sec:FIRE}
-To create Milky Way-like galaxies which integrate the metallicity-dependent binary fraction, we use the metallicity-dependent ages and positions of galaxy \textbf{m12i} from the ``Latte" suite of the FIRE simulations \citep{Hopkins2015, Wetzel2016, Hopkins2018} to create synthetic, Milky Way-like DWD populations.
+To create Milky Way-like galaxies which integrate the metallicity-dependent binary fraction, we use the metallicity-dependent ages and positions of galaxy \textbf{m12i} from the ``Latte" suite of the FIRE-2 simulations \citep{Hopkins2015, Wetzel2016, Hopkins2018} to create synthetic, Milky Way-like DWD populations.
 
@@
     \caption{The metallicity-dependent binary fraction for close solar-type binaries with P $< 10^4$ days (black) plotted against the logarithm of Z/Z$_\odot$, with scatter points denoting the location of the metallicity grid used in our \cosmic\ simulations.
-The secondary axis shows the amount of mass in stars formed within each metallicity bin from galaxy \textbf{m12i} of the ``Latte" suite in FIRE-2 simulations as a red histogram.
+The secondary axis shows the amount of mass in stars formed within each metallicity bin from galaxy \textbf{m12i} of the ``Latte" suite in the FIRE-2 simulations as a red histogram.
 The amount of stellar mass formed with super-solar metallicities dominates the distribution.
@@
 \end{equation}
-\noindent where $R_\text{NS} = 1.4\cdot 10^{-5}$ R$_\odot$ is the radius of a neutron star, $M_{\text{Ch}}=1.44$ M$_\odot$ is the Chandrasekhar limit for the mass of a stable WD, and $M$ is the mass of the DWD in solar masses.
+\noindent where $R_\text{NS} = 1.4\cdot 10^{-5}$ R$_\odot$ is the radius of a neutron star, $M_{\text{Ch}}=1.44$ M$_\odot$ is the Chandrasekhar limit for the mass of a stable WD, and $M$ is the mass of the WD in solar masses.
 
@@
 \end{equation}
-with the observation time $T_{\text{obs}}$. Here, $h_2$ is strain amplitude of the source for the second orbital frequency harmonic
+with the observation time $T_{\text{obs}}$. Here, $h_2$ is strain amplitude of the source for the second orbital frequency harmonic,
 \begin{equation}
-   h_2^2 = \frac{2^{22/3}}{5}\frac{(G\mathcal{M}_c)^{10/3}}{c^8D_L^2}(\pi f_\text{orb})^{4/3}.
+   h_2^2 = \frac{2^{22/3}}{5}\frac{(G\mathcal{M}_c)^{10/3}}{c^8D_L^2}(\pi f_\text{orb})^{4/3}
 \end{equation}
@@
 \begin{equation}
-    h_2^2 = \frac{\dot{f}_{2}}{f_{\rm{orb}}^2} h_c^2.
+    h_2^2 = \frac{\dot{f}_{2}}{f_{\rm{orb}}^2} h_c^2
 \end{equation}
@@
 
-If a lower-metallicity system forms a CO + He DWD and a higher-metallicity system does not, this is because the initially more massive binary component initiates a CE while on the giant branch (GB) instead of the AGB.
+If a lower-metallicity system forms a CO + He DWD and a higher-metallicity system does not, this is because the initially more massive binary component initiates a CE while on the giant branch (GB) instead of the asymptotic giant branch (AGB).
 This instead leaves behind a He WD with a stellar companion, which is the dominating scenario that restricts formation efficiency.

### 2021-11-26 src/ms.tex
abstract shorten for journal

--- 2021-11-26 src/ms.tex
@@
 Short-period double white dwarf (DWD) binaries will be the most prolific source of gravitational waves (GWs) for the Laser Interferometer Space Antenna (LISA).
-Not only will tens of thousands of DWDs be individually resolved, but DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be the dominant contributor to a stochastic foreground caused by confusion from overlapping GW signals, limiting the detectability of individual sources of all kinds.
-Population modeling of Galactic DWDs typically assumes a standard binary fraction of $50\%$.
-However, recent observations have shown that the binary fraction of close ($P_{\text{orb}}$ $\leq 10^4$ days) solar-type stars exhibits a strong anti-correlation with metallicity.
+DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be the dominant contributor to a stochastic foreground caused by overlapping GW signals, limiting the detectability of individual sources of all kinds.
+Population modeling of Galactic DWDs typically assumes a binary fraction of $50\%$.
+However, recent observations have shown that the binary fraction of close, solar-type stars exhibits a strong anti-correlation with metallicity.
 In this study we perform the first simulation of the Galactic DWD population observable by LISA which incorporates an empirically-derived metallicity-dependent binary fraction.
@@
 However, the size of the total Galactic DWD population orbiting in the LISA frequency band is reduced by more than half when accounting for a metallicity-dependent binary fraction.
-This effect serves to lower the confusion foreground, effectively increasing the sensitivity for detecting all types of low-frequency LISA sources.
+This effect lowers the confusion foreground, effectively increasing the sensitivity for detecting all types of low-frequency LISA sources.
 We repeat our analysis for three different assumptions for Roche-lobe overflow interactions and find the population reduction to be robust when a metallicity-dependent binary fraction is assumed.
-
 \end{abstract}

### 2022-04-30 src/ms.tex
Update ms.tex
added line numbers
add linenums for journal
Update ms.tex

@@
 % Define document class
-\documentclass[twocolumn]{aastex631}
+\documentclass[twocolumn, linenumbers]{aastex631}
 
@@
 \newcommand{\legwork}{\texttt{LEGWORK}}
+\usepackage{xcolor}
 
@@
 The shape and strength of the Galactic DWD foreground can also be used as a tool to study the structure of the Milky Way \citep{Benacquista2006, Breivik2020b} as well as the separation distribution of close DWDs \citep{Korol2021}.
+
+%I did some switching around of words
+\textbf{The transition between individually resolved DWDs and the confusion limited, or unresolved, DWD foreground is expected to occur near $\sim1\,\rm{mHz}$ frequencies \citep[e.g.
+][]{Ruiter2010}.
+In the confusion limited regime, more than one binary radiates GWs in each LISA frequency bin, thus creating a superposition of signals which are unable to be disentangled.
+There are multiple parameters which shape the Galactic DWD foreground.
+Assuming the evolution of each DWD system is driven solely by GW emission, the frequency derivative scales proportionally to $f_{\rm{GW}}^{11/3}$, causing a pileup of DWDs at lower frequencies \citep{Breivik2019fg}.
+The spatial density of DWDs in the Galaxy  which defines the distance to each binary also impacts the foreground amplitude, since strain scales inversely with distance.
+Star formation history assumptions combine these two effects by assigning ages and positions to each DWD in the population which determine the present day orbital (and thus GW) frequencies as well as distances to each source.}
+
+%\textbf{There also exists a ``transition" GW frequency at which the GW spectrum transitions from confusion limited to being able to detect individual sources \citep{Ruiter2010}.
+In the confusion-limited regime, greater than one binary exists per LISA frequency bin, creating a superposition of signals which are unable to be disentangled.
+There are multiple parameters which serve to shape the Galactic DWD foreground.
+Assuming the evolution of each DWD system is driven solely by GW emission, the frequency derivative scales proportionally to $f_{\rm{GW}}^{11/3}$, causing a pileup of DWDs at lower frequencies \citep{Breivik2019fg}.
+The distance dependence of the spatial density of DWDs in the Galaxy also impacts the foreground amplitude, since strain scales inversely with distance.
+Star formation history assumptions impact the foreground height, as the duration of GW orbital evolution of each system will impact contributions to strain.}
 
@@
 We further discard any DWDs for which the lower mass WD overflows it's Roche lobe before present day, because the outcomes of these interactions are highly uncertain and their treatment is outside the scope of this work \citep[e.g., ][]{Shen2015, Kremer2017}.
-The separation at which the lower mass WD overflows its Roche Lobe is defined as
+\textbf{We also note that stably accreting WD binaries are unlikely to contribute appreciably to the Galactic DWD foreground due to their small mass ratios at frequencies below $1\,\rm{mHz}$ \citep{Breivik2018}.} The separation at which the lower mass WD overflows its Roche Lobe is defined as
 
@@
 
-\section{Binary evolution assumption variations}
+\section{Binary evolution \textbfparameter variations}
 \label{sec:model_compare}
@@
 	\includegraphics[width=0.45\textwidth]{figures/model_comp.pdf}
-    \caption{The top panel shows the Galactic DWD confusion fit vs GW frequency for different binary evolution assumption variations (colors) with model F50 shown in dashed lines and model FZ shown in solid lines.
+    \caption{The top panel shows the Galactic DWD confusion fit vs GW frequency for different binary evolution \textbf{parameter variations} (colors) with model F50 shown in dashed lines and model FZ shown in solid lines.
 The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for model FZ to model F50 vs to number of DWDs orbiting in the LISA band for model F50 only.
@@
 
-In order to test the robustness of the reduction of the height of the Galactic DWD GW foreground when assuming a metallicity-dependent binary fraction, we repeat our analysis using three different binary evolution assumption variations.
+In order to test the robustness of the reduction of the height of the Galactic DWD GW foreground when assuming a metallicity-dependent binary fraction, we repeat our analysis using three different binary evolution \textbf{parameter variations}.
 For each variation, we consider models FZ and F50 as done in the fiducial case described above.
@@
 
-We extended our study to include three binary evolution assumption variations to investigate whether the DWD population reduction was robust to changes in assumptions for mass transfer stability and common envelope ejection efficiencies.
-While our binary evolution assumption variations change the size of the LISA-observable populations dramatically, the reduction in the size of the close Galactic DWD population and the height of the confusion foreground for models which assume a metallicity-dependent binary fraction is robust.
+We extended our study to include three binary evolution \textbf{parameter variations} to investigate whether the DWD population reduction was robust to changes in assumptions for mass transfer stability and common envelope ejection efficiencies.
+While our binary evolution \textbf{parameter variations} change the size of the LISA-observable populations dramatically, the reduction in the size of the close Galactic DWD population and the height of the confusion foreground for models which assume a metallicity-dependent binary fraction is robust.
 An important consequence of a lower Galactic DWD confusion foreground is that relative to the total DWD population, more DWDs can be individually resolved because of the reduction in competing GW signals.

### 2022-05-23 src/figures/LISA_SNR.py
upgrade to syw v0.3

@@ -1,116 +1,0 @@
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-import astropy.units as u
-from legwork.visualisation import plot_sensitivity_curve
-from legwork import psd
-
-
-def plot_LISAcurves(model):
-    def func(x, a, b, c, d, e):
-        return a + b * x + c * x ** 2 + d * x ** 3 + e * x ** 4
-
-    def cosmic_confusion(f, L, t_obs=4 * u.yr, approximate_R=True, confusion_noise=None):
-        lisa_psd_no_conf = psd.power_spectral_density(
-            f, confusion_noise=None, t_obs=4 * u.yr
-        )
-        conf = 10 ** func(
-            x=np.log10(f.value), 
-            a=popt[0], 
-            b=popt[1], 
-            c=popt[2], 
-            d=popt[3], 
-            e=popt[4]
-        ) * t_obs.to(u.s)
-
-        psd_plus_conf = conf + lisa_psd_no_conf
-        return psd_plus_conf.to(u.Hz ** (-1))
-
-    resolved = pd.read_hdf("../data/results.hdf", key="resolved_DWDs_{}_{}".format(model, "fiducial"))
-    popt = pd.read_hdf("../data/results.hdf", key="conf_fit_DWDs_{}_{}".format(model, "fiducial"))
-    popt = popt.values.flatten()
-    
-    resolved_HeHe = resolved.loc[(resolved.kstar_1 == 10) & (resolved.kstar_2 == 10)]
-    resolved_COHe = resolved.loc[((resolved.kstar_1 == 11) & (resolved.kstar_2 == 10)) |
-                                 ((resolved.kstar_2 == 11) & (resolved.kstar_1 == 10))]
-    resolved_COCO = resolved.loc[(resolved.kstar_1 == 11) & (resolved.kstar_2 == 11)]
-    resolved_ONeX = resolved.loc[((resolved.kstar_1 == 12) & (resolved.kstar_2.isin([10,11,12]))) |
-                                 ((resolved.kstar_2 == 12) & (resolved.kstar_1.isin([10,11,12])))]
-    
-    t_obs = 4 * u.yr
-    
-    
-    psd_conf = psd.power_spectral_density(
-        f=np.linspace(1e-4, 1e-1, 1000000) * u.Hz, 
[…]

### 2022-05-23 src/figures/lisa_nums.py

@@ -1,148 +1,0 @@
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-from matplotlib.ticker import AutoMinorLocator
-
-model = "fiducial"
-numsFZ = pd.read_hdf("../data/results.hdf", key="numLISA_30bins_{}_{}".format("FZ", model))
-numsF50 = pd.read_hdf("../data/results.hdf", key="numLISA_30bins_{}_{}".format("F50", model))
-
-FIREmin = 0.00015
-FIREmax = 13.346
-Z_sun = 0.02
-num = 30
-
-met_bins = np.logspace(np.log10(FIREmin), np.log10(FIREmax), num) * Z_sun
-
-
-Henums = numsFZ.He.values
-COHenums = numsFZ.COHe.values
-COnums = numsFZ.CO.values
-ONenums = numsFZ.ONe.values
-
-Henums05 = numsF50.He.values
-COHenums05 = numsF50.COHe.values
-COnums05 = numsF50.CO.values
-ONenums05 = numsF50.ONe.values
-
-fig, ax = plt.subplots(1, 4, figsize=(16, 4))
-
-fig, ax = plt.subplots(1, 4, figsize=(16, 4.5))
-
-ax[0].plot(
-    np.log10(met_bins[1:]/Z_sun), 
-    Henums/1e5, 
-    drawstyle='steps-mid', 
-    color='xkcd:tomato red', 
-    lw=3, 
-    label='FZ',
-    rasterized=True
-)
-                      
-ax[0].plot(
-    np.log10(met_bins[1:]/Z_sun), 
-    Henums05/1e5,       
-    drawstyle='steps-mid', 
-    color='xkcd:tomato red', 
-    ls='--', 
-    lw=3, 
-    label='F50', 
-    rasterized=True
-)
-
-ax[0].text(0.05, 0.85, 'He + He', fontsize=18, transform=ax[0].transAxes)
-
-ax[1].plot(
-    np.log10(met_bins[1:]/Z_sun), 
-    COHenums/1e5, 
-    drawstyle='steps-mid',     
-    color='xkcd:blurple', 
-    lw=3, 
-    label='FZ', 
-    rasterized=True
-)
-ax[1].plot(
-    np.log10(met_bins[1:]/Z_sun), 
-    COHenums05/1e5, 
-    drawstyle='steps-mid', 
[…]

### 2022-05-23 src/figures/postproc.py

@@ -1,1119 +1,0 @@
-
-import utils as dutil
-
-import numpy as np
-import pandas as pd
-import astropy.units as u
-from astropy.time import Time
-import astropy.constants as const
-import astropy.coordinates as coords
-from astropy.coordinates import SkyCoord
-from scipy.interpolate import interp1d, UnivariateSpline
-from scipy.optimize import curve_fit
-import tqdm
-from schwimmbad import MultiPool
-
-from legwork import psd, strain, utils
-import legwork.source as source
-
-pd.options.mode.chained_assignment = None
-
-
-# Specific to Thiele et al. (2021), here are the used metallicity
-# array, the associated binary fractions for each Z value, and the ratios 
-# of mass in singles to mass in binaries of the Lband with each specific 
-# binary fraction as found using COSMIC's independent samplers
-# (See Binary_Fraction_Modeling.ipynb for Tutorials). All values were
-# rounded to 4 significant digits except metallicity which used 8:
-
-met_arr = np.logspace(np.log10(1e-4), np.log10(0.03), 15)
-met_arr = np.round(met_arr, 8)
-met_arr = np.append(0.0, met_arr)
-
-binfracs = np.array([0.4847, 0.4732, 0.4618, 0.4503, 0.4388, 
-                     0.4274, 0.4159, 0.4044, 0.3776, 0.3426, 
-                     0.3076, 0.2726, 0.2376, 0.2027, 0.1677])
-
-ratios = np.array([0.68, 0.71, 0.74, 0.78, 0.82, 
-                   0.86, 0.9, 0.94, 1.05, 1.22, 
-                   1.44, 1.7 , 2.05, 2.51, 3.17])
-
-ratio_05 = 0.64
-
-# LEGWORK uses astropy units so we do also for consistency
-G = const.G.value  # gravitational constant
-c = const.c.value  # speed of light in m s^-1
-M_sol = const.M_sun.value  # sun's mass in kg
-R_sol = const.R_sun.value  # sun's radius in metres
-sec_Myr = u.Myr.to('s')  # seconds in a million years
-m_kpc = u.kpc.to('m')  # metres in a kiloparsec
-L_sol = const.L_sun.value  # solar luminosity in Watts
-Z_sun = 0.02  # solar metallicity
-sun = coords.get_sun(Time("2021-04-23T00:00:00", scale='utc'))  # sun coordinates
[…]

### 2022-05-23 src/scripts/CEsep.py

@@ -3,6 +3,7 @@ import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 import matplotlib as mpl
+import paths
 
 model = "fiducial"
 FIREmin = 0.00015
@@ -13,10 +14,10 @@ met_bins = np.logspace(np.log10(FIREmin), np.log10(FIREmax), num)
 met_mids = (met_bins[1:] + met_bins[:-1]) / 2
 whichsep = "CEsep"
 
-Heinter = pd.read_hdf("../data/results.hdf", key='intersep_{}_{}_{}_{}'.format(10, 10, "FZ", "fiducial"))
-COHeinter = pd.read_hdf("../data/results.hdf", key='intersep_{}_{}_{}_{}'.format(11, 10, "FZ", "fiducial"))
-COinter = pd.read_hdf("../data/results.hdf", key='intersep_{}_{}_{}_{}'.format(11, 11, "FZ", "fiducial"))
-ONeinter = pd.read_hdf("../data/results.hdf", key='intersep_{}_{}_{}_{}'.format(12, 10, "FZ", "fiducial"))
+Heinter = pd.read_hdf(paths.data / "results.hdf", key='intersep_{}_{}_{}_{}'.format(10, 10, "FZ", "fiducial"))
+COHeinter = pd.read_hdf(paths.data / "results.hdf", key='intersep_{}_{}_{}_{}'.format(11, 10, "FZ", "fiducial"))
+COinter = pd.read_hdf(paths.data / "results.hdf", key='intersep_{}_{}_{}_{}'.format(11, 11, "FZ", "fiducial"))
+ONeinter = pd.read_hdf(paths.data / "results.hdf", key='intersep_{}_{}_{}_{}'.format(12, 10, "FZ", "fiducial"))
 
 Heavgs = []
 Hecovs = []
@@ -152,4 +153,4 @@ ax[3].set_ylim(top=3.05)
 plt.tight_layout()
 plt.subplots_adjust(wspace=0.25)
 
-plt.savefig("CEsep.pdf", dpi=100)
+plt.savefig(paths.figures / "CEsep.pdf", dpi=100)

### 2022-05-23 src/scripts/LISA_SNR.py

@@ -1,0 +1,229 @@
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import astropy.units as u
+from legwork.visualisation import plot_sensitivity_curve
+from legwork import psd
+import paths
+
+
+def plot_LISAcurves(model):
+    def func(x, a, b, c, d, e):
+        return a + b * x + c * x ** 2 + d * x ** 3 + e * x ** 4
+
+    def cosmic_confusion(
+        f, L, t_obs=4 * u.yr, approximate_R=True, confusion_noise=None
+    ):
+        lisa_psd_no_conf = psd.power_spectral_density(
+            f, confusion_noise=None, t_obs=4 * u.yr
+        )
+        conf = 10 ** func(
+            x=np.log10(f.value), a=popt[0], b=popt[1], c=popt[2], d=popt[3], e=popt[4]
+        ) * t_obs.to(u.s)
+
+        psd_plus_conf = conf + lisa_psd_no_conf
+        return psd_plus_conf.to(u.Hz ** (-1))
+
+    resolved = pd.read_hdf(
+        paths.data / "results.hdf", key="resolved_DWDs_{}_{}".format(model, "fiducial")
+    )
+    popt = pd.read_hdf(
+        paths.data / "results.hdf", key="conf_fit_DWDs_{}_{}".format(model, "fiducial")
+    )
+    popt = popt.values.flatten()
+
+    resolved_HeHe = resolved.loc[(resolved.kstar_1 == 10) & (resolved.kstar_2 == 10)]
+    resolved_COHe = resolved.loc[
+        ((resolved.kstar_1 == 11) & (resolved.kstar_2 == 10))
+        | ((resolved.kstar_2 == 11) & (resolved.kstar_1 == 10))
+    ]
+    resolved_COCO = resolved.loc[(resolved.kstar_1 == 11) & (resolved.kstar_2 == 11)]
+    resolved_ONeX = resolved.loc[
+        ((resolved.kstar_1 == 12) & (resolved.kstar_2.isin([10, 11, 12])))
+        | ((resolved.kstar_2 == 12) & (resolved.kstar_1.isin([10, 11, 12])))
+    ]
+
+    t_obs = 4 * u.yr
+
+    psd_conf = psd.power_spectral_density(
+        f=np.linspace(1e-4, 1e-1, 1000000) * u.Hz,
+        instrument="custom",
+        custom_psd=cosmic_confusion,
[…]

### 2022-05-23 src/scripts/Mc_vs_dist.py

@@ -5,16 +5,17 @@ import pandas as pd
 import matplotlib.pyplot as plt
 import astropy.units as u
 import seaborn as sns
+import paths
 
 model = "fiducial"
 
 resolved_dat_FZ = pd.read_hdf(
-   "../data/results.hdf", key="resolved_DWDs_{}_{}".format("FZ", model)
+    paths.data / "results.hdf", key="resolved_DWDs_{}_{}".format("FZ", model)
 )
 resolved_dat_FZ = resolved_dat_FZ.loc[resolved_dat_FZ.resolved_chirp == 1.0]
 
 resolved_dat_F50 = pd.read_hdf(
-    "../data/results.hdf", key="resolved_DWDs_{}_{}".format("F50", model)
+    paths.data / "results.hdf", key="resolved_DWDs_{}_{}".format("F50", model)
 )
 resolved_dat_F50 = resolved_dat_F50.loc[resolved_dat_F50.resolved_chirp == 1.0]
 
@@ -22,15 +23,15 @@ Heplot = resolved_dat_FZ.loc[
     (resolved_dat_FZ.kstar_1 == 10) & (resolved_dat_FZ.kstar_2 == 10)
 ]
 COHeplot = resolved_dat_FZ.loc[
-    ((resolved_dat_FZ.kstar_1 == 11) & (resolved_dat_FZ.kstar_2 == 10)) |
-    ((resolved_dat_FZ.kstar_2 == 11) & (resolved_dat_FZ.kstar_1 == 10))
+    ((resolved_dat_FZ.kstar_1 == 11) & (resolved_dat_FZ.kstar_2 == 10))
+    | ((resolved_dat_FZ.kstar_2 == 11) & (resolved_dat_FZ.kstar_1 == 10))
 ]
 COplot = resolved_dat_FZ.loc[
     (resolved_dat_FZ.kstar_1 == 11) & (resolved_dat_FZ.kstar_2 == 11)
 ]
 ONeplot = resolved_dat_FZ.loc[
-    ((resolved_dat_FZ.kstar_1 == 12) & (resolved_dat_FZ.kstar_2.isin([10, 11, 12]))) |
-    ((resolved_dat_FZ.kstar_2 == 12) & (resolved_dat_FZ.kstar_1.isin([10, 11, 12])))
[…]

### 2022-05-23 src/scripts/PSD.py

@@ -2,25 +2,31 @@ import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 import astropy.units as u
+import paths
 
 
 def func(x, a, b, c, d, e):
     return a + b * x + c * x ** 2 + d * x ** 3 + e * x ** 4
+
 
 model = "fiducial"
 colors = ["#add0ed", "#2b5d87", "#4288c2", "#17334a"]
 Tobs = 4 * u.yr
 
 power_dat_F50 = pd.read_hdf(
-    "../data/results.hdf", key="total_power_DWDs_{}_{}".format("F50", model)
+    paths.data / "results.hdf", key="total_power_DWDs_{}_{}".format("F50", model)
 )
-popt_F50 = pd.read_hdf("../data/results.hdf",  key="conf_fit_DWDs_{}_{}".format("F50", model))
+popt_F50 = pd.read_hdf(
+    paths.data / "results.hdf", key="conf_fit_DWDs_{}_{}".format("F50", model)
+)
 popt_F50 = popt_F50.values.flatten()
 
 power_dat_FZ = pd.read_hdf(
-    "../data/results.hdf", key="total_power_DWDs_{}_{}".format("FZ", model)
+    paths.data / "results.hdf", key="total_power_DWDs_{}_{}".format("FZ", model)
 )
-popt_FZ = pd.read_hdf("../data/results.hdf", key="conf_fit_DWDs_{}_{}".format("FZ", model))
+popt_FZ = pd.read_hdf(
+    paths.data / "results.hdf", key="conf_fit_DWDs_{}_{}".format("FZ", model)
+)
 popt_FZ = popt_FZ.values.flatten()
 
 conf_fit_FZ = (
@@ -94,5 +100,5 @@ plt.xlim(1e-4, 3e-2)
 plt.ylim(1e-38, 5e-34)
 plt.legend(prop={"size": 12}, ncol=2, frameon=False, loc=(0, 1))
 plt.tight_layout()
-plt.savefig("PSD.pdf", dpi=100)
-ax1.set_ylabel(r'PSD [Hz$^{-1}$]', size=15)
+plt.savefig(paths.figures / "PSD.pdf", dpi=100)
+ax1.set_ylabel(r"PSD [Hz$^{-1}$]", size=15)

### 2022-05-23 src/scripts/form_eff.py

@@ -3,8 +3,9 @@ import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
 import utils
+import paths
 
-'''
+"""
 Creates plot files with formation efficiency of DWDs. In order to
 run this, there must be already-existing LISA band files created with
 make_galaxy() at pathtoLband.
@@ -19,18 +20,22 @@ RETURNS
 ----------------------
 No direct function outputs, but saves formation efficiency data for all
 DWD types and metallicity bins to files contained in pathtosave.
-'''
+"""
 met_arr = np.logspace(np.log10(1e-4), np.log10(0.03), 15)
 met_arr = np.round(met_arr, 8)
 met_arr = np.append(0.0, met_arr)
 Z_sun = 0.02
-kstar1_list = ['10', '11', '11', '12']
-kstar2_list = ['10', '10', '11', '10_12']
-labels = ['10_10', '11_10', '11_11', '12']
-pathtodat = "../data/"
+kstar1_list = ["10", "11", "11", "12"]
+kstar2_list = ["10", "10", "11", "10_12"]
+labels = ["10_10", "11_10", "11_11", "12"]
+pathtodat = paths.data / ""
 
-DWDeff = pd.read_hdf('../data/results.hdf', key='DWDeff_{}_{}'.format("FZ", "fiducial"))
-DWDeff05 = pd.read_hdf('../data/results.hdf', key='DWDeff_{}_{}'.format("F50", "fiducial"))
+DWDeff = pd.read_hdf(
+    paths.data / "results.hdf", key="DWDeff_{}_{}".format("FZ", "fiducial")
+)
+DWDeff05 = pd.read_hdf(
+    paths.data / "results.hdf", key="DWDeff_{}_{}".format("F50", "fiducial")
+)
 
 effHe = DWDeff.He.values
 effCOHe = DWDeff.COHe.values
@@ -46,99 +51,102 @@ fig, ax = plt.subplots(1, 4, figsize=(16, 4.5))
 ax[0].plot(
     np.log10(met_arr[1:] / Z_sun),
     effHe * 1e3,
-    color='xkcd:tomato red',
-    drawstyle='steps-mid',
+    color="xkcd:tomato red",
+    drawstyle="steps-mid",
     lw=3,
-    label='FZ',
-    rasterized=True
+    label="FZ",
[…]

### 2022-05-23 src/scripts/lisa_nums.py

@@ -1,0 +1,153 @@
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from matplotlib.ticker import AutoMinorLocator
+import paths
+
+model = "fiducial"
+numsFZ = pd.read_hdf(
+    paths.data / "results.hdf", key="numLISA_30bins_{}_{}".format("FZ", model)
+)
+numsF50 = pd.read_hdf(
+    paths.data / "results.hdf", key="numLISA_30bins_{}_{}".format("F50", model)
+)
+
+FIREmin = 0.00015
+FIREmax = 13.346
+Z_sun = 0.02
+num = 30
+
+met_bins = np.logspace(np.log10(FIREmin), np.log10(FIREmax), num) * Z_sun
+
+
+Henums = numsFZ.He.values
+COHenums = numsFZ.COHe.values
+COnums = numsFZ.CO.values
+ONenums = numsFZ.ONe.values
+
+Henums05 = numsF50.He.values
+COHenums05 = numsF50.COHe.values
+COnums05 = numsF50.CO.values
+ONenums05 = numsF50.ONe.values
+
+fig, ax = plt.subplots(1, 4, figsize=(16, 4))
+
+fig, ax = plt.subplots(1, 4, figsize=(16, 4.5))
+
+ax[0].plot(
+    np.log10(met_bins[1:] / Z_sun),
+    Henums / 1e5,
+    drawstyle="steps-mid",
+    color="xkcd:tomato red",
+    lw=3,
+    label="FZ",
+    rasterized=True,
+)
+
+ax[0].plot(
+    np.log10(met_bins[1:] / Z_sun),
+    Henums05 / 1e5,
+    drawstyle="steps-mid",
+    color="xkcd:tomato red",
+    ls="--",
+    lw=3,
+    label="F50",
+    rasterized=True,
+)
+
+ax[0].text(0.05, 0.85, "He + He", fontsize=18, transform=ax[0].transAxes)
+
+ax[1].plot(
+    np.log10(met_bins[1:] / Z_sun),
+    COHenums / 1e5,
+    drawstyle="steps-mid",
+    color="xkcd:blurple",
+    lw=3,
+    label="FZ",
+    rasterized=True,
+)
+ax[1].plot(
+    np.log10(met_bins[1:] / Z_sun),
+    COHenums05 / 1e5,
+    drawstyle="steps-mid",
[…]

### 2022-05-23 src/scripts/model_comp.py

@@ -3,6 +3,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 import seaborn as sns
 import astropy.units as u
+import paths
 
 models = ["log_uniform", "qcflag_4", "alpha_0.25", "alpha_5"]
 model_names = ["fiducial", "q3", "alpha25", "alpha5"]
@@ -32,12 +33,19 @@ popt_F50_list = []
 popt_FZ_list = []
 
 for model in model_names:
-    numsFZ = pd.read_hdf("../data/results.hdf", key="numLISA_30bins_{}_{}".format("FZ", model))
-    numsF50 = pd.read_hdf("../data/results.hdf", key="numLISA_30bins_{}_{}".format("F50", model))
+    numsFZ = pd.read_hdf(
+        paths.data / "results.hdf", key="numLISA_30bins_{}_{}".format("FZ", model)
+    )
+    numsF50 = pd.read_hdf(
+        paths.data / "results.hdf", key="numLISA_30bins_{}_{}".format("F50", model)
+    )
 
-
-    popt_F50 = pd.read_hdf("../data/results.hdf", key="conf_fit_DWDs_{}_{}".format("F50", model))
-    popt_FZ = pd.read_hdf("../data/results.hdf", key="conf_fit_DWDs_{}_{}".format("FZ", model))
+    popt_F50 = pd.read_hdf(
+        paths.data / "results.hdf", key="conf_fit_DWDs_{}_{}".format("F50", model)
+    )
+    popt_FZ = pd.read_hdf(
+        paths.data / "results.hdf", key="conf_fit_DWDs_{}_{}".format("FZ", model)
+    )
 
     n_lisa_F50 = np.sum(numsF50.values.flatten())
     n_lisa_FZ = np.sum(numsFZ.values.flatten())
@@ -125,4 +133,4 @@ ax_dict["B"].set_xlabel(r"N$_{\rm{LISA, F50}}$", size=18)
 ax_dict["A"].tick_params(labelsize=14)
 ax_dict["B"].tick_params(labelsize=14)
 plt.tight_layout()
-plt.savefig("model_comp.pdf", dpi=100)
+plt.savefig(paths.figures / "model_comp.pdf", dpi=100)

### 2022-05-23 src/scripts/pipeline.py

@@ -1,11 +1,11 @@
-#=========================================================================
+# =========================================================================
 # This script creates LISA DWD galaxies across 15 metallicity bins,
 # incorporating the metallicity-dependent binary fraction as
 # discussed in Thiele et al. (2021).
 #
 # Authors: Sarah Thiele & Katelyn Breivik
 # Last updated: Oct 14th, 2021
-#=========================================================================
+# =========================================================================
 
 import numpy as np
 from astropy import constants as const
@@ -14,12 +14,13 @@ import astropy.coordinates as coords
 from astropy.time import Time
 import argparse
 import postproc as pp
+import paths
 
 
-DWD_list = ['He_He', 'CO_He', 'CO_CO', 'ONe_X']
-dat_path = "../data/"
-FIRE_path = "../data/"
-models = ['fiducial', 'alpha25', 'alpha5', 'q3']
+DWD_list = ["He_He", "CO_He", "CO_CO", "ONe_X"]
+dat_path = str(paths.data) + "/"
+FIRE_path = str(paths.data) + "/"
+models = ["fiducial", "alpha25", "alpha5", "q3"]
 interfile = False
 nproc = 4
 
@@ -27,30 +28,24 @@ for model in models:
     pp.save_full_galaxy(
         DWD_list, dat_path, FIRE_path, dat_path, interfile, model, nproc
     )
-    print('Gx done!')
+    print("Gx done!")
 
-    if model == 'fiducial':
-        pp.get_formeff(
-            pathtodat=dat_path, pathtosave=dat_path
-        )
-    print('formation efficiency done')
+    if model == "fiducial":
+        pp.get_formeff(pathtodat=dat_path, pathtosave=dat_path)
+    print("formation efficiency done")
 
     pp.get_interactionsep_and_numLISA(
         pathtodat=dat_path, pathtosave=dat_path, model=model, var=True
     )
-    print('interaction sep FZ done')
- 
+    print("interaction sep FZ done")
+
     pp.get_interactionsep_and_numLISA(
         pathtodat=dat_path, pathtosave=dat_path, model=model, var=False
     )
-    print('interaction sep F50 done')
-    
-    pp.get_resolvedDWDs(
-        dat_path, dat_path, var=True, model=model, window=1000
-    )
-    print('resolved FZ done')
-    pp.get_resolvedDWDs(
-        dat_path, dat_path, var=False, model=model, window=1000
-    )
[…]

### 2022-05-23 src/scripts/postproc.py

@@ -1,0 +1,1393 @@
+import utils as dutil
+
+import numpy as np
+import pandas as pd
+import astropy.units as u
+from astropy.time import Time
+import astropy.constants as const
+import astropy.coordinates as coords
+from astropy.coordinates import SkyCoord
+from scipy.interpolate import interp1d, UnivariateSpline
+from scipy.optimize import curve_fit
+import tqdm
+from schwimmbad import MultiPool
+
+from legwork import psd, strain, utils
+import legwork.source as source
+import paths
+
+pd.options.mode.chained_assignment = None
+
+
+# Specific to Thiele et al. (2021), here are the used metallicity
+# array, the associated binary fractions for each Z value, and the ratios
+# of mass in singles to mass in binaries of the Lband with each specific
+# binary fraction as found using COSMIC's independent samplers
+# (See Binary_Fraction_Modeling.ipynb for Tutorials). All values were
+# rounded to 4 significant digits except metallicity which used 8:
+
+met_arr = np.logspace(np.log10(1e-4), np.log10(0.03), 15)
+met_arr = np.round(met_arr, 8)
+met_arr = np.append(0.0, met_arr)
+
+binfracs = np.array(
+    [
+        0.4847,
+        0.4732,
+        0.4618,
+        0.4503,
+        0.4388,
+        0.4274,
+        0.4159,
+        0.4044,
+        0.3776,
+        0.3426,
+        0.3076,
+        0.2726,
+        0.2376,
+        0.2027,
+        0.1677,
+    ]
+)
+
+ratios = np.array(
+    [
+        0.68,
+        0.71,
+        0.74,
+        0.78,
+        0.82,
+        0.86,
+        0.9,
+        0.94,
+        1.05,
+        1.22,
+        1.44,
+        1.7,
+        2.05,
+        2.51,
+        3.17,
+    ]
+)
+
+ratio_05 = 0.64
+
+# LEGWORK uses astropy units so we do also for consistency
+G = const.G.value  # gravitational constant
+c = const.c.value  # speed of light in m s^-1
+M_sol = const.M_sun.value  # sun's mass in kg
+R_sol = const.R_sun.value  # sun's radius in metres
+sec_Myr = u.Myr.to("s")  # seconds in a million years
+m_kpc = u.kpc.to("m")  # metres in a kiloparsec
+L_sol = const.L_sun.value  # solar luminosity in Watts
+Z_sun = 0.02  # solar metallicity
[…]

### 2022-05-23 src/scripts/sfh_vs_fb.py

@@ -6,6 +6,7 @@ import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib import rcParams
+import paths
 
 
 def get_FeH_from_Z(Z, Z_sun=0.02):
@@ -58,7 +59,7 @@ met_arr = np.append(0.0, met_arr)
 
 Z_sun = 0.02
 
-FIRE = pd.read_hdf("../data/FIRE.h5")
+FIRE = pd.read_hdf(paths.data / "FIRE.h5")
 fig, ax = plt.subplots()
 plt.grid(lw=0.25, which="both")
 bins = np.append(met_arr[1:-1] / Z_sun, FIRE.met.max())
@@ -99,7 +100,7 @@ ax.legend(
     borderaxespad=0,
     frameon=False,
 )
-   
+
 ax.set_zorder(ax2.get_zorder() + 1)
 ax.patch.set_visible(False)
 ax.set_xlabel("Log$_{10}$(Z/Z$_\odot$)", size=18)
@@ -109,5 +110,5 @@ ax2.set_yticks([1e4, 1e5, 1e6, 1e7])
 ax2.set_yticklabels(["7e7", "7e8", "7e9", "7e10"])
 ax2.tick_params(labelsize=15)
 ax.tick_params(labelsize=15)
-ax2.set_ylim(1e4-0.1e4, 1e7+0.1e7)
-plt.savefig("sfh_vs_fb.pdf",  bbox_inches='tight', dpi=100)
+ax2.set_ylim(1e4 - 0.1e4, 1e7 + 0.1e7)
+plt.savefig(paths.figures / "sfh_vs_fb.pdf", bbox_inches="tight", dpi=100)

### 2022-07-12 src/tex/ms.tex
upgrade to syw v0.3

--- 2022-04-30 src/ms.tex
@@
 \usepackage{xcolor}
+\usepackage{showyourwork}
 
@@
 
-%I did some switching around of words
 \textbf{The transition between individually resolved DWDs and the confusion limited, or unresolved, DWD foreground is expected to occur near $\sim1\,\rm{mHz}$ frequencies \citep[e.g.
@@
 Star formation history assumptions combine these two effects by assigning ages and positions to each DWD in the population which determine the present day orbital (and thus GW) frequencies as well as distances to each source.}
-
-%\textbf{There also exists a ``transition" GW frequency at which the GW spectrum transitions from confusion limited to being able to detect individual sources \citep{Ruiter2010}.
-In the confusion-limited regime, greater than one binary exists per LISA frequency bin, creating a superposition of signals which are unable to be disentangled.
-There are multiple parameters which serve to shape the Galactic DWD foreground.
-Assuming the evolution of each DWD system is driven solely by GW emission, the frequency derivative scales proportionally to $f_{\rm{GW}}^{11/3}$, causing a pileup of DWDs at lower frequencies \citep{Breivik2019fg}.
-The distance dependence of the spatial density of DWDs in the Galaxy also impacts the foreground amplitude, since strain scales inversely with distance.
-Star formation history assumptions impact the foreground height, as the duration of GW orbital evolution of each system will impact contributions to strain.}
 
@@
     \label{fig:sfh_vs_fb}
+    \script{sfh_vs_fb.py}
 \end{figure}
@@
     \label{fig:form_eff}
+    \script{form_eff.py}
 \end{figure*}
@@
     \label{fig:CEsep}
+    \script{CEsep.py}
 \end{figure*}
@@
     \label{fig:lisa_nums}
+    \script{lisa_nums.py}
 \end{figure*}
@@
     \label{fig:PSD}
+    \script{PSD.py}
 \end{figure}
@@
 \begin{figure*}
-	\includegraphics[width=\textwidth]{figures/LISA_SNR_FZ.pdf}
-	\includegraphics[width=\textwidth]{figures/LISA_SNR_F50.pdf}
+	\includegraphics[width=\textwidth]{figures/LISA_SNR_fiducial_Z.pdf}
+	\includegraphics[width=\textwidth]{figures/LISA_SNR_fiducial.pdf}
     \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for each DWD type where the top row shows the population from model FZ and the bottom row shows the population from model F50.
@@
     \label{fig:LISA_SNR}
+    \script{LISA_SNR.py}
 \end{figure*}
@@
     \label{fig:Mc_vs_dist}
+    \script{Mc_vs_dist.py}
 \end{figure*}
@@
 
-\section{Binary evolution \textbfparameter variations}
+\section{Binary evolution \textbf{parameter variations}}
 \label{sec:model_compare}
@@
     \label{fig:model_comp}
+    \script{model_comp.py}
 \end{figure}
@@
 The authors are grateful for helpful discussions with Carles Badenes, Christine Mazzola Daher, and the Gravitational Waves and Astronomical Data groups at the CCA.
+The authors are also grateful to the referee for providing a thoughtful review which strengthened the presentation of the manuscript.
 S.T.\ was supported by an Undergraduate Student Research Award (USRA) at CITA from the Natural Sciences and Engineering Research Council of Canada (NSERC), Reference \# 498223.

### 2022-07-26 src/scripts/model_comp.py
update postprocessing to impose 1000Rsun upper limit and update to dev version of syw for cacheing

@@ -10,7 +10,7 @@ paths = Paths()
 
 
 models = ["fiducial", "q3", "alpha25", "alpha5", "fiducial_Z", "q3_Z", "alpha25_Z", "alpha5_Z"]
-model_names = ["fiducial", "q3", "alpha25", "alpha5", "fiducial", "q3", "alpha25", "alpha5", "fiducial_Z", "q3_Z", "alpha25_Z", "alpha5_Z"]
+model_names = ["fiducial", "q3", "alpha25", "alpha5", "fiducial_Z", "q3_Z", "alpha25_Z", "alpha5_Z"]
 colors = sns.color_palette("mako", n_colors=len(models))
 
 Tobs = 4 * u.yr
@@ -36,23 +36,21 @@ n_lisa_F50_list = []
 popt_F50_list = []
 popt_FZ_list = []
 
-for model in model_names:
-    if 'Z' in model:
-        numsFZ = pd.read_hdf(paths.data / "results.hdf", key="numLISA_30bins_{}_{}".format("FZ", model))
-        popt_FZ = pd.read_hdf(paths.data / "results.hdf", key="conf_fit_DWDs_{}_{}".format("FZ", model))
-        n_lisa_FZ = np.sum(numsFZ.values.flatten())
-        lisa_ratio.append(n_lisa_FZ / n_lisa_F50)
-        popt_FZ = popt_FZ.values.flatten()
-        popt_FZ_list.append(popt_FZ)
+for model in model_names[:4]:
+    numsF50 = pd.read_hdf(paths.data / "results.hdf", key="numLISA_30bins_{}_{}".format("F50", model))
+    popt_F50 = pd.read_hdf(paths.data / "results.hdf", key="conf_fit_DWDs_{}_{}".format("F50", model))
+    n_lisa_F50 = np.sum(numsF50.values.flatten())
+    n_lisa_F50_list.append(n_lisa_F50)
+    popt_F50 = popt_F50.values.flatten()
+    popt_F50_list.append(popt_F50)
         
     
-    else:
-        numsF50 = pd.read_hdf(paths.data / "results.hdf", key="numLISA_30bins_{}_{}".format("F50", model))
-        popt_F50 = pd.read_hdf(paths.data / "results.hdf", key="conf_fit_DWDs_{}_{}".format("F50", model))
-        n_lisa_F50 = np.sum(numsF50.values.flatten())
[…]

### 2022-07-26 src/scripts/pipeline.py

@@ -24,8 +24,8 @@ paths = Paths()
 
 
 DWD_list = ['He_He', 'CO_He', 'CO_CO', 'ONe_X']
-dat_path = paths.data / "cosmic_dat/"
-LISA_path = paths.data / "postproc/"
+dat_path = paths.data / "cosmic_dat"
+LISA_path = paths.data / "postproc"
 FIRE_path = paths.data
 results_path = paths.data
 models = ['fiducial', 'fiducial_Z', 'alpha25', 'alpha25_Z', 'alpha5', 'alpha5_Z', 'q3', 'q3_Z']
@@ -33,42 +33,42 @@ interfile = False
 nproc_gx = 28
 nproc_results = len(models)
     
-#for model in models:
-    #pp.save_full_galaxy(
-    #    DWD_list, dat_path, FIRE_path, LISA_path, interfile, model, nproc_gx
-    #)
-    #print('Gx done!')
+for model in models:
+    pp.save_full_galaxy(
+        DWD_list, dat_path, FIRE_path, LISA_path, interfile, model, nproc_gx
+    )
+    print('Gx done!')
     
-#def get_results(dat):
-#    
-#    dat_path, LISA_path, results_path, var, model, window = dat
-#    pp.get_formeff(
-#        pathtodat=dat_path, pathtosave=results_path, model=model, var=var,
-#    )
-#    print('formation efficiency done for model: {}'.format(model))
-#    
-#    pp.get_interactionsep_and_numLISA(
-#        pathtocosmic=dat_path, pathtoLISA=LISA_path, pathtoresults=results_path, model=model, var=var,     
-#    )
-#    print('interaction sep done')
-#    
-#    pp.get_resolvedDWDs(
-#        pathtoLISA=LISA_path, pathtosave=results_path, var=var, model=model, window=window
-#    )
-#    print('resolved sources done')
-#    
-#    return []
-#
-#dat = []
-#for model in models:
-#    if 'Z' in model:
-#        dat.append([dat_path, LISA_path, results_path, True, model, 1000])    
-#    else:
-#        dat.append([dat_path, LISA_path, results_path, False, model, 1000])
-#    
-#with MultiPool(processes=nproc_results) as pool:
-#    _ = list(pool.map(get_results, dat))
-#             
+def get_results(dat):
+    
+    dat_path, LISA_path, results_path, var, model, window = dat
+    pp.get_formeff(
[…]

### 2022-07-26 src/scripts/postproc.py

@@ -508,27 +508,31 @@ def make_galaxy(dat, verbose=False):
     Lkey = 'Lband_{}_{}'.format(var_label, model)
     Rkey = 'rand_seed_{}_{}'.format(var_label, model)
     Lsavefile = 'Lband_{}_{}_{}_{}.hdf'.format(label, var_label, model, i)
-    
+    FIREfile = 'FIRE.h5' 
     try:
-        breakpoint()
         pd.read_hdf(pathtosave / Lsavefile, key=Lkey)
         
         return [], [], []
     except:
-        FIRE = pd.read_hdf(fire_path+'FIRE.h5').sort_values('met')
+        FIRE = pd.read_hdf(fire_path / FIREfile).sort_values('met')
     
         rand_seed = np.random.randint(0, 100, 1)
         np.random.seed(rand_seed)
         
         rand_seed = pd.DataFrame(rand_seed)
-        rand_seed.to_hdf(pathtosave+Lsavefile, key=Rkey)
+        rand_seed.to_hdf(pathtosave / Lsavefile, key=Rkey)
     
         # Choose metallicity bin
         met_start = met_arr[i] / Z_sun
         met_end = met_arr[i+1] / Z_sun
         
         # Load DWD data at formation of the second DWD component
-        conv = pd.read_hdf(pathtodat+filename, key='conv')
+        conv = pd.read_hdf(pathtodat / filename, key='conv')
+        
+        # Limit to 1000 Rsun
+        conv = conv.loc[conv.sep < 1000]
+        
+        # get bin_num indices if needed
         if 'bin_num' not in conv.columns:
             conv.index = conv.index.rename('index')
             conv['bin_num'] = conv.index.values
@@ -645,15 +649,20 @@ def make_galaxy(dat, verbose=False):
                 jlast = int(jlast)
                 if jlast > N_sample_int:
                     jlast = N_sample_int
-            #LISA_band_list = []
-            #for dat in dat_filter:
-            #    LISA_band_list.append(filter_population(dat))
-            with MultiPool(processes=nproc) as pool:
-                LISA_band_list = list(pool.map(filter_population, dat_filter))
+            LISA_band_list = []
+            if i < 13:
+                for dat in dat_filter:
+                    LISA_band_list.append(filter_population(dat))
+                for LISA_band in LISA_band_list:
[…]

### 2022-07-26 src/scripts/lisa_nums.py
adding scripts from sarah!

@@ -2,12 +2,6 @@ import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 from matplotlib.ticker import AutoMinorLocator
-import paths
-
-model_Z = "fiducial_Z"
-model = "fiducial"
-numsFZ = pd.read_hdf(paths.data / "results.hdf", key="numLISA_30bins_{}_{}".format("FZ", model_Z))
-numsF50 = pd.read_hdf(paths.data / "results.hdf", key="numLISA_30bins_{}_{}".format("F50", model))
 
 FIREmin = 0.00015
 FIREmax = 13.346
@@ -15,136 +9,144 @@ Z_sun = 0.02
 num = 30
 
 met_bins = np.logspace(np.log10(FIREmin), np.log10(FIREmax), num) * Z_sun
+    
+models = ["fiducial", "q3", "alpha25", "alpha5"]
+model_labels = ["fiducial", "$q3$", "$\\alpha 25$", "$\\alpha 5$"]
 
+for m, model in enumerate(models):
+    model_Z = model + "_Z"
+    numsFZ = pd.read_hdf("../data/results.hdf", key="numLISA_30bins_{}_{}".format("FZ", model_Z))
+    numsF50 = pd.read_hdf("../data/results.hdf", key="numLISA_30bins_{}_{}".format("F50", model))
 
-Henums = numsFZ.He.values
-COHenums = numsFZ.COHe.values
-COnums = numsFZ.CO.values
-ONenums = numsFZ.ONe.values
+    Henums = numsFZ.He.values
+    COHenums = numsFZ.COHe.values
+    COnums = numsFZ.CO.values
+    ONenums = numsFZ.ONe.values
 
-Henums05 = numsF50.He.values
-COHenums05 = numsF50.COHe.values
-COnums05 = numsF50.CO.values
-ONenums05 = numsF50.ONe.values
+    Henums05 = numsF50.He.values
+    COHenums05 = numsF50.COHe.values
+    COnums05 = numsF50.CO.values
+    ONenums05 = numsF50.ONe.values
 
-fig, ax = plt.subplots(1, 4, figsize=(16, 4))
+    fig, ax = plt.subplots(1, 4, figsize=(16, 4.5))
 
-fig, ax = plt.subplots(1, 4, figsize=(16, 4.5))
-
-ax[0].plot(
-    np.log10(met_bins[1:]/Z_sun), 
-    Henums/1e5, 
-    drawstyle='steps-mid', 
[…]

### 2022-07-26 src/scripts/PSD.py
updating PSD figure from Sarah

@@ -2,98 +2,108 @@ import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 import astropy.units as u
-import paths
 
 
 def func(x, a, b, c, d, e):
     return a + b * x + c * x ** 2 + d * x ** 3 + e * x ** 4
 
-model = "fiducial"
-colors = ["#add0ed", "#2b5d87", "#4288c2", "#17334a"]
-Tobs = 4 * u.yr
+models = ["fiducial", "q3", "alpha25", "alpha5"]
+names = ["fiducial", "$q3$", "$\\alpha25$", "$\\alpha5$"]
 
-power_dat_F50 = pd.read_hdf(
-    paths.data / "results.hdf", key="total_power_DWDs_{}_{}".format("F50", model)
-)
-popt_F50 = pd.read_hdf(paths.data / "results.hdf",  key="conf_fit_DWDs_{}_{}".format("F50", model))
-popt_F50 = popt_F50.values.flatten()
+fig, ax = plt.subplots(1, 4, figsize=(25, 5))
+for i, model in enumerate(models):
+    print(model)
+    colors = ["#add0ed", "#2b5d87", "#4288c2", "#17334a"]
+    Tobs = 4 * u.yr
 
-model = "fiducial_Z"
-power_dat_FZ = pd.read_hdf(
-    paths.data / "results.hdf", key="total_power_DWDs_{}_{}".format("FZ", model)
-)
-popt_FZ = pd.read_hdf(paths.data / "results.hdf", key="conf_fit_DWDs_{}_{}".format("FZ", model))
-popt_FZ = popt_FZ.values.flatten()
-
-conf_fit_FZ = (
-    10
-    ** func(
-        x=np.log10(np.linspace(1e-4, 1e-1, 100000)),
-        a=popt_FZ[0],
-        b=popt_FZ[1],
-        c=popt_FZ[2],
-        d=popt_FZ[3],
-        e=popt_FZ[4],
+    power_dat_F50 = pd.read_hdf(
+        "../data/results.hdf", key="total_power_DWDs_{}_{}".format("F50", model)
     )
-    * Tobs.to(u.s).value
-)
+    popt_F50 = pd.read_hdf("../data/results.hdf",  key="conf_fit_DWDs_{}_{}".format("F50", model))
+    popt_F50 = popt_F50.values.flatten()
 
-conf_fit_F50 = (
-    10
[…]

### 2022-07-27 src/scripts/PSD.py
fixed paths

@@ -17,16 +17,16 @@ for i, model in enumerate(models):
     Tobs = 4 * u.yr
 
     power_dat_F50 = pd.read_hdf(
-        "../data/results.hdf", key="total_power_DWDs_{}_{}".format("F50", model)
+        paths.data / "results.hdf", key="total_power_DWDs_{}_{}".format("F50", model)
     )
-    popt_F50 = pd.read_hdf("../data/results.hdf",  key="conf_fit_DWDs_{}_{}".format("F50", model))
+    popt_F50 = pd.read_hdf(paths.data / "results.hdf",  key="conf_fit_DWDs_{}_{}".format("F50", model))
     popt_F50 = popt_F50.values.flatten()
 
     model = model + "_Z"
     power_dat_FZ = pd.read_hdf(
-        "../data/results.hdf", key="total_power_DWDs_{}_{}".format("FZ", model)
+        paths.data / "results.hdf", key="total_power_DWDs_{}_{}".format("FZ", model)
     )
-    popt_FZ = pd.read_hdf("../data/results.hdf", key="conf_fit_DWDs_{}_{}".format("FZ", model))
+    popt_FZ = pd.read_hdf(paths.data / "results.hdf", key="conf_fit_DWDs_{}_{}".format("FZ", model))
     popt_FZ = popt_FZ.values.flatten()
 
     conf_fit_FZ = (

### 2022-07-27 src/scripts/form_eff.py

@@ -2,6 +2,7 @@ from matplotlib.ticker import AutoMinorLocator
 import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
+import paths
 
 '''
 Creates plot files with formation efficiency of DWDs. In order to
@@ -26,7 +27,7 @@ Z_sun = 0.02
 kstar1_list = ['10', '11', '11', '12']
 kstar2_list = ['10', '10', '11', '10_12']
 labels = ['10_10', '11_10', '11_11', '12']
-pathtodat = "../data/"
+pathtodat = paths.data
 
 models = ["fiducial", "q3", "alpha25", "alpha5"]
 model_labels = ["fiducial", "$q3$", "$\\alpha 25$", "$\\alpha 5$"]
@@ -34,8 +35,8 @@ model_labels = ["fiducial", "$q3$", "$\\alpha 25$", "$\\alpha 5$"]
 for m, model_F50 in enumerate(models):
     model_FZ = model_F50 + "_Z"
 
-    DWDeff = pd.read_hdf(pathtodat+'results.hdf', key='DWDeff_{}'.format(model_FZ))
-    DWDeff05 = pd.read_hdf(pathtodat+'results.hdf', key='DWDeff_{}'.format(model_F50))
+    DWDeff = pd.read_hdf(pathtodat / 'results.hdf', key='DWDeff_{}'.format(model_FZ))
+    DWDeff05 = pd.read_hdf(pathtodat / 'results.hdf', key='DWDeff_{}'.format(model_F50))
 
     effHe = DWDeff.He.values
     effCOHe = DWDeff.COHe.values
@@ -157,14 +158,17 @@ for m, model_F50 in enumerate(models):
         ax[0].set_ylim(top=2.6)
         ax[1].set_yticks(np.arange(1.5, 10.0, 1.))
         ax[1].set_ylim(1.4, 5.7)
-        ax[2].set_yticks(np.arange(1., 7., 1.))
-        ax[2].set_yticklabels(['1.0', '2.0', '3.0', '4.0', '5.0', '6.0'])
-        ax[2].set_ylim(top=6.2)
+        #ax[2].set_yticks(np.arange(1., 7., 1.))
+        #ax[2].set_yticklabels(['1.0', '2.0', '3.0', '4.0', '5.0', '6.0'])
+        ax[2].set_ylim(top=3.2)
         ax[3].set_yticks(np.arange(0.1, 0.5, 0.1))
[…]

### 2022-07-27 src/scripts/lisa_nums.py

@@ -2,6 +2,7 @@ import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 from matplotlib.ticker import AutoMinorLocator
+import paths
 
 FIREmin = 0.00015
 FIREmax = 13.346
@@ -15,8 +16,8 @@ model_labels = ["fiducial", "$q3$", "$\\alpha 25$", "$\\alpha 5$"]
 
 for m, model in enumerate(models):
     model_Z = model + "_Z"
-    numsFZ = pd.read_hdf("../data/results.hdf", key="numLISA_30bins_{}_{}".format("FZ", model_Z))
-    numsF50 = pd.read_hdf("../data/results.hdf", key="numLISA_30bins_{}_{}".format("F50", model))
+    numsFZ = pd.read_hdf(paths.data / "results.hdf", key="numLISA_30bins_{}_{}".format("FZ", model_Z))
+    numsF50 = pd.read_hdf(paths.data / "results.hdf", key="numLISA_30bins_{}_{}".format("F50", model))
 
     Henums = numsFZ.He.values
     COHenums = numsFZ.COHe.values

### 2022-07-27 src/scripts/model_comp.py

@@ -3,6 +3,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 import seaborn as sns
 import astropy.units as u
+import paths 
 
 models = ["fiducial", "q3", "alpha25", "alpha5", "fiducial_Z", "q3_Z", "alpha25_Z", "alpha5_Z"]
 model_names = ["fiducial", "q3", "alpha25", "alpha5", "fiducial", "q3", "alpha25", "alpha5", "fiducial_Z", "q3_Z", "alpha25_Z", "alpha5_Z"]
@@ -34,8 +35,8 @@ popt_FZ_list = []
 
 for model in model_names:
     if 'Z' in model:
-        numsFZ = pd.read_hdf("../data/results.hdf", key="numLISA_30bins_{}_{}".format("FZ", model))
-        popt_FZ = pd.read_hdf("../data/results.hdf", key="conf_fit_DWDs_{}_{}".format("FZ", model))
+        numsFZ = pd.read_hdf(paths.data / "results.hdf", key="numLISA_30bins_{}_{}".format("FZ", model))
+        popt_FZ = pd.read_hdf(paths.data / "results.hdf", key="conf_fit_DWDs_{}_{}".format("FZ", model))
         n_lisa_FZ = np.sum(numsFZ.values.flatten())
         print('\n'+ model)
         print('n_lisa_FZ: ', n_lisa_FZ)
@@ -46,8 +47,8 @@ for model in model_names:
         
     
     else:
-        numsF50 = pd.read_hdf("../data/results.hdf", key="numLISA_30bins_{}_{}".format("F50", model))
-        popt_F50 = pd.read_hdf("../data/results.hdf", key="conf_fit_DWDs_{}_{}".format("F50", model))
+        numsF50 = pd.read_hdf(paths.data / "results.hdf", key="numLISA_30bins_{}_{}".format("F50", model))
+        popt_F50 = pd.read_hdf(paths.data / "results.hdf", key="conf_fit_DWDs_{}_{}".format("F50", model))
         #print(popt_F50)
         n_lisa_F50 = np.sum(numsF50.values.flatten())
         print('\n'+ model)

### 2022-07-27 src/scripts/pipeline.py

@@ -66,7 +66,7 @@ for model in models:
     
 with MultiPool(processes=nproc_results) as pool:
     _ = list(pool.map(get_results, dat))
-             
+            
 for model in models:
     if 'Z' in model:
         var_label = 'FZ'

### 2022-07-27 src/scripts/postproc.py

@@ -802,7 +802,6 @@ def get_interactionsep_and_numLISA(pathtocosmic, pathtoLISA, pathtoresults, mode
         data_RLOF['RLOFtime'] = np.repeat(RLOFsep['tphys'], RLOFsep['weights']).values
         
         data_RLOF = data_RLOF[['CEsep', 'CEporb', 'CEmass1', 'CEmass2', 'CEtime', 'RLOFsep', 'RLOFtime', 'met']]    
-        print('CEsep results path: ', pathtoresults)
         data_RLOF.to_hdf(pathtoresults / result_file, key=interkey, append=True) 
         return
     
@@ -861,7 +860,6 @@ def get_interactionsep_and_numLISA(pathtocosmic, pathtoLISA, pathtoresults, mode
         key = 'numLISA_30bins_{}_{}'.format("FZ", model)
     else:
         key = 'numLISA_30bins_{}_{}'.format("F50", model)
-    print('numLISA results path: ', pathtoresults)
 
     numLISA_30bins.to_hdf(pathtoresults / result_file, key=key)
     
@@ -1242,7 +1240,6 @@ def get_resolvedDWDs(pathtoLISA, pathtosave, var, model, window):
     
     dat.to_hdf(pathtosave / result_file, key=Rkey)    
     sources_conf = []
-    print('sources written')
     
     dat = []
     popt_df = pd.DataFrame(popt)
@@ -1303,7 +1300,6 @@ def get_formeff(pathtodat, pathtosave, model, var):
     for kstar1, kstar2, label in tqdm.tqdm(zip(kstar1_list, kstar2_list, labels)):
         files, lab = dutil.getfiles(kstar1=kstar1, kstar2=kstar2, model=model)
         eff.append(formeff(files, pathtodat, model))
-        #print('finished {}'.format(label))
     
     if var:
         var_label='FZ'
@@ -1311,7 +1307,6 @@ def get_formeff(pathtodat, pathtosave, model, var):
         var_label='F50'
     result_file = 'results_{}_{}.hdf'.format(var_label, model)
     DWDeff = pd.DataFrame(np.array(eff).T, columns=['He', 'COHe', 'CO', 'ONe'])
-    print('DWDEff results save', pathtosave)
     DWDeff.to_hdf(pathtosave / result_file, key='DWDeff_{}'.format(model))
     
     return

### 2022-07-27 src/scripts/postproc.py
removed tqdm and printing

@@ -10,7 +10,6 @@ import astropy.coordinates as coord
 from astropy.coordinates import SkyCoord
 from scipy.interpolate import interp1d, UnivariateSpline
 from scipy.optimize import curve_fit
-import tqdm
 from schwimmbad import MultiPool
 
 from legwork import psd, strain, utils
@@ -1297,7 +1296,7 @@ def get_formeff(pathtodat, pathtosave, model, var):
     labels = ['10_10', '11_10', '11_11', '12']
 
     eff = []
-    for kstar1, kstar2, label in tqdm.tqdm(zip(kstar1_list, kstar2_list, labels)):
+    for kstar1, kstar2, label in zip(kstar1_list, kstar2_list, labels):
         files, lab = dutil.getfiles(kstar1=kstar1, kstar2=kstar2, model=model)
         eff.append(formeff(files, pathtodat, model))
     

### 2022-07-27 src/scripts/PSD.py
forgot to import paths

@@ -2,7 +2,7 @@ import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 import astropy.units as u
-
+import paths
 
 def func(x, a, b, c, d, e):
     return a + b * x + c * x ** 2 + d * x ** 3 + e * x ** 4
@@ -12,7 +12,6 @@ names = ["fiducial", "$q3$", "$\\alpha25$", "$\\alpha5$"]
 
 fig, ax = plt.subplots(1, 4, figsize=(25, 5))
 for i, model in enumerate(models):
-    print(model)
     colors = ["#add0ed", "#2b5d87", "#4288c2", "#17334a"]
     Tobs = 4 * u.yr
 

### 2022-07-28 src/tex/ms.tex
fixed figure paths in scripts and text

@@
 \begin{figure*}
-	\includegraphics[width=\textwidth]{figures/form_eff.pdf}
+	\includegraphics[width=\textwidth]{figures/form_eff_fiducial.pdf}
+	\includegraphics[width=\textwidth]{figures/form_eff_alpha25.pdf}
+	\includegraphics[width=\textwidth]{figures/form_eff_alpha5.pdf}
+	\includegraphics[width=\textwidth]{figures/form_eff_q3.pdf}
     \caption{The DWD formation efficiency vs metallicity of DWD populations simulated with \cosmic.
@@
 \begin{figure*}
-	\includegraphics[width=\textwidth]{figures/lisa_nums.pdf}
+	\includegraphics[width=\textwidth]{figures/lisa_nums_fiducial.pdf}
+	\includegraphics[width=\textwidth]{figures/lisa_nums_alpha25.pdf}
+	\includegraphics[width=\textwidth]{figures/lisa_nums_alpha5.pdf}
+	\includegraphics[width=\textwidth]{figures/lisa_nums_q3.pdf}
     \caption{The number of LISA-band systems formed for each DWD type as a function of the base-10 logarithm of metallicity, normalized to solar value.

### 2022-07-28 src/scripts/PSD.py

@@ -105,4 +105,4 @@ for i, model in enumerate(models):
 
 plt.subplots_adjust(wspace=0.25)
 plt.tight_layout()
-plt.savefig("PSD.pdf".format(model), dpi=100)
+plt.savefig(paths.figures / "PSD.pdf".format(model), dpi=100)

### 2022-07-28 src/scripts/form_eff.py

@@ -168,7 +168,4 @@ for m, model_F50 in enumerate(models):
     if "q3" in model_F50:
         ax[2].set_ylim(bottom=5)
         
-    if "alpha25" in model_F50:
-        
-
-    plt.savefig("form_eff_{}.pdf".format(model_F50), dpi=100)
+    plt.savefig(paths.figures / "form_eff_{}.pdf".format(model_F50), dpi=100)

### 2022-07-28 src/scripts/lisa_nums.py

@@ -150,4 +150,4 @@ for m, model in enumerate(models):
         ax[1].set_yticklabels(np.arange(0, 20, 4).astype(float).astype(str))
         ax[3].set_ylim(top=0.81)
 
-    plt.savefig("lisa_nums_{}.pdf".format(model), dpi=100)
+    plt.savefig(paths.figures / "lisa_nums_{}.pdf".format(model), dpi=100)

### 2022-07-28 src/scripts/model_comp.py

@@ -134,4 +134,4 @@ ax_dict["B"].set_xlabel(r"N$_{\rm{LISA, F50}}$", size=18)
 ax_dict["A"].tick_params(labelsize=14)
 ax_dict["B"].tick_params(labelsize=14)
 plt.tight_layout()
-plt.savefig("model_comp.pdf", dpi=100)
+plt.savefig(paths.figures / "model_comp.pdf", dpi=100)

### 2022-07-28 src/scripts/pipeline.py

@@ -75,10 +75,6 @@ for model in models:
     result_file = 'results_{}_{}.hdf'.format(var_label, model)
     file = h5py.File(results_path / result_file, "r")
     for key in file.keys():
-        if ('fiducial' in model) & ('total_power' in key):
-            df = pd.read_hdf(results_path / result_file, key)
-            df.to_hdf(results_path / 'results.hdf', key=key)
-        elif 'total_power' not in key:
-            df = pd.read_hdf(results_path / result_file, key)
-            df.to_hdf(results_path / 'results.hdf', key=key)
+        df = pd.read_hdf(results_path / result_file, key)
+        df.to_hdf(results_path / 'results.hdf', key=key)
         #os.remove(results_path / result_file)

### 2022-08-17 src/tex/ms.tex
updating figs and adding met_dep_porb fig

--- 2022-07-12 src/tex/ms.tex
@@
 \usepackage{showyourwork}
+\newcommand{\snotes}[1]{\textcolor{purple}{#1}}
+\newcommand{\kb}[1]{\textcolor{teal}{#1}}
 
@@
 In this section we describe the setup of our DWD simulations using the binary population synthesis suite \cosmic, and the process to scale these simulations to create Milky Way-like galaxies using the star formation history of galaxy \textbf{\textbf{m12i}} in the Latte suite of the FIRE-2 simulations \citep{Wetzel2016, Hopkins2018} and stellar positions assigned according to the the Ananke framework \citep{Sanderson2020}.
+
+\subsection{Metallicity-dependent binary fraction}\label{subsec:metbinfrac}
+\snotes{The binary fraction in the Galaxy has been empirically shown to depend on metallicity.
+This is manifested through an explicit dependence of the companion frequency on orbital period \citep{Moe2021}.
+When anchored to a log-normal orbital period distribution, the \emph{frequency} of solar-type binary companions is skewed to shorter orbital periods.
+The companion frequency differs from the binary fraction: the companion frequency is the probability of a star having a companion at a given orbital period, and the integration of this probability over all periods results in the binary fraction of the population.
+The metallicity dependence of the companion frequency is observed only } %\kb{\sout{orbital period-dependence of the companion frequency is dependent on metallicity only}}
+\snotes{below P$_{\rm{orb}}=10^6$ days, above which there are not sufficient observational results of binary systems to infer a metallicity dependence.} %\kb{\sout{Below this threshold, we see an increasing skew to shorter periods with decreasing metallicity}}.}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{figures/met_dep_porb.pdf}
+    \caption{}
+    \label{fig:met_dep_porb}
+    \script{met_dep_porb.py}
+\end{figure}
+
+\snotes{Figure \ref{fig:binfrac_porb}, shows the companion frequency f$_{\rm{logP}}$ for solar-type stars as a function of the logarithm of orbital period, mirroring the inner binaries curve of Figure 2 in \citet{Moe2021} and scaling to an overall multiplicity frequency of 0.67 (equivalent to an integrated binary fraction of 50\%) at solar metallicity.} To obtain the normalization of the companion frequency for close binaries ($\log_{10}(P_{\rm{orb}}/\rm{day}$), we fit the results presented in \citet{Moe2019} using linear regression to obtain a piecewise relation between the metallicity, [Fe/H] and \snotes{close} binary fraction $f_{\rm{b}}$ as
+
+\[f_{\rm{b}}= \begin{cases} 
+      - 0.0648 \cdot [\rm{Fe/H}] + 0.3356, & [\rm{Fe/H}]\leq -1.0 \numberthis \\
+      -0.1977 \cdot [\rm{Fe/H}] + 0.2025, & [\rm{Fe/H}]> -1.0  , 
+   \end{cases}
+\]
+
+\noindent where we convert between [Fe/H] and metallicity Z, assuming all stars have solar abundance such that
+\begin{equation}
+\label{eq:metallicity}
+    [\rm{Fe/H}] = \log_{10}\Big(\frac{Z}{Z_{\odot}}\Big),
+\end{equation}
+\noindent where we assume $Z_{\odot}=0.02$.
+
+\snotes{We count all higher-order companions as secondary, or binary, components.
+We show curves for all 15 of our metallicity bins, increasing in metallicity from darkest to lightest curve colour.
+The lowest metallicity ([Fe/H]=-2.3) shows the highest propensity for short-period binaries, in contrast to higher metallicity systems which have a frequency distribution that has a relatively constant companion frequency \kb{for orbital periods between $10^4$ and $10^6$ days.}}
+%between log$_{10}(\rm{P}_{\rm{orb}}/$day) of four and six.}
+
+%\kb{\sout{Note that this fit represents the binary fraction only for close binaries, equivalent to an integration of the companion frequency curve of Figure \ref{fig:binfrac_porb} up to log$_{10}(\rm{P}_{\rm{orb}}/$day)=6.}}
+\snotes{While we simulate binaries across the entire orbital period distribution, the close binary fraction, which exhibits the discussed metallicity dependence, will be that which impacts the LISA population as systems with $\log_{10}(\rm{P}_{\rm{orb}}/$day)$>4$ will be unlikely to evolve enough to enter the LISA band by present day.}
 
@@
 
-\begin{figure}
-	\includegraphics[width=1\columnwidth]{figures/PSD.pdf}
+\begin{figure*}
+	\includegraphics[width=\textwidth]{figures/PSD.pdf}
     \caption{The PSD of the entire Galactic DWD GW foreground, summed over all metallicities and DWD types vs GW frequency for models FZ and F50.
@@
     \script{PSD.py}
-\end{figure}
+\end{figure*}
 
 \begin{figure*}
-	\includegraphics[width=\textwidth]{figures/LISA_SNR_fiducial_Z.pdf}
 	\includegraphics[width=\textwidth]{figures/LISA_SNR_fiducial.pdf}

### 2022-08-17 src/scripts/CEsep.py

@@ -5,7 +5,10 @@ import matplotlib.pyplot as plt
 import matplotlib as mpl
 import paths
 
-model = "fiducial"
+models = ["fiducial", "alpha25", "alpha5"]
+model_labels = ["fiducial", "$\\alpha 25$", "$\\alpha 5$"]
+metmodel = "F50"
+
 FIREmin = 0.00015
 FIREmax = 13.346
 Z_sun = 0.02
@@ -14,143 +17,158 @@ met_bins = np.logspace(np.log10(FIREmin), np.log10(FIREmax), num)
 met_mids = (met_bins[1:] + met_bins[:-1]) / 2
 whichsep = "CEsep"
 
-Heinter = pd.read_hdf(paths.data / "results.hdf", key = 'intersep_{}_{}_{}_{}'.format(10, 10, "F50", model))
-COHeinter = pd.read_hdf(paths.data / "results.hdf", key='intersep_{}_{}_{}_{}'.format(11, 10,  "F50", model))
-COinter = pd.read_hdf(paths.data / "results.hdf", key='intersep_{}_{}_{}_{}'.format(11, 11,  "F50", model))
-ONeinter = pd.read_hdf(paths.data / "results.hdf", key='intersep_{}_{}_{}_{}'.format(12, 10,  "F50", model))
+fig, ax = plt.subplots(3, 4, figsize=(16, 11))
 
-Heavgs = []
-Hecovs = []
-COHeavgs = []
-COHecovs = []
-COavgs = []
-COcovs = []
-ONeavgs = []
-ONecovs = []
-for i in range(num - 1):
-    meti = met_bins[i]
-    metf = met_bins[i + 1]
-
-    Hebin = Heinter.loc[(Heinter.met>=meti)&(Heinter.met<=metf)]
-    COHebin = COHeinter.loc[(COHeinter.met>=meti)&(COHeinter.met<=metf)]
-    CObin = COinter.loc[(COinter.met>=meti)&(COinter.met<=metf)]
-    ONebin = ONeinter.loc[(ONeinter.met>=meti)&(ONeinter.met<=metf)]
-    if len(Hebin) != 0:
-        Heavgs.append(np.mean(Hebin[whichsep].values))
-        Hecovs.append(np.std(Hebin[whichsep].values))
+for m, model in enumerate(models):
+    if "Z" in model:
[…]

### 2022-08-17 src/scripts/LISA_SNR.py

@@ -4,38 +4,33 @@ import matplotlib.pyplot as plt
 import astropy.units as u
 from legwork.visualisation import plot_sensitivity_curve
 from legwork import psd
+import utils
 import paths
 
 
-def plot_LISAcurves(var, model):
-    from showyourwork.paths import user as Paths
-
-    # instantiate the paths
-    paths = Paths()
+def plot_LISAcurves(var, model, label, ii):
     
     def func(x, a, b, c, d, e):
         return a + b * x + c * x ** 2 + d * x ** 3 + e * x ** 4
-
-    def cosmic_confusion(f, L, t_obs=4 * u.yr, approximate_R=True, confusion_noise=None):
-        lisa_psd_no_conf = psd.power_spectral_density(
-            f, confusion_noise=None, t_obs=4 * u.yr
-        )
-        conf = 10 ** func(
-            x=np.log10(f.value), 
-            a=popt[0], 
-            b=popt[1], 
-            c=popt[2], 
-            d=popt[3], 
-            e=popt[4]
-        ) * t_obs.to(u.s)
-
-        psd_plus_conf = conf + lisa_psd_no_conf
-        return psd_plus_conf.to(u.Hz ** (-1))
-        
-    resolved = pd.read_hdf(paths.data / "results.hdf", key="resolved_DWDs_{}_{}".format(var, model))
     
-    popt = pd.read_hdf(paths.data / "results.hdf", key="conf_fit_DWDs_{}_{}".format(var, model))
-    popt = popt.values.flatten()
+    if model == 'fiducial_Z':
+        cosmic_confusion = utils.cosmic_confusion_var_fiducial
+    elif model == 'alpha25_Z':
+        cosmic_confusion = utils.cosmic_confusion_var_alpha25
+    elif model == 'alpha5_Z':
+        cosmic_confusion = utils.cosmic_confusion_var_alpha5
+    elif model == 'q3_Z':
+        cosmic_confusion = utils.cosmic_confusion_var_q3
+    elif model == 'fiducial':
+        cosmic_confusion = utils.cosmic_confusion_50_fiducial
+    elif model == 'alpha25':
[…]

### 2022-08-17 src/scripts/Mc_vs_dist.py

@@ -7,129 +7,136 @@ import astropy.units as u
 import seaborn as sns
 import paths
 
-model = "fiducial"
-model_Z = "fiducial_Z"
+models = ["fiducial", "alpha25", "alpha5", "q3"]
+model_Zs = ["fiducial_Z", "alpha25_Z", "alpha5_Z", "q3_Z"]
 
-resolved_dat_FZ = pd.read_hdf(
-   paths.data / "results.hdf", key="resolved_DWDs_{}_{}".format("FZ", model_Z)
-
-)
-resolved_dat_FZ = resolved_dat_FZ.loc[resolved_dat_FZ.resolved_chirp == 1.0]
-resolved_dat_F50 = pd.read_hdf(
-    paths.data / "results.hdf", key="resolved_DWDs_{}_{}".format("F50", model)
-)
-resolved_dat_F50 = resolved_dat_F50.loc[resolved_dat_F50.resolved_chirp == 1.0]
-
-Heplot = resolved_dat_FZ.loc[
-    (resolved_dat_FZ.kstar_1 == 10) & (resolved_dat_FZ.kstar_2 == 10)
-]
-COHeplot = resolved_dat_FZ.loc[
-    ((resolved_dat_FZ.kstar_1 == 11) & (resolved_dat_FZ.kstar_2 == 10)) |
-    ((resolved_dat_FZ.kstar_2 == 11) & (resolved_dat_FZ.kstar_1 == 10))
-]
-COplot = resolved_dat_FZ.loc[
-    (resolved_dat_FZ.kstar_1 == 11) & (resolved_dat_FZ.kstar_2 == 11)
-]
-ONeplot = resolved_dat_FZ.loc[
-    ((resolved_dat_FZ.kstar_1 == 12) & (resolved_dat_FZ.kstar_2.isin([10, 11, 12]))) |
-    ((resolved_dat_FZ.kstar_2 == 12) & (resolved_dat_FZ.kstar_1.isin([10, 11, 12])))
-]
-
-
-Heplot_F50 = resolved_dat_F50.loc[
-    (resolved_dat_F50.kstar_1 == 10) & (resolved_dat_F50.kstar_2 == 10)
-]
-COHeplot_F50 = resolved_dat_F50.loc[
-    ((resolved_dat_F50.kstar_1 == 11) & (resolved_dat_F50.kstar_2 == 10)) |
[…]

### 2022-08-17 src/scripts/form_eff.py

@@ -29,9 +29,11 @@ kstar2_list = ['10', '10', '11', '10_12']
 labels = ['10_10', '11_10', '11_11', '12']
 pathtodat = paths.data
 
-models = ["fiducial", "q3", "alpha25", "alpha5"]
-model_labels = ["fiducial", "$q3$", "$\\alpha 25$", "$\\alpha 5$"]
+models = ["fiducial", "alpha25", "alpha5", "q3"]
+model_labels = ["fiducial", "$\\alpha 25$", "$\\alpha 5$",  "$q3$"]
 
+fig, ax = plt.subplots(4, 4, figsize=(16, 14))
+ii = 0
 for m, model_F50 in enumerate(models):
     model_FZ = model_F50 + "_Z"
 
@@ -48,8 +50,8 @@ for m, model_F50 in enumerate(models):
     effCO05 = DWDeff05.CO.values
     effONe05 = DWDeff05.ONe.values
 
-    fig, ax = plt.subplots(1, 4, figsize=(16, 4.5))
-    ax[0].plot(
+    
+    ax[ii, 0].plot(
         np.log10(met_arr[1:] / Z_sun),
         effHe * 1e3,
         color='xkcd:tomato red',
@@ -59,7 +61,7 @@ for m, model_F50 in enumerate(models):
         rasterized=True
     )
 
-    ax[0].plot(
+    ax[ii, 0].plot(
         np.log10(met_arr[1:] / Z_sun),
         effHe05 * 1e3,
         color='xkcd:tomato red',
@@ -70,7 +72,7 @@ for m, model_F50 in enumerate(models):
         rasterized=True
     )
 
-    ax[1].plot(
+    ax[ii, 1].plot(
         np.log10(met_arr[1:] / Z_sun),
         effCOHe * 1e3,
         color='xkcd:blurple',
@@ -80,7 +82,7 @@ for m, model_F50 in enumerate(models):
         rasterized=True
     )
 
-    ax[1].plot(
+    ax[ii, 1].plot(
         np.log10(met_arr[1:] / Z_sun),
         effCOHe05 * 1e3,
         color='xkcd:blurple',
@@ -91,7 +93,7 @@ for m, model_F50 in enumerate(models):
         rasterized=True
     )
 
-    ax[2].plot(
+    ax[ii, 2].plot(
         np.log10(met_arr[1:] / Z_sun),
         effCO * 1e3,
         color='xkcd:pink',
[…]

### 2022-08-17 src/scripts/lisa_nums.py

@@ -14,6 +14,8 @@ met_bins = np.logspace(np.log10(FIREmin), np.log10(FIREmax), num) * Z_sun
 models = ["fiducial", "q3", "alpha25", "alpha5"]
 model_labels = ["fiducial", "$q3$", "$\\alpha 25$", "$\\alpha 5$"]
 
+fig, ax = plt.subplots(4, 4, figsize=(16, 14))
+
 for m, model in enumerate(models):
     model_Z = model + "_Z"
     numsFZ = pd.read_hdf(paths.data / "results.hdf", key="numLISA_30bins_{}_{}".format("FZ", model_Z))
@@ -29,9 +31,7 @@ for m, model in enumerate(models):
     COnums05 = numsF50.CO.values
     ONenums05 = numsF50.ONe.values
 
-    fig, ax = plt.subplots(1, 4, figsize=(16, 4.5))
-
-    ax[0].plot(
+    ax[m, 0].plot(
         np.log10(met_bins[1:]/Z_sun), 
         Henums/1e5, 
         drawstyle='steps-mid', 
@@ -41,7 +41,7 @@ for m, model in enumerate(models):
         rasterized=True
     )
 
-    ax[0].plot(
+    ax[m, 0].plot(
         np.log10(met_bins[1:]/Z_sun), 
         Henums05/1e5,       
         drawstyle='steps-mid', 
@@ -52,9 +52,8 @@ for m, model in enumerate(models):
         rasterized=True
     )
 
-    ax[0].text(0.05, 0.875, 'He + He', fontsize=18, transform=ax[0].transAxes)
     
-    ax[1].plot(
+    ax[m, 1].plot(
         np.log10(met_bins[1:]/Z_sun), 
         COHenums/1e5, 
         drawstyle='steps-mid',     
@@ -63,7 +62,7 @@ for m, model in enumerate(models):
         label='FZ', 
         rasterized=True
     )
-    ax[1].plot(
+    ax[m, 1].plot(
         np.log10(met_bins[1:]/Z_sun), 
         COHenums05/1e5, 
         drawstyle='steps-mid', 
@@ -74,9 +73,8 @@ for m, model in enumerate(models):
         rasterized=True
     )
 
-    ax[1].text(0.05, 0.875, 'CO + He', fontsize=18, transform=ax[1].transAxes)
 
-    ax[2].plot(
+    ax[m, 2].plot(
         np.log10(met_bins[1:]/Z_sun), 
[…]

### 2022-08-17 src/scripts/met_dep_porb.py

@@ -1,0 +1,150 @@
+from scipy.stats import gaussian_kde, norm
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+from scipy.interpolate import interp1d
+from utils import get_Z_from_FeH, get_FeH_from_Z, get_binfrac_of_Z
+import scipy.integrate as integrate
+from matplotlib import rcParams
+import paths
+
+
+def get_porb_kde(Z, close_logP=4.0, wide_logP=6.0, binfrac_tot_solar=0.53, Z_sun=0.02):
+    '''Returns a kde with weights consistent with Fig 19 of Moe+19
+    for the orbital period distribution
+    
+    INPUTS
+    ------------------------
+    Z [array]: metallicity values
+        
+    close_logP [float]: divding line beween close and intermediate orbits
+    
+    wide_logP [float]: dividing line between intermediate and wide orbits
+    
+    binfrac_tot [float]: integrated total binary fraction at solar metallicity
+    
+    RETURNS
+    ------------------------
+    logp [array]: orbital periods drawn from the distribution
+    '''
+    # import the interpolation package
+    from scipy.interpolate import interp1d
+    from scipy.stats import norm
+    from scipy.integrate import trapz
+    
+    # fix to values used in Moe+21
+    logP_lo_lim=0
+    logP_hi_lim=9
+    log_P = np.linspace(logP_lo_lim, logP_hi_lim, 10000)
+    
+    # hard coded from Moe+21
+    logP_pdf = norm.pdf(log_P, loc=4.4, scale=2.1)
+    
+    # set up the wide binary fraction inflection point
+    norm_wide = binfrac_tot_solar/trapz(logP_pdf, log_P)
+    
+    # set up the close binary fraction inflection point
+    FeHclose = np.linspace(-3.0, 0.5, 100)
+    fclose = -0.0648 * FeHclose + 0.3356
+    fclose[FeHclose > -1.0] = -0.1977 * FeHclose[FeHclose > -1.0] + 0.2025
+
+    Zclose = get_Z_from_FeH(FeHclose, Z_sun=Z_sun)
+    
+    fclose_interp = interp1d(Zclose, fclose)
+    
+    fclose_Z = fclose_interp(Z)
[…]

### 2022-08-17 src/scripts/pipeline.py

@@ -28,13 +28,14 @@ FIRE_path = paths.data
 results_path = paths.data
 models = ['fiducial', 'fiducial_Z', 'alpha25', 'alpha25_Z', 'alpha5', 'alpha5_Z', 'q3', 'q3_Z']
 interfile = False
-nproc_gx = 28
+nproc_gx = 40
 nproc_results = len(models)
   
 
 # Get the FIRE metallicity data for the results file
 pp.get_FIRE_met_dat(FIRE_path, results_path)
-    
+
+print('FIRE done!')
 # Generate Milky Way galaxies for each model
 for model in models:
     pp.save_full_galaxy(

### 2022-08-17 src/scripts/postproc.py

@@ -500,27 +500,32 @@ def make_galaxy(dat, verbose=False):
     '''
     pathtodat, fire_path, pathtosave, filename, i, label, ratio, binfrac, interfile, model, nproc = dat
     
+    
     if binfrac < 0.5:
         var_label = 'FZ'
     else:
         var_label = 'F50'
+    
+    
+        
     Lkey = 'Lband_{}_{}'.format(var_label, model)
     Rkey = 'rand_seed_{}_{}'.format(var_label, model)
     Lsavefile = 'Lband_{}_{}_{}_{}.hdf'.format(label, var_label, model, i)
     FIREfile = 'FIRE.h5' 
-    try:
-        pd.read_hdf(pathtosave / Lsavefile, key=Lkey)
-        
-        return [], [], []
-    except:
-        FIRE = pd.read_hdf(fire_path / FIREfile).sort_values('met')
     
+    try:
+        lisa_dat = pd.read_hdf(pathtosave / Lsavefile, key=Lkey)
+        return [], [], [], []
+    except FileNotFoundError:
+        
+        FIRE = pd.read_hdf(fire_path / FIREfile).sort_values('met')
+        
         rand_seed = np.random.randint(0, 100, 1)
         np.random.seed(rand_seed)
         
         rand_seed = pd.DataFrame(rand_seed)
         rand_seed.to_hdf(pathtosave / Lsavefile, key=Rkey)
-    
+        
         # Choose metallicity bin
         met_start = met_arr[i] / Z_sun
         met_end = met_arr[i+1] / Z_sun
@@ -528,8 +533,8 @@ def make_galaxy(dat, verbose=False):
         # Load DWD data at formation of the second DWD component
         conv = pd.read_hdf(pathtodat / filename, key='conv')
         
-        # Limit to 1000 Rsun
-        conv = conv.loc[conv.sep < 1000]
+        # Limit to 10000 Rsun
+        conv = conv.loc[conv.sep < 10000]
         
         # get bin_num indices if needed
         if 'bin_num' not in conv.columns:
@@ -593,7 +598,7 @@ def make_galaxy(dat, verbose=False):
         # systems added from the decimal component of N_astro
         dat = [pop_init_dec[params_list], i, label, ratio, binfrac, pathtosave, interfile]
         LISA_band = filter_population(dat)
-    
+        
         if len(LISA_band) > 0:
             LISA_band = LISA_band[final_params]
[…]

### 2022-08-17 src/scripts/utils.py

@@ -1,4 +1,8 @@
 import numpy as np
+import paths
+import astropy.units as u
+import pandas as pd
+from legwork import psd
 
 #===================================================================================
 # File and Organizing Functions:
@@ -63,6 +67,7 @@ def get_binfrac_of_Z(Z):
     binfrac = np.append(binfrac_low, binfrac_high)
     return binfrac
 
+
 def get_Z_from_FeH(FeH, Z_sun=0.02):
     '''
     Converts from FeH to Z under the assumption that
@@ -80,6 +85,7 @@ def get_Z_from_FeH(FeH, Z_sun=0.02):
     Z = 10**(FeH + np.log10(Z_sun))
     return Z
 
+
 def get_FeH_from_Z(Z, Z_sun=0.02):
     '''
     Converts from Z to FeH under the assumption that
@@ -96,3 +102,157 @@ def get_FeH_from_Z(Z, Z_sun=0.02):
     '''
     FeH = np.log10(Z) - np.log10(Z_sun)
     return FeH
+
+
+def func(x, a, b, c, d, e):
+        return a + b*x + c*x**2 + d*x**3 + e*x**4
+
+    
+def cosmic_confusion_var_fiducial(f, L, t_obs=4 * u.yr, approximate_R=True, confusion_noise=None):
+    popt = pd.read_hdf(paths.data / "results.hdf", key="conf_fit_DWDs_{}_{}".format("FZ", "fiducial_Z"))
+    popt = popt.values.flatten()
+
+    lisa_psd_no_conf = psd.power_spectral_density(
+        f, confusion_noise=None, t_obs=4 * u.yr
+    )
+    conf = 10 ** func(
+        x=np.log10(f.value),
+        a=popt[0],
+        b=popt[1],
+        c=popt[2],
+        d=popt[3],
+        e=popt[4]
+    ) * t_obs.to(u.s)
+
+    psd_plus_conf = conf + lisa_psd_no_conf
+    return psd_plus_conf.to(u.Hz ** (-1))
+
+def cosmic_confusion_var_alpha25(f, L, t_obs=4 * u.yr, approximate_R=True, confusion_noise=None):
+    popt = pd.read_hdf(paths.data / "results.hdf", key="conf_fit_DWDs_{}_{}".format("FZ", "alpha25_Z"))
+    popt = popt.values.flatten()
+
[…]

### 2022-08-18 src/tex/ms.tex
updated text, added more to table, fixed chirp mass figure

@@
 
+%I did some switching around of words
 \textbf{The transition between individually resolved DWDs and the confusion limited, or unresolved, DWD foreground is expected to occur near $\sim1\,\rm{mHz}$ frequencies \citep[e.g.
@@
 There are multiple parameters which shape the Galactic DWD foreground.
+Assuming the evolution of each DWD system is driven solely by GW emission, the frequency derivative scales proportionally to $f_{\rm{GW}}^{11/3}$, causing a pileup of DWDs at lower frequencies \citep[e.g.][]{Breivik2020b}.
+The spatial density of DWDs in the Galaxy which defines the distance to each binary also impacts the foreground amplitude, since GW strain scales inversely with distance.
+Star formation history assumptions combine these two effects by assigning ages and positions to each DWD in the population which determine the present day orbital (and thus GW) frequencies as well as distances to each source.}
+
+%\textbf{There also exists a ``transition" GW frequency at which the GW spectrum transitions from confusion limited to being able to detect individual sources \citep{Ruiter2010}.
+In the confusion-limited regime, greater than one binary exists per LISA frequency bin, creating a superposition of signals which are unable to be disentangled.
+There are multiple parameters which serve to shape the Galactic DWD foreground.
 Assuming the evolution of each DWD system is driven solely by GW emission, the frequency derivative scales proportionally to $f_{\rm{GW}}^{11/3}$, causing a pileup of DWDs at lower frequencies \citep{Breivik2019fg}.
-The spatial density of DWDs in the Galaxy  which defines the distance to each binary also impacts the foreground amplitude, since strain scales inversely with distance.
-Star formation history assumptions combine these two effects by assigning ages and positions to each DWD in the population which determine the present day orbital (and thus GW) frequencies as well as distances to each source.}
+The distance dependence of the spatial density of DWDs in the Galaxy also impacts the foreground amplitude, since strain scales inversely with distance.
+Star formation history assumptions impact the foreground height, as the duration of GW orbital evolution of each system will impact contributions to strain.}
 
@@
 
-%\subsection{The metallicity-dependent binary fraction}
 To date, population synthesis studies of the Galactic population of close DWDs have either assumed a $100\%$ binary fraction or a $50\%$ binary fraction, such that for every three stars formed, two reside in a binary system \citep{Nelemans2001a, Yu2013, Korol2017, Lamberts2019}.
@@
 
-In Section \ref{sec:simulations} we discuss our binary evolution assumptions used in simulating DWD populations and detail the process to produce present-day synthetic Milky-Way-like galaxies.
+In Section \ref{sec:simulations} we discuss our %binary evolution KB commented out
+assumptions used in simulating DWD populations and detail the process to produce present-day synthetic Milky-Way-like galaxies.
 In Section \ref{sec:LISA_obs} we review the derivation of LISA detectability for circular DWD populations at mHz frequencies.
-In Section \ref{sec:results} we detail results showing how a metallicity-dependent binary fraction affects the formation and evolution of DWD populations assuming a fiducial set of binary evolution assumptions.
+In Section \ref{sec:results} we detail results showing how a metallicity-dependent binary fraction affects the formation and evolution of DWD populations assuming \kb{\sout{a fiducial set} four sets of} of binary evolution assumptions.
 In Section \ref{sec:LISA_met} we detail the metallicity dependence of the LISA DWD foreground and resolved population.
-Finally, we repeat our analysis for three sets of binary evolution assumptions to show a robust reduction of the size of the Galactic DWD foreground in LISA for populations simulated with a metallicity-dependent binary fraction in Section \ref{sec:model_compare} and conclude in Section \ref{sec:conclusions}.
+Finally, \kb{\sout{we repeat our analysis for three sets of binary evolution assumptions  to show a robust reduction of the size} we consider how a metallicity-dependent close binary fraction impacts the height} of the Galactic DWD foreground in LISA for \kb{\sout{populations simulated with a metallicity-dependent binary fraction} different binary evolution assumptions} in Section \ref{sec:model_compare} and conclude in Section \ref{sec:conclusions}.
 
@@
 For each DWD type we simulate a grid of $15$ metallicities spaced uniformly in $\log_{10}(Z)$ between $Z=10^{-4}$ to $0.03$, to account for the limits of the \citet{Hurley2000} stellar evolution tracks employed in \cosmic.
-This results in a total of $60$ populations across all DWD types and metallicities.
+This results in a total of $60$ populations across all DWD types and metallicities \kb{for each set of model assumptions}.
 The output of \cosmic\ contains information limited to intrinsic binary properties like mass and orbital period.
@@
 We assume that the Zero Age Main Sequence (ZAMS) masses, orbital periods and eccentricities for each binary are independently distributed.
-We choose primary masses following \citet{Kroupa2001}, a flat mass ratio distribution \citep{Mazeh1992, Goldberg1994}, a log-uniform period distribution following Opik's Law, and a uniform eccentricity distribution following \cite{Geller2019}.
-We initialize all binaries with the same evolution time of $13.7\,\rm{Gyr}$ to capture all potential evolution within a Hubble time.
-We assume a $100\%$ binary fraction in our COSMIC simulations to reduce computation time and scale the simulations to models which assume a constant $50\%$ binary fraction (model F50) or a metallicity-dependent binary fraction (model FZ) in a post-processing scheme.
+We choose primary masses following \citet{Kroupa2001}, a flat mass ratio distribution \citep{Mazeh1992, Goldberg1994} and a uniform eccentricity distribution following \cite{Geller2019}.
+\snotes{For our simulations which follow a metallicity-dependent binary fraction (model FZ), a skewed log-normal orbital period distribution is sampled in accordance with the metallicity-dependent companion frequency of \citet{Moe2021} \kb{\sout{which will be} as} discussed in Section \ref{subsec:metbinfrac}.}
+%\kb{Binaries are then assigned orbital periods by sampling from this distribution.
+As will be discussed below, when this distribution is integrated it results in the binaries having the binary fraction associated with that metallicity.
+} I cut this since I think it's covered above now!
+%\kb{For all FZ simulations, we only retain the binary systems and discard single stars, but save information regarding how much mass in stars is required to create each population for incorporating a metallicity-dependent star formation history as will be discussed in Section \ref{sec:FIRE}.
+} I also don't think we need this info
+\snotes{For our simulations which assume a constant 50\% binary fraction (model F50), we use a log-uniform period distribution following Opik's Law similar to previous studies \citep[e.g.][]{Nelemans2001a, Toonen2012, Korol2017, Lamberts2019}.
+We assume a $100\%$ binary fraction in the F50 COSMIC simulations to reduce computation time and scale the simulations to a constant $50\%$ binary fraction in a post-processing scheme.} We initialize all binaries with the same evolution time of $13.7\,\rm{Gyr}$ to capture all potential evolution within a Hubble time.
+\snotes{Although we simulate binaries across the full orbital period distribution, we discard \kb{DWD} binaries \kb{which form} with separations $a\geq 1000$ R$_\odot$ during post-processing, \kb{\sout{to save on computational work}} since these are unlikely to evolve into the LISA band by present day.}
 
-Since we are primarily interested in the effects of a metallicity-dependent binary fraction, we use a single set of assumptions for binary interactions.
-Our choices follow the \texttt{COSMIC} defaults described in \citet{Breivik2020a} except for the treatment of Roche-lobe overflow (RLO).
+\kb{We consider a fiducial set of assumptions which } follow the \texttt{COSMIC} defaults described in \citet{Breivik2020a} except for the treatment of Roche-lobe overflow (RLO).
 The stability of RLO mass transfer is determined using critical mass ratios resulting from radius-mass exponents \citep{Webbink1985, Hurley2002}, where the critical mass ratio is defined as the ratio of the donor to accretor mass.
@@
 
-\subsection{Metallicity-dependent binary fraction}
-We fit the results presented in \citet{Moe2019} using linear regression to obtain a piecewise relation between the metallicity, [Fe/H] and binary fraction $f_{\rm{b}}$ as
-
-\[f_{\rm{b}}= \begin{cases} 
-      - 0.0648 \cdot [\rm{Fe/H}] + 0.3356, & [\rm{Fe/H}]\leq -1.0 \numberthis \\
-      -0.1977 \cdot [\rm{Fe/H}] + 0.2025, & [\rm{Fe/H}]> -1.0  
-   \end{cases}
-\]
-
-\noindent We convert between [Fe/H] and metallicity Z, assuming all stars have solar abundance such that
-\begin{equation}
-\label{eq:metallicity}
-    [\rm{Fe/H}] = \log_{10}\Big(\frac{Z}{Z_{\odot}}\Big),
-\end{equation}
-\noindent where we assume $Z_{\odot}=0.02$.
+\snotes{The LISA-detectable DWD populations that result from our simulations may vary depending on the assumptions made regarding binary interactions.
+In order to explore the range of results, we complete this study for three binary evolution parameter variations on top of our fiducial set of assumptions.
+For each variation, we consider models FZ and F50 as done in the fiducial case described above.
+In variation $q3$, we vary the assumption for the critical mass ratios at which a RLO interaction remains stable or becomes unstable from our fiducial assumptions such that the critical mass ratio is increased to $3.0$ and thus allows stable mass transfer for more massive RLO donors.
+In variations $\alpha25$ and $\alpha5$, we modify the common envelope ejection efficiency to be either much less ($\alpha=0.25$) or more ($\alpha=5$) than in our fiducial assumption ($\alpha=1$).
+Larger common envelope ejection efficiencies lead to wider post-CE separations, while smaller ejection efficiencies either lead to closer post-CE separations or \kb{stellar} mergers where the envelope ejection fails.
+\kb{\sout{This will be discussed further later on.}} Between all variations, all other prescriptions for binary evolution remain identical besides the one varied parameter.
+We delve in depth into the fiducial results in each section, and then give a brief overview of how the results change for each parameter variation.}
 
@@
 \label{sec:FIRE}
-To create Milky Way-like galaxies which integrate the metallicity-dependent binary fraction, we use the metallicity-dependent ages and positions of galaxy \textbf{m12i} from the ``Latte" suite of the FIRE-2 simulations \citep{Hopkins2015, Wetzel2016, Hopkins2018} to create synthetic, Milky Way-like DWD populations.
+To create Milky-Way-like galaxies which integrate the metallicity-dependent binary fraction, we use the metallicity-dependent ages and positions of galaxy \textbf{m12i} from the ``Latte" suite of the FIRE-2 simulations \citep{Hopkins2015, Wetzel2016, Hopkins2018} to create synthetic, Milky-Way-like DWD populations.
 
@@
 
-The metallicity-dependent binary fraction is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid.
+The metallicity-dependent \kb{close} binary fraction \snotes{for \kb{\sout{close, }}solar-type binaries (P $< 10^4$ days), or simply the \kb{close} binary fraction from here on,} is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid.
 The binary fraction, $f_{\rm{b}}$, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly.
@@
 
-Since our \cosmic\ simulations assume a binary fraction of $f_{\rm{b}} = 1$, we scale the amount of mass sampled at ZAMS required to produce our \cosmic-generated population of DWDs ($M_{\text{b,ZAMS}}$) to the proper amount of mass sampled in single and binary stars ($M_{\text{ZAMS,sim}}$) for each binary fraction and model.
-We do this by sampling single stars and primary masses of binary stars from the \cite{Kroupa2001} IMF and sampling secondary masses of the binary stars from a uniform mass distribution, where the number of binaries is determined by the binary fraction model (F50 or FZ).
-From this sample, we obtain the ratio of mass in single stars to the mass in binary stars as a function of the binary fraction, $R(f_{\rm{b}})$.
+Since our \cosmic\ simulations assume a binary fraction of $f_{\rm{b}} = 1$ \snotes{for model F50}, we scale the amount of mass sampled at ZAMS required to produce our \cosmic-generated population of DWDs ($M_{\text{b,ZAMS}}$) to the proper amount of mass sampled in single and binary stars ($M_{\text{ZAMS,sim}}$).
+We do this by sampling single stars and primary masses of binary stars from the \cite{Kroupa2001} IMF and sampling secondary masses of the binary stars from a uniform mass distribution, where the number of binaries is calculated to ensure $f_{\rm{b}}=0.5$.
+From this sample, we obtain the ratio of mass in single stars to the mass in binary stars, $R(f_{\rm{b}})$.
 For model F50, the ratio is a constant $R(f_{\rm{b}}) = 0.64$.
-For model FZ, the ratio increases from 0.68 at low metallicities to 3.17 at solar metallicity indicating less mass in binaries relative to single stars.
-The total amount of ZAMS mass in single and binary stars is then $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}} (1 + R(f_{\rm{b}}))$.
+\snotes{The total amount of ZAMS mass in single and binary stars is then $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}} (1 + R(f_{\rm{b}}))$.
+For model FZ, no scaling is done since the \cosmic\ simulations already have the binary fraction incorporated, so $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}}$}.
 
@@
 We further discard any DWDs for which the lower mass WD overflows it's Roche lobe before present day, because the outcomes of these interactions are highly uncertain and their treatment is outside the scope of this work \citep[e.g., ][]{Shen2015, Kremer2017}.
-\textbf{We also note that stably accreting WD binaries are unlikely to contribute appreciably to the Galactic DWD foreground due to their small mass ratios at frequencies below $1\,\rm{mHz}$ \citep{Breivik2018}.} The separation at which the lower mass WD overflows its Roche Lobe is defined as
+\textbf{This choice does not significantly affect our results since stably accreting WD binaries are unlikely to contribute appreciably to the Galactic DWD foreground due to their small mass ratios at frequencies below 1 mHz \citep{Breivik2018}.} The separation at which the lower mass WD overflows its Roche Lobe is defined as
 
@@
     \centering
-    \begin{tabular}{|c|c|c|c|c|c|}
+    \begin{tabular}{|c|c|c|c|c|c|c|}
        \hline
-       model & a & b & c & d & e \\
+       parameter variation & model & a & b & c & d & e \\
        \hline
        \hline
-       F50 & -223.5 & -189.8 & -76.8 & -14.0 & -1.0 \\
+       fiducial & F50 & -217.8 & -183.9 & -74.5 & -13.7 & -0.94452821 \\
        \hline
-       FZ & -558.5 & -575.4 & -243.1 & -45.8 & -3.2 \\
+       fiducial & FZ & -268.2 & -243.0 & -100.5 & -18.7 & -1.3 \\
+       \hline
+       $\alpha25$ & F50 & -5520.2 & -6078.3 & -2528.8 & -467.1 & -32.3 \\
+       \hline
+       $\alpha25$ & FZ & -2816.0 & -3066.4 & -1272.7 & -234.7 & -16.2 \\
+       \hline
+       $\alpha5$ & F50 & -178.7 & -142.8 & -58.7 & -11.0 & -0.8 \\
+       \hline
+       $\alpha5$ & FZ & -265.9 & -239.8 & -99.1 & -18.5 & -1.3 \\
+       \hline
+       q3 & F50 & -114.5 & -73.5 & -30.9 & -6.1 & -0.5 \\
+       \hline
+       q3 & FZ & -336.9 & -323.5 & -136.2 & -25.8 & -1.8 \\
        \hline
@@
 \subsection{Metallicity-dependent trends in the formation efficiency of DWDs}\label{sec:formeff}
-The number of DWDs formed per unit solar mass of ZAMS star formation, or DWD formation efficiency $\eta_{\rm{form}}(Z))$, varies with metallicity.
+The number of DWDs formed per unit solar mass of ZAMS star formation, or DWD formation efficiency $\eta_{\rm{form}}(Z)$, varies with metallicity.
 Consequently, a metallicity-dependent binary fraction further impacts the efficiency of DWD formation within the Galaxy.
-Figure \ref{fig:form_eff} shows the DWD formation efficiency as a function of metallicity for each DWD type and for each of our binary fraction models.
+Figure \ref{fig:form_eff} shows the DWD formation efficiency as a function of metallicity for each DWD type\snotes{,\sout{ and for each of our}} binary fraction models\snotes{, and binary evolution parameter variations}.
 In general, the formation efficiency decreases with increasing metallicity.
@@
 
+\subsubsection{\snotes{Fiducial formation efficiency trends}}\label{sec:formeff_fid}
+
 For He + He DWDs, the sudden drop in formation efficiency near $\log(Z/Z_{\odot})=-1.0$, is generally caused by the timescale for which the initially more massive star in the DWD progenitor overflows it's Roche lobe.
-At lower metallicities, donors tend to fill their Roche lobes while they are still on the main sequence and the mass transfer remains stable.
+At lower metallicities, donors tend to fill their Roche lobes while they are still on the main sequence and the mass transfer remains stable \snotes{and serves to widen the binary}.
 This is because, in our \cosmic\ models lower metallicity stars evolve faster than high-metallicity stars and have larger radii near the end of the MS.
-At higher metallicities, mass transfer is initiated when the donor has left the main sequence and the binary enters a common envelope evolution.
+At higher metallicities, mass transfer is initiated when the donor has left the main sequence, and the binary enters a common envelope evolution.
 The ZAMS orbital period leads to different specific evolutionary channels.
@@
 At higher metallicities, the CO WD merges with its companion.
-Higher-metallicity progenitors have a larger fraction of their mass in the convective envelope when compared to lower-metallicity stars of the same mass \citep{Amard2019, Amard2020} Thus a CE phase with a higher-metallicity progenitor requires more orbital energy to eject the common envelope, causing a larger amount of orbital shrinking which results in a merger later in its binary evolution.
+Higher-metallicity progenitors have a larger fraction of their mass in the convective envelope when compared to lower-metallicity stars of the same mass \citep{Amard2019, Amard2020}.
+Thus a CE phase with a higher-metallicity progenitor requires more orbital energy to eject the common envelope, causing a larger amount of orbital shrinking which results in a merger later in its binary evolution.
 
@@
 A subdominant channel of stable He + He DWDs can also occur when a high-metallicity primary overflows it's Roche lobe while still on the GB and thus forms a He WD.
+\snotes{In general, a CO + He binaries fails to form because either a CO + CO or He + He is formed isntead, or a merger occurs before DWD formation.
+We see higher efficiency for FZ than F50 because Co + He binaries prefer to form in log$_{10}$(P$_{\rm{orb}}$/day)$\sim2-4$, which is where the orbital period distribution of FZ peaks.}
 
@@
 Conversely, the lower-metallicity progenitors retain enough mass to cause carbon ignition and leave behind an ONe WD.
+
+\subsubsection{\snotes{Parameter variations formation efficiency trends}}\label{subsec:formeff_vars}
+
+\snotes{For our simulations with parameter variations, we see an interplay of the physics of binary evolution with the skews introduced by the metallicity-dependent orbital period distribution/binary fraction.
+We will summarize how the formation efficiency of each DWD type is impacted by the parameter variations.
+Of note in this analysis is that a) the log-normal metallicity-dependent ZAMS orbital period distribution increasingly skews towards orbital periods below $10^4$ days for decreasing metallicity.
+However, b) the log-uniform P$_{\rm{orb}}$ distribution of F50 produces a higher number of the shortest orbital period systems (below $\sim 100$ days) than for FZ as the tails of the FZ distribution fall quickly below this threshold.}
+
+\snotes{For binary systems leading to He + He DWDs, there are many more mergers for $\alpha25$ than for the fiducial simulations.
+The lower CE efficiency entails mergers from the binary failing to eject the CE, or shrinking the orbit such that it then merges on the second CE phase.
+Because, as discussed above, there are more very short-period binaries in F50, as the ZAMS binary population evolves there are more likely to be binary interactions in the population for F50 than FZ.
+This leads to more mergers in $\alpha25$ occurring for F50 before formation of the DWD and thus a lower formation efficiency overall for F50 in contrast to FZ, as we see in the $\alpha25$ He + He plot of Figure \ref{fig:form_eff}.
+Similarly to the fiducial, a binary that becomes a He + He DWD at lower metallicities would merge before becoming one at higher metallicities because of the longer evolution timescales.
+These later interactions lead to closer post-CE separations and thus more mergers.
+The dip at [Fe/H]=$\sim -1.5\%$ stems from mergers before the DWD forms, similar to for our fiducial model.
+The  peak that occurs in $\alpha25$ at $\sim 10\%$ Z$_\odot$ arises from binaries evolving faster (i.e.
+interacting earlier) as metallicity increases, meaning that equivalent binaries that would have merged or formed a CO + He DWD instead at lower metallicities now survive into an He + He.
+At higher metallicities, there are a higher proportion of wide-separation systems, which evolve off the Main Sequence too slowly to form a He + He DWD, causing the efficiency drop.
+For $\alpha5$, there are significantly fewer mergers, as expected since binaries are more likely to survive a CE phase from the higher CE efficiency.
+Systems that would normally merge for $\alpha25$ now survive, and are shrunk to short orbits through CE interactions to evolve in the LISA band.
+The number of DWDs thus makes up a higher fraction of the total simulated binary population overall, thus we see in general higher formation efficiencies than for our fiducial simulations (which has $\alpha=1$), and even higher than for our variation with $\alpha=0.25$.
+Beyond this, the efficiency drop across metallicity is similar to the fiducial in that it depends on the metallicity-dependent ZAMS orbital period distribution emphasizing short-period systems at low metallicities, and in the change of formation channel for different period ranges across metallicity.
+We see the highest formation efficiency for variation $q3$.
+Only the shortest-period binaries do not form a DWD through mergers at higher metallicities.
+At low metallicities, we see that even binaries with very close ZAMS separations form He + He DWDs.
+We thus see a higher efficiency from F50 over FZ because of the higher number of shortest-period ZAMS binaries in the log-uniform distribution of F50.}
+
+\snotes{For CO + He binaries, there are again many more mergers for $\alpha25$ relative to the fiducial case.
+This is the dominating way that binaries are lost at higher metallicities.
+At low metallicities we also see a number of systems form CO + CO binaries instead -- this is especially the case in a ``Goldilocks zone" around log$_{10}$(Z/Z$_\odot$)sim -2, where RLOF occurs late enough in evolution that mass transfer remains stable and CO + CO's are formed, hence why we see a dip in the formation efficiency.
+Because $\alpha5$ allows for less mergers due to the high CE efficiency, the formation efficiency is mostly governed by our metallicity-dependent orbital period distribution.
+At higher metallicities the majority of lost systems from mergers or from forming He + He binaries instead due to the faster evolution at high metallicities and increasing radii allowing for earlier interactions and hence stripping of both star's envelopes [$\leftarrow$ is this correct logic?].
+At higher metallicities, we also have the ZAMS orbital period distribution of FZ drops below the flat distribution for F50 and extends out to orbital periods beyond what would form a CO + He, thus the formation efficiencies for FZ and F50 cross at log$_{10}$(Z/Z$_\odot$)$\sim-0.5$.}
+
+\snotes{** still need to do q3 **, and all for CO + CO and ONe + X}
 
@@
 The solid lines denote the average value, and the $1\sigma$ variance is shown in the surrounding shading.
-The average CE separation increases in general across metallicity.
+\snotes{We show this for our fiducial model and two of the binary parameter variations.
+For our fiducial, $\alpha25$ and $\alpha5$ models,} the average CE separation increases in general across metallicity.
 Higher-metallicity binaries will interact earlier in the binary's lifetime than a lower-metallicity binary of equal separation due to their relatively larger maximum radii.
@@
 This regulation plays a key role in smearing out any observable effects of a metallicity-dependent binary fraction in the population of DWDs observable by LISA.
+\snotes{The slope of the increase for these three models is dictated by the CE efficiency $\alpha$.
+With increasing metallicity there is a deepening of the convective envelope of the star compared to its lower metallicity counterparts at the same point in its evolution [is this the first time this idea is introduced?
+need to check], requiring more orbital energy to be available in order to eject the CE.
+Thus the high-metallicity binaries must have even wider separations for lower $\alpha$ values to ensure the binary does not merge before the envelope is ejected.
+We thus see a steeper separation slope for $\alpha25$, a less steep slope for $\alpha5$, and an intermediate slope for our fiducial model which has $\alpha=1$.}
 
-Note that the average CE separation is close to the qualitative limit for close binaries of $P_{\rm{orb}}\gtrsim10^{4}\,\rm{day}$ for the CO + CO and ONe + X binaries.
+\snotes{The DWDs in model $q3$ that survive into the LISA band at present day have different formation channels than those of our other three models.
+Most importantly, the first interaction of these binaries are \emph{not} a CE interaction, but rather a phase of stable mass transfer.
+Because of this, we do not include it in Figure \ref{fig:CEsep} because it does not reflect the binary interactions for these simulations.
+All the binaries in the other models have more than one instance of a CE phase during their evolution, and rarely undergo stable mass transfer.
+The systems in $q3$ by contrast typically undergo RLO followed by a phase of stable mass transfer as the binary's first interaction.
+During mass transfer the orbit first shrinks, and then will slightly widen once the binary's mass ratio flips.
+This process leads to formation of the first WD component.
+The companion is then formed later in the binary's evolution through a CE phase.
+Almost all systems in $q3$ undergo only a single CE phase.
+Of particular interest in $q3$ is the CO + He systems.
+All of the $q3$ CO + He binaries that end up in the LISA band have the Helium WD unexpectedly form first through stable mass transfer, with the CO WD forming second through a CE.
+These binaries tend to all have similar resulting orbital separations from mass transfer,  as can be seen by the relatively constant curve for CO + He's $\overline{a}_{\rm{CE}}$.
+There is still a slight increasing trend in CO + He (as well as CO + CO and a more pronounced trend in He + He) for $q3$ that stems from the metallicity-dependent convective envelope discussion above.
+We also see that the average interaction separation are overall lower for models $q3$ and $\alpha5$ than for the other two due to the orbital shrinkage that has already occured from stable mass transfer and the efficient CE phase that will lead to minimal orbital shrinkage respectively.}
+
+\snotes{Strikeout: [\emph{Note that the average CE separation is close to the qualitative limit for close binaries of $P_{\rm{orb}}\gtrsim10^{4}\,\rm{day}$ for the CO + CO and ONe + X binaries.
 We investigated the fraction of close DWD progenitors which formed with orbital periods above this range for each DWD type.
@@
 This suggests that our application of the close binary fraction may not be valid over the entire range of the DWD progenitor population.
-However, since the relative sizes of CO + CO and ONe + X are small compared to the He + He and CO + He populations, we leave a further investigation of these effects to a future study.
+However, since the relative sizes of CO + CO and ONe + X are small compared to the He + He and CO + He populations, we leave a further investigation of these effects to a future study.}] [$\leftarrow$ I think we can take out this whole paragraph since we now take this into account!]}
 
@@
 While metallicity impacts the intrinsic properties of our simulated DWD populations as described in Sections~\ref{sec:formeff} and \ref{sec:CEsep}, when we consider the present-day Galactic close DWDs we find that the population detectable by LISA changes only numerically.
-The number of DWDs in the LISA frequency band decreases by $\sim50\%$ when comparing model F50 to model FZ.
+The number of DWDs in the LISA frequency band decreases by $\sim50\%$ when comparing model F50 to model FZ \snotes{for variations $\alpha5$ and $q3$, but remain approximately unchanged for our fiducial and $\alpha25$ variations.}
 
@@
 
-Figure \ref{fig:lisa_nums} shows the number of DWDs orbiting with frequencies $f_{\rm{GW}} > 0.1\,\rm{mHz}$ against metallicity for each DWD type.
+Figure \ref{fig:lisa_nums} shows the number of DWDs orbiting with frequencies $f_{\rm{GW}} > 0.1\,\rm{mHz}$ against metallicity for each DWD type \snotes{and parameter variation}.
 The solid lines show DWDs from model FZ, and the dashed lines show DWDs from model F50.
@@
 The largest contribution to the population comes from metallicities above $\sim$ 0.01Z$_\odot$.
-The discrepancy between the two binary fraction models is also the most significant above this threshold.
-When creating our DWD populations the DWD formation efficiency, number of \textbf{m12i} star particles, and binary fraction all compete.
+\snotes{Any} discrepancy between the two binary fraction models is also the most significant above this threshold.
+When creating our DWD populations the DWD formation efficiency, number of \textbf{m12i} star particles, and \snotes{metallicity-dependent} binary fraction \snotes{and ZAMS orbital period distribution} all compete.
 The amount of stars formed in \textbf{m12i} at higher metallicity values overwhelms the drop in DWD formation efficiency by multiple orders of magnitude, so this effect dominates when determining the number of stars initially sampled in the population for $f_{\rm{b}}$.
 
-There are two peaks in the distribution of He + He DWDs.
-This occurs because near $Z\simeq 0.1Z_\odot$, the DWD formation efficiency transitions from near constant values to a sharp decrease (see Figure \ref{fig:form_eff}).
+There are two peaks in the distribution of He + He DWDs \snotes{which are most prominent in the fiducial and $\alpha25$ variations, and not as obvious for $\alpha5$ or $q3$.
+The prominent first peak in fiducial and $\alpha25$} occurs because near $Z\simeq 0.1Z_\odot$, the DWD formation efficiency transitions from near constant values to a sharp decrease (see Figure \ref{fig:form_eff}).
 However, for a drop in the formation efficiency by a factor of of $\sim$ six, the amount of star formation in galaxy \textbf{m12i} increases by more than an order of magnitude for supersolar metallicities.
 Above $Z=Z_\odot$ this overcompensates for the efficiency drop, producing the second peak.
+\snotes{For $\alpha5$ and $q3$, the lack of constraints on binary evolution -- from the increased CE efficiency in the former and increased propensity for stable mass transfer in the latter -- allow for less failed binaries from merging.
+This leads to less dramatic drops in formation efficiency across metallicity and thus suppressing the formation of two peaks in the number of LISA-band systems.}
+
+\snotes{The $\alpha5$ and $q3$ variations have a higher number of F50 systems than FZ for all DWD types.
+This is due to the log-uniform P$_{\rm{orb}}$ distribution of F50 having more of the shortest-period binaries than the tails of the log-normal distribution of FZ, a discrepancy which becomes more significant with increasing metallicity as the FZ distribution moves from a peak of log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 3-4$ to log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 4-6$.
+This tail is less likely to survive to the LISA band at present day for the first two variations due to the harder binary evolution constraints.
+This is why we see essentially equal number of systems between FZ and F50 for the fiducial and $\alpha25$ variation: although the close binary fraction leads to a greater number of low-metallicity systems, this is compensated for by the FIRE distribution as well as the tendency for the shortest-period systems that F50 has a greater number of to merge, essentially washing out all differences between the populations.}
 
 \begin{figure*}
-	\includegraphics[width=\textwidth]{figures/Mc_vs_dist.pdf}
+	\includegraphics[width=\textwidth]{figures/Mc_vs_dist_fiducial.pdf}
     \caption{The chirp mass vs distance for each DWD type is shown.
@@
 
-The reduced number of DWDs in model FZ relative to model F50 is also apparent in the GW PSD LISA will observe.
+\snotes{\sout{The reduced} A change in the} number of DWDs in model FZ relative to model F50 is also apparent in the GW PSD LISA will observe.
 We show the GW PSD of each model, as well as the confusion estimate, in Figure~\ref{fig:PSD}.
-While model F50 (dark blue) and model FZ (light blue) produce several thousand large spikes in the PSD across LISA's frequency band, the overall foreground height, including the confusion, is larger for model F50.
+While model F50 (dark blue) and model FZ (light blue) produce several thousand large spikes in the PSD across LISA's frequency band, the overall foreground height, including the confusion, is larger for model F50 \snotes{for $\alpha5$ and $q3$}.
 This is a direct consequence of the overall reduction in the size of the close DWD population in model FZ.
+\snotes{As we would expect, the foreground height remains unchanged for the fiducial and $\alpha25$ variations}.
 
@@
 modeled confusion foreground from each population in black, and the the entire population for each model in grey.
-Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models.
+\snotes{Plots for our three parameter variations can be found in Appendix \ref{appendix:ASD_vars}.} Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models.
 The populations containing at least one He WD occupy the lower-ASD, higher-GW frequency region of parameter space compared to the total population, with CO + He DWDs having larger ASDs than the He + He DWD population.
@@
 
-We note that while the height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 2 for model FZ relative to model F50, the number of resolved sources is not reduced to an equal degree.
-This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.
-Between models FZ and F50, the number of resolvable systems with SNR $>7$ over all DWD types decreases by only $\sim14\%$.
+We note that \snotes{\sout{while} for all our simulation results, any changes in} the height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ \snotes{Strikeout: [\emph{is reduced by a factor of 2 for model FZ relative to model F50, the number of resolved sources is not reduced to an equal degree.}] between F50 and FZ does not necessarily reflect how the number of individually resolvable systems is impacted.
+For the fiducial model and $\alpha25$ variation, the number of resolvable systems with SNR $>7$ do not change much (are reduced by 7\% and increased by 6\% respectively).
+However, $\alpha5$ sees a reduction in the number of resolvable systems by only 14\%, and $q3$ sees an \emph{increase} by 23\%.
+A large portion of the increase of $q3$ is contributed to by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).
+[Not really sure what to say about the alpha5 reduction?]} %The metallicity-dependent ZAMS orbital period distribution of Figure \ref{fig:binfrac_porb} also has a wide-binary tail that extents more than an order of magnitude longer than the log-uniform distribution of F50 -- there are thus more wide binaries created in the FZ simulations than F50.
+Many of these may not make it to the LISA band by present day, but }
+\snotes{Strikeout: [\emph{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.
+Between models FZ and F50, the number of resolvable systems with SNR $>7$ over all DWD types decreases by only $\sim14\%$.}]}
 
@@
 Assuming a chirp resolution of $1/T_{\rm{obs}}^2 \sim 8\times10^{-9}\,\rm{Hz}^2$, we select the DWDs whose chirp masses and distances can be measured.
-Figure \ref{fig:Mc_vs_dist} shows the chirp mass vs the luminosity distance for each DWD type in this selected population.
+Figure \ref{fig:Mc_vs_dist} shows the chirp mass vs the luminosity distance for each DWD type \snotes{and variation} in this selected population.
 The contours show the $5^{\rm{th}}$, $25^{\rm{th}}$, $50^{\rm{th}}$, $75^{\rm{th}}$, and $95^{\rm{th}}$ percentiles for models FZ (light blue) and F50 (dark blue, dashed).
 Despite the reduction in the height of the confusion foreground when considering model FZ relative to F50, we find that LISA is unable to differentiate between the chirp mass -- distance distributions of the two models.
+\snotes{Minor observed differences -- e.g.
+slightly changed contour shapes in He + He $\alpha25$ or ONe + X $q3$ -- are artifacts caused by low statistics since there are so few binaries in this selected population.
+The only population with a significant change between models is for ONe + X's $\alpha5$ distributions, where we see a skew to lower masses.
+This is because a higher fraction of the binaries are ONe + He (in which Helium WDs tend to have smaller masses) for FZ than F50 -- a Helium companion makes up 10\% of this selected population for F50 compared with 42\% for FZ.
+Furthermore, $\sim8$\% of the F50 measurable systems are ONe + ONe binaries, versus 0\% for FZ.
+Because ONe have larger masses, this also creates the high-mass concentration we see in the F50 contours.}
 
-\section{Binary evolution \textbf{parameter variations}}
+\section{Binary evolution \textbf{parameter variations} \snotes{discussion}}
 \label{sec:model_compare}
@@
 
-In order to test the robustness of the reduction of the height of the Galactic DWD GW foreground when assuming a metallicity-dependent binary fraction, we repeat our analysis using three different binary evolution \textbf{parameter variations}.
-For each variation, we consider models FZ and F50 as done in the fiducial case described above.
+\snotes{Strikeout: [\emph{In order to test the robustness of the reduction of the height of the Galactic DWD GW foreground when assuming a metallicity-dependent binary fraction, we repeat our analysis using three different binary evolution \textbf{parameter variations}.}]}
+
+\snotes{[For each variation, we consider models FZ and F50 as done in the fiducial case described above.
 In variation $q3$, we vary the assumption for the critical mass ratios at which a RLO interaction remains stable or becomes unstable from our fiducial assumptions such that the critical mass ratio is increased to $3.0$ and thus allows stable mass transfer for more massive RLO donors.
 In variations $\alpha25$ and $\alpha5$, we modify the common envelope ejection efficiency to be either much less ($\alpha=0.25$) or more ($\alpha=5$) than in our fiducial assumption ($\alpha=1$).
-Larger common envelope ejection efficiencies lead to wider post-CE separations, while smaller ejection efficiencies either lead to closer post-CE separations or mergers where the envelope ejection fails.
+Larger common envelope ejection efficiencies lead to wider post-CE separations, while smaller ejection efficiencies either lead to closer post-CE separations or mergers where the envelope ejection fails.] $\leftarrow$ this paragraph was moved to methods}
 
@@
 
-Interestingly, when we compare the populations of each binary fraction model for our variations, we find that the number of close DWDs reduces by the constant factor of two as seen in our fiducial set of assumptions.
-This is illustrated in \ref{fig:model_comp}.
+Interestingly, when we compare the populations of each binary fraction model for our variations, we find that the number of close DWDs \snotes{Strikeout: [\emph{reduces by the constant factor of two as seen in our fiducial set of assumptions.}] remains approximately unchanged for our fiducial set of assumptions and $\alpha25$ variation, but is reduced by 50\% for variations $\alpha5$ and $q3$.} This is illustrated in Figure \ref{fig:model_comp}.
 The top panel shows the confusion foreground fits for each binary evolution variation (different colored lines) and for each binary fraction model where the solid lines show FZ models and dotted lines show F50 models.
 The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for the FZ models vs the F50 models for each variation.
-Even though the number of DWDs in the LISA band spans over two orders of magnitude, the ratio of FZ to F50, as well as the spectral shape of the confusion fit, stays fixed at a constant factor of two reduction.
-This suggests that assuming a metallicity-dependent binary fraction reduces the size of the Galactic close DWD population by a factor of $\sim$ two and the strength of the Galactic DWD GW foreground for LISA \emph{regardless of the chosen binary evolution model}.
+\snotes{\sout{Even though} The} number of DWDs in the LISA band spans over two orders of magnitude, \snotes{and} the ratio of FZ to F50, as well as the spectral shape of the confusion fit, \snotes{\sout{stays fixed at a constant factor of two reduction} is either relatively unchanged or reduced by a factor of approximately two}.
+This suggests that assuming a metallicity-dependent binary fraction \snotes{\sout{reduces} may change} the size of the Galactic close DWD population by a factor of $\sim$ two and the strength of the Galactic DWD GW foreground for LISA \snotes{\sout{\emph{regardless of the chosen binary evolution model}} depending on the chosen binary evolution model.}
 
@@
 However, when considering the close DWD populations observable by LISA, we find that the only distinguishing features between models which assume a metallicity-dependent binary fraction (model FZ) and models which assume a flat $50\%$ binary fraction (model F50) are the population sizes and the strength of the Galactic DWD GW foreground.
-Models which assume a metallicity-dependent binary fraction produce Galactic DWD populations that are reduced by a factor of two relative to the standard model assumptions.
-This reduction extends to the height of the confusion foreground in the LISA data stream.
+Models which assume a metallicity-dependent binary fraction produce Galactic DWD populations that \snotes{\sout{are reduced by a factor of two} were unchanged} relative to the standard model assumptions.
+\snotes{However, our results are highly dependent on the chosen binary evolution model.
+We extended our study to include three binary evolution \textbf{parameter variations} to investigate the sensitivity of the DWD population changes in assumptions for mass transfer stability and common envelope ejection efficiencies.
+While our binary evolution parameter variations change the size of the LISA-observable populations dramatically, the size of the close Galactic DWD population and the height of the confusion foreground for models which assume a metallicity-dependent binary fraction appears to either remain unchanged \emph{or} be reduced by 50\%.} This reduction extends to the height of the confusion foreground in the LISA data stream.
+\snotes{These two results highlight the interplay between our dominating distributions (from the FIRE star formation history, metallicity-dependent ZAMS orbital period, and subsequent metallicity-dependent binary fraction) and physics constraints on LISA DWD formation, and serves to emphasize the sensitivity of the Galactic population of LISA-detectable DWDs to the intricacies of binary evolution.
+Values like CE efficiency are undergoing continuous study in current literature and an exact value has yet to be identified.
+We hope by exploring a range of possibilities in this work, we can capture the variation in predictions of the LISA DWD population that may be observed.}
 
-We extended our study to include three binary evolution \textbf{parameter variations} to investigate whether the DWD population reduction was robust to changes in assumptions for mass transfer stability and common envelope ejection efficiencies.
-While our binary evolution \textbf{parameter variations} change the size of the LISA-observable populations dramatically, the reduction in the size of the close Galactic DWD population and the height of the confusion foreground for models which assume a metallicity-dependent binary fraction is robust.
-An important consequence of a lower Galactic DWD confusion foreground is that relative to the total DWD population, more DWDs can be individually resolved because of the reduction in competing GW signals.
-While the number of DWDs radiating GWs in the LISA frequency band is reduced by a factor of two for model FZ relative to model F50, the number of resolved sources is less affected with a population-wide reduction of $14\%$.
+\snotes{Strikeout: [\emph{We extended our study to include three binary evolution \textbf{parameter variations} to investigate whether the DWD population reduction was robust to changes in assumptions for mass transfer stability and common envelope ejection efficiencies.
+While our binary evolution \textbf{parameter variations} change the size of the LISA-observable populations dramatically, the reduction in the size of the close Galactic DWD population and the height of the confusion foreground for models which assume a metallicity-dependent binary fraction is robust.}]$\leftarrow$[moved/edited into above paragraph]} An important consequence of a lower Galactic DWD confusion foreground is that relative to the total DWD population, more DWDs can be individually resolved because of the reduction in competing GW signals.
+While the number of DWDs radiating GWs in the LISA frequency band is reduced by a factor of two for model FZ relative to model F50 \snotes{for variations $\alpha25$ and $q3$}, the number of resolved sources is less affected with a population-wide reduction of $14\%$ \snotes{for the former, and surprisingly an increase by 23\% for the latter}.
 These results are far-reaching since the strength of the Galactic DWD confusion foreground has direct consequences on the detectability of all other LISA sources with small SNRs.
 An increase in resolution capability from the reduced confusion foreground can be extended to other galactic binaries that LISA will observe at these frequencies like those involving neutron stars and stellar-origin black holes, as well as other more exotic GW sources like merging supermassive black holes, extreme mass ratio inspirals, or cosmological GW backgrounds.
-Based on our results, we suggest that studies which employ fits to the confusion foreground based on population synthesis results consider reducing the strength of the Galactic foreground PSD by a factor of two.
+Based on our results, we suggest that studies which employ fits to the confusion foreground based on population synthesis results consider reducing the strength of the Galactic foreground PSD by a factor of two \snotes{depending on the chosen binary evolution model}.
 
 \begin{acknowledgments}
-The authors are grateful for helpful discussions with Carles Badenes, Christine Mazzola Daher, and the Gravitational Waves and Astronomical Data groups at the CCA.
+The authors are grateful for helpful discussions with Carles Badenes, Christine Mazzola Daher, Kaitlin Kratter, and the Gravitational Waves and Astronomical Data groups at the CCA.
 The authors are also grateful to the referee for providing a thoughtful review which strengthened the presentation of the manuscript.
@@
           \texttt{scipy}\ \citep{scipy}
+          \texttt{seaborn}\ \citep{Waskom2021}
           }
@@
 
+\appendix
+\section{Amplitude Spectral Densities for Binary Evolution Parameter Variations}\label{appendix:ASD_vars}
+
+\begin{figure*}[h]
+    \centering
+	\includegraphics[width=0.8\textwidth]{figures/LISA_SNR_alpha25.pdf}
+	\includegraphics[width=0.8\textwidth]{figures/LISA_SNR_alpha5.pdf}
+	\includegraphics[width=0.8\textwidth]{figures/LISA_SNR_q3.pdf}
+    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for each DWD type \snotes{and variation}.\snotes{\sout{ where the top row shows} The rows alternate between \sout{ the population from}} model FZ and \snotes{\sout{the bottom row shows the population}} from model F50.
+In each panel, the LISA sensitivity curve, including the confusion foreground for each model, is shown in black and the total population for each model is shown in grey.
+\snotes{Again, w}e find that each model qualitatively exhibits similar characteristics and that the only change is in the yield of resolved DWDs for each type based on the strength of the confusion foreground.}
+    \label{fig:LISA_SNR_vars}
+     \script{LISA_SNR.py}
+
+\end{figure*}
+
+\begin{figure*}[h]
+    \centering
+	\includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_alpha25.pdf}
+	\includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_alpha5.pdf}
+	\includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_q3.pdf}
+    \caption{chirp mass distance distributions}
+    \label{fig:Mc_vs_dist_vars}
+    \script{Mc_vs_dist.py}
+\end{figure*}
 \end{document}
+
+\end{document}

### 2022-08-18 src/scripts/Mc_vs_dist.py

@@ -6,18 +6,19 @@ import matplotlib.pyplot as plt
 import astropy.units as u
 import seaborn as sns
 import paths
+from matplotlib import patches
 
 models = ["fiducial", "alpha25", "alpha5", "q3"]
 model_Zs = ["fiducial_Z", "alpha25_Z", "alpha5_Z", "q3_Z"]
 
-fig, ax = plt.subplots(4, 4, figsize=(16,16))
-levels = [0.05, 0.25, 0.50, 0.75]
+levels = [0.05, 0.25, 0.50, 0.75, 0.95]
+#levels=5
 label_y = [0.35, 0.49, 0.95, 1.6]
 colors = ['#add0ed', '#2b5d87', '#4288c2', '#17334a']
 figlabels = ['He + He', 'CO + He', 'CO + CO', 'ONe + X']
 
-ii = 0
 for model, model_Z in zip(models, model_Zs):
+    fig, ax = plt.subplots(1, 4, figsize=(16,4.5))
 
     resolved_dat_FZ = pd.read_hdf(
        paths.data / "results.hdf", key="resolved_DWDs_{}_{}".format("FZ", model_Z)
@@ -73,70 +74,97 @@ for model, model_Z in zip(models, model_Zs):
         for x in [Heplot_F50, COHeplot_F50, COplot_F50, ONeplot_F50]
     ]
     
-    for dist, Mc, dist_F50, Mc_F50, jj in zip(dists[:1], M_c[:1], dists_F50[:1], M_c_F50[:1], range(len(dists))[:1]):
-        sns.kdeplot(
-            x=dist, 
-            y=Mc, 
-            fill=False, 
-            ax=ax[ii, jj], 
-            color=colors[0], 
-            zorder=3, 
-            linewidths=3.5, 
-            label='FZ', 
-            levels=levels
-        )
-        sns.kdeplot(
-            x=dist_F50, 
-            y=Mc_F50, 
-            fill=False, 
-            ax=ax[ii, jj], 
-            color=colors[1], 
-            zorder=6,
-            linewidths=3.5, 
-            linestyles='--', 
-            label='F50', 
-            levels=levels 
-        )
-        handles, labels = ax[ii, jj].get_legend_handles_labels(legend_handler_map=None)
-        ax[ii, jj].legend(handles=handles,
-                      labels=labels,
-                      loc=(0, 1.01),
-                      prop={'size': 15},
-                      ncol=2, 
-                      frameon=False)
[…]

### 2022-08-18 src/scripts/model_comp.py

@@ -46,6 +46,7 @@ for model in model_names:
         lisa_ratio.append(n_lisa_FZ / n_lisa_F50)
         popt_FZ = popt_FZ.values.flatten()
         popt_FZ_list.append(popt_FZ)
+        print(model, popt_FZ)
         
     
     else:
@@ -58,6 +59,7 @@ for model in model_names:
         n_lisa_F50_list.append(n_lisa_F50)
         popt_F50 = popt_F50.values.flatten()
         popt_F50_list.append(popt_F50)
+        print(model, popt_F50)
         
 
 for popt_F50, popt_FZ, ii in zip(popt_F50_list, popt_FZ_list, range(len(popt_FZ_list))):

### 2022-08-19 src/tex/ms.tex
minor text edits

@@
     \centering
-    \begin{tabular}{|c|c|c|c|c|c|c|}
+    \begin{tabular}{|c|c|c|c|c|c|}
        \hline
-       parameter variation & model & a & b & c & d & e \\
+       model & a & b & c & d & e \\
        \hline
        \hline
-       fiducial & F50 & -217.8 & -183.9 & -74.5 & -13.7 & -0.94452821 \\
+       fiducial, F50 & -217.8 & -183.9 & -74.5 & -13.7 & -1.0 \\
        \hline
-       fiducial & FZ & -268.2 & -243.0 & -100.5 & -18.7 & -1.3 \\
+       fiducial, FZ & -268.2 & -243.0 & -100.5 & -18.7 & -1.3 \\
        \hline
-       $\alpha25$ & F50 & -5520.2 & -6078.3 & -2528.8 & -467.1 & -32.3 \\
+       $\alpha25$, F50 & -5520.2 & -6078.3 & -2528.8 & -467.1 & -32.3 \\
        \hline
-       $\alpha25$ & FZ & -2816.0 & -3066.4 & -1272.7 & -234.7 & -16.2 \\
+       $\alpha25$, FZ & -2816.0 & -3066.4 & -1272.7 & -234.7 & -16.2 \\
        \hline
-       $\alpha5$ & F50 & -178.7 & -142.8 & -58.7 & -11.0 & -0.8 \\
+       $\alpha5$, F50 & -178.7 & -142.8 & -58.7 & -11.0 & -0.8 \\
        \hline
-       $\alpha5$ & FZ & -265.9 & -239.8 & -99.1 & -18.5 & -1.3 \\
+       $\alpha5$, FZ & -265.9 & -239.8 & -99.1 & -18.5 & -1.3 \\
        \hline
-       q3 & F50 & -114.5 & -73.5 & -30.9 & -6.1 & -0.5 \\
+       q3, F50 & -114.5 & -73.5 & -30.9 & -6.1 & -0.5 \\
        \hline
-       q3 & FZ & -336.9 & -323.5 & -136.2 & -25.8 & -1.8 \\
+       q3, FZ & -336.9 & -323.5 & -136.2 & -25.8 & -1.8 \\
        \hline
     \end{tabular}
-    \caption{Polynomial fitting coefficients for the confusion foreground fit of Equation~\ref{eq:fit} for each binary fraction model.}
+    \caption{Polynomial fitting coefficients for the confusion foreground fit of Equation~\ref{eq:fit} for each binary fraction model and parameter variation.}
     \label{tbl:fits}
@@
 CO DWDs thus have a distribution in progenitor separation that extends to larger values than for other DWD types.
-Most need $> 0.3$ Gyr to form.
-These systems have component WD masses between $0.35$--$1.0\,M_\odot$ and make up the majority of the DWD population.
+Most \kb{CO + CO} DWDs need $> 0.3$ Gyr to form\kb{\sout{.
+These systems},} have component WD masses between $0.35$--$1.0\,M_\odot$, and make up the majority of the DWD population.
 
@@
 Because an ONe WD can have a companion of any other WD type in our study, there is a spread in their distributions for separation, secondary mass, final orbital period, and formation time.
-In general, however, these systems result from wider separations to allow for the evolution of the ONe component without merging, e.g.
-all initial separations in our \cosmic \ populations have separations $\gtrsim 1.5\,R_\odot$.
-ONe + X DWDs can form on short timescales, as low as $30\,\rm{Myr}$ for the majority of high-metallicity systems.
+In general, however, these systems result from wider separations to allow for the evolution of the ONe component without merging\kb{\sout{, e.g.}.
+For example,} all initial separations in our \cosmic \ populations have separations $\gtrsim 1.5\,R_\odot$.
+ONe + X DWDs can form on short timescales, as low as $30\,\rm{Myr}$, for the majority of high-metallicity systems.
 
@@
 In general, the formation efficiency decreases with increasing metallicity.
-This effect is exaggerated for model FZ which assumes a binary fraction which also decreases with increasing metallicity.
+This effect is exaggerated for model FZ which assumes a \kb{close} binary fraction which also decreases with increasing metallicity.
+\kb{In the following sub-sections, we describe the formation efficiency trends for our fiducial model in detail and then describe the changes arising from each binary evolution parameter variation.}
 
@@
 The ZAMS orbital period leads to different specific evolutionary channels.
-For short-period systems with periods below $10~\rm{days}$, this leads to a stellar merger due to insufficient orbital energy to eject the envelope.
+For short-period systems with periods below $10~\rm{days}$, \kb{\sout{this} and common envelope} leads to a stellar merger due to insufficient orbital energy to eject the envelope.
 Stellar mergers continue to dominate the evolutionary pathways of systems with intermediate orbital periods ($1 < \log_{10}(P_{\rm{orb}}/\rm{day}) < 2.5$).
@@
 
-For short-period CO + He DWD progenitor binaries with orbital periods below $\sim30~\rm{days}$, the only channel for mergers before DWD formation is during a CE evolution.
+For short-period CO + He DWD progenitor binaries with orbital periods below $\sim30~\rm{days}$, the only channel for \kb{stellar} mergers before DWD formation is during a CE evolution.
 This channel is similar to the stellar merger channel for He + He DWDs, but due to higher-mass progenitors the CE evolution results in the binary component with a higher mass becoming a CO WD.
@@
 For CO + He DWD progenitor systems with intermediate orbital periods ($1.5\leq \log_{10}(P_{\rm{orb}}/\rm{day})< 2.5$) the mechanisms which impact formation efficiency are complex.
-The dominant way to lose CO + He DWDs is stellar mergers that occur during the second CE phase.
+The dominant way to \kb{\sout{lose} not form} CO + He DWDs is stellar mergers that occur during the second CE phase.
 For lower-metallicity systems, the second CE is successful, while the opposite is true for higher-metallicity systems.
@@
 A subdominant channel of stable He + He DWDs can also occur when a high-metallicity primary overflows it's Roche lobe while still on the GB and thus forms a He WD.
-\snotes{In general, a CO + He binaries fails to form because either a CO + CO or He + He is formed isntead, or a merger occurs before DWD formation.
-We see higher efficiency for FZ than F50 because Co + He binaries prefer to form in log$_{10}$(P$_{\rm{orb}}$/day)$\sim2-4$, which is where the orbital period distribution of FZ peaks.}
+\snotes{In general, a CO + He binary fails to form because either a CO + CO or He + He is formed instead, or a merger occurs before DWD formation.
+We see higher formation efficiencies for FZ than F50 because CO + He DWDs prefer to form in progenitor binaries with orbital periods near $\log_{10}$(P$_{\rm{orb}}$/day)$\sim2-4$, which is where the orbital period distribution of FZ peaks.}
 
@@
 
-\snotes{For our simulations with parameter variations, we see an interplay of the physics of binary evolution with the skews introduced by the metallicity-dependent orbital period distribution/binary fraction.
-We will summarize how the formation efficiency of each DWD type is impacted by the parameter variations.
-Of note in this analysis is that a) the log-normal metallicity-dependent ZAMS orbital period distribution increasingly skews towards orbital periods below $10^4$ days for decreasing metallicity.
-However, b) the log-uniform P$_{\rm{orb}}$ distribution of F50 produces a higher number of the shortest orbital period systems (below $\sim 100$ days) than for FZ as the tails of the FZ distribution fall quickly below this threshold.}
+\snotes{For our simulations with binary evolution parameter variations, we see an interplay of the physics of binary evolution with skews introduced by the metallicity-dependent orbital period distribution and binary fraction.
+Below, we summarize how the formation efficiency of each DWD type is impacted by the parameter variations.
+\kb{Two important features of our FZ and F50 models drive the differences in our binary evolution parameter variations.
+\sout{Of note in this analysis is that a)}}.
+First, the log-normal metallicity-dependent ZAMS orbital period distribution increasingly skews towards orbital periods below $10^4$ days for decreasing metallicity.
+However, \kb{second,} the log-uniform P$_{\rm{orb}}$ distribution of F50 produces a higher number of the shortest orbital period systems (below $\sim 100$ days) than for FZ as the tails of the FZ distribution fall quickly below this threshold.}
 

### 2022-08-25 src/tex/ms.tex
updated some text and modified figures; fig 1 still borked

@@
 This effect lowers the confusion foreground, effectively increasing the sensitivity for detecting all types of low-frequency LISA sources.
-We repeat our analysis for three different assumptions for Roche-lobe overflow interactions and find the population reduction to be robust when a metallicity-dependent binary fraction is assumed.
+\kb{***Need to update this***}We repeat our analysis for three different assumptions for Roche-lobe overflow interactions and find the population reduction to be robust when a metallicity-dependent binary fraction is assumed.
 \end{abstract}
@@
 
-In Section \ref{sec:simulations} we discuss our %binary evolution KB commented out
-assumptions used in simulating DWD populations and detail the process to produce present-day synthetic Milky-Way-like galaxies.
+In Section \ref{sec:simulations} we discuss our assumptions used in simulating DWD populations and detail the process to produce present-day synthetic Milky-Way-like galaxies.
 In Section \ref{sec:LISA_obs} we review the derivation of LISA detectability for circular DWD populations at mHz frequencies.
-In Section \ref{sec:results} we detail results showing how a metallicity-dependent binary fraction affects the formation and evolution of DWD populations assuming \kb{\sout{a fiducial set} four sets of} of binary evolution assumptions.
+In Section \ref{sec:results} we detail results showing how a metallicity-dependent binary fraction affects the formation and evolution of DWD populations assuming \textbf{four sets of} of binary evolution assumptions.
 In Section \ref{sec:LISA_met} we detail the metallicity dependence of the LISA DWD foreground and resolved population.
-Finally, \kb{\sout{we repeat our analysis for three sets of binary evolution assumptions  to show a robust reduction of the size} we consider how a metallicity-dependent close binary fraction impacts the height} of the Galactic DWD foreground in LISA for \kb{\sout{populations simulated with a metallicity-dependent binary fraction} different binary evolution assumptions} in Section \ref{sec:model_compare} and conclude in Section \ref{sec:conclusions}.
+Finally, \textbf{we consider how a metallicity-dependent close binary fraction impacts the height} of the Galactic DWD foreground in LISA for \textbf{different binary evolution assumptions} in Section \ref{sec:model_compare} and conclude in Section \ref{sec:conclusions}.
 
@@
 \subsection{Metallicity-dependent binary fraction}\label{subsec:metbinfrac}
-\snotes{The binary fraction in the Galaxy has been empirically shown to depend on metallicity.
+\textbf{The binary fraction in the Galaxy has been empirically shown to depend on metallicity.
 This is manifested through an explicit dependence of the companion frequency on orbital period \citep{Moe2021}.
@@
 The companion frequency differs from the binary fraction: the companion frequency is the probability of a star having a companion at a given orbital period, and the integration of this probability over all periods results in the binary fraction of the population.
-The metallicity dependence of the companion frequency is observed only } %\kb{\sout{orbital period-dependence of the companion frequency is dependent on metallicity only}}
-\snotes{below P$_{\rm{orb}}=10^6$ days, above which there are not sufficient observational results of binary systems to infer a metallicity dependence.} %\kb{\sout{Below this threshold, we see an increasing skew to shorter periods with decreasing metallicity}}.}
+The metallicity dependence of the companion frequency is observed only below P$_{\rm{orb}}=10^6$ days, above which there are not sufficient observational data of binary systems to infer a metallicity dependence.}
 
@@
 
-\snotes{Figure \ref{fig:binfrac_porb}, shows the companion frequency f$_{\rm{logP}}$ for solar-type stars as a function of the logarithm of orbital period, mirroring the inner binaries curve of Figure 2 in \citet{Moe2021} and scaling to an overall multiplicity frequency of 0.67 (equivalent to an integrated binary fraction of 50\%) at solar metallicity.} To obtain the normalization of the companion frequency for close binaries ($\log_{10}(P_{\rm{orb}}/\rm{day}$), we fit the results presented in \citet{Moe2019} using linear regression to obtain a piecewise relation between the metallicity, [Fe/H] and \snotes{close} binary fraction $f_{\rm{b}}$ as
+\textbf{Figure \ref{fig:met_dep_porb}, shows the companion frequency f$_{\rm{logP}}$ for solar-type stars as a function of the logarithm of orbital period, mirroring the inner binaries curve of Figure 2 in \citet{Moe2021} and scaling to an overall multiplicity frequency of 0.67 (equivalent to an integrated binary fraction of 50\%) at solar metallicity.
+To obtain the normalization of the companion frequency for close binaries ($\log_{10}(P_{\rm{orb}}/\rm{day}<10^4$)),} we fit the results presented in \citet{Moe2019} using linear regression to obtain a piecewise relation between the metallicity, [Fe/H] and \text{close} binary fraction $f_{\rm{b}}$ as
 
@@
 
-\snotes{We count all higher-order companions as secondary, or binary, components.
+\textbf{We count all higher-order companions as secondary, or binary, components.
 We show curves for all 15 of our metallicity bins, increasing in metallicity from darkest to lightest curve colour.
-The lowest metallicity ([Fe/H]=-2.3) shows the highest propensity for short-period binaries, in contrast to higher metallicity systems which have a frequency distribution that has a relatively constant companion frequency \kb{for orbital periods between $10^4$ and $10^6$ days.}}
-%between log$_{10}(\rm{P}_{\rm{orb}}/$day) of four and six.}
+The lowest metallicity ([Fe/H]=-2.3) shows the highest propensity for short-period binaries, in contrast to higher metallicity systems which have a frequency distribution that has a relatively constant companion frequency for orbital periods between $10^4$ and $10^6$ days.}
 
-%\kb{\sout{Note that this fit represents the binary fraction only for close binaries, equivalent to an integration of the companion frequency curve of Figure \ref{fig:binfrac_porb} up to log$_{10}(\rm{P}_{\rm{orb}}/$day)=6.}}
-\snotes{While we simulate binaries across the entire orbital period distribution, the close binary fraction, which exhibits the discussed metallicity dependence, will be that which impacts the LISA population as systems with $\log_{10}(\rm{P}_{\rm{orb}}/$day)$>4$ will be unlikely to evolve enough to enter the LISA band by present day.}
+\textbf{While we simulate binaries across the entire orbital period distribution, the close binary fraction, which exhibits the discussed metallicity dependence, will be that which impacts the LISA population as systems with $\log_{10}(\rm{P}_{\rm{orb}}/$day)$>4$ will be unlikely to evolve enough to enter the LISA band by present day.}
 
@@
 For each DWD type we simulate a grid of $15$ metallicities spaced uniformly in $\log_{10}(Z)$ between $Z=10^{-4}$ to $0.03$, to account for the limits of the \citet{Hurley2000} stellar evolution tracks employed in \cosmic.
-This results in a total of $60$ populations across all DWD types and metallicities \kb{for each set of model assumptions}.
+This results in a total of $60$ populations across all DWD types and metallicities \textbf{for each set of model assumptions}.
 The output of \cosmic\ contains information limited to intrinsic binary properties like mass and orbital period.
@@
 We choose primary masses following \citet{Kroupa2001}, a flat mass ratio distribution \citep{Mazeh1992, Goldberg1994} and a uniform eccentricity distribution following \cite{Geller2019}.
-\snotes{For our simulations which follow a metallicity-dependent binary fraction (model FZ), a skewed log-normal orbital period distribution is sampled in accordance with the metallicity-dependent companion frequency of \citet{Moe2021} \kb{\sout{which will be} as} discussed in Section \ref{subsec:metbinfrac}.}
-%\kb{Binaries are then assigned orbital periods by sampling from this distribution.
-As will be discussed below, when this distribution is integrated it results in the binaries having the binary fraction associated with that metallicity.
-} I cut this since I think it's covered above now!
-%\kb{For all FZ simulations, we only retain the binary systems and discard single stars, but save information regarding how much mass in stars is required to create each population for incorporating a metallicity-dependent star formation history as will be discussed in Section \ref{sec:FIRE}.
-} I also don't think we need this info
-\snotes{For our simulations which assume a constant 50\% binary fraction (model F50), we use a log-uniform period distribution following Opik's Law similar to previous studies \citep[e.g.][]{Nelemans2001a, Toonen2012, Korol2017, Lamberts2019}.
+\textbf{For our simulations which follow a metallicity-dependent binary fraction (model FZ), a skewed log-normal orbital period distribution is sampled in accordance with the metallicity-dependent companion frequency of \citet{Moe2021} as discussed in Section \ref{subsec:metbinfrac}.
+For our simulations which assume a constant 50\% binary fraction (model F50), we use a log-uniform period distribution following Opik's Law similar to previous studies \citep[e.g.][]{Nelemans2001a, Toonen2012, Korol2017, Lamberts2019}.
 We assume a $100\%$ binary fraction in the F50 COSMIC simulations to reduce computation time and scale the simulations to a constant $50\%$ binary fraction in a post-processing scheme.} We initialize all binaries with the same evolution time of $13.7\,\rm{Gyr}$ to capture all potential evolution within a Hubble time.
-\snotes{Although we simulate binaries across the full orbital period distribution, we discard \kb{DWD} binaries \kb{which form} with separations $a\geq 1000$ R$_\odot$ during post-processing, \kb{\sout{to save on computational work}} since these are unlikely to evolve into the LISA band by present day.}
+\textbf{Although we simulate binaries across the full orbital period distribution, we discard DWD binaries which form with separations $a\geq 1000$ R$_\odot$ during post-processing, since these are unlikely to evolve into the LISA band by present day.}
 
-\kb{We consider a fiducial set of assumptions which } follow the \texttt{COSMIC} defaults described in \citet{Breivik2020a} except for the treatment of Roche-lobe overflow (RLO).
+\textbf{We consider a fiducial set of assumptions which} follow the \texttt{COSMIC} defaults described in \citet{Breivik2020a} except for the treatment of Roche-lobe overflow (RLO).
 The stability of RLO mass transfer is determined using critical mass ratios resulting from radius-mass exponents \citep{Webbink1985, Hurley2002}, where the critical mass ratio is defined as the ratio of the donor to accretor mass.
@@
 
-\snotes{The LISA-detectable DWD populations that result from our simulations may vary depending on the assumptions made regarding binary interactions.
+\textbf{The LISA-detectable DWD populations that result from our simulations may vary depending on the assumptions made regarding binary interactions.
 In order to explore the range of results, we complete this study for three binary evolution parameter variations on top of our fiducial set of assumptions.
@@
 In variations $\alpha25$ and $\alpha5$, we modify the common envelope ejection efficiency to be either much less ($\alpha=0.25$) or more ($\alpha=5$) than in our fiducial assumption ($\alpha=1$).
-Larger common envelope ejection efficiencies lead to wider post-CE separations, while smaller ejection efficiencies either lead to closer post-CE separations or \kb{stellar} mergers where the envelope ejection fails.
-\kb{\sout{This will be discussed further later on.}} Between all variations, all other prescriptions for binary evolution remain identical besides the one varied parameter.
+Larger common envelope ejection efficiencies lead to wider post-CE separations, while smaller ejection efficiencies either lead to closer post-CE separations or stellar mergers where the envelope ejection fails.
+Between all variations, all other prescriptions for binary evolution remain identical besides the one varied parameter.
 We delve in depth into the fiducial results in each section, and then give a brief overview of how the results change for each parameter variation.}
@@
 
-The metallicity-dependent \kb{close} binary fraction \snotes{for \kb{\sout{close, }}solar-type binaries (P $< 10^4$ days), or simply the \kb{close} binary fraction from here on,} is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid.
-The binary fraction, $f_{\rm{b}}$, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly.
+The metallicity-dependent \textbf{close} binary fraction \textbf{for solar-type binaries (P $< 10^4$ days), or simply the \kb{close} binary fraction from here on, }% S: Should I change all instances of "binary fraction" to "close binary fraction" then?
+%KB: I will keep an eye out to make the changes
+is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid.
+The \textbf{close} binary fraction, $f_{\rm{b}}$, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly.
 These two opposing trends compete throughout this study along with the impact of metallicity on single star evolution to form the final numerical distribution of systems in our DWD populations.
 
-Since our \cosmic\ simulations assume a binary fraction of $f_{\rm{b}} = 1$ \snotes{for model F50}, we scale the amount of mass sampled at ZAMS required to produce our \cosmic-generated population of DWDs ($M_{\text{b,ZAMS}}$) to the proper amount of mass sampled in single and binary stars ($M_{\text{ZAMS,sim}}$).
+Since our \cosmic\ simulations assume a binary fraction of $f_{\rm{b}} = 1$ \textbf{for model F50}, we scale the amount of mass sampled at ZAMS required to produce our \cosmic-generated population of DWDs ($M_{\text{b,ZAMS}}$) to the proper amount of mass sampled in single and binary stars ($M_{\text{ZAMS,sim}}$).
 We do this by sampling single stars and primary masses of binary stars from the \cite{Kroupa2001} IMF and sampling secondary masses of the binary stars from a uniform mass distribution, where the number of binaries is calculated to ensure $f_{\rm{b}}=0.5$.
@@
 For model F50, the ratio is a constant $R(f_{\rm{b}}) = 0.64$.
-\snotes{The total amount of ZAMS mass in single and binary stars is then $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}} (1 + R(f_{\rm{b}}))$.
-For model FZ, no scaling is done since the \cosmic\ simulations already have the binary fraction incorporated, so $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}}$}.
+\textbf{The total amount of ZAMS mass in single and binary stars is then $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}} (1 + R(f_{\rm{b}}))$.
+For model FZ, no scaling is applied since our \cosmic\ simulations already have the population-wide binary fraction incorporated, and thus $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}}$}.
 
@@
     \caption{The DWD formation efficiency vs metallicity of DWD populations simulated with \cosmic.
-Each panel shows the formation efficiency for a given DWD type.
+Each panel shows the formation efficiency for a given DWD type \snotes{and variation}.
 The solid lines indicate the formation efficiency for model FZ which incorporates a metallicity-dependent binary fraction.
 The dashed lines indicate the formation efficiency for model F50, which assumes a constant binary fraction of $50\%$.
-The DWD formation efficiency drops by a factor of $4-5$ for model FZ and a factor of 2-5 for model F50.
+The DWD formation efficiency drops by a factor of $4-5$ for model FZ and a factor of \snotes{\sout{2-5} 1-5} for model F50.
 See Section~\ref{sec:formeff} for a careful description of the trends for each DWD type.}
@@
 CO DWDs thus have a distribution in progenitor separation that extends to larger values than for other DWD types.
-Most \kb{CO + CO} DWDs need $> 0.3$ Gyr to form\kb{\sout{.
-These systems},} have component WD masses between $0.35$--$1.0\,M_\odot$, and make up the majority of the DWD population.
+Most \textbf{CO + CO} DWDs need $> 0.3$ Gyr to form, have component WD masses between $0.35$--$1.0\,M_\odot$, and make up the majority of the DWD population.
 
@@
 Because an ONe WD can have a companion of any other WD type in our study, there is a spread in their distributions for separation, secondary mass, final orbital period, and formation time.
-In general, however, these systems result from wider separations to allow for the evolution of the ONe component without merging\kb{\sout{, e.g.}.
-For example,} all initial separations in our \cosmic \ populations have separations $\gtrsim 1.5\,R_\odot$.
+In general, however, these systems result from wider separations to allow for the evolution of the ONe component without merging.
+\textbf{For example,} all initial separations in our \cosmic \ populations have separations $\gtrsim 1.5\,R_\odot$.
 ONe + X DWDs can form on short timescales, as low as $30\,\rm{Myr}$, for the majority of high-metallicity systems.
@@
 Consequently, a metallicity-dependent binary fraction further impacts the efficiency of DWD formation within the Galaxy.
-Figure \ref{fig:form_eff} shows the DWD formation efficiency as a function of metallicity for each DWD type\snotes{,\sout{ and for each of our}} binary fraction models\snotes{, and binary evolution parameter variations}.
+Figure \ref{fig:form_eff} shows the DWD formation efficiency as a function of metallicity for each DWD type\textbf{, binary fraction models, and binary evolution parameter variations}.
 In general, the formation efficiency decreases with increasing metallicity.
-This effect is exaggerated for model FZ which assumes a \kb{close} binary fraction which also decreases with increasing metallicity.
-\kb{In the following sub-sections, we describe the formation efficiency trends for our fiducial model in detail and then describe the changes arising from each binary evolution parameter variation.}
+This effect is exaggerated for model FZ which assumes a \textbf{close} binary fraction which also decreases with increasing metallicity.
+\textbf{In the following sub-sections, we describe the formation efficiency trends for our fiducial model in detail and then describe the changes arising from each binary evolution parameter variation.}
 
-\subsubsection{\snotes{Fiducial formation efficiency trends}}\label{sec:formeff_fid}
+\subsubsection{\textbf{Fiducial formation efficiency trends}}\label{sec:formeff_fid}
 
 For He + He DWDs, the sudden drop in formation efficiency near $\log(Z/Z_{\odot})=-1.0$, is generally caused by the timescale for which the initially more massive star in the DWD progenitor overflows it's Roche lobe.
-At lower metallicities, donors tend to fill their Roche lobes while they are still on the main sequence and the mass transfer remains stable \snotes{and serves to widen the binary}.
+At lower metallicities, donors tend to fill their Roche lobes while they are still on the main sequence and the mass transfer remains stable \textbf{and serves to widen the binary}.
 This is because, in our \cosmic\ models lower metallicity stars evolve faster than high-metallicity stars and have larger radii near the end of the MS.
@@
 The ZAMS orbital period leads to different specific evolutionary channels.
-For short-period systems with periods below $10~\rm{days}$, \kb{\sout{this} and common envelope} leads to a stellar merger due to insufficient orbital energy to eject the envelope.
+For short-period systems with periods below $10~\rm{days}$, \textbf{and common envelope} leads to a stellar merger due to insufficient orbital energy to eject the envelope.
 Stellar mergers continue to dominate the evolutionary pathways of systems with intermediate orbital periods ($1 < \log_{10}(P_{\rm{orb}}/\rm{day}) < 2.5$).
@@
 	\includegraphics[width=\textwidth]{figures/CEsep.pdf}
-    \caption{Average interaction separation, $\overline{\mathrm{a}}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type from model FZ.
+    \caption{Average interaction separation, $\overline{\mathrm{a}}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type \snotes{and variation} from model FZ.
 Solid lines show the average separation at the first RLO for binaries in each metallicity bin.
 The shaded regions show the $1\sigma$ spread around the mean within each metallicity bin.
-The average interaction separation increases with metallicity for every DWD type.
+The average interaction separation increases with metallicity for every DWD type\snotes{, except for $\alpha5$ which remains approximately constant for CO + He and ONe + X}.
 The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts.
-The sharp drop of the CO + CO average at the highest-metallicity bin is due to binning effects of the figure: it only contains 115 systems, of which the majority stem from a single low-separation system which was sampled 94 times times during the simulation.}
+The sharp drop of the CO + CO average at the highest-metallicity bin \snotes{of the fiducial simulation} is due to binning effects of the figure: it only contains 115 systems, of which the majority stem from a single low-separation system which was sampled 94 times times during the simulation.}
     \label{fig:CEsep}
@@
 For CO + He DWD progenitor systems with intermediate orbital periods ($1.5\leq \log_{10}(P_{\rm{orb}}/\rm{day})< 2.5$) the mechanisms which impact formation efficiency are complex.
-The dominant way to \kb{\sout{lose} not form} CO + He DWDs is stellar mergers that occur during the second CE phase.
+The dominant way to % R: lose
+\textbf{not form} CO + He DWDs is stellar mergers that occur during the second CE phase.
 For lower-metallicity systems, the second CE is successful, while the opposite is true for higher-metallicity systems.
@@
 A subdominant channel of stable He + He DWDs can also occur when a high-metallicity primary overflows it's Roche lobe while still on the GB and thus forms a He WD.
-\snotes{In general, a CO + He binary fails to form because either a CO + CO or He + He is formed instead, or a merger occurs before DWD formation.
+\textbf{In general, a CO + He binary fails to form because either a CO + CO or He + He is formed instead, or a merger occurs before DWD formation.
 We see higher formation efficiencies for FZ than F50 because CO + He DWDs prefer to form in progenitor binaries with orbital periods near $\log_{10}$(P$_{\rm{orb}}$/day)$\sim2-4$, which is where the orbital period distribution of FZ peaks.}
@@
 
-\subsubsection{\snotes{Parameter variations formation efficiency trends}}\label{subsec:formeff_vars}
+\subsubsection{\textbf{Parameter variations formation efficiency trends}}\label{subsec:formeff_vars}
 
-\snotes{For our simulations with binary evolution parameter variations, we see an interplay of the physics of binary evolution with skews introduced by the metallicity-dependent orbital period distribution and binary fraction.
+\textbf{For our simulations with binary evolution parameter variations, we see an interplay of the physics of binary evolution with skews introduced by the metallicity-dependent orbital period distribution and binary fraction.
 Below, we summarize how the formation efficiency of each DWD type is impacted by the parameter variations.
-\kb{Two important features of our FZ and F50 models drive the differences in our binary evolution parameter variations.
-\sout{Of note in this analysis is that a)}}.
+Two important features of our FZ and F50 models drive the differences in our binary evolution parameter variations.
 First, the log-normal metallicity-dependent ZAMS orbital period distribution increasingly skews towards orbital periods below $10^4$ days for decreasing metallicity.
-However, \kb{second,} the log-uniform P$_{\rm{orb}}$ distribution of F50 produces a higher number of the shortest orbital period systems (below $\sim 100$ days) than for FZ as the tails of the FZ distribution fall quickly below this threshold.}
+However, second, the log-uniform P$_{\rm{orb}}$ distribution of F50 produces a higher number of the shortest orbital period systems (below $\sim 100$ days) than for FZ as the tails of the FZ distribution fall quickly below this threshold.}
 
-\snotes{For binary systems leading to He + He DWDs, there are many more mergers for $\alpha25$ than for the fiducial simulations.
-The lower CE efficiency entails mergers from the binary failing to eject the CE, or shrinking the orbit such that it then merges on the second CE phase.
-Because, as discussed above, there are more very short-period binaries in F50, as the ZAMS binary population evolves there are more likely to be binary interactions in the population for F50 than FZ.
-This leads to more mergers in $\alpha25$ occurring for F50 before formation of the DWD and thus a lower formation efficiency overall for F50 in contrast to FZ, as we see in the $\alpha25$ He + He plot of Figure \ref{fig:form_eff}.
-Similarly to the fiducial, a binary that becomes a He + He DWD at lower metallicities would merge before becoming one at higher metallicities because of the longer evolution timescales.
+\snotes{For binary systems leading to He + He DWDs, there are many more mergers for $\alpha25$ than for the fiducial \kb{model}.
+The lower CE efficiency \kb{\sout{entails} leads to DWD progenitor} mergers from \kb{failed CE ejection \sout{the binary failing to eject the CE}}, or \kb{the CE} shrinking the orbit such that it then merges on the second CE phase.
+Because\kb{\sout{, as discussed above,}} there are more \kb{\sout{very short-period} ZAMS binaries with orbital periods shorter than $10^4$ days} in F50, as the \kb{\sout{ZAMS binary}} population evolves there are more likely to be binary interactions in the population for F50 than FZ.
+This leads to more mergers in $\alpha25$ occurring for F50 before formation of the DWD and thus a lower formation efficiency overall for F50 in contrast to FZ.
+\kb{\sout{as we see} This is illustrated} in the $\alpha25$ He + He plot of Figure \ref{fig:form_eff}.
+Similar to the fiducial \kb{model}, a binary that becomes a He + He DWD at lower metallicities would merge before becoming one at higher metallicities because of the longer evolution timescales.
 These later interactions lead to closer post-CE separations and thus more mergers.
-The dip at [Fe/H]=$\sim -1.5\%$ stems from mergers before the DWD forms, similar to for our fiducial model.
-The  peak that occurs in $\alpha25$ at $\sim 10\%$ Z$_\odot$ arises from binaries evolving faster (i.e.
-interacting earlier) as metallicity increases, meaning that equivalent binaries that would have merged or formed a CO + He DWD instead at lower metallicities now survive into an He + He.
-At higher metallicities, there are a higher proportion of wide-separation systems, which evolve off the Main Sequence too slowly to form a He + He DWD, causing the efficiency drop.
-For $\alpha5$, there are significantly fewer mergers, as expected since binaries are more likely to survive a CE phase from the higher CE efficiency.
-Systems that would normally merge for $\alpha25$ now survive, and are shrunk to short orbits through CE interactions to evolve in the LISA band.
-The number of DWDs thus makes up a higher fraction of the total simulated binary population overall, thus we see in general higher formation efficiencies than for our fiducial simulations (which has $\alpha=1$), and even higher than for our variation with $\alpha=0.25$.
-Beyond this, the efficiency drop across metallicity is similar to the fiducial in that it depends on the metallicity-dependent ZAMS orbital period distribution emphasizing short-period systems at low metallicities, and in the change of formation channel for different period ranges across metallicity.
-We see the highest formation efficiency for variation $q3$.
+The dip at [Fe/H]=$\sim -1.5\%$ stems from mergers before the DWD forms, \kb{again} similar to \kb{sout{for our}the } fiducial model.
+The peak that occurs in $\alpha25$ at $\sim 10\%$ Z$_\odot$ arises from binaries evolving faster \kb{\sout{(i.e.} and thus}} interacting earlier as metallicity increases.
+\kb{This means \sout{meaning}} that equivalent binaries that would have merged or formed a CO + He DWD instead at lower metallicities now survive \kb{\sout{into} to produce} a He + He \kb{DWD}.
+At higher metallicities, there are a higher proportion of wide\kb{\sout{-separation systems} ZMAS binaries}, which evolve off the Main Sequence too slowly to form a He + He DWD, causing the efficiency drop.
+
+\snotes{For $\alpha5$, there are significantly fewer \kb{DWD progenitor} mergers, \kb{\sout{as expected}} since binaries are more likely to survive a CE phase \kb{\sout{from} due to} the higher CE \kb{ejection} efficiency.
+Systems that would normally merge for $\alpha25$ \kb{\sout{now} instead} survive, and are shrunk to short orbits through CE interactions to \kb{\sout{evolve} reside} in the LISA band \kb{at present}.
+The number of DWDs thus makes up a higher fraction of the total simulated binary population \kb{\sout{overall}}, thus we see \kb{\sout{in general}} higher formation efficiencies than for \kb{\sout{our} the} fiducial \kb{\sout{simulations} model} (\kb{\sout{which has }}$\alpha=1$).
+\kb{\sout{, and even higher than for our} This effect is even more pronouced in comparison with the $\alpha25$} variation \kb{\sout{with} which sets} $\alpha=0.25$.
+}
+
+\snotes{Beyond \kb{\sout{this} the effects described above}, the efficiency drop across metallicity is similar to the fiducial \kb{model} in that it depends on the metallicity-dependent ZAMS orbital period distribution emphasizing short-period systems at low metallicities, and in the change of formation channel for different period ranges across metallicity.
+We \kb{\sout{see} find} the highest formation efficiency for variation $q3$.
 Only the shortest-period binaries do not form a DWD through mergers at higher metallicities.
-At low metallicities, we see that even binaries with very close ZAMS separations form He + He DWDs.
-We thus see a higher efficiency from F50 over FZ because of the higher number of shortest-period ZAMS binaries in the log-uniform distribution of F50.}
+At low metallicities, \kb{\sout{we see that}} even binaries with \kb{\sout{very close}} ZAMS separations \kb{less than XX} form He + He DWDs.
+\kb{\sout{We}} Thus \kb{\sout{see} this leads to} a higher \kb{formation} efficiency from F50 over FZ for parameter variation $q3$ because of the higher number of shortest-period ZAMS binaries in the log-uniform distribution of F50.}
 
-\snotes{For CO + He binaries, there are again many more mergers for $\alpha25$ relative to the fiducial case.
-This is the dominating way that binaries are lost at higher metallicities.
-At low metallicities we also see a number of systems form CO + CO binaries instead -- this is especially the case in a ``Goldilocks zone" around log$_{10}$(Z/Z$_\odot$)sim -2, where RLOF occurs late enough in evolution that mass transfer remains stable and CO + CO's are formed, hence why we see a dip in the formation efficiency.
-Because $\alpha5$ allows for less mergers due to the high CE efficiency, the formation efficiency is mostly governed by our metallicity-dependent orbital period distribution.
-At higher metallicities the majority of lost systems from mergers or from forming He + He binaries instead due to the faster evolution at high metallicities and increasing radii allowing for earlier interactions and hence stripping of both star's envelopes [$\leftarrow$ is this correct logic?].
-At higher metallicities, we also have the ZAMS orbital period distribution of FZ drops below the flat distribution for F50 and extends out to orbital periods beyond what would form a CO + He, thus the formation efficiencies for FZ and F50 cross at log$_{10}$(Z/Z$_\odot$)$\sim-0.5$.}
+\snotes{For CO + He binaries, there are again many more mergers for \kb{parameter variation} $\alpha25$ relative to the fiducial case.
+This is the \kb{\sout{dominating} dominant} way that \kb{progenitors do not evolve to produce DWDs \sout{binaries are lost}} at higher metallicities.
+At low metallicities \kb{\sout{we also see}} a number of \kb{\sout{systems} progenitor binaries} form CO + CO \kb{\sout{binaries} DWDs instead of He + CO DWDs}.
+\kb{\sout{-- t}T}his is especially the case in a ``Goldilocks zone" around log$_{10}$(Z/Z$_\odot$)sim -2, where RLO occurs late enough in \kb{a binary's} evolution that mass transfer remains stable and CO + CO's are formed rather than CO + He, hence \kb{\sout{why we see} producing} a dip in the formation efficiency.
+Because \kb{parameter variation} $\alpha5$ \kb{\sout{entails leads to}} less mergers due to the high CE efficiency, the formation efficiency is mostly governed by the metallicity-dependent ZAMS orbital period distribution.
+At higher metallicities the majority of \kb{\sout{lost systems} cases in model FZ where progenitors don't produce a CO + He DWD} are due to \kb{progenitor} mergers or to He + He \kb{\sout{binaries} DWDs} forming instead \kb{CO + He DWDs.} %due to the faster evolution at high metallicities and increasing radii inducing earlier binary interactions and hence stripping of both star's envelopes [$\leftarrow$ is this correct logic?].
+I think this is already discussed above for fiducial so we don't need to worry about it.
+At higher metallicities, the ZAMS orbital period distribution of FZ also drops below the \kb{orbital period} distribution \kb{\sout{for} of} F50 and extends out to orbital periods beyond what would form a CO + He.
+\kb{This causes \sout{ which is why}} the formation efficiencies for FZ and F50 \kb{to} cross at log$_{10}$(Z/Z$_\odot$)$\sim-0.5$.
+\kb{This is also apparent \sout{which we also see}} for the $q3$ variation, and to a lesser extent in the fiducial \kb{\sout{variation} case}.} %Any lost systems in $q3$ also is contributed to by: (i) some binaries at high metallicities not forming a CO + He DWD by present day due to envelope-stripping timescales being delayed by phases of stable mass transfer, (ii) mergers, and (ii) ONe + X DWDs forming instead.
+\snotes{In $q3$, for any given orbital period we find that lower mass systems come from lower metallicities, which leads to an approximately constant formation efficiency.}
 
-\snotes{** still need to do q3 **, and all for CO + CO and ONe + X}
+\snotes{For CO + CO, across all variations, very close \kb{ZAMS} binaries (P$_{\rm{orb}} \mathcal{O}(100$ days)) are lost at high metallicities when a binary that would form a CO + CO at low metallicities forms a CO + He or He + He DWD instead because the binary interacts before core Helium burning of one or both components.
+There are again many more mergers in $\alpha25$, and less mergers for $\alpha5$.
+Due to the high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods survive to become CO + CO DWDs rather than merging or becoming CO/He + He DWDs.
+There are many less mergers overall for $q3$ than all the $\alpha$ values because of the phase of stable mass transfer occurring before the CE phase rather than multiple CE phases, hence why the $q3$ efficiency is approximately constant across metallicity.}
+\kb{**I think maybe another thing to point out is that the majority of CO + CO don't interact }
+
+\snotes{[** Might need to fact check this paragraph **] The FZ curves for ONe + X are relatively similar amongst variations beyond height, and the loss of systems is the same as described for the fiducial simulation.
+We have more mergers once again for $\alpha25$, which lowers the F50 curve below FZ because F50 has the shortest-ZAMS-period end that FZ does not have.
+$\alpha5$ and $q3$ show F50 efficiencies with a very shallow slope due to the flat orbital period distribution, as well as due to less mergers overall.}
 
@@
     \caption{The number of LISA-band systems formed for each DWD type as a function of the base-10 logarithm of metallicity, normalized to solar value.
-The solid line shows the FZ population with a metallicity-dependent binary fraction incorporated, and the dashed line shows the F50 population for a standard binary fraction of 0.5.
+The solid line shows the FZ population with a metallicity-dependent \snotes{close} binary fraction incorporated, and the dashed line shows the F50 population for a standard binary fraction of 0.5.
 The LISA population of DWDs is dominated by stars with super-solar metallicities.
 This is true even for model FZ, which drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond Z$\simeq$Z$_\odot$.
-There is a double peak in the He + He population; the first peak is caused by the sharp drop in formation efficiency past Z$\simeq$0.1$Z_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
+There is a double peak in the \snotes{fiducial and $\alpha25$ }He + He population\snotes{s}; the first peak is caused by the sharp drop in formation efficiency past Z$\simeq$0.1$Z_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
     \label{fig:lisa_nums}
@@
 	\includegraphics[width=\textwidth]{figures/Mc_vs_dist_fiducial.pdf}
-    \caption{The chirp mass vs distance for each DWD type is shown.
+    \caption{The chirp mass vs distance for each DWD type is shown\snotes{ for our fiducial simulation}.
 Only systems with observable evolution in their GW frequency, i.e those which are chirping, and with SNR $>7$, are shown, since these are systems for which distance can be separated from chirp mass within their strain amplitude.
@@
 
-We note that \snotes{\sout{while} for all our simulation results, any changes in} the height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ \snotes{Strikeout: [\emph{is reduced by a factor of 2 for model FZ relative to model F50, the number of resolved sources is not reduced to an equal degree.}] between F50 and FZ does not necessarily reflect how the number of individually resolvable systems is impacted.
-For the fiducial model and $\alpha25$ variation, the number of resolvable systems with SNR $>7$ do not change much (are reduced by 7\% and increased by 6\% respectively).
-However, $\alpha5$ sees a reduction in the number of resolvable systems by only 14\%, and $q3$ sees an \emph{increase} by 23\%.
-A large portion of the increase of $q3$ is contributed to by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).
-[Not really sure what to say about the alpha5 reduction?]} %The metallicity-dependent ZAMS orbital period distribution of Figure \ref{fig:binfrac_porb} also has a wide-binary tail that extents more than an order of magnitude longer than the log-uniform distribution of F50 -- there are thus more wide binaries created in the FZ simulations than F50.
-Many of these may not make it to the LISA band by present day, but }
-\snotes{Strikeout: [\emph{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.
-Between models FZ and F50, the number of resolvable systems with SNR $>7$ over all DWD types decreases by only $\sim14\%$.}]}
+We note that the height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 2 for model FZ relative to model F50\snotes{ for variations $\alpha5$ and $q3$}, the number of resolved sources is not reduced to an equal degree.
+\snotes{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.
+For the fiducial model and $\alpha25$ variation, the number of resolvable systems with SNR $>7$ do not change much (are reduced by 4.5\% and increased by 3\% respectively).
+However, $\alpha5$ sees a reduction in the number of resolvable systems by only 26\%, and $q3$ remains almost \emph{unchanged}, seeing a 1\% reduction, even though the overall LISA population of both variations is halved.
+A large portion of the maintenance of $q3$ is contributed to by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).} \snotes{[\emph{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.}][$\leftarrow$ moved to beginning of paragraph] Strikeout: [\emph{Between models FZ and F50, the number of resolvable systems with SNR $>7$ over all DWD types decreases by only $\sim14\%$.}]}
 
@@
 Assuming a chirp resolution of $1/T_{\rm{obs}}^2 \sim 8\times10^{-9}\,\rm{Hz}^2$, we select the DWDs whose chirp masses and distances can be measured.
-Figure \ref{fig:Mc_vs_dist} shows the chirp mass vs the luminosity distance for each DWD type \snotes{and variation} in this selected population.
+Figure \ref{fig:Mc_vs_dist} shows the chirp mass vs the luminosity distance for each DWD type in this selected population \snotes{for the fiducial simulation.
+The same figure for our three variations is shown in Appendix \ref{appendix:Mc_dist_vars}}.
 The contours show the $5^{\rm{th}}$, $25^{\rm{th}}$, $50^{\rm{th}}$, $75^{\rm{th}}$, and $95^{\rm{th}}$ percentiles for models FZ (light blue) and F50 (dark blue, dashed).
 Despite the reduction in the height of the confusion foreground when considering model FZ relative to F50, we find that LISA is unable to differentiate between the chirp mass -- distance distributions of the two models.
-\snotes{Minor observed differences -- e.g.
-slightly changed contour shapes in He + He $\alpha25$ or ONe + X $q3$ -- are artifacts caused by low statistics since there are so few binaries in this selected population.
+\snotes{For $\alpha25$ we plot these as scatter plots for He + He and ONe + X due to low statistics since there are so few binaries in this selected population.
 The only population with a significant change between models is for ONe + X's $\alpha5$ distributions, where we see a skew to lower masses.
-This is because a higher fraction of the binaries are ONe + He (in which Helium WDs tend to have smaller masses) for FZ than F50 -- a Helium companion makes up 10\% of this selected population for F50 compared with 42\% for FZ.
+This is because a higher fraction of the binaries are ONe + He (in which Helium WDs tend to have smaller masses) for FZ than F50 -- a Helium companion makes up 10\% of this selected population for F50 compared with 44\% for FZ.
 Furthermore, $\sim8$\% of the F50 measurable systems are ONe + ONe binaries, versus 0\% for FZ.
-Because ONe have larger masses, this also creates the high-mass concentration we see in the F50 contours.}
+Because ONe WDs have larger masses, this also creates the high-mass concentration we see in the F50 contours.}
 
-\section{Binary evolution \textbf{parameter variations} \snotes{discussion}}
+\section{\snotes{\sout{Binary evolution \textbf{parameter variations}} Galactic DWD Confusion Foreground Discussion}}
 \label{sec:model_compare}
@@
 The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for model FZ to model F50 vs to number of DWDs orbiting in the LISA band for model F50 only.
-While both the height of the confusion foreground and number of LISA DWDs changes for each variation, the FZ models within each variation exhibit a constant reduction by a factor of two compared with the F50 models.}
+While both the height of the confusion foreground and number of LISA DWDs changes for each variation, the FZ models within each variation exhibit \snotes{either no change or }a constant reduction by a factor of two compared with the F50 models.}
     \label{fig:model_comp}
@@
 This is because there are fewer stellar mergers which occur before the formation of a DWD, thus allowing more systems to evolve due to GW emission and orbit in the LISA frequency band at present.
-Conversely, for variation $\alpha0.25$, we find that the number of DWDs orbiting with frequencies in the LISA band is drastically reduced.
+Conversely, for variation $\alpha25$, we find that the number of DWDs orbiting with frequencies in the LISA band is drastically reduced.
 This is because of the highly inefficient use of orbital energy to eject the common envelope, thus producing more stellar mergers, or closer binaries which are more prone to future mergers.
@@
 \snotes{\sout{Even though} The} number of DWDs in the LISA band spans over two orders of magnitude, \snotes{and} the ratio of FZ to F50, as well as the spectral shape of the confusion fit, \snotes{\sout{stays fixed at a constant factor of two reduction} is either relatively unchanged or reduced by a factor of approximately two}.
-This suggests that assuming a metallicity-dependent binary fraction \snotes{\sout{reduces} may change} the size of the Galactic close DWD population by a factor of $\sim$ two and the strength of the Galactic DWD GW foreground for LISA \snotes{\sout{\emph{regardless of the chosen binary evolution model}} depending on the chosen binary evolution model.}
+This suggests that assuming a metallicity-dependent binary fraction \snotes{\sout{reduces} may change} the size of the Galactic close DWD population by a factor of $\sim$two and the strength of the Galactic DWD GW foreground for LISA \snotes{\sout{\emph{regardless of the chosen binary evolution model}} depending on the chosen binary evolution model.}
 
@@
 While our binary evolution \textbf{parameter variations} change the size of the LISA-observable populations dramatically, the reduction in the size of the close Galactic DWD population and the height of the confusion foreground for models which assume a metallicity-dependent binary fraction is robust.}]$\leftarrow$[moved/edited into above paragraph]} An important consequence of a lower Galactic DWD confusion foreground is that relative to the total DWD population, more DWDs can be individually resolved because of the reduction in competing GW signals.
-While the number of DWDs radiating GWs in the LISA frequency band is reduced by a factor of two for model FZ relative to model F50 \snotes{for variations $\alpha25$ and $q3$}, the number of resolved sources is less affected with a population-wide reduction of $14\%$ \snotes{for the former, and surprisingly an increase by 23\% for the latter}.
+While the number of DWDs radiating GWs in the LISA frequency band is reduced by a factor of two for model FZ relative to model F50 \snotes{for variations $\alpha25$ and $q3$}, the number of resolved sources is less affected with a population-wide reduction of $26\%$ \snotes{for the former, and surprisingly only by 1\% for the latter}.
 These results are far-reaching since the strength of the Galactic DWD confusion foreground has direct consequences on the detectability of all other LISA sources with small SNRs.
@@
 
+\section{Chirp Mass -- Distance Distributions for Binary Evolution Parameter Variations}\label{appendix:Mc_dist_vars}
 \begin{figure*}[h]

### 2022-08-25 src/scripts/LISA_SNR.py

@@ -106,7 +106,7 @@ def plot_LISAcurves(var, model, label, ii):
         ax[ii, i].set_yscale('log')
         ax[ii, i].set_xscale('log')
         ax[ii, i].tick_params(labelsize=20)
-        if ii == 0:
+        if ii == 1:
             ax[ii, i].set_xlabel(r'f$_{\rm{GW}}$ [Hz]', size=24)
         ax[ii, i].set_ylim(top=5e-16)
     ax[ii, 0].set_ylabel(r'ASD [Hz$^{-1/2}$]', size=24)

### 2022-08-25 src/scripts/met_dep_porb.py

@@ -140,9 +140,10 @@ for norm_wide, norm_close, Z, FeH, color in zip(norm_wide_list, norm_close_list,
     else:
         plt.plot(x_dat, y_dat, c=color)
 
-plt.legend(ncol=2, loc=[0, 1.01], frameon=False, prop={'size':12})
-plt.xlabel(r'log$_{10}(P_{\rm{orb}}/day)$', size=15)
-plt.ylabel(r'$f_{\rm{logP}}$', size=15)
+plt.legend(ncol=2, loc=[0, 1.01], frameon=False)
+plt.tick_params(labelsize=15)
+plt.xlabel(r'log$_{10}(P_{\rm{orb}}/day)$', size=18)
+plt.ylabel(r'$f_{\rm{logP}}$', size=18)
 plt.xlim(0, 8.5)
 plt.ylim(0, 0.23)
 plt.tight_layout()

### 2022-08-30 src/tex/ms.tex
changed up text and switched around order of parameter variations in figures

@@
 \kb{This means \sout{meaning}} that equivalent binaries that would have merged or formed a CO + He DWD instead at lower metallicities now survive \kb{\sout{into} to produce} a He + He \kb{DWD}.
-At higher metallicities, there are a higher proportion of wide\kb{\sout{-separation systems} ZMAS binaries}, which evolve off the Main Sequence too slowly to form a He + He DWD, causing the efficiency drop.
+At higher metallicities, there are a higher proportion of wide\kb{\sout{-separation systems} ZAMS binaries}, which evolve off the Main Sequence too slowly to form a He + He DWD, causing the efficiency drop.
 
@@
 At low metallicities \kb{\sout{we also see}} a number of \kb{\sout{systems} progenitor binaries} form CO + CO \kb{\sout{binaries} DWDs instead of He + CO DWDs}.
-\kb{\sout{-- t}T}his is especially the case in a ``Goldilocks zone" around log$_{10}$(Z/Z$_\odot$)sim -2, where RLO occurs late enough in \kb{a binary's} evolution that mass transfer remains stable and CO + CO's are formed rather than CO + He, hence \kb{\sout{why we see} producing} a dip in the formation efficiency.
+\kb{\sout{-- t}T}his is especially the case in \kb{\sout{a ``Goldilocks zone" around} near} log$_{10}$(Z/Z$_\odot)\sim -2$, where RLO occurs late enough in \kb{a binary's} evolution that mass transfer remains stable and CO + CO's are formed rather than CO + He, hence \kb{\sout{why we see} producing} a dip in the formation efficiency.
 Because \kb{parameter variation} $\alpha5$ \kb{\sout{entails leads to}} less mergers due to the high CE efficiency, the formation efficiency is mostly governed by the metallicity-dependent ZAMS orbital period distribution.
-At higher metallicities the majority of \kb{\sout{lost systems} cases in model FZ where progenitors don't produce a CO + He DWD} are due to \kb{progenitor} mergers or to He + He \kb{\sout{binaries} DWDs} forming instead \kb{CO + He DWDs.} %due to the faster evolution at high metallicities and increasing radii inducing earlier binary interactions and hence stripping of both star's envelopes [$\leftarrow$ is this correct logic?].
+At higher metallicities the majority of \kb{\sout{lost systems} cases in model FZ where progenitors don't produce a CO + He DWD} are due to \kb{progenitor} mergers or to He + He \kb{\sout{binaries} DWDs} forming instead \kb{CO + He DWDs.}} %due to the faster evolution at high metallicities and increasing radii inducing earlier binary interactions and hence stripping of both star's envelopes [$\leftarrow$ is this correct logic?].
 I think this is already discussed above for fiducial so we don't need to worry about it.
-At higher metallicities, the ZAMS orbital period distribution of FZ also drops below the \kb{orbital period} distribution \kb{\sout{for} of} F50 and extends out to orbital periods beyond what would form a CO + He.
+\snotes{At higher metallicities, the ZAMS orbital period distribution of FZ also drops below the \kb{orbital period} distribution \kb{\sout{for} of} F50 and extends out to orbital periods beyond what would form a CO + He.
 \kb{This causes \sout{ which is why}} the formation efficiencies for FZ and F50 \kb{to} cross at log$_{10}$(Z/Z$_\odot$)$\sim-0.5$.
 \kb{This is also apparent \sout{which we also see}} for the $q3$ variation, and to a lesser extent in the fiducial \kb{\sout{variation} case}.} %Any lost systems in $q3$ also is contributed to by: (i) some binaries at high metallicities not forming a CO + He DWD by present day due to envelope-stripping timescales being delayed by phases of stable mass transfer, (ii) mergers, and (ii) ONe + X DWDs forming instead.
-\snotes{In $q3$, for any given orbital period we find that lower mass systems come from lower metallicities, which leads to an approximately constant formation efficiency.}
+\snotes{In $q3$, for any given orbital period we find that lower mass \kb{\sout{systems} DWDs originate \sout{come}} from lower metallicities,\kb{\sout{which leads} thus leading} to an approximately constant formation efficiency.}
 
-\snotes{For CO + CO, across all variations, very close \kb{ZAMS} binaries (P$_{\rm{orb}} \mathcal{O}(100$ days)) are lost at high metallicities when a binary that would form a CO + CO at low metallicities forms a CO + He or He + He DWD instead because the binary interacts before core Helium burning of one or both components.
-There are again many more mergers in $\alpha25$, and less mergers for $\alpha5$.
-Due to the high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods survive to become CO + CO DWDs rather than merging or becoming CO/He + He DWDs.
-There are many less mergers overall for $q3$ than all the $\alpha$ values because of the phase of stable mass transfer occurring before the CE phase rather than multiple CE phases, hence why the $q3$ efficiency is approximately constant across metallicity.}
-\kb{**I think maybe another thing to point out is that the majority of CO + CO don't interact }
+\snotes{For CO + CO, across all variations, very close \kb{ZAMS} binaries (P$_{\rm{orb}} \mathcal{O}(100$ days)) at high metallicities} \kb{form a CO + He or He + He DWD instead of a CO + CO because the binary interacts before core Helium burning of one or both components.
+}
+%lost at high metallicities when a binary that would form a CO + CO at low metallicities forms a CO + He or He + He DWD instead 
+There are again many more mergers in $\alpha25$, and \kb{\sout{less} fewer} mergers for $\alpha5$.
+Due to the high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods survive to become CO + CO DWDs rather than merging or becoming CO + He or He + He DWDs.
+There are \kb{\sout{less} fewer} mergers overall for $q3$ than all the $\alpha$ \kb{\sout{values} variations} because \kb{\sout{of the phase of stable mass transfer occurring before the CE phase} the first RLO occurrence leads to stable mass transfer from the primary to the secondary} rather than multiple CE phases.
+\kb{For both the $\alpha5$ and $q3$ variations, the majority of CO + CO DWDs originate in wide enough orbits that they don't interact before DWD formation.
+This leads to an approximately constant formation efficiency across metllicity in both cases.}
 
-\snotes{[** Might need to fact check this paragraph **] The FZ curves for ONe + X are relatively similar amongst variations beyond height, and the loss of systems is the same as described for the fiducial simulation.
+%\kb{This also leads to \kb\souce{hence why} \kb{an approximately constant formation efficiency} $q3$ \sout{efficiency}\kb{parameter variation} is approximately constant across metallicity.}
+%\kb{**I think maybe another thing to point out is that the majority of CO + CO don't interact }
+
+\kb{For model FZ, the ONe + X formation efficiencies follow similar trends aross each parameter variation.
+Their formation scenarios are similar to those described above for the fiducial binary evolution parameter set.
+The main difference between each parameter variation is only in the number of sources produced since the number of stellar mergers that occur before DWD formation increases with decreasing common envelope efficiency.
+In model F50, the formation efficiency is decreased significantly for parameter variation $\alpha25$ because the log-uniform orbital period distribution produces many ZAMS binaries with very short orbital periods which lead to stellar mergers during the CE phases.}
+
+% Reworked this into the paragraph above.
+%\snotes{[** Might need to fact check this paragraph **] The FZ curves for ONe + X are relatively similar amongst variations beyond height, and the loss of systems is the same as described for the fiducial simulation.
 We have more mergers once again for $\alpha25$, which lowers the F50 curve below FZ because F50 has the shortest-ZAMS-period end that FZ does not have.
@@
 The solid lines denote the average value, and the $1\sigma$ variance is shown in the surrounding shading.
-\snotes{We show this for our fiducial model and two of the binary parameter variations.
-For our fiducial, $\alpha25$ and $\alpha5$ models,} the average CE separation increases in general across metallicity.
+\snotes{We show this for our fiducial model and each of our binary parameter variations.
+For our fiducial, $\alpha25$ and $\alpha5$ parameter variations,} the average CE separation increases in general across metallicity.
 Higher-metallicity binaries will interact earlier in the binary's lifetime than a lower-metallicity binary of equal separation due to their relatively larger maximum radii.
@@
 \snotes{The slope of the increase for these three models is dictated by the CE efficiency $\alpha$.
-With increasing metallicity there is a deepening of the convective envelope of the star compared to its lower metallicity counterparts at the same point in its evolution [is this the first time this idea is introduced?
-need to check], requiring more orbital energy to be available in order to eject the CE.
+With increasing metallicity there is a deepening of the convective envelope of the star compared to its lower metallicity counterparts at the same point in its evolution,} %[is this the first time this idea is introduced?
+need to check], \KB I think this is ok!
+\snotes{requiring more orbital energy to be available in order to eject the CE.
 Thus the high-metallicity binaries must have even wider separations for lower $\alpha$ values to ensure the binary does not merge before the envelope is ejected.
@@
 
-\snotes{The DWDs in model $q3$ that survive into the LISA band at present day have different formation channels than those of our other three models.
+\snotes{The DWDs in model $q3$ that survive into the LISA band at present day have different formation channels than those of our other three \kb{\sout{models} parameter variations}.
 Most importantly, the first interaction of these binaries are \emph{not} a CE interaction, but rather a phase of stable mass transfer.
-Because of this, we do not include it in Figure \ref{fig:CEsep} because it does not reflect the binary interactions for these simulations.
-All the binaries in the other models have more than one instance of a CE phase during their evolution, and rarely undergo stable mass transfer.
-The systems in $q3$ by contrast typically undergo RLO followed by a phase of stable mass transfer as the binary's first interaction.
-During mass transfer the orbit first shrinks, and then will slightly widen once the binary's mass ratio flips.
+\kb{\sout{Because of this, }} \kb{we show the CE phase which results from the second interaction for parameter variation $q3$} in Figure \ref{fig:CEsep}.}
+% because it does not reflect the binary interactions for these simulations.} 
+%All the binaries in the other models have more than one instance of a CE phase during their evolution, and rarely undergo stable mass transfer. 
+\kb{In contrast to two CE phases for the fiducial, $\alpha25$ and $\alpha5$ parameter varitions, the DWD progenitors in parameter variation $q3$ typically undergo a phase of stable mass transfer as the binary's first interaction.} During mass transfer the orbit first shrinks, and then will slightly widen once the binary's mass ratio flips.
 This process leads to formation of the first WD component.
 The companion is then formed later in the binary's evolution through a CE phase.
-Almost all systems in $q3$ undergo only a single CE phase.
-Of particular interest in $q3$ is the CO + He systems.
-All of the $q3$ CO + He binaries that end up in the LISA band have the Helium WD unexpectedly form first through stable mass transfer, with the CO WD forming second through a CE.
+%Almost all systems in parameter variation $q3$ undergo only a single CE phase.
+
+\snotes{Of particular interest in $q3$ is the CO + He systems.
+For all of the $q3$ CO + He binaries that \kb{\sout{end up} reside} in the LISA band \kb{at present}, the He WD \sout{unexpectedly} forms first through stable mass transfer, with the CO WD forming second through a CE.
 These binaries tend to all have similar resulting orbital separations from mass transfer, as can be seen by the relatively constant curve for CO + He's $\overline{a}_{\rm{CE}}$.
@@
 
-\snotes{Strikeout: [\emph{Note that the average CE separation is close to the qualitative limit for close binaries of $P_{\rm{orb}}\gtrsim10^{4}\,\rm{day}$ for the CO + CO and ONe + X binaries.
+%\snotes{Strikeout: [\emph{Note that the average CE separation is close to the qualitative limit for close binaries of $P_{\rm{orb}}\gtrsim10^{4}\,\rm{day}$ for the CO + CO and ONe + X binaries.
 We investigated the fraction of close DWD progenitors which formed with orbital periods above this range for each DWD type.
@@
 This suggests that our application of the close binary fraction may not be valid over the entire range of the DWD progenitor population.
-However, since the relative sizes of CO + CO and ONe + X are small compared to the He + He and CO + He populations, we leave a further investigation of these effects to a future study.}] [$\leftarrow$ I think we can take out this whole paragraph since we now take this into account!]}
+However, since the relative sizes of CO + CO and ONe + X are small compared to the He + He and CO + He populations, we leave a further investigation of these effects to a future study.}] [$\leftarrow$ I think we can take out this whole paragraph since we now take this into account!]} \kb{agreed!}
 
@@
 Above $Z=Z_\odot$ this overcompensates for the efficiency drop, producing the second peak.
-\snotes{For $\alpha5$ and $q3$, the lack of constraints on binary evolution -- from the increased CE efficiency in the former and increased propensity for stable mass transfer in the latter -- allow for less failed binaries from merging.
+\snotes{For $\alpha5$ and $q3$, the lack of \kb{\sout{constraints on binary} dramatic orbital shrinking} -- from the increased CE efficiency in the former and increased propensity for stable mass transfer in the latter -- allow for less failed binaries from merging.
 This leads to less dramatic drops in formation efficiency across metallicity and thus suppressing the formation of two peaks in the number of LISA-band systems.}
 
-\snotes{The $\alpha5$ and $q3$ variations have a higher number of F50 systems than FZ for all DWD types.
-This is due to the log-uniform P$_{\rm{orb}}$ distribution of F50 having more of the shortest-period binaries than the tails of the log-normal distribution of FZ, a discrepancy which becomes more significant with increasing metallicity as the FZ distribution moves from a peak of log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 3-4$ to log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 4-6$.
-This tail is less likely to survive to the LISA band at present day for the first two variations due to the harder binary evolution constraints.
-This is why we see essentially equal number of systems between FZ and F50 for the fiducial and $\alpha25$ variation: although the close binary fraction leads to a greater number of low-metallicity systems, this is compensated for by the FIRE distribution as well as the tendency for the shortest-period systems that F50 has a greater number of to merge, essentially washing out all differences between the populations.}
+\snotes{The $\alpha5$ and $q3$ variations \kb{\sout{have} produce} a higher number of F50 systems than FZ for all DWD types.
+This is due to the log-uniform P$_{\rm{orb}}$ distribution of model F50 having more of the shortest-period binaries than the tails of the log-normal distribution of FZ; a discrepancy which becomes more significant with increasing metallicity as the FZ distribution moves from a peak of log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 3-4$ to log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 4-6$.
+This tail is less likely to survive to the LISA band at present for the \kb{\sout{first two} fiducial and $\alpha25$} variations due to the \kb{\sout{harder binary evolution constraints} increased propensity for mergers of DWD progenitors}.
+This \kb{\sout{is why we see essentially} effect produces an} equal number of systems between FZ and F50 for the fiducial and $\alpha25$ variations.
+\kb{In both cases, a}lthough the close binary fraction leads to a greater number of low-metallicity systems, this is compensated for by the FIRE \kb{star particle metallicity} distribution as well as the tendency for the shortest-period DWD progenitors \kb{in model} F50 to merge, essentially washing out all differences between the populations.}
 
@@
 \snotes{\sout{The reduced} A change in the} number of DWDs in model FZ relative to model F50 is also apparent in the GW PSD LISA will observe.
-We show the GW PSD of each model, as well as the confusion estimate, in Figure~\ref{fig:PSD}.
-While model F50 (dark blue) and model FZ (light blue) produce several thousand large spikes in the PSD across LISA's frequency band, the overall foreground height, including the confusion, is larger for model F50 \snotes{for $\alpha5$ and $q3$}.
+We show the GW PSD of each model, as well as the confusion forground estimate, in Figure~\ref{fig:PSD}.
+While model F50 (dark blue) and model FZ (light blue) produce several thousand large spikes in the PSD across LISA's frequency band, the overall foreground height, including the confusion, is larger for model F50 \snotes{for parameter variations $\alpha5$ and $q3$}.
 This is a direct consequence of the overall reduction in the size of the close DWD population in model FZ.
-\snotes{As we would expect, the foreground height remains unchanged for the fiducial and $\alpha25$ variations}.
+\snotes{\sout{As we would expect, t}\kb{T}he foreground height remains unchanged for the fiducial and $\alpha25$ variations when comparing models FZ and F50}.
 
 Similar to previous studies, we find that LISA will be able to resolve several thousand DWDs.
-Figure \ref{fig:LISA_SNR} shows the amplitude spectral density vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the top and bottom rows show results for models FZ and F50 respectively.
+Figure \ref{fig:LISA_SNR} shows the amplitude spectral density vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the top and bottom rows show results for models FZ and F50 respectively for the fiducial parameter variation.
 For comparison, we also show the LISA sensitivity curve, including the
@@
 \snotes{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.
-For the fiducial model and $\alpha25$ variation, the number of resolvable systems with SNR $>7$ do not change much (are reduced by 4.5\% and increased by 3\% respectively).
-However, $\alpha5$ sees a reduction in the number of resolvable systems by only 26\%, and $q3$ remains almost \emph{unchanged}, seeing a 1\% reduction, even though the overall LISA population of both variations is halved.
-A large portion of the maintenance of $q3$ is contributed to by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).} \snotes{[\emph{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.}][$\leftarrow$ moved to beginning of paragraph] Strikeout: [\emph{Between models FZ and F50, the number of resolvable systems with SNR $>7$ over all DWD types decreases by only $\sim14\%$.}]}
+For the fiducial and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ \kb{\sout{do not change much}} are reduced by 4.5\% and increased by 3\% respectively.
+However, for $\alpha5$ the number of resolvable DWDs is reduced by only 26\%, and the number of resolvable DWDs $q3$ remains almost \emph{unchanged}, with a 1\% reduction even though the overall LISA population of both variations is halved.
+A large portion of the maintenance of the number of DWDs in parameter variation $q3$ is contributed to by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).}
+
+%\snotes{[\emph{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.}][$\leftarrow$ moved to beginning of paragraph] Strikeout: [\emph{Between models FZ and F50, the number of resolvable systems with SNR $>7$ over all DWD types decreases by only $\sim14\%$.}]}
 

### 2022-08-30 src/scripts/CEsep.py

@@ -5,8 +5,8 @@ import matplotlib.pyplot as plt
 import matplotlib as mpl
 import paths
 
-models = ["fiducial", "alpha25", "alpha5"]
-model_labels = ["fiducial", "$\\alpha 25$", "$\\alpha 5$"]
+models = ["fiducial", "alpha25", "alpha5", "q3"]
+model_labels = ["fiducial", "$\\alpha 25$", "$\\alpha 5$", "$q3$"]
 metmodel = "F50"
 
 FIREmin = 0.00015
@@ -17,7 +17,7 @@ met_bins = np.logspace(np.log10(FIREmin), np.log10(FIREmax), num)
 met_mids = (met_bins[1:] + met_bins[:-1]) / 2
 whichsep = "CEsep"
 
-fig, ax = plt.subplots(3, 4, figsize=(16, 11))
+fig, ax = plt.subplots(4, 4, figsize=(16, 15))
 
 for m, model in enumerate(models):
     if "Z" in model:

### 2022-08-30 src/scripts/PSD.py

@@ -7,8 +7,8 @@ import paths
 def func(x, a, b, c, d, e):
     return a + b * x + c * x ** 2 + d * x ** 3 + e * x ** 4
 
-models = ["fiducial", "q3", "alpha25", "alpha5"]
-names = ["fiducial", "$q3$", "$\\alpha25$", "$\\alpha5$"]
+models = ["fiducial", "alpha25", "alpha5", "q3"]
+names = ["fiducial", "$\\alpha25$", "$\\alpha5$", "$q3$"]
 
 fig, ax = plt.subplots(1, 4, figsize=(25, 5))
 for i, model in enumerate(models):

### 2022-08-30 src/scripts/CEsep.py
update CEsep and model comp to be right label and order

@@ -140,7 +140,7 @@ for m, model in enumerate(models):
         ax[m, i].set_xticks([-3., -2., -1., 0., 1.])
         ax[m, i].tick_params(labelsize=15)
         ax[m, i].set_xlim(np.log10(met_mids[0]), np.log10(met_mids[-1]))
-        if m == 2:
+        if m == 3:
             ax[m, i].set_xlabel('Log$_{10}$(Z/Z$_\odot$)', fontsize=18)
         if m == 0:
             ax[m, i].legend(

### 2022-08-30 src/scripts/model_comp.py

@@ -5,10 +5,10 @@ import seaborn as sns
 import astropy.units as u
 import paths 
 
-models = ["fiducial", "q3", "alpha25", "alpha5", "fiducial_Z", "q3_Z", "alpha25_Z", "alpha5_Z"]
-model_names = ["fiducial", "q3", "alpha25", "alpha5", "fiducial", "q3", "alpha25", "alpha5", "fiducial_Z", "q3_Z", "alpha25_Z", "alpha5_Z"]
+models = ["fiducial", "alpha25", "alpha5", "q3", "fiducial_Z", "alpha25_Z", "alpha5_Z", "q3_Z"]
+model_names = ["fiducial", "alpha25", "alpha5", "q3", "fiducial_Z", "alpha25_Z", "alpha5_Z", "q3_Z"]
 colors = sns.color_palette("mako", n_colors=4)
-names = ["fiducial", "$q3$", "$\\alpha25$", "$\\alpha5$", "fiducial", "$q3$", "$\\alpha25$", "$\\alpha5$", "fiducial", "$q3$", "$\\alpha25$", "$\\alpha5$"]
+names = ["fiducial", "$\\alpha25$", "$\\alpha5$", "$q3$", "fiducial", "$\\alpha25$", "$\\alpha5$", "$q3$"]
 Tobs = 4 * u.yr
 
 
@@ -46,7 +46,6 @@ for model in model_names:
         lisa_ratio.append(n_lisa_FZ / n_lisa_F50)
         popt_FZ = popt_FZ.values.flatten()
         popt_FZ_list.append(popt_FZ)
-        print(model, popt_FZ)
         
     
     else:
@@ -59,7 +58,6 @@ for model in model_names:
         n_lisa_F50_list.append(n_lisa_F50)
         popt_F50 = popt_F50.values.flatten()
         popt_F50_list.append(popt_F50)
-        print(model, popt_F50)
         
 
 for popt_F50, popt_FZ, ii in zip(popt_F50_list, popt_FZ_list, range(len(popt_FZ_list))):

### 2022-08-31 src/scripts/LISA_SNR.py
fixed sizing and labels!

@@ -66,7 +66,11 @@ def plot_LISAcurves(var, model, label, ii):
     ax[ii, 0].scatter(resolved_HeHe.f_gw, Heasd, zorder=10, color='xkcd:tomato red', label='He + He', rasterized=True)
     lgnd = ax[ii, 0].legend(loc='lower left', ncol=4, borderaxespad=0, frameon=False, fontsize=22, markerscale=2.5, handletextpad=0.15)
     lgnd.legendHandles[0]._sizes = [100]
-    ax[ii, 0].text(0.1, 2e-16, var+', SNR > 7: {}'.format(len(Heasd)), fontsize=24, horizontalalignment='right')
+    if ("Z" not in model) & ("fiducial" not in model):
+        ax[ii, 0].text(0.1, 2e-16, label+', '+var+', SNR > 7: {}'.format(len(Heasd)), fontsize=24, horizontalalignment='right')
+    else:
+        ax[ii, 0].text(0.1, 2e-16, var+', SNR > 7: {}'.format(len(Heasd)), fontsize=24, horizontalalignment='right')
+    
     
     ax[ii, 2].plot(np.linspace(1e-4, 1e-1, 1000000), psd_conf**0.5, c='black', rasterized=True, lw=2)
     ax[ii, 2].scatter(resolved_COHe.f_gw, COHeasd, zorder=10, color='xkcd:light grey', rasterized=True)
@@ -75,8 +79,10 @@ def plot_LISAcurves(var, model, label, ii):
     ax[ii, 2].scatter(resolved_COCO.f_gw, COasd, zorder=10, color='xkcd:pink', label='CO + CO', rasterized=True)
     lgnd = ax[ii, 2].legend(loc='lower left',  ncol=4, borderaxespad=0, frameon=False, fontsize=22, markerscale=2.5, handletextpad=0.15)
     lgnd.legendHandles[0]._sizes = [100]
-    ax[ii, 2].text(0.1, 2e-16, var+', SNR > 7: {}'.format(len(COasd)),  fontsize=24, horizontalalignment='right')
-    
+    if ("Z" not in model) & ("fiducial" not in model):
+        ax[ii, 2].text(0.1, 2e-16, label+', '+var+', SNR > 7: {}'.format(len(COasd)),  fontsize=24, horizontalalignment='right')
+    else:
+        ax[ii, 2].text(0.1, 2e-16, var+', SNR > 7: {}'.format(len(COasd)),  fontsize=24, horizontalalignment='right')
[…]

### 2022-08-31 src/scripts/met_dep_porb.py

@@ -118,7 +118,7 @@ logP_lo_lim=0
 logP_hi_lim=9
 log_P = np.linspace(logP_lo_lim, logP_hi_lim, 10000)
 
-fig, ax = plt.subplots()
+fig, ax = plt.subplots(figsize=(7.5,5))
 
 for norm_wide, norm_close, Z, FeH, color in zip(norm_wide_list, norm_close_list, met_arr, FeH_list, colors):
     neval = 500
@@ -140,7 +140,7 @@ for norm_wide, norm_close, Z, FeH, color in zip(norm_wide_list, norm_close_list,
     else:
         plt.plot(x_dat, y_dat, c=color)
 
-plt.legend(ncol=2, loc=[0, 1.01], frameon=False)
+plt.legend(ncol=2, loc=[0, 1.01], frameon=False, prop={'size':16})
 plt.tick_params(labelsize=15)
 plt.xlabel(r'log$_{10}(P_{\rm{orb}}/day)$', size=18)
 plt.ylabel(r'$f_{\rm{logP}}$', size=18)

### 2022-08-31 src/scripts/postproc.py
update downsampling

@@ -1179,7 +1179,7 @@ def get_resolvedDWDs(pathtoLISA, pathtosave, var, model, window):
     
     power_dat_median = power_dat.rolling(window).median()
     power_dat_median = power_dat_median[window:]
-    power_dat_downsample = power_dat.sample(int(len(power_dat)/5), replace=False)
+    power_dat_downsample = power_dat.sample(int(len(power_dat)/10), replace=False)
     power_dat_downsample = power_dat_downsample.sort_values('f_gw')
     power_dat_downsample.to_hdf(pathtosave / result_file, key=Pkey)
     #power_dat.to_hdf(pathtoLISA / result_file, key=Pkey)

### 2022-08-31 src/scripts/pipeline.py
remove prints

@@ -28,7 +28,7 @@ FIRE_path = paths.data
 results_path = paths.data
 models = ['fiducial', 'fiducial_Z', 'alpha25', 'alpha25_Z', 'alpha5', 'alpha5_Z', 'q3', 'q3_Z']
 interfile = False
-nproc_gx = 40
+nproc_gx = 28
 nproc_results = len(models)
   
 
@@ -50,17 +50,17 @@ def get_results(dat):
     pp.get_formeff(
         pathtodat=dat_path, pathtosave=results_path, model=model, var=var,
     )
-    print('formation efficiency done for model: {}'.format(model))
+    #print('formation efficiency done for model: {}'.format(model))
     
     pp.get_interactionsep_and_numLISA(
         pathtocosmic=dat_path, pathtoLISA=LISA_path, pathtoresults=results_path, model=model, var=var,     
     )
-    print('interaction sep done')
+    #print('interaction sep done')
     
     pp.get_resolvedDWDs(
         pathtoLISA=LISA_path, pathtosave=results_path, var=var, model=model, window=window
     )
-    print('resolved sources done')
+    #print('resolved sources done')
     
     return []
 

### 2022-08-31 src/tex/ms.tex
update bolding and a couple of references

@@
 \affiliation{Canadian Institute for Theoretical Astrophysics, University
-of Toronto, 60 St. George Street, Toronto, Ontario, M5S 1A7,
+of Toronto, 60 St. George Street, Toronto, ON, M5S 1A7,
 Canada}
@@
 DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be the dominant contributor to a stochastic foreground caused by overlapping GW signals, limiting the detectability of individual sources of all kinds.
-Population modeling of Galactic DWDs typically assumes a binary fraction of $50\%$.
-However, recent observations have shown that the binary fraction of close, solar-type stars exhibits a strong anti-correlation with metallicity.
+Population modeling of Galactic DWDs typically assumes a binary fraction of $50\%$ \textbf{and a log-uniform Zero Age Main Sequence (ZAMS) orbital period distribution}.
+However, recent observations have shown that the binary fraction of close, solar-type stars exhibits a strong anti-correlation with metallicity \textbf{which modulates the ZAMS orbital period distribution below $10^4$ days}.
 In this study we perform the first simulation of the Galactic DWD population observable by LISA which incorporates an empirically-derived metallicity-dependent binary fraction.
 We simulate DWDs using the binary population synthesis suite \cosmic\ and incorporate a metallicity-dependent star formation history to create a Galactic population of short-period DWDs.
-We compare two models: one which assumes a metallicity-dependent binary fraction, and one with a binary fraction of 50\%.
-We find that while metallicity impacts the evolution and intrinsic properties of our simulated DWD progenitor binaries, the LISA-resolvable populations of the two models remain roughly indistinguishable.
-However, the size of the total Galactic DWD population orbiting in the LISA frequency band is reduced by more than half when accounting for a metallicity-dependent binary fraction.
-This effect lowers the confusion foreground, effectively increasing the sensitivity for detecting all types of low-frequency LISA sources.
-\kb{***Need to update this***}We repeat our analysis for three different assumptions for Roche-lobe overflow interactions and find the population reduction to be robust when a metallicity-dependent binary fraction is assumed.
+We compare two models: one which assumes a metallicity-dependent binary fraction \textbf{and ZAMS orbital period distribution}, and one with a binary fraction of 50\% \textbf{and log-uniform ZAMS orbital period distribution}.
+\textbf{We repeat our analysis for three different assumptions for Roche-lobe overflow interactions.} We find that while metallicity impacts the evolution and intrinsic properties of our simulated DWD progenitor binaries, the LISA-resolvable populations of the two models remain roughly indistinguishable.
+However, the size of the total Galactic DWD population orbiting in the LISA frequency band is reduced by more than half when accounting for a metallicity-dependent binary fraction \textbf{for two of our four variations.} This effect lowers the confusion foreground, effectively increasing the sensitivity for detecting all types of low-frequency LISA sources.
+\textbf{The LISA population remains unchanged in number for two variations, highlighting the sensitivity of the population to binary evolution prescriptions.} %KB: I think this is a good choice!\textbf{Strikeout: [\emph{We repeat our analysis for three different assumptions for Roche-lobe overflow interactions and find the population reduction to be robust when a metallicity-dependent binary fraction is assumed.}]}
 \end{abstract}
@@
 The Laser Interferometer Space Antenna (LISA) is expected to resolve at least $10^4$ individual DWD binaries in the Milky Way and will also observe GW emission from the entire Galactic DWD population through the unresolved foreground created by overlapping signals at sub-mHz frequencies \citep[e.g.,][]{Nelemans2001a, Ruiter2010, Nissanke2012, Yu2013, Korol2017, Lamberts2019, Breivik2020a}.
-The resolved population will enable the study of several important aspects of binary evolution like the strength of tides \citep{Valsecchi2012} and the stability of mass transfer in DWD systems \citep[e.g.,][]{Marsh2004, Shen2015, Gokhale2007, Sepinsky2014, Kremer2015} as well as provide a probe of Galactic structure \citep{Korol2019} and the Local Group \citep{Korol2018}.
-The shape and strength of the Galactic DWD foreground can also be used as a tool to study the structure of the Milky Way \citep{Benacquista2006, Breivik2020b} as well as the separation distribution of close DWDs \citep{Korol2021}.
+The resolved population will enable the study of several important aspects of binary evolution like the strength of tides \citep{Valsecchi2012}, the stability of mass transfer in DWD systems \citep[e.g.,][]{Marsh2004, Shen2015, Gokhale2007, Sepinsky2014, Kremer2015}\textbf{, and the separation distribution of close DWDs \citep{Korol2021}} as well as provide a probe of Galactic structure \citep{Korol2019} and the Local Group \citep{Korol2018}.
+The shape and strength of the Galactic DWD foreground can also be used as a tool to study the structure of the Milky Way \citep{Benacquista2006, Breivik2020b}.
 
@@
 \subsection{Metallicity-dependent binary fraction}\label{subsec:metbinfrac}
-\textbf{The binary fraction in the Galaxy has been empirically shown to depend on metallicity.
+\textbf{The close binary fraction in the Galaxy has been empirically shown to depend on metallicity.
 This is manifested through an explicit dependence of the companion frequency on orbital period \citep{Moe2021}.
@@
 	\includegraphics[width=\columnwidth]{figures/met_dep_porb.pdf}
-    \caption{}
+    \caption{The distribution of the companion frequency f$_{\rm{logP}}$ for solar-type stars is dependent on both ZAMS orbital period and metallicity.
+Each curve is coloured by metallicity, with the darkest curve corresponding to the lowest-metallicity bin in our simulations at [Fe/H]$=-2.3$ and the lightest curve corresponding to our highest-metallicity bin at [Fe/H]$=0.18$.
+Above $\log_{10}(P_{\rm{orb}}/\rm{day})\sim 4$, the companion frequency distribution is the same for all metallicity bins as no identified metallicity dependence at those periods exists in current literature.}
     \label{fig:met_dep_porb}
@@
 \textbf{Figure \ref{fig:met_dep_porb}, shows the companion frequency f$_{\rm{logP}}$ for solar-type stars as a function of the logarithm of orbital period, mirroring the inner binaries curve of Figure 2 in \citet{Moe2021} and scaling to an overall multiplicity frequency of 0.67 (equivalent to an integrated binary fraction of 50\%) at solar metallicity.
-To obtain the normalization of the companion frequency for close binaries ($\log_{10}(P_{\rm{orb}}/\rm{day}<10^4$)),} we fit the results presented in \citet{Moe2019} using linear regression to obtain a piecewise relation between the metallicity, [Fe/H] and \text{close} binary fraction $f_{\rm{b}}$ as
+To obtain the normalization of the companion frequency for close binaries (P$_{\rm{orb}}<10^4$),} we fit the results presented in \citet{Moe2019} using linear regression to obtain a piecewise relation between the metallicity, [Fe/H] and \text{close} binary fraction $f_{\rm{b}}$ as
 
@@
 In variation $q3$, we vary the assumption for the critical mass ratios at which a RLO interaction remains stable or becomes unstable from our fiducial assumptions such that the critical mass ratio is increased to $3.0$ and thus allows stable mass transfer for more massive RLO donors.
-In variations $\alpha25$ and $\alpha5$, we modify the common envelope ejection efficiency to be either much less ($\alpha=0.25$) or more ($\alpha=5$) than in our fiducial assumption ($\alpha=1$).
+In variations $\alpha25$ and $\alpha5$, we modify the common envelope ejection efficiency to be either much less ($\alpha=0.25$) or more ($\alpha=5$) than in our fiducial assumption ($\alpha=1$) to capture the range of possible CE ejection efficiencies quoted in the literature  \citep[e.g.][]{Zorotovic2010, Fragos2019}.
 Larger common envelope ejection efficiencies lead to wider post-CE separations, while smaller ejection efficiencies either lead to closer post-CE separations or stellar mergers where the envelope ejection fails.
@@
 
-The metallicity-dependent \textbf{close} binary fraction \textbf{for solar-type binaries (P $< 10^4$ days), or simply the \kb{close} binary fraction from here on, }% S: Should I change all instances of "binary fraction" to "close binary fraction" then?
+The metallicity-dependent \textbf{close} binary fraction \textbf{for solar-type binaries (P $< 10^4$ days), or simply the close binary fraction from here on, }% S: Should I change all instances of "binary fraction" to "close binary fraction" then?
 %KB: I will keep an eye out to make the changes
@@
 \begin{equation}
-    \rho_{\text{circ,stat}}^2 = \frac{h_{2}^2T_{\text{obs}}}{4 S_n(f_2)}
+    \rho_{\text{circ,stat}}^2 = \frac{h_{2}^2T_{\text{obs}}}{ S_n(f_2)}
 \end{equation}
@@
 \end{equation}
-\noindent and $x=\log_{10}(f_{\rm{GW}}/\rm{Hz})$. We add the fitted polynomial of the PSD's running median to the LISA noise PSD to obtain a sensitivity curve for each model.
+\noindent and $x=\log_{10}(f_{\rm{GW}}/\rm{Hz})$. We add the fitted polynomial of the PSD's running median to the LISA noise PSD to obtain a sensitivity curve for each model \textbf{and variation}.
 
@@
     \caption{The DWD formation efficiency vs metallicity of DWD populations simulated with \cosmic.
-Each panel shows the formation efficiency for a given DWD type \snotes{and variation}.
+Each panel shows the formation efficiency for a given DWD type \textbf{and variation}.
 The solid lines indicate the formation efficiency for model FZ which incorporates a metallicity-dependent binary fraction.
 The dashed lines indicate the formation efficiency for model F50, which assumes a constant binary fraction of $50\%$.
-The DWD formation efficiency drops by a factor of $4-5$ for model FZ and a factor of \snotes{\sout{2-5} 1-5} for model F50.
-See Section~\ref{sec:formeff} for a careful description of the trends for each DWD type.}
+The DWD formation efficiency drops by a factor of $4-5$ for model FZ and a factor of %\textbf{\sout{2-5}
+    \textbf{1-5} for model F50. See Section~\ref{sec:formeff} for a careful description of the trends for each DWD type.}
     \label{fig:form_eff}
@@
 This effect is exaggerated for model FZ which assumes a \textbf{close} binary fraction which also decreases with increasing metallicity.
-\textbf{In the following sub-sections, we describe the formation efficiency trends for our fiducial model in detail and then describe the changes arising from each binary evolution parameter variation.}
+\textbf{In the following sub-sections, we describe the formation efficiency trends for our fiducial variation in detail and then describe the changes arising from each binary evolution parameter variation.}
 
@@
 	\includegraphics[width=\textwidth]{figures/CEsep.pdf}
-    \caption{Average interaction separation, $\overline{\mathrm{a}}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type \snotes{and variation} from model FZ.
+    \caption{Average interaction separation, $\overline{\mathrm{a}}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type \textbf{and variation} from model FZ.
 Solid lines show the average separation at the first RLO for binaries in each metallicity bin.
 The shaded regions show the $1\sigma$ spread around the mean within each metallicity bin.
-The average interaction separation increases with metallicity for every DWD type\snotes{, except for $\alpha5$ which remains approximately constant for CO + He and ONe + X}.
+The average interaction separation increases with metallicity for every DWD type\textbf{, except for $\alpha5$ which remains approximately constant for CO + He and ONe + X}.
 The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts.
-The sharp drop of the CO + CO average at the highest-metallicity bin \snotes{of the fiducial simulation} is due to binning effects of the figure: it only contains 115 systems, of which the majority stem from a single low-separation system which was sampled 94 times times during the simulation.}
+The sharp drop of the CO + CO average at the highest-metallicity bin \textbf{of the fiducial variation} is due to binning effects of the figure: it only contains 115 systems, of which the majority stem from a single low-separation system which was sampled 94 times times during the simulation.
+\textbf{The regions of metallicity where there is not shading beyond the mean trend are also due to low numbers of DWDs in each bin}.}
     \label{fig:CEsep}
@@
 
-\snotes{For binary systems leading to He + He DWDs, there are many more mergers for $\alpha25$ than for the fiducial \kb{model}.
-The lower CE efficiency \kb{\sout{entails} leads to DWD progenitor} mergers from \kb{failed CE ejection \sout{the binary failing to eject the CE}}, or \kb{the CE} shrinking the orbit such that it then merges on the second CE phase.
-Because\kb{\sout{, as discussed above,}} there are more \kb{\sout{very short-period} ZAMS binaries with orbital periods shorter than $10^4$ days} in F50, as the \kb{\sout{ZAMS binary}} population evolves there are more likely to be binary interactions in the population for F50 than FZ.
+\textbf{For binary systems leading to He + He DWDs, there are many more mergers for $\alpha25$ than for the fiducial variation.
+The lower CE efficiency leads to DWD progenitor mergers from failed CE ejection, or the CE shrinking the orbit such that it then merges on the second CE phase.
+Because there are more ZAMS binaries with orbital periods shorter than $10^4$ days in F50, as the population evolves there are more likely to be binary interactions in the population for F50 than FZ.
 This leads to more mergers in $\alpha25$ occurring for F50 before formation of the DWD and thus a lower formation efficiency overall for F50 in contrast to FZ.
-\kb{\sout{as we see} This is illustrated} in the $\alpha25$ He + He plot of Figure \ref{fig:form_eff}.
-Similar to the fiducial \kb{model}, a binary that becomes a He + He DWD at lower metallicities would merge before becoming one at higher metallicities because of the longer evolution timescales.
+This is illustrated in the $\alpha25$ He + He plot of Figure \ref{fig:form_eff}.
+Similar to the fiducial parameter variation, a binary that becomes a He + He DWD at lower metallicities would merge before becoming one at higher metallicities because of the longer evolution timescales.
 These later interactions lead to closer post-CE separations and thus more mergers.
-The dip at [Fe/H]=$\sim -1.5\%$ stems from mergers before the DWD forms, \kb{again} similar to \kb{sout{for our}the } fiducial model.
-The peak that occurs in $\alpha25$ at $\sim 10\%$ Z$_\odot$ arises from binaries evolving faster \kb{\sout{(i.e.} and thus}} interacting earlier as metallicity increases.
-\kb{This means \sout{meaning}} that equivalent binaries that would have merged or formed a CO + He DWD instead at lower metallicities now survive \kb{\sout{into} to produce} a He + He \kb{DWD}.
-At higher metallicities, there are a higher proportion of wide\kb{\sout{-separation systems} ZAMS binaries}, which evolve off the Main Sequence too slowly to form a He + He DWD, causing the efficiency drop.
+The dip at [Fe/H] $\simeq -1.5\%$ stems from mergers before the DWD forms, again similar to the fiducial parameter variation.
+The peak that occurs in $\alpha25$ at $\sim 10\%$ Z$_\odot$ arises from binaries evolving faster and thus interacting earlier as metallicity increases.
+This means that equivalent binaries that would have merged or formed a CO + He DWD instead at lower metallicities now survive to produce a He + He DWD.
+At higher metallicities, there are a higher proportion of wide ZAMS binaries, which evolve off the Main Sequence too slowly to form a He + He DWD, causing the efficiency drop.}
 
-\snotes{For $\alpha5$, there are significantly fewer \kb{DWD progenitor} mergers, \kb{\sout{as expected}} since binaries are more likely to survive a CE phase \kb{\sout{from} due to} the higher CE \kb{ejection} efficiency.
-Systems that would normally merge for $\alpha25$ \kb{\sout{now} instead} survive, and are shrunk to short orbits through CE interactions to \kb{\sout{evolve} reside} in the LISA band \kb{at present}.
-The number of DWDs thus makes up a higher fraction of the total simulated binary population \kb{\sout{overall}}, thus we see \kb{\sout{in general}} higher formation efficiencies than for \kb{\sout{our} the} fiducial \kb{\sout{simulations} model} (\kb{\sout{which has }}$\alpha=1$).
-\kb{\sout{, and even higher than for our} This effect is even more pronouced in comparison with the $\alpha25$} variation \kb{\sout{with} which sets} $\alpha=0.25$.
-}
+\textbf{For $\alpha5$, there are significantly fewer DWD progenitor mergers since binaries are more likely to survive a CE phase due to the higher CE ejection efficiency.
+Systems that would normally merge for $\alpha25$ instead survive, and are shrunk to short orbits through CE interactions to reside in the LISA band at present.
+The number of DWDs then makes up a higher fraction of the total simulated binary population , thus we see in general higher formation efficiencies than for the fiducial parameter variation which sets $\alpha=1$.
+This effect is even more pronounced in comparison with the $\alpha25$ variation which sets $\alpha=0.25$.}
 
-\snotes{Beyond \kb{\sout{this} the effects described above}, the efficiency drop across metallicity is similar to the fiducial \kb{model} in that it depends on the metallicity-dependent ZAMS orbital period distribution emphasizing short-period systems at low metallicities, and in the change of formation channel for different period ranges across metallicity.
-We \kb{\sout{see} find} the highest formation efficiency for variation $q3$.
+\textbf{Beyond the effects described above, the efficiency drop across metallicity is similar to the fiducial parameter variation in that it depends on the metallicity-dependent ZAMS orbital period distribution emphasizing short-period systems at low metallicities, and in the change of formation channel for different period ranges across metallicity.
+We find the highest formation efficiency for variation $q3$.
 Only the shortest-period binaries do not form a DWD through mergers at higher metallicities.
-At low metallicities, \kb{\sout{we see that}} even binaries with \kb{\sout{very close}} ZAMS separations \kb{less than XX} form He + He DWDs.
-\kb{\sout{We}} Thus \kb{\sout{see} this leads to} a higher \kb{formation} efficiency from F50 over FZ for parameter variation $q3$ because of the higher number of shortest-period ZAMS binaries in the log-uniform distribution of F50.}
+At low metallicities, even binaries with ZAMS orbital periods P$_{\rm{orb}}\lesssim 100$ days form He + He DWDs, with binaries in model FZ reaching ZAMS orbital periods less than a day in length.
+This leads to a higher formation efficiency from F50 over FZ for parameter variation $q3$ because of the higher number of shortest-period ZAMS binaries in the log-uniform distribution of F50.}
 
-\snotes{For CO + He binaries, there are again many more mergers for \kb{parameter variation} $\alpha25$ relative to the fiducial case.
-This is the \kb{\sout{dominating} dominant} way that \kb{progenitors do not evolve to produce DWDs \sout{binaries are lost}} at higher metallicities.
-At low metallicities \kb{\sout{we also see}} a number of \kb{\sout{systems} progenitor binaries} form CO + CO \kb{\sout{binaries} DWDs instead of He + CO DWDs}.
-\kb{\sout{-- t}T}his is especially the case in \kb{\sout{a ``Goldilocks zone" around} near} log$_{10}$(Z/Z$_\odot)\sim -2$, where RLO occurs late enough in \kb{a binary's} evolution that mass transfer remains stable and CO + CO's are formed rather than CO + He, hence \kb{\sout{why we see} producing} a dip in the formation efficiency.
-Because \kb{parameter variation} $\alpha5$ \kb{\sout{entails leads to}} less mergers due to the high CE efficiency, the formation efficiency is mostly governed by the metallicity-dependent ZAMS orbital period distribution.
-At higher metallicities the majority of \kb{\sout{lost systems} cases in model FZ where progenitors don't produce a CO + He DWD} are due to \kb{progenitor} mergers or to He + He \kb{\sout{binaries} DWDs} forming instead \kb{CO + He DWDs.}} %due to the faster evolution at high metallicities and increasing radii inducing earlier binary interactions and hence stripping of both star's envelopes [$\leftarrow$ is this correct logic?].
+\textbf{For CO + He binaries, there are again many more mergers for parameter variation $\alpha25$ relative to the fiducial case.
+This is the dominant way that progenitors do not evolve to produce DWDs at higher metallicities.
+At low metallicities, a number of progenitor binaries form CO + CO DWDs instead of He + CO DWDs.
+This is especially the case in near $\log_{10}$(Z/Z$_\odot)\sim -2$, where RLO occurs late enough in a binary's evolution that mass transfer remains stable and CO + CO's are formed rather than CO + He, hence producing a dip in the formation efficiency.
+Because parameter variation $\alpha5$ leads to less mergers due to the high CE efficiency, the formation efficiency is mostly governed by the metallicity-dependent ZAMS orbital period distribution.
+At higher metallicities the majority of cases in model FZ where progenitors don't produce a CO + He DWD are due to progenitor mergers or to He + He DWDs forming instead of CO + He DWDs.} %due to the faster evolution at high metallicities and increasing radii inducing earlier binary interactions and hence stripping of both star's envelopes [$\leftarrow$ is this correct logic?].
 I think this is already discussed above for fiducial so we don't need to worry about it.
-\snotes{At higher metallicities, the ZAMS orbital period distribution of FZ also drops below the \kb{orbital period} distribution \kb{\sout{for} of} F50 and extends out to orbital periods beyond what would form a CO + He.
-\kb{This causes \sout{ which is why}} the formation efficiencies for FZ and F50 \kb{to} cross at log$_{10}$(Z/Z$_\odot$)$\sim-0.5$.
-\kb{This is also apparent \sout{which we also see}} for the $q3$ variation, and to a lesser extent in the fiducial \kb{\sout{variation} case}.} %Any lost systems in $q3$ also is contributed to by: (i) some binaries at high metallicities not forming a CO + He DWD by present day due to envelope-stripping timescales being delayed by phases of stable mass transfer, (ii) mergers, and (ii) ONe + X DWDs forming instead.
-\snotes{In $q3$, for any given orbital period we find that lower mass \kb{\sout{systems} DWDs originate \sout{come}} from lower metallicities,\kb{\sout{which leads} thus leading} to an approximately constant formation efficiency.}
+\textbf{At higher metallicities, the ZAMS orbital period distribution of FZ also drops below the orbital period distribution of F50 and extends out to orbital periods beyond what would form a CO + He.
+This causes the formation efficiencies for FZ and F50 to cross at log$_{10}$(Z/Z$_\odot$)$\sim-0.5$.
+This is also apparent for the $q3$ variation, and to a lesser extent in the fiducial case.} %Any lost systems in $q3$ also is contributed to by: (i) some binaries at high metallicities not forming a CO + He DWD by present day due to envelope-stripping timescales being delayed by phases of stable mass transfer, (ii) mergers, and (ii) ONe + X DWDs forming instead.
+\textbf{In $q3$, for any given orbital period we find that lower mass DWDs originate from lower metallicities, thus leading to an approximately constant formation efficiency.}
 
-\snotes{For CO + CO, across all variations, very close \kb{ZAMS} binaries (P$_{\rm{orb}} \mathcal{O}(100$ days)) at high metallicities} \kb{form a CO + He or He + He DWD instead of a CO + CO because the binary interacts before core Helium burning of one or both components.
+\textbf{For CO + CO, across all variations, very close ZAMS binaries (P$_{\rm{orb}}\sim\mathcal{O}(100$ days)) at high metallicities form a CO + He or He + He DWD instead of a CO + CO because the binary interacts before core Helium burning of one or both components.
 }
 %lost at high metallicities when a binary that would form a CO + CO at low metallicities forms a CO + He or He + He DWD instead 
-There are again many more mergers in $\alpha25$, and \kb{\sout{less} fewer} mergers for $\alpha5$.
+\textbf{There are again many more mergers in $\alpha25$, and fewer mergers for $\alpha5$.
 Due to the high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods survive to become CO + CO DWDs rather than merging or becoming CO + He or He + He DWDs.
-There are \kb{\sout{less} fewer} mergers overall for $q3$ than all the $\alpha$ \kb{\sout{values} variations} because \kb{\sout{of the phase of stable mass transfer occurring before the CE phase} the first RLO occurrence leads to stable mass transfer from the primary to the secondary} rather than multiple CE phases.
-\kb{For both the $\alpha5$ and $q3$ variations, the majority of CO + CO DWDs originate in wide enough orbits that they don't interact before DWD formation.
-This leads to an approximately constant formation efficiency across metllicity in both cases.}
+There are less fewer mergers overall for $q3$ than all the $\alpha$ variations because the first RLO occurrence leads to stable mass transfer from the primary to the secondary rather than multiple CE phases.
+For both the $\alpha5$ and $q3$ variations, the majority of CO + CO DWDs originate in wide enough orbits that they don't interact before DWD formation.
+This leads to an approximately constant formation efficiency across metallicity in both cases.}
 
-%\kb{This also leads to \kb\souce{hence why} \kb{an approximately constant formation efficiency} $q3$ \sout{efficiency}\kb{parameter variation} is approximately constant across metallicity.}
-%\kb{**I think maybe another thing to point out is that the majority of CO + CO don't interact }
-
-\kb{For model FZ, the ONe + X formation efficiencies follow similar trends aross each parameter variation.
+\textbf{For model FZ, the ONe + X formation efficiencies follow similar trends aross each parameter variation.
 Their formation scenarios are similar to those described above for the fiducial binary evolution parameter set.
@@
 % Reworked this into the paragraph above.
-%\snotes{[** Might need to fact check this paragraph **] The FZ curves for ONe + X are relatively similar amongst variations beyond height, and the loss of systems is the same as described for the fiducial simulation.
+%\textbf{[** Might need to fact check this paragraph **] The FZ curves for ONe + X are relatively similar amongst variations beyond height, and the loss of systems is the same as described for the \kb{fiducial variation}.
 We have more mergers once again for $\alpha25$, which lowers the F50 curve below FZ because F50 has the shortest-ZAMS-period end that FZ does not have.
@@
     \caption{The number of LISA-band systems formed for each DWD type as a function of the base-10 logarithm of metallicity, normalized to solar value.
-The solid line shows the FZ population with a metallicity-dependent \snotes{close} binary fraction incorporated, and the dashed line shows the F50 population for a standard binary fraction of 0.5.
+The solid line shows the FZ population with a metallicity-dependent \textbf{close} binary fraction incorporated, and the dashed line shows the F50 population for a standard binary fraction of 0.5.
 The LISA population of DWDs is dominated by stars with super-solar metallicities.
 This is true even for model FZ, which drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond Z$\simeq$Z$_\odot$.
-There is a double peak in the \snotes{fiducial and $\alpha25$ }He + He population\snotes{s}; the first peak is caused by the sharp drop in formation efficiency past Z$\simeq$0.1$Z_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
+There is a double peak in the \textbf{fiducial and $\alpha25$} He + He populations; the first peak is caused by the sharp drop in formation efficiency past Z$\simeq$0.1$Z_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
     \label{fig:lisa_nums}
@@
 The solid lines denote the average value, and the $1\sigma$ variance is shown in the surrounding shading.
-\snotes{We show this for our fiducial model and each of our binary parameter variations.
+\textbf{We show this for our fiducial variation and each of our binary parameter variations.
 For our fiducial, $\alpha25$ and $\alpha5$ parameter variations,} the average CE separation increases in general across metallicity.
@@
 This regulation plays a key role in smearing out any observable effects of a metallicity-dependent binary fraction in the population of DWDs observable by LISA.
-\snotes{The slope of the increase for these three models is dictated by the CE efficiency $\alpha$.
+
+\textbf{The slope of the increase for these three models is dictated by the CE efficiency $\alpha$.
 With increasing metallicity there is a deepening of the convective envelope of the star compared to its lower metallicity counterparts at the same point in its evolution,} %[is this the first time this idea is introduced?
 need to check], \KB I think this is ok!
-\snotes{requiring more orbital energy to be available in order to eject the CE.
+\textbf{requiring more orbital energy to be available in order to eject the CE.
 Thus the high-metallicity binaries must have even wider separations for lower $\alpha$ values to ensure the binary does not merge before the envelope is ejected.
-We thus see a steeper separation slope for $\alpha25$, a less steep slope for $\alpha5$, and an intermediate slope for our fiducial model which has $\alpha=1$.}
+We thus see a steeper separation slope for $\alpha25$, a less steep slope for $\alpha5$, and an intermediate slope for our fiducial variation which has $\alpha=1$.}
 
-\snotes{The DWDs in model $q3$ that survive into the LISA band at present day have different formation channels than those of our other three \kb{\sout{models} parameter variations}.
+\textbf{The DWDs in model $q3$ that survive into the LISA band at present day have different formation channels than those of our other three parameter variations.
 Most importantly, the first interaction of these binaries are \emph{not} a CE interaction, but rather a phase of stable mass transfer.
-\kb{\sout{Because of this, }} \kb{we show the CE phase which results from the second interaction for parameter variation $q3$} in Figure \ref{fig:CEsep}.}
+We show the CE phase which results from the second interaction for parameter variation $q3$ in Figure \ref{fig:CEsep}.}
 % because it does not reflect the binary interactions for these simulations.} 
 %All the binaries in the other models have more than one instance of a CE phase during their evolution, and rarely undergo stable mass transfer. 
-\kb{In contrast to two CE phases for the fiducial, $\alpha25$ and $\alpha5$ parameter varitions, the DWD progenitors in parameter variation $q3$ typically undergo a phase of stable mass transfer as the binary's first interaction.} During mass transfer the orbit first shrinks, and then will slightly widen once the binary's mass ratio flips.
+\textbf{In contrast to two CE phases for the fiducial, $\alpha25$ and $\alpha5$ parameter varitions, the DWD progenitors in parameter variation $q3$ typically undergo a phase of stable mass transfer as the binary's first interaction.
+During mass transfer the orbit first shrinks, and then will slightly widen once the binary's mass ratio flips.
 This process leads to formation of the first WD component.
 The companion is then formed later in the binary's evolution through a CE phase.
+}
 %Almost all systems in parameter variation $q3$ undergo only a single CE phase.
 
-\snotes{Of particular interest in $q3$ is the CO + He systems.
-For all of the $q3$ CO + He binaries that \kb{\sout{end up} reside} in the LISA band \kb{at present}, the He WD \sout{unexpectedly} forms first through stable mass transfer, with the CO WD forming second through a CE.
-These binaries tend to all have similar resulting orbital separations from mass transfer, as can be seen by the relatively constant curve for CO + He's $\overline{a}_{\rm{CE}}$.
+\textbf{Of particular interest in variation $q3$ is the CO + He systems.
+For all of the $q3$ CO + He binaries that reside in the LISA band at present, the He WD unexpectedly forms first through stable mass transfer, with the CO WD forming second through a CE.
+These binaries tend to all have similar resulting orbital separations from mass transfer, as can be seen by the relatively constant curve for CO + He's separation at CE onset.
 There is still a slight increasing trend in CO + He (as well as CO + CO and a more pronounced trend in He + He) for $q3$ that stems from the metallicity-dependent convective envelope discussion above.
-We also see that the average interaction separation are overall lower for models $q3$ and $\alpha5$ than for the other two due to the orbital shrinkage that has already occured from stable mass transfer and the efficient CE phase that will lead to minimal orbital shrinkage respectively.}
+We also see that the average interaction separation are overall lower for models $q3$ and $\alpha5$ than for the other two due to the orbital shrinkage that has already occurred from stable mass transfer and the efficient CE phase that will lead to minimal orbital shrinkage respectively.}
 
-%\snotes{Strikeout: [\emph{Note that the average CE separation is close to the qualitative limit for close binaries of $P_{\rm{orb}}\gtrsim10^{4}\,\rm{day}$ for the CO + CO and ONe + X binaries.
+%\textbf{Strikeout: [\emph{Note that the average CE separation is close to the qualitative limit for close binaries of $P_{\rm{orb}}\gtrsim10^{4}\,\rm{day}$ for the CO + CO and ONe + X binaries.
 We investigated the fraction of close DWD progenitors which formed with orbital periods above this range for each DWD type.
@@
 
-While metallicity impacts the intrinsic properties of our simulated DWD populations as described in Sections~\ref{sec:formeff} and \ref{sec:CEsep}, when we consider the present-day Galactic close DWDs we find that the population detectable by LISA changes only numerically.
-The number of DWDs in the LISA frequency band decreases by $\sim50\%$ when comparing model F50 to model FZ \snotes{for variations $\alpha5$ and $q3$, but remain approximately unchanged for our fiducial and $\alpha25$ variations.}
+While metallicity impacts the intrinsic properties of our simulated DWD populations as described in Sections~\ref{sec:formeff} and \ref{sec:CEsep}, when we consider the present-day Galactic close DWDs we find that the population detectable by LISA \textbf{largely only has numerical changes}.
+The number of DWDs in the LISA frequency band decreases by $\sim50\%$ when comparing model F50 to model FZ \textbf{for variations $\alpha5$ and $q3$, but remain approximately unchanged for our fiducial and $\alpha25$ variations.}
 
@@
 	\includegraphics[width=\textwidth]{figures/PSD.pdf}
-    \caption{The PSD of the entire Galactic DWD GW foreground, summed over all metallicities and DWD types vs GW frequency for models FZ and F50.
-The vertical lines show the PSD where model F50 is shown in dark blue and model FZ is shown in light blue.
+    \caption{The PSD of the entire Galactic DWD GW foreground, summed over all metallicities and DWD types vs GW frequency for models FZ and F50\textbf{, where the PSD is downsampled by a factor of $10$ for plotting purposes}.
+\textbf{Each panel shows a different parameter variation} The vertical lines show the PSD where model F50 is shown in dark blue and model FZ is shown in light blue.
 The dashed lines show fits to the rolling boxcar median of width 1000 bins for each PSD (see \ref{sec:LISA_obs} for a discussion).
-A metallicity-dependent binary fraction (model FZ) yields fewer DWDs across all frequencies than a $50\%$ binary fraction (model F50) by roughly a factor of $2$.
-This produces a lower GW confusion foreground for frequencies with f$_{\rm{GW}}\leq\sim10^{-3}$ Hz.}
+A metallicity-dependent binary fraction (model FZ) yields fewer DWDs across all frequencies than a $50\%$ binary fraction (model F50) by roughly a factor of $2$ for the $\alpha5$ and $q3$ parameter variations.
+This produces a lower GW confusion foreground for frequencies with f$_{\rm{GW}}\leq\sim10^{-3}$ Hz.
+\textbf{In contrast, the fiducial and $\alpha25$ parameter variations show very similar confusion foregrounds.}}
     \label{fig:PSD}
@@
 
-Figure \ref{fig:lisa_nums} shows the number of DWDs orbiting with frequencies $f_{\rm{GW}} > 0.1\,\rm{mHz}$ against metallicity for each DWD type \snotes{and parameter variation}.
+Figure \ref{fig:lisa_nums} shows the number of DWDs orbiting with frequencies $f_{\rm{GW}} > 0.1\,\rm{mHz}$ against metallicity for each DWD type \textbf{and parameter variation}.
 The solid lines show DWDs from model FZ, and the dashed lines show DWDs from model F50.
@@
 The largest contribution to the population comes from metallicities above $\sim$ 0.01Z$_\odot$.
-\snotes{Any} discrepancy between the two binary fraction models is also the most significant above this threshold.
-When creating our DWD populations the DWD formation efficiency, number of \textbf{m12i} star particles, and \snotes{metallicity-dependent} binary fraction \snotes{and ZAMS orbital period distribution} all compete.
+\textbf{Any} discrepancy between the two binary fraction models is also the most significant above this threshold.
+When creating our DWD populations the DWD formation efficiency, number of \textbf{m12i} star particles, and \textbf{the metallicity-dependent} binary fraction \textbf{and ZAMS orbital period distribution} all compete.
 The amount of stars formed in \textbf{m12i} at higher metallicity values overwhelms the drop in DWD formation efficiency by multiple orders of magnitude, so this effect dominates when determining the number of stars initially sampled in the population for $f_{\rm{b}}$.
 
-There are two peaks in the distribution of He + He DWDs \snotes{which are most prominent in the fiducial and $\alpha25$ variations, and not as obvious for $\alpha5$ or $q3$.
+There are two peaks in the distribution of He + He DWDs \textbf{which are most prominent in the fiducial and $\alpha25$ variations, and not as obvious for $\alpha5$ or $q3$.
 The prominent first peak in fiducial and $\alpha25$} occurs because near $Z\simeq 0.1Z_\odot$, the DWD formation efficiency transitions from near constant values to a sharp decrease (see Figure \ref{fig:form_eff}).
@@
 Above $Z=Z_\odot$ this overcompensates for the efficiency drop, producing the second peak.
-\snotes{For $\alpha5$ and $q3$, the lack of \kb{\sout{constraints on binary} dramatic orbital shrinking} -- from the increased CE efficiency in the former and increased propensity for stable mass transfer in the latter -- allow for less failed binaries from merging.
+\textbf{For $\alpha5$ and $q3$, the lack of dramatic orbital shrinking -- from the increased CE efficiency in the former and increased propensity for stable mass transfer in the latter -- allow for less failed DWDs due to stellar mergers.
 This leads to less dramatic drops in formation efficiency across metallicity and thus suppressing the formation of two peaks in the number of LISA-band systems.}
 
-\snotes{The $\alpha5$ and $q3$ variations \kb{\sout{have} produce} a higher number of F50 systems than FZ for all DWD types.
+\textbf{The $\alpha5$ and $q3$ variations produce a higher number of F50 systems than FZ for all DWD types.
 This is due to the log-uniform P$_{\rm{orb}}$ distribution of model F50 having more of the shortest-period binaries than the tails of the log-normal distribution of FZ; a discrepancy which becomes more significant with increasing metallicity as the FZ distribution moves from a peak of log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 3-4$ to log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 4-6$.
-This tail is less likely to survive to the LISA band at present for the \kb{\sout{first two} fiducial and $\alpha25$} variations due to the \kb{\sout{harder binary evolution constraints} increased propensity for mergers of DWD progenitors}.
-This \kb{\sout{is why we see essentially} effect produces an} equal number of systems between FZ and F50 for the fiducial and $\alpha25$ variations.
-\kb{In both cases, a}lthough the close binary fraction leads to a greater number of low-metallicity systems, this is compensated for by the FIRE \kb{star particle metallicity} distribution as well as the tendency for the shortest-period DWD progenitors \kb{in model} F50 to merge, essentially washing out all differences between the populations.}
+This tail is less likely to survive to the LISA band at present for the fiducial and $\alpha25$ variations due to the increased propensity for mergers of DWD progenitors.
+This effect produces an equal number of systems between FZ and F50 for the fiducial and $\alpha25$ variations.
+Although the close binary fraction leads to a greater number of low-metallicity systems, this is compensated for by the FIRE star particle metallicity distribution as well as the tendency for the shortest-period DWD progenitors in model F50 to merge, essentially washing out all differences between the populations.}
 
@@
 	\includegraphics[width=\textwidth]{figures/Mc_vs_dist_fiducial.pdf}
-    \caption{The chirp mass vs distance for each DWD type is shown\snotes{ for our fiducial simulation}.
+    \caption{The chirp mass vs distance for each DWD type is shown \textbf{for our fiducial parameter variation}.
 Only systems with observable evolution in their GW frequency, i.e those which are chirping, and with SNR $>7$, are shown, since these are systems for which distance can be separated from chirp mass within their strain amplitude.
@@
 
-\snotes{\sout{The reduced} A change in the} number of DWDs in model FZ relative to model F50 is also apparent in the GW PSD LISA will observe.
+\textbf{A change in the} number of DWDs in model FZ relative to model F50 is also apparent in the GW PSD LISA will observe.
 We show the GW PSD of each model, as well as the confusion forground estimate, in Figure~\ref{fig:PSD}.
-While model F50 (dark blue) and model FZ (light blue) produce several thousand large spikes in the PSD across LISA's frequency band, the overall foreground height, including the confusion, is larger for model F50 \snotes{for parameter variations $\alpha5$ and $q3$}.
+\textbf{We downsample the PSD frequencies by a factor of 10 for plotting purposes.} While model F50 (dark blue) and model FZ (light blue) produce several thousand large spikes in the PSD across LISA's frequency band, the overall foreground height, including the confusion, is larger for model F50 \textbf{for parameter variations $\alpha5$ and $q3$}.
 This is a direct consequence of the overall reduction in the size of the close DWD population in model FZ.
-\snotes{\sout{As we would expect, t}\kb{T}he foreground height remains unchanged for the fiducial and $\alpha25$ variations when comparing models FZ and F50}.
+\textbf{The foreground height remains unchanged for the fiducial and $\alpha25$ variations when comparing models FZ and F50}.
 
@@
 modeled confusion foreground from each population in black, and the the entire population for each model in grey.
-\snotes{Plots for our three parameter variations can be found in Appendix \ref{appendix:ASD_vars}.} Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models.
+\textbf{Plots for our three parameter variations can be found in Appendix \ref{appendix:ASD_vars}.} Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models.
 The populations containing at least one He WD occupy the lower-ASD, higher-GW frequency region of parameter space compared to the total population, with CO + He DWDs having larger ASDs than the He + He DWD population.
@@
 
-We note that the height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 2 for model FZ relative to model F50\snotes{ for variations $\alpha5$ and $q3$}, the number of resolved sources is not reduced to an equal degree.
-\snotes{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.
-For the fiducial and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ \kb{\sout{do not change much}} are reduced by 4.5\% and increased by 3\% respectively.
+We note that the height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 2 for model FZ relative to model F50 \textbf{for variations $\alpha5$ and $q3$}, the number of resolved sources is not reduced to an equal degree.
+\textbf{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.
+For the fiducial and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ are reduced by 4.5\% and increased by 3\% respectively.
 However, for $\alpha5$ the number of resolvable DWDs is reduced by only 26\%, and the number of resolvable DWDs $q3$ remains almost \emph{unchanged}, with a 1\% reduction even though the overall LISA population of both variations is halved.
@@
 
-%\snotes{[\emph{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.}][$\leftarrow$ moved to beginning of paragraph] Strikeout: [\emph{Between models FZ and F50, the number of resolvable systems with SNR $>7$ over all DWD types decreases by only $\sim14\%$.}]}
+%\textbf{[\emph{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.}][$\leftarrow$ moved to beginning of paragraph] Strikeout: [\emph{Between models FZ and F50, the number of resolvable systems with SNR $>7$ over all DWD types decreases by only $\sim14\%$.}]}
 
@@
 Assuming a chirp resolution of $1/T_{\rm{obs}}^2 \sim 8\times10^{-9}\,\rm{Hz}^2$, we select the DWDs whose chirp masses and distances can be measured.
-Figure \ref{fig:Mc_vs_dist} shows the chirp mass vs the luminosity distance for each DWD type in this selected population \snotes{for the fiducial simulation.
-The same figure for our three variations is shown in Appendix \ref{appendix:Mc_dist_vars}}.
+Figure \ref{fig:Mc_vs_dist} shows the chirp mass vs the luminosity distance for each DWD type in this selected population \textbf{for the fiducial variation.
+The same figure for our other three parameter variations is shown in Appendix \ref{appendix:Mc_dist_vars}}.
 The contours show the $5^{\rm{th}}$, $25^{\rm{th}}$, $50^{\rm{th}}$, $75^{\rm{th}}$, and $95^{\rm{th}}$ percentiles for models FZ (light blue) and F50 (dark blue, dashed).
 Despite the reduction in the height of the confusion foreground when considering model FZ relative to F50, we find that LISA is unable to differentiate between the chirp mass -- distance distributions of the two models.
-\snotes{For $\alpha25$ we plot these as scatter plots for He + He and ONe + X due to low statistics since there are so few binaries in this selected population.
-The only population with a significant change between models is for ONe + X's $\alpha5$ distributions, where we see a skew to lower masses.
-This is because a higher fraction of the binaries are ONe + He (in which Helium WDs tend to have smaller masses) for FZ than F50 -- a Helium companion makes up 10\% of this selected population for F50 compared with 44\% for FZ.
-Furthermore, $\sim8$\% of the F50 measurable systems are ONe + ONe binaries, versus 0\% for FZ.
-Because ONe WDs have larger masses, this also creates the high-mass concentration we see in the F50 contours.}
 
-\section{\snotes{\sout{Binary evolution \textbf{parameter variations}} Galactic DWD Confusion Foreground Discussion}}
+\section{\textbf{Galactic DWD Confusion Foreground Discussion}}
 \label{sec:model_compare}
@@
 The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for model FZ to model F50 vs to number of DWDs orbiting in the LISA band for model F50 only.
-While both the height of the confusion foreground and number of LISA DWDs changes for each variation, the FZ models within each variation exhibit \snotes{either no change or }a constant reduction by a factor of two compared with the F50 models.}
+While both the height of the confusion foreground and number of LISA DWDs changes for each variation, the FZ models within each variation exhibit \textbf{either very little change or }a  near-constant reduction by a factor of two compared with the F50 models.}
     \label{fig:model_comp}
@@
 
-\snotes{Strikeout: [\emph{In order to test the robustness of the reduction of the height of the Galactic DWD GW foreground when assuming a metallicity-dependent binary fraction, we repeat our analysis using three different binary evolution \textbf{parameter variations}.}]}
+%\textbf{Strikeout: [\emph{In order to test the robustness of the reduction of the height of the Galactic DWD GW foreground when assuming a metallicity-dependent binary fraction, we repeat our analysis using three different binary evolution \textbf{parameter variations}.}]}
 
-\snotes{[For each variation, we consider models FZ and F50 as done in the fiducial case described above.
+%\textbf{[For each parameter variation, we consider models FZ and F50 as done in the fiducial case described above.
 In variation $q3$, we vary the assumption for the critical mass ratios at which a RLO interaction remains stable or becomes unstable from our fiducial assumptions such that the critical mass ratio is increased to $3.0$ and thus allows stable mass transfer for more massive RLO donors.
@@
 
-In each variation, changing the binary evolution assumptions dramatically changes the formation and evolution of the DWD populations.
+In each parameter variation, changing the binary evolution assumptions dramatically changes the formation and evolution of the DWD populations.
 These changes lead to large shifts in the overall number of close DWDs in our synthetic present-day Milky-Way-like galaxies.
@@
 
-Interestingly, when we compare the populations of each binary fraction model for our variations, we find that the number of close DWDs \snotes{Strikeout: [\emph{reduces by the constant factor of two as seen in our fiducial set of assumptions.}] remains approximately unchanged for our fiducial set of assumptions and $\alpha25$ variation, but is reduced by 50\% for variations $\alpha5$ and $q3$.} This is illustrated in Figure \ref{fig:model_comp}.
+Interestingly, when we compare the populations of each binary fraction model for our variations, we find that the number of close DWDs %\textbf{Strikeout: [\emph{reduces by the constant factor of two as seen in our fiducial set of assumptions.}]
+\textbf{remains approximately unchanged for our fiducial set of assumptions and $\alpha25$ variation, but is reduced by 50\% for variations $\alpha5$ and $q3$.} This is illustrated in Figure \ref{fig:model_comp}.
 The top panel shows the confusion foreground fits for each binary evolution variation (different colored lines) and for each binary fraction model where the solid lines show FZ models and dotted lines show F50 models.
 The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for the FZ models vs the F50 models for each variation.
-\snotes{\sout{Even though} The} number of DWDs in the LISA band spans over two orders of magnitude, \snotes{and} the ratio of FZ to F50, as well as the spectral shape of the confusion fit, \snotes{\sout{stays fixed at a constant factor of two reduction} is either relatively unchanged or reduced by a factor of approximately two}.
-This suggests that assuming a metallicity-dependent binary fraction \snotes{\sout{reduces} may change} the size of the Galactic close DWD population by a factor of $\sim$two and the strength of the Galactic DWD GW foreground for LISA \snotes{\sout{\emph{regardless of the chosen binary evolution model}} depending on the chosen binary evolution model.}
+\textbf{The} number of DWDs in the LISA band spans over two orders of magnitude, \textbf{and} the ratio of FZ to F50, as well as the spectral shape of the confusion fit, \textbf{is either relatively unchanged or reduced by a factor of approximately two}.
+This suggests that assuming a metallicity-dependent binary fraction \textbf{may change} the size of the Galactic close DWD population by a factor of $\sim$two and the strength of the Galactic DWD GW foreground for LISA \textbf{depending on the chosen binary evolution model.}
 
@@
 However, when considering the close DWD populations observable by LISA, we find that the only distinguishing features between models which assume a metallicity-dependent binary fraction (model FZ) and models which assume a flat $50\%$ binary fraction (model F50) are the population sizes and the strength of the Galactic DWD GW foreground.
-Models which assume a metallicity-dependent binary fraction produce Galactic DWD populations that \snotes{\sout{are reduced by a factor of two} were unchanged} relative to the standard model assumptions.
-\snotes{However, our results are highly dependent on the chosen binary evolution model.
+Models which assume a metallicity-dependent binary fraction produce Galactic DWD populations that \textbf{were unchanged} relative to the standard model assumptions.
+\textbf{However, our results are highly dependent on the chosen binary evolution model.
 We extended our study to include three binary evolution \textbf{parameter variations} to investigate the sensitivity of the DWD population changes in assumptions for mass transfer stability and common envelope ejection efficiencies.
 While our binary evolution parameter variations change the size of the LISA-observable populations dramatically, the size of the close Galactic DWD population and the height of the confusion foreground for models which assume a metallicity-dependent binary fraction appears to either remain unchanged \emph{or} be reduced by 50\%.} This reduction extends to the height of the confusion foreground in the LISA data stream.
-\snotes{These two results highlight the interplay between our dominating distributions (from the FIRE star formation history, metallicity-dependent ZAMS orbital period, and subsequent metallicity-dependent binary fraction) and physics constraints on LISA DWD formation, and serves to emphasize the sensitivity of the Galactic population of LISA-detectable DWDs to the intricacies of binary evolution.
-Values like CE efficiency are undergoing continuous study in current literature and an exact value has yet to be identified.
-We hope by exploring a range of possibilities in this work, we can capture the variation in predictions of the LISA DWD population that may be observed.}
+\textbf{These two results highlight the interplay between the dominating factors which shape the LISA DWD population: the metallicity-dependent star formation history of the \textbf{m12i} galaxy, the metallicity-dependent close binary fraction which alters the ZAMS orbital period distribution, and the impact of binary evolution assumptions on DWD formation.
+This comparison emphasizes the sensitivity of the Galactic population of LISA-detectable DWDs to the intricacies of binary evolution.
+Binary evolution assumptions like CE efficiency are undergoing continuous study in current literature and an exact value has yet to be identified.
+By exploring a range of possibilities in this work, we capture the variation in predictions of the LISA DWD population that may be observed.}
 
-\snotes{Strikeout: [\emph{We extended our study to include three binary evolution \textbf{parameter variations} to investigate whether the DWD population reduction was robust to changes in assumptions for mass transfer stability and common envelope ejection efficiencies.
-While our binary evolution \textbf{parameter variations} change the size of the LISA-observable populations dramatically, the reduction in the size of the close Galactic DWD population and the height of the confusion foreground for models which assume a metallicity-dependent binary fraction is robust.}]$\leftarrow$[moved/edited into above paragraph]} An important consequence of a lower Galactic DWD confusion foreground is that relative to the total DWD population, more DWDs can be individually resolved because of the reduction in competing GW signals.
-While the number of DWDs radiating GWs in the LISA frequency band is reduced by a factor of two for model FZ relative to model F50 \snotes{for variations $\alpha25$ and $q3$}, the number of resolved sources is less affected with a population-wide reduction of $26\%$ \snotes{for the former, and surprisingly only by 1\% for the latter}.
+%\textbf{Strikeout: [\emph{We extended our study to include three binary evolution \textbf{parameter variations} to investigate whether the DWD population reduction was robust to changes in assumptions for mass transfer stability and common envelope ejection efficiencies.
+While our binary evolution \textbf{parameter variations} change the size of the LISA-observable populations dramatically, the reduction in the size of the close Galactic DWD population and the height of the confusion foreground for models which assume a metallicity-dependent binary fraction is robust.}]$\leftarrow$[moved/edited into above paragraph]}
+An important consequence of a lower Galactic DWD confusion foreground is that relative to the total DWD population, more DWDs can be individually resolved because of the reduction in competing GW signals.
+While the number of DWDs radiating GWs in the LISA frequency band is reduced by a factor of two for model FZ relative to model F50 \textbf{for variations $\alpha25$ and $q3$}, the number of resolved sources is less affected with a population-wide reduction of $26\%$ \textbf{for the former, and surprisingly only by 1\% for the latter}.
 These results are far-reaching since the strength of the Galactic DWD confusion foreground has direct consequences on the detectability of all other LISA sources with small SNRs.
-An increase in resolution capability from the reduced confusion foreground can be extended to other galactic binaries that LISA will observe at these frequencies like those involving neutron stars and stellar-origin black holes, as well as other more exotic GW sources like merging supermassive black holes, extreme mass ratio inspirals, or cosmological GW backgrounds.
-Based on our results, we suggest that studies which employ fits to the confusion foreground based on population synthesis results consider reducing the strength of the Galactic foreground PSD by a factor of two \snotes{depending on the chosen binary evolution model}.
+An increase in resolution capability from the reduced confusion foreground can be extended to other Galactic binaries that LISA will observe at these frequencies like those involving neutron stars and stellar-origin black holes, as well as other more exotic GW sources like merging supermassive black holes, extreme mass ratio inspirals, or cosmological GW backgrounds.
+Based on our results, we suggest that studies which employ fits to the confusion foreground based on population synthesis results consider reducing the strength of the Galactic foreground PSD by a factor of two \textbf{depending on the chosen binary evolution model}.
 
@@
 
+Figure \ref{fig:LISA_SNR_vars} shows the ASD vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the rows alternate between models F50 and FZ for the $\alpha25$, $\alpha5$, and $q3$ parameter variations.
+The LISA sensitivity curve is also shown in black, which includes the modeled confusion foreground from each population in black.
+The entire population is shown as grey scatter points.
+As discussed in Section \ref{sec:LISA_met}, apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models.
+
+The height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 2 for model FZ relative to model F50 for variations $\alpha5$ and $q3$, however the number of resolved sources is not reduced to an equal degree.
+The number of observable systems with SNR $>7$ increases by 3\% for $\alpha25$.
+For $\alpha5$ the number of resolvable DWDs is reduced by only 26\%, and the number of resolvable DWDs $q3$ only experiences a 1\% reduction even though the overall LISA population of both variations is halved.
+A large portion of the maintenance of the number of DWDs in parameter variation $q3$ is contributed to by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).
+
 \begin{figure*}[h]
@@
 	\includegraphics[width=0.8\textwidth]{figures/LISA_SNR_q3.pdf}
-    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for each DWD type \snotes{and variation}.\snotes{\sout{ where the top row shows} The rows alternate between \sout{ the population from}} model FZ and \snotes{\sout{the bottom row shows the population}} from model F50.
+    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for each DWD type and parameter variation.
+The rows alternate between model F50 and from model FZ.
 In each panel, the LISA sensitivity curve, including the confusion foreground for each model, is shown in black and the total population for each model is shown in grey.
-\snotes{Again, w}e find that each model qualitatively exhibits similar characteristics and that the only change is in the yield of resolved DWDs for each type based on the strength of the confusion foreground.}
+Again, we find that each model qualitatively exhibits similar characteristics and that the only change is in the yield of resolved DWDs for each type based on the strength of the confusion foreground.}
     \label{fig:LISA_SNR_vars}
@@
 \section{Chirp Mass -- Distance Distributions for Binary Evolution Parameter Variations}\label{appendix:Mc_dist_vars}
+
+Figure~\ref{fig:Mc_vs_dist_vars} shows the chirp mass vs distance distribution for the $\alpha25$, $\alpha5$, and $q3$ parameter variations.
+For $\alpha25$ we plot scatter plots for He + He and ONe + X due to low statistics since there are too few binaries in this selected population to produce reliable kernel density estimates.
+The only population with a significant change between each variation is for ONe + X DWDs where $\alpha5$.
+Here, we see a skew to lower masses because a higher fraction of the binaries are ONe + He for FZ than F50 -- a Helium companion makes up 10\% of this selected population for F50 compared with 44\% for FZ.
+This leads to lower average chirp masses for the ONe + X distribution.
+Furthermore, $\sim8$\% of the F50 measurable systems are ONe + ONe binaries, versus 0\% for FZ.
+Because ONe WDs have larger masses, this also creates the high-mass concentration we see in the F50 contours.
 \begin{figure*}[h]
@@
 	\includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_q3.pdf}
-    \caption{chirp mass distance distributions}
+    \caption{Chirp mass -- distance distributions for our other three binary evolution parameter variations.
+We plot the $\alpha25$ populations of He + He and ONe + X DWDs as scatter points since there are too few binaries to produce meaningful density distributions.
+Again, we have plotted each DWD type's population that exhibit observable GW frequency evolution and have SNR$>7$.
+Contours show the 5$^{\rm{th}}$, 25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$ and 95$^{\rm{th}}$ percentiles.
+Most populations remain unchanged between binary fraction models except for ONe + X DWDs in $\alpha5$, due to the number of He vs.
+CO vs.
+ONe companions between each model.}
     \label{fig:Mc_vs_dist_vars}

### 2022-09-01 src/tex/ms.tex
text edits

@@
 \shorttitle{Applying a metallicity-dependent binary fraction to DWD formation}
-\shortauthors{Thiele, Breivik, \& Sanderson}
+\shortauthors{Thiele et al.}
 
@@
 \affiliation{Canadian Institute for Theoretical Astrophysics, University
-of Toronto, 60 St. George Street, Toronto, ON, M5S 1A7,
+of Toronto, 60 St. George Street, Toronto, Ontario, M5S 1A7,
 Canada}
@@
 \affiliation{Department of Physics and Astronomy, University of Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
+\author[0000-0002-0296-3826]{Rodrigo Luger}
 \affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
@@
 However, the size of the total Galactic DWD population orbiting in the LISA frequency band is reduced by more than half when accounting for a metallicity-dependent binary fraction \textbf{for two of our four variations.} This effect lowers the confusion foreground, effectively increasing the sensitivity for detecting all types of low-frequency LISA sources.
-\textbf{The LISA population remains unchanged in number for two variations, highlighting the sensitivity of the population to binary evolution prescriptions.} %KB: I think this is a good choice!\textbf{Strikeout: [\emph{We repeat our analysis for three different assumptions for Roche-lobe overflow interactions and find the population reduction to be robust when a metallicity-dependent binary fraction is assumed.}]}
+\textbf{The LISA population remains unchanged in number for two variations, highlighting the sensitivity of the population to binary evolution prescriptions.}
 \end{abstract}
@@
 
-\textbf{Figure \ref{fig:met_dep_porb}, shows the companion frequency f$_{\rm{logP}}$ for solar-type stars as a function of the logarithm of orbital period, mirroring the inner binaries curve of Figure 2 in \citet{Moe2021} and scaling to an overall multiplicity frequency of 0.67 (equivalent to an integrated binary fraction of 50\%) at solar metallicity.
+\textbf{Figure \ref{fig:met_dep_porb} shows the companion frequency f$_{\rm{logP}}$ for solar-type stars as a function of the logarithm of orbital period, mirroring the inner binaries curve of Figure 2 in \citet{Moe2021} and scaling to an overall multiplicity frequency of 0.67 (equivalent to an integrated binary fraction of 50\%) at solar metallicity.
 To obtain the normalization of the companion frequency for close binaries (P$_{\rm{orb}}<10^4$),} we fit the results presented in \citet{Moe2019} using linear regression to obtain a piecewise relation between the metallicity, [Fe/H] and \text{close} binary fraction $f_{\rm{b}}$ as
@@
 We show curves for all 15 of our metallicity bins, increasing in metallicity from darkest to lightest curve colour.
-The lowest metallicity ([Fe/H]=-2.3) shows the highest propensity for short-period binaries, in contrast to higher metallicity systems which have a frequency distribution that has a relatively constant companion frequency for orbital periods between $10^4$ and $10^6$ days.}
+The lowest metallicity ([Fe/H]=-2.3) shows the highest propensity for short-period binaries, in contrast to higher metallicity systems which have a frequency distribution with a relatively constant companion frequency for orbital periods between $10^4$ and $10^6$ days.}
 
-\textbf{While we simulate binaries across the entire orbital period distribution, the close binary fraction, which exhibits the discussed metallicity dependence, will be that which impacts the LISA population as systems with $\log_{10}(\rm{P}_{\rm{orb}}/$day)$>4$ will be unlikely to evolve enough to enter the LISA band by present day.}
+\textbf{While we simulate binaries across the entire orbital period distribution, the close binary fraction, which exhibits the discussed metallicity dependence, will be that which impacts the LISA population since systems with $\log_{10}(\rm{P}_{\rm{orb}}/$day)$>4$ will be unlikely to evolve enough to enter the LISA band by present day.}
 
@@
 
-The metallicity-dependent \textbf{close} binary fraction \textbf{for solar-type binaries (P $< 10^4$ days), or simply the close binary fraction from here on, }% S: Should I change all instances of "binary fraction" to "close binary fraction" then?
-%KB: I will keep an eye out to make the changes
-is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid.
+The metallicity-dependent \textbf{close} binary fraction \textbf{for solar-type binaries (P $< 10^4$ days), or simply the close binary fraction from here on, } is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid.
 The \textbf{close} binary fraction, $f_{\rm{b}}$, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly.
@@
 \noindent where $h_c$ is the characteristic strain of the system, $S_n(f)$ is the LISA sensitivity curve of \citet{Robson2019}, and the frequency limits are determined by the orbital evolution over the observation time, $T_{\rm{obs}}=4\,\rm{yr}$.
-The characteristic strain for %DWDs
-circular orbits is 
+The characteristic strain for circular orbits is
 \begin{equation}
@@
 \end{equation}
-\noindent and $x=\log_{10}(f_{\rm{GW}}/\rm{Hz})$. We add the fitted polynomial of the PSD's running median to the LISA noise PSD to obtain a sensitivity curve for each model \textbf{and variation}.
+\noindent and $\rm{x}=\log_{10}(f_{\rm{GW}}/\rm{Hz})$.
+We add the fitted polynomial of the PSD's running median to the LISA noise PSD to obtain a sensitivity curve for each model \textbf{and variation}.
 
@@
 The dashed lines indicate the formation efficiency for model F50, which assumes a constant binary fraction of $50\%$.
-The DWD formation efficiency drops by a factor of $4-5$ for model FZ and a factor of %\textbf{\sout{2-5}
-    \textbf{1-5} for model F50. See Section~\ref{sec:formeff} for a careful description of the trends for each DWD type.}
+The DWD formation efficiency drops by a factor of $4-5$ for model FZ and a factor of \textbf{1-5} for model F50.
+See Section~\ref{sec:formeff} for a careful description of the trends for each DWD type.}
     \label{fig:form_eff}
@@
 	\includegraphics[width=\textwidth]{figures/CEsep.pdf}
-    \caption{Average interaction separation, $\overline{\mathrm{a}}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type \textbf{and variation} from model FZ.
+    \caption{Average interaction separation, $\overline{\mathrm{a}}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type \textbf{and variation} from model F50.
 Solid lines show the average separation at the first RLO for binaries in each metallicity bin.
@@
 The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts.
-The sharp drop of the CO + CO average at the highest-metallicity bin \textbf{of the fiducial variation} is due to binning effects of the figure: it only contains 115 systems, of which the majority stem from a single low-separation system which was sampled 94 times times during the simulation.
+The sharp drop of the CO + CO average at the highest-metallicity bin \textbf{of the fiducial variation} is due to binning effects of the figure: it only contains \textbf{506} systems, of which the majority stem from a single low-separation system which was sampled \textbf{468} times times during the simulation.
 \textbf{The regions of metallicity where there is not shading beyond the mean trend are also due to low numbers of DWDs in each bin}.}
@@
 
-For short-period CO + He DWD progenitor binaries with orbital periods below $\sim30~\rm{days}$, the only channel for \kb{stellar} mergers before DWD formation is during a CE evolution.
+For short-period CO + He DWD progenitor binaries with orbital periods below $\sim30~\rm{days}$, the only channel for \textbf{stellar} mergers before DWD formation is during a CE evolution.
 This channel is similar to the stellar merger channel for He + He DWDs, but due to higher-mass progenitors the CE evolution results in the binary component with a higher mass becoming a CO WD.
@@
 For CO + He DWD progenitor systems with intermediate orbital periods ($1.5\leq \log_{10}(P_{\rm{orb}}/\rm{day})< 2.5$) the mechanisms which impact formation efficiency are complex.
-The dominant way to % R: lose
-\textbf{not form} CO + He DWDs is stellar mergers that occur during the second CE phase.
+The dominant way to \textbf{not form} CO + He DWDs is stellar mergers that occur during the second CE phase.
 For lower-metallicity systems, the second CE is successful, while the opposite is true for higher-metallicity systems.
@@
 \textbf{For binary systems leading to He + He DWDs, there are many more mergers for $\alpha25$ than for the fiducial variation.
-The lower CE efficiency leads to DWD progenitor mergers from failed CE ejection, or the CE shrinking the orbit such that it then merges on the second CE phase.
+The lower CE efficiency leads to DWD progenitor mergers from a failed CE ejection, or the CE shrinking the orbit such that it then merges on the second CE phase.
 Because there are more ZAMS binaries with orbital periods shorter than $10^4$ days in F50, as the population evolves there are more likely to be binary interactions in the population for F50 than FZ.
@@
 These later interactions lead to closer post-CE separations and thus more mergers.
-The dip at [Fe/H] $\simeq -1.5\%$ stems from mergers before the DWD forms, again similar to the fiducial parameter variation.
+The dip at [Fe/H] $\simeq -1.5$ stems from mergers before the DWD forms, again similar to the fiducial parameter variation.
 The peak that occurs in $\alpha25$ at $\sim 10\%$ Z$_\odot$ arises from binaries evolving faster and thus interacting earlier as metallicity increases.
@@
 
-\textbf{Beyond the effects described above, the efficiency drop across metallicity is similar to the fiducial parameter variation in that it depends on the metallicity-dependent ZAMS orbital period distribution emphasizing short-period systems at low metallicities, and in the change of formation channel for different period ranges across metallicity.
+\textbf{Beyond the effects described above, the efficiency drop across metallicity is similar to the fiducial parameter variation in that it depends on the metallicity-dependent ZAMS orbital period distribution emphasizing short-period systems at low metallicities, and on the change of formation channel for different period ranges across metallicity.
 We find the highest formation efficiency for variation $q3$.
@@
 At low metallicities, a number of progenitor binaries form CO + CO DWDs instead of He + CO DWDs.
-This is especially the case in near $\log_{10}$(Z/Z$_\odot)\sim -2$, where RLO occurs late enough in a binary's evolution that mass transfer remains stable and CO + CO's are formed rather than CO + He, hence producing a dip in the formation efficiency.
+This is especially the case near $\log_{10}$(Z/Z$_\odot)\sim -2$, where RLO occurs late enough in a binary's evolution that mass transfer remains stable and CO + CO's are formed rather than CO + He, hence producing a dip in the formation efficiency.
 Because parameter variation $\alpha5$ leads to less mergers due to the high CE efficiency, the formation efficiency is mostly governed by the metallicity-dependent ZAMS orbital period distribution.
-At higher metallicities the majority of cases in model FZ where progenitors don't produce a CO + He DWD are due to progenitor mergers or to He + He DWDs forming instead of CO + He DWDs.} %due to the faster evolution at high metallicities and increasing radii inducing earlier binary interactions and hence stripping of both star's envelopes [$\leftarrow$ is this correct logic?].
-I think this is already discussed above for fiducial so we don't need to worry about it.
-\textbf{At higher metallicities, the ZAMS orbital period distribution of FZ also drops below the orbital period distribution of F50 and extends out to orbital periods beyond what would form a CO + He.
+At higher metallicities, the majority of cases in model FZ where progenitors don't produce a CO + He DWD are from progenitor mergers or from He + He DWDs forming instead of CO + He DWDs.
+At higher metallicities, the ZAMS orbital period distribution of FZ also drops below that of F50 and extends out to orbital periods beyond what would form a CO + He.
 This causes the formation efficiencies for FZ and F50 to cross at log$_{10}$(Z/Z$_\odot$)$\sim-0.5$.
-This is also apparent for the $q3$ variation, and to a lesser extent in the fiducial case.} %Any lost systems in $q3$ also is contributed to by: (i) some binaries at high metallicities not forming a CO + He DWD by present day due to envelope-stripping timescales being delayed by phases of stable mass transfer, (ii) mergers, and (ii) ONe + X DWDs forming instead.
-\textbf{In $q3$, for any given orbital period we find that lower mass DWDs originate from lower metallicities, thus leading to an approximately constant formation efficiency.}
+This is also apparent for the $q3$ variation, and to a lesser extent in the fiducial case.
+In $q3$, for any given orbital period we find that lower mass DWDs originate from lower metallicities, thus leading to an approximately constant formation efficiency.}
 
 \textbf{For CO + CO, across all variations, very close ZAMS binaries (P$_{\rm{orb}}\sim\mathcal{O}(100$ days)) at high metallicities form a CO + He or He + He DWD instead of a CO + CO because the binary interacts before core Helium burning of one or both components.
-}
-%lost at high metallicities when a binary that would form a CO + CO at low metallicities forms a CO + He or He + He DWD instead 
-\textbf{There are again many more mergers in $\alpha25$, and fewer mergers for $\alpha5$.
+There are again many more mergers in $\alpha25$, and fewer mergers for $\alpha5$.
 Due to the high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods survive to become CO + CO DWDs rather than merging or becoming CO + He or He + He DWDs.
@@
 \textbf{For model FZ, the ONe + X formation efficiencies follow similar trends aross each parameter variation.
-Their formation scenarios are similar to those described above for the fiducial binary evolution parameter set.
+Their formation scenarios are similar to those described above for ONe + X DWDs in the fiducial binary evolution parameter set.
 The main difference between each parameter variation is only in the number of sources produced since the number of stellar mergers that occur before DWD formation increases with decreasing common envelope efficiency.
 In model F50, the formation efficiency is decreased significantly for parameter variation $\alpha25$ because the log-uniform orbital period distribution produces many ZAMS binaries with very short orbital periods which lead to stellar mergers during the CE phases.}
-
-% Reworked this into the paragraph above.
-%\textbf{[** Might need to fact check this paragraph **] The FZ curves for ONe + X are relatively similar amongst variations beyond height, and the loss of systems is the same as described for the \kb{fiducial variation}.
-We have more mergers once again for $\alpha25$, which lowers the F50 curve below FZ because F50 has the shortest-ZAMS-period end that FZ does not have.
-$\alpha5$ and $q3$ show F50 efficiencies with a very shallow slope due to the flat orbital period distribution, as well as due to less mergers overall.}
 
@@
 	\includegraphics[width=\textwidth]{figures/lisa_nums.pdf}
-    \caption{The number of LISA-band systems formed for each DWD type as a function of the base-10 logarithm of metallicity, normalized to solar value.
+    \caption{The number of LISA-band systems formed for each DWD type \textbf{and parameter variation} as a function of the base-10 logarithm of metallicity, normalized to solar value.
 The solid line shows the FZ population with a metallicity-dependent \textbf{close} binary fraction incorporated, and the dashed line shows the F50 population for a standard binary fraction of 0.5.
@@
 This is true even for model FZ, which drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond Z$\simeq$Z$_\odot$.
-There is a double peak in the \textbf{fiducial and $\alpha25$} He + He populations; the first peak is caused by the sharp drop in formation efficiency past Z$\simeq$0.1$Z_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
+There is a double peak in the \textbf{fiducial and $\alpha25$} He + He populations; the first peak is caused by the sharp drop in formation efficiency past $\rm{Z}\simeq0.1 \rm{Z}_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
     \label{fig:lisa_nums}
@@
 \textbf{The slope of the increase for these three models is dictated by the CE efficiency $\alpha$.
-With increasing metallicity there is a deepening of the convective envelope of the star compared to its lower metallicity counterparts at the same point in its evolution,} %[is this the first time this idea is introduced?
-need to check], \KB I think this is ok!
-\textbf{requiring more orbital energy to be available in order to eject the CE.
+With increasing metallicity there is a deepening of the convective envelope of the star compared to its lower metallicity counterparts at the same point in its evolution, requiring more orbital energy to be available in order to eject the CE.
 Thus the high-metallicity binaries must have even wider separations for lower $\alpha$ values to ensure the binary does not merge before the envelope is ejected.
-We thus see a steeper separation slope for $\alpha25$, a less steep slope for $\alpha5$, and an intermediate slope for our fiducial variation which has $\alpha=1$.}
+We therefore see a steeper separation slope for $\alpha25$, a less steep slope for $\alpha5$, and an intermediate slope for our fiducial variation which has $\alpha=1$.}
 
 \textbf{The DWDs in model $q3$ that survive into the LISA band at present day have different formation channels than those of our other three parameter variations.
-Most importantly, the first interaction of these binaries are \emph{not} a CE interaction, but rather a phase of stable mass transfer.
-We show the CE phase which results from the second interaction for parameter variation $q3$ in Figure \ref{fig:CEsep}.}
-% because it does not reflect the binary interactions for these simulations.} 
-%All the binaries in the other models have more than one instance of a CE phase during their evolution, and rarely undergo stable mass transfer. 
-\textbf{In contrast to two CE phases for the fiducial, $\alpha25$ and $\alpha5$ parameter varitions, the DWD progenitors in parameter variation $q3$ typically undergo a phase of stable mass transfer as the binary's first interaction.
+Most importantly, in contrast to two CE phases for the fiducial, $\alpha25$ and $\alpha5$ parameter variations, the DWD progenitors in parameter variation $q3$ typically undergo a phase of stable mass transfer as the binary's first interaction.
 During mass transfer the orbit first shrinks, and then will slightly widen once the binary's mass ratio flips.
@@
 The companion is then formed later in the binary's evolution through a CE phase.
-}
-%Almost all systems in parameter variation $q3$ undergo only a single CE phase.
+We show the CE phase which results from the second interaction for parameter variation $q3$ in Figure \ref{fig:CEsep}.}
 
@@
 There is still a slight increasing trend in CO + He (as well as CO + CO and a more pronounced trend in He + He) for $q3$ that stems from the metallicity-dependent convective envelope discussion above.
-We also see that the average interaction separation are overall lower for models $q3$ and $\alpha5$ than for the other two due to the orbital shrinkage that has already occurred from stable mass transfer and the efficient CE phase that will lead to minimal orbital shrinkage respectively.}
-
-%\textbf{Strikeout: [\emph{Note that the average CE separation is close to the qualitative limit for close binaries of $P_{\rm{orb}}\gtrsim10^{4}\,\rm{day}$ for the CO + CO and ONe + X binaries.
-We investigated the fraction of close DWD progenitors which formed with orbital periods above this range for each DWD type.
-For the He + He DWDs, less than $10\%$ of all progenitors, regardless of metallicity originate in wide orbits.
-For CO + He population, the percentage increases from $10$--$15\%$ from low to high metallicities, and for the more massive CO + CO and ONe + X DWDs, the percentages increase from $15$--$25\%$ and $20$--$40\%$ respectively.
-This suggests that our application of the close binary fraction may not be valid over the entire range of the DWD progenitor population.
-However, since the relative sizes of CO + CO and ONe + X are small compared to the He + He and CO + He populations, we leave a further investigation of these effects to a future study.}] [$\leftarrow$ I think we can take out this whole paragraph since we now take this into account!]} \kb{agreed!}
+We also see that the average interaction separation are overall lower for variations $q3$ and $\alpha5$ than for the other two due to the orbital shrinkage that has already occurred from stable mass transfer and the efficient CE phase that will lead to minimal orbital shrinkage respectively.}
 
@@
 
-While metallicity impacts the intrinsic properties of our simulated DWD populations as described in Sections~\ref{sec:formeff} and \ref{sec:CEsep}, when we consider the present-day Galactic close DWDs we find that the population detectable by LISA \textbf{largely only has numerical changes}.
-The number of DWDs in the LISA frequency band decreases by $\sim50\%$ when comparing model F50 to model FZ \textbf{for variations $\alpha5$ and $q3$, but remain approximately unchanged for our fiducial and $\alpha25$ variations.}
+While metallicity impacts the intrinsic properties of our simulated DWD populations as described in Sections~\ref{sec:formeff} and \ref{sec:CEsep}, when we consider the present-day Galactic close DWDs we find that the population detectable by LISA \textbf{largely only changes numerically}.
+The number of DWDs in the LISA frequency band decreases by $\sim50\%$ when comparing model F50 to model FZ \textbf{for variations $\alpha5$ and $q3$, but remains approximately unchanged for our fiducial and $\alpha25$ variations.}
 
@@
     \caption{The PSD of the entire Galactic DWD GW foreground, summed over all metallicities and DWD types vs GW frequency for models FZ and F50\textbf{, where the PSD is downsampled by a factor of $10$ for plotting purposes}.
-\textbf{Each panel shows a different parameter variation} The vertical lines show the PSD where model F50 is shown in dark blue and model FZ is shown in light blue.
-The dashed lines show fits to the rolling boxcar median of width 1000 bins for each PSD (see \ref{sec:LISA_obs} for a discussion).
+\textbf{Each panel shows a different parameter variation.} The vertical lines show the PSD where model F50 is shown in dark blue and model FZ is shown in light blue.
+The dashed lines show fits to the rolling boxcar median of width 1000 bins for each PSD (see Section \ref{sec:LISA_obs} for a discussion).
 A metallicity-dependent binary fraction (model FZ) yields fewer DWDs across all frequencies than a $50\%$ binary fraction (model F50) by roughly a factor of $2$ for the $\alpha5$ and $q3$ parameter variations.
@@
 	\includegraphics[width=\textwidth]{figures/LISA_SNR_fiducial.pdf}
-    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for each DWD type where the top row shows the population from model FZ and the bottom row shows the population from model F50.
+    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for each DWD type where the top row shows the population from model F50 and the bottom row shows the population from model FZ \textbf{for the fiducial variation}.
 In each panel, the LISA sensitivity curve, including the confusion foreground for each model, is shown in black and the total population for each model is shown in grey.
@@
 \textbf{For $\alpha5$ and $q3$, the lack of dramatic orbital shrinking -- from the increased CE efficiency in the former and increased propensity for stable mass transfer in the latter -- allow for less failed DWDs due to stellar mergers.
-This leads to less dramatic drops in formation efficiency across metallicity and thus suppressing the formation of two peaks in the number of LISA-band systems.}
+This leads to less dramatic drops in formation efficiency across metallicity which thus suppresses the formation of two peaks in the number of LISA-band systems.}
 
-\textbf{The $\alpha5$ and $q3$ variations produce a higher number of F50 systems than FZ for all DWD types.
+\textbf{The $\alpha5$ and $q3$ variations produce a higher number of F50 systems than FZ when summed over all DWD types.
 This is due to the log-uniform P$_{\rm{orb}}$ distribution of model F50 having more of the shortest-period binaries than the tails of the log-normal distribution of FZ; a discrepancy which becomes more significant with increasing metallicity as the FZ distribution moves from a peak of log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 3-4$ to log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 4-6$.
@@
 
-%\textbf{[\emph{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.}][$\leftarrow$ moved to beginning of paragraph] Strikeout: [\emph{Between models FZ and F50, the number of resolvable systems with SNR $>7$ over all DWD types decreases by only $\sim14\%$.}]}
-
 The distance and chirp mass of DWDs which exhibit observable orbital evolution due to the emission of GWs during the LISA mission can be measured.
@@
 
-%\textbf{Strikeout: [\emph{In order to test the robustness of the reduction of the height of the Galactic DWD GW foreground when assuming a metallicity-dependent binary fraction, we repeat our analysis using three different binary evolution \textbf{parameter variations}.}]}
-
-%\textbf{[For each parameter variation, we consider models FZ and F50 as done in the fiducial case described above.
-In variation $q3$, we vary the assumption for the critical mass ratios at which a RLO interaction remains stable or becomes unstable from our fiducial assumptions such that the critical mass ratio is increased to $3.0$ and thus allows stable mass transfer for more massive RLO donors.
-In variations $\alpha25$ and $\alpha5$, we modify the common envelope ejection efficiency to be either much less ($\alpha=0.25$) or more ($\alpha=5$) than in our fiducial assumption ($\alpha=1$).
-Larger common envelope ejection efficiencies lead to wider post-CE separations, while smaller ejection efficiencies either lead to closer post-CE separations or mergers where the envelope ejection fails.] $\leftarrow$ this paragraph was moved to methods}
-
 In each parameter variation, changing the binary evolution assumptions dramatically changes the formation and evolution of the DWD populations.
@@
 
-Interestingly, when we compare the populations of each binary fraction model for our variations, we find that the number of close DWDs %\textbf{Strikeout: [\emph{reduces by the constant factor of two as seen in our fiducial set of assumptions.}]
-\textbf{remains approximately unchanged for our fiducial set of assumptions and $\alpha25$ variation, but is reduced by 50\% for variations $\alpha5$ and $q3$.} This is illustrated in Figure \ref{fig:model_comp}.
+Interestingly, when we compare the populations of each binary fraction model for our variations, we find that the number of close DWDs \textbf{remains approximately unchanged for our fiducial set of assumptions and $\alpha25$ variation, but is reduced by 50\% for variations $\alpha5$ and $q3$.} This is illustrated in Figure \ref{fig:model_comp}.
 The top panel shows the confusion foreground fits for each binary evolution variation (different colored lines) and for each binary fraction model where the solid lines show FZ models and dotted lines show F50 models.
@@
 
-%\textbf{Strikeout: [\emph{We extended our study to include three binary evolution \textbf{parameter variations} to investigate whether the DWD population reduction was robust to changes in assumptions for mass transfer stability and common envelope ejection efficiencies.
-While our binary evolution \textbf{parameter variations} change the size of the LISA-observable populations dramatically, the reduction in the size of the close Galactic DWD population and the height of the confusion foreground for models which assume a metallicity-dependent binary fraction is robust.}]$\leftarrow$[moved/edited into above paragraph]}
 An important consequence of a lower Galactic DWD confusion foreground is that relative to the total DWD population, more DWDs can be individually resolved because of the reduction in competing GW signals.

### 2022-09-01 src/scripts/CEsep.py
Update CEsep.py

@@ -171,4 +171,3 @@ plt.tight_layout()
 #plt.subplots_adjust(wspace=0.25)
 
 plt.savefig(paths.figures / "CEsep.pdf", dpi=100)
-    

### 2022-09-01 src/scripts/CEsep.py
Update CEsep.py

@@ -171,3 +171,4 @@ plt.tight_layout()
 #plt.subplots_adjust(wspace=0.25)
 
 plt.savefig(paths.figures / "CEsep.pdf", dpi=100)
+    

### 2022-09-01 src/tex/ms.tex
Revert to 5ee28f6
text edits

@@
 Short-period double white dwarf (DWD) binaries will be the most prolific source of gravitational waves (GWs) for the Laser Interferometer Space Antenna (LISA).
-DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be the dominant contributor to a stochastic foreground caused by overlapping GW signals, limiting the detectability of individual sources of all kinds.
+DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be the dominant contributor to a stochastic foreground caused by overlapping GW signals.%, limiting the detectability of individual sources of all kinds.
 Population modeling of Galactic DWDs typically assumes a binary fraction of $50\%$ \textbf{and a log-uniform Zero Age Main Sequence (ZAMS) orbital period distribution}.
 However, recent observations have shown that the binary fraction of close, solar-type stars exhibits a strong anti-correlation with metallicity \textbf{which modulates the ZAMS orbital period distribution below $10^4$ days}.
-In this study we perform the first simulation of the Galactic DWD population observable by LISA which incorporates an empirically-derived metallicity-dependent binary fraction.
-We simulate DWDs using the binary population synthesis suite \cosmic\ and incorporate a metallicity-dependent star formation history to create a Galactic population of short-period DWDs.
-We compare two models: one which assumes a metallicity-dependent binary fraction \textbf{and ZAMS orbital period distribution}, and one with a binary fraction of 50\% \textbf{and log-uniform ZAMS orbital period distribution}.
+In this study we perform the first simulation of the Galactic DWD population observable by LISA which incorporates an empirically-derived metallicity-dependent binary fraction \textbf{using the binary population synthesis suite \cosmic\ and a metallicity-dependent star formation history}.
+%We simulate DWDs using the binary population synthesis suite \cosmic\ and incorporate a metallicity-dependent star formation history to create a Galactic population of short-period DWDs. 
+We compare two models: one which assumes a metallicity-dependent binary fraction, %\textbf{and ZAMS orbital period distribution}, 
+and one with a binary fraction of 50\%
+%\textbf{and log-uniform ZAMS orbital period distribution}. 
 \textbf{We repeat our analysis for three different assumptions for Roche-lobe overflow interactions.} We find that while metallicity impacts the evolution and intrinsic properties of our simulated DWD progenitor binaries, the LISA-resolvable populations of the two models remain roughly indistinguishable.
-However, the size of the total Galactic DWD population orbiting in the LISA frequency band is reduced by more than half when accounting for a metallicity-dependent binary fraction \textbf{for two of our four variations.} This effect lowers the confusion foreground, effectively increasing the sensitivity for detecting all types of low-frequency LISA sources.
+However, the size of the total Galactic DWD population orbiting in the LISA frequency band is reduced by more than half when accounting for a metallicity-dependent binary fraction \textbf{for two of our four variations.}
+%This effect lowers the confusion foreground, effectively increasing the sensitivity for detecting all types of low-frequency LISA sources. 
 \textbf{The LISA population remains unchanged in number for two variations, highlighting the sensitivity of the population to binary evolution prescriptions.}

### 2022-09-01 src/tex/ms.tex
text

--- 2022-09-01 src/tex/ms.tex
@@
 Short-period double white dwarf (DWD) binaries will be the most prolific source of gravitational waves (GWs) for the Laser Interferometer Space Antenna (LISA).
-DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be the dominant contributor to a stochastic foreground caused by overlapping GW signals, limiting the detectability of individual sources of all kinds.
+DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be the dominant contributor to a stochastic foreground caused by overlapping GW signals.
 Population modeling of Galactic DWDs typically assumes a binary fraction of $50\%$ \textbf{and a log-uniform Zero Age Main Sequence (ZAMS) orbital period distribution}.
 However, recent observations have shown that the binary fraction of close, solar-type stars exhibits a strong anti-correlation with metallicity \textbf{which modulates the ZAMS orbital period distribution below $10^4$ days}.
-In this study we perform the first simulation of the Galactic DWD population observable by LISA which incorporates an empirically-derived metallicity-dependent binary fraction.
-We simulate DWDs using the binary population synthesis suite \cosmic\ and incorporate a metallicity-dependent star formation history to create a Galactic population of short-period DWDs.
-We compare two models: one which assumes a metallicity-dependent binary fraction \textbf{and ZAMS orbital period distribution}, and one with a binary fraction of 50\% \textbf{and log-uniform ZAMS orbital period distribution}.
+In this study we perform the first simulation of the Galactic DWD population observable by LISA which incorporates an empirically-derived metallicity-dependent binary fraction, \textbf{using the binary population synthesis suite \cosmic\ and a metallicity-dependent star formation history}.
+We compare two models: one which assumes a metallicity-dependent binary fraction, and one with a binary fraction of 50\%.
 \textbf{We repeat our analysis for three different assumptions for Roche-lobe overflow interactions.} We find that while metallicity impacts the evolution and intrinsic properties of our simulated DWD progenitor binaries, the LISA-resolvable populations of the two models remain roughly indistinguishable.
-However, the size of the total Galactic DWD population orbiting in the LISA frequency band is reduced by more than half when accounting for a metallicity-dependent binary fraction \textbf{for two of our four variations.} This effect lowers the confusion foreground, effectively increasing the sensitivity for detecting all types of low-frequency LISA sources.
-\textbf{The LISA population remains unchanged in number for two variations, highlighting the sensitivity of the population to binary evolution prescriptions.}
+However, the size of the total Galactic DWD population orbiting in the LISA frequency band is reduced by more than half when accounting for a metallicity-dependent binary fraction \textbf{for two of our four variations, which also lowers the effective foreground.
+The LISA population remains unchanged in number for two variations, highlighting the sensitivity of the population to binary evolution prescriptions.}
 \end{abstract}

### 2022-10-03 src/tex/ms.tex
text changes for referee second round

@@
 \newcommand{\kb}[1]{\textcolor{teal}{#1}}
-
-\shorttitle{Applying a metallicity-dependent binary fraction to DWD formation}
+\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+
+\shorttitle{Applying a metallicity-dependent binary fraction to DWD 
+formation}
 \shortauthors{Thiele et al.}
@@
 % Title
-\title{Applying the metallicity-dependent binary fraction to double white dwarf formation: \\ Implications for LISA}
+\title{Applying the metallicity-dependent binary fraction to double white 
+dwarf formation: \\ Implications for LISA}
 
@@
 \author[0000-0001-7442-6926]{Sarah Thiele}
-\affiliation{Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC, V6T 1Z1, Canada}
+\affiliation{Department of Physics and Astronomy, University of British 
+Columbia, 6224 Agricultural Road, Vancouver, BC, V6T 1Z1, Canada}
 \affiliation{Canadian Institute for Theoretical Astrophysics, University
@@
 \author[0000-0001-5228-6598]{Katelyn Breivik}
-\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 
+162 Fifth Ave, New York, NY, 10010, USA}
 \affiliation{Canadian Institute for Theoretical Astrophysics, University
@@
 \author[0000-0003-3939-3297]{Robyn E. Sanderson}
-\affiliation{Department of Physics and Astronomy, University of Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA}
-\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
+\affiliation{Department of Physics and Astronomy, University of 
+Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 
+162 Fifth Ave, New York, NY, 10010, USA}
 \author[0000-0002-0296-3826]{Rodrigo Luger}
-\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 
+162 Fifth Ave, New York, NY, 10010, USA}
 
@@
 \begin{abstract}
-Short-period double white dwarf (DWD) binaries will be the most prolific source of gravitational waves (GWs) for the Laser Interferometer Space Antenna (LISA).
-DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be the dominant contributor to a stochastic foreground caused by overlapping GW signals.
-Population modeling of Galactic DWDs typically assumes a binary fraction of $50\%$ \textbf{and a log-uniform Zero Age Main Sequence (ZAMS) orbital period distribution}.
-However, recent observations have shown that the binary fraction of close, solar-type stars exhibits a strong anti-correlation with metallicity \textbf{which modulates the ZAMS orbital period distribution below $10^4$ days}.
-In this study we perform the first simulation of the Galactic DWD population observable by LISA which incorporates an empirically-derived metallicity-dependent binary fraction, \textbf{using the binary population synthesis suite \cosmic\ and a metallicity-dependent star formation history}.
-We compare two models: one which assumes a metallicity-dependent binary fraction, and one with a binary fraction of 50\%.
-\textbf{We repeat our analysis for three different assumptions for Roche-lobe overflow interactions.} We find that while metallicity impacts the evolution and intrinsic properties of our simulated DWD progenitor binaries, the LISA-resolvable populations of the two models remain roughly indistinguishable.
-However, the size of the total Galactic DWD population orbiting in the LISA frequency band is reduced by more than half when accounting for a metallicity-dependent binary fraction \textbf{for two of our four variations, which also lowers the effective foreground.
-The LISA population remains unchanged in number for two variations, highlighting the sensitivity of the population to binary evolution prescriptions.}
+Short-period double white dwarf (DWD) binaries will be the most prolific 
+source of gravitational waves (GWs) for the Laser Interferometer Space 
+Antenna (LISA). DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be 
+the dominant contributor to a stochastic foreground caused by overlapping 
+GW signals. Population modeling of Galactic DWDs typically assumes a 
+binary fraction of $50\%$ and a log-uniform Zero Age Main Sequence (ZAMS) 
+orbital period distribution. However, recent observations have shown that 
+the binary fraction of close, solar-type stars exhibits a strong 
+anti-correlation with metallicity which modulates the ZAMS orbital period 
+distribution below $10^4$ days. In this study we perform the first 
+simulation of the Galactic DWD population observable by LISA which 
+incorporates an empirically-derived metallicity-dependent binary fraction, 
+using the binary population synthesis suite \cosmic\ and a 
+metallicity-dependent star formation history. We compare two models: one 
+which assumes a metallicity-dependent binary fraction, and one with a 
+binary fraction of 50\%. We repeat our analysis for three different 
+assumptions for Roche-lobe overflow interactions. We find that while 
+metallicity impacts the evolution and intrinsic properties of our 
+simulated DWD progenitor binaries, the LISA-resolvable populations of the 
+two models remain roughly indistinguishable. However, the size of the 
+total Galactic DWD population orbiting in the LISA frequency band is 
+reduced by more than half when accounting for a metallicity-dependent 
+binary fraction for two of our four variations, which also lowers the 
+effective foreground. The LISA population remains unchanged in number for 
+two variations, highlighting the sensitivity of the population to binary 
+evolution prescriptions.
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
-Most stars in the Galaxy will end their lives as white dwarfs.
-Of the stars which are born with a binary companion, many will undergo interactions which bring the two stars closer together, eventually forming a close double white dwarf (DWD).
-Close DWDs, with orbital periods shorter than $\sim2.75\,\rm{hr}$ are the largest source by number of mHz gravitational waves (GWs) in the Galaxy \citep[e.g.,][]{LISAMissionProposal}.
-The Laser Interferometer Space Antenna (LISA) is expected to resolve at least $10^4$ individual DWD binaries in the Milky Way and will also observe GW emission from the entire Galactic DWD population through the unresolved foreground created by overlapping signals at sub-mHz frequencies \citep[e.g.,][]{Nelemans2001a, Ruiter2010, Nissanke2012, Yu2013, Korol2017, Lamberts2019, Breivik2020a}.
-The resolved population will enable the study of several important aspects of binary evolution like the strength of tides \citep{Valsecchi2012}, the stability of mass transfer in DWD systems \citep[e.g.,][]{Marsh2004, Shen2015, Gokhale2007, Sepinsky2014, Kremer2015}\textbf{, and the separation distribution of close DWDs \citep{Korol2021}} as well as provide a probe of Galactic structure \citep{Korol2019} and the Local Group \citep{Korol2018}.
-The shape and strength of the Galactic DWD foreground can also be used as a tool to study the structure of the Milky Way \citep{Benacquista2006, Breivik2020b}.
-
-\textbf{The transition between individually resolved DWDs and the confusion limited, or unresolved, DWD foreground is expected to occur near $\sim1\,\rm{mHz}$ frequencies \citep[e.g.
-][]{Ruiter2010}.
-In the confusion limited regime, more than one binary radiates GWs in each LISA frequency bin, thus creating a superposition of signals which are unable to be disentangled.
-There are multiple parameters which shape the Galactic DWD foreground.
-Assuming the evolution of each DWD system is driven solely by GW emission, the frequency derivative scales proportionally to $f_{\rm{GW}}^{11/3}$, causing a pileup of DWDs at lower frequencies \citep[e.g.][]{Breivik2020b}.
-The spatial density of DWDs in the Galaxy which defines the distance to each binary also impacts the foreground amplitude, since GW strain scales inversely with distance.
-Star formation history assumptions combine these two effects by assigning ages and positions to each DWD in the population which determine the present day orbital (and thus GW) frequencies as well as distances to each source.}
-
-When viewed strictly as a source of noise, the unresolved Galactic DWD foreground is the dominant noise source for LISA in the sub-mHz part of LISA's frequency range.
-This extra noise above the detector noise floor affects the detection of all other LISA sources including extreme mass ratio inspirals \citep[e.g.,][]{Berti2006, Barack2007, Babak2017, Moore2017}, merging black holes with masses between $10^4$--$10^7$ M$_{\odot}$ \citep[e.g.,][]{Klein2016, Bellovary2019}, and cosmological GW backgrounds \citep[e.g.,][]{Bartolo2016, Caprini2016, Caldwell2019}.
-For sources which have signals buried by the Galactic DWD population, the foreground must be carefully analyzed and subtracted \citep[][]{Adams2014,Cornish2020,Littenberg2020,Boileau2021}.
-The number of resolved DWDs and the height of the unresolved DWD foreground are a direct consequence of the number of DWD progenitors which form and evolve over the Milky Way's history.
-
-While the binary fraction remains approximately constant across a large metallicity range ($-1.5 \leq$ [Fe/H] $< 0.5$) for wide binaries, close OB stars, and the stellar Initial Mass Function (IMF) \citep{Moe2017, Moe2019}, the binary fraction for solar-type star systems with orbital period $P_{\text{orb}}\leq 10^4$ days (separation $a \leq 10$ AU) shows a strong anti-correlation with metallicity \citep[e.g.][]{Badenes2018, Moe2019, Mazzola2020, Price-Whelan2020}.
-Because close DWDs are the remnants of close, solar-type binary stars, this anti-correlation plays an important role in the formation, evolution, and characteristics of the DWD population that LISA will observe.
-
-To date, population synthesis studies of the Galactic population of close DWDs have either assumed a $100\%$ binary fraction or a $50\%$ binary fraction, such that for every three stars formed, two reside in a binary system \citep{Nelemans2001a, Yu2013, Korol2017, Lamberts2019}.
-In this study, we investigate the effects of a metallicity-dependent binary fraction on the formation and evolution of DWDs.
-To this end, we create synthetic present-day Milky Way-like galaxies of DWDs and specifically select systems with GW signals that may be observable by the space-based detector LISA.
-Throughout, we make comparisons between the standard assumption of a constant $50\%$ initial binary fraction (hereafter model F50) and one with a metallicity-dependent binary fraction (hereafter model FZ).
-
-In Section \ref{sec:simulations} we discuss our assumptions used in simulating DWD populations and detail the process to produce present-day synthetic Milky-Way-like galaxies.
-In Section \ref{sec:LISA_obs} we review the derivation of LISA detectability for circular DWD populations at mHz frequencies.
-In Section \ref{sec:results} we detail results showing how a metallicity-dependent binary fraction affects the formation and evolution of DWD populations assuming \textbf{four sets of} of binary evolution assumptions.
-In Section \ref{sec:LISA_met} we detail the metallicity dependence of the LISA DWD foreground and resolved population.
-Finally, \textbf{we consider how a metallicity-dependent close binary fraction impacts the height} of the Galactic DWD foreground in LISA for \textbf{different binary evolution assumptions} in Section \ref{sec:model_compare} and conclude in Section \ref{sec:conclusions}.
+Most stars in the Galaxy will end their lives as white dwarfs. Of the 
+stars which are born with a binary companion, many will undergo 
+interactions which bring the two stars closer together, eventually forming 
+a close double white dwarf (DWD). Close DWDs, with orbital periods shorter 
+than $\sim2.75\,\rm{hr}$ are the largest source by number of mHz 
+gravitational waves (GWs) in the Galaxy 
+\citep[e.g.,][]{LISAMissionProposal}. The Laser Interferometer Space 
+Antenna (LISA) is expected to resolve at least $10^4$ individual DWD 
+binaries in the Milky Way and will also observe GW emission from the 
+entire Galactic DWD population through the unresolved foreground created 
+by overlapping signals at sub-mHz frequencies 
+\citep[e.g.,][]{Nelemans2001a, Ruiter2010, Nissanke2012, Yu2013, 
+Korol2017, Lamberts2019, Breivik2020a}. The resolved population will 
+enable the study of several important aspects of binary evolution like the 
+strength of tides \citep{Valsecchi2012}, the stability of mass transfer in 
+DWD systems \citep[e.g.,][]{Marsh2004, Shen2015, Gokhale2007, 
+Sepinsky2014, Kremer2015}, and the separation distribution of close DWDs 
+\citep{Korol2021} as well as provide a probe of Galactic structure 
+\citep{Korol2019} and the Local Group \citep{Korol2018}. The shape and 
+strength of the Galactic DWD foreground can also be used as a tool to 
+study the structure of the Milky Way \citep{Benacquista2006, 
+Breivik2020b}.
+
+The transition between individually resolved DWDs and the confusion 
+limited, or unresolved, DWD foreground is expected to occur near 
+$\sim1\,\rm{mHz}$ frequencies \citep[e.g. ][]{Ruiter2010}. In the 
+confusion limited regime, more than one binary radiates GWs in each LISA 
+frequency bin, thus creating a superposition of signals which are unable 
+to be disentangled. There are multiple parameters which shape the Galactic 
+DWD foreground. Assuming the evolution of each DWD system is driven solely 
+by GW emission, the frequency derivative scales proportionally to 
+$f_{\rm{GW}}^{11/3}$, causing a pileup of DWDs at lower frequencies 
+\citep[e.g.][]{Breivik2020b}. The spatial density of DWDs in the Galaxy 
+which defines the distance to each binary also impacts the foreground 
+amplitude, since GW strain scales inversely with distance. Star formation 
+history assumptions combine these two effects by assigning ages and 
+positions to each DWD in the population which determine the present day 
+orbital (and thus GW) frequencies as well as distances to each source.
+
+When viewed strictly as a source of noise, the unresolved Galactic DWD 
+foreground is the dominant noise source for LISA in the sub-mHz part of 
+LISA's frequency range. This extra noise above the detector noise floor 
+affects the detection of all other LISA sources including extreme mass 
+ratio inspirals \citep[e.g.,][]{Berti2006, Barack2007, Babak2017, 
+Moore2017}, merging black holes with masses between 
+$10^4$--$10^7\,M_{\odot}$ \citep[e.g.,][]{Klein2016, Bellovary2019}, and 
+cosmological GW backgrounds \citep[e.g.,][]{Bartolo2016, Caprini2016, 
+Caldwell2019}. For sources which have signals buried by the Galactic DWD 
+population, the foreground must be carefully analyzed and subtracted 
+\citep[][]{Adams2014,Cornish2020,Littenberg2020,Boileau2021}. The number 
+of resolved DWDs and the height of the unresolved DWD foreground are a 
+direct consequence of the number of DWD progenitors which form and evolve 
+over the Milky Way's history.
+
+While the binary fraction remains approximately constant across a large 
+metallicity range ($-1.5 \leq$ [Fe/H] $< 0.5$) for wide binaries, close OB 
+stars, and the stellar Initial Mass Function (IMF) \citep{Moe2017, 
+Moe2019}, the binary fraction for solar-type star systems with orbital 
+period $P_{\rm{orb}}\leq 10^4$ days (separation $a \leq 10$ AU) shows a 
+strong anti-correlation with metallicity \citep[e.g.][]{Badenes2018, 
+Moe2019, Mazzola2020, Price-Whelan2020}. Because close DWDs are the 
+remnants of close, solar-type binary stars, this anti-correlation plays an 
+important role in the formation, evolution, and characteristics of the DWD 
+population that LISA will observe.
+
+To date, population synthesis studies of the Galactic population of close 
+DWDs have either assumed a $100\%$ binary fraction or a $50\%$ binary 
+fraction, such that for every three stars formed, two reside in a binary 
+system \citep{Nelemans2001a, Yu2013, Korol2017, Lamberts2019}. In this 
+study, we investigate the effects of a metallicity-dependent binary 
+fraction on the formation and evolution of DWDs. To this end, we create 
+synthetic present-day Milky Way-like galaxies of DWDs and specifically 
+select systems with GW signals that may be observable by the space-based 
+detector LISA. Throughout, we make comparisons between the standard 
+assumption of a constant $50\%$ initial binary fraction (hereafter model 
+F50) and one with a metallicity-dependent binary fraction (hereafter model 
+FZ).
+
+In Section \ref{sec:simulations} we discuss our assumptions used in 
+simulating DWD populations and detail the process to produce present-day 
+synthetic Milky-Way-like galaxies. In Section \ref{sec:LISA_obs} we review 
+the derivation of LISA detectability for circular DWD populations at mHz 
+frequencies. In Section \ref{sec:results} we detail results showing how a 
+metallicity-dependent binary fraction affects the formation and evolution 
+of DWD populations assuming four sets of of binary evolution assumptions. 
+In Section \ref{sec:LISA_met} we detail the metallicity dependence of the 
+LISA DWD foreground and resolved population. Finally, we consider how a 
+metallicity-dependent close binary fraction impacts the height of the 
+Galactic DWD foreground in LISA for different binary evolution assumptions 
+in Section \ref{sec:model_compare} and conclude in Section 
+\ref{sec:conclusions}.
 
 \section{Simulating a Galactic DWD population}\label{sec:simulations}
-In this section we describe the setup of our DWD simulations using the binary population synthesis suite \cosmic, and the process to scale these simulations to create Milky Way-like galaxies using the star formation history of galaxy \textbf{\textbf{m12i}} in the Latte suite of the FIRE-2 simulations \citep{Wetzel2016, Hopkins2018} and stellar positions assigned according to the the Ananke framework \citep{Sanderson2020}.
-
-\subsection{Metallicity-dependent binary fraction}\label{subsec:metbinfrac}
-\textbf{The close binary fraction in the Galaxy has been empirically shown to depend on metallicity.
-This is manifested through an explicit dependence of the companion frequency on orbital period \citep{Moe2021}.
-When anchored to a log-normal orbital period distribution, the \emph{frequency} of solar-type binary companions is skewed to shorter orbital periods.
-The companion frequency differs from the binary fraction: the companion frequency is the probability of a star having a companion at a given orbital period, and the integration of this probability over all periods results in the binary fraction of the population.
-The metallicity dependence of the companion frequency is observed only below P$_{\rm{orb}}=10^6$ days, above which there are not sufficient observational data of binary systems to infer a metallicity dependence.}
+In this section we describe the setup of our DWD simulations using the 
+binary population synthesis suite \cosmic, and the process to scale these 
+simulations to create Milky Way-like galaxies using the star formation 
+history of galaxy \textbf{m12i} in the Latte suite of the FIRE-2 
+simulations \citep{Wetzel2016, Hopkins2018} and stellar positions assigned 
+according to the the Ananke framework \citep{Sanderson2020}.
+
+\subsection{Metallicity-dependent binary 
+fraction}\label{subsec:metbinfrac}
+The close binary fraction in the Galaxy has been empirically shown to 
+depend on metallicity. This is manifested through an explicit dependence 
+of the companion frequency on orbital period \citep{Moe2021}. When 
+anchored to a log-normal orbital period distribution, the \emph{frequency} 
+of solar-type binary companions is skewed to shorter orbital periods. The 
+companion frequency differs from the binary fraction: the companion 
+frequency is the probability of a star having a companion at a given 
+orbital period, and the integration of this probability over all periods 
+results in the binary fraction of the population. The metallicity 
+dependence of the companion frequency is observed only below 
+$P_{\rm{orb}}=10^6$ days, above which there are not sufficient 
+observational data of binary systems to infer a metallicity dependence.
 
@@
 	\includegraphics[width=\columnwidth]{figures/met_dep_porb.pdf}
-    \caption{The distribution of the companion frequency f$_{\rm{logP}}$ for solar-type stars is dependent on both ZAMS orbital period and metallicity.
-Each curve is coloured by metallicity, with the darkest curve corresponding to the lowest-metallicity bin in our simulations at [Fe/H]$=-2.3$ and the lightest curve corresponding to our highest-metallicity bin at [Fe/H]$=0.18$.
-Above $\log_{10}(P_{\rm{orb}}/\rm{day})\sim 4$, the companion frequency distribution is the same for all metallicity bins as no identified metallicity dependence at those periods exists in current literature.}
+    \caption{The distribution of the companion frequency f$_{\rm{logP}}$ 
+for solar-type stars is dependent on both ZAMS orbital period and 
+metallicity. Each curve is coloured by metallicity, with the darkest curve 
+corresponding to the lowest-metallicity bin in our simulations at [Fe/H] 
+$=-2.3$ and the lightest curve corresponding to our highest-metallicity 
+bin at [Fe/H] $=0.18$. Above $\log_{10}(P_{\rm{orb}}/\rm{day})\sim 4$, the 
+companion frequency distribution is the same for all metallicity bins as 
+no identified metallicity dependence at those periods exists in current 
+literature.}
     \label{fig:met_dep_porb}
@@
 
-\textbf{Figure \ref{fig:met_dep_porb} shows the companion frequency f$_{\rm{logP}}$ for solar-type stars as a function of the logarithm of orbital period, mirroring the inner binaries curve of Figure 2 in \citet{Moe2021} and scaling to an overall multiplicity frequency of 0.67 (equivalent to an integrated binary fraction of 50\%) at solar metallicity.
-To obtain the normalization of the companion frequency for close binaries (P$_{\rm{orb}}<10^4$),} we fit the results presented in \citet{Moe2019} using linear regression to obtain a piecewise relation between the metallicity, [Fe/H] and \text{close} binary fraction $f_{\rm{b}}$ as
+Figure \ref{fig:met_dep_porb} shows the companion frequency 
+f$_{\rm{logP}}$ for solar-type stars as a function of the logarithm of 
+orbital period, mirroring the inner binaries curve of Figure 2 in 
+\citet{Moe2021} and scaling to an overall multiplicity frequency of 0.67 
+(equivalent to an integrated binary fraction of 50\%) at solar 
+metallicity. To obtain the normalization of the companion frequency for 
+close binaries ($P_{\rm{orb}}<10^4$), we fit the results presented in 
+\citet{Moe2019} using linear regression to obtain a piecewise relation 
+between the metallicity, [Fe/H] and \textbf{close} binary fraction 
+$f_{\rm{b}}$ as
 
 \[f_{\rm{b}}= \begin{cases} 
-      - 0.0648 \cdot [\rm{Fe/H}] + 0.3356, & [\rm{Fe/H}]\leq -1.0 \numberthis \\
+      - 0.0648 \cdot [\rm{Fe/H}] + 0.3356, & [\rm{Fe/H}]\leq -1.0 
+\numberthis \\
       -0.1977 \cdot [\rm{Fe/H}] + 0.2025, & [\rm{Fe/H}]> -1.0  , 
@@
 
-\noindent where we convert between [Fe/H] and metallicity Z, assuming all stars have solar abundance such that
+\noindent where we convert between [Fe/H] and metallicity Z, assuming all 
+stars have solar abundance such that
 \begin{equation}
 \label{eq:metallicity}
-    [\rm{Fe/H}] = \log_{10}\Big(\frac{Z}{Z_{\odot}}\Big),
+    [\rm{Fe/H}] = 
+\log_{10}\Big(\frac{\textit{Z}}{\textit{Z}_{\odot}}\Big),
 \end{equation}
@@
 
-\textbf{We count all higher-order companions as secondary, or binary, components.
-We show curves for all 15 of our metallicity bins, increasing in metallicity from darkest to lightest curve colour.
-The lowest metallicity ([Fe/H]=-2.3) shows the highest propensity for short-period binaries, in contrast to higher metallicity systems which have a frequency distribution with a relatively constant companion frequency for orbital periods between $10^4$ and $10^6$ days.}
-
-\textbf{While we simulate binaries across the entire orbital period distribution, the close binary fraction, which exhibits the discussed metallicity dependence, will be that which impacts the LISA population since systems with $\log_{10}(\rm{P}_{\rm{orb}}/$day)$>4$ will be unlikely to evolve enough to enter the LISA band by present day.}
+We count all higher-order companions as secondary, or binary, components. 
+We show curves for all 15 of our metallicity bins, increasing in 
+metallicity from darkest to lightest curve colour. The lowest metallicity 
+($\rm{[Fe/H]}=-2.3$) shows the highest propensity for short-period 
+binaries, in contrast to higher metallicity systems which have a frequency 
+distribution with a relatively constant companion frequency for orbital 
+periods between $10^4$ and $10^6$ days.
+
+While we simulate binaries across the entire orbital period distribution, 
+the close binary fraction, which exhibits the discussed metallicity 
+dependence, will be that which impacts the LISA population since systems 
+with $\log_{10}(P_{\rm{orb}}/$day)$>4$ will be unlikely to evolve enough 
+to enter the LISA band by present day.
 
@@
 \label{sec:bin_pop}
-We simulate the evolution of DWD progenitor populations using \cosmic\footnote{https://cosmic-popsynth.github.io}, an open-source Python-based rapid binary population synthesis suite which employs single and binary star evolution using \texttt{SSE/BSE} \citep{Hurley2000, Hurley2002}.
-Several modifications have been added to \cosmic\ which incorporate updates for massive star evolution and binary interactions.
-For a detailed description of these modifications see \citet{Breivik2020a}.
-\cosmic\ has been used in several studies to examine the effects of binary evolution on binary populations from blue stragglers \citep{Leiner2021} and heartbeat stars \citep{Jayasinghe2021}, to white dwarf populations \citep{Kremer2017,Breivik2018,Kilic2021}, to merging compact object populations in isolated binaries \citep{Zevin2020b, Zevin2020a, Zevin2021, Wong2021, Mandhai2021} and in dynamical environments around super-massive black holes \citep{Stephan2019, Wang2021}.
-
-\cosmic\ is especially useful for efficient generation of large populations of compact binaries.
-Instead of choosing a fixed number of binary stars for each simulation, \cosmic\ iteratively simulates populations until parameter distributions of the binary population converge to a stable shape as more binaries are added.
-This process is quantified through the $match$ parameter inspired by matched filtering techniques \citep[e.g.
-Eq.
-6 of ][]{Chatziioannou2017} defined as
+We simulate the evolution of DWD progenitor populations using 
+\cosmic\footnote{https://cosmic-popsynth.github.io}, an open-source 
+Python-based rapid binary population synthesis suite which employs single 
+and binary star evolution using \texttt{SSE/BSE} \citep{Hurley2000, 
+Hurley2002}. Several modifications have been added to \cosmic\ which 
+incorporate updates for massive star evolution and binary interactions. 
+For a detailed description of these modifications see 
+\citet{Breivik2020a}. \cosmic\ has been used in several studies to examine 
+the effects of binary evolution on binary populations from blue stragglers 
+\citep{Leiner2021} and heartbeat stars \citep{Jayasinghe2021}, to white 
+dwarf populations \citep{Kremer2017,Breivik2018,Kilic2021}, to merging 
+compact object populations in isolated binaries \citep{Zevin2020b, 
+Zevin2020a, Zevin2021, Wong2021, Mandhai2021} and in dynamical 
+environments around super-massive black holes \citep{Stephan2019, 
+Wang2021}.
+
+\cosmic\ is especially useful for efficient generation of large 
+populations of compact binaries. Instead of choosing a fixed number of 
+binary stars for each simulation, \cosmic\ iteratively simulates 
+populations until parameter distributions of the binary population 
+converge to a stable shape as more binaries are added. This process is 
+quantified through the $match$ parameter inspired by matched filtering 
+techniques \citep[e.g. Eq. 6 of ][]{Chatziioannou2017} defined as
 
 \begin{equation}
-   match = \frac{\sum_{k=1}^{N}P_{k,i}P_{k,i+1}}{\sqrt{\sum_{k=1}^{N}P_{k,i}P_{k,i}\sum_{k=1}^{N}P_{k,i+1}P_{k,i+1}}},
+   match = 
+\frac{\sum_{k=1}^{N}P_{k,i}P_{k,i+1}}{\sqrt{\sum_{k=1}^{N}P_{k,i}P_{k,i}\sum_{k=1}^{N}P_{k,i+1}P_{k,i+1}}},
 \end{equation}
-where $P_{k,i}$ represents the height of bin $k$ on the $i\rm{th}$ iteration \citep{Breivik2020a}.
-In this study, we simulate binaries until $\log_{10}(1-match) \leq -5$ for the masses and orbital periods of each DWD population at the formation of the second WD.
-Since all DWD progenitor binaries simulated with \cosmic\ are circularized through mass transfer or tides before the second WD forms \citep[e.g.][]{Marsh2004, Gokhale2007, Sepinsky2014, Kremer2015}, we do not consider convergence of DWD eccentricities.
-
-The masses and orbital periods at the formation of the second-formed WD span a wide range depending on the WD binary component types, thus we consider four DWD combinations: two helium WDs (He + He), a carbon-oxygen WD orbiting a helium WD (CO + He), two carbon-oxygen WDs (CO + CO), and an oxygen-neon orbiting a helium, carbon-oxygen, or oxygen-neon WD (ONe + X).
-For each DWD type we simulate a grid of $15$ metallicities spaced uniformly in $\log_{10}(Z)$ between $Z=10^{-4}$ to $0.03$, to account for the limits of the \citet{Hurley2000} stellar evolution tracks employed in \cosmic.
-This results in a total of $60$ populations across all DWD types and metallicities \textbf{for each set of model assumptions}.
-The output of \cosmic\ contains information limited to intrinsic binary properties like mass and orbital period.
-External parameters like Galactic position and orientation are assigned in a post-processing scheme which uses metallicity-dependent positions and ages from the Ananke framework of galaxy \textbf{m12i} from the Latte Suite of the FIRE-2 simulations (see Section~\ref{sec:FIRE} for details).
-
-We assume that the Zero Age Main Sequence (ZAMS) masses, orbital periods and eccentricities for each binary are independently distributed.
-We choose primary masses following \citet{Kroupa2001}, a flat mass ratio distribution \citep{Mazeh1992, Goldberg1994} and a uniform eccentricity distribution following \cite{Geller2019}.
-\textbf{For our simulations which follow a metallicity-dependent binary fraction (model FZ), a skewed log-normal orbital period distribution is sampled in accordance with the metallicity-dependent companion frequency of \citet{Moe2021} as discussed in Section \ref{subsec:metbinfrac}.
-For our simulations which assume a constant 50\% binary fraction (model F50), we use a log-uniform period distribution following Opik's Law similar to previous studies \citep[e.g.][]{Nelemans2001a, Toonen2012, Korol2017, Lamberts2019}.
-We assume a $100\%$ binary fraction in the F50 COSMIC simulations to reduce computation time and scale the simulations to a constant $50\%$ binary fraction in a post-processing scheme.} We initialize all binaries with the same evolution time of $13.7\,\rm{Gyr}$ to capture all potential evolution within a Hubble time.
-\textbf{Although we simulate binaries across the full orbital period distribution, we discard DWD binaries which form with separations $a\geq 1000$ R$_\odot$ during post-processing, since these are unlikely to evolve into the LISA band by present day.}
-
-\textbf{We consider a fiducial set of assumptions which} follow the \texttt{COSMIC} defaults described in \citet{Breivik2020a} except for the treatment of Roche-lobe overflow (RLO).
-The stability of RLO mass transfer is determined using critical mass ratios resulting from radius-mass exponents \citep{Webbink1985, Hurley2002}, where the critical mass ratio is defined as the ratio of the donor to accretor mass.
-We assume critical mass ratios following \citet{Claeys2014} which reduce the standard critical mass ratio assumptions from \citet{Hurley2002} for main sequence (MS) donors by $\sim50\%$ from $3$ to $1.6$ based on the models of \citet{deMink2007} and treat WD accretors separately following the models of \citet{Soberman1997}.
-We increase the mass loss rate from the donor following Equation 11 of \citet{Claeys2014}.
-The amount of mass lost during RLO from the donor is limited by the overflow factor of the donor radius to its Roche radius following \citet{Hurley2002}.
-The amount of mass accepted by the accretor is limited to $10$ times the accretor's mass divided by the accretor's thermal timescale.
-Finally, for RLO mass loss which becomes unstable and leads to common envelope evolution (CEE) we assume that the donor's binding energy is calculated according to the fits detailed in Appendix B of \citet{Claeys2014} and that orbital energy is deposited with $100\%$ efficiency into unbinding the common envelope ($\alpha=1$).
-
-\textbf{The LISA-detectable DWD populations that result from our simulations may vary depending on the assumptions made regarding binary interactions.
-In order to explore the range of results, we complete this study for three binary evolution parameter variations on top of our fiducial set of assumptions.
-For each variation, we consider models FZ and F50 as done in the fiducial case described above.
-In variation $q3$, we vary the assumption for the critical mass ratios at which a RLO interaction remains stable or becomes unstable from our fiducial assumptions such that the critical mass ratio is increased to $3.0$ and thus allows stable mass transfer for more massive RLO donors.
-In variations $\alpha25$ and $\alpha5$, we modify the common envelope ejection efficiency to be either much less ($\alpha=0.25$) or more ($\alpha=5$) than in our fiducial assumption ($\alpha=1$) to capture the range of possible CE ejection efficiencies quoted in the literature  \citep[e.g.][]{Zorotovic2010, Fragos2019}.
-Larger common envelope ejection efficiencies lead to wider post-CE separations, while smaller ejection efficiencies either lead to closer post-CE separations or stellar mergers where the envelope ejection fails.
-Between all variations, all other prescriptions for binary evolution remain identical besides the one varied parameter.
-We delve in depth into the fiducial results in each section, and then give a brief overview of how the results change for each parameter variation.}
-
-\subsection{A metallicity-dependent SFH: Convolving with the FIRE-2 models}
+where $P_{k,i}$ represents the height of bin $k$ on the $i\rm{th}$ 
+iteration \citep{Breivik2020a}. In this study, we simulate binaries until 
+$\log_{10}(1-match) \leq -5$ for the masses and orbital periods of each 
+DWD population at the formation of the second WD. Since all DWD progenitor 
+binaries simulated with \cosmic\ are circularized through mass transfer or 
+tides before the second WD forms \citep[e.g.][]{Marsh2004, Gokhale2007, 
+Sepinsky2014, Kremer2015}, we do not consider convergence of DWD 
+eccentricities.
+
+The masses and orbital periods at the formation of the second-formed WD 
+span a wide range depending on the WD binary component types, thus we 
+consider four DWD combinations: two helium WDs (He + He), a carbon-oxygen 
+WD orbiting a helium WD (CO + He), two carbon-oxygen WDs (CO + CO), and an 
+oxygen-neon orbiting a helium, carbon-oxygen, or oxygen-neon WD (ONe + X). 
+For each DWD type we simulate a grid of $15$ metallicities spaced 
+uniformly in $\log_{10}(Z)$ between $Z=10^{-4}$ to $0.03$, to account for 
+the limits of the \citet{Hurley2000} stellar evolution tracks employed in 
+\cosmic. This results in a total of $60$ populations across all DWD types 
+and metallicities for each set of model assumptions. The output of 
+\cosmic\ contains information limited to intrinsic binary properties like 
+mass and orbital period. External parameters like Galactic position and 
+orientation are assigned in a post-processing scheme which uses 
+metallicity-dependent positions and ages from the Ananke framework of 
+galaxy \textbf{m12i} from the Latte Suite of the FIRE-2 simulations (see 
+Section~\ref{sec:FIRE} for details).
+
+We assume that the Zero Age Main Sequence (ZAMS) masses, orbital periods 
+and eccentricities for each binary are independently distributed. We 
+choose primary masses following \citet{Kroupa2001}, a flat mass ratio 
+distribution \citep{Mazeh1992, Goldberg1994} and a uniform eccentricity 
+distribution following \cite{Geller2019}. For our simulations which follow 
+a metallicity-dependent binary fraction (model FZ), a skewed log-normal 
+orbital period distribution is sampled in accordance with the 
+metallicity-dependent companion frequency of \citet{Moe2021} as discussed 
+in Section \ref{subsec:metbinfrac}. For our simulations which assume a 
+constant 50\% binary fraction (model F50), we use a log-uniform period 
+distribution following Opik's Law similar to previous studies 
+\citep[e.g.][]{Nelemans2001a, Toonen2012, Korol2017, Lamberts2019}. We 
+assume a $100\%$ binary fraction in the F50 COSMIC simulations to reduce 
+computation time and scale the simulations to a constant $50\%$ binary 
+fraction in a post-processing scheme. We initialize all binaries with the 
+same evolution time of $13.7\,\rm{Gyr}$ to capture all potential evolution 
+within a Hubble time. Although we simulate binaries across the full 
+orbital period distribution, we discard DWD binaries which form with 
+separations $a\geq 1000\,R_\odot$ during post-processing, since these are 
+unlikely to evolve into the LISA band by present day.
+
+We consider a fiducial set of assumptions which follow the \cosmic\ 
+defaults described in \citet{Breivik2020a} except for the treatment of 
+Roche-lobe overflow (RLO). The stability of RLO mass transfer is 
+determined using critical mass ratios resulting from radius-mass exponents 
+\citep{Webbink1985, Hurley2002}, where the critical mass ratio is defined 
+as the ratio of the donor to accretor mass. We assume critical mass ratios 
+following \citet{Claeys2014} which reduce the standard critical mass ratio 
+assumptions from \citet{Hurley2002} for main sequence (MS) donors by 
+$\sim50\%$ from $3$ to $1.6$ based on the models of \citet{deMink2007} and 
+treat WD accretors separately following the models of 
+\citet{Soberman1997}. We increase the mass loss rate from the donor 
+following Equation 11 of \citet{Claeys2014}. The amount of mass lost 
+during RLO from the donor is limited by the overflow factor of the donor 
+radius to its Roche radius following \citet{Hurley2002}. The amount of 
+mass accepted by the accretor is limited to $10$ times the accretor's mass 
+divided by the accretor's thermal timescale. Finally, for RLO mass loss 
+which becomes unstable and leads to common envelope evolution (CEE) we 
+assume that the donor's binding energy is calculated according to the fits 
+detailed in Appendix B of \citet{Claeys2014} and that orbital energy is 
+deposited with $100\%$ efficiency into unbinding the common envelope 
+($\alpha=1$).
+
+The LISA-detectable DWD populations that result from our simulations may 
+vary depending on the assumptions made regarding binary interactions. In 
+order to explore the range of results, we complete this study for three 
+binary evolution parameter variations on top of our fiducial set of 
+assumptions. For each variation, we consider models FZ and F50 as done in 
+the fiducial case described above. In variation $q3$, we vary the 
+assumption for the critical mass ratios at which a RLO interaction remains 
+stable or becomes unstable from our fiducial assumptions. The critical 
+mass ratio $q_c$ is increased to $3.0$ and thus allows stable mass 
+transfer for more massive RLO donors. In variations $\alpha25$ and 
+$\alpha5$, we modify the common envelope ejection efficiency to be either 
+much less ($\alpha=0.25$) or more ($\alpha=5$) than in our fiducial 
+assumption ($\alpha=1$) to capture the range of possible CE ejection 
+efficiencies quoted in the literature  \citep[e.g.][]{Zorotovic2010, 
+Fragos2019}. Larger common envelope ejection efficiencies lead to wider 
+post-CE separations, while smaller ejection efficiencies either lead to 
+closer post-CE separations or stellar mergers where the envelope ejection 
+fails. Between all variations, all other prescriptions for binary 
+evolution remain identical besides the one varied parameter. \textbf{A 
+summary of all models and variations explored in this work is given in 
+Table \ref{tbl:models}.} We delve in depth into the fiducial results in 
+each section, and then give a brief overview of how the results change for 
+each parameter variation.
+
+\begin{table}[]
+    \centering
+    \begin{tabular}{|c|c|c|}
+       \hline
+       model & binary fraction & orbital period distribution \\
+       \hline
+       FZ & \citet{Moe2019} & \citet{Moe2021}\\
+       F50 & 50\% & flat in $\log(P_{\rm{orb}}/\rm{day})$\\
+       \hline
+       \hline       
+       variation & parameter change & binary evolution change \\
+       \hline
+       fiducial  & none & none \\
+       $\alpha25$ & $\alpha=0.25$ & reduced CE efficiency \\
+       $\alpha5$  & $\alpha=5$ & increased CE efficiency\\
+       $q3$ & $q_c=3$ & increased critical mass ratio \\
+       \hline
+    \end{tabular}
+    \caption{\textbf{Summary of the models and binary evolution assumption 
+variation simulations that are explored in this study.}}
+    \label{tbl:models}
+\end{table}
+
+\subsection{A metallicity-dependent SFH: Convolving with the FIRE-2 
+models}
 \label{sec:FIRE}
-To create Milky-Way-like galaxies which integrate the metallicity-dependent binary fraction, we use the metallicity-dependent ages and positions of galaxy \textbf{m12i} from the ``Latte" suite of the FIRE-2 simulations \citep{Hopkins2015, Wetzel2016, Hopkins2018} to create synthetic, Milky-Way-like DWD populations.
-
-The \textbf{m12i} galaxy provides particle mass resolution of 7070 M$_\odot$ per star particle.
-Each star particle has an associated metallicity, position, and age, which is combined with the output of \cosmic\ to assign DWDs to each star particle by matching its metallicity to our \cosmic\ metallicity grid.
-The positions of each DWD are assigned using the Ananke framework since multiple DWD binaries can form within a single star particle.
-Specifically, we use an epanechnikov kernel where the kernel size is inversely proportional to the local density to assign the radial component of spherically symmetric offsets from the center of each star particle following \citet{Sanderson2020}.
+To create Milky-Way-like galaxies which integrate the 
+metallicity-dependent binary fraction, we use the metallicity-dependent 
+ages and positions of galaxy \textbf{m12i} from the ``Latte" suite of the 
+FIRE-2 simulations \citep{Hopkins2015, Wetzel2016, Hopkins2018} to create 
+synthetic, Milky-Way-like DWD populations.
+
+The \textbf{m12i} galaxy provides particle mass resolution of 7070 
+$M_\odot$ per star particle. Each star particle has an associated 
+metallicity, position, and age, which is combined with the output of 
+\cosmic\ to assign DWDs to each star particle by matching its metallicity 
+to our \cosmic\ metallicity grid. The positions of each DWD are assigned 
+using the Ananke framework since multiple DWD binaries can form within a 
+single star particle. Specifically, we use an epanechnikov kernel where 
+the kernel size is inversely proportional to the local density to assign 
+the radial component of spherically symmetric offsets from the center of 
+each star particle following \citet{Sanderson2020}.
 
@@
 	\includegraphics[width=\columnwidth]{figures/sfh_vs_fb.pdf}
-    \caption{The metallicity-dependent binary fraction for close solar-type binaries with P $< 10^4$ days (black) plotted against the logarithm of Z/Z$_\odot$, with scatter points denoting the location of the metallicity grid used in our \cosmic\ simulations.
-The secondary axis shows the amount of mass in stars formed within each metallicity bin from galaxy \textbf{m12i} of the ``Latte" suite in the FIRE-2 simulations as a red histogram.
-The amount of stellar mass formed with super-solar metallicities dominates the distribution.
-Note that the primary axis shows $f_{\rm{b}}(Z)$ in linear scale, and the secondary axis shows amount of mass formed in log-scale.
-The opposing trends of these two distributions compete throughout this study.}
+    \caption{The metallicity-dependent binary fraction for close 
+solar-type binaries with P $< 10^4$ days (black) plotted against the 
+logarithm of $Z/Z_\odot$, with scatter points denoting the location of the 
+metallicity grid used in our \cosmic\ simulations. The secondary axis 
+shows the amount of mass in stars formed within each metallicity bin from 
+galaxy \textbf{m12i} of the ``Latte" suite in the FIRE-2 simulations as a 
+red histogram. The amount of stellar mass formed with super-solar 
+metallicities dominates the distribution. Note that the primary axis shows 
+$f_{\rm{b}}(Z)$ in linear scale, and the secondary axis shows amount of 
+mass formed in log-scale. The opposing trends of these two distributions 
+compete throughout this study.}
     \label{fig:sfh_vs_fb}
@@
 
-The metallicity-dependent \textbf{close} binary fraction \textbf{for solar-type binaries (P $< 10^4$ days), or simply the close binary fraction from here on, } is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid.
-The \textbf{close} binary fraction, $f_{\rm{b}}$, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly.
-These two opposing trends compete throughout this study along with the impact of metallicity on single star evolution to form the final numerical distribution of systems in our DWD populations.
-
-Since our \cosmic\ simulations assume a binary fraction of $f_{\rm{b}} = 1$ \textbf{for model F50}, we scale the amount of mass sampled at ZAMS required to produce our \cosmic-generated population of DWDs ($M_{\text{b,ZAMS}}$) to the proper amount of mass sampled in single and binary stars ($M_{\text{ZAMS,sim}}$).
-We do this by sampling single stars and primary masses of binary stars from the \cite{Kroupa2001} IMF and sampling secondary masses of the binary stars from a uniform mass distribution, where the number of binaries is calculated to ensure $f_{\rm{b}}=0.5$.
-From this sample, we obtain the ratio of mass in single stars to the mass in binary stars, $R(f_{\rm{b}})$.
-For model F50, the ratio is a constant $R(f_{\rm{b}}) = 0.64$.
-\textbf{The total amount of ZAMS mass in single and binary stars is then $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}} (1 + R(f_{\rm{b}}))$.
-For model FZ, no scaling is applied since our \cosmic\ simulations already have the population-wide binary fraction incorporated, and thus $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}}$}.
-
-Once we determine the total ZAMS mass required to produce our simulated population for a given metallicity, the number of DWDs formed per unit solar mass at metallicity $Z_i$ is
+The metallicity-dependent close binary fraction for solar-type binaries 
+($P_{\rm{orb}} < 10^4$ days), or simply the close binary fraction from 
+here on, is shown in black in Figure \ref{fig:sfh_vs_fb} along with the 
+mass in star particles from galaxy \textbf{m12i}, shown in red, as a 
+function of our metallicity grid. The close binary fraction, $f_{\rm{b}}$, 
+drops drastically across metallicity while the mass formed in 
+\textbf{m12i} increases significantly. These two opposing trends compete 
+throughout this study along with the impact of metallicity on single star 
+evolution to form the final numerical distribution of systems in our DWD 
+populations.
+
+Since our \cosmic\ simulations assume a binary fraction of $f_{\rm{b}} = 
+1$ for model F50, we scale the amount of mass sampled at ZAMS required to 
+produce our \cosmic-generated population of DWDs ($M_{\text{b,ZAMS}}$) to 
+the proper amount of mass sampled in single and binary stars 
+($M_{\text{ZAMS,sim}}$). We do this by sampling single stars and primary 
+masses of binary stars from the \cite{Kroupa2001} IMF and sampling 
+secondary masses of the binary stars from a uniform mass distribution, 
+where the number of binaries is calculated to ensure $f_{\rm{b}}=0.5$. 
+From this sample, we obtain the ratio of mass in single stars to the mass 
+in binary stars, $R(f_{\rm{b}})$. For model F50, the ratio is a constant 
+$R(f_{\rm{b}}) = 0.64$. The total amount of ZAMS mass in single and binary 
+stars is then $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}} (1 + 
+R(f_{\rm{b}}))$. For model FZ, no scaling is applied since our \cosmic\ 
+simulations already have the population-wide binary fraction incorporated, 
+and thus $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}}$.
+
+Once we determine the total ZAMS mass required to produce our simulated 
+population for a given metallicity, the number of DWDs formed per unit 
+solar mass at metallicity $Z_i$ is
 \begin{equation}
-    n_{\rm{DWD}}(Z_i) = \frac{N_{\rm{DWD, sim}}(Z_i)}{M_{\rm{ZAMS, sim}}(Z_i)}.
+    n_{\rm{DWD}}(Z_i) = \frac{N_{\rm{DWD, sim}}(Z_i)}{M_{\rm{ZAMS, 
+sim}}(Z_i)}.
 \end{equation}
 
-\noindent The number of DWD’s per \textbf{m12i} star particle at metallicity $Z_i$ is then
+\noindent The number of DWD’s per \textbf{m12i} star particle at 
+metallicity $Z_i$ is then
 \begin{equation}
@@
 
-\noindent where $M_\star = 7070\,M_\odot$ is the mass per \textbf{m12i} star particle.
-Since $N_{\rm{DWD},\star} (Z_i)$ is not an integer, we treat the decimal component as the probability that the star particle contains an extra DWD in addition to the integer number.
-For each star particle, we sample with replacement $N_{\rm{DWD},\star}(Z_i)$ DWDs from the corresponding simulated \cosmic\ population at that metallicity and assign the ZAMS birth time of each DWD to the formation time of the star particle.
-For most DWD types there is more than one DWD binary system assigned to each \textbf{m12i} star particle.
-
-If the DWD formation time is less than the age of the star particle, we evolve the DWD over the remaining time between its formation and star particle age, $t_{\rm{evol}}$, to produce the present-day population.
-Once a DWD is formed, we assume that the binary evolves only due to the emission of GWs.
-Due to tidal effects and mass transfer between their progenitor binaries, all DWDs in our simulations are circular, thus eccentricity does not need to be considered.
-The orbital evolution over the time $t_{\rm{evol}}$ is then simply defined according to \citet{Peters1964} as
+\noindent where $M_\star = 7070\,M_\odot$ is the mass per \textbf{m12i} 
+star particle. Since $N_{\rm{DWD},\star} (Z_i)$ is not an integer, we 
+treat the decimal component as the probability that the star particle 
+contains an extra DWD in addition to the integer number. For each star 
+particle, we sample with replacement $N_{\rm{DWD},\star}(Z_i)$ DWDs from 
+the corresponding simulated \cosmic\ population at that metallicity and 
+assign the ZAMS birth time of each DWD to the formation time of the star 
+particle. For most DWD types there is more than one DWD binary system 
+assigned to each \textbf{m12i} star particle.
+
+If the DWD formation time is less than the age of the star particle, we 
+evolve the DWD over the remaining time between its formation and star 
+particle age, $t_{\rm{evol}}$, to produce the present-day population. Once 
+a DWD is formed, we assume that the binary evolves only due to the 
+emission of GWs. Due to tidal effects and mass transfer between their 
+progenitor binaries, all DWDs in our simulations are circular, thus 
+eccentricity does not need to be considered. The orbital evolution over 
+the time $t_{\rm{evol}}$ is then simply defined according to 
+\citet{Peters1964} as
 \begin{equation}
@@
 
-We discard any DWDs for which the sum of their ZAMS birth time, given by the star particle formation time, and DWD formation time is larger than the age of the star particle since the system will not have evolved long enough to become a DWD at present.
-We further discard any DWDs for which the lower mass WD overflows it's Roche lobe before present day, because the outcomes of these interactions are highly uncertain and their treatment is outside the scope of this work \citep[e.g., ][]{Shen2015, Kremer2017}.
-\textbf{This choice does not significantly affect our results since stably accreting WD binaries are unlikely to contribute appreciably to the Galactic DWD foreground due to their small mass ratios at frequencies below 1 mHz \citep{Breivik2018}.} The separation at which the lower mass WD overflows its Roche Lobe is defined as
+We discard any DWDs for which the sum of their ZAMS birth time, given by 
+the star particle formation time, and DWD formation time is larger than 
+the age of the star particle since the system will not have evolved long 
+enough to become a DWD at present. We further discard any DWDs for which 
+the lower mass WD overflows it's Roche lobe before present day, because 
+the outcomes of these interactions are highly uncertain and their 
+treatment is outside the scope of this work \citep[e.g., ][]{Shen2015, 
+Kremer2017}. This choice does not significantly affect our results since 
+stably accreting WD binaries are unlikely to contribute appreciably to the 
+Galactic DWD foreground due to their small mass ratios at frequencies 
+below 1 mHz \citep{Breivik2018}. The separation at which the lower mass WD 
+overflows its Roche Lobe is defined as
 
 \begin{equation}
-    a_{\text{RLO,}\ell} = R_{\ell} \frac{0.6 q_{\ell}^{2/3} + \ln{(1+q_{\ell}^{1/3})}}{0.49 q_{\ell}^{2/3}}
+    a_{\text{RLO,}\ell} = R_{\ell} \frac{0.6 q_{\ell}^{2/3} + 
+\ln{(1+q_{\ell}^{1/3})}}{0.49 q_{\ell}^{2/3}}
 \end{equation}
-where $R_{\ell}$ is the radius of the lower mass WD and $q_{\ell} = M_{\ell}/M_{h}$ is the ratio of the lower- to higher-mass WD components. \citep{Eggleton1983}. 
+where $R_{\ell}$ is the radius of the lower mass WD and $q_{\ell} = 
+M_{\ell}/M_{h}$ is the ratio of the lower- to higher-mass WD components. 
+\citep{Eggleton1983}. 
 We define the radius of a WD following \citet{Tout1997, Hurley2000} as
 \begin{equation}
-    R_{\rm{WD}} = \max\Bigg(R_\text{NS}, 0.0115\sqrt{\left(\frac{M_\text{Ch}}{M}\right)^{2/3}-\left(\frac{M}{M_\text{Ch}}\right)^{2/3}} \Bigg) 
+    R_{\rm{WD}} = \max\Bigg(R_\text{NS}, 
+0.0115\sqrt{\left(\frac{M_\text{Ch}}{M}\right)^{2/3}-\left(\frac{M}{M_\text{Ch}}\right)^{2/3}} 
+\Bigg) 
 \end{equation}
-\noindent where $R_\text{NS} = 1.4\cdot 10^{-5}$ R$_\odot$ is the radius of a neutron star, $M_{\text{Ch}}=1.44$ M$_\odot$ is the Chandrasekhar limit for the mass of a stable WD, and $M$ is the mass of the WD in solar masses.
-
-For the non-discarded systems, we log the present-day separations from which the present-day orbital frequency $f_\text{orb}$ can be found using Kepler's third law.
-The GW frequency is then $f_\text{GW} = 2f_\text{orb}$.
+\noindent where $R_\text{NS} = 1.4\cdot 10^{-5}~R_\odot$ is the radius of 
+a neutron star, $M_{\text{Ch}}=1.44 ~M_\odot$ is the Chandrasekhar limit 
+for the mass of a stable WD, and $M$ is the mass of the WD in solar 
+masses.
+
+For the non-discarded systems, we log the present-day separations from 
+which the present-day orbital frequency $f_\text{orb}$ can be found using 
+Kepler's third law. The GW frequency is then $f_\text{GW} = 
+2f_\text{orb}$.
 
@@
 \label{sec:LISA_obs}
-We use \legwork\footnote{https://legwork.readthedocs.io} \citep{Wagg2021} to determine the detectability of our simulated DWD populations for sources with GW frequencies $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$.
-\legwork\ calculates the position-, orientation-, and angle-averaged signal to noise ratio (SNR) for inspiraling GW sources closely following the derivations of \citet{Flanagan1998} and using the LISA noise power spectral density (PSD) of \citet{Robson2019}.
-
-To lowest order in the post-Newtonian expansion, the frequency evolution of circular orbits for quadrupole GW emission is defined as
+We use \legwork\footnote{https://legwork.readthedocs.io} \citep{Wagg2021} 
+to determine the detectability of our simulated DWD populations for 
+sources with GW frequencies $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$. \legwork\ 
+calculates the position-, orientation-, and angle-averaged signal to noise 
+ratio (SNR) for inspiraling GW sources closely following the derivations 
+of \citet{Flanagan1998} and using the LISA noise power spectral density 
+(PSD) of \citet{Robson2019}.
+
+To lowest order in the post-Newtonian expansion, the frequency evolution 
+of circular orbits for quadrupole GW emission is defined as
 \begin{equation}
-    \Dot{f}_n = \frac{48n}{5\pi} \frac{(G\mathcal{M}_c)^{5/3}}{c^5} (2\pi f_\text{orb})^{11/3}.
+    \Dot{f}_n = \frac{48n}{5\pi} \frac{(G\mathcal{M}_c)^{5/3}}{c^5} (2\pi 
+f_\text{orb})^{11/3}.
 \end{equation}
-We classify DWDs as evolving, or ``chirping", when $\Dot{f}_n \geq 1/t_\text{obs}^2$. For evolving sources, the SNR is
+We classify DWDs as evolving, or ``chirping", when $\Dot{f}_n \geq 
+1/t_\text{obs}^2$. For evolving sources, the SNR is
 
 \begin{equation}
-   \langle \rho \rangle^2_{\text{circ,evol}} = \int_{f_0}^{f_1}df   \frac{h_{c}^2}{f^2S_n(f)}
+   \langle \rho \rangle^2_{\text{circ,evol}} = \int_{f_0}^{f_1}df   
+\frac{h_{c}^2}{f^2S_n(f)}
 \end{equation}
 
-\noindent where $h_c$ is the characteristic strain of the system, $S_n(f)$ is the LISA sensitivity curve of \citet{Robson2019}, and the frequency limits are determined by the orbital evolution over the observation time, $T_{\rm{obs}}=4\,\rm{yr}$.
-The characteristic strain for circular orbits is
+\noindent where $h_c$ is the characteristic strain of the system, $S_n(f)$ 
+is the LISA sensitivity curve of \citet{Robson2019}, and the frequency 
+limits are determined by the orbital evolution over the observation time, 
+$T_{\rm{obs}}=4\,\rm{yr}$. The characteristic strain for circular orbits 
+is 
 \begin{equation}
-    h_{c}^2 = \frac{2^{2/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}},
+    h_{c}^2 = \frac{2^{2/3}}{3 \pi^{4/3}} \frac{(G 
+\mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}},
 \end{equation}
-\noindent where $\mathcal{M}_c = (M_1M_2)^{3/5}/(M_1 + M_2)^{1/5}$ is the system's chirp mass, and $D_L$ is the systems luminosity distance which we assume to be the distance of each simulated DWD to the Sun.
-
-For stationary sources, the SNR is modified due to the lack of observable orbital evolution as
+\noindent where $\mathcal{M}_c = (M_1M_2)^{3/5}/(M_1 + M_2)^{1/5}$ is the 
+system's chirp mass, and $D_L$ is the systems luminosity distance which we 
+assume to be the distance of each simulated DWD to the Sun.
+
+For stationary sources, the SNR is modified due to the lack of observable 
+orbital evolution as
 \begin{equation}
@@
 \end{equation}
-with the observation time $T_{\text{obs}}$. Here, $h_2$ is strain amplitude of the source for the second orbital frequency harmonic,
+with the observation time $T_{\text{obs}}$. Here, $h_2$ is strain 
+amplitude of the source for the second orbital frequency harmonic,
 \begin{equation}
-   h_2^2 = \frac{2^{22/3}}{5}\frac{(G\mathcal{M}_c)^{10/3}}{c^8D_L^2}(\pi f_\text{orb})^{4/3}
+   h_2^2 = \frac{2^{22/3}}{5}\frac{(G\mathcal{M}_c)^{10/3}}{c^8D_L^2}(\pi 
+f_\text{orb})^{4/3}
 \end{equation}
@@
 
-The amplitude spectral density for a stationary system is finally defined as $ASD = h_{2} \sqrt{T_\text{obs}}$, such that the SNR for stationary source is simply, $\rho \sim ASD/S_n$.
-
-The Galactic foreground included in the \citet{Robson2019} LISA noise curve was generated using a different binary evolution code and set of model assumptions for DWD formation and evolution \citep{Toonen2012, Korol2017}.
-Thus, we use the detector curve only and generate an approximate foreground from each of our populations as follows.
-Instead of performing a full source subtraction algorithm \citep[e.g.][]{Littenberg2020}, which is out of the scope of this work, we calculate the PSD of the Galactic DWD population with a frequency resolution set by the LISA mission time as $1/T_{\rm{obs}}\sim1/4\,\rm{yr}^{-1}\sim8\times10^{-9}\,\rm{Hz}$.
-We then approximate the foreground as the running median of the PSD with a boxcar window with a width of $10^3$ frequency bins similar to \citet{Benacquista2006}.
-The Galactic DWD PSD is truncated near $10\,\rm{mHz}$ for both of our models because we remove all DWDs which experience Roche-lobe overflow.
-In order to smooth the effect of this truncation in our foreground, we fit each running median with fourth-order polynomials for GW frequencies up to $1\,\rm{mHz}$, thus allowing an approximation of the foreground PSD for higher frequencies.
-These fits are listed in Table~\ref{tbl:fits} where the polynomial is described as
+The amplitude spectral density for a stationary system is finally defined 
+as $ASD = h_{2} \sqrt{T_\text{obs}}$, such that the SNR for stationary 
+source is simply, $\rho \sim ASD/S_n$.
+
+The Galactic foreground included in the \citet{Robson2019} LISA noise 
+curve was generated using a different binary evolution code and set of 
+model assumptions for DWD formation and evolution \citep{Toonen2012, 
+Korol2017}. Thus, we use the detector curve only and generate an 
+approximate foreground from each of our populations as follows. Instead of 
+performing a full source subtraction algorithm 
+\citep[e.g.][]{Littenberg2020}, which is out of the scope of this work, we 
+calculate the PSD of the Galactic DWD population with a frequency 
+resolution set by the LISA mission time as 
+$1/T_{\rm{obs}}\sim1/4\,\rm{yr}^{-1}\sim8\times10^{-9}\,\rm{Hz}$. We then 
+approximate the foreground as the running median of the PSD with a boxcar 
+window with a width of $10^3$ frequency bins similar to 
+\citet{Benacquista2006}. The Galactic DWD PSD is truncated near 
+$10\,\rm{mHz}$ for both of our models because we remove all DWDs which 
+experience Roche-lobe overflow. In order to smooth the effect of this 
+truncation in our foreground, we fit each running median with fourth-order 
+polynomials for GW frequencies up to $1\,\rm{mHz}$, thus allowing an 
+approximation of the foreground PSD for higher frequencies. These fits are 
+listed in Table~\ref{tbl:fits} where the polynomial is described as
 \begin{equation}
 \label{eq:fit}
-    \log_{10}(\rm{confusion\ fit}/\rm{Hz}) = a\,x^4 + b\,x^3 + c\,x^2 + d\,x + e
+    \log_{10}(\rm{confusion\ fit}/\rm{Hz}) = a\,x^4 + b\,x^3 + c\,x^2 + 
+d\,x + e
 \end{equation}
-\noindent and $\rm{x}=\log_{10}(f_{\rm{GW}}/\rm{Hz})$.
-We add the fitted polynomial of the PSD's running median to the LISA noise PSD to obtain a sensitivity curve for each model \textbf{and variation}.
+\noindent and $\rm{x}=\log_{10}(f_{\rm{GW}}/\rm{Hz})$. We add the fitted 
+polynomial of the PSD's running median to the LISA noise PSD to obtain a 
+sensitivity curve for each model and variation.
 
@@
     \end{tabular}
-    \caption{Polynomial fitting coefficients for the confusion foreground fit of Equation~\ref{eq:fit} for each binary fraction model and parameter variation.}
+    \caption{Polynomial fitting coefficients for the confusion foreground 
+fit of Equation~\ref{eq:fit} for each binary fraction model and parameter 
+variation.}
     \label{tbl:fits}
@@
 
-\section{Metallicity effects on the formation and evolution of DWDs}\label{sec:results}
+\section{Metallicity effects on the formation and evolution of 
+DWDs}\label{sec:results}
 
 \subsection{DWD types and their formation channels}\label{sec:ini}
-As discussed in Section\,\ref{sec:bin_pop}, we consider four DWD sub-types, which each contribute differently to LISA's GW signals: He + He, CO + He, CO + CO, and ONe + X.
-Each sub-type has a unique distribution in their formation times, initial masses, radii, and orbital periods stemming from variations in their evolution channels and their formation efficiency.
-Here we describe the general formation scenarios and population properties of Galactic close DWDs which may be observable by LISA.
-
-He WDs are unable to form through single star evolution within the lifetime of the Milky Way.
-Instead, they originate through interactions in close binary systems or binaries with large eccentricities.
-Because of this, He WDs are able to form with low component masses on order $\sim$ 0.1M$_\odot$, with the majority of He WDs in our simulations having masses between 0.2-0.5 M$_\odot$.
-He + He DWDs form through evolution of close binary systems, during which their envelopes are both stripped through RLO and CE phase interactions before Helium ignition occurs.
-The two progenitor stars generally have masses $\lesssim 3 M_\odot$ which is lower than the progenitors of other DWD types.
-Our simulated He + He DWDs have an approximately constant distribution of formation times $\gtrsim$ 2.5 Gyr.
-Lastly, since the ZAMS separations are skewed towards shorter values, we also see that the resulting DWD separations are smaller on average than that of other DWD types.
+As discussed in Section\,\ref{sec:bin_pop}, we consider four DWD 
+sub-types, which each contribute differently to LISA's GW signals: He + 
+He, CO + He, CO + CO, and ONe + X. Each sub-type has a unique distribution 
+in their formation times, initial masses, radii, and orbital periods 
+stemming from variations in their evolution channels and their formation 
+efficiency. Here we describe the general formation scenarios and 
+population properties of Galactic close DWDs which may be observable by 
+LISA.
+
+He WDs are unable to form through single star evolution within the 
+lifetime of the Milky Way. Instead, they originate through interactions in 
+close binary systems or binaries with large eccentricities. Because of 
+this, He WDs are able to form with low component masses on order $\sim 
+0.1\,M_\odot$, with the majority of He WDs in our simulations having 
+masses between 0.2-0.5 $M_\odot$. He + He DWDs form through evolution of 
+close binary systems, during which their envelopes are both stripped 
+through RLO and CE phase interactions before Helium ignition occurs. The 
+two progenitor stars generally have masses $\lesssim 3\,M_\odot$ which is 
+lower than the progenitors of other DWD types. Our simulated He + He DWDs 
+have an approximately constant distribution of formation times $\gtrsim 
+2.5\,\rm{Gyr}$. Lastly, since the ZAMS separations are skewed towards 
+shorter values, we also see that the resulting DWD separations are smaller 
+on average than that of other DWD types.
 
@@
 	\includegraphics[width=\textwidth]{figures/form_eff.pdf}
-    \caption{The DWD formation efficiency vs metallicity of DWD populations simulated with \cosmic.
-Each panel shows the formation efficiency for a given DWD type \textbf{and variation}.
-The solid lines indicate the formation efficiency for model FZ which incorporates a metallicity-dependent binary fraction.
-The dashed lines indicate the formation efficiency for model F50, which assumes a constant binary fraction of $50\%$.
-The DWD formation efficiency drops by a factor of $4-5$ for model FZ and a factor of \textbf{1-5} for model F50.
-See Section~\ref{sec:formeff} for a careful description of the trends for each DWD type.}
+    \caption{The DWD formation efficiency vs metallicity of DWD 
+populations simulated with \cosmic. Each panel shows the formation 
+efficiency for a given DWD type and variation. The solid lines indicate 
+the formation efficiency for model FZ which incorporates a 
+metallicity-dependent binary fraction. The dashed lines indicate the 
+formation efficiency for model F50, which assumes a constant binary 
+fraction of $50\%$. The DWD formation efficiency drops by a factor of 
+$4$--$5$ for model FZ and a factor of $1$--$5$ for model F50. See 
+Section~\ref{sec:formeff} for a careful description of the trends for each 
+DWD type.}
     \label{fig:form_eff}
@@
 
-A CO WD forms when a star is able to begin the helium burning process before its envelope is stripped.
-Thus to form a CO + He DWD, RLO and CE stages occur after one component experiences core helium burning, but before the other component can.
-Most close CO + He DWDs form in approximately 2 Gyr after ZAMS and with very short periods because the He WD is formed through the ejection of a common envelope which greatly reduces the orbital separation.
-Because of these short formation separations, many CO + He DWDs merge before the present day.
-Due to their asymmetric mass distributions, they have lower chirp masses, but their shorter periods make them important candidates for LISA detection.
-
-To prevent the two stars' envelopes from being stripped before helium ignition, CO + CO DWDs typically form from progenitors in wider orbits, and the two components may have little to no interaction during their evolution from ZAMS to DWD.
-CO DWDs thus have a distribution in progenitor separation that extends to larger values than for other DWD types.
-Most \textbf{CO + CO} DWDs need $> 0.3$ Gyr to form, have component WD masses between $0.35$--$1.0\,M_\odot$, and make up the majority of the DWD population.
-
-ONe WDs are rare and typically form from massive progenitor stars which evolve through the asymptotic giant branch (AGB) phase, thus resulting in a higher mass WD.
-All ONe WDs in our \cosmic\ populations, e.g., have progenitor ZAMS masses above $4\,M_\odot$, and the resulting ONe WDs have a relatively flat distribution of masses from $1.05\,M_\odot$ up to the Chandrasekkhar limit of $1.4\,M_\odot$.
-Because an ONe WD can have a companion of any other WD type in our study, there is a spread in their distributions for separation, secondary mass, final orbital period, and formation time.
-In general, however, these systems result from wider separations to allow for the evolution of the ONe component without merging.
-\textbf{For example,} all initial separations in our \cosmic \ populations have separations $\gtrsim 1.5\,R_\odot$.
-ONe + X DWDs can form on short timescales, as low as $30\,\rm{Myr}$, for the majority of high-metallicity systems.
-
-\subsection{Metallicity-dependent trends in the formation efficiency of DWDs}\label{sec:formeff}
-The number of DWDs formed per unit solar mass of ZAMS star formation, or DWD formation efficiency $\eta_{\rm{form}}(Z)$, varies with metallicity.
-Consequently, a metallicity-dependent binary fraction further impacts the efficiency of DWD formation within the Galaxy.
-Figure \ref{fig:form_eff} shows the DWD formation efficiency as a function of metallicity for each DWD type\textbf{, binary fraction models, and binary evolution parameter variations}.
-In general, the formation efficiency decreases with increasing metallicity.
-This effect is exaggerated for model FZ which assumes a \textbf{close} binary fraction which also decreases with increasing metallicity.
-\textbf{In the following sub-sections, we describe the formation efficiency trends for our fiducial variation in detail and then describe the changes arising from each binary evolution parameter variation.}
-
-\subsubsection{\textbf{Fiducial formation efficiency trends}}\label{sec:formeff_fid}
-
-For He + He DWDs, the sudden drop in formation efficiency near $\log(Z/Z_{\odot})=-1.0$, is generally caused by the timescale for which the initially more massive star in the DWD progenitor overflows it's Roche lobe.
-At lower metallicities, donors tend to fill their Roche lobes while they are still on the main sequence and the mass transfer remains stable \textbf{and serves to widen the binary}.
-This is because, in our \cosmic\ models lower metallicity stars evolve faster than high-metallicity stars and have larger radii near the end of the MS.
-At higher metallicities, mass transfer is initiated when the donor has left the main sequence, and the binary enters a common envelope evolution.
-The ZAMS orbital period leads to different specific evolutionary channels.
-For short-period systems with periods below $10~\rm{days}$, \textbf{and common envelope} leads to a stellar merger due to insufficient orbital energy to eject the envelope.
-Stellar mergers continue to dominate the evolutionary pathways of systems with intermediate orbital periods ($1 < \log_{10}(P_{\rm{orb}}/\rm{day}) < 2.5$).
-However, an additional growing number of merging systems arises with one WD component and one stellar companion, and systems which don't interact at all and thus do not form a He + He DWD.
-The distinction between the various scenarios in this intermediate orbital period range depends on the combination of their ZAMS masses and orbital periods.
-Finally, at wider initial periods $\log_{10}(\rm{P}) > 2.5$, the decrease in formation efficiency is dominated by systems which never interact and thus do not form a DWD before the present day.
+A CO WD forms when a star is able to begin the helium burning process 
+before its envelope is stripped. Thus to form a CO + He DWD, RLO and CE 
+stages occur after one component experiences core helium burning, but 
+before the other component can. Most close CO + He DWDs form in 
+approximately 2 Gyr after ZAMS and with very short periods because the He 
+WD is formed through the ejection of a common envelope which greatly 
+reduces the orbital separation. Because of these short formation 
+separations, many CO + He DWDs merge before the present day. Due to their 
+asymmetric mass distributions, they have lower chirp masses, but their 
+shorter periods make them important candidates for LISA detection.
+
+To prevent the two stars' envelopes from being stripped before helium 
+ignition, CO + CO DWDs typically form from progenitors in wider orbits, 
+and the two components may have little to no interaction during their 
+evolution from ZAMS to DWD. CO DWDs thus have a distribution in progenitor 
+separation that extends to larger values than for other DWD types. Most CO 
++ CO DWDs need $> 0.3$ Gyr to form, have component WD masses between 
+$0.35$--$1.0\,M_\odot$, and make up the majority of the DWD population.
+
+ONe WDs are rare and typically form from massive progenitor stars which 
+evolve through the asymptotic giant branch phase, thus resulting in a 
+higher mass WD. All ONe WDs in our \cosmic\ populations, e.g., have 
+progenitor ZAMS masses above $4\,M_\odot$, and the resulting ONe WDs have 
+a relatively flat distribution of masses from $1.05\,M_\odot$ up to the 
+Chandrasekkhar limit of $1.4\,M_\odot$. Because an ONe WD can have a 
+companion of any other WD type in our study, there is a spread in their 
+distributions for separation, secondary mass, final orbital period, and 
+formation time. In general, however, these systems result from wider 
+separations to allow for the evolution of the ONe component without 
+merging. For example, all initial separations in our \cosmic \ populations 
+have separations $\gtrsim 1.5\,R_\odot$. ONe + X DWDs can form on short 
+timescales, as low as $30\,\rm{Myr}$, for the majority of high-metallicity 
+systems.
+
+\subsection{Metallicity-dependent trends in the formation efficiency of 
+DWDs}\label{sec:formeff}
+The number of DWDs formed per unit solar mass of ZAMS star formation, or 
+DWD formation efficiency $\eta_{\rm{form}}(Z)$, varies with metallicity. 
+Consequently, a metallicity-dependent binary fraction further impacts the 
+efficiency of DWD formation within the Galaxy. Figure \ref{fig:form_eff} 
+shows the DWD formation efficiency as a function of metallicity for each 
+DWD type, binary fraction model, and binary evolution parameter variation. 
+In general, the formation efficiency decreases with increasing 
+metallicity. This effect is exaggerated for model FZ which assumes a close 
+binary fraction which also decreases with increasing metallicity. In 
+\textbf{this section}, we \textbf{give a brief overview of the general 
+trends observed in formation efficiency and their underlying causes. For a 
+detailed description for each DWD type and binary evolution parameter 
+variation, see Appendix \ref{appendix:form_eff}.}
+
+\textbf{There are two common ways that the formation of DWDs from stellar 
+progenitors is inhibited. The first is through stellar mergers, where the 
+binary merges before both components become WDs. The second is due to 
+evolutionary outcomes like forming a different DWD type, or not forming a 
+DWD by the present day. For all DWD types except ONe + X, which has other 
+dominating affects hindering formation efficiency like 
+metallicity-dependent stellar winds, we find that different regimes of 
+ZAMS orbital period leads to different specific evolutionary channels.}
+
+\textbf{In our \cosmic\ models, lower-metallicity stars evolve faster than 
+high-metallicity stars and have larger radii near the end of the MS. This 
+changes the timescales of RLO: low-metallicity stars tend to fill their 
+Roche lobes while still on the MS, meaning mass transfer can remain stable 
+which serves to widen the binary. In contrast, high-metallicity systems 
+initiate mass transfer after the donor has left the main sequence, so the 
+binary is more likely to enter a CE phase. Moreover, high-metallicity 
+progenitors tend to have deeper convective envelopes such that a larger 
+fraction of their mass is contained in the envelope relative to 
+lower-metallicity counterparts of the same mass \citep{Amard2019, 
+Amard2020}. When these systems enter a CE phase, it thus requires more 
+orbital energy to eject the CE than for a low-metallicity star at the same 
+point in its evolution, causing a large amount of orbital shrinking. These 
+effects often leads to a stellar merger at higher metallicities for a 
+system that would have survived the CE phase at a lower metallicity, thus 
+causing a decrease in formation efficiency with metallicity.}
+
+The skews introduced by the metallicity-dependent ZAMS orbital period 
+distribution and binary fraction of FZ also contribute to the formation 
+efficiency trends. The log-normal metallicity-dependent $P_{\rm{orb}}$ 
+distribution increasingly skews towards orbital periods below 10$^4$ days 
+for decreasing metallicity. This amplifies the effects of 
+metallicity-dependent stellar evolution discussed above. For example, the 
+skew induces more mergers at high metallicities where the deeper 
+convective envelope leads to increased orbital shrinkage. However, it is 
+also of note that the log-uniform orbital period distribution of F50 
+produces a higher number of the shortest-orbital period systems (below 
+$\sim100$ days) than FZ, since the tails of the FZ distribution fall 
+quickly below this threshold. These systems also have a propensity for 
+merging before the formation of a DWD.
+
+\textbf{Our binary evolution parameter variations emphasizes the interplay 
+of the aforementioned effects of the distributions of F50 and FZ with the 
+physics of binary evolution. For example, the lower CE efficiency of 
+variation $\alpha25$ is the dominating formation efficiency inhibitor 
+since it induces a higher merger rate. In contrast, variations $\alpha5$ 
+and $q3$ relax hindrances to DWD formation (through an increased ability 
+to survive a CE phase and undergo stable mass transfer respectively). We 
+thus find less mergers overall in both cases, and that the effect of the 
+metallicity-dependent $P_{\rm{orb}}$ distribution dominates the formation 
+efficiency trends rather than restrictions imposed by binary evolution 
+prescriptions.
+}
 
@@
 	\includegraphics[width=\textwidth]{figures/CEsep.pdf}
-    \caption{Average interaction separation, $\overline{\mathrm{a}}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type \textbf{and variation} from model F50.
-Solid lines show the average separation at the first RLO for binaries in each metallicity bin.
-The shaded regions show the $1\sigma$ spread around the mean within each metallicity bin.
-The average interaction separation increases with metallicity for every DWD type\textbf{, except for $\alpha5$ which remains approximately constant for CO + He and ONe + X}.
-The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts.
-The sharp drop of the CO + CO average at the highest-metallicity bin \textbf{of the fiducial variation} is due to binning effects of the figure: it only contains \textbf{506} systems, of which the majority stem from a single low-separation system which was sampled \textbf{468} times times during the simulation.
-\textbf{The regions of metallicity where there is not shading beyond the mean trend are also due to low numbers of DWDs in each bin}.}
+    \caption{Average interaction separation, 
+$\overline{\mathrm{a}}_{\rm{CE}}$ of progenitors of close DWDs across 
+metallicity for each DWD type and variation from model F50. Solid lines 
+show the average separation at the first RLO for binaries in each 
+metallicity bin. The shaded regions show the $1\sigma$ spread around the 
+mean within each metallicity bin. The average interaction separation 
+increases with metallicity for every DWD type, except for $\alpha5$ which 
+remains approximately constant for CO + He and ONe + X. The positive trend 
+in the average interaction separation is a direct consequence of larger 
+envelope masses of higher-metallicity donors which are less evolved than 
+their lower-metallicity counterparts. The sharp drop of the CO + CO 
+average at the highest-metallicity bin of the fiducial variation is due to 
+binning effects of the figure: it only contains 506 systems, of which the 
+majority stem from a single low-separation system which was sampled 468 
+times times during the simulation. The regions of metallicity where there 
+is not shading beyond the mean trend are also due to low numbers of DWDs 
+in each bin.} 
     \label{fig:CEsep}
@@
 
-For short-period CO + He DWD progenitor binaries with orbital periods below $\sim30~\rm{days}$, the only channel for \textbf{stellar} mergers before DWD formation is during a CE evolution.
-This channel is similar to the stellar merger channel for He + He DWDs, but due to higher-mass progenitors the CE evolution results in the binary component with a higher mass becoming a CO WD.
-At higher metallicities, the CO WD merges with its companion.
-Higher-metallicity progenitors have a larger fraction of their mass in the convective envelope when compared to lower-metallicity stars of the same mass \citep{Amard2019, Amard2020}.
-Thus a CE phase with a higher-metallicity progenitor requires more orbital energy to eject the common envelope, causing a larger amount of orbital shrinking which results in a merger later in its binary evolution.
-
-For CO + He DWD progenitor systems with intermediate orbital periods ($1.5\leq \log_{10}(P_{\rm{orb}}/\rm{day})< 2.5$) the mechanisms which impact formation efficiency are complex.
-The dominant way to \textbf{not form} CO + He DWDs is stellar mergers that occur during the second CE phase.
-For lower-metallicity systems, the second CE is successful, while the opposite is true for higher-metallicity systems.
-This is again because the envelope mass of the CE evolution donor at higher metallicity is larger than it would be at lower metallicity and thus requires more orbital energy to eject in the CE phase.
-This leads to shorter post-CE orbital periods after the first CE phase and hence mergers during the second phase.
-
-If a lower-metallicity system forms a CO + He DWD and a higher-metallicity system does not, this is because the initially more massive binary component initiates a CE while on the giant branch (GB) instead of the asymptotic giant branch (AGB).
-This instead leaves behind a He WD with a stellar companion, which is the dominating scenario that restricts formation efficiency.
-There are a few edge cases where either a He + He DWD is formed instead, or when a CO WD and a stellar companion is formed and there has been very nearly but not quite enough time for a CO + He DWD to form.
-
-Long-period binaries with $\log_{10}(P_{\rm{orb}}/\rm{day})>2.5$ also display complex scenarios that hinder CO + He DWD formation.
-In near-equal contributions, our \cosmic\ simulations produce either stellar mergers or stable non-DWD binaries at the end of the Hubble time.
-At these orbital periods, stellar mergers always occur with a CE phase between a stellar companion and a CO or He WD.
-Similar to binaries with shorter orbital periods, the mergers occur because of increased CE donor envelope masses at higher metallicities.
-A subdominant channel of stable He + He DWDs can also occur when a high-metallicity primary overflows it's Roche lobe while still on the GB and thus forms a He WD.
-\textbf{In general, a CO + He binary fails to form because either a CO + CO or He + He is formed instead, or a merger occurs before DWD formation.
-We see higher formation efficiencies for FZ than F50 because CO + He DWDs prefer to form in progenitor binaries with orbital periods near $\log_{10}$(P$_{\rm{orb}}$/day)$\sim2-4$, which is where the orbital period distribution of FZ peaks.}
-
-The decrease in the CO + CO DWD formation efficiency with increasing metallicity stems from different evolutionary channels which arise at the ZAMS orbital period boundary of $\log_{10}(P_{\rm{orb}}/\rm{day})\simeq3$.
-We find that for binaries with orbital periods below this boundary, the most common way that CO + CO DWDs form at lower metallicities but not at higher metallicities is through stellar mergers during a CE phase with a donor that is still on the GB.
-For lower-metallicity binaries, which evolve on faster timescales, the primaries enter CE evolution while on the AGB instead and the binary is able to survive.
-For binaries with orbital periods above the boundary, the vast majority of systems with wide initial orbits end up as stable binaries.
-The systems which don’t form a CO DWD at high metallicity do so because one or both of the binary components initiate a CE phase while still on the GB thus producing a CO + He or He + He DWD.
-
-The strongest effect which hinders formations of higher-metallicity ONe + X DWDs is the strength of metallicity-dependent stellar winds assumed in our model \citep{Vink2001}.
-The strength of line-driven winds varies more strongly for the more massive ($\geq5\,\rm{M}_\odot$) progenitors of ONe WDs relative to the other lower mass WD progenitors.
-At higher metallicities, ONe WD progenitors can lose enough mass through winds such that they don't ignite their CO cores and thus leave behind a CO WD.
-Conversely, the lower-metallicity progenitors retain enough mass to cause carbon ignition and leave behind an ONe WD.
-
-\subsubsection{\textbf{Parameter variations formation efficiency trends}}\label{subsec:formeff_vars}
-
-\textbf{For our simulations with binary evolution parameter variations, we see an interplay of the physics of binary evolution with skews introduced by the metallicity-dependent orbital period distribution and binary fraction.
-Below, we summarize how the formation efficiency of each DWD type is impacted by the parameter variations.
-Two important features of our FZ and F50 models drive the differences in our binary evolution parameter variations.
-First, the log-normal metallicity-dependent ZAMS orbital period distribution increasingly skews towards orbital periods below $10^4$ days for decreasing metallicity.
-However, second, the log-uniform P$_{\rm{orb}}$ distribution of F50 produces a higher number of the shortest orbital period systems (below $\sim 100$ days) than for FZ as the tails of the FZ distribution fall quickly below this threshold.}
-
-\textbf{For binary systems leading to He + He DWDs, there are many more mergers for $\alpha25$ than for the fiducial variation.
-The lower CE efficiency leads to DWD progenitor mergers from a failed CE ejection, or the CE shrinking the orbit such that it then merges on the second CE phase.
-Because there are more ZAMS binaries with orbital periods shorter than $10^4$ days in F50, as the population evolves there are more likely to be binary interactions in the population for F50 than FZ.
-This leads to more mergers in $\alpha25$ occurring for F50 before formation of the DWD and thus a lower formation efficiency overall for F50 in contrast to FZ.
-This is illustrated in the $\alpha25$ He + He plot of Figure \ref{fig:form_eff}.
-Similar to the fiducial parameter variation, a binary that becomes a He + He DWD at lower metallicities would merge before becoming one at higher metallicities because of the longer evolution timescales.
-These later interactions lead to closer post-CE separations and thus more mergers.
-The dip at [Fe/H] $\simeq -1.5$ stems from mergers before the DWD forms, again similar to the fiducial parameter variation.
-The peak that occurs in $\alpha25$ at $\sim 10\%$ Z$_\odot$ arises from binaries evolving faster and thus interacting earlier as metallicity increases.
-This means that equivalent binaries that would have merged or formed a CO + He DWD instead at lower metallicities now survive to produce a He + He DWD.
-At higher metallicities, there are a higher proportion of wide ZAMS binaries, which evolve off the Main Sequence too slowly to form a He + He DWD, causing the efficiency drop.}
-
-\textbf{For $\alpha5$, there are significantly fewer DWD progenitor mergers since binaries are more likely to survive a CE phase due to the higher CE ejection efficiency.
-Systems that would normally merge for $\alpha25$ instead survive, and are shrunk to short orbits through CE interactions to reside in the LISA band at present.
-The number of DWDs then makes up a higher fraction of the total simulated binary population , thus we see in general higher formation efficiencies than for the fiducial parameter variation which sets $\alpha=1$.
-This effect is even more pronounced in comparison with the $\alpha25$ variation which sets $\alpha=0.25$.}
-
-\textbf{Beyond the effects described above, the efficiency drop across metallicity is similar to the fiducial parameter variation in that it depends on the metallicity-dependent ZAMS orbital period distribution emphasizing short-period systems at low metallicities, and on the change of formation channel for different period ranges across metallicity.
-We find the highest formation efficiency for variation $q3$.
-Only the shortest-period binaries do not form a DWD through mergers at higher metallicities.
-At low metallicities, even binaries with ZAMS orbital periods P$_{\rm{orb}}\lesssim 100$ days form He + He DWDs, with binaries in model FZ reaching ZAMS orbital periods less than a day in length.
-This leads to a higher formation efficiency from F50 over FZ for parameter variation $q3$ because of the higher number of shortest-period ZAMS binaries in the log-uniform distribution of F50.}
-
-\textbf{For CO + He binaries, there are again many more mergers for parameter variation $\alpha25$ relative to the fiducial case.
-This is the dominant way that progenitors do not evolve to produce DWDs at higher metallicities.
-At low metallicities, a number of progenitor binaries form CO + CO DWDs instead of He + CO DWDs.
-This is especially the case near $\log_{10}$(Z/Z$_\odot)\sim -2$, where RLO occurs late enough in a binary's evolution that mass transfer remains stable and CO + CO's are formed rather than CO + He, hence producing a dip in the formation efficiency.
-Because parameter variation $\alpha5$ leads to less mergers due to the high CE efficiency, the formation efficiency is mostly governed by the metallicity-dependent ZAMS orbital period distribution.
-At higher metallicities, the majority of cases in model FZ where progenitors don't produce a CO + He DWD are from progenitor mergers or from He + He DWDs forming instead of CO + He DWDs.
-At higher metallicities, the ZAMS orbital period distribution of FZ also drops below that of F50 and extends out to orbital periods beyond what would form a CO + He.
-This causes the formation efficiencies for FZ and F50 to cross at log$_{10}$(Z/Z$_\odot$)$\sim-0.5$.
-This is also apparent for the $q3$ variation, and to a lesser extent in the fiducial case.
-In $q3$, for any given orbital period we find that lower mass DWDs originate from lower metallicities, thus leading to an approximately constant formation efficiency.}
-
-\textbf{For CO + CO, across all variations, very close ZAMS binaries (P$_{\rm{orb}}\sim\mathcal{O}(100$ days)) at high metallicities form a CO + He or He + He DWD instead of a CO + CO because the binary interacts before core Helium burning of one or both components.
-There are again many more mergers in $\alpha25$, and fewer mergers for $\alpha5$.
-Due to the high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods survive to become CO + CO DWDs rather than merging or becoming CO + He or He + He DWDs.
-There are less fewer mergers overall for $q3$ than all the $\alpha$ variations because the first RLO occurrence leads to stable mass transfer from the primary to the secondary rather than multiple CE phases.
-For both the $\alpha5$ and $q3$ variations, the majority of CO + CO DWDs originate in wide enough orbits that they don't interact before DWD formation.
-This leads to an approximately constant formation efficiency across metallicity in both cases.}
-
-\textbf{For model FZ, the ONe + X formation efficiencies follow similar trends aross each parameter variation.
-Their formation scenarios are similar to those described above for ONe + X DWDs in the fiducial binary evolution parameter set.
-The main difference between each parameter variation is only in the number of sources produced since the number of stellar mergers that occur before DWD formation increases with decreasing common envelope efficiency.
-In model F50, the formation efficiency is decreased significantly for parameter variation $\alpha25$ because the log-uniform orbital period distribution produces many ZAMS binaries with very short orbital periods which lead to stellar mergers during the CE phases.}
-
-\subsection{Metallicity trends in DWD progenitor common envelope separation}\label{sec:CEsep}
+\subsection{Metallicity trends in DWD progenitor common envelope 
+separation}\label{sec:CEsep}
 
@@
 	\includegraphics[width=\textwidth]{figures/lisa_nums.pdf}
-    \caption{The number of LISA-band systems formed for each DWD type \textbf{and parameter variation} as a function of the base-10 logarithm of metallicity, normalized to solar value.
-The solid line shows the FZ population with a metallicity-dependent \textbf{close} binary fraction incorporated, and the dashed line shows the F50 population for a standard binary fraction of 0.5.
-The LISA population of DWDs is dominated by stars with super-solar metallicities.
-This is true even for model FZ, which drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond Z$\simeq$Z$_\odot$.
-There is a double peak in the \textbf{fiducial and $\alpha25$} He + He populations; the first peak is caused by the sharp drop in formation efficiency past $\rm{Z}\simeq0.1 \rm{Z}_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
+    \caption{The number of LISA-band systems formed for each DWD type and 
+parameter variation as a function of the base-10 logarithm of metallicity, 
+normalized to solar value. The solid line shows the FZ population with a 
+metallicity-dependent close binary fraction incorporated, and the dashed 
+line shows the F50 population for a standard binary fraction of 0.5. The 
+LISA population of DWDs is dominated by stars with super-solar 
+metallicities. This is true even for model FZ, which drops off 
+significantly for higher metallicities, because of the large number of 
+stars formed in \textbf{m12i} beyond $Z\simeq Z_\odot$. There is a double 
+peak in the fiducial and $\alpha25$ He + He populations; the first peak is 
+caused by the sharp drop in formation efficiency past 
+$Z\simeq0.1\,Z_\odot$ which is then greatly overcompensated for by the 
+amount of star formation at higher metallicities which forms the second 
+peak.}
     \label{fig:lisa_nums}
@@
 
-All systems that end up radiating GWs in the LISA band have undergone at least one phase of CE evolution.
-For systems which experience a stable RLO mass transfer in the first interaction, the CE phase plays a key role in shrinking systems with initially wide separations to bring them into the LISA band.
-
-Figure \ref{fig:CEsep} shows the average separation at the first instance of CE evolution, $a_{\text{CE}}$ of all DWD progenitors that result in systems orbiting in the LISA frequency band at present day, as a function of metallicity for each DWD type.
-The solid lines denote the average value, and the $1\sigma$ variance is shown in the surrounding shading.
-\textbf{We show this for our fiducial variation and each of our binary parameter variations.
-For our fiducial, $\alpha25$ and $\alpha5$ parameter variations,} the average CE separation increases in general across metallicity.
-Higher-metallicity binaries will interact earlier in the binary's lifetime than a lower-metallicity binary of equal separation due to their relatively larger maximum radii.
-Since higher-metallicity binaries are also more likely to merge during CE interactions because of their relatively more massive donor envelopes, the DWDs which survive and eventually orbit in the LISA band originate from systems with higher interaction separations which allow their orbits to shrink significantly during CE phases without merging.
-This regulation plays a key role in smearing out any observable effects of a metallicity-dependent binary fraction in the population of DWDs observable by LISA.
-
-\textbf{The slope of the increase for these three models is dictated by the CE efficiency $\alpha$.
-With increasing metallicity there is a deepening of the convective envelope of the star compared to its lower metallicity counterparts at the same point in its evolution, requiring more orbital energy to be available in order to eject the CE.
-Thus the high-metallicity binaries must have even wider separations for lower $\alpha$ values to ensure the binary does not merge before the envelope is ejected.
-We therefore see a steeper separation slope for $\alpha25$, a less steep slope for $\alpha5$, and an intermediate slope for our fiducial variation which has $\alpha=1$.}
-
-\textbf{The DWDs in model $q3$ that survive into the LISA band at present day have different formation channels than those of our other three parameter variations.
-Most importantly, in contrast to two CE phases for the fiducial, $\alpha25$ and $\alpha5$ parameter variations, the DWD progenitors in parameter variation $q3$ typically undergo a phase of stable mass transfer as the binary's first interaction.
-During mass transfer the orbit first shrinks, and then will slightly widen once the binary's mass ratio flips.
-This process leads to formation of the first WD component.
-The companion is then formed later in the binary's evolution through a CE phase.
-We show the CE phase which results from the second interaction for parameter variation $q3$ in Figure \ref{fig:CEsep}.}
-
-\textbf{Of particular interest in variation $q3$ is the CO + He systems.
-For all of the $q3$ CO + He binaries that reside in the LISA band at present, the He WD unexpectedly forms first through stable mass transfer, with the CO WD forming second through a CE.
-These binaries tend to all have similar resulting orbital separations from mass transfer, as can be seen by the relatively constant curve for CO + He's separation at CE onset.
-There is still a slight increasing trend in CO + He (as well as CO + CO and a more pronounced trend in He + He) for $q3$ that stems from the metallicity-dependent convective envelope discussion above.
-We also see that the average interaction separation are overall lower for variations $q3$ and $\alpha5$ than for the other two due to the orbital shrinkage that has already occurred from stable mass transfer and the efficient CE phase that will lead to minimal orbital shrinkage respectively.}
+All systems that end up radiating GWs in the LISA band have undergone at 
+least one phase of CE evolution. For systems which experience a stable RLO 
+mass transfer in the first interaction, the CE phase plays a key role in 
+shrinking systems with initially wide separations to bring them into the 
+LISA band.
+
+Figure \ref{fig:CEsep} shows the average separation at the first instance 
+of CE evolution, $a_{\text{CE}}$ of all DWD progenitors that result in 
+systems orbiting in the LISA frequency band at present day, as a function 
+of metallicity for each DWD type. The solid lines denote the average 
+value, and the $1\sigma$ variance is shown in the surrounding shading. We 
+show this for our fiducial variation and each of our binary parameter 
+variations. For our fiducial, $\alpha25$ and $\alpha5$ parameter 
+variations, the average CE separation increases in general across 
+metallicity. Higher-metallicity binaries will interact earlier in the 
+binary's lifetime than a lower-metallicity binary of equal separation due 
+to their relatively larger maximum radii. Since higher-metallicity 
+binaries are also more likely to merge during CE interactions because of 
+their relatively more massive donor envelopes, the DWDs which survive and 
+eventually orbit in the LISA band originate from systems with higher 
+interaction separations which allow their orbits to shrink significantly 
+during CE phases without merging. This regulation plays a key role in 
+smearing out any observable effects of a metallicity-dependent binary 
+fraction in the population of DWDs observable by LISA.
+
+The slope of the increase for these three models is dictated by the CE 
+efficiency $\alpha$. \textbf{As discussed in Section \ref{sec:formeff}, 
+with} increasing metallicity there is a deepening of the convective 
+envelope of the star \textbf{compared to its lower metallicity 
+counterpart}, requiring more orbital energy to be available in order to 
+eject the CE. Thus the high-metallicity binaries must have even wider 
+separations for lower $\alpha$ values to ensure the binary does not merge 
+before the envelope is ejected. We therefore see a steeper separation 
+slope for $\alpha25$, a less steep slope for $\alpha5$, and an 
+intermediate slope for our fiducial variation which has $\alpha=1$.
+
+The DWDs in model $q3$ that survive into the LISA band at present day have 
+different formation channels than those of our other three parameter 
+variations. Most importantly, in contrast to two CE phases for the 
+fiducial, $\alpha25$ and $\alpha5$ parameter variations, the DWD 
+progenitors in parameter variation $q3$ typically undergo a phase of 
+stable mass transfer as the binary's first interaction. During mass 
+transfer the orbit first shrinks, and then will slightly widen once the 
+binary's mass ratio flips. This process leads to formation of the first WD 
+component. The companion is then formed later in the binary's evolution 
+through a CE phase. We show the CE phase which results from the second 
+interaction for parameter variation $q3$ in Figure \ref{fig:CEsep}.
+
+Of particular interest in variation $q3$ is the CO + He systems. For all 
+of the $q3$ CO + He binaries that reside in the LISA band at present, the 
+He WD unexpectedly forms first through stable mass transfer, with the CO 
+WD forming second through a CE. These binaries tend to all have similar 
+resulting orbital separations from mass transfer, as can be seen by the 
+relatively constant curve for CO + He separation at CE onset. There is 
+still a slight increasing trend in CO + He (as well as CO + CO and a more 
+pronounced trend in He + He) for $q3$ that stems from the 
+metallicity-dependent convective envelope discussion above. We also see 
+that the average interaction separation are overall lower for variations 
+$q3$ and $\alpha5$ than for the other two due to the orbital shrinkage 
+that has already occurred from stable mass transfer and the efficient CE 
+phase that will lead to minimal orbital shrinkage respectively.
 
@@
 
-While metallicity impacts the intrinsic properties of our simulated DWD populations as described in Sections~\ref{sec:formeff} and \ref{sec:CEsep}, when we consider the present-day Galactic close DWDs we find that the population detectable by LISA \textbf{largely only changes numerically}.
-The number of DWDs in the LISA frequency band decreases by $\sim50\%$ when comparing model F50 to model FZ \textbf{for variations $\alpha5$ and $q3$, but remains approximately unchanged for our fiducial and $\alpha25$ variations.}
+While metallicity impacts the intrinsic properties of our simulated DWD 
+populations as described in Sections~\ref{sec:formeff} and 
+\ref{sec:CEsep}, when we consider the present-day Galactic close DWDs we 
+find that the population detectable by LISA largely only changes 
+\textbf{in total number, but not in frequency distribution}. The number of 
+DWDs in the LISA frequency band decreases by $\sim50\%$ when comparing 
+model F50 to model FZ for variations $\alpha5$ and $q3$, but remains 
+approximately unchanged for our fiducial and $\alpha25$ variations.
 
@@
 	\includegraphics[width=\textwidth]{figures/PSD.pdf}
-    \caption{The PSD of the entire Galactic DWD GW foreground, summed over all metallicities and DWD types vs GW frequency for models FZ and F50\textbf{, where the PSD is downsampled by a factor of $10$ for plotting purposes}.
-\textbf{Each panel shows a different parameter variation.} The vertical lines show the PSD where model F50 is shown in dark blue and model FZ is shown in light blue.
-The dashed lines show fits to the rolling boxcar median of width 1000 bins for each PSD (see Section \ref{sec:LISA_obs} for a discussion).
-A metallicity-dependent binary fraction (model FZ) yields fewer DWDs across all frequencies than a $50\%$ binary fraction (model F50) by roughly a factor of $2$ for the $\alpha5$ and $q3$ parameter variations.
-This produces a lower GW confusion foreground for frequencies with f$_{\rm{GW}}\leq\sim10^{-3}$ Hz.
-\textbf{In contrast, the fiducial and $\alpha25$ parameter variations show very similar confusion foregrounds.}}
+    \caption{The PSD of the entire Galactic DWD GW foreground, summed over 
+all metallicities and DWD types vs GW frequency for models FZ and F50, 
+where the PSD is downsampled by a factor of $10$ for plotting purposes. 
+Each panel shows a different parameter variation. The vertical lines show 
+the PSD where model F50 is shown in dark blue and model FZ is shown in 
+light blue. The dashed lines show fits to the rolling boxcar median of 
+width 1000 bins for each PSD (see Section \ref{sec:LISA_obs} for a 
+discussion). A metallicity-dependent binary fraction (model FZ) yields 
+fewer DWDs across all frequencies than a $50\%$ binary fraction (model 
+F50) by roughly a factor of $2$ for the $\alpha5$ and $q3$ parameter 
+variations. This produces a lower GW confusion foreground for frequencies 
+with f$_{\rm{GW}}\leq\sim10^{-3}$ Hz. In contrast, the fiducial and 
+$\alpha25$ parameter variations show very similar confusion foregrounds.}
     \label{fig:PSD}
@@
 	\includegraphics[width=\textwidth]{figures/LISA_SNR_fiducial.pdf}
-    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for each DWD type where the top row shows the population from model F50 and the bottom row shows the population from model FZ \textbf{for the fiducial variation}.
-In each panel, the LISA sensitivity curve, including the confusion foreground for each model, is shown in black and the total population for each model is shown in grey.
-We find that each model qualitatively exhibits similar characteristics and that the only change is in the yield of resolved DWDs for each type based on the strength of the confusion foreground.}
+    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for 
+each DWD type where the top row shows the population from model F50 and 
+the bottom row shows the population from model FZ for the fiducial 
+variation. In each panel, the LISA sensitivity curve, including the 
+confusion foreground for each model, is shown in black and the total 
+population for each model is shown in grey. We find that each model 
+qualitatively exhibits similar characteristics and that the only change is 
+in the yield of resolved DWDs for each type based on the strength of the 
+confusion foreground.}
     \label{fig:LISA_SNR}
@@
 
-Figure \ref{fig:lisa_nums} shows the number of DWDs orbiting with frequencies $f_{\rm{GW}} > 0.1\,\rm{mHz}$ against metallicity for each DWD type \textbf{and parameter variation}.
-The solid lines show DWDs from model FZ, and the dashed lines show DWDs from model F50.
-The He + CO, CO + CO, and ONe + X populations each have strong peaks in the number of DWDs near solar metallicity at which the majority of star formation in galaxy {\bf{m12i}} occurs.
-The largest contribution to the population comes from metallicities above $\sim$ 0.01Z$_\odot$.
-\textbf{Any} discrepancy between the two binary fraction models is also the most significant above this threshold.
-When creating our DWD populations the DWD formation efficiency, number of \textbf{m12i} star particles, and \textbf{the metallicity-dependent} binary fraction \textbf{and ZAMS orbital period distribution} all compete.
-The amount of stars formed in \textbf{m12i} at higher metallicity values overwhelms the drop in DWD formation efficiency by multiple orders of magnitude, so this effect dominates when determining the number of stars initially sampled in the population for $f_{\rm{b}}$.
-
-There are two peaks in the distribution of He + He DWDs \textbf{which are most prominent in the fiducial and $\alpha25$ variations, and not as obvious for $\alpha5$ or $q3$.
-The prominent first peak in fiducial and $\alpha25$} occurs because near $Z\simeq 0.1Z_\odot$, the DWD formation efficiency transitions from near constant values to a sharp decrease (see Figure \ref{fig:form_eff}).
-However, for a drop in the formation efficiency by a factor of of $\sim$ six, the amount of star formation in galaxy \textbf{m12i} increases by more than an order of magnitude for supersolar metallicities.
-Above $Z=Z_\odot$ this overcompensates for the efficiency drop, producing the second peak.
-\textbf{For $\alpha5$ and $q3$, the lack of dramatic orbital shrinking -- from the increased CE efficiency in the former and increased propensity for stable mass transfer in the latter -- allow for less failed DWDs due to stellar mergers.
-This leads to less dramatic drops in formation efficiency across metallicity which thus suppresses the formation of two peaks in the number of LISA-band systems.}
-
-\textbf{The $\alpha5$ and $q3$ variations produce a higher number of F50 systems than FZ when summed over all DWD types.
-This is due to the log-uniform P$_{\rm{orb}}$ distribution of model F50 having more of the shortest-period binaries than the tails of the log-normal distribution of FZ; a discrepancy which becomes more significant with increasing metallicity as the FZ distribution moves from a peak of log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 3-4$ to log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 4-6$.
-This tail is less likely to survive to the LISA band at present for the fiducial and $\alpha25$ variations due to the increased propensity for mergers of DWD progenitors.
-This effect produces an equal number of systems between FZ and F50 for the fiducial and $\alpha25$ variations.
-Although the close binary fraction leads to a greater number of low-metallicity systems, this is compensated for by the FIRE star particle metallicity distribution as well as the tendency for the shortest-period DWD progenitors in model F50 to merge, essentially washing out all differences between the populations.}
+Figure \ref{fig:lisa_nums} shows the number of DWDs orbiting with 
+frequencies $f_{\rm{GW}} > 0.1\,\rm{mHz}$ against metallicity for each DWD 
+type and parameter variation. The solid lines show DWDs from model FZ, and 
+the dashed lines show DWDs from model F50. The He + CO, CO + CO, and ONe + 
+X populations each have strong peaks in the number of DWDs near solar 
+metallicity at which the majority of star formation in galaxy {\bf{m12i}} 
+occurs. The largest contribution to the population comes from 
+metallicities above $\sim 0.01\,Z_\odot$. Any discrepancy between the two 
+binary fraction models is also the most significant above this threshold. 
+When creating our DWD populations the DWD formation efficiency, number of 
+\textbf{m12i} star particles, and the metallicity-dependent binary 
+fraction and ZAMS orbital period distribution all compete. The amount of 
+stars formed in \textbf{m12i} at higher metallicity values overwhelms the 
+drop in DWD formation efficiency by multiple orders of magnitude, so this 
+effect dominates when determining the number of stars initially sampled in 
+the population for $f_{\rm{b}}$.
+
+There are two peaks in the distribution of He + He DWDs which are most 
+prominent in the fiducial and $\alpha25$ variations, and not as obvious 
+for $\alpha5$ or $q3$. The prominent first peak in fiducial and $\alpha25$ 
+occurs because near $Z\simeq 0.1\,Z_\odot$, the DWD formation efficiency 
+transitions from near constant values to a sharp decrease (see Figure 
+\ref{fig:form_eff}). However, for a drop in the formation efficiency by a 
+factor of of $\sim$ six, the amount of star formation in galaxy 
+\textbf{m12i} increases by more than an order of magnitude for supersolar 
+metallicities. Above $Z=Z_\odot$ this overcompensates for the efficiency 
+drop, producing the second peak. For $\alpha5$ and $q3$, the lack of 
+dramatic orbital shrinking -- from the increased CE efficiency in the 
+former and increased propensity for stable mass transfer in the latter -- 
+allow for less failed DWDs due to stellar mergers. This leads to less 
+dramatic drops in formation efficiency across metallicity which thus 
+suppresses the formation of two peaks in the number of LISA-band systems.
+
+The $\alpha5$ and $q3$ variations produce a higher number of F50 systems 
+than FZ when summed over all DWD types. This is due to the log-uniform 
+P$_{\rm{orb}}$ distribution of model F50 having more of the 
+shortest-period binaries than the tails of the log-normal distribution of 
+FZ; a discrepancy which becomes more significant with increasing 
+metallicity as the FZ distribution moves from a peak of 
+log$_{10}$($P_{\rm{orb}}\rm{/day})\simeq 3-4$ to 
+log$_{10}$($P_{\rm{orb}}\rm{/day})\simeq 4-6$. This tail is less likely to 
+survive to the LISA band at present for the fiducial and $\alpha25$ 
+variations due to the increased propensity for mergers of DWD progenitors. 
+This effect produces an equal number of systems between FZ and F50 for the 
+fiducial and $\alpha25$ variations. Although the close binary fraction 
+leads to a greater number of low-metallicity systems, this is compensated 
+for by the FIRE star particle metallicity distribution as well as the 
+tendency for the shortest-period DWD progenitors in model F50 to merge, 
+essentially washing out all differences between the populations.
 
 \begin{figure*}
+
 \includegraphics[width=\textwidth]{figures/Mc_vs_dist_fiducial.pdf}
-    \caption{The chirp mass vs distance for each DWD type is shown \textbf{for our fiducial parameter variation}.
-Only systems with observable evolution in their GW frequency, i.e those which are chirping, and with SNR $>7$, are shown, since these are systems for which distance can be separated from chirp mass within their strain amplitude.
-Each panel shows one DWD type, summed over all metallicities.
-Model FZ is indicated with solid light blue contours, and model F50 is indicated with dark blue dashed contours respectively.
-Contours are shown at the $5^{\rm{th}}$, 25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$, and 95$^{\rm{th}}$ percentiles.
-Despite intrinsic changes to population properties induced by a metallicity-dependent binary fraction, and a reduction in the height of the DWD Galactic foreground the distributions are very similar.}
+    \caption{The chirp mass vs distance for each DWD type is shown for our 
+fiducial parameter variation. Only systems with observable evolution in 
+their GW frequency, i.e those which are chirping, and with SNR $>7$, are 
+shown, since these are systems for which distance can be separated from 
+chirp mass within their strain amplitude. Each panel shows one DWD type, 
+summed over all metallicities. Model FZ is indicated with solid light blue 
+contours, and model F50 is indicated with dark blue dashed contours 
+respectively. Contours are shown at the $5^{\rm{th}}$, 25$^{\rm{th}}$, 
+50$^{\rm{th}}$, 75$^{\rm{th}}$, and 95$^{\rm{th}}$ percentiles. Despite 
+intrinsic changes to population properties induced by a 
+metallicity-dependent binary fraction, and a reduction in the height of 
+the DWD Galactic foreground the distributions are very similar.}
     \label{fig:Mc_vs_dist}
@@
 
-\textbf{A change in the} number of DWDs in model FZ relative to model F50 is also apparent in the GW PSD LISA will observe.
-We show the GW PSD of each model, as well as the confusion forground estimate, in Figure~\ref{fig:PSD}.
-\textbf{We downsample the PSD frequencies by a factor of 10 for plotting purposes.} While model F50 (dark blue) and model FZ (light blue) produce several thousand large spikes in the PSD across LISA's frequency band, the overall foreground height, including the confusion, is larger for model F50 \textbf{for parameter variations $\alpha5$ and $q3$}.
-This is a direct consequence of the overall reduction in the size of the close DWD population in model FZ.
-\textbf{The foreground height remains unchanged for the fiducial and $\alpha25$ variations when comparing models FZ and F50}.
-
-Similar to previous studies, we find that LISA will be able to resolve several thousand DWDs.
-Figure \ref{fig:LISA_SNR} shows the amplitude spectral density vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the top and bottom rows show results for models FZ and F50 respectively for the fiducial parameter variation.
-For comparison, we also show the LISA sensitivity curve, including the
-modeled confusion foreground from each population in black, and the the entire population for each model in grey.
-\textbf{Plots for our three parameter variations can be found in Appendix \ref{appendix:ASD_vars}.} Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models.
-The populations containing at least one He WD occupy the lower-ASD, higher-GW frequency region of parameter space compared to the total population, with CO + He DWDs having larger ASDs than the He + He DWD population.
-Conversely, DWD types without a He WD component tend to occupy the higher-ASD, lower-GW frequency region of parameter space.
-This difference is largely due to the formation scenario of DWDs containing a He WD, which form from the ejection of a common envelope created by the He WD progenitor.
-These lower mass progenitors overflow their Roche lobes at closer separations relative to the higher mass progenitors (e.g.
-Figure~\ref{fig:CEsep}) and thus also produce closer DWDs.
-While the distance to any one DWD strongly influences its ASD, DWD populations without a He WD component have, on average, higher ASDs due to their more massive WD components.
-
-We note that the height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 2 for model FZ relative to model F50 \textbf{for variations $\alpha5$ and $q3$}, the number of resolved sources is not reduced to an equal degree.
-\textbf{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.
-For the fiducial and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ are reduced by 4.5\% and increased by 3\% respectively.
-However, for $\alpha5$ the number of resolvable DWDs is reduced by only 26\%, and the number of resolvable DWDs $q3$ remains almost \emph{unchanged}, with a 1\% reduction even though the overall LISA population of both variations is halved.
-A large portion of the maintenance of the number of DWDs in parameter variation $q3$ is contributed to by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).}
-
-The distance and chirp mass of DWDs which exhibit observable orbital evolution due to the emission of GWs during the LISA mission can be measured.
-This is because the chirp mass -- distance degeneracy in the observed strain can be broken with the observed GW frequency evolution, or chirp.
-Assuming a chirp resolution of $1/T_{\rm{obs}}^2 \sim 8\times10^{-9}\,\rm{Hz}^2$, we select the DWDs whose chirp masses and distances can be measured.
-Figure \ref{fig:Mc_vs_dist} shows the chirp mass vs the luminosity distance for each DWD type in this selected population \textbf{for the fiducial variation.
-The same figure for our other three parameter variations is shown in Appendix \ref{appendix:Mc_dist_vars}}.
-The contours show the $5^{\rm{th}}$, $25^{\rm{th}}$, $50^{\rm{th}}$, $75^{\rm{th}}$, and $95^{\rm{th}}$ percentiles for models FZ (light blue) and F50 (dark blue, dashed).
-Despite the reduction in the height of the confusion foreground when considering model FZ relative to F50, we find that LISA is unable to differentiate between the chirp mass -- distance distributions of the two models.
-
-\section{\textbf{Galactic DWD Confusion Foreground Discussion}}
+A change in the number of DWDs in model FZ relative to model F50 is also 
+apparent in the GW PSD LISA will observe. We show the GW PSD of each 
+model, as well as the confusion forground estimate, in 
+Figure~\ref{fig:PSD}. We downsample the PSD frequencies by a factor of 10 
+for plotting purposes. While model F50 (dark blue) and model FZ (light 
+blue) produce several thousand large spikes in the PSD across LISA's 
+frequency band, the overall foreground height, including the confusion, is 
+larger for model F50 for parameter variations $\alpha5$ and $q3$. This is 
+a direct consequence of the overall reduction in the size of the close DWD 
+population in model FZ. The foreground height remains unchanged for the 
+fiducial and $\alpha25$ variations when comparing models FZ and F50.
+
+Similar to previous studies, we find that LISA will be able to resolve 
+several thousand DWDs. Figure \ref{fig:LISA_SNR} shows the amplitude 
+spectral density vs GW frequency of the resolved systems with SNR $> 7$ 
+for each DWD type, where the top and bottom rows show results for models 
+FZ and F50 respectively for the fiducial parameter variation. For 
+comparison, we also show the LISA sensitivity curve, including the 
+modeled confusion foreground from each population in black, and the the 
+entire population for each model in grey. Plots for our three parameter 
+variations can be found in Appendix \ref{appendix:ASD_vars}. Apart from 
+each DWD type having a different abundance of resolved systems, the 
+population-wide characteristics remain unchanged between the two binary 
+fraction models. The populations containing at least one He WD occupy the 
+lower-ASD, higher-GW frequency region of parameter space compared to the 
+total population, with CO + He DWDs having larger ASDs than the He + He 
+DWD population. Conversely, DWD types without a He WD component tend to 
+occupy the higher-ASD, lower-GW frequency region of parameter space. This 
+difference is largely due to the formation scenario of DWDs containing a 
+He WD, which form from the ejection of a common envelope created by the He 
+WD progenitor. These lower mass progenitors overflow their Roche lobes at 
+closer separations relative to the higher mass progenitors (e.g. 
+Figure~\ref{fig:CEsep}) and thus also produce closer DWDs. While the 
+distance to any one DWD strongly influences its ASD, DWD populations 
+without a He WD component have, on average, higher ASDs due to their more 
+massive WD components.
+
+We note that the height of the confusion foreground and the number of DWDs 
+radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor 
+of 2 for model FZ relative to model F50 for variations $\alpha5$ and $q3$, 
+the number of resolved sources is not reduced to an equal degree. This is 
+because in the absence of less competing GW signals from DWDs in the LISA 
+frequency band, more DWDs can be individually resolved. For the fiducial 
+and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ 
+are reduced by 4.5\% and increased by 3\% respectively. However, for 
+$\alpha5$ the number of resolvable DWDs is reduced by only 26\%, and the 
+number of resolvable DWDs $q3$ remains almost \emph{unchanged}, with a 1\% 
+reduction even though the overall LISA population of both variations is 
+halved. A large portion of the maintenance of the number of DWDs in 
+parameter variation $q3$ is contributed to by He + He binaries with higher 
+GW frequencies and lower ASDs which can now survive CE interactions due to 
+an initial phase of mass transfer (see discussion of this formation 
+channel in Section \ref{sec:CEsep}).
+
+The distance and chirp mass of DWDs which exhibit observable orbital 
+evolution due to the emission of GWs during the LISA mission can be 
+measured. This is because the chirp mass -- distance degeneracy in the 
+observed strain can be broken with the observed GW frequency evolution, or 
+chirp. Assuming a chirp resolution of $1/T_{\rm{obs}}^2 \sim 
+8\times10^{-9}\,\rm{Hz}^2$, we select the DWDs whose chirp masses and 
+distances can be measured. Figure \ref{fig:Mc_vs_dist} shows the chirp 
+mass vs the luminosity distance for each DWD type in this selected 
+population for the fiducial variation. The same figure for our other three 
+parameter variations is shown in Appendix \ref{appendix:Mc_dist_vars}. The 
+contours show the $5^{\rm{th}}$, $25^{\rm{th}}$, $50^{\rm{th}}$, 
+$75^{\rm{th}}$, and $95^{\rm{th}}$ percentiles for models FZ (light blue) 
+and F50 (dark blue, dashed). Despite the reduction in the height of the 
+confusion foreground when considering model FZ relative to F50, we find 
+that LISA is unable to differentiate between the chirp mass -- distance 
+distributions of the two models.
+
+\section{Galactic DWD Confusion Foreground Discussion}
 \label{sec:model_compare}
@@
 	\includegraphics[width=0.45\textwidth]{figures/model_comp.pdf}
-    \caption{The top panel shows the Galactic DWD confusion fit vs GW frequency for different binary evolution \textbf{parameter variations} (colors) with model F50 shown in dashed lines and model FZ shown in solid lines.
-The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for model FZ to model F50 vs to number of DWDs orbiting in the LISA band for model F50 only.
-While both the height of the confusion foreground and number of LISA DWDs changes for each variation, the FZ models within each variation exhibit \textbf{either very little change or }a  near-constant reduction by a factor of two compared with the F50 models.}
+    \caption{The top panel shows the Galactic DWD confusion fit vs GW 
+frequency for different binary evolution parameter variations (colors) 
+with model F50 shown in dashed lines and model FZ shown in solid lines. 
+The bottom panel shows the ratio of the number of DWDs orbiting in the 
+LISA frequency band for model FZ to model F50 vs to number of DWDs 
+orbiting in the LISA band for model F50 only. While both the height of the 
+confusion foreground and number of LISA DWDs changes for each variation, 
+the FZ models within each variation exhibit either very little change or a  
+near-constant reduction by a factor of two compared with the F50 models.}
     \label{fig:model_comp}
@@
 
-In each parameter variation, changing the binary evolution assumptions dramatically changes the formation and evolution of the DWD populations.
-These changes lead to large shifts in the overall number of close DWDs in our synthetic present-day Milky-Way-like galaxies.
-We find that the total number of DWDs with $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$ increases for both variations $q3$ and $\alpha5$.
-This is because there are fewer stellar mergers which occur before the formation of a DWD, thus allowing more systems to evolve due to GW emission and orbit in the LISA frequency band at present.
-Conversely, for variation $\alpha25$, we find that the number of DWDs orbiting with frequencies in the LISA band is drastically reduced.
-This is because of the highly inefficient use of orbital energy to eject the common envelope, thus producing more stellar mergers, or closer binaries which are more prone to future mergers.
-
-Interestingly, when we compare the populations of each binary fraction model for our variations, we find that the number of close DWDs \textbf{remains approximately unchanged for our fiducial set of assumptions and $\alpha25$ variation, but is reduced by 50\% for variations $\alpha5$ and $q3$.} This is illustrated in Figure \ref{fig:model_comp}.
-The top panel shows the confusion foreground fits for each binary evolution variation (different colored lines) and for each binary fraction model where the solid lines show FZ models and dotted lines show F50 models.
-The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for the FZ models vs the F50 models for each variation.
-\textbf{The} number of DWDs in the LISA band spans over two orders of magnitude, \textbf{and} the ratio of FZ to F50, as well as the spectral shape of the confusion fit, \textbf{is either relatively unchanged or reduced by a factor of approximately two}.
-This suggests that assuming a metallicity-dependent binary fraction \textbf{may change} the size of the Galactic close DWD population by a factor of $\sim$two and the strength of the Galactic DWD GW foreground for LISA \textbf{depending on the chosen binary evolution model.}
+In each parameter variation, changing the binary evolution assumptions 
+dramatically changes the formation and evolution of the DWD populations. 
+These changes lead to large shifts in the overall number of close DWDs in 
+our synthetic present-day Milky-Way-like galaxies. We find that the total 
+number of DWDs with $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$ increases for both 
+variations $q3$ and $\alpha5$. This is because there are fewer stellar 
+mergers which occur before the formation of a DWD, thus allowing more 
+systems to evolve due to GW emission and orbit in the LISA frequency band 
+at present. Conversely, for variation $\alpha25$, we find that the number 
+of DWDs orbiting with frequencies in the LISA band is drastically reduced. 
+This is because of the highly inefficient use of orbital energy to eject 
+the common envelope, thus producing more stellar mergers, or closer 
+binaries which are more prone to future mergers.
+
+Interestingly, when we compare the populations of each binary fraction 
+model for our variations, we find that the number of close DWDs remains 
+approximately unchanged for our fiducial set of assumptions and $\alpha25$ 
+variation, but is reduced by 50\% for variations $\alpha5$ and $q3$. This 
+is illustrated in Figure \ref{fig:model_comp}. The top panel shows the 
+confusion foreground fits for each binary evolution variation (different 
+colored lines) and for each binary fraction model where the solid lines 
+show FZ models and dotted lines show F50 models. The bottom panel shows 
+the ratio of the number of DWDs orbiting in the LISA frequency band for 
+the FZ models vs the F50 models for each variation. The number of DWDs in 
+the LISA band spans over two orders of magnitude, and the ratio of FZ to 
+F50, as well as the spectral shape of the confusion fit, is either 
+relatively unchanged or reduced by a factor of approximately two. This 
+suggests that assuming a metallicity-dependent binary fraction may change 
+the size of the Galactic close DWD population by a factor of $\sim$ two 
+and the strength of the Galactic DWD GW foreground for LISA depending on 
+the chosen binary evolution model.
 
 \section{Conclusions}\label{sec:conclusions}
-In this study, we have investigated the effects of assuming a metallicity-dependent binary fraction on the formation and evolution of the Galactic population of DWDs with a special focus on the implications for LISA.
-Based on our synthetic Milky-Way-like galaxy catalogs of DWDs, we find that applying a metallicity-dependent binary fraction changes the formation efficiency and evolutionary history of DWD populations.
-However, when considering the close DWD populations observable by LISA, we find that the only distinguishing features between models which assume a metallicity-dependent binary fraction (model FZ) and models which assume a flat $50\%$ binary fraction (model F50) are the population sizes and the strength of the Galactic DWD GW foreground.
-Models which assume a metallicity-dependent binary fraction produce Galactic DWD populations that \textbf{were unchanged} relative to the standard model assumptions.
-\textbf{However, our results are highly dependent on the chosen binary evolution model.
-We extended our study to include three binary evolution \textbf{parameter variations} to investigate the sensitivity of the DWD population changes in assumptions for mass transfer stability and common envelope ejection efficiencies.
-While our binary evolution parameter variations change the size of the LISA-observable populations dramatically, the size of the close Galactic DWD population and the height of the confusion foreground for models which assume a metallicity-dependent binary fraction appears to either remain unchanged \emph{or} be reduced by 50\%.} This reduction extends to the height of the confusion foreground in the LISA data stream.
-\textbf{These two results highlight the interplay between the dominating factors which shape the LISA DWD population: the metallicity-dependent star formation history of the \textbf{m12i} galaxy, the metallicity-dependent close binary fraction which alters the ZAMS orbital period distribution, and the impact of binary evolution assumptions on DWD formation.
-This comparison emphasizes the sensitivity of the Galactic population of LISA-detectable DWDs to the intricacies of binary evolution.
-Binary evolution assumptions like CE efficiency are undergoing continuous study in current literature and an exact value has yet to be identified.
-By exploring a range of possibilities in this work, we capture the variation in predictions of the LISA DWD population that may be observed.}
-
-An important consequence of a lower Galactic DWD confusion foreground is that relative to the total DWD population, more DWDs can be individually resolved because of the reduction in competing GW signals.
-While the number of DWDs radiating GWs in the LISA frequency band is reduced by a factor of two for model FZ relative to model F50 \textbf{for variations $\alpha25$ and $q3$}, the number of resolved sources is less affected with a population-wide reduction of $26\%$ \textbf{for the former, and surprisingly only by 1\% for the latter}.
-These results are far-reaching since the strength of the Galactic DWD confusion foreground has direct consequences on the detectability of all other LISA sources with small SNRs.
-An increase in resolution capability from the reduced confusion foreground can be extended to other Galactic binaries that LISA will observe at these frequencies like those involving neutron stars and stellar-origin black holes, as well as other more exotic GW sources like merging supermassive black holes, extreme mass ratio inspirals, or cosmological GW backgrounds.
-Based on our results, we suggest that studies which employ fits to the confusion foreground based on population synthesis results consider reducing the strength of the Galactic foreground PSD by a factor of two \textbf{depending on the chosen binary evolution model}.
+In this study, we have investigated the effects of assuming a 
+metallicity-dependent binary fraction on the formation and evolution of 
+the Galactic population of DWDs with a special focus on the implications 
+for LISA. Based on our synthetic Milky-Way-like galaxy catalogs of DWDs, 
+we find that applying a metallicity-dependent binary fraction changes the 
+formation efficiency and evolutionary history of DWD populations. However, 
+when considering the close DWD populations observable by LISA, we find 
+that the only distinguishing features between models which assume a 
+metallicity-dependent binary fraction (model FZ) and models which assume a 
+flat $50\%$ binary fraction (model F50) are the population sizes and the 
+strength of the Galactic DWD GW foreground. Models which assume a 
+metallicity-dependent binary fraction produce Galactic DWD populations 
+that were unchanged relative to the standard model assumptions. However, 
+our results are highly dependent on the chosen binary evolution model. We 
+extended our study to include three binary evolution parameter variations 
+to investigate the sensitivity of the DWD population changes in 
+assumptions for mass transfer stability and common envelope ejection 
+efficiencies. While our binary evolution parameter variations change the 
+size of the LISA-observable populations dramatically, the size of the 
+close Galactic DWD population and the height of the confusion foreground 
+for models which assume a metallicity-dependent binary fraction appears to 
+either remain unchanged \emph{or} be reduced by 50\%. This reduction 
+extends to the height of the confusion foreground in the LISA data stream. 
+These two results highlight the interplay between the dominating factors 
+which shape the LISA DWD population: the metallicity-dependent star 
+formation history of the \textbf{m12i} galaxy, the metallicity-dependent 
+close binary fraction which alters the ZAMS orbital period distribution, 
+and the impact of binary evolution assumptions on DWD formation. This 
+comparison emphasizes the sensitivity of the Galactic population of 
+LISA-detectable DWDs to the intricacies of binary evolution. Binary 
+evolution assumptions like CE efficiency are undergoing continuous study 
+in current literature and an exact value has yet to be identified. By 
+exploring a range of possibilities in this work, we capture the variation 
+in predictions of the LISA DWD population that may be observed.
+
+An important consequence of a lower Galactic DWD confusion foreground is 
+that relative to the total DWD population, more DWDs can be individually 
+resolved because of the reduction in competing GW signals. While the 
+number of DWDs radiating GWs in the LISA frequency band is reduced by a 
+factor of two for model FZ relative to model F50 for variations $\alpha25$ 
+and $q3$, the number of resolved sources is less affected with a 
+population-wide reduction of $26\%$ for the former, and surprisingly only 
+by 1\% for the latter. These results are far-reaching since the strength 
+of the Galactic DWD confusion foreground has direct consequences on the 
+detectability of all other LISA sources with small SNRs. An increase in 
+resolution capability from the reduced confusion foreground can be 
+extended to other Galactic binaries that LISA will observe at these 
+frequencies like those involving neutron stars and stellar-origin black 
+holes, as well as other more exotic GW sources like merging supermassive 
+black holes, extreme mass ratio inspirals, or cosmological GW backgrounds. 
+Based on our results, we suggest that studies which employ fits to the 
+confusion foreground based on population synthesis results consider 
+reducing the strength of the Galactic foreground PSD by a factor of two 
+depending on the chosen binary evolution model.
 
 \begin{acknowledgments}
-The authors are grateful for helpful discussions with Carles Badenes, Christine Mazzola Daher, Kaitlin Kratter, and the Gravitational Waves and Astronomical Data groups at the CCA.
-The authors are also grateful to the referee for providing a thoughtful review which strengthened the presentation of the manuscript.
-S.T.\ was supported by an Undergraduate Student Research Award (USRA) at CITA from the Natural Sciences and Engineering Research Council of Canada (NSERC), Reference \# 498223.
-K.B.\ is grateful for support from the Jeffrey L.
-Bishop Fellowship.
-The Flatiron Institute is supported by the Simons Foundation.
+The authors are grateful for helpful discussions with Carles Badenes, 
+Christine Mazzola Daher, Kaitlin Kratter, and the Gravitational Waves and 
+Astronomical Data groups at the CCA. The authors are also grateful to the 
+referee for providing a thoughtful review which strengthened the 
+presentation of the manuscript. S.T.\ was supported by an Undergraduate 
+Student Research Award (USRA) at CITA from the Natural Sciences and 
+Engineering Research Council of Canada (NSERC), Reference \# 498223. K.B.\ 
+is grateful for support from the Jeffrey L. Bishop Fellowship. The 
+Flatiron Institute is supported by the Simons Foundation.
 \end{acknowledgments}
@@
 
-All data and software required to reproduce our results are available through GitHub and Zenodo which are accessible through the icon links associated with our abstract and each figure.
+All data and software required to reproduce our results are available 
+through GitHub and Zenodo which are accessible through the icon links 
+associated with our abstract and each figure.
 
@@
           \texttt{numpy}\ \citep{numpy}; 
-          \texttt{pandas}\ \citep{mckinney-proc-scipy-2010, reback2020pandas}; 
+          \texttt{pandas}\ \citep{mckinney-proc-scipy-2010, 
+reback2020pandas}; 
           \texttt{scipy}\ \citep{scipy}
@@
 \appendix
-\section{Amplitude Spectral Densities for Binary Evolution Parameter Variations}\label{appendix:ASD_vars}
-
-Figure \ref{fig:LISA_SNR_vars} shows the ASD vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the rows alternate between models F50 and FZ for the $\alpha25$, $\alpha5$, and $q3$ parameter variations.
-The LISA sensitivity curve is also shown in black, which includes the modeled confusion foreground from each population in black.
-The entire population is shown as grey scatter points.
-As discussed in Section \ref{sec:LISA_met}, apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models.
-
-The height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 2 for model FZ relative to model F50 for variations $\alpha5$ and $q3$, however the number of resolved sources is not reduced to an equal degree.
-The number of observable systems with SNR $>7$ increases by 3\% for $\alpha25$.
-For $\alpha5$ the number of resolvable DWDs is reduced by only 26\%, and the number of resolvable DWDs $q3$ only experiences a 1\% reduction even though the overall LISA population of both variations is halved.
-A large portion of the maintenance of the number of DWDs in parameter variation $q3$ is contributed to by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).
+\section{\textbf{Formation efficiency trends}}\label{appendix:form_eff}
+\textbf{As discussed in Section \ref{sec:formeff}, the formation 
+efficiency of DWDs exhibitis a metallicity dependence. This is both due to 
+the impact of metallicity on stellar evolution, and on the ZAMS orbital 
+period distribution of model F50 vs. FZ. Each DWD type and binary 
+evolution parameter variation exhibits unique trends in efficiency and in 
+their evolutionary channel. In the following subsections we go through 
+each DWD type in detail, first for our fiducial simulations and then for 
+our variations.}
+
+\subsection{Fiducial formation efficiency 
+trends}\label{subsec:formeff_fid}
+
+\subsubsection{\textbf{He + He}}\label{formeff_HeHe}
+For He + He DWDs, the sudden drop in formation efficiency near 
+$\log(Z/Z_{\odot})=-1.0$ \textbf{(see Figure \ref{fig:form_eff})} is 
+generally caused by the timescale for which the initially more massive 
+star in the DWD progenitor overflows it's Roche lobe. \textbf{As discussed 
+in Section \ref{sec:formeff}, at} lower metallicities, donors tend to fill 
+their Roche lobes while they are still on the MS and the mass transfer 
+remains stable and serves to widen the binary. At higher metallicities, 
+mass transfer is initiated when the donor has left the main sequence, and 
+the binary enters a common envelope evolution.
+
+The ZAMS orbital period leads to different specific \textbf{He + He} 
+evolutionary channels. For short-period systems with periods below 
+$10~\rm{days}$, CE leads to a stellar merger due to insufficient orbital 
+energy to eject the envelope. Stellar mergers continue to dominate the 
+evolutionary pathways of systems with intermediate orbital periods ($1 < 
+\log_{10}(P_{\rm{orb}}/\rm{day}) < 2.5$). However, an additional growing 
+number of merging systems arises with one WD component and one stellar 
+companion, and \textbf{surviving} systems which don't interact at all and 
+thus do not form a He + He DWD. The distinction between the various 
+scenarios in this intermediate orbital period range depends on the 
+combination of their ZAMS masses and orbital periods. Finally, at wider 
+initial periods $\log_{10}(\rm{P}) > 2.5$, the decrease in formation 
+efficiency is dominated by systems which never interact and thus do not 
+form a DWD before the present day.
+
+\subsubsection{\textbf{CO + He}}\label{formeff_COHe}
+\textbf{In general, a CO + He DWD fails to form because either a stellar 
+merger occurs before DWD formation, or a CO + CO or He + He DWD is formed 
+instead. We discuss the specifics of these effects for three ZAMS orbital 
+period regimes below. Model FZ yields higher formation efficiencies than 
+F50 because CO + He DWDs prefer to form from progenitor binaries with 
+orbital periods near $\log_{10}(P_{\rm{orb}}/~\rm{day})\sim2-4$, which is 
+where the orbital period distribution of FZ peaks.}
+
+For short-period CO + He DWD progenitor binaries with orbital periods 
+below $\sim30~\rm{days}$, the only channel for stellar mergers before DWD 
+formation is during a CE evolution. This channel is similar to the stellar 
+merger channel for He + He DWDs, but due to higher-mass progenitors the CE 
+evolution results in the binary component with a higher mass becoming a CO 
+WD. At higher metallicities, the CO WD merges with its companion. 
+\textbf{As discussed in Section \ref{sec:formeff}, h}igher-metallicity 
+progenitors have a larger fraction of their mass in the convective 
+envelope when compared to lower-metallicity stars of the same mass. Thus a 
+CE phase with a higher-metallicity progenitor requires more orbital energy 
+to eject the common envelope, causing a larger amount of orbital shrinking 
+which results in a merger later in its binary evolution.
+
+For CO + He DWD progenitor systems with intermediate orbital periods 
+($1.5\leq \log_{10}(P_{\rm{orb}}/\rm{day})< 2.5$) the mechanisms which 
+impact formation efficiency are complex. The dominant way CO + He DWDs 
+\textbf{fail to form} is stellar mergers that occur during the second CE 
+phase. \textbf{Low-metallicity systems survive this second CE phase 
+whereas high-metallicity systems do not.} \textbf{Similar to the 
+short-period systems, there is increased orbital shrinkage for 
+high-metallicity progenitor binaries due to the deeper convective envelope 
+of the CE evolution donor. This creates shorter post-CE orbital periods 
+which leads to mergers during the CE second phase.}
+
+If a lower-metallicity system forms a CO + He DWD and a higher-metallicity 
+system does not, this \textbf{could also be} because the initially more 
+massive binary component initiates a CE while on the giant branch instead 
+of the asymptotic giant branch. This leaves behind a He WD with a stellar 
+companion \textbf{instead of a CO + He}, which is the dominating scenario 
+that restricts formation efficiency. There are a few edge cases where 
+either a He + He DWD is formed instead, or a CO WD and a stellar companion 
+is formed and there has been very nearly but not quite enough time for a 
+CO + He DWD to form.
+
+Long-period binaries with $\log_{10}(P_{\rm{orb}}/\rm{day})>2.5$ also 
+display complex scenarios that hinder CO + He DWD formation. In near-equal 
+contributions, our \cosmic\ simulations produce either stellar mergers or 
+stable non-DWD binaries at the end of the Hubble time. At these orbital 
+periods, stellar mergers always occur with a CE phase between a stellar 
+companion and a CO or He WD. \textbf{Again}, the mergers occur because of 
+increased CE donor envelope masses at higher metallicities. A subdominant 
+channel of stable He + He DWDs can also occur when a high-metallicity 
+primary overflows it's Roche lobe while still on the giant branch and thus 
+forms a He WD.
+
+\subsubsection{\textbf{CO + CO}}\label{formeff_COCO}
+The decrease in the CO + CO DWD formation efficiency with increasing 
+metallicity stems from different evolutionary channels which arise at the 
+ZAMS orbital period boundary of $\log_{10}(P_{\rm{orb}}/\rm{day})\simeq3$. 
+We find that for binaries with orbital periods below this boundary, the 
+most common way that CO + CO DWDs form at lower metallicities but not at 
+higher metallicities is through stellar mergers during a CE phase with a 
+donor that is still on the giant branch. For lower-metallicity binaries, 
+which evolve on faster timescales, the primaries enter CE evolution while 
+on the asymptotic giant branch instead and the binary is able to survive. 
+For binaries with orbital periods above the boundary, the vast majority of 
+systems with wide initial orbits end up as stable binaries. The 
+\textbf{wide} systems which don’t form a CO DWD at high metallicity do so 
+because one or both of the binary components initiate a CE phase while 
+still on the giant branch, thus producing a CO + He or He + He DWD.
+
+\subsubsection{\textbf{ONe + X}}\label{formeff_ONe}
+The strongest effect which hinders formations of higher-metallicity ONe + 
+X DWDs is the strength of metallicity-dependent stellar winds assumed in 
+our model \citep{Vink2001}. The strength of line-driven winds varies more 
+strongly for the more massive ($\geq5\,M_\odot$) progenitors of ONe WDs 
+relative to the other lower mass WD progenitors. At higher metallicities, 
+ONe WD progenitors can lose enough mass through winds such that they don't 
+ignite their CO cores and thus leave behind a CO WD. Conversely, the 
+lower-metallicity progenitors retain enough mass to cause carbon ignition 
+and leave behind an ONe WD.
+
+\subsection{Parameter variations formation efficiency 
+trends}\label{subsec:formeff_vars}
+
+\textbf{As discussed in Section \ref{sec:formeff},} our simulations with 
+binary evolution parameter variations \textbf{show competition between} 
+the physics of binary evolution with skews introduced by the 
+metallicity-dependent orbital period distribution and binary fraction. Two 
+important features of our FZ and F50 models drive the differences in 
+\textbf{formation efficiency for} our binary evolution parameter 
+variations. First, the log-normal metallicity-dependent ZAMS orbital 
+period distribution increasingly skews towards 
+\textbf{$P_{\rm{orb}}\lesssim 10^4$ days} for decreasing metallicity. 
+However, second, the log-uniform $P_{\rm{orb}}$ distribution of F50 
+produces a higher number of the shortest-period systems 
+(\textbf{$P_{\rm{orb}}\lesssim 100$ days}) than for FZ as the tail of the 
+FZ distribution falls \textbf{below F50 in this regime.} \textbf{Because 
+there are more ZAMS binaries with $P_{\rm{orb}} \lesssim 10^4$ days in 
+F50, as the population evolves there are more likely to be binary 
+interactions in the population for F50 than FZ. This leads to more mergers 
+in $\alpha25$ occurring for F50 before formation of the DWD, and thus a 
+lower $\alpha25$ formation efficiency overall for F50 in contrast to FZ. 
+Below we summarize how the formation efficiency of each DWD type is 
+impacted by the parameter variations. Across all DWD types, we find that 
+there are more mergers for variation $\alpha25$ compared with the fiducial 
+variation, and fewer for $\alpha5$, due to the CE efficiency's impact on 
+CE phase orbital energy requirements. We also find fewer mergers for $q3$, 
+because of the ability for binaries to maintain stable mass transfer, thus 
+increasing their chance of survival.}
+
+\subsubsection{\textbf{Parameter variations: He + 
+He}}\label{formeff_HeHe_vars}
+For binary systems leading to He + He DWDs, \textbf{as stated above} there 
+are many more mergers for $\alpha25$ than for the fiducial variation. The 
+lower CE efficiency leads to more DWD progenitor mergers from a failed CE 
+ejection, or the CE shrinking the orbit such that it then merges on the 
+second CE phase. \textbf{As discussed above, there are also more close 
+binaries in the orbital period distribution of F50 than FZ, creating a 
+higher propensity for binary interactions and thus mergers for 
+$\alpha25$.} This is illustrated in the $\alpha25$ He + He plot of Figure 
+\ref{fig:form_eff}. Similar to the fiducial parameter variation, a binary 
+that becomes a He + He DWD at lower metallicities would merge before 
+becoming one at higher metallicities because of the longer evolution 
+timescales. These later interactions lead to closer post-CE separations 
+and thus more mergers. The dip at [Fe/H] $\simeq -1.5$ \textbf{(see Figure 
+\ref{fig:form_eff})} stems from mergers before the DWD forms, again 
+similar to the fiducial parameter variation. The peak that occurs in 
+$\alpha25$ at $\sim 10\%\,Z_\odot$ arises from binaries evolving faster, 
+and thus interacting earlier, as metallicity increases. This means that 
+equivalent binaries that would have merged or formed a CO + He DWD instead 
+at lower metallicities now survive to produce a He + He DWD. At higher 
+metallicities, there are also a higher proportion of wide ZAMS binaries, 
+which evolve off the Main Sequence too slowly to form a He + He DWD, 
+\textbf{adding to} the efficiency drop.
+
+For $\alpha5$, there are significantly fewer DWD progenitor mergers since 
+binaries are more likely to survive a CE phase due to the higher CE 
+ejection efficiency. Systems that would merge for $\alpha25$ instead 
+survive, shrinking to short orbits through CE interactions to reside in 
+the LISA band at present. The number of DWDs then makes up a higher 
+fraction of the total simulated binary population, thus we find in general 
+higher formation efficiencies than for the fiducial parameter variation 
+which sets $\alpha=1$. This effect is even more pronounced in comparison 
+with the $\alpha25$ variation which sets $\alpha=0.25$.
+
+Beyond the effects described above, the efficiency drop across metallicity 
+is similar to the fiducial parameter variation in that it depends on the 
+metallicity-dependent ZAMS orbital period distribution emphasizing 
+short-period systems at low metallicities, and on the change of formation 
+channel for different period ranges across metallicity. We find the 
+variation $q3$ yields the highest formation efficiency. Only the 
+shortest-period binaries do not form a DWD\textbf{, which are lost} 
+through mergers at higher metallicities. At low metallicities, even 
+binaries with ZAMS orbital periods $P_{\rm{orb}}\lesssim 100$ days form He 
++ He DWDs, with binaries in model FZ reaching ZAMS orbital periods less 
+than a day in length. This leads to a higher formation efficiency from F50 
+over FZ for parameter variation $q3$ because of the higher number of 
+shortest-period ZAMS binaries in the log-uniform distribution of F50.
+
+\subsubsection{\textbf{Parameter variations: CO + 
+He}}\label{formeff_COHe_vars}
+For CO + He binaries, there are again many more mergers for parameter 
+variation $\alpha25$ relative to the fiducial case. This is the dominant 
+\textbf{reason} that progenitors do not evolve to produce DWDs at higher 
+metallicities. At low metallicities, a number of progenitor binaries form 
+CO + CO DWDs instead of He + CO DWDs. This is especially the case near 
+$\log_{10}(Z/Z_\odot)\sim -2$, where RLO occurs late enough in a binary's 
+evolution that mass transfer remains stable and CO + CO's are formed 
+rather than CO + He, hence producing a dip in the formation efficiency 
+\textbf{(see Figure \ref{fig:form_eff})}.
+
+Because parameter variation $\alpha5$ \textbf{yields fewer} mergers, the 
+formation efficiency is mostly governed by the metallicity-dependent ZAMS 
+orbital period distribution. At higher metallicities, the majority of 
+cases in model FZ where progenitors do not produce a CO + He DWD are from 
+progenitor mergers, or from He + He DWDs forming instead of CO + He DWDs. 
+At higher metallicities, the ZAMS orbital period distribution of FZ also 
+drops below that of F50 and extends out to orbital periods beyond what 
+would form a CO + He. This causes the formation efficiencies for FZ and 
+F50 to cross at log$_{10}(Z/Z_\odot)\sim-0.5$. This is also apparent for 
+the $q3$ variation, and to a lesser extent in the fiducial case. In $q3$, 
+for any given orbital period we find that lower-mass DWDs originate from 
+lower metallicities, thus leading to an approximately constant formation 
+efficiency.
+
+\subsubsection{\textbf{Parameter variations: CO + 
+CO}}\label{formeff_CO_vars}
+For CO + CO, across all variations, very close ZAMS binaries 
+($P_{\rm{orb}}\sim\mathcal{O}(100$ days)) at high metallicities form a CO 
++ He or He + He DWD instead of a CO + CO because the binary interacts 
+before core Helium burning of one or both components. There are again many 
+more mergers in $\alpha25$, and fewer mergers for $\alpha5$. Due to the 
+high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods 
+survive to become CO + CO DWDs rather than merging or becoming CO + He or 
+He + He DWDs. There are fewer mergers overall for $q3$ than all the 
+$\alpha$ variations because the first RLO occurrence leads to stable mass 
+transfer from the primary to the secondary rather than multiple CE phases. 
+For both the $\alpha5$ and $q3$ variations, the majority of CO + CO DWDs 
+originate in wide enough orbits that they do not interact before DWD 
+formation. This leads to an approximately constant formation efficiency 
+across metallicity in both cases.
+
+\subsubsection{\textbf{Parameter variations: ONe + 
+X}}\label{formeff_ONe_vars}
+For model FZ, the ONe + X formation efficiencies follow similar trends 
+aross each parameter variation. Their formation scenarios are similar to 
+those described \textbf{in Section \ref{sec:formeff}} for ONe + X DWDs in 
+the fiducial binary evolution parameter set. The main difference between 
+each parameter variation is only in the number of sources produced since 
+the number of stellar mergers that occur before DWD formation increases 
+with decreasing common envelope efficiency. In model F50, the formation 
+efficiency is decreased significantly for parameter variation $\alpha25$ 
+because the log-uniform orbital period distribution produces many ZAMS 
+binaries with very short orbital periods which lead to stellar mergers 
+during the CE phases.
+
+\section{Amplitude Spectral Densities for Binary Evolution Parameter 
+Variations}\label{appendix:ASD_vars}
+
+Figure \ref{fig:LISA_SNR_vars} shows the ASD vs GW frequency of the 
+resolved systems with SNR $> 7$ for each DWD type, where the rows 
+alternate between models F50 and FZ for the $\alpha25$, $\alpha5$, and 
+$q3$ parameter variations. The LISA sensitivity curve is also shown in 
+black, which includes the modeled confusion foreground \textbf{(see 
+Section \ref{sec:LISA_met} for details on fitting the foreground) for the 
+given variation}. The entire population is shown as grey scatter points. 
+As discussed in Section \ref{sec:LISA_met}, apart from each DWD type 
+having a different abundance of resolved systems, the population-wide 
+characteristics remain unchanged between the two binary fraction models.
+
+The height of the confusion foreground and the number of DWDs radiating 
+GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 
+\textbf{two} for model FZ relative to model F50 for variations $\alpha5$ 
+and $q3$, however the number of resolved\textbf{, i.e. observable,} 
+sources is not reduced to an equal degree. The number of observable 
+systems with SNR $>7$ increases by 3\% for $\alpha25$\textbf{, mimicking 
+the LISA-band population remaining relatively unchanged}. \textbf{However, 
+}the number of \textbf{observable} DWDs is reduced by only 26\% for 
+$\alpha5$, and \textbf{by only 1\% for $q3$}, even though the overall LISA 
+population of both variations is halved. \textbf{Maintaining} the number 
+of DWDs in parameter variation $q3$ is contributed to \textbf{largely} by 
+He + He binaries with higher GW frequencies and lower ASDs which can now 
+survive CE interactions due to an initial phase of mass transfer (see 
+discussion of this formation channel in Section \ref{sec:CEsep}).
 
@@
     \centering
+
 \includegraphics[width=0.8\textwidth]{figures/LISA_SNR_alpha25.pdf}
@@
 	\includegraphics[width=0.8\textwidth]{figures/LISA_SNR_q3.pdf}
-    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for each DWD type and parameter variation.
-The rows alternate between model F50 and from model FZ.
-In each panel, the LISA sensitivity curve, including the confusion foreground for each model, is shown in black and the total population for each model is shown in grey.
-Again, we find that each model qualitatively exhibits similar characteristics and that the only change is in the yield of resolved DWDs for each type based on the strength of the confusion foreground.}
+    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for 
+each DWD type and parameter variation. The rows alternate between model 
+F50 and from model FZ. In each panel, the LISA sensitivity curve, 
+including the confusion foreground for each model, is shown in black and 
+the total population for each model is shown in grey. Again, we find that 
+each model qualitatively exhibits similar characteristics and that the 
+only change is in the yield of resolved DWDs for each type based on the 
+strength of the confusion foreground.}
     \label{fig:LISA_SNR_vars}
@@
 
-\section{Chirp Mass -- Distance Distributions for Binary Evolution Parameter Variations}\label{appendix:Mc_dist_vars}
-
-Figure~\ref{fig:Mc_vs_dist_vars} shows the chirp mass vs distance distribution for the $\alpha25$, $\alpha5$, and $q3$ parameter variations.
-For $\alpha25$ we plot scatter plots for He + He and ONe + X due to low statistics since there are too few binaries in this selected population to produce reliable kernel density estimates.
-The only population with a significant change between each variation is for ONe + X DWDs where $\alpha5$.
-Here, we see a skew to lower masses because a higher fraction of the binaries are ONe + He for FZ than F50 -- a Helium companion makes up 10\% of this selected population for F50 compared with 44\% for FZ.
-This leads to lower average chirp masses for the ONe + X distribution.
-Furthermore, $\sim8$\% of the F50 measurable systems are ONe + ONe binaries, versus 0\% for FZ.
-Because ONe WDs have larger masses, this also creates the high-mass concentration we see in the F50 contours.
+\section{Chirp Mass -- Distance Distributions for Binary Evolution 
+Parameter Variations}\label{appendix:Mc_dist_vars}
+
+Figure~\ref{fig:Mc_vs_dist_vars} shows the chirp mass vs distance 
+distribution for the $\alpha25$, $\alpha5$, and $q3$ parameter variations. 
+For $\alpha25$ we plot scatter plots for He + He and ONe + X due to low 
+statistics; there are too few binaries in this selected population to 
+produce reliable kernel density estimates. The only population with a 
+significant change between \textbf{binary fraction models} is for ONe + X 
+DWDs\textbf{, variation} $\alpha5$. Here, we find a skew to lower 
+\textbf{chirp} masses because a higher fraction of the binaries are ONe + 
+He for FZ \textbf{compared to} F50: a Helium companion makes up 44\% of 
+this selected population for FZ, compared with 10\% for F50. This leads to 
+lower average chirp masses for the ONe + X distribution. Furthermore, 
+$\sim8$\% of the F50 measurable systems are ONe + ONe binaries, versus 0\% 
+for FZ. Because ONe WDs have larger masses, this also creates the 
+high-mass concentration we \textbf{find} in the F50 contours.
 \begin{figure*}[h]
     \centering
+
 \includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_alpha25.pdf}
+
 \includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_alpha5.pdf}
 	\includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_q3.pdf}
-    \caption{Chirp mass -- distance distributions for our other three binary evolution parameter variations.
-We plot the $\alpha25$ populations of He + He and ONe + X DWDs as scatter points since there are too few binaries to produce meaningful density distributions.
-Again, we have plotted each DWD type's population that exhibit observable GW frequency evolution and have SNR$>7$.
-Contours show the 5$^{\rm{th}}$, 25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$ and 95$^{\rm{th}}$ percentiles.
-Most populations remain unchanged between binary fraction models except for ONe + X DWDs in $\alpha5$, due to the number of He vs.
-CO vs.
-ONe companions between each model.}
+    \caption{Chirp mass -- distance distributions for our other three 
+binary evolution parameter variations. We plot the $\alpha25$ populations 
+of He + He and ONe + X DWDs as scatter points since there are too few 
+binaries to produce meaningful density distributions. Again, we have 
+plotted each DWD type's population that exhibit observable GW frequency 
+evolution and have $\rm{SNR}>7$. Contours show the 5$^{\rm{th}}$, 
+25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$ and 95$^{\rm{th}}$ 
+percentiles. Most populations remain unchanged between binary fraction 
+models except for ONe + X DWDs in $\alpha5$, due to the number of He vs. 
+CO vs. ONe companions between each model.}
     \label{fig:Mc_vs_dist_vars}

### 2022-10-03 src/tex/ms.tex
text edits

@@
 evolutionary channels. For short-period systems with periods below 
-$10~\rm{days}$, CE leads to a stellar merger due to insufficient orbital 
-energy to eject the envelope. Stellar mergers continue to dominate the 
-evolutionary pathways of systems with intermediate orbital periods ($1 < 
-\log_{10}(P_{\rm{orb}}/\rm{day}) < 2.5$). However, an additional growing 
-number of merging systems arises with one WD component and one stellar 
-companion, and \textbf{surviving} systems which don't interact at all and 
-thus do not form a He + He DWD. The distinction between the various 
-scenarios in this intermediate orbital period range depends on the 
-combination of their ZAMS masses and orbital periods. Finally, at wider 
-initial periods $\log_{10}(\rm{P}) > 2.5$, the decrease in formation 
-efficiency is dominated by systems which never interact and thus do not 
-form a DWD before the present day.
+$10~\rm{days}$, \textbf{a CE phase} leads to a stellar merger due to 
+insufficient orbital energy to eject the envelope. Stellar mergers 
+continue to dominate the evolutionary pathways of systems with 
+intermediate orbital periods ($1 < \log_{10}(P_{\rm{orb}}/\rm{day}) < 
+2.5$). However, an additional growing number of merging systems arises 
+with one WD component and one stellar companion, and \textbf{surviving} 
+systems which don't interact at all and thus do not form a He + He DWD. 
+The distinction between the various scenarios in this intermediate orbital 
+period range depends on the combination of their ZAMS masses and orbital 
+periods. Finally, at wider initial periods $\log_{10}(\rm{P}) > 2.5$, the 
+decrease in formation efficiency is dominated by systems which never 
+interact and thus do not form a DWD before the present day.
 
@@
 survive to become CO + CO DWDs rather than merging or becoming CO + He or 
-He + He DWDs. There are fewer mergers overall for $q3$ than all the 
-$\alpha$ variations because the first RLO occurrence leads to stable mass 
-transfer from the primary to the secondary rather than multiple CE phases. 
-For both the $\alpha5$ and $q3$ variations, the majority of CO + CO DWDs 
-originate in wide enough orbits that they do not interact before DWD 
-formation. This leads to an approximately constant formation efficiency 
-across metallicity in both cases.
+He + He DWDs. There are \textbf{fewer} mergers overall for $q3$ than all 
+the $\alpha$ variations because the first RLO occurrence leads to stable 
+mass transfer from the primary to the secondary rather than multiple CE 
+phases. For both the $\alpha5$ and $q3$ variations, the majority of CO + 
+CO DWDs originate in wide enough orbits that they do not interact before 
+DWD formation. This leads to an approximately constant formation 
+efficiency across metallicity in both cases.
 

### 2022-10-31 src/tex/ms.tex
Update ms.tex

@@
 
-\shorttitle{Applying a metallicity-dependent binary fraction to DWD 
-formation}
+\shorttitle{Applying a metallicity-dependent binary fraction to DWD formation}
 \shortauthors{Thiele et al.}
@@
 % Title
-\title{Applying the metallicity-dependent binary fraction to double white 
-dwarf formation: \\ Implications for LISA}
+\title{Applying the metallicity-dependent binary fraction to double white dwarf formation: \\ Implications for LISA}
 
@@
 \author[0000-0001-7442-6926]{Sarah Thiele}
-\affiliation{Department of Physics and Astronomy, University of British 
-Columbia, 6224 Agricultural Road, Vancouver, BC, V6T 1Z1, Canada}
+\affiliation{Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC, V6T 1Z1, Canada}
 \affiliation{Canadian Institute for Theoretical Astrophysics, University
@@
 \author[0000-0001-5228-6598]{Katelyn Breivik}
-\affiliation{Center for Computational Astrophysics, Flatiron Institute, 
-162 Fifth Ave, New York, NY, 10010, USA}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
 \affiliation{Canadian Institute for Theoretical Astrophysics, University
@@
 \author[0000-0003-3939-3297]{Robyn E. Sanderson}
-\affiliation{Department of Physics and Astronomy, University of 
-Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA}
-\affiliation{Center for Computational Astrophysics, Flatiron Institute, 
-162 Fifth Ave, New York, NY, 10010, USA}
+\affiliation{Department of Physics and Astronomy, University of Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
 \author[0000-0002-0296-3826]{Rodrigo Luger}
-\affiliation{Center for Computational Astrophysics, Flatiron Institute, 
-162 Fifth Ave, New York, NY, 10010, USA}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
 
@@
 \begin{abstract}
-Short-period double white dwarf (DWD) binaries will be the most prolific 
-source of gravitational waves (GWs) for the Laser Interferometer Space 
-Antenna (LISA). DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be 
-the dominant contributor to a stochastic foreground caused by overlapping 
-GW signals. Population modeling of Galactic DWDs typically assumes a 
-binary fraction of $50\%$ and a log-uniform Zero Age Main Sequence (ZAMS) 
-orbital period distribution. However, recent observations have shown that 
-the binary fraction of close, solar-type stars exhibits a strong 
-anti-correlation with metallicity which modulates the ZAMS orbital period 
-distribution below $10^4$ days. In this study we perform the first 
-simulation of the Galactic DWD population observable by LISA which 
-incorporates an empirically-derived metallicity-dependent binary fraction, 
-using the binary population synthesis suite \cosmic\ and a 
-metallicity-dependent star formation history. We compare two models: one 
-which assumes a metallicity-dependent binary fraction, and one with a 
-binary fraction of 50\%. We repeat our analysis for three different 
-assumptions for Roche-lobe overflow interactions. We find that while 
-metallicity impacts the evolution and intrinsic properties of our 
-simulated DWD progenitor binaries, the LISA-resolvable populations of the 
-two models remain roughly indistinguishable. However, the size of the 
-total Galactic DWD population orbiting in the LISA frequency band is 
-reduced by more than half when accounting for a metallicity-dependent 
-binary fraction for two of our four variations, which also lowers the 
-effective foreground. The LISA population remains unchanged in number for 
-two variations, highlighting the sensitivity of the population to binary 
-evolution prescriptions.
+Short-period double white dwarf (DWD) binaries will be the most prolific source of gravitational waves (GWs) for the Laser Interferometer Space Antenna (LISA).
+DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be the dominant contributor to a stochastic foreground caused by overlapping GW signals.
+Population modeling of Galactic DWDs typically assumes a binary fraction of $50\%$ and a log-uniform Zero Age Main Sequence (ZAMS) orbital period distribution.
+However, recent observations have shown that the binary fraction of close, solar-type stars exhibits a strong anti-correlation with metallicity which modulates the ZAMS orbital period distribution below $10^4$ days.
+In this study we perform the first simulation of the Galactic DWD population observable by LISA which incorporates an empirically-derived metallicity-dependent binary fraction, using the binary population synthesis suite \cosmic\ and a metallicity-dependent star formation history.
+We compare two models: one which assumes a metallicity-dependent binary fraction, and one with a binary fraction of 50\%.
+We repeat our analysis for three different assumptions for Roche-lobe overflow interactions.
+We find that while metallicity impacts the evolution and intrinsic properties of our simulated DWD progenitor binaries, the LISA-resolvable populations of the two models remain roughly indistinguishable.
+However, the size of the total Galactic DWD population orbiting in the LISA frequency band is reduced by more than half when accounting for a metallicity-dependent binary fraction for two of our four variations, which also lowers the effective foreground.
+The LISA population remains unchanged in number for two variations, highlighting the sensitivity of the population to binary evolution prescriptions.
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
-Most stars in the Galaxy will end their lives as white dwarfs. Of the 
-stars which are born with a binary companion, many will undergo 
-interactions which bring the two stars closer together, eventually forming 
-a close double white dwarf (DWD). Close DWDs, with orbital periods shorter 
-than $\sim2.75\,\rm{hr}$ are the largest source by number of mHz 
-gravitational waves (GWs) in the Galaxy 
-\citep[e.g.,][]{LISAMissionProposal}. The Laser Interferometer Space 
-Antenna (LISA) is expected to resolve at least $10^4$ individual DWD 
-binaries in the Milky Way and will also observe GW emission from the 
-entire Galactic DWD population through the unresolved foreground created 
-by overlapping signals at sub-mHz frequencies 
-\citep[e.g.,][]{Nelemans2001a, Ruiter2010, Nissanke2012, Yu2013, 
-Korol2017, Lamberts2019, Breivik2020a}. The resolved population will 
-enable the study of several important aspects of binary evolution like the 
-strength of tides \citep{Valsecchi2012}, the stability of mass transfer in 
-DWD systems \citep[e.g.,][]{Marsh2004, Shen2015, Gokhale2007, 
-Sepinsky2014, Kremer2015}, and the separation distribution of close DWDs 
-\citep{Korol2021} as well as provide a probe of Galactic structure 
-\citep{Korol2019} and the Local Group \citep{Korol2018}. The shape and 
-strength of the Galactic DWD foreground can also be used as a tool to 
-study the structure of the Milky Way \citep{Benacquista2006, 
-Breivik2020b}.
-
-The transition between individually resolved DWDs and the confusion 
-limited, or unresolved, DWD foreground is expected to occur near 
-$\sim1\,\rm{mHz}$ frequencies \citep[e.g. ][]{Ruiter2010}. In the 
-confusion limited regime, more than one binary radiates GWs in each LISA 
-frequency bin, thus creating a superposition of signals which are unable 
-to be disentangled. There are multiple parameters which shape the Galactic 
-DWD foreground. Assuming the evolution of each DWD system is driven solely 
-by GW emission, the frequency derivative scales proportionally to 
-$f_{\rm{GW}}^{11/3}$, causing a pileup of DWDs at lower frequencies 
-\citep[e.g.][]{Breivik2020b}. The spatial density of DWDs in the Galaxy 
-which defines the distance to each binary also impacts the foreground 
-amplitude, since GW strain scales inversely with distance. Star formation 
-history assumptions combine these two effects by assigning ages and 
-positions to each DWD in the population which determine the present day 
-orbital (and thus GW) frequencies as well as distances to each source.
-
-When viewed strictly as a source of noise, the unresolved Galactic DWD 
-foreground is the dominant noise source for LISA in the sub-mHz part of 
-LISA's frequency range. This extra noise above the detector noise floor 
-affects the detection of all other LISA sources including extreme mass 
-ratio inspirals \citep[e.g.,][]{Berti2006, Barack2007, Babak2017, 
-Moore2017}, merging black holes with masses between 
-$10^4$--$10^7\,M_{\odot}$ \citep[e.g.,][]{Klein2016, Bellovary2019}, and 
-cosmological GW backgrounds \citep[e.g.,][]{Bartolo2016, Caprini2016, 
-Caldwell2019}. For sources which have signals buried by the Galactic DWD 
-population, the foreground must be carefully analyzed and subtracted 
-\citep[][]{Adams2014,Cornish2020,Littenberg2020,Boileau2021}. The number 
-of resolved DWDs and the height of the unresolved DWD foreground are a 
-direct consequence of the number of DWD progenitors which form and evolve 
-over the Milky Way's history.
-
-While the binary fraction remains approximately constant across a large 
-metallicity range ($-1.5 \leq$ [Fe/H] $< 0.5$) for wide binaries, close OB 
-stars, and the stellar Initial Mass Function (IMF) \citep{Moe2017, 
-Moe2019}, the binary fraction for solar-type star systems with orbital 
-period $P_{\rm{orb}}\leq 10^4$ days (separation $a \leq 10$ AU) shows a 
-strong anti-correlation with metallicity \citep[e.g.][]{Badenes2018, 
-Moe2019, Mazzola2020, Price-Whelan2020}. Because close DWDs are the 
-remnants of close, solar-type binary stars, this anti-correlation plays an 
-important role in the formation, evolution, and characteristics of the DWD 
-population that LISA will observe.
-
-To date, population synthesis studies of the Galactic population of close 
-DWDs have either assumed a $100\%$ binary fraction or a $50\%$ binary 
-fraction, such that for every three stars formed, two reside in a binary 
-system \citep{Nelemans2001a, Yu2013, Korol2017, Lamberts2019}. In this 
-study, we investigate the effects of a metallicity-dependent binary 
-fraction on the formation and evolution of DWDs. To this end, we create 
-synthetic present-day Milky Way-like galaxies of DWDs and specifically 
-select systems with GW signals that may be observable by the space-based 
-detector LISA. Throughout, we make comparisons between the standard 
-assumption of a constant $50\%$ initial binary fraction (hereafter model 
-F50) and one with a metallicity-dependent binary fraction (hereafter model 
-FZ).
-
-In Section \ref{sec:simulations} we discuss our assumptions used in 
-simulating DWD populations and detail the process to produce present-day 
-synthetic Milky-Way-like galaxies. In Section \ref{sec:LISA_obs} we review 
-the derivation of LISA detectability for circular DWD populations at mHz 
-frequencies. In Section \ref{sec:results} we detail results showing how a 
-metallicity-dependent binary fraction affects the formation and evolution 
-of DWD populations assuming four sets of of binary evolution assumptions. 
-In Section \ref{sec:LISA_met} we detail the metallicity dependence of the 
-LISA DWD foreground and resolved population. Finally, we consider how a 
-metallicity-dependent close binary fraction impacts the height of the 
-Galactic DWD foreground in LISA for different binary evolution assumptions 
-in Section \ref{sec:model_compare} and conclude in Section 
-\ref{sec:conclusions}.
+Most stars in the Galaxy will end their lives as white dwarfs.
+Of the stars which are born with a binary companion, many will undergo interactions which bring the two stars closer together, eventually forming a close double white dwarf (DWD).
+Close DWDs, with orbital periods shorter than $\sim2.75\,\rm{hr}$ are the largest source by number of mHz gravitational waves (GWs) in the Galaxy \citep[e.g.,][]{LISAMissionProposal}.
+The Laser Interferometer Space Antenna (LISA) is expected to resolve at least $10^4$ individual DWD binaries in the Milky Way and will also observe GW emission from the entire Galactic DWD population through the unresolved foreground created by overlapping signals at sub-mHz frequencies \citep[e.g.,][]{Nelemans2001a, Ruiter2010, Nissanke2012, Yu2013, Korol2017, Lamberts2019, Breivik2020a}.
+The resolved population will enable the study of several important aspects of binary evolution like the strength of tides \citep{Valsecchi2012}, the stability of mass transfer in DWD systems \citep[e.g.,][]{Marsh2004, Shen2015, Gokhale2007, Sepinsky2014, Kremer2015}, and the separation distribution of close DWDs \citep{Korol2021} as well as provide a probe of Galactic structure \citep{Korol2019} and the Local Group \citep{Korol2018}.
+The shape and strength of the Galactic DWD foreground can also be used as a tool to study the structure of the Milky Way \citep{Benacquista2006, Breivik2020b}.
+
+The transition between individually resolved DWDs and the confusion limited, or unresolved, DWD foreground is expected to occur near $\sim1\,\rm{mHz}$ frequencies \citep[e.g.
+][]{Ruiter2010}.
+In the confusion limited regime, more than one binary radiates GWs in each LISA frequency bin, thus creating a superposition of signals which are unable to be disentangled.
+There are multiple parameters which shape the Galactic DWD foreground.
+Assuming the evolution of each DWD system is driven solely by GW emission, the frequency derivative scales proportionally to $f_{\rm{GW}}^{11/3}$, causing a pileup of DWDs at lower frequencies \citep[e.g.][]{Breivik2020b}.
+The spatial density of DWDs in the Galaxy which defines the distance to each binary also impacts the foreground amplitude, since GW strain scales inversely with distance.
+Star formation history assumptions combine these two effects by assigning ages and positions to each DWD in the population which determine the present day orbital (and thus GW) frequencies as well as distances to each source.
+
+When viewed strictly as a source of noise, the unresolved Galactic DWD foreground is the dominant noise source for LISA in the sub-mHz part of LISA's frequency range.
+This extra noise above the detector noise floor affects the detection of all other LISA sources including extreme mass ratio inspirals \citep[e.g.,][]{Berti2006, Barack2007, Babak2017, Moore2017}, merging black holes with masses between $10^4$--$10^7\,M_{\odot}$ \citep[e.g.,][]{Klein2016, Bellovary2019}, and cosmological GW backgrounds \citep[e.g.,][]{Bartolo2016, Caprini2016, Caldwell2019}.
+For sources which have signals buried by the Galactic DWD population, the foreground must be carefully analyzed and subtracted \citep[][]{Adams2014,Cornish2020,Littenberg2020,Boileau2021}.
+The number of resolved DWDs and the height of the unresolved DWD foreground are a direct consequence of the number of DWD progenitors which form and evolve over the Milky Way's history.
+
+While the binary fraction remains approximately constant across a large metallicity range ($-1.5 \leq$ [Fe/H] $< 0.5$) for wide binaries, close OB stars, and the stellar Initial Mass Function (IMF) \citep{Moe2017, Moe2019}, the binary fraction for solar-type star systems with orbital period $P_{\rm{orb}}\leq 10^4$ days (separation $a \leq 10$ AU) shows a strong anti-correlation with metallicity \citep[e.g.][]{Badenes2018, Moe2019, Mazzola2020, Price-Whelan2020}.
+Because close DWDs are the remnants of close, solar-type binary stars, this anti-correlation plays an important role in the formation, evolution, and characteristics of the DWD population that LISA will observe.
+
+To date, population synthesis studies of the Galactic population of close DWDs have either assumed a $100\%$ binary fraction or a $50\%$ binary fraction, such that for every three stars formed, two reside in a binary system \citep{Nelemans2001a, Yu2013, Korol2017, Lamberts2019}.
+In this study, we investigate the effects of a metallicity-dependent binary fraction on the formation and evolution of DWDs.
+To this end, we create synthetic present-day Milky Way-like galaxies of DWDs and specifically select systems with GW signals that may be observable by the space-based detector LISA.
+Throughout, we make comparisons between the standard assumption of a constant $50\%$ initial binary fraction (hereafter model F50) and one with a metallicity-dependent binary fraction (hereafter model FZ).
+
+In Section \ref{sec:simulations} we discuss our assumptions used in simulating DWD populations and detail the process to produce present-day synthetic Milky-Way-like galaxies.
+In Section \ref{sec:LISA_obs} we review the derivation of LISA detectability for circular DWD populations at mHz frequencies.
+In Section \ref{sec:results} we detail results showing how a metallicity-dependent binary fraction affects the formation and evolution of DWD populations assuming four sets of of binary evolution assumptions.
+In Section \ref{sec:LISA_met} we detail the metallicity dependence of the LISA DWD foreground and resolved population.
+Finally, we consider how a metallicity-dependent binary fraction impacts the height of the Galactic DWD foreground in LISA for different binary evolution assumptions in Section \ref{sec:model_compare} and conclude in Section \ref{sec:conclusions}.
 
 \section{Simulating a Galactic DWD population}\label{sec:simulations}
-In this section we describe the setup of our DWD simulations using the 
-binary population synthesis suite \cosmic, and the process to scale these 
-simulations to create Milky Way-like galaxies using the star formation 
-history of galaxy \textbf{m12i} in the Latte suite of the FIRE-2 
-simulations \citep{Wetzel2016, Hopkins2018} and stellar positions assigned 
-according to the the Ananke framework \citep{Sanderson2020}.
-
-\subsection{Metallicity-dependent binary 
-fraction}\label{subsec:metbinfrac}
-The close binary fraction in the Galaxy has been empirically shown to 
-depend on metallicity. This is manifested through an explicit dependence 
-of the companion frequency on orbital period \citep{Moe2021}. When 
-anchored to a log-normal orbital period distribution, the \emph{frequency} 
-of solar-type binary companions is skewed to shorter orbital periods. The 
-companion frequency differs from the binary fraction: the companion 
-frequency is the probability of a star having a companion at a given 
-orbital period, and the integration of this probability over all periods 
-results in the binary fraction of the population. The metallicity 
-dependence of the companion frequency is observed only below 
-$P_{\rm{orb}}=10^6$ days, above which there are not sufficient 
-observational data of binary systems to infer a metallicity dependence.
+In this section we describe the setup of our DWD simulations using the binary population synthesis suite \cosmic, and the process to scale these simulations to create Milky Way-like galaxies using the star formation history of galaxy \textbf{m12i} in the Latte suite of the FIRE-2 simulations \citep{Wetzel2016, Hopkins2018} and stellar positions assigned according to the the Ananke framework \citep{Sanderson2020}.
+
+\subsection{Metallicity-dependent binary fraction}\label{subsec:metbinfrac}
+The close binary fraction in the Galaxy has been empirically shown to depend on metallicity.
+This is manifested through an explicit dependence of the companion frequency on orbital period \citep{Moe2021}.
+When anchored to a log-normal orbital period distribution, the \emph{frequency} of solar-type binary companions is skewed to shorter orbital periods.
+The companion frequency differs from the binary fraction: the companion frequency is the probability of a star having a companion at a given orbital period, and the integration of this probability over all periods results in the binary fraction of the population.
+The metallicity dependence of the companion frequency is observed only below $P_{\rm{orb}}=10^6$ days, above which there are not sufficient observational data of binary systems to infer a metallicity dependence.
 
@@
 	\includegraphics[width=\columnwidth]{figures/met_dep_porb.pdf}
-    \caption{The distribution of the companion frequency f$_{\rm{logP}}$ 
-for solar-type stars is dependent on both ZAMS orbital period and 
-metallicity. Each curve is coloured by metallicity, with the darkest curve 
-corresponding to the lowest-metallicity bin in our simulations at [Fe/H] 
-$=-2.3$ and the lightest curve corresponding to our highest-metallicity 
-bin at [Fe/H] $=0.18$. Above $\log_{10}(P_{\rm{orb}}/\rm{day})\sim 4$, the 
-companion frequency distribution is the same for all metallicity bins as 
-no identified metallicity dependence at those periods exists in current 
-literature.}
+    \caption{The distribution of the companion frequency f$_{\rm{logP}}$ for solar-type stars is dependent on both ZAMS orbital period and metallicity.
+Each curve is coloured by metallicity, with the darkest curve corresponding to the lowest-metallicity bin in our simulations at [Fe/H] $=-2.3$ and the lightest curve corresponding to our highest-metallicity bin at [Fe/H] $=0.18$.
+Above $\log_{10}(P_{\rm{orb}}/\rm{day})\sim 4$, the companion frequency distribution \textbf{converges to} the same \textbf{curve} for all metallicity bins as no identified metallicity dependence at those periods exists in current literature.}
     \label{fig:met_dep_porb}
@@
 
-Figure \ref{fig:met_dep_porb} shows the companion frequency 
-f$_{\rm{logP}}$ for solar-type stars as a function of the logarithm of 
-orbital period, mirroring the inner binaries curve of Figure 2 in 
-\citet{Moe2021} and scaling to an overall multiplicity frequency of 0.67 
-(equivalent to an integrated binary fraction of 50\%) at solar 
-metallicity. To obtain the normalization of the companion frequency for 
-close binaries ($P_{\rm{orb}}<10^4$), we fit the results presented in 
-\citet{Moe2019} using linear regression to obtain a piecewise relation 
-between the metallicity, [Fe/H] and \textbf{close} binary fraction 
-$f_{\rm{b}}$ as
+Figure \ref{fig:met_dep_porb} shows the companion frequency f$_{\rm{logP}}$ for solar-type stars as a function of the logarithm of orbital period, mirroring the inner binaries curve of Figure 2 in \citet{Moe2021} and scaling to an overall multiplicity frequency of 0.67 (equivalent to an integrated binary fraction of 50\%) at solar metallicity.
+To obtain the normalization of the companion frequency for close binaries ($P_{\rm{orb}}<10^4$), we fit the results presented in \citet{Moe2019} using linear regression to obtain a piecewise relation between the metallicity, [Fe/H] and \textbf{close} binary fraction $f_{\rm{b}}$ as
 
 \[f_{\rm{b}}= \begin{cases} 
-      - 0.0648 \cdot [\rm{Fe/H}] + 0.3356, & [\rm{Fe/H}]\leq -1.0 
-\numberthis \\
-      -0.1977 \cdot [\rm{Fe/H}] + 0.2025, & [\rm{Fe/H}]> -1.0  , 
+      - 0.0648 \, \rm{ [Fe/H]} + 0.3356, & [\rm{Fe/H}]\leq -1.0 \numberthis \\
+     -0.1977 \, \rm{ [Fe/H]} + 0.2025, & [\rm{Fe/H}]> -1.0  , 
    \end{cases}
@@
 
-\noindent where we convert between [Fe/H] and metallicity Z, assuming all 
-stars have solar abundance such that
+\noindent where we convert between [Fe/H] and metallicity Z, assuming all stars have solar abundance such that
 \begin{equation}
 \label{eq:metallicity}
-    [\rm{Fe/H}] = 
-\log_{10}\Big(\frac{\textit{Z}}{\textit{Z}_{\odot}}\Big),
+    [\rm{Fe/H}] = \log_{10}\Big(\frac{\textit{Z}}{\textit{Z}_{\odot}}\Big),
 \end{equation}
@@
 We count all higher-order companions as secondary, or binary, components.
-We show curves for all 15 of our metallicity bins, increasing in 
-metallicity from darkest to lightest curve colour. The lowest metallicity 
-($\rm{[Fe/H]}=-2.3$) shows the highest propensity for short-period 
-binaries, in contrast to higher metallicity systems which have a frequency 
-distribution with a relatively constant companion frequency for orbital 
-periods between $10^4$ and $10^6$ days.
-
-While we simulate binaries across the entire orbital period distribution, 
-the close binary fraction, which exhibits the discussed metallicity 
-dependence, will be that which impacts the LISA population since systems 
-with $\log_{10}(P_{\rm{orb}}/$day)$>4$ will be unlikely to evolve enough 
-to enter the LISA band by present day.
+We show curves for all 15 of our metallicity bins, increasing in metallicity from darkest to lightest curve colour.
+The lowest metallicity ($\rm{[Fe/H]}=-2.3$) shows the highest propensity for short-period binaries, in contrast to higher metallicity systems which have a frequency distribution with a relatively constant companion frequency for orbital periods between $10^4$ and $10^6$ days.
+
+While we simulate binaries across the entire orbital period distribution, the close binary fraction, which exhibits the discussed metallicity dependence, will be that which impacts the LISA population since systems with $\log_{10}(P_{\rm{orb}}/$day)$>4$ will be unlikely to evolve enough to enter the LISA band by present day.
 
@@
 \label{sec:bin_pop}
-We simulate the evolution of DWD progenitor populations using 
-\cosmic\footnote{https://cosmic-popsynth.github.io}, an open-source 
-Python-based rapid binary population synthesis suite which employs single 
-and binary star evolution using \texttt{SSE/BSE} \citep{Hurley2000, 
-Hurley2002}. Several modifications have been added to \cosmic\ which 
-incorporate updates for massive star evolution and binary interactions. 
-For a detailed description of these modifications see 
-\citet{Breivik2020a}. \cosmic\ has been used in several studies to examine 
-the effects of binary evolution on binary populations from blue stragglers 
-\citep{Leiner2021} and heartbeat stars \citep{Jayasinghe2021}, to white 
-dwarf populations \citep{Kremer2017,Breivik2018,Kilic2021}, to merging 
-compact object populations in isolated binaries \citep{Zevin2020b, 
-Zevin2020a, Zevin2021, Wong2021, Mandhai2021} and in dynamical 
-environments around super-massive black holes \citep{Stephan2019, 
-Wang2021}.
-
-\cosmic\ is especially useful for efficient generation of large 
-populations of compact binaries. Instead of choosing a fixed number of 
-binary stars for each simulation, \cosmic\ iteratively simulates 
-populations until parameter distributions of the binary population 
-converge to a stable shape as more binaries are added. This process is 
-quantified through the $match$ parameter inspired by matched filtering 
-techniques \citep[e.g. Eq. 6 of ][]{Chatziioannou2017} defined as
-
-\begin{equation}
-   match = 
-\frac{\sum_{k=1}^{N}P_{k,i}P_{k,i+1}}{\sqrt{\sum_{k=1}^{N}P_{k,i}P_{k,i}\sum_{k=1}^{N}P_{k,i+1}P_{k,i+1}}},
-\end{equation}
-where $P_{k,i}$ represents the height of bin $k$ on the $i\rm{th}$ 
-iteration \citep{Breivik2020a}. In this study, we simulate binaries until 
-$\log_{10}(1-match) \leq -5$ for the masses and orbital periods of each 
-DWD population at the formation of the second WD. Since all DWD progenitor 
-binaries simulated with \cosmic\ are circularized through mass transfer or 
-tides before the second WD forms \citep[e.g.][]{Marsh2004, Gokhale2007, 
-Sepinsky2014, Kremer2015}, we do not consider convergence of DWD 
-eccentricities.
-
-The masses and orbital periods at the formation of the second-formed WD 
-span a wide range depending on the WD binary component types, thus we 
-consider four DWD combinations: two helium WDs (He + He), a carbon-oxygen 
-WD orbiting a helium WD (CO + He), two carbon-oxygen WDs (CO + CO), and an 
-oxygen-neon orbiting a helium, carbon-oxygen, or oxygen-neon WD (ONe + X). 
-For each DWD type we simulate a grid of $15$ metallicities spaced 
-uniformly in $\log_{10}(Z)$ between $Z=10^{-4}$ to $0.03$, to account for 
-the limits of the \citet{Hurley2000} stellar evolution tracks employed in 
-\cosmic. This results in a total of $60$ populations across all DWD types 
-and metallicities for each set of model assumptions. The output of 
-\cosmic\ contains information limited to intrinsic binary properties like 
-mass and orbital period. External parameters like Galactic position and 
-orientation are assigned in a post-processing scheme which uses 
-metallicity-dependent positions and ages from the Ananke framework of 
-galaxy \textbf{m12i} from the Latte Suite of the FIRE-2 simulations (see 
-Section~\ref{sec:FIRE} for details).
-
-We assume that the Zero Age Main Sequence (ZAMS) masses, orbital periods 
-and eccentricities for each binary are independently distributed. We 
-choose primary masses following \citet{Kroupa2001}, a flat mass ratio 
-distribution \citep{Mazeh1992, Goldberg1994} and a uniform eccentricity 
-distribution following \cite{Geller2019}. For our simulations which follow 
-a metallicity-dependent binary fraction (model FZ), a skewed log-normal 
-orbital period distribution is sampled in accordance with the 
-metallicity-dependent companion frequency of \citet{Moe2021} as discussed 
-in Section \ref{subsec:metbinfrac}. For our simulations which assume a 
-constant 50\% binary fraction (model F50), we use a log-uniform period 
-distribution following Opik's Law similar to previous studies 
-\citep[e.g.][]{Nelemans2001a, Toonen2012, Korol2017, Lamberts2019}. We 
-assume a $100\%$ binary fraction in the F50 COSMIC simulations to reduce 
-computation time and scale the simulations to a constant $50\%$ binary 
-fraction in a post-processing scheme. We initialize all binaries with the 
-same evolution time of $13.7\,\rm{Gyr}$ to capture all potential evolution 
-within a Hubble time. Although we simulate binaries across the full 
-orbital period distribution, we discard DWD binaries which form with 
-separations $a\geq 1000\,R_\odot$ during post-processing, since these are 
-unlikely to evolve into the LISA band by present day.
-
-We consider a fiducial set of assumptions which follow the \cosmic\ 
-defaults described in \citet{Breivik2020a} except for the treatment of 
-Roche-lobe overflow (RLO). The stability of RLO mass transfer is 
-determined using critical mass ratios resulting from radius-mass exponents 
-\citep{Webbink1985, Hurley2002}, where the critical mass ratio is defined 
-as the ratio of the donor to accretor mass. We assume critical mass ratios 
-following \citet{Claeys2014} which reduce the standard critical mass ratio 
-assumptions from \citet{Hurley2002} for main sequence (MS) donors by 
-$\sim50\%$ from $3$ to $1.6$ based on the models of \citet{deMink2007} and 
-treat WD accretors separately following the models of 
-\citet{Soberman1997}. We increase the mass loss rate from the donor 
-following Equation 11 of \citet{Claeys2014}. The amount of mass lost 
-during RLO from the donor is limited by the overflow factor of the donor 
-radius to its Roche radius following \citet{Hurley2002}. The amount of 
-mass accepted by the accretor is limited to $10$ times the accretor's mass 
-divided by the accretor's thermal timescale. Finally, for RLO mass loss 
-which becomes unstable and leads to common envelope evolution (CEE) we 
-assume that the donor's binding energy is calculated according to the fits 
-detailed in Appendix B of \citet{Claeys2014} and that orbital energy is 
-deposited with $100\%$ efficiency into unbinding the common envelope 
-($\alpha=1$).
-
-The LISA-detectable DWD populations that result from our simulations may 
-vary depending on the assumptions made regarding binary interactions. In 
-order to explore the range of results, we complete this study for three 
-binary evolution parameter variations on top of our fiducial set of 
-assumptions. For each variation, we consider models FZ and F50 as done in 
-the fiducial case described above. In variation $q3$, we vary the 
-assumption for the critical mass ratios at which a RLO interaction remains 
-stable or becomes unstable from our fiducial assumptions. The critical 
-mass ratio $q_c$ is increased to $3.0$ and thus allows stable mass 
-transfer for more massive RLO donors. In variations $\alpha25$ and 
-$\alpha5$, we modify the common envelope ejection efficiency to be either 
-much less ($\alpha=0.25$) or more ($\alpha=5$) than in our fiducial 
-assumption ($\alpha=1$) to capture the range of possible CE ejection 
-efficiencies quoted in the literature  \citep[e.g.][]{Zorotovic2010, 
-Fragos2019}. Larger common envelope ejection efficiencies lead to wider 
-post-CE separations, while smaller ejection efficiencies either lead to 
-closer post-CE separations or stellar mergers where the envelope ejection 
-fails. Between all variations, all other prescriptions for binary 
-evolution remain identical besides the one varied parameter. \textbf{A 
-summary of all models and variations explored in this work is given in 
-Table \ref{tbl:models}.} We delve in depth into the fiducial results in 
-each section, and then give a brief overview of how the results change for 
-each parameter variation.
+We simulate the evolution of DWD progenitor populations using \cosmic\footnote{https://cosmic-popsynth.github.io}, an open-source Python-based rapid binary population synthesis suite which employs single and binary star evolution using \texttt{SSE/BSE} \citep{Hurley2000, Hurley2002}.
+Several modifications have been added to \cosmic\ which incorporate updates for massive star evolution and binary interactions.
+For a detailed description of these modifications see \citet{Breivik2020a}.
+\cosmic\ has been used in several studies to examine the effects of binary evolution on binary populations from blue stragglers \citep{Leiner2021} and heartbeat stars \citep{Jayasinghe2021}, to white dwarf populations \citep{Kremer2017,Breivik2018,Kilic2021}, to merging compact object populations in isolated binaries \citep{Zevin2020b, Zevin2020a, Zevin2021, Wong2021, Mandhai2021} and in dynamical environments around super-massive black holes \citep{Stephan2019, Wang2021}.
+
+\cosmic\ is especially useful for efficient generation of large populations of compact binaries.
+Instead of choosing a fixed number of binary stars for each simulation, \cosmic\ iteratively simulates populations until parameter distributions of the binary population converge to a stable shape as more binaries are added.
+This process is quantified through the $match$ parameter inspired by matched filtering techniques \citep[e.g.
+Eq.
+6 of ][]{Chatziioannou2017} defined as
+
+\begin{equation}
+   match = \frac{\sum_{k=1}^{N}P_{k,i}P_{k,i+1}}{\sqrt{\sum_{k=1}^{N}P_{k,i}P_{k,i}\sum_{k=1}^{N}P_{k,i+1}P_{k,i+1}}},
+\end{equation}
+where $P_{k,i}$ represents the height of bin $k$ on the $i\rm{th}$ iteration \citep{Breivik2020a}.
+In this study, we simulate binaries until $\log_{10}(1-match) \leq -5$ for the masses and orbital periods of each DWD population at the formation of the second WD.
+Since all DWD progenitor binaries simulated with \cosmic\ are circularized through mass transfer or tides before the second WD forms \citep[e.g.][]{Marsh2004, Gokhale2007, Sepinsky2014, Kremer2015}, we do not consider convergence of DWD eccentricities.
+
+The masses and orbital periods at the formation of the second-formed WD span a wide range depending on the WD binary component types, thus we consider four DWD combinations: two helium WDs (He + He), a carbon-oxygen WD orbiting a helium WD (CO + He), two carbon-oxygen WDs (CO + CO), and an oxygen-neon orbiting a helium, carbon-oxygen, or oxygen-neon WD (ONe + X).
+For each DWD type we simulate a grid of $15$ metallicities spaced uniformly in $\log_{10}(Z)$ between $Z=10^{-4}$ to $0.03$, to account for the limits of the \citet{Hurley2000} stellar evolution tracks employed in \cosmic.
+This results in a total of $60$ populations across all DWD types and metallicities for each set of model assumptions.
+The output of \cosmic\ contains information limited to intrinsic binary properties like mass and orbital period.
+External parameters like Galactic position and orientation are assigned in a post-processing scheme which uses metallicity-dependent positions and ages from the Ananke framework of galaxy \textbf{m12i} from the Latte Suite of the FIRE-2 simulations (see Section~\ref{sec:FIRE} for details).
+
+We assume that the Zero Age Main Sequence (ZAMS) masses, orbital periods and eccentricities for each binary are independently distributed.
+We choose primary masses following \citet{Kroupa2001}, a flat mass ratio distribution \citep{Mazeh1992, Goldberg1994} and a uniform eccentricity distribution following \cite{Geller2019}.
+For our simulations which follow a metallicity-dependent binary fraction (model FZ), a skewed log-normal orbital period distribution is sampled in accordance with the metallicity-dependent companion frequency of \citet{Moe2021} as discussed in Section \ref{subsec:metbinfrac}.
+For our simulations which assume a constant 50\% binary fraction (model F50), we use a log-uniform period distribution following Opik's Law similar to previous studies \citep[e.g.][]{Nelemans2001a, Toonen2012, Korol2017, Lamberts2019}.
+We assume a $100\%$ binary fraction in the F50 COSMIC simulations to reduce computation time and scale the simulations to a constant $50\%$ binary fraction in a post-processing scheme.
+We initialize all binaries with the same evolution time of $13.7\,\rm{Gyr}$ to capture all potential evolution within a Hubble time.
+Although we simulate binaries across the full orbital period distribution, we discard DWD binaries which form with separations $a\geq 1000\,R_\odot$ during post-processing, since these are unlikely to evolve into the LISA band by present day.
+
+We consider a fiducial set of assumptions which follow the \cosmic\ defaults described in \citet{Breivik2020a} except for the treatment of Roche-lobe overflow (RLO).
+The stability of RLO mass transfer is determined using critical mass ratios resulting from radius-mass exponents \citep{Webbink1985, Hurley2002}, where the critical mass ratio is defined as the ratio of the donor to accretor mass.
+We assume critical mass ratios following \citet{Claeys2014} which reduce the standard critical mass ratio assumptions from \citet{Hurley2002} for main sequence (MS) donors by $\sim50\%$ from $3$ to $1.6$ based on the models of \citet{deMink2007} and treat WD accretors separately following the models of \citet{Soberman1997}.
+We increase the mass loss rate from the donor following Equation 11 of \citet{Claeys2014}.
+The amount of mass lost during RLO from the donor is limited by the overflow factor of the donor radius to its Roche radius following \citet{Hurley2002}.
+The amount of mass accepted by the accretor is limited to $10$ times the accretor's mass divided by the accretor's thermal timescale.
+Finally, for RLO mass loss which becomes unstable and leads to common envelope evolution (CEE) we assume that the donor's binding energy is calculated according to the fits detailed in Appendix B of \citet{Claeys2014} and that orbital energy is deposited with $100\%$ efficiency into unbinding the common envelope ($\alpha=1$).
+
+The LISA-detectable DWD populations that result from our simulations may vary depending on the assumptions made regarding binary interactions.
+In order to explore the range of results, we complete this study for three binary evolution parameter variations on top of our fiducial set of assumptions.
+For each variation, we consider models FZ and F50 as done in the fiducial case described above.
+In variation $q3$, we vary the assumption for the critical mass ratios at which a RLO interaction remains stable or becomes unstable from our fiducial assumptions.
+The critical mass ratio $q_c$ is increased to $3.0$ and thus allows stable mass transfer for more massive RLO donors.
+In variations $\alpha25$ and $\alpha5$, we modify the common envelope ejection efficiency to be either much less ($\alpha=0.25$) or more ($\alpha=5$) than in our fiducial assumption ($\alpha=1$) to capture the range of possible CE ejection efficiencies quoted in the literature  \citep[e.g.][]{Zorotovic2010, Fragos2019}.
+Larger common envelope ejection efficiencies lead to wider post-CE separations, while smaller ejection efficiencies either lead to closer post-CE separations or stellar mergers where the envelope ejection fails.
+Between all variations, all other prescriptions for binary evolution remain identical besides the one varied parameter.
+\textbf{A summary of all models and variations explored in this work is given in Table \ref{tbl:models}.} We delve in depth into the fiducial results in each section, and then give a brief overview of how the results change for each parameter variation.
 
@@
     \end{tabular}
-    \caption{\textbf{Summary of the models and binary evolution assumption 
-variation simulations that are explored in this study.}}
+    \caption{\textbf{Summary of the models and binary evolution assumption variation simulations that are explored in this study.}}
     \label{tbl:models}
@@
 
-\subsection{A metallicity-dependent SFH: Convolving with the FIRE-2 
-models}
+\subsection{A metallicity-dependent SFH: Convolving with the FIRE-2 models}
 \label{sec:FIRE}
-To create Milky-Way-like galaxies which integrate the 
-metallicity-dependent binary fraction, we use the metallicity-dependent 
-ages and positions of galaxy \textbf{m12i} from the ``Latte" suite of the 
-FIRE-2 simulations \citep{Hopkins2015, Wetzel2016, Hopkins2018} to create 
-synthetic, Milky-Way-like DWD populations.
-
-The \textbf{m12i} galaxy provides particle mass resolution of 7070 
-$M_\odot$ per star particle. Each star particle has an associated 
-metallicity, position, and age, which is combined with the output of 
-\cosmic\ to assign DWDs to each star particle by matching its metallicity 
-to our \cosmic\ metallicity grid. The positions of each DWD are assigned 
-using the Ananke framework since multiple DWD binaries can form within a 
-single star particle. Specifically, we use an epanechnikov kernel where 
-the kernel size is inversely proportional to the local density to assign 
-the radial component of spherically symmetric offsets from the center of 
-each star particle following \citet{Sanderson2020}.
+To create Milky-Way-like galaxies which integrate the metallicity-dependent binary fraction, we use the metallicity-dependent ages and positions of galaxy \textbf{m12i} from the ``Latte" suite of the FIRE-2 simulations \citep{Hopkins2015, Wetzel2016, Hopkins2018} to create synthetic, Milky-Way-like DWD populations.
+
+The \textbf{m12i} galaxy provides particle mass resolution of 7070 $M_\odot$ per star particle.
+Each star particle has an associated metallicity, position, and age, which is combined with the output of \cosmic\ to assign DWDs to each star particle by matching its metallicity to our \cosmic\ metallicity grid.
+The positions of each DWD are assigned using the Ananke framework since multiple DWD binaries can form within a single star particle.
+Specifically, we use an epanechnikov kernel where the kernel size is inversely proportional to the local density to assign the radial component of spherically symmetric offsets from the center of each star particle following \citet{Sanderson2020}.
 
@@
 	\includegraphics[width=\columnwidth]{figures/sfh_vs_fb.pdf}
-    \caption{The metallicity-dependent binary fraction for close 
-solar-type binaries with P $< 10^4$ days (black) plotted against the 
-logarithm of $Z/Z_\odot$, with scatter points denoting the location of the 
-metallicity grid used in our \cosmic\ simulations. The secondary axis 
-shows the amount of mass in stars formed within each metallicity bin from 
-galaxy \textbf{m12i} of the ``Latte" suite in the FIRE-2 simulations as a 
-red histogram. The amount of stellar mass formed with super-solar 
-metallicities dominates the distribution. Note that the primary axis shows 
-$f_{\rm{b}}(Z)$ in linear scale, and the secondary axis shows amount of 
-mass formed in log-scale. The opposing trends of these two distributions 
-compete throughout this study.}
+    \caption{The metallicity-dependent binary fraction for close solar-type binaries with P $< 10^4$ days (black) plotted against the logarithm of $Z/Z_\odot$, with scatter points denoting the location of the metallicity grid used in our \cosmic\ simulations.
+The secondary axis shows the amount of mass in stars formed within each metallicity bin from galaxy \textbf{m12i} of the ``Latte" suite in the FIRE-2 simulations as a red histogram.
+The amount of stellar mass formed with super-solar metallicities dominates the distribution.
+Note that the primary axis shows $f_{\rm{b}}(Z)$ in linear scale, and the secondary axis shows amount of mass formed in log-scale.
+The opposing trends of these two distributions compete throughout this study.}
     \label{fig:sfh_vs_fb}
@@
 
-The metallicity-dependent close binary fraction for solar-type binaries 
-($P_{\rm{orb}} < 10^4$ days), or simply the close binary fraction from 
-here on, is shown in black in Figure \ref{fig:sfh_vs_fb} along with the 
-mass in star particles from galaxy \textbf{m12i}, shown in red, as a 
-function of our metallicity grid. The close binary fraction, $f_{\rm{b}}$, 
-drops drastically across metallicity while the mass formed in 
-\textbf{m12i} increases significantly. These two opposing trends compete 
-throughout this study along with the impact of metallicity on single star 
-evolution to form the final numerical distribution of systems in our DWD 
-populations.
-
-Since our \cosmic\ simulations assume a binary fraction of $f_{\rm{b}} = 
-1$ for model F50, we scale the amount of mass sampled at ZAMS required to 
-produce our \cosmic-generated population of DWDs ($M_{\text{b,ZAMS}}$) to 
-the proper amount of mass sampled in single and binary stars 
-($M_{\text{ZAMS,sim}}$). We do this by sampling single stars and primary 
-masses of binary stars from the \cite{Kroupa2001} IMF and sampling 
-secondary masses of the binary stars from a uniform mass distribution, 
-where the number of binaries is calculated to ensure $f_{\rm{b}}=0.5$. 
-From this sample, we obtain the ratio of mass in single stars to the mass 
-in binary stars, $R(f_{\rm{b}})$. For model F50, the ratio is a constant 
-$R(f_{\rm{b}}) = 0.64$. The total amount of ZAMS mass in single and binary 
-stars is then $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}} (1 + 
-R(f_{\rm{b}}))$. For model FZ, no scaling is applied since our \cosmic\ 
-simulations already have the population-wide binary fraction incorporated, 
-and thus $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}}$.
-
-Once we determine the total ZAMS mass required to produce our simulated 
-population for a given metallicity, the number of DWDs formed per unit 
-solar mass at metallicity $Z_i$ is
-\begin{equation}
-    n_{\rm{DWD}}(Z_i) = \frac{N_{\rm{DWD, sim}}(Z_i)}{M_{\rm{ZAMS, 
-sim}}(Z_i)}.
-\end{equation}
-
-\noindent The number of DWD’s per \textbf{m12i} star particle at 
-metallicity $Z_i$ is then
+The metallicity-dependent close binary fraction for solar-type binaries ($P_{\rm{orb}} < 10^4$ days), or simply the close binary fraction from here on, is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid.
+The close binary fraction, $f_{\rm{b}}$, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly.
+These two opposing trends compete throughout this study along with the impact of metallicity on single star evolution to form the final numerical distribution of systems in our DWD populations.
+
+Since our \cosmic\ simulations assume a binary fraction of $f_{\rm{b}} = 1$ for model F50, we scale the amount of mass sampled at ZAMS required to produce our \cosmic-generated population of DWDs ($M_{\text{b,ZAMS}}$) to the proper amount of mass sampled in single and binary stars ($M_{\text{ZAMS,sim}}$).
+We do this by sampling single stars and primary masses of binary stars from the \cite{Kroupa2001} IMF and sampling secondary masses of the binary stars from a uniform mass distribution, where the number of binaries is calculated to ensure $f_{\rm{b}}=0.5$.
+From this sample, we obtain the ratio of mass in single stars to the mass in binary stars, $R(f_{\rm{b}})$.
+For model F50, the ratio is a constant $R(f_{\rm{b}}) = 0.64$.
+The total amount of ZAMS mass in single and binary stars is then $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}} (1 + R(f_{\rm{b}}))$.
+For model FZ, no scaling is applied since our \cosmic\ simulations already have the population-wide binary fraction incorporated, and thus $M_{\text{ZAMS,sim}} =  M_{\text{b,ZAMS}}$.
+
+Once we determine the total ZAMS mass required to produce our simulated population for a given metallicity, the number of DWDs formed per unit solar mass at metallicity $Z_i$ is
+\begin{equation}
+    n_{\rm{DWD}}(Z_i) = \frac{N_{\rm{DWD, sim}}(Z_i)}{M_{\rm{ZAMS, sim}}(Z_i)}.
+\end{equation}
+
+\noindent The number of DWD’s per \textbf{m12i} star particle at metallicity $Z_i$ is then
 \begin{equation}
@@
 
-\noindent where $M_\star = 7070\,M_\odot$ is the mass per \textbf{m12i} 
-star particle. Since $N_{\rm{DWD},\star} (Z_i)$ is not an integer, we 
-treat the decimal component as the probability that the star particle 
-contains an extra DWD in addition to the integer number. For each star 
-particle, we sample with replacement $N_{\rm{DWD},\star}(Z_i)$ DWDs from 
-the corresponding simulated \cosmic\ population at that metallicity and 
-assign the ZAMS birth time of each DWD to the formation time of the star 
-particle. For most DWD types there is more than one DWD binary system 
-assigned to each \textbf{m12i} star particle.
-
-If the DWD formation time is less than the age of the star particle, we 
-evolve the DWD over the remaining time between its formation and star 
-particle age, $t_{\rm{evol}}$, to produce the present-day population. Once 
-a DWD is formed, we assume that the binary evolves only due to the 
-emission of GWs. Due to tidal effects and mass transfer between their 
-progenitor binaries, all DWDs in our simulations are circular, thus 
-eccentricity does not need to be considered. The orbital evolution over 
-the time $t_{\rm{evol}}$ is then simply defined according to 
-\citet{Peters1964} as
+\noindent where $M_\star = 7070\,M_\odot$ is the mass per \textbf{m12i} star particle.
+Since $N_{\rm{DWD},\star} (Z_i)$ is not an integer, we treat the decimal component as the probability that the star particle contains an extra DWD in addition to the integer number.
+For each star particle, we sample with replacement $N_{\rm{DWD},\star}(Z_i)$ DWDs from the corresponding simulated \cosmic\ population at that metallicity and assign the ZAMS birth time of each DWD to the formation time of the star particle.
+For most DWD types there is more than one DWD binary system assigned to each \textbf{m12i} star particle.
+
+If the DWD formation time is less than the age of the star particle, we evolve the DWD over the remaining time between its formation and star particle age, $t_{\rm{evol}}$, to produce the present-day population.
+Once a DWD is formed, we assume that the binary evolves only due to the emission of GWs.
+Due to tidal effects and mass transfer between their progenitor binaries, all DWDs in our simulations are circular, thus eccentricity does not need to be considered.
+The orbital evolution over the time $t_{\rm{evol}}$ is then simply defined according to \citet{Peters1964} as
 \begin{equation}
@@
 
-We discard any DWDs for which the sum of their ZAMS birth time, given by 
-the star particle formation time, and DWD formation time is larger than 
-the age of the star particle since the system will not have evolved long 
-enough to become a DWD at present. We further discard any DWDs for which 
-the lower mass WD overflows it's Roche lobe before present day, because 
-the outcomes of these interactions are highly uncertain and their 
-treatment is outside the scope of this work \citep[e.g., ][]{Shen2015, 
-Kremer2017}. This choice does not significantly affect our results since 
-stably accreting WD binaries are unlikely to contribute appreciably to the 
-Galactic DWD foreground due to their small mass ratios at frequencies 
-below 1 mHz \citep{Breivik2018}. The separation at which the lower mass WD 
-overflows its Roche Lobe is defined as
-
-\begin{equation}
-    a_{\text{RLO,}\ell} = R_{\ell} \frac{0.6 q_{\ell}^{2/3} + 
-\ln{(1+q_{\ell}^{1/3})}}{0.49 q_{\ell}^{2/3}}
-\end{equation}
-where $R_{\ell}$ is the radius of the lower mass WD and $q_{\ell} = 
-M_{\ell}/M_{h}$ is the ratio of the lower- to higher-mass WD components. 
-\citep{Eggleton1983}. 
+We discard any DWDs for which the sum of their ZAMS birth time, given by the star particle formation time, and DWD formation time is larger than the age of the star particle since the system will not have evolved long enough to become a DWD at present.
+We further discard any DWDs for which the lower-mass WD overflows it's Roche lobe before present day, because the outcomes of these interactions are highly uncertain and their treatment is outside the scope of this work \citep[e.g., ][]{Shen2015, Kremer2017}.
+This choice does not significantly affect our results since stably accreting WD binaries are unlikely to contribute appreciably to the Galactic DWD foreground due to their small mass ratios at frequencies below 1 mHz \citep{Breivik2018}.
+The separation at which the lower-mass WD overflows its Roche Lobe is defined as
+
+\begin{equation}
+    a_{\text{RLO,}\ell} = R_{\ell} \frac{0.6 q_{\ell}^{2/3} + \ln{(1+q_{\ell}^{1/3})}}{0.49 q_{\ell}^{2/3}}
+\end{equation}
+where $R_{\ell}$ is the radius of the lower-mass WD and $q_{\ell} = M_{\ell}/M_{h}$ is the ratio of the lower- to higher-mass WD components \citep{Eggleton1983}. 
 We define the radius of a WD following \citet{Tout1997, Hurley2000} as
 \begin{equation}
-    R_{\rm{WD}} = \max\Bigg(R_\text{NS}, 
-0.0115\sqrt{\left(\frac{M_\text{Ch}}{M}\right)^{2/3}-\left(\frac{M}{M_\text{Ch}}\right)^{2/3}} 
-\Bigg) 
-\end{equation}
-\noindent where $R_\text{NS} = 1.4\cdot 10^{-5}~R_\odot$ is the radius of 
-a neutron star, $M_{\text{Ch}}=1.44 ~M_\odot$ is the Chandrasekhar limit 
-for the mass of a stable WD, and $M$ is the mass of the WD in solar 
-masses.
-
-For the non-discarded systems, we log the present-day separations from 
-which the present-day orbital frequency $f_\text{orb}$ can be found using 
-Kepler's third law. The GW frequency is then $f_\text{GW} = 
-2f_\text{orb}$.
+    R_{\rm{WD}} = \max\Bigg(R_\text{NS}, 0.0115\sqrt{\left(\frac{M_\text{Ch}}{M}\right)^{2/3}-\left(\frac{M}{M_\text{Ch}}\right)^{2/3}} \Bigg) 
+\end{equation}
+\noindent where $R_\text{NS} = 1.4\cdot 10^{-5}~R_\odot$ is the radius of a neutron star, $M_{\text{Ch}}=1.44 ~M_\odot$ is the Chandrasekhar limit for the mass of a stable WD, and $M$ is the mass of the WD in solar masses.
+
+For the non-discarded systems, we log the present-day separations from which the present-day orbital frequency $f_\text{orb}$ can be found using Kepler's third law.
+The GW frequency is then $f_\text{GW} = 2f_\text{orb}$.
 
@@
 \label{sec:LISA_obs}
-We use \legwork\footnote{https://legwork.readthedocs.io} \citep{Wagg2021} 
-to determine the detectability of our simulated DWD populations for 
-sources with GW frequencies $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$. \legwork\ 
-calculates the position-, orientation-, and angle-averaged signal to noise 
-ratio (SNR) for inspiraling GW sources closely following the derivations 
-of \citet{Flanagan1998} and using the LISA noise power spectral density 
-(PSD) of \citet{Robson2019}.
-
-To lowest order in the post-Newtonian expansion, the frequency evolution 
-of circular orbits for quadrupole GW emission is defined as
-\begin{equation}
-    \Dot{f}_n = \frac{48n}{5\pi} \frac{(G\mathcal{M}_c)^{5/3}}{c^5} (2\pi 
-f_\text{orb})^{11/3}.
-\end{equation}
-We classify DWDs as evolving, or ``chirping", when $\Dot{f}_n \geq 
-1/t_\text{obs}^2$. For evolving sources, the SNR is
-
-\begin{equation}
-   \langle \rho \rangle^2_{\text{circ,evol}} = \int_{f_0}^{f_1}df   
-\frac{h_{c}^2}{f^2S_n(f)}
-\end{equation}
-
-\noindent where $h_c$ is the characteristic strain of the system, $S_n(f)$ 
-is the LISA sensitivity curve of \citet{Robson2019}, and the frequency 
-limits are determined by the orbital evolution over the observation time, 
-$T_{\rm{obs}}=4\,\rm{yr}$. The characteristic strain for circular orbits 
-is 
-\begin{equation}
-    h_{c}^2 = \frac{2^{2/3}}{3 \pi^{4/3}} \frac{(G 
-\mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}},
-\end{equation}
-\noindent where $\mathcal{M}_c = (M_1M_2)^{3/5}/(M_1 + M_2)^{1/5}$ is the 
-system's chirp mass, and $D_L$ is the systems luminosity distance which we 
-assume to be the distance of each simulated DWD to the Sun.
-
-For stationary sources, the SNR is modified due to the lack of observable 
-orbital evolution as
+We use \legwork\footnote{https://legwork.readthedocs.io} \citep{Wagg2021} to determine the detectability of our simulated DWD populations for sources with GW frequencies $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$.
+\legwork\ calculates the position-, orientation-, and angle-averaged signal to noise ratio (SNR) for inspiraling GW sources closely following the derivations of \citet{Flanagan1998} and using the LISA noise power spectral density (PSD) of \citet{Robson2019}.
+
+To lowest order in the post-Newtonian expansion, the frequency evolution of circular orbits for quadrupole GW emission is defined as
+\begin{equation}
+    \Dot{f}_n = \frac{48n}{5\pi} \frac{(G\mathcal{M}_c)^{5/3}}{c^5} (2\pi f_\text{orb})^{11/3}.
+\end{equation}
+We classify DWDs as evolving, or ``chirping", when $\Dot{f}_n \geq 1/T_\text{obs}^2$. For evolving sources, the SNR is
+
+\begin{equation}
+   \langle \rho \rangle^2_{\text{circ,evol}} = \int_{f_0}^{f_1}df   \frac{h_{c}^2}{f^2S_n(f)}
+\end{equation}
+
+\noindent where $h_c$ is the characteristic strain of the system, $S_n(f)$ is the LISA sensitivity curve of \citet{Robson2019}, and the frequency limits are determined by the orbital evolution over the observation time, $T_{\rm{obs}}=4\,\rm{yr}$.
+The characteristic strain for circular orbits is
+\begin{equation}
+    h_{c}^2 = \frac{2^{2/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}},
+\end{equation}
+\noindent where $\mathcal{M}_c = (M_1M_2)^{3/5}/(M_1 + M_2)^{1/5}$ is the system's chirp mass, and $D_L$ is the systems luminosity distance which we assume to be the distance of each simulated DWD to the Sun.
+
+For stationary sources, the SNR is modified due to the lack of observable orbital evolution as
 \begin{equation}
@@
 \end{equation}
-with the observation time $T_{\text{obs}}$. Here, $h_2$ is strain 
-amplitude of the source for the second orbital frequency harmonic,
-\begin{equation}
-   h_2^2 = \frac{2^{22/3}}{5}\frac{(G\mathcal{M}_c)^{10/3}}{c^8D_L^2}(\pi 
-f_\text{orb})^{4/3}
+with the observation time $T_{\text{obs}}$. Here, $h_2$ is strain amplitude of the source for the second orbital frequency harmonic,
+\begin{equation}
+   h_2^2 = \frac{2^{22/3}}{5}\frac{(G\mathcal{M}_c)^{10/3}}{c^8D_L^2}(\pi f_\text{orb})^{4/3}
 \end{equation}
@@
 
-The amplitude spectral density for a stationary system is finally defined 
-as $ASD = h_{2} \sqrt{T_\text{obs}}$, such that the SNR for stationary 
-source is simply, $\rho \sim ASD/S_n$.
-
-The Galactic foreground included in the \citet{Robson2019} LISA noise 
-curve was generated using a different binary evolution code and set of 
-model assumptions for DWD formation and evolution \citep{Toonen2012, 
-Korol2017}. Thus, we use the detector curve only and generate an 
-approximate foreground from each of our populations as follows. Instead of 
-performing a full source subtraction algorithm 
-\citep[e.g.][]{Littenberg2020}, which is out of the scope of this work, we 
-calculate the PSD of the Galactic DWD population with a frequency 
-resolution set by the LISA mission time as 
-$1/T_{\rm{obs}}\sim1/4\,\rm{yr}^{-1}\sim8\times10^{-9}\,\rm{Hz}$. We then 
-approximate the foreground as the running median of the PSD with a boxcar 
-window with a width of $10^3$ frequency bins similar to 
-\citet{Benacquista2006}. The Galactic DWD PSD is truncated near 
-$10\,\rm{mHz}$ for both of our models because we remove all DWDs which 
-experience Roche-lobe overflow. In order to smooth the effect of this 
-truncation in our foreground, we fit each running median with fourth-order 
-polynomials for GW frequencies up to $1\,\rm{mHz}$, thus allowing an 
-approximation of the foreground PSD for higher frequencies. These fits are 
-listed in Table~\ref{tbl:fits} where the polynomial is described as
+The amplitude spectral density for a stationary system is finally defined as $ASD = h_{2} \sqrt{T_\text{obs}}$, such that the SNR for stationary source is simply, $\rho \sim ASD/S_n$.
+
+The Galactic foreground included in the \citet{Robson2019} LISA noise curve was generated using a different binary evolution code and set of model assumptions for DWD formation and evolution \citep{Toonen2012, Korol2017}.
+Thus, we use the detector curve only and generate an approximate foreground from each of our populations as follows.
+Instead of performing a full source subtraction algorithm \citep[e.g.][]{Littenberg2020}, which is out of the scope of this work, we calculate the PSD of the Galactic DWD population with a frequency resolution set by the LISA mission time as $1/T_{\rm{obs}}\sim1/4\,\rm{yr}^{-1}\sim8\times10^{-9}\,\rm{Hz}$.
+We then approximate the foreground as the running median of the PSD with a boxcar window with a width of $10^3$ frequency bins similar to \citet{Benacquista2006}.
+The Galactic DWD PSD is truncated near $10\,\rm{mHz}$ for both of our models because we remove all DWDs which experience Roche-lobe overflow.
+In order to smooth the effect of this truncation in our foreground, we fit each running median with fourth-order polynomials for GW frequencies up to $1\,\rm{mHz}$, thus allowing an approximation of the foreground PSD for higher frequencies.
+These fits are listed in Table~\ref{tbl:fits} where the polynomial is described as
 \begin{equation}
 \label{eq:fit}
-    \log_{10}(\rm{confusion\ fit}/\rm{Hz}) = a\,x^4 + b\,x^3 + c\,x^2 + 
-d\,x + e
-\end{equation}
-\noindent and $\rm{x}=\log_{10}(f_{\rm{GW}}/\rm{Hz})$. We add the fitted 
-polynomial of the PSD's running median to the LISA noise PSD to obtain a 
-sensitivity curve for each model and variation.
+    \log_{10}(\rm{confusion\ fit}/\rm{Hz}) = a\,x^4 + b\,x^3 + c\,x^2 + d\,x + e
+\end{equation}
+\noindent and $\rm{x}=\log_{10}(f_{\rm{GW}}/\rm{Hz})$. We add the fitted polynomial of the PSD's running median to the LISA noise PSD to obtain a sensitivity curve for each model and variation.
 
@@
     \end{tabular}
-    \caption{Polynomial fitting coefficients for the confusion foreground 
-fit of Equation~\ref{eq:fit} for each binary fraction model and parameter 
-variation.}
+    \caption{Polynomial fitting coefficients for the confusion foreground fit of Equation~\ref{eq:fit} for each binary fraction model and parameter variation.}
     \label{tbl:fits}
@@
 
-\section{Metallicity effects on the formation and evolution of 
-DWDs}\label{sec:results}
+\section{Metallicity effects on the formation and evolution of DWDs}\label{sec:results}
 
 \subsection{DWD types and their formation channels}\label{sec:ini}
-As discussed in Section\,\ref{sec:bin_pop}, we consider four DWD 
-sub-types, which each contribute differently to LISA's GW signals: He + 
-He, CO + He, CO + CO, and ONe + X. Each sub-type has a unique distribution 
-in their formation times, initial masses, radii, and orbital periods 
-stemming from variations in their evolution channels and their formation 
-efficiency. Here we describe the general formation scenarios and 
-population properties of Galactic close DWDs which may be observable by 
-LISA.
-
-He WDs are unable to form through single star evolution within the 
-lifetime of the Milky Way. Instead, they originate through interactions in 
-close binary systems or binaries with large eccentricities. Because of 
-this, He WDs are able to form with low component masses on order $\sim 
-0.1\,M_\odot$, with the majority of He WDs in our simulations having 
-masses between 0.2-0.5 $M_\odot$. He + He DWDs form through evolution of 
-close binary systems, during which their envelopes are both stripped 
-through RLO and CE phase interactions before Helium ignition occurs. The 
-two progenitor stars generally have masses $\lesssim 3\,M_\odot$ which is 
-lower than the progenitors of other DWD types. Our simulated He + He DWDs 
-have an approximately constant distribution of formation times $\gtrsim 
-2.5\,\rm{Gyr}$. Lastly, since the ZAMS separations are skewed towards 
-shorter values, we also see that the resulting DWD separations are smaller 
-on average than that of other DWD types.
+As discussed in Section\,\ref{sec:bin_pop}, we consider four DWD sub-types, which each contribute differently to LISA's GW signals: He + He, CO + He, CO + CO, and ONe + X.
+Each sub-type has a unique distribution in their formation times, initial masses, radii, and orbital periods stemming from variations in their evolution channels and their formation efficiency.
+Here we describe the general formation scenarios and population properties of Galactic close DWDs which may be observable by LISA.
+
+He WDs are unable to form through single star evolution within the lifetime of the Milky Way.
+Instead, they originate through interactions in close binary systems or binaries with large eccentricities.
+Because of this, He WDs are able to form with low component masses on order $\sim 0.1\,M_\odot$, with the majority of He WDs in our simulations having masses between 0.2-0.5 $M_\odot$.
+He + He DWDs form through evolution of close binary systems, during which their envelopes are both stripped through RLO and CE phase interactions before Helium ignition occurs.
+The two progenitor stars generally have masses $\lesssim 3\,M_\odot$ which is lower than the progenitors of other DWD types.
+Our simulated He + He DWDs have an approximately constant distribution of formation times $\gtrsim 2.5\,\rm{Gyr}$.
+Lastly, since the ZAMS separations are skewed towards shorter values, we also see that the resulting DWD separations are smaller on average than that of other DWD types.
 
@@
 	\includegraphics[width=\textwidth]{figures/form_eff.pdf}
-    \caption{The DWD formation efficiency vs metallicity of DWD 
-populations simulated with \cosmic. Each panel shows the formation 
-efficiency for a given DWD type and variation. The solid lines indicate 
-the formation efficiency for model FZ which incorporates a 
-metallicity-dependent binary fraction. The dashed lines indicate the 
-formation efficiency for model F50, which assumes a constant binary 
-fraction of $50\%$. The DWD formation efficiency drops by a factor of 
-$4$--$5$ for model FZ and a factor of $1$--$5$ for model F50. See 
-Section~\ref{sec:formeff} for a careful description of the trends for each 
-DWD type.}
+    \caption{The DWD formation efficiency vs metallicity of DWD populations simulated with \cosmic.
+Each panel shows the formation efficiency for a given DWD type and variation.
+The solid lines indicate the formation efficiency for model FZ which incorporates a metallicity-dependent binary fraction.
+The dashed lines indicate the formation efficiency for model F50, which assumes a constant binary fraction of $50\%$.
+The DWD formation efficiency drops by a factor of $4$--$5$ for model FZ and a factor of $1$--$5$ for model F50.
+See Section~\ref{sec:formeff} for a careful description of the trends for each DWD type.}
     \label{fig:form_eff}
@@
 
-A CO WD forms when a star is able to begin the helium burning process 
-before its envelope is stripped. Thus to form a CO + He DWD, RLO and CE 
-stages occur after one component experiences core helium burning, but 
-before the other component can. Most close CO + He DWDs form in 
-approximately 2 Gyr after ZAMS and with very short periods because the He 
-WD is formed through the ejection of a common envelope which greatly 
-reduces the orbital separation. Because of these short formation 
-separations, many CO + He DWDs merge before the present day. Due to their 
-asymmetric mass distributions, they have lower chirp masses, but their 
-shorter periods make them important candidates for LISA detection.
-
-To prevent the two stars' envelopes from being stripped before helium 
-ignition, CO + CO DWDs typically form from progenitors in wider orbits, 
-and the two components may have little to no interaction during their 
-evolution from ZAMS to DWD. CO DWDs thus have a distribution in progenitor 
-separation that extends to larger values than for other DWD types. Most CO 
-+ CO DWDs need $> 0.3$ Gyr to form, have component WD masses between 
-$0.35$--$1.0\,M_\odot$, and make up the majority of the DWD population.
-
-ONe WDs are rare and typically form from massive progenitor stars which 
-evolve through the asymptotic giant branch phase, thus resulting in a 
-higher mass WD. All ONe WDs in our \cosmic\ populations, e.g., have 
-progenitor ZAMS masses above $4\,M_\odot$, and the resulting ONe WDs have 
-a relatively flat distribution of masses from $1.05\,M_\odot$ up to the 
-Chandrasekkhar limit of $1.4\,M_\odot$. Because an ONe WD can have a 
-companion of any other WD type in our study, there is a spread in their 
-distributions for separation, secondary mass, final orbital period, and 
-formation time. In general, however, these systems result from wider 
-separations to allow for the evolution of the ONe component without 
-merging. For example, all initial separations in our \cosmic \ populations 
-have separations $\gtrsim 1.5\,R_\odot$. ONe + X DWDs can form on short 
-timescales, as low as $30\,\rm{Myr}$, for the majority of high-metallicity 
-systems.
-
-\subsection{Metallicity-dependent trends in the formation efficiency of 
-DWDs}\label{sec:formeff}
-The number of DWDs formed per unit solar mass of ZAMS star formation, or 
-DWD formation efficiency $\eta_{\rm{form}}(Z)$, varies with metallicity. 
-Consequently, a metallicity-dependent binary fraction further impacts the 
-efficiency of DWD formation within the Galaxy. Figure \ref{fig:form_eff} 
-shows the DWD formation efficiency as a function of metallicity for each 
-DWD type, binary fraction model, and binary evolution parameter variation. 
-In general, the formation efficiency decreases with increasing 
-metallicity. This effect is exaggerated for model FZ which assumes a close 
-binary fraction which also decreases with increasing metallicity. In 
-\textbf{this section}, we \textbf{give a brief overview of the general 
-trends observed in formation efficiency and their underlying causes. For a 
-detailed description for each DWD type and binary evolution parameter 
-variation, see Appendix \ref{appendix:form_eff}.}
-
-\textbf{There are two common ways that the formation of DWDs from stellar 
-progenitors is inhibited. The first is through stellar mergers, where the 
-binary merges before both components become WDs. The second is due to 
-evolutionary outcomes like forming a different DWD type, or not forming a 
-DWD by the present day. For all DWD types except ONe + X, which has other 
-dominating affects hindering formation efficiency like 
-metallicity-dependent stellar winds, we find that different regimes of 
-ZAMS orbital period leads to different specific evolutionary channels.}
-
-\textbf{In our \cosmic\ models, lower-metallicity stars evolve faster than 
-high-metallicity stars and have larger radii near the end of the MS. This 
-changes the timescales of RLO: low-metallicity stars tend to fill their 
-Roche lobes while still on the MS, meaning mass transfer can remain stable 
-which serves to widen the binary. In contrast, high-metallicity systems 
-initiate mass transfer after the donor has left the main sequence, so the 
-binary is more likely to enter a CE phase. Moreover, high-metallicity 
-progenitors tend to have deeper convective envelopes such that a larger 
-fraction of their mass is contained in the envelope relative to 
-lower-metallicity counterparts of the same mass \citep{Amard2019, 
-Amard2020}. When these systems enter a CE phase, it thus requires more 
-orbital energy to eject the CE than for a low-metallicity star at the same 
-point in its evolution, causing a large amount of orbital shrinking. These 
-effects often leads to a stellar merger at higher metallicities for a 
-system that would have survived the CE phase at a lower metallicity, thus 
-causing a decrease in formation efficiency with metallicity.}
-
-The skews introduced by the metallicity-dependent ZAMS orbital period 
-distribution and binary fraction of FZ also contribute to the formation 
-efficiency trends. The log-normal metallicity-dependent $P_{\rm{orb}}$ 
-distribution increasingly skews towards orbital periods below 10$^4$ days 
-for decreasing metallicity. This amplifies the effects of 
-metallicity-dependent stellar evolution discussed above. For example, the 
-skew induces more mergers at high metallicities where the deeper 
-convective envelope leads to increased orbital shrinkage. However, it is 
-also of note that the log-uniform orbital period distribution of F50 
-produces a higher number of the shortest-orbital period systems (below 
-$\sim100$ days) than FZ, since the tails of the FZ distribution fall 
-quickly below this threshold. These systems also have a propensity for 
-merging before the formation of a DWD.
-
-\textbf{Our binary evolution parameter variations emphasizes the interplay 
-of the aforementioned effects of the distributions of F50 and FZ with the 
-physics of binary evolution. For example, the lower CE efficiency of 
-variation $\alpha25$ is the dominating formation efficiency inhibitor 
-since it induces a higher merger rate. In contrast, variations $\alpha5$ 
-and $q3$ relax hindrances to DWD formation (through an increased ability 
-to survive a CE phase and undergo stable mass transfer respectively). We 
-thus find less mergers overall in both cases, and that the effect of the 
-metallicity-dependent $P_{\rm{orb}}$ distribution dominates the formation 
-efficiency trends rather than restrictions imposed by binary evolution 
-prescriptions.
+A CO WD forms when a star is able to begin the helium burning process before its envelope is stripped.
+Thus to form a CO + He DWD, RLO and CE stages occur after one component experiences core helium burning, but before the other component can.
+Most close CO + He DWDs form in approximately 2 Gyr after ZAMS and with very short periods because the He WD is formed through the ejection of a common envelope which greatly reduces the orbital separation.
+Because of these short formation separations, many CO + He DWDs merge before the present day.
+Due to their asymmetric mass distributions, they have lower chirp masses, but their shorter periods make them important candidates for LISA detection.
+
+To prevent the two stars' envelopes from being stripped before helium ignition, CO + CO DWDs typically form from progenitors in wider orbits, and the two components may have little to no interaction during their evolution from ZAMS to DWD.
+CO DWDs thus have a distribution in progenitor separation that extends to larger values than for other DWD types.
+Most CO + CO DWDs need $> 0.3$ Gyr to form, have component WD masses between $0.35$--$1.0\,M_\odot$, and make up the majority of the DWD population.
+
+ONe WDs are rare and typically form from massive progenitor stars which evolve through the asymptotic giant branch phase, thus resulting in a higher-mass WD.
+All ONe WDs in our \cosmic\ populations, e.g., have progenitor ZAMS masses above $4\,M_\odot$, and the resulting ONe WDs have a relatively flat distribution of masses from $1.05\,M_\odot$ up to the Chandrasekkhar limit of $1.4\,M_\odot$.
+Because an ONe WD can have a companion of any other WD type in our study, there is a spread in their distributions for separation, secondary mass, final orbital period, and formation time.
+In general, however, these systems result from wider separations to allow for the evolution of the ONe component without merging.
+For example, all initial separations in our \cosmic \ populations have separations $\gtrsim 1.5\,R_\odot$.
+ONe + X DWDs can form on short timescales, as low as $30\,\rm{Myr}$, for the majority of high-metallicity systems.
+
+\subsection{Metallicity-dependent trends in the formation efficiency of DWDs}\label{sec:formeff}
+The number of DWDs formed per unit solar mass of ZAMS star formation, or DWD formation efficiency $\eta_{\rm{form}}(Z)$, varies with metallicity.
+Consequently, a metallicity-dependent binary fraction further impacts the efficiency of DWD formation within the Galaxy.
+Figure \ref{fig:form_eff} shows the DWD formation efficiency as a function of metallicity for each DWD type, binary fraction model, and binary evolution parameter variation.
+In general, the formation efficiency decreases with increasing metallicity.
+This effect is exaggerated for model FZ which assumes a close binary fraction which also decreases with increasing metallicity.
+In \textbf{this section}, we \textbf{give a brief overview of the general trends observed in formation efficiency and their underlying causes.
+For a detailed description for each DWD type and binary evolution parameter variation, see Appendix \ref{appendix:form_eff}.}
+
+\textbf{There are two common ways that the formation of DWDs from stellar progenitors is inhibited.
+The first is through stellar mergers, where the binary merges before both components become WDs.
+The second is due to evolutionary outcomes like forming a different DWD type, or not forming a DWD by the present day.
+For all DWD types except ONe + X, which has other dominating \textbf{effects} hindering formation efficiency like metallicity-dependent stellar winds, we find that different regimes of ZAMS orbital period leads to different specific evolutionary channels.}
+
+\textbf{In our \cosmic\ models, lower-metallicity stars evolve faster than high-metallicity stars and have larger radii near the end of the MS.
+This changes the timescales of RLO: low-metallicity stars tend to fill their Roche lobes while still on the MS, meaning mass transfer can remain stable which serves to widen the binary.
+In contrast, high-metallicity systems initiate mass transfer after the donor has left the main sequence, so the binary is more likely to enter a CE phase.
+Moreover, high-metallicity progenitors tend to have deeper convective envelopes such that a larger fraction of their mass is contained in the envelope relative to lower-metallicity counterparts of the same mass \citep{Amard2019, Amard2020}.
+When these systems enter a CE phase, it thus requires more orbital energy to eject the CE than for a low-metallicity star at the same point in its evolution, causing a large amount of orbital shrinking.
+These effects often leads{\sout{s}} to a stellar merger at higher metallicities for a system that would have survived the CE phase at a lower metallicity, thus causing a decrease in formation efficiency with metallicity.}
+
+The skews introduced by the metallicity-dependent ZAMS orbital period distribution and binary fraction of FZ also contribute to the formation efficiency trends.
+The log-normal metallicity-dependent $P_{\rm{orb}}$ distribution increasingly skews towards orbital periods below 10$^4$ days for decreasing metallicity.
+This amplifies the effects of metallicity-dependent stellar evolution discussed above.
+For example, the skew induces more mergers at high metallicities where the deeper convective envelope leads to increased orbital shrinkage.
+However, it is also of note that the log-uniform orbital period distribution of F50 produces a higher number of the shortest-orbital period systems (below $\sim100$ days) than FZ, since the tail of the FZ distribution falls quickly below this threshold.
+These systems also have a propensity for merging before the formation of a DWD.
+
+\textbf{Our binary evolution parameter variations emphasizes the interplay of the aforementioned effects of the distributions of F50 and FZ with the physics of binary evolution.
+For example, the lower CE efficiency of variation $\alpha25$ is the dominating formation efficiency inhibitor since it induces a higher merger rate.
+In contrast, variations $\alpha5$ and $q3$ relax hindrances to DWD formation (through an increased ability to survive a CE phase and undergo stable mass transfer respectively).
+We thus find less mergers overall in both cases, and that the effect of the metallicity-dependent $P_{\rm{orb}}$ distribution dominates the formation efficiency trends rather than restrictions imposed by binary evolution prescriptions.
 }
@@
 	\includegraphics[width=\textwidth]{figures/CEsep.pdf}
-    \caption{Average interaction separation, 
-$\overline{\mathrm{a}}_{\rm{CE}}$ of progenitors of close DWDs across 
-metallicity for each DWD type and variation from model F50. Solid lines 
-show the average separation at the first RLO for binaries in each 
-metallicity bin. The shaded regions show the $1\sigma$ spread around the 
-mean within each metallicity bin. The average interaction separation 
-increases with metallicity for every DWD type, except for $\alpha5$ which 
-remains approximately constant for CO + He and ONe + X. The positive trend 
-in the average interaction separation is a direct consequence of larger 
-envelope masses of higher-metallicity donors which are less evolved than 
-their lower-metallicity counterparts. The sharp drop of the CO + CO 
-average at the highest-metallicity bin of the fiducial variation is due to 
-binning effects of the figure: it only contains 506 systems, of which the 
-majority stem from a single low-separation system which was sampled 468 
-times times during the simulation. The regions of metallicity where there 
-is not shading beyond the mean trend are also due to low numbers of DWDs 
-in each bin.} 
+    \caption{Average interaction separation, $\overline{\mathrm{a}}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type and variation from model F50.
+Solid lines show the average separation at the first RLO for binaries in each metallicity bin.
+The shaded regions show the $1\sigma$ spread around the mean within each metallicity bin.
+The average interaction separation increases with metallicity for every DWD type, except for $\alpha5$ which remains approximately constant for CO + He and ONe + X.
+The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts.
+The sharp drop of the CO + CO average at the highest-metallicity bin of the fiducial variation is due to binning effects of the figure: it only contains 506 systems, of which the majority stem from a single low-separation system which was sampled 468 times times during the simulation.
+The regions of metallicity where there is not shading beyond the mean trend are also due to low numbers of DWDs in each bin.}
     \label{fig:CEsep}
@@
 
-\subsection{Metallicity trends in DWD progenitor common envelope 
-separation}\label{sec:CEsep}
+\subsection{Metallicity trends in DWD progenitor common envelope separation}\label{sec:CEsep}
 
@@
 	\includegraphics[width=\textwidth]{figures/lisa_nums.pdf}
-    \caption{The number of LISA-band systems formed for each DWD type and 
-parameter variation as a function of the base-10 logarithm of metallicity, 
-normalized to solar value. The solid line shows the FZ population with a 
-metallicity-dependent close binary fraction incorporated, and the dashed 
-line shows the F50 population for a standard binary fraction of 0.5. The 
-LISA population of DWDs is dominated by stars with super-solar 
-metallicities. This is true even for model FZ, which drops off 
-significantly for higher metallicities, because of the large number of 
-stars formed in \textbf{m12i} beyond $Z\simeq Z_\odot$. There is a double 
-peak in the fiducial and $\alpha25$ He + He populations; the first peak is 
-caused by the sharp drop in formation efficiency past 
-$Z\simeq0.1\,Z_\odot$ which is then greatly overcompensated for by the 
-amount of star formation at higher metallicities which forms the second 
-peak.}
+    \caption{The number of LISA-band systems formed for each DWD type and parameter variation as a function of the base-10 logarithm of metallicity, normalized to solar value.
+The solid line shows the FZ population with a metallicity-dependent close binary fraction incorporated, and the dashed line shows the F50 population for a standard binary fraction of 0.5.
+The LISA population of DWDs is dominated by stars with super-solar metallicities.
+This is true even for model FZ, which drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond $Z\simeq Z_\odot$.
+There is a double peak in the fiducial and $\alpha25$ He + He populations; the first peak is caused by the sharp drop in formation efficiency past $Z\simeq0.1\,Z_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
     \label{fig:lisa_nums}
@@
 
-All systems that end up radiating GWs in the LISA band have undergone at 
-least one phase of CE evolution. For systems which experience a stable RLO 
-mass transfer in the first interaction, the CE phase plays a key role in 
-shrinking systems with initially wide separations to bring them into the 
-LISA band.
-
-Figure \ref{fig:CEsep} shows the average separation at the first instance 
-of CE evolution, $a_{\text{CE}}$ of all DWD progenitors that result in 
-systems orbiting in the LISA frequency band at present day, as a function 
-of metallicity for each DWD type. The solid lines denote the average 
-value, and the $1\sigma$ variance is shown in the surrounding shading. We 
-show this for our fiducial variation and each of our binary parameter 
-variations. For our fiducial, $\alpha25$ and $\alpha5$ parameter 
-variations, the average CE separation increases in general across 
-metallicity. Higher-metallicity binaries will interact earlier in the 
-binary's lifetime than a lower-metallicity binary of equal separation due 
-to their relatively larger maximum radii. Since higher-metallicity 
-binaries are also more likely to merge during CE interactions because of 
-their relatively more massive donor envelopes, the DWDs which survive and 
-eventually orbit in the LISA band originate from systems with higher 
-interaction separations which allow their orbits to shrink significantly 
-during CE phases without merging. This regulation plays a key role in 
-smearing out any observable effects of a metallicity-dependent binary 
-fraction in the population of DWDs observable by LISA.
-
-The slope of the increase for these three models is dictated by the CE 
-efficiency $\alpha$. \textbf{As discussed in Section \ref{sec:formeff}, 
-with} increasing metallicity there is a deepening of the convective 
-envelope of the star \textbf{compared to its lower metallicity 
-counterpart}, requiring more orbital energy to be available in order to 
-eject the CE. Thus the high-metallicity binaries must have even wider 
-separations for lower $\alpha$ values to ensure the binary does not merge 
-before the envelope is ejected. We therefore see a steeper separation 
-slope for $\alpha25$, a less steep slope for $\alpha5$, and an 
-intermediate slope for our fiducial variation which has $\alpha=1$.
-
-The DWDs in model $q3$ that survive into the LISA band at present day have 
-different formation channels than those of our other three parameter 
-variations. Most importantly, in contrast to two CE phases for the 
-fiducial, $\alpha25$ and $\alpha5$ parameter variations, the DWD 
-progenitors in parameter variation $q3$ typically undergo a phase of 
-stable mass transfer as the binary's first interaction. During mass 
-transfer the orbit first shrinks, and then will slightly widen once the 
-binary's mass ratio flips. This process leads to formation of the first WD 
-component. The companion is then formed later in the binary's evolution 
-through a CE phase. We show the CE phase which results from the second 
-interaction for parameter variation $q3$ in Figure \ref{fig:CEsep}.
-
-Of particular interest in variation $q3$ is the CO + He systems. For all 
-of the $q3$ CO + He binaries that reside in the LISA band at present, the 
-He WD unexpectedly forms first through stable mass transfer, with the CO 
-WD forming second through a CE. These binaries tend to all have similar 
-resulting orbital separations from mass transfer, as can be seen by the 
-relatively constant curve for CO + He separation at CE onset. There is 
-still a slight increasing trend in CO + He (as well as CO + CO and a more 
-pronounced trend in He + He) for $q3$ that stems from the 
-metallicity-dependent convective envelope discussion above. We also see 
-that the average interaction separation are overall lower for variations 
-$q3$ and $\alpha5$ than for the other two due to the orbital shrinkage 
-that has already occurred from stable mass transfer and the efficient CE 
-phase that will lead to minimal orbital shrinkage respectively.
+All systems that end up radiating GWs in the LISA band have undergone at least one phase of CE evolution.
+For systems which experience a stable RLO mass transfer in the first interaction, the CE phase plays a key role in shrinking systems with initially wide separations to bring them into the LISA band.
+
+Figure \ref{fig:CEsep} shows the average separation at the first instance of CE evolution, $\overline{\mathrm{a}}_{\rm{CE}}$, of all DWD progenitors that result in systems orbiting in the LISA frequency band at present day, as a function of metallicity for each DWD type.
+The solid lines denote the average value, and the $1\sigma$ variance is shown in the surrounding shading.
+We show this for our fiducial variation and each of our binary parameter variations.
+For our fiducial, $\alpha25$ and $\alpha5$ parameter variations, the average CE separation increases in general across metallicity.
+Higher-metallicity binaries will interact earlier in the binary's lifetime than a lower-metallicity binary of equal separation due to their relatively larger maximum radii.
+Since higher-metallicity binaries are also more likely to merge during CE interactions because of their relatively more massive donor envelopes, the DWDs which survive and eventually orbit in the LISA band originate from systems with higher interaction separations which allow their orbits to shrink significantly during CE phases without merging.
+This regulation plays a key role in smearing out any observable effects of a metallicity-dependent binary fraction in the population of DWDs observable by LISA.
+
+The slope of the increase for these three models is dictated by the CE efficiency $\alpha$.
+\textbf{As discussed in Section \ref{sec:formeff}, with} increasing metallicity there is a deepening of the convective envelope of the star \textbf{compared to its lower metallicity counterpart}, requiring more orbital energy to be available in order to eject the CE.
+Thus the high-metallicity binaries must have even wider separations for lower $\alpha$ values to ensure the binary does not merge before the envelope is ejected.
+We therefore see a steeper separation slope for $\alpha25$, a less steep slope for $\alpha5$, and an intermediate slope for our fiducial variation which has $\alpha=1$.
+
+The DWDs in model $q3$ that survive into the LISA band at present day have different formation channels than those of our other three parameter variations.
+Most importantly, in contrast to two CE phases for the fiducial, $\alpha25$ and $\alpha5$ parameter variations, the DWD progenitors in parameter variation $q3$ typically undergo a phase of stable mass transfer as the binary's first interaction.
+During mass transfer the orbit first shrinks, and then will slightly widen once the binary's mass ratio flips.
+This process leads to formation of the first WD component.
+The companion is then formed later in the binary's evolution through a CE phase.
+We show the CE phase which results from the second interaction for parameter variation $q3$ in Figure \ref{fig:CEsep}.
+
+Of particular interest in variation $q3$ is the CO + He systems.
+For all of the $q3$ CO + He binaries that reside in the LISA band at present, the He WD unexpectedly forms first through stable mass transfer, with the CO WD forming second through a CE.
+These binaries tend to all have similar resulting orbital separations from mass transfer, as can be seen by the relatively constant curve for CO + He separation at CE onset.
+There is still a slight increasing trend in CO + He (as well as CO + CO and a more pronounced trend in He + He) for $q3$ that stems from the metallicity-dependent convective envelope discussion above.
+We also see that the average interaction separation are overall lower for variations $q3$ and $\alpha5$ than for the other two due to the orbital shrinkage that has already occurred from stable mass transfer and the efficient CE phase that will lead to minimal orbital shrinkage respectively.
 
@@
 
-While metallicity impacts the intrinsic properties of our simulated DWD 
-populations as described in Sections~\ref{sec:formeff} and 
-\ref{sec:CEsep}, when we consider the present-day Galactic close DWDs we 
-find that the population detectable by LISA largely only changes 
-\textbf{in total number, but not in frequency distribution}. The number of 
-DWDs in the LISA frequency band decreases by $\sim50\%$ when comparing 
-model F50 to model FZ for variations $\alpha5$ and $q3$, but remains 
-approximately unchanged for our fiducial and $\alpha25$ variations.
+While metallicity impacts the intrinsic properties of our simulated DWD populations as described in Sections~\ref{sec:formeff} and \ref{sec:CEsep}, when we consider the present-day Galactic close DWDs we find that the population detectable by LISA largely only changes \textbf{in total number, but not in frequency distribution}.
+The number of DWDs in the LISA frequency band decreases by $\sim50\%$ when comparing model F50 to model FZ for variations $\alpha5$ and $q3$, but remains approximately unchanged for our fiducial and $\alpha25$ variations.
 
@@
 	\includegraphics[width=\textwidth]{figures/PSD.pdf}
-    \caption{The PSD of the entire Galactic DWD GW foreground, summed over 
-all metallicities and DWD types vs GW frequency for models FZ and F50, 
-where the PSD is downsampled by a factor of $10$ for plotting purposes. 
-Each panel shows a different parameter variation. The vertical lines show 
-the PSD where model F50 is shown in dark blue and model FZ is shown in 
-light blue. The dashed lines show fits to the rolling boxcar median of 
-width 1000 bins for each PSD (see Section \ref{sec:LISA_obs} for a 
-discussion). A metallicity-dependent binary fraction (model FZ) yields 
-fewer DWDs across all frequencies than a $50\%$ binary fraction (model 
-F50) by roughly a factor of $2$ for the $\alpha5$ and $q3$ parameter 
-variations. This produces a lower GW confusion foreground for frequencies 
-with f$_{\rm{GW}}\leq\sim10^{-3}$ Hz. In contrast, the fiducial and 
-$\alpha25$ parameter variations show very similar confusion foregrounds.}
+    \caption{The PSD of the entire Galactic DWD GW foreground, summed over all metallicities and DWD types vs GW frequency for models FZ and F50, where the PSD is downsampled by a factor of $10$ for plotting purposes.
+Each panel shows a different parameter variation.
+The vertical lines show the PSD where model F50 is shown in dark blue and model FZ is shown in light blue.
+The dashed lines show fits to the rolling boxcar median of width 1000 bins for each PSD (see Section \ref{sec:LISA_obs} for a discussion).
+A metallicity-dependent binary fraction (model FZ) yields fewer DWDs across all frequencies than a $50\%$ binary fraction (model F50) by roughly a factor of $2$ for the $\alpha5$ and $q3$ parameter variations.
+This produces a lower GW confusion foreground for frequencies with f$_{\rm{GW}}\leq\sim10^{-3}$ Hz.
+In contrast, the fiducial and $\alpha25$ parameter variations show very similar confusion foregrounds.}
     \label{fig:PSD}
@@
 	\includegraphics[width=\textwidth]{figures/LISA_SNR_fiducial.pdf}
-    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for 
-each DWD type where the top row shows the population from model F50 and 
-the bottom row shows the population from model FZ for the fiducial 
-variation. In each panel, the LISA sensitivity curve, including the 
-confusion foreground for each model, is shown in black and the total 
-population for each model is shown in grey. We find that each model 
-qualitatively exhibits similar characteristics and that the only change is 
-in the yield of resolved DWDs for each type based on the strength of the 
-confusion foreground.}
+    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for each DWD type where the top row shows the population from model F50 and the bottom row shows the population from model FZ for the fiducial variation.
+In each panel, the LISA sensitivity curve, including the confusion foreground for each model, is shown in black and the total population for each model is shown in grey.
+We find that each model qualitatively exhibits similar characteristics and that the only change is in the yield of resolved DWDs for each type based on the strength of the confusion foreground.}
     \label{fig:LISA_SNR}
@@
 
-Figure \ref{fig:lisa_nums} shows the number of DWDs orbiting with 
-frequencies $f_{\rm{GW}} > 0.1\,\rm{mHz}$ against metallicity for each DWD 
-type and parameter variation. The solid lines show DWDs from model FZ, and 
-the dashed lines show DWDs from model F50. The He + CO, CO + CO, and ONe + 
-X populations each have strong peaks in the number of DWDs near solar 
-metallicity at which the majority of star formation in galaxy {\bf{m12i}} 
-occurs. The largest contribution to the population comes from 
-metallicities above $\sim 0.01\,Z_\odot$. Any discrepancy between the two 
-binary fraction models is also the most significant above this threshold. 
-When creating our DWD populations the DWD formation efficiency, number of 
-\textbf{m12i} star particles, and the metallicity-dependent binary 
-fraction and ZAMS orbital period distribution all compete. The amount of 
-stars formed in \textbf{m12i} at higher metallicity values overwhelms the 
-drop in DWD formation efficiency by multiple orders of magnitude, so this 
-effect dominates when determining the number of stars initially sampled in 
-the population for $f_{\rm{b}}$.
-
-There are two peaks in the distribution of He + He DWDs which are most 
-prominent in the fiducial and $\alpha25$ variations, and not as obvious 
-for $\alpha5$ or $q3$. The prominent first peak in fiducial and $\alpha25$ 
-occurs because near $Z\simeq 0.1\,Z_\odot$, the DWD formation efficiency 
-transitions from near constant values to a sharp decrease (see Figure 
-\ref{fig:form_eff}). However, for a drop in the formation efficiency by a 
-factor of of $\sim$ six, the amount of star formation in galaxy 
-\textbf{m12i} increases by more than an order of magnitude for supersolar 
-metallicities. Above $Z=Z_\odot$ this overcompensates for the efficiency 
-drop, producing the second peak. For $\alpha5$ and $q3$, the lack of 
-dramatic orbital shrinking -- from the increased CE efficiency in the 
-former and increased propensity for stable mass transfer in the latter -- 
-allow for less failed DWDs due to stellar mergers. This leads to less 
-dramatic drops in formation efficiency across metallicity which thus 
-suppresses the formation of two peaks in the number of LISA-band systems.
-
-The $\alpha5$ and $q3$ variations produce a higher number of F50 systems 
-than FZ when summed over all DWD types. This is due to the log-uniform 
-P$_{\rm{orb}}$ distribution of model F50 having more of the 
-shortest-period binaries than the tails of the log-normal distribution of 
-FZ; a discrepancy which becomes more significant with increasing 
-metallicity as the FZ distribution moves from a peak of 
-log$_{10}$($P_{\rm{orb}}\rm{/day})\simeq 3-4$ to 
-log$_{10}$($P_{\rm{orb}}\rm{/day})\simeq 4-6$. This tail is less likely to 
-survive to the LISA band at present for the fiducial and $\alpha25$ 
-variations due to the increased propensity for mergers of DWD progenitors. 
-This effect produces an equal number of systems between FZ and F50 for the 
-fiducial and $\alpha25$ variations. Although the close binary fraction 
-leads to a greater number of low-metallicity systems, this is compensated 
-for by the FIRE star particle metallicity distribution as well as the 
-tendency for the shortest-period DWD progenitors in model F50 to merge, 
-essentially washing out all differences between the populations.
+Figure \ref{fig:lisa_nums} shows the number of DWDs orbiting with frequencies $f_{\rm{GW}} > 0.1\,\rm{mHz}$ against metallicity for each DWD type and parameter variation.
+The solid lines show DWDs from model FZ, and the dashed lines show DWDs from model F50.
+The He + CO, CO + CO, and ONe + X populations each have strong peaks in the number of DWDs near solar metallicity at which the majority of star formation in galaxy {\bf{m12i}} occurs.
+The largest contribution to the population comes from metallicities above $\sim 0.01\,Z_\odot$.
+Any discrepancy between the two binary fraction models is also the most significant above this threshold.
+When creating our DWD populations the DWD formation efficiency, number of \textbf{m12i} star particles, and the metallicity-dependent binary fraction and ZAMS orbital period distribution all compete.
+The amount of stars formed in \textbf{m12i} at higher metallicity values overwhelms the drop in DWD formation efficiency by multiple orders of magnitude, so this effect dominates when determining the number of stars initially sampled in the population for $f_{\rm{b}}$.
+
+There are two peaks in the distribution of He + He DWDs which are most prominent in the fiducial and $\alpha25$ variations, and not as obvious for $\alpha5$ or $q3$.
+The prominent first peak in fiducial and $\alpha25$ occurs because near $Z\simeq 0.1\,Z_\odot$, the DWD formation efficiency transitions from near constant values to a sharp decrease (see Figure \ref{fig:form_eff}).
+However, for a drop in the formation efficiency by a factor of of $\sim$ six, the amount of star formation in galaxy \textbf{m12i} increases by more than an order of magnitude for supersolar metallicities.
+Above $Z=Z_\odot$ this overcompensates for the efficiency drop, producing the second peak.
+For $\alpha5$ and $q3$, the lack of dramatic orbital shrinking -- from the increased CE efficiency in the former and increased propensity for stable mass transfer in the latter -- allow for less failed DWDs due to stellar mergers.
+This leads to less dramatic drops in formation efficiency across metallicity which thus suppresses the formation of two peaks in the number of LISA-band systems.
+
+The $\alpha5$ and $q3$ variations produce a higher number of F50 systems than FZ when summed over all DWD types.
+This is due to the log-uniform P$_{\rm{orb}}$ distribution of model F50 having more of the shortest-period binaries than the tails of the log-normal distribution of FZ; a discrepancy which becomes more significant with increasing metallicity as the FZ distribution moves from a peak of log$_{10}$($P_{\rm{orb}}\rm{/day})\simeq 3-4$ to log$_{10}$($P_{\rm{orb}}\rm{/day})\simeq 4-6$.
+This tail is less likely to survive to the LISA band at present for the fiducial and $\alpha25$ variations due to the increased propensity for mergers of DWD progenitors.
+This effect produces an equal number of systems between FZ and F50 for the fiducial and $\alpha25$ variations.
+Although the close binary fraction leads to a greater number of low-metallicity systems, this is compensated for by the FIRE star particle metallicity distribution as well as the tendency for the shortest-period DWD progenitors in model F50 to merge, essentially washing out all differences between the populations.
 
 \begin{figure*}
-
 	\includegraphics[width=\textwidth]{figures/Mc_vs_dist_fiducial.pdf}
-    \caption{The chirp mass vs distance for each DWD type is shown for our 
-fiducial parameter variation. Only systems with observable evolution in 
-their GW frequency, i.e those which are chirping, and with SNR $>7$, are 
-shown, since these are systems for which distance can be separated from 
-chirp mass within their strain amplitude. Each panel shows one DWD type, 
-summed over all metallicities. Model FZ is indicated with solid light blue 
-contours, and model F50 is indicated with dark blue dashed contours 
-respectively. Contours are shown at the $5^{\rm{th}}$, 25$^{\rm{th}}$, 
-50$^{\rm{th}}$, 75$^{\rm{th}}$, and 95$^{\rm{th}}$ percentiles. Despite 
-intrinsic changes to population properties induced by a 
-metallicity-dependent binary fraction, and a reduction in the height of 
-the DWD Galactic foreground the distributions are very similar.}
+    \caption{The chirp mass vs distance for each DWD type is shown for our fiducial parameter variation.
+Only systems with observable evolution in their GW frequency, i.e those which are chirping, and with SNR $>7$, are shown, since these are systems for which distance can be separated from chirp mass within their strain amplitude.
+Each panel shows one DWD type, summed over all metallicities.
+Model FZ is indicated with solid light blue contours, and model F50 is indicated with dark blue dashed contours respectively.
+Contours are shown at the $5^{\rm{th}}$, 25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$, and 95$^{\rm{th}}$ percentiles.
+Despite intrinsic changes to population properties induced by a metallicity-dependent binary fraction, and a reduction in the height of the DWD Galactic foreground the distributions are very similar.}
     \label{fig:Mc_vs_dist}
@@
 
-A change in the number of DWDs in model FZ relative to model F50 is also 
-apparent in the GW PSD LISA will observe. We show the GW PSD of each 
-model, as well as the confusion forground estimate, in 
-Figure~\ref{fig:PSD}. We downsample the PSD frequencies by a factor of 10 
-for plotting purposes. While model F50 (dark blue) and model FZ (light 
-blue) produce several thousand large spikes in the PSD across LISA's 
-frequency band, the overall foreground height, including the confusion, is 
-larger for model F50 for parameter variations $\alpha5$ and $q3$. This is 
-a direct consequence of the overall reduction in the size of the close DWD 
-population in model FZ. The foreground height remains unchanged for the 
-fiducial and $\alpha25$ variations when comparing models FZ and F50.
-
-Similar to previous studies, we find that LISA will be able to resolve 
-several thousand DWDs. Figure \ref{fig:LISA_SNR} shows the amplitude 
-spectral density vs GW frequency of the resolved systems with SNR $> 7$ 
-for each DWD type, where the top and bottom rows show results for models 
-FZ and F50 respectively for the fiducial parameter variation. For 
-comparison, we also show the LISA sensitivity curve, including the 
-modeled confusion foreground from each population in black, and the the 
-entire population for each model in grey. Plots for our three parameter 
-variations can be found in Appendix \ref{appendix:ASD_vars}. Apart from 
-each DWD type having a different abundance of resolved systems, the 
-population-wide characteristics remain unchanged between the two binary 
-fraction models. The populations containing at least one He WD occupy the 
-lower-ASD, higher-GW frequency region of parameter space compared to the 
-total population, with CO + He DWDs having larger ASDs than the He + He 
-DWD population. Conversely, DWD types without a He WD component tend to 
-occupy the higher-ASD, lower-GW frequency region of parameter space. This 
-difference is largely due to the formation scenario of DWDs containing a 
-He WD, which form from the ejection of a common envelope created by the He 
-WD progenitor. These lower mass progenitors overflow their Roche lobes at 
-closer separations relative to the higher mass progenitors (e.g. 
-Figure~\ref{fig:CEsep}) and thus also produce closer DWDs. While the 
-distance to any one DWD strongly influences its ASD, DWD populations 
-without a He WD component have, on average, higher ASDs due to their more 
-massive WD components.
-
-We note that the height of the confusion foreground and the number of DWDs 
-radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor 
-of 2 for model FZ relative to model F50 for variations $\alpha5$ and $q3$, 
-the number of resolved sources is not reduced to an equal degree. This is 
-because in the absence of less competing GW signals from DWDs in the LISA 
-frequency band, more DWDs can be individually resolved. For the fiducial 
-and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ 
-are reduced by 4.5\% and increased by 3\% respectively. However, for 
-$\alpha5$ the number of resolvable DWDs is reduced by only 26\%, and the 
-number of resolvable DWDs $q3$ remains almost \emph{unchanged}, with a 1\% 
-reduction even though the overall LISA population of both variations is 
-halved. A large portion of the maintenance of the number of DWDs in 
-parameter variation $q3$ is contributed to by He + He binaries with higher 
-GW frequencies and lower ASDs which can now survive CE interactions due to 
-an initial phase of mass transfer (see discussion of this formation 
-channel in Section \ref{sec:CEsep}).
-
-The distance and chirp mass of DWDs which exhibit observable orbital 
-evolution due to the emission of GWs during the LISA mission can be 
-measured. This is because the chirp mass -- distance degeneracy in the 
-observed strain can be broken with the observed GW frequency evolution, or 
-chirp. Assuming a chirp resolution of $1/T_{\rm{obs}}^2 \sim 
-8\times10^{-9}\,\rm{Hz}^2$, we select the DWDs whose chirp masses and 
-distances can be measured. Figure \ref{fig:Mc_vs_dist} shows the chirp 
-mass vs the luminosity distance for each DWD type in this selected 
-population for the fiducial variation. The same figure for our other three 
-parameter variations is shown in Appendix \ref{appendix:Mc_dist_vars}. The 
-contours show the $5^{\rm{th}}$, $25^{\rm{th}}$, $50^{\rm{th}}$, 
-$75^{\rm{th}}$, and $95^{\rm{th}}$ percentiles for models FZ (light blue) 
-and F50 (dark blue, dashed). Despite the reduction in the height of the 
-confusion foreground when considering model FZ relative to F50, we find 
-that LISA is unable to differentiate between the chirp mass -- distance 
-distributions of the two models.
+A change in the number of DWDs in model FZ relative to model F50 is also apparent in the GW PSD LISA will observe.
+We show the GW PSD of each model, as well as the confusion forground estimate, in Figure~\ref{fig:PSD}.
+We downsample the PSD frequencies by a factor of 10 for plotting purposes.
+While model F50 (dark blue) and model FZ (light blue) produce several thousand large spikes in the PSD across LISA's frequency band, the overall foreground height, including the confusion, is larger for model F50 for parameter variations $\alpha5$ and $q3$.
+This is a direct consequence of the overall reduction in the size of the close DWD population in model FZ.
+The foreground height remains unchanged for the fiducial and $\alpha25$ variations when comparing models FZ and F50.
+
+Similar to previous studies, we find that LISA will be able to resolve several thousand DWDs.
+Figure \ref{fig:LISA_SNR} shows the amplitude spectral density vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the top and bottom rows show results for models FZ and F50 respectively for the fiducial parameter variation.
+For comparison, we also show the LISA sensitivity curve, including the
+modeled confusion foreground from each population in black, and the the entire population for each model in grey.
+Plots for our three parameter variations can be found in Appendix \ref{appendix:ASD_vars}.
+Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models.
+The populations containing at least one He WD occupy the lower-ASD, higher-GW frequency region of parameter space compared to the total population, with CO + He DWDs having larger ASDs than the He + He DWD population.
+Conversely, DWD types without a He WD component tend to occupy the higher-ASD, lower-GW frequency region of parameter space.
+This difference is largely due to the formation scenario of DWDs containing a He WD, which form from the ejection of a common envelope created by the He WD progenitor.
+These lower-mass progenitors overflow their Roche lobes at closer separations relative to the higher-mass progenitors (e.g.
+Figure~\ref{fig:CEsep}) and thus also produce closer DWDs.
+While the distance to any one DWD strongly influences its ASD, DWD populations without a He WD component have, on average, higher ASDs due to their more massive WD components.
+
+We \textbf{highlight} that the height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 2 for model FZ relative to model F50 for variations $\alpha5$ and $q3$, the number of resolved sources is not reduced to an equal degree.
+This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.
+For the fiducial and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ are reduced by 4.5\% and increased by 3\% respectively.
+However, for $\alpha5$ the number of resolvable DWDs is reduced by only 26\%, and the number of resolvable DWDs $q3$ remains almost \emph{unchanged}, with a 1\% reduction even though the overall LISA population of both variations is halved.
+A large portion of the maintenance of the number of DWDs in parameter variation $q3$ is contributed to by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).
+
+The distance and chirp mass of DWDs which exhibit observable orbital evolution due to the emission of GWs during the LISA mission can be measured.
+This is because the chirp mass -- distance degeneracy in the observed strain can be broken with the observed GW frequency evolution, or chirp.
+Assuming a chirp resolution of $1/T_{\rm{obs}}^2 \sim 8\times10^{-9}\,\rm{Hz}^2$, we select the DWDs whose chirp masses and distances can be measured.
+Figure \ref{fig:Mc_vs_dist} shows the chirp mass vs the luminosity distance for each DWD type in this selected population for the fiducial variation.
+The same figure for our other three parameter variations is shown in Appendix \ref{appendix:Mc_dist_vars}.
+The contours show the $5^{\rm{th}}$, $25^{\rm{th}}$, $50^{\rm{th}}$, $75^{\rm{th}}$, and $95^{\rm{th}}$ percentiles for models FZ (light blue) and F50 (dark blue, dashed).
+Despite the reduction in the height of the confusion foreground when considering model FZ relative to F50, we find that LISA is unable to differentiate between the chirp mass -- distance distributions of the two models.
 
@@
 	\includegraphics[width=0.45\textwidth]{figures/model_comp.pdf}
-    \caption{The top panel shows the Galactic DWD confusion fit vs GW 
-frequency for different binary evolution parameter variations (colors) 
-with model F50 shown in dashed lines and model FZ shown in solid lines. 
-The bottom panel shows the ratio of the number of DWDs orbiting in the 
-LISA frequency band for model FZ to model F50 vs to number of DWDs 
-orbiting in the LISA band for model F50 only. While both the height of the 
-confusion foreground and number of LISA DWDs changes for each variation, 
-the FZ models within each variation exhibit either very little change or a  
-near-constant reduction by a factor of two compared with the F50 models.}
+    \caption{The top panel shows the Galactic DWD confusion fit vs GW frequency for different binary evolution parameter variations (colors) with model F50 shown in dashed lines and model FZ shown in solid lines.
+The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for model FZ to model F50 vs to number of DWDs orbiting in the LISA band for model F50 only.
+While both the height of the confusion foreground and number of LISA DWDs changes for each variation, the FZ models within each variation exhibit either very little change or a  near-constant reduction by a factor of two compared with the F50 models.}
     \label{fig:model_comp}
@@
 
-In each parameter variation, changing the binary evolution assumptions 
-dramatically changes the formation and evolution of the DWD populations. 
-These changes lead to large shifts in the overall number of close DWDs in 
-our synthetic present-day Milky-Way-like galaxies. We find that the total 
-number of DWDs with $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$ increases for both 
-variations $q3$ and $\alpha5$. This is because there are fewer stellar 
-mergers which occur before the formation of a DWD, thus allowing more 
-systems to evolve due to GW emission and orbit in the LISA frequency band 
-at present. Conversely, for variation $\alpha25$, we find that the number 
-of DWDs orbiting with frequencies in the LISA band is drastically reduced. 
-This is because of the highly inefficient use of orbital energy to eject 
-the common envelope, thus producing more stellar mergers, or closer 
-binaries which are more prone to future mergers.
-
-Interestingly, when we compare the populations of each binary fraction 
-model for our variations, we find that the number of close DWDs remains 
-approximately unchanged for our fiducial set of assumptions and $\alpha25$ 
-variation, but is reduced by 50\% for variations $\alpha5$ and $q3$. This 
-is illustrated in Figure \ref{fig:model_comp}. The top panel shows the 
-confusion foreground fits for each binary evolution variation (different 
-colored lines) and for each binary fraction model where the solid lines 
-show FZ models and dotted lines show F50 models. The bottom panel shows 
-the ratio of the number of DWDs orbiting in the LISA frequency band for 
-the FZ models vs the F50 models for each variation. The number of DWDs in 
-the LISA band spans over two orders of magnitude, and the ratio of FZ to 
-F50, as well as the spectral shape of the confusion fit, is either 
-relatively unchanged or reduced by a factor of approximately two. This 
-suggests that assuming a metallicity-dependent binary fraction may change 
-the size of the Galactic close DWD population by a factor of $\sim$ two 
-and the strength of the Galactic DWD GW foreground for LISA depending on 
-the chosen binary evolution model.
+In each parameter variation, changing the binary evolution assumptions dramatically changes the formation and evolution of the DWD populations.
+These changes lead to large shifts in the overall number of close DWDs in our synthetic present-day Milky-Way-like galaxies.
+We find that the total number of DWDs with $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$ increases for both variations $q3$ and $\alpha5$ \textbf{with respect to the fiducial case}.
+This is because there are fewer stellar mergers which occur before the formation of a DWD, thus allowing more systems to evolve due to GW emission and orbit in the LISA frequency band at present.
+Conversely, for variation $\alpha25$, we find that the number of DWDs orbiting with frequencies in the LISA band is drastically reduced.
+This is because of the highly inefficient use of orbital energy to eject the common envelope, \textbf{which produces} more stellar mergers, or closer binaries which are more prone to future mergers.
+
+Interestingly, when we compare the populations of each binary fraction model for our variations, we find that the number of close DWDs remains approximately unchanged for our fiducial set of assumptions and $\alpha25$ variation, but is reduced by 50\% for variations $\alpha5$ and $q3$.
+This is illustrated in Figure \ref{fig:model_comp}.
+The top panel shows the confusion foreground fits for each binary evolution variation (different colored lines) and for each binary fraction model where the solid lines show FZ models and dotted lines show F50 models.
+The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for the FZ models vs the F50 models for each variation.
+The number of DWDs in the LISA band spans over two orders of magnitude, \textbf{but} the ratio of FZ to F50, as well as the spectral shape of the confusion fit, is either relatively unchanged or reduced by a factor of approximately two.
+This suggests that assuming a metallicity-dependent binary fraction may change the size of the Galactic close DWD population by a factor of $\sim$ two and the strength of the Galactic DWD GW foreground for LISA depending on the chosen binary evolution model.
 
 \section{Conclusions}\label{sec:conclusions}
-In this study, we have investigated the effects of assuming a 
-metallicity-dependent binary fraction on the formation and evolution of 
-the Galactic population of DWDs with a special focus on the implications 
-for LISA. Based on our synthetic Milky-Way-like galaxy catalogs of DWDs, 
-we find that applying a metallicity-dependent binary fraction changes the 
-formation efficiency and evolutionary history of DWD populations. However, 
-when considering the close DWD populations observable by LISA, we find 
-that the only distinguishing features between models which assume a 
-metallicity-dependent binary fraction (model FZ) and models which assume a 
-flat $50\%$ binary fraction (model F50) are the population sizes and the 
-strength of the Galactic DWD GW foreground. Models which assume a 
-metallicity-dependent binary fraction produce Galactic DWD populations 
-that were unchanged relative to the standard model assumptions. However, 
-our results are highly dependent on the chosen binary evolution model. We 
-extended our study to include three binary evolution parameter variations 
-to investigate the sensitivity of the DWD population changes in 
-assumptions for mass transfer stability and common envelope ejection 
-efficiencies. While our binary evolution parameter variations change the 
-size of the LISA-observable populations dramatically, the size of the 
-close Galactic DWD population and the height of the confusion foreground 
-for models which assume a metallicity-dependent binary fraction appears to 
-either remain unchanged \emph{or} be reduced by 50\%. This reduction 
-extends to the height of the confusion foreground in the LISA data stream. 
-These two results highlight the interplay between the dominating factors 
-which shape the LISA DWD population: the metallicity-dependent star 
-formation history of the \textbf{m12i} galaxy, the metallicity-dependent 
-close binary fraction which alters the ZAMS orbital period distribution, 
-and the impact of binary evolution assumptions on DWD formation. This 
-comparison emphasizes the sensitivity of the Galactic population of 
-LISA-detectable DWDs to the intricacies of binary evolution. Binary 
-evolution assumptions like CE efficiency are undergoing continuous study 
-in current literature and an exact value has yet to be identified. By 
-exploring a range of possibilities in this work, we capture the variation 
-in predictions of the LISA DWD population that may be observed.
-
-An important consequence of a lower Galactic DWD confusion foreground is 
-that relative to the total DWD population, more DWDs can be individually 
-resolved because of the reduction in competing GW signals. While the 
-number of DWDs radiating GWs in the LISA frequency band is reduced by a 
-factor of two for model FZ relative to model F50 for variations $\alpha25$ 
-and $q3$, the number of resolved sources is less affected with a 
-population-wide reduction of $26\%$ for the former, and surprisingly only 
-by 1\% for the latter. These results are far-reaching since the strength 
-of the Galactic DWD confusion foreground has direct consequences on the 
-detectability of all other LISA sources with small SNRs. An increase in 
-resolution capability from the reduced confusion foreground can be 
-extended to other Galactic binaries that LISA will observe at these 
-frequencies like those involving neutron stars and stellar-origin black 
-holes, as well as other more exotic GW sources like merging supermassive 
-black holes, extreme mass ratio inspirals, or cosmological GW backgrounds. 
-Based on our results, we suggest that studies which employ fits to the 
-confusion foreground based on population synthesis results consider 
-reducing the strength of the Galactic foreground PSD by a factor of two 
-depending on the chosen binary evolution model.
+In this study, we have investigated the effects of assuming a metallicity-dependent binary fraction on the formation and evolution of the Galactic population of DWDs with a special focus on the implications for LISA.
+Based on our synthetic Milky Way-like galaxy catalogs of DWDs, we find that applying a metallicity-dependent binary fraction changes the formation efficiency and evolutionary history of DWD populations.
+However, when considering the close DWD populations observable by LISA, we find that the only distinguishing features between models which assume a metallicity-dependent binary fraction (model FZ) and models which assume a flat $50\%$ binary fraction (model F50) are the population sizes and the strength of the Galactic DWD GW foreground.
+Models which assume a metallicity-dependent binary fraction produce Galactic DWD populations that were unchanged relative to the standard model assumptions.
+However, our results are highly dependent on the chosen binary evolution model.
+We extended our study to include three binary evolution parameter variations to investigate the sensitivity of the DWD population changes in assumptions for mass transfer stability and common envelope ejection efficiencies.
+While our binary evolution parameter variations change the size of the LISA-observable populations dramatically, the size of the close Galactic DWD population and the height of the confusion foreground for models which assume a metallicity-dependent binary fraction appears to either remain unchanged \emph{or} be reduced by 50\%.
+These two results highlight the interplay between the dominating factors which shape the LISA DWD population: the metallicity-dependent star formation history of the \textbf{m12i} galaxy, the metallicity-dependent close binary fraction which alters the ZAMS orbital period distribution, and the impact of binary evolution assumptions on DWD formation.
+This comparison emphasizes the sensitivity of the Galactic population of LISA-detectable DWDs to the intricacies of binary evolution.
+Binary evolution assumptions like CE efficiency are undergoing continuous study in current literature and an exact value has yet to be identified.
+By exploring a range of possibilities in this work, we capture the variation in predictions of the LISA DWD population that may be observed.
+
+An important consequence of a lower Galactic DWD confusion foreground is that relative to the total DWD population, more DWDs can be individually resolved because of the reduction in competing GW signals.
+While the number of DWDs radiating GWs in the LISA frequency band is reduced by a factor of two for model FZ relative to model F50 for variations $\alpha25$ and $q3$, the number of resolved sources is less affected with a population-wide reduction of $26\%$ for the former, and surprisingly only by 1\% for the latter.
+These results are far-reaching since the strength of the Galactic DWD confusion foreground has direct consequences on the detectability of all other LISA sources with small SNRs.
+An increase in resolution capability from the reduced confusion foreground can be extended to other Galactic binaries that LISA will observe at these frequencies like those involving neutron stars and stellar-origin black holes, as well as other more exotic GW sources like merging supermassive black holes, extreme mass ratio inspirals, or cosmological GW backgrounds.
+Based on our results, we suggest that studies which employ fits to the confusion foreground based on population synthesis results consider reducing the strength of the Galactic foreground PSD by a factor of two depending on the chosen binary evolution model.
 
 \begin{acknowledgments}
-The authors are grateful for helpful discussions with Carles Badenes, 
-Christine Mazzola Daher, Kaitlin Kratter, and the Gravitational Waves and 
-Astronomical Data groups at the CCA. The authors are also grateful to the 
-referee for providing a thoughtful review which strengthened the 
-presentation of the manuscript. S.T.\ was supported by an Undergraduate 
-Student Research Award (USRA) at CITA from the Natural Sciences and 
-Engineering Research Council of Canada (NSERC), Reference \# 498223. K.B.\ 
-is grateful for support from the Jeffrey L. Bishop Fellowship. The 
-Flatiron Institute is supported by the Simons Foundation.
+The authors are grateful for helpful discussions with Carles Badenes, Christine Mazzola Daher, Kaitlin Kratter, and the Gravitational Waves and Astronomical Data groups at the CCA.
+The authors are also grateful to the referee for providing a thoughtful review which strengthened the presentation of the manuscript.
+S.T.\ was supported by an Undergraduate Student Research Award (USRA) at CITA from the Natural Sciences and Engineering Research Council of Canada (NSERC), Reference \# 498223.
+K.B.\ is grateful for support from the Jeffrey L.
+Bishop Fellowship.
+The Flatiron Institute is supported by the Simons Foundation.
 \end{acknowledgments}
@@
 
-All data and software required to reproduce our results are available 
-through GitHub and Zenodo which are accessible through the icon links 
-associated with our abstract and each figure.
+All data and software required to reproduce our results are available through GitHub and Zenodo which are accessible through the icon links associated with our abstract and each figure.
 
@@
           \texttt{numpy}\ \citep{numpy}; 
-          \texttt{pandas}\ \citep{mckinney-proc-scipy-2010, 
-reback2020pandas}; 
+          \texttt{pandas}\ \citep{mckinney-proc-scipy-2010, reback2020pandas}; 
           \texttt{scipy}\ \citep{scipy}
@@
 \section{\textbf{Formation efficiency trends}}\label{appendix:form_eff}
-\textbf{As discussed in Section \ref{sec:formeff}, the formation 
-efficiency of DWDs exhibitis a metallicity dependence. This is both due to 
-the impact of metallicity on stellar evolution, and on the ZAMS orbital 
-period distribution of model F50 vs. FZ. Each DWD type and binary 
-evolution parameter variation exhibits unique trends in efficiency and in 
-their evolutionary channel. In the following subsections we go through 
-each DWD type in detail, first for our fiducial simulations and then for 
-our variations.}
-
-\subsection{Fiducial formation efficiency 
-trends}\label{subsec:formeff_fid}
+\textbf{As discussed in Section \ref{sec:formeff}, the formation efficiency of DWDs exhibits a metallicity dependence.
+This is due to the impact of metallicity on \textbf{both} stellar evolution, and the ZAMS orbital period distribution of model F50 vs.
+FZ.
+Each DWD type and binary evolution parameter variation exhibits unique trends in efficiency and in their evolutionary channel.
+In the following subsections we go through each DWD type in detail, first for our fiducial simulations and then for our variations.}
+
+\subsection{Fiducial formation efficiency trends}\label{subsec:formeff_fid}
 
 \subsubsection{\textbf{He + He}}\label{formeff_HeHe}
-For He + He DWDs, the sudden drop in formation efficiency near 
-$\log(Z/Z_{\odot})=-1.0$ \textbf{(see Figure \ref{fig:form_eff})} is 
-generally caused by the timescale for which the initially more massive 
-star in the DWD progenitor overflows it's Roche lobe. \textbf{As discussed 
-in Section \ref{sec:formeff}, at} lower metallicities, donors tend to fill 
-their Roche lobes while they are still on the MS and the mass transfer 
-remains stable and serves to widen the binary. At higher metallicities, 
-mass transfer is initiated when the donor has left the main sequence, and 
-the binary enters a common envelope evolution.
-
-The ZAMS orbital period leads to different specific \textbf{He + He} 
-evolutionary channels. For short-period systems with periods below 
-$10~\rm{days}$, \textbf{a CE phase} leads to a stellar merger due to 
-insufficient orbital energy to eject the envelope. Stellar mergers 
-continue to dominate the evolutionary pathways of systems with 
-intermediate orbital periods ($1 < \log_{10}(P_{\rm{orb}}/\rm{day}) < 
-2.5$). However, an additional growing number of merging systems arises 
-with one WD component and one stellar companion, and \textbf{surviving} 
-systems which don't interact at all and thus do not form a He + He DWD. 
-The distinction between the various scenarios in this intermediate orbital 
-period range depends on the combination of their ZAMS masses and orbital 
-periods. Finally, at wider initial periods $\log_{10}(\rm{P}) > 2.5$, the 
-decrease in formation efficiency is dominated by systems which never 
-interact and thus do not form a DWD before the present day.
+For He + He DWDs, the sudden drop in formation efficiency near $\log(Z/Z_{\odot})=-1.0$ \textbf{(see Figure \ref{fig:form_eff})} is generally caused by the timescale for which the initially more massive star in the DWD progenitor overflows it's Roche lobe.
+\textbf{As discussed in Section \ref{sec:formeff}, at} lower metallicities, donors tend to fill their Roche lobes while they are still on the MS and the mass transfer remains stable and serves to widen the binary.
+At higher metallicities, mass transfer is initiated when the donor has left the main sequence, and the binary enters a common envelope evolution.
+
+The ZAMS orbital period leads to different specific \textbf{He + He} evolutionary channels.
+For short-period systems with periods below $10~\rm{days}$, \textbf{a CE phase} leads to a stellar merger due to insufficient orbital energy to eject the envelope.
+Stellar mergers continue to dominate the evolutionary pathways of systems with intermediate orbital periods ($1 < \log_{10}(P_{\rm{orb}}/\rm{day}) < 2.5$).
+However, an additional growing number of merging systems arises with one WD component and one stellar companion, and \textbf{surviving} systems which don't interact at all and thus do not form a He + He DWD.
+The distinction between the various scenarios in this intermediate orbital period range depends on the combination of their ZAMS masses and orbital periods.
+Finally, at wider initial periods $\log_{10}(\rm{P}) > 2.5$, the decrease in formation efficiency is dominated by systems which never interact and thus do not form a DWD before the present day.
 
 \subsubsection{\textbf{CO + He}}\label{formeff_COHe}
-\textbf{In general, a CO + He DWD fails to form because either a stellar 
-merger occurs before DWD formation, or a CO + CO or He + He DWD is formed 
-instead. We discuss the specifics of these effects for three ZAMS orbital 
-period regimes below. Model FZ yields higher formation efficiencies than 
-F50 because CO + He DWDs prefer to form from progenitor binaries with 
-orbital periods near $\log_{10}(P_{\rm{orb}}/~\rm{day})\sim2-4$, which is 
-where the orbital period distribution of FZ peaks.}
-
-For short-period CO + He DWD progenitor binaries with orbital periods 
-below $\sim30~\rm{days}$, the only channel for stellar mergers before DWD 
-formation is during a CE evolution. This channel is similar to the stellar 
-merger channel for He + He DWDs, but due to higher-mass progenitors the CE 
-evolution results in the binary component with a higher mass becoming a CO 
-WD. At higher metallicities, the CO WD merges with its companion. 
-\textbf{As discussed in Section \ref{sec:formeff}, h}igher-metallicity 
-progenitors have a larger fraction of their mass in the convective 
-envelope when compared to lower-metallicity stars of the same mass. Thus a 
-CE phase with a higher-metallicity progenitor requires more orbital energy 
-to eject the common envelope, causing a larger amount of orbital shrinking 
-which results in a merger later in its binary evolution.
-
-For CO + He DWD progenitor systems with intermediate orbital periods 
-($1.5\leq \log_{10}(P_{\rm{orb}}/\rm{day})< 2.5$) the mechanisms which 
-impact formation efficiency are complex. The dominant way CO + He DWDs 
-\textbf{fail to form} is stellar mergers that occur during the second CE 
-phase. \textbf{Low-metallicity systems survive this second CE phase 
-whereas high-metallicity systems do not.} \textbf{Similar to the 
-short-period systems, there is increased orbital shrinkage for 
-high-metallicity progenitor binaries due to the deeper convective envelope 
-of the CE evolution donor. This creates shorter post-CE orbital periods 
-which leads to mergers during the CE second phase.}
-
-If a lower-metallicity system forms a CO + He DWD and a higher-metallicity 
-system does not, this \textbf{could also be} because the initially more 
-massive binary component initiates a CE while on the giant branch instead 
-of the asymptotic giant branch. This leaves behind a He WD with a stellar 
-companion \textbf{instead of a CO + He}, which is the dominating scenario 
-that restricts formation efficiency. There are a few edge cases where 
-either a He + He DWD is formed instead, or a CO WD and a stellar companion 
-is formed and there has been very nearly but not quite enough time for a 
-CO + He DWD to form.
-
-Long-period binaries with $\log_{10}(P_{\rm{orb}}/\rm{day})>2.5$ also 
-display complex scenarios that hinder CO + He DWD formation. In near-equal 
-contributions, our \cosmic\ simulations produce either stellar mergers or 
-stable non-DWD binaries at the end of the Hubble time. At these orbital 
-periods, stellar mergers always occur with a CE phase between a stellar 
-companion and a CO or He WD. \textbf{Again}, the mergers occur because of 
-increased CE donor envelope masses at higher metallicities. A subdominant 
-channel of stable He + He DWDs can also occur when a high-metallicity 
-primary overflows it's Roche lobe while still on the giant branch and thus 
-forms a He WD.
+\textbf{In general, a CO + He DWD fails to form because either a stellar merger occurs before DWD formation, or a CO + CO or He + He DWD is formed instead.
+We discuss the specifics of these effects for three ZAMS orbital period regimes below.
+Model FZ yields higher formation efficiencies than F50 because CO + He DWDs prefer to form from progenitor binaries with orbital periods near $\log_{10}(P_{\rm{orb}}/~\rm{day})\sim2-4$, which is where the orbital period distribution of FZ peaks.}
+
+For short-period CO + He DWD progenitor binaries with orbital periods below $\sim30~\rm{days}$, the only channel for stellar mergers before DWD formation is during a CE evolution.
+This channel is similar to the stellar merger channel for He + He DWDs, but due to higher-mass progenitors the CE evolution results in the binary component with a higher mass becoming a CO WD.
+At higher metallicities, the CO WD merges with its companion.
+\textbf{As discussed in Section \ref{sec:formeff}, h}igher-metallicity progenitors have a larger fraction of their mass in the convective envelope when compared to lower-metallicity stars of the same mass.
+Thus a CE phase with a higher-metallicity progenitor requires more orbital energy to eject the common envelope, causing a larger amount of orbital shrinking which results in a merger later in its binary evolution.
+
+For CO + He DWD progenitor systems with intermediate orbital periods ($1.5\leq \log_{10}(P_{\rm{orb}}/\rm{day})< 2.5$) the mechanisms which impact formation efficiency are complex.
+The dominant way CO + He DWDs \textbf{fail to form} is stellar mergers that occur during the second CE phase.
+\textbf{Low-metallicity systems survive this second CE phase whereas high-metallicity systems do not.} \textbf{Similar to the short-period systems, there is increased orbital shrinkage for high-metallicity progenitor binaries due to the deeper convective envelope of the CE evolution donor.
+This creates shorter post-CE orbital periods which leads to mergers during the second \textbf{CE} phase.}
+
+If a lower-metallicity system forms a CO + He DWD and a higher-metallicity system does not, this \textbf{could also be} because the initially more massive binary component initiates a CE while on the giant branch instead of the asymptotic giant branch.
+This leaves behind a He WD with a stellar companion \textbf{instead of a CO + He}, which is the dominating scenario that restricts formation efficiency.
+There are a few edge cases where either a He + He DWD is formed instead, or a CO WD and a stellar companion is formed and there has been very nearly but not quite enough time for a CO + He DWD to form.
+
+Long-period binaries with $\log_{10}(P_{\rm{orb}}/\rm{day})>2.5$ also display complex scenarios that hinder CO + He DWD formation.
+In near-equal contributions, our \cosmic\ simulations produce either stellar mergers or stable non-DWD binaries at the end of the Hubble time.
+At these orbital periods, stellar mergers always occur with a CE phase between a stellar companion and a CO or He WD.
+\textbf{Again}, the mergers occur because of increased CE donor envelope masses at higher metallicities.
+A subdominant channel of stable He + He DWDs can also occur when a high-metallicity primary overflows it's Roche lobe while still on the giant branch and thus forms a He WD.
 
 \subsubsection{\textbf{CO + CO}}\label{formeff_COCO}
-The decrease in the CO + CO DWD formation efficiency with increasing 
-metallicity stems from different evolutionary channels which arise at the 
-ZAMS orbital period boundary of $\log_{10}(P_{\rm{orb}}/\rm{day})\simeq3$. 
-We find that for binaries with orbital periods below this boundary, the 
-most common way that CO + CO DWDs form at lower metallicities but not at 
-higher metallicities is through stellar mergers during a CE phase with a 
-donor that is still on the giant branch. For lower-metallicity binaries, 
-which evolve on faster timescales, the primaries enter CE evolution while 
-on the asymptotic giant branch instead and the binary is able to survive. 
-For binaries with orbital periods above the boundary, the vast majority of 
-systems with wide initial orbits end up as stable binaries. The 
-\textbf{wide} systems which don’t form a CO DWD at high metallicity do so 
-because one or both of the binary components initiate a CE phase while 
-still on the giant branch, thus producing a CO + He or He + He DWD.
+The decrease in the CO + CO DWD formation efficiency with increasing metallicity stems from different evolutionary channels which arise at the ZAMS orbital period boundary of $\log_{10}(P_{\rm{orb}}/\rm{day})\simeq3$.
+We find that for binaries with orbital periods below this boundary, the most common way that CO + CO DWDs form at lower metallicities but not at higher metallicities is through stellar mergers during a CE phase with a donor that is still on the giant branch.
+For lower-metallicity binaries, which evolve on faster timescales, the primaries enter CE evolution while on the asymptotic giant branch instead and the binary is able to survive.
+For binaries with orbital periods above the boundary, the vast majority of systems with wide initial orbits end up as stable binaries.
+The \textbf{wide} systems which don’t form a CO DWD at high metallicity do so because one or both of the binary components initiate a CE phase while still on the giant branch, thus producing a CO + He or He + He DWD.
 
 \subsubsection{\textbf{ONe + X}}\label{formeff_ONe}
-The strongest effect which hinders formations of higher-metallicity ONe + 
-X DWDs is the strength of metallicity-dependent stellar winds assumed in 
-our model \citep{Vink2001}. The strength of line-driven winds varies more 
-strongly for the more massive ($\geq5\,M_\odot$) progenitors of ONe WDs 
-relative to the other lower mass WD progenitors. At higher metallicities, 
-ONe WD progenitors can lose enough mass through winds such that they don't 
-ignite their CO cores and thus leave behind a CO WD. Conversely, the 
-lower-metallicity progenitors retain enough mass to cause carbon ignition 
-and leave behind an ONe WD.
-
-\subsection{Parameter variations formation efficiency 
-trends}\label{subsec:formeff_vars}
-
-\textbf{As discussed in Section \ref{sec:formeff},} our simulations with 
-binary evolution parameter variations \textbf{show competition between} 
-the physics of binary evolution with skews introduced by the 
-metallicity-dependent orbital period distribution and binary fraction. Two 
-important features of our FZ and F50 models drive the differences in 
-\textbf{formation efficiency for} our binary evolution parameter 
-variations. First, the log-normal metallicity-dependent ZAMS orbital 
-period distribution increasingly skews towards 
-\textbf{$P_{\rm{orb}}\lesssim 10^4$ days} for decreasing metallicity. 
-However, second, the log-uniform $P_{\rm{orb}}$ distribution of F50 
-produces a higher number of the shortest-period systems 
-(\textbf{$P_{\rm{orb}}\lesssim 100$ days}) than for FZ as the tail of the 
-FZ distribution falls \textbf{below F50 in this regime.} \textbf{Because 
-there are more ZAMS binaries with $P_{\rm{orb}} \lesssim 10^4$ days in 
-F50, as the population evolves there are more likely to be binary 
-interactions in the population for F50 than FZ. This leads to more mergers 
-in $\alpha25$ occurring for F50 before formation of the DWD, and thus a 
-lower $\alpha25$ formation efficiency overall for F50 in contrast to FZ. 
-Below we summarize how the formation efficiency of each DWD type is 
-impacted by the parameter variations. Across all DWD types, we find that 
-there are more mergers for variation $\alpha25$ compared with the fiducial 
-variation, and fewer for $\alpha5$, due to the CE efficiency's impact on 
-CE phase orbital energy requirements. We also find fewer mergers for $q3$, 
-because of the ability for binaries to maintain stable mass transfer, thus 
-increasing their chance of survival.}
-
-\subsubsection{\textbf{Parameter variations: He + 
-He}}\label{formeff_HeHe_vars}
-For binary systems leading to He + He DWDs, \textbf{as stated above} there 
-are many more mergers for $\alpha25$ than for the fiducial variation. The 
-lower CE efficiency leads to more DWD progenitor mergers from a failed CE 
-ejection, or the CE shrinking the orbit such that it then merges on the 
-second CE phase. \textbf{As discussed above, there are also more close 
-binaries in the orbital period distribution of F50 than FZ, creating a 
-higher propensity for binary interactions and thus mergers for 
-$\alpha25$.} This is illustrated in the $\alpha25$ He + He plot of Figure 
-\ref{fig:form_eff}. Similar to the fiducial parameter variation, a binary 
-that becomes a He + He DWD at lower metallicities would merge before 
-becoming one at higher metallicities because of the longer evolution 
-timescales. These later interactions lead to closer post-CE separations 
-and thus more mergers. The dip at [Fe/H] $\simeq -1.5$ \textbf{(see Figure 
-\ref{fig:form_eff})} stems from mergers before the DWD forms, again 
-similar to the fiducial parameter variation. The peak that occurs in 
-$\alpha25$ at $\sim 10\%\,Z_\odot$ arises from binaries evolving faster, 
-and thus interacting earlier, as metallicity increases. This means that 
-equivalent binaries that would have merged or formed a CO + He DWD instead 
-at lower metallicities now survive to produce a He + He DWD. At higher 
-metallicities, there are also a higher proportion of wide ZAMS binaries, 
-which evolve off the Main Sequence too slowly to form a He + He DWD, 
-\textbf{adding to} the efficiency drop.
-
-For $\alpha5$, there are significantly fewer DWD progenitor mergers since 
-binaries are more likely to survive a CE phase due to the higher CE 
-ejection efficiency. Systems that would merge for $\alpha25$ instead 
-survive, shrinking to short orbits through CE interactions to reside in 
-the LISA band at present. The number of DWDs then makes up a higher 
-fraction of the total simulated binary population, thus we find in general 
-higher formation efficiencies than for the fiducial parameter variation 
-which sets $\alpha=1$. This effect is even more pronounced in comparison 
-with the $\alpha25$ variation which sets $\alpha=0.25$.
-
-Beyond the effects described above, the efficiency drop across metallicity 
-is similar to the fiducial parameter variation in that it depends on the 
-metallicity-dependent ZAMS orbital period distribution emphasizing 
-short-period systems at low metallicities, and on the change of formation 
-channel for different period ranges across metallicity. We find the 
-variation $q3$ yields the highest formation efficiency. Only the 
-shortest-period binaries do not form a DWD\textbf{, which are lost} 
-through mergers at higher metallicities. At low metallicities, even 
-binaries with ZAMS orbital periods $P_{\rm{orb}}\lesssim 100$ days form He 
-+ He DWDs, with binaries in model FZ reaching ZAMS orbital periods less 
-than a day in length. This leads to a higher formation efficiency from F50 
-over FZ for parameter variation $q3$ because of the higher number of 
-shortest-period ZAMS binaries in the log-uniform distribution of F50.
-
-\subsubsection{\textbf{Parameter variations: CO + 
-He}}\label{formeff_COHe_vars}
-For CO + He binaries, there are again many more mergers for parameter 
-variation $\alpha25$ relative to the fiducial case. This is the dominant 
-\textbf{reason} that progenitors do not evolve to produce DWDs at higher 
-metallicities. At low metallicities, a number of progenitor binaries form 
-CO + CO DWDs instead of He + CO DWDs. This is especially the case near 
-$\log_{10}(Z/Z_\odot)\sim -2$, where RLO occurs late enough in a binary's 
-evolution that mass transfer remains stable and CO + CO's are formed 
-rather than CO + He, hence producing a dip in the formation efficiency 
-\textbf{(see Figure \ref{fig:form_eff})}.
-
-Because parameter variation $\alpha5$ \textbf{yields fewer} mergers, the 
-formation efficiency is mostly governed by the metallicity-dependent ZAMS 
-orbital period distribution. At higher metallicities, the majority of 
-cases in model FZ where progenitors do not produce a CO + He DWD are from 
-progenitor mergers, or from He + He DWDs forming instead of CO + He DWDs. 
-At higher metallicities, the ZAMS orbital period distribution of FZ also 
-drops below that of F50 and extends out to orbital periods beyond what 
-would form a CO + He. This causes the formation efficiencies for FZ and 
-F50 to cross at log$_{10}(Z/Z_\odot)\sim-0.5$. This is also apparent for 
-the $q3$ variation, and to a lesser extent in the fiducial case. In $q3$, 
-for any given orbital period we find that lower-mass DWDs originate from 
-lower metallicities, thus leading to an approximately constant formation 
-efficiency.
-
-\subsubsection{\textbf{Parameter variations: CO + 
-CO}}\label{formeff_CO_vars}
-For CO + CO, across all variations, very close ZAMS binaries 
-($P_{\rm{orb}}\sim\mathcal{O}(100$ days)) at high metallicities form a CO 
-+ He or He + He DWD instead of a CO + CO because the binary interacts 
-before core Helium burning of one or both components. There are again many 
-more mergers in $\alpha25$, and fewer mergers for $\alpha5$. Due to the 
-high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods 
-survive to become CO + CO DWDs rather than merging or becoming CO + He or 
-He + He DWDs. There are \textbf{fewer} mergers overall for $q3$ than all 
-the $\alpha$ variations because the first RLO occurrence leads to stable 
-mass transfer from the primary to the secondary rather than multiple CE 
-phases. For both the $\alpha5$ and $q3$ variations, the majority of CO + 
-CO DWDs originate in wide enough orbits that they do not interact before 
-DWD formation. This leads to an approximately constant formation 
-efficiency across metallicity in both cases.
-
-\subsubsection{\textbf{Parameter variations: ONe + 
-X}}\label{formeff_ONe_vars}
-For model FZ, the ONe + X formation efficiencies follow similar trends 
-aross each parameter variation. Their formation scenarios are similar to 
-those described \textbf{in Section \ref{sec:formeff}} for ONe + X DWDs in 
-the fiducial binary evolution parameter set. The main difference between 
-each parameter variation is only in the number of sources produced since 
-the number of stellar mergers that occur before DWD formation increases 
-with decreasing common envelope efficiency. In model F50, the formation 
-efficiency is decreased significantly for parameter variation $\alpha25$ 
-because the log-uniform orbital period distribution produces many ZAMS 
-binaries with very short orbital periods which lead to stellar mergers 
-during the CE phases.
-
-\section{Amplitude Spectral Densities for Binary Evolution Parameter 
-Variations}\label{appendix:ASD_vars}
-
-Figure \ref{fig:LISA_SNR_vars} shows the ASD vs GW frequency of the 
-resolved systems with SNR $> 7$ for each DWD type, where the rows 
-alternate between models F50 and FZ for the $\alpha25$, $\alpha5$, and 
-$q3$ parameter variations. The LISA sensitivity curve is also shown in 
-black, which includes the modeled confusion foreground \textbf{(see 
-Section \ref{sec:LISA_met} for details on fitting the foreground) for the 
-given variation}. The entire population is shown as grey scatter points. 
-As discussed in Section \ref{sec:LISA_met}, apart from each DWD type 
-having a different abundance of resolved systems, the population-wide 
-characteristics remain unchanged between the two binary fraction models.
-
-The height of the confusion foreground and the number of DWDs radiating 
-GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 
-\textbf{two} for model FZ relative to model F50 for variations $\alpha5$ 
-and $q3$, however the number of resolved\textbf{, i.e. observable,} 
-sources is not reduced to an equal degree. The number of observable 
-systems with SNR $>7$ increases by 3\% for $\alpha25$\textbf{, mimicking 
-the LISA-band population remaining relatively unchanged}. \textbf{However, 
-}the number of \textbf{observable} DWDs is reduced by only 26\% for 
-$\alpha5$, and \textbf{by only 1\% for $q3$}, even though the overall LISA 
-population of both variations is halved. \textbf{Maintaining} the number 
-of DWDs in parameter variation $q3$ is contributed to \textbf{largely} by 
-He + He binaries with higher GW frequencies and lower ASDs which can now 
-survive CE interactions due to an initial phase of mass transfer (see 
-discussion of this formation channel in Section \ref{sec:CEsep}).
+The strongest effect which hinders formations of higher-metallicity ONe + X DWDs is the strength of metallicity-dependent stellar winds assumed in our model \citep{Vink2001}.
+The strength of line-driven winds varies more strongly for the more massive ($\geq5\,M_\odot$) progenitors of ONe WDs relative to the other lower-mass WD progenitors.
+At higher metallicities, ONe WD progenitors can lose enough mass through winds such that they don't ignite their CO cores and thus leave behind a CO WD.
+Conversely, the lower-metallicity progenitors retain enough mass to cause carbon ignition and leave behind an ONe WD.
+
+\subsection{Parameter variations formation efficiency trends}\label{subsec:formeff_vars}
+
+\textbf{As discussed in Section \ref{sec:formeff},} our simulations with binary evolution parameter variations \textbf{show competition between} the physics of binary evolution \textbf{and} skews introduced by the metallicity-dependent orbital period distribution and binary fraction.
+Two important features of our FZ and F50 models drive the differences in \textbf{formation efficiency for} our binary evolution parameter variations.
+First, the log-normal metallicity-dependent ZAMS orbital period distribution increasingly skews towards \textbf{$P_{\rm{orb}}\lesssim 10^4$ days} for decreasing metallicity.
+However, second, the log-uniform $P_{\rm{orb}}$ distribution of F50 produces a higher number of the shortest-period systems (\textbf{$P_{\rm{orb}}\lesssim 100$ days}) than for FZ as the tail of the FZ distribution falls \textbf{below F50 in this regime.} \textbf{Because there are more ZAMS binaries with $P_{\rm{orb}} \lesssim 10^4$ days in F50, as the population evolves there are more likely to be binary interactions in the population for F50 than FZ.
+This leads to more mergers in $\alpha25$ occurring for F50 before formation of the DWD, and thus a lower $\alpha25$ formation efficiency overall for F50 in contrast to FZ.
+Below we summarize how the formation efficiency of each DWD type is impacted by the parameter variations.
+Across all DWD types, we find that there are more mergers for variation $\alpha25$ compared with the fiducial variation, and fewer for $\alpha5$, due to the CE efficiency's impact on CE phase orbital energy requirements.
+We also find fewer mergers for $q3$, because of the ability for binaries to maintain stable mass transfer, thus increasing their chance of survival.}
+
+\subsubsection{\textbf{Parameter variations: He + He}}\label{formeff_HeHe_vars}
+For binary systems leading to He + He DWDs, \textbf{as stated above} there are many more mergers for $\alpha25$ than for the fiducial variation.
+The lower CE efficiency leads to more DWD progenitor mergers from a failed CE ejection, or the CE shrinking the orbit such that it then merges on the second CE phase.
+\textbf{As discussed above, there are also more close binaries in the orbital period distribution of F50 than FZ, creating a higher propensity for binary interactions and thus mergers for $\alpha25$.} This is illustrated in the $\alpha25$ He + He plot of Figure \ref{fig:form_eff}.
+Similar to the fiducial parameter variation, a binary that becomes a He + He DWD at lower metallicities would merge before becoming one at higher metallicities because of the longer evolution timescales.
+These later interactions lead to closer post-CE separations and thus more mergers.
+The dip at [Fe/H] $\simeq -1.5$ \textbf{(see Figure \ref{fig:form_eff})} stems from mergers before the DWD forms, again similar to the fiducial parameter variation.
+The peak that occurs in $\alpha25$ at $\sim 10\%\,Z_\odot$ arises from binaries evolving faster, and thus interacting earlier, as metallicity increases.
+This means that equivalent binaries that would have merged or formed a CO + He DWD instead at lower metallicities now survive to produce a He + He DWD.
+At higher metallicities, there are also a higher proportion of wide ZAMS binaries, which evolve off the Main Sequence too slowly to form a He + He DWD, \textbf{adding to} the efficiency drop.
+
+For $\alpha5$, there are significantly fewer DWD progenitor mergers since binaries are more likely to survive a CE phase due to the higher CE ejection efficiency.
+Systems that would merge for $\alpha25$ instead survive, shrinking to short orbits through CE interactions to reside in the LISA band at present.
+The number of DWDs then makes up a higher fraction of the total simulated binary population, thus we find in general higher formation efficiencies than for the fiducial parameter variation which sets $\alpha=1$.
+This effect is even more pronounced in comparison with the $\alpha25$ variation which sets $\alpha=0.25$.
+
+Beyond the effects described above, the efficiency drop across metallicity is similar to the fiducial parameter variation in that it depends on the metallicity-dependent ZAMS orbital period distribution emphasizing short-period systems at low metallicities, and on the change of formation channel for different period ranges across metallicity.
+We find \textbf{that} variation $q3$ yields the highest formation efficiency.
+Only the shortest-period binaries do not form a DWD\textbf{, which are lost} through mergers at higher metallicities.
+At low metallicities, even binaries with ZAMS orbital periods $P_{\rm{orb}}\lesssim 100$ days form He + He DWDs, with binaries in model FZ reaching ZAMS orbital periods less than a day in length.
+This leads to a higher formation efficiency from F50 over FZ for parameter variation $q3$ because of the higher number of shortest-period ZAMS binaries in the log-uniform distribution of F50.
+
+\subsubsection{\textbf{Parameter variations: CO + He}}\label{formeff_COHe_vars}
+For CO + He binaries, there are again many more mergers for parameter variation $\alpha25$ relative to the fiducial case.
+This is the dominant \textbf{reason} that progenitors do not evolve to produce DWDs at higher metallicities.
+At low metallicities, a number of progenitor binaries form CO + CO DWDs instead of He + CO DWDs.
+This is especially the case near $\log_{10}(Z/Z_\odot)\sim -2$, where RLO occurs late enough in a binary's evolution that mass transfer remains stable and CO + CO's are formed rather than CO + He, hence producing a dip in the formation efficiency \textbf{(see Figure \ref{fig:form_eff})}.
+
+Because parameter variation $\alpha5$ \textbf{yields fewer} mergers, the formation efficiency is mostly governed by the metallicity-dependent ZAMS orbital period distribution.
+At higher metallicities, the majority of cases in model FZ where progenitors do not produce a CO + He DWD are from progenitor mergers, or from He + He DWDs forming instead of CO + He DWDs.
+At higher metallicities, the ZAMS orbital period distribution of FZ also drops below that of F50 and extends out to orbital periods beyond what would form a CO + He.
+This causes the formation efficiencies for FZ and F50 to cross at log$_{10}(Z/Z_\odot)\sim-0.5$.
+This is also apparent for the $q3$ variation, and to a lesser extent in the fiducial case.
+In $q3$, for any given orbital period we find that lower-mass DWDs originate from lower metallicities, thus leading to an approximately constant formation efficiency.
+
+\subsubsection{\textbf{Parameter variations: CO + CO}}\label{formeff_CO_vars}
+For CO + CO, across all variations, very close ZAMS binaries ($P_{\rm{orb}}\sim\mathcal{O}(100$ days)) at high metallicities form a CO + He or He + He DWD instead of a CO + CO because the binary interacts before core Helium burning of one or both components.
+There are again many more mergers in $\alpha25$, and fewer mergers for $\alpha5$.
+Due to the high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods survive to become CO + CO DWDs rather than merging or becoming CO + He or He + He DWDs.
+There are \textbf{fewer} mergers overall for $q3$ than all the $\alpha$ variations because the first RLO occurrence leads to stable mass transfer from the primary to the secondary rather than multiple CE phases.
+For both the $\alpha5$ and $q3$ variations, the majority of CO + CO DWDs originate in wide enough orbits that they do not interact before DWD formation.
+This leads to an approximately constant formation efficiency across metallicity in both cases.
+
+\subsubsection{\textbf{Parameter variations: ONe + X}}\label{formeff_ONe_vars}
+For model FZ, the ONe + X formation efficiencies follow similar trends aross each parameter variation.
+Their formation scenarios are similar to those described \textbf{in Section \ref{sec:formeff}} for ONe + X DWDs in the fiducial binary evolution parameter set.
+The main difference between each parameter variation is only in the number of sources produced since the number of stellar mergers that occur before DWD formation increases with decreasing common envelope efficiency.
+In model F50, the formation efficiency is decreased significantly for parameter variation $\alpha25$ because the log-uniform orbital period distribution produces many ZAMS binaries with very short orbital periods which lead to stellar mergers during the CE phases.
+
+\section{Amplitude Spectral Densities for Binary Evolution Parameter Variations}\label{appendix:ASD_vars}
+
+Figure \ref{fig:LISA_SNR_vars} shows the ASD vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the rows alternate between models F50 and FZ for the $\alpha25$, $\alpha5$, and $q3$ parameter variations.
+The LISA sensitivity curve is also shown in black, which includes the modeled confusion foreground \textbf{(see Section \ref{sec:LISA_met} for details on fitting the foreground) for the given variation}.
+The entire population is shown as grey scatter points.
+As discussed in Section \ref{sec:LISA_met}, apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models.
+
+The height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of \textbf{two} for model FZ relative to model F50 for variations $\alpha5$ and $q3$, however the number of resolved\textbf{, i.e.
+observable,} sources is not reduced to an equal degree.
+The number of observable systems with SNR $>7$ increases by 3\% for $\alpha25$\textbf{, mimicking the LISA-band population remaining relatively unchanged}.
+\textbf{However, }the number of \textbf{observable} DWDs is reduced by only 26\% for $\alpha5$, and \textbf{by only 1\% for $q3$}, even though the overall LISA population of both variations is halved.
+\textbf{Maintaining} the number of DWDs in parameter variation $q3$ is contributed to \textbf{largely} by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).
 
@@
     \centering
-
 	\includegraphics[width=0.8\textwidth]{figures/LISA_SNR_alpha25.pdf}
@@
 	\includegraphics[width=0.8\textwidth]{figures/LISA_SNR_q3.pdf}
-    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for 
-each DWD type and parameter variation. The rows alternate between model 
-F50 and from model FZ. In each panel, the LISA sensitivity curve, 
-including the confusion foreground for each model, is shown in black and 
-the total population for each model is shown in grey. Again, we find that 
-each model qualitatively exhibits similar characteristics and that the 
-only change is in the yield of resolved DWDs for each type based on the 
-strength of the confusion foreground.}
+    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for each DWD type and parameter variation.
+The rows alternate between model F50 and from model FZ.
+In each panel, the LISA sensitivity curve, including the confusion foreground for each model, is shown in black and the total population for each model is shown in grey.
+Again, we find that each model qualitatively exhibits similar characteristics and that the only change is in the yield of resolved DWDs for each type based on the strength of the confusion foreground.}
     \label{fig:LISA_SNR_vars}
@@
 
-\section{Chirp Mass -- Distance Distributions for Binary Evolution 
-Parameter Variations}\label{appendix:Mc_dist_vars}
-
-Figure~\ref{fig:Mc_vs_dist_vars} shows the chirp mass vs distance 
-distribution for the $\alpha25$, $\alpha5$, and $q3$ parameter variations. 
-For $\alpha25$ we plot scatter plots for He + He and ONe + X due to low 
-statistics; there are too few binaries in this selected population to 
-produce reliable kernel density estimates. The only population with a 
-significant change between \textbf{binary fraction models} is for ONe + X 
-DWDs\textbf{, variation} $\alpha5$. Here, we find a skew to lower 
-\textbf{chirp} masses because a higher fraction of the binaries are ONe + 
-He for FZ \textbf{compared to} F50: a Helium companion makes up 44\% of 
-this selected population for FZ, compared with 10\% for F50. This leads to 
-lower average chirp masses for the ONe + X distribution. Furthermore, 
-$\sim8$\% of the F50 measurable systems are ONe + ONe binaries, versus 0\% 
-for FZ. Because ONe WDs have larger masses, this also creates the 
-high-mass concentration we \textbf{find} in the F50 contours.
+\section{Chirp Mass -- Distance Distributions for Binary Evolution Parameter Variations}\label{appendix:Mc_dist_vars}
+
+Figure~\ref{fig:Mc_vs_dist_vars} shows the chirp mass vs.
+distance distribution for the $\alpha25$, $\alpha5$, and $q3$ parameter variations.
+For $\alpha25$ we plot scatter plots for He + He and ONe + X due to low statistics; there are too few binaries in this selected population to produce reliable kernel density estimates.
+The only population with a significant change between \textbf{binary fraction models} is for ONe + X DWDs\textbf{, variation} $\alpha5$.
+Here, we find a skew to lower \textbf{chirp} masses because a higher fraction of the binaries are ONe + He for FZ \textbf{compared to} F50: a Helium companion makes up 44\% of this selected population for FZ, compared with 10\% for F50.
+This leads to lower average chirp masses for the ONe + X distribution.
+Furthermore, $\sim8$\% of the F50 measurable systems are ONe + ONe binaries, versus 0\% for FZ.
+Because ONe WDs have larger masses, this also creates the high-mass concentration we \textbf{find} in the F50 contours.
 \begin{figure*}[h]
     \centering
-
 	\includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_alpha25.pdf}
-
 	\includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_alpha5.pdf}
 	\includegraphics[width=0.8\textwidth]{figures/Mc_vs_dist_q3.pdf}
-    \caption{Chirp mass -- distance distributions for our other three 
-binary evolution parameter variations. We plot the $\alpha25$ populations 
-of He + He and ONe + X DWDs as scatter points since there are too few 
-binaries to produce meaningful density distributions. Again, we have 
-plotted each DWD type's population that exhibit observable GW frequency 
-evolution and have $\rm{SNR}>7$. Contours show the 5$^{\rm{th}}$, 
-25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$ and 95$^{\rm{th}}$ 
-percentiles. Most populations remain unchanged between binary fraction 
-models except for ONe + X DWDs in $\alpha5$, due to the number of He vs. 
-CO vs. ONe companions between each model.}
+    \caption{Chirp mass -- distance distributions for our other three binary evolution parameter variations.
+We plot the $\alpha25$ populations of He + He and ONe + X DWDs as scatter points since there are too few binaries to produce meaningful density distributions.
+Again, we have plotted each DWD type's population that exhibit observable GW frequency evolution and have $\rm{SNR}>7$.
+Contours show the 5$^{\rm{th}}$, 25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$ and 95$^{\rm{th}}$ percentiles.
+Most populations remain unchanged between binary fraction models except for ONe + X DWDs in $\alpha5$, due to the number of He vs.
+CO vs.
+ONe companions between each model.}
     \label{fig:Mc_vs_dist_vars}

### 2022-11-03 src/scripts/LISA_SNR.py
updates to get pipeline to run

@@ -4,7 +4,7 @@ import matplotlib.pyplot as plt
 import astropy.units as u
 from legwork.visualisation import plot_sensitivity_curve
 from legwork import psd
-import utils
+import dutils
 import paths
 
 
@@ -14,21 +14,21 @@ def plot_LISAcurves(var, model, label, ii):
         return a + b * x + c * x ** 2 + d * x ** 3 + e * x ** 4
     
     if model == 'fiducial_Z':
-        cosmic_confusion = utils.cosmic_confusion_var_fiducial
+        cosmic_confusion = dutils.cosmic_confusion_var_fiducial
     elif model == 'alpha25_Z':
-        cosmic_confusion = utils.cosmic_confusion_var_alpha25
+        cosmic_confusion = dutils.cosmic_confusion_var_alpha25
     elif model == 'alpha5_Z':
-        cosmic_confusion = utils.cosmic_confusion_var_alpha5
+        cosmic_confusion = dutils.cosmic_confusion_var_alpha5
     elif model == 'q3_Z':
-        cosmic_confusion = utils.cosmic_confusion_var_q3
+        cosmic_confusion = dutils.cosmic_confusion_var_q3
     elif model == 'fiducial':
-        cosmic_confusion = utils.cosmic_confusion_50_fiducial
+        cosmic_confusion = dutils.cosmic_confusion_50_fiducial
     elif model == 'alpha25':
-        cosmic_confusion = utils.cosmic_confusion_50_alpha25
+        cosmic_confusion = dutils.cosmic_confusion_50_alpha25
     elif model == 'alpha5':
-        cosmic_confusion = utils.cosmic_confusion_50_alpha5
+        cosmic_confusion = dutils.cosmic_confusion_50_alpha5
     elif model == 'q3':
-        cosmic_confusion = utils.cosmic_confusion_50_q3
+        cosmic_confusion = dutils.cosmic_confusion_50_q3
             
     resolved = pd.read_hdf(paths.data / "results.hdf", key="resolved_DWDs_{}_{}".format(var, model))
     

### 2022-11-03 src/scripts/dutils.py

@@ -1,0 +1,258 @@
+import numpy as np
+import paths
+import astropy.units as u
+import pandas as pd
+from legwork import psd
+
+#===================================================================================
+# File and Organizing Functions:
+#===================================================================================
+
+def getfiles(kstar1, kstar2, model):
+    '''
+    Get the list of COSMIC dat files used to create 
+    DWD populations.
+    
+    INPUTS
+    ----------------------
+    kstar1 [10, 11, 12]: type of first WD
+    kstar2 [10, 11, 12]: type of second WD
+    model: model variation from 'fiducial', 'q3', 
+           'alpha25', 'alpha5', and 'fiducial_Z', 
+           'q3_Z', 'alpha25_Z', 'alpha5_Z'
+    
+    RETURNS
+    ----------------------
+    filename_list [list, str]: list of files names
+    label [str]: DWD type label
+    '''
+    met_list = [0.0001, 0.00015029, 0.00022588, 0.00033948, 0.00051021, 
+                0.00076681, 0.00115245, 0.00173205, 0.00260314, 0.00391233, 
+                0.00587993, 0.0088371, 0.01328149, 0.01996108, 0.03]
+    
+    filename_list = []
+    for ii in range(len(met_list)):
+        if kstar1 == '12':
+            fname = '{}_12_10_12_{}.h5'.format(model, ii)
+        else:
+            fname = '{}_{}_{}_{}.h5'.format(model, kstar1, kstar2, ii)
+        filename_list.append(fname)
+        
+    if kstar1 == '12':
+        label='12'
+    else:
+        label='{}_{}'.format(kstar1, kstar2)
+        
+    return filename_list, label
+
+
+def get_binfrac_of_Z(Z):
+    '''
+    Calculates the theoretical binary fraction as a 
+    function of metallicity.
+    
+    INPUTS
+    ----------------------
+    Z [array]: metallicity Z values
+    
+    RETURNS
+    ----------------------
+    binfrac [array]: binary fraction values
+    '''
+    FeH = get_FeH_from_Z(Z)
[…]

### 2022-11-03 src/scripts/met_dep_porb.py

@@ -3,7 +3,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 import seaborn as sns
 from scipy.interpolate import interp1d
-from utils import get_Z_from_FeH, get_FeH_from_Z, get_binfrac_of_Z
+from dutils import get_Z_from_FeH, get_FeH_from_Z, get_binfrac_of_Z
 import scipy.integrate as integrate
 from matplotlib import rcParams
 import paths

### 2022-11-03 src/scripts/pipeline.py

@@ -28,7 +28,7 @@ FIRE_path = paths.data
 results_path = paths.data
 models = ['fiducial', 'fiducial_Z', 'alpha25', 'alpha25_Z', 'alpha5', 'alpha5_Z', 'q3', 'q3_Z']
 interfile = False
-nproc_gx = 28
+nproc_gx = 40
 nproc_results = len(models)
   
 
@@ -50,17 +50,17 @@ def get_results(dat):
     pp.get_formeff(
         pathtodat=dat_path, pathtosave=results_path, model=model, var=var,
     )
-    #print('formation efficiency done for model: {}'.format(model))
+    print('formation efficiency done for model: {}'.format(model))
     
     pp.get_interactionsep_and_numLISA(
         pathtocosmic=dat_path, pathtoLISA=LISA_path, pathtoresults=results_path, model=model, var=var,     
     )
-    #print('interaction sep done')
+    print('interaction sep done')
     
     pp.get_resolvedDWDs(
         pathtoLISA=LISA_path, pathtosave=results_path, var=var, model=model, window=window
     )
-    #print('resolved sources done')
+    print('resolved sources done')
     
     return []
 

### 2022-11-03 src/scripts/postproc.py

@@ -1,5 +1,5 @@
 
-import utils as dutil
+import dutils as dutil
 
 import numpy as np
 import pandas as pd
@@ -1179,7 +1179,7 @@ def get_resolvedDWDs(pathtoLISA, pathtosave, var, model, window):
     
     power_dat_median = power_dat.rolling(window).median()
     power_dat_median = power_dat_median[window:]
-    power_dat_downsample = power_dat.sample(int(len(power_dat)/10), replace=False)
+    power_dat_downsample = power_dat.sample(int(len(power_dat)/20), replace=False)
     power_dat_downsample = power_dat_downsample.sort_values('f_gw')
     power_dat_downsample.to_hdf(pathtosave / result_file, key=Pkey)
     #power_dat.to_hdf(pathtoLISA / result_file, key=Pkey)

### 2022-11-03 src/scripts/utils.py
updating to reflect published zenodo"

@@ -1,258 +1,0 @@
-import numpy as np
-import paths
-import astropy.units as u
-import pandas as pd
-from legwork import psd
-
-#===================================================================================
-# File and Organizing Functions:
-#===================================================================================
-
-def getfiles(kstar1, kstar2, model):
-    '''
-    Get the list of COSMIC dat files used to create 
-    DWD populations.
-    
-    INPUTS
-    ----------------------
-    kstar1 [10, 11, 12]: type of first WD
-    kstar2 [10, 11, 12]: type of second WD
-    model: model variation from 'fiducial', 'q3', 
-           'alpha25', 'alpha5', and 'fiducial_Z', 
-           'q3_Z', 'alpha25_Z', 'alpha5_Z'
-    
-    RETURNS
-    ----------------------
-    filename_list [list, str]: list of files names
-    label [str]: DWD type label
-    '''
-    met_list = [0.0001, 0.00015029, 0.00022588, 0.00033948, 0.00051021, 
-                0.00076681, 0.00115245, 0.00173205, 0.00260314, 0.00391233, 
-                0.00587993, 0.0088371, 0.01328149, 0.01996108, 0.03]
-    
-    filename_list = []
-    for ii in range(len(met_list)):
-        if kstar1 == '12':
-            fname = '{}_12_10_12_{}.h5'.format(model, ii)
-        else:
-            fname = '{}_{}_{}_{}.h5'.format(model, kstar1, kstar2, ii)
-        filename_list.append(fname)
-        
-    if kstar1 == '12':
-        label='12'
-    else:
-        label='{}_{}'.format(kstar1, kstar2)
-        
-    return filename_list, label
-
-
-def get_binfrac_of_Z(Z):
-    '''
-    Calculates the theoretical binary fraction as a 
-    function of metallicity.
-    
-    INPUTS
-    ----------------------
-    Z [array]: metallicity Z values
-    
-    RETURNS
-    ----------------------
-    binfrac [array]: binary fraction values
-    '''
-    FeH = get_FeH_from_Z(Z)
[…]

### 2022-11-18 src/tex/ms.tex
updating to reflect published zenodo"
add linenumbers back to tex
update ms.tex

@@
 \documentclass[twocolumn, linenumbers]{aastex631}
-
+%\documentclass[twocolumn]{aastex631}
 \newcommand{\vdag}{(v)^\dagger}
@@
 	\includegraphics[width=\textwidth]{figures/CEsep.pdf}
-    \caption{Average interaction separation, $\overline{\mathrm{a}}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type and variation from model F50.
+    \caption{Average interaction separation, $\overline{a}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type and variation from model F50.
 Solid lines show the average separation at the first RLO for binaries in each metallicity bin.
@@
 The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts.
-The sharp drop of the CO + CO average at the highest-metallicity bin of the fiducial variation is due to binning effects of the figure: it only contains 506 systems, of which the majority stem from a single low-separation system which was sampled 468 times times during the simulation.
+The sharp drop of the CO + CO average at the highest-metallicity bin of the fiducial variation is due to binning effects of the figure: it only contains \textbf{304} systems, of which the majority stem from a single low-separation system which was sampled \textbf{258} times times during the simulation.
 The regions of metallicity where there is not shading beyond the mean trend are also due to low numbers of DWDs in each bin.}
@@
 
-Figure \ref{fig:CEsep} shows the average separation at the first instance of CE evolution, $\overline{\mathrm{a}}_{\rm{CE}}$, of all DWD progenitors that result in systems orbiting in the LISA frequency band at present day, as a function of metallicity for each DWD type.
+Figure \ref{fig:CEsep} shows the average separation at the first instance of CE evolution, $\overline{a}_{\rm{CE}}$, of all DWD progenitors that result in systems orbiting in the LISA frequency band at present day, as a function of metallicity for each DWD type.
 The solid lines denote the average value, and the $1\sigma$ variance is shown in the surrounding shading.
@@
 	\includegraphics[width=\textwidth]{figures/PSD.pdf}
-    \caption{The PSD of the entire Galactic DWD GW foreground, summed over all metallicities and DWD types vs GW frequency for models FZ and F50, where the PSD is downsampled by a factor of $10$ for plotting purposes.
+    \caption{The PSD of the entire Galactic DWD GW foreground, summed over all metallicities and DWD types vs GW frequency for models FZ and F50, where the PSD is downsampled by a factor of \textbf{$20$} for plotting purposes.
 Each panel shows a different parameter variation.
@@
 This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.
-For the fiducial and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ are reduced by 4.5\% and increased by 3\% respectively.
-However, for $\alpha5$ the number of resolvable DWDs is reduced by only 26\%, and the number of resolvable DWDs $q3$ remains almost \emph{unchanged}, with a 1\% reduction even though the overall LISA population of both variations is halved.
-A large portion of the maintenance of the number of DWDs in parameter variation $q3$ is contributed to by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).
+For the fiducial and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ are reduced by \textbf{$\sim 17$\%} and increased by \textbf{$\sim3\%$} respectively\textbf{, with relatively unchanged overall LISA population sizes}.
+For $\alpha5$ the number of resolvable DWDs is reduced by only \textbf{$\sim 22\%$}, and the number of resolvable DWDs $q3$ remains almost \emph{unchanged}, with a \textbf{$\sim 5\%$} reduction even though the overall LISA population of both variations is halved.
+\textbf{The majority of systems which become resolvable with a lower foreground (in model FZ) are non-chirping systems.
+This is because both chirping and non-chirping systems have their populations halved, but the lower foreground allows a relative increase in the number of resolved non-chirping sources.
+Thus, the incorporation of a metallicity-dependent binary fraction reduces the number of chirping binaries relative to non-chirping binaries by a factor of two for variations $\alpha5$ and $q3$.
+The number of chirping systems in the fiducial and $\alpha25$ variations remain unchanged between models F50 and FZ.}
 

### 2022-11-18 src/scripts/LISA_SNR.py
script updates

@@ -125,7 +125,7 @@ def plot_LISAcurves(var, model, label, ii):
         ax[ii, i].set_ylim(top=5e-16)
     ax[ii, 0].set_ylabel(r'ASD [Hz$^{-1/2}$]', size=24)
 
-    return
+    return resolved_HeHe, resolved_COHe, resolved_COCO, resolved_ONeX
 
 
 

### 2022-11-18 src/tex/ms.tex

@@
 The only population with a significant change between \textbf{binary fraction models} is for ONe + X DWDs\textbf{, variation} $\alpha5$.
-Here, we find a skew to lower \textbf{chirp} masses because a higher fraction of the binaries are ONe + He for FZ \textbf{compared to} F50: a Helium companion makes up 44\% of this selected population for FZ, compared with 10\% for F50.
+Here, we find a skew to lower \textbf{chirp} masses because a higher fraction of the binaries are ONe + He for FZ \textbf{compared to} F50: a Helium companion makes up \textbf{38\%} of this selected population for FZ, compared with \textbf{12\%} for F50.
 This leads to lower average chirp masses for the ONe + X distribution.
-Furthermore, $\sim8$\% of the F50 measurable systems are ONe + ONe binaries, versus 0\% for FZ.
+Furthermore, \textbf{$\sim6$\%} of the F50 measurable systems are ONe + ONe binaries, versus 0\% for FZ.
 Because ONe WDs have larger masses, this also creates the high-mass concentration we \textbf{find} in the F50 contours.

### 2022-11-18 src/tex/ms.tex
fixing axes stuff and discussion

@@
 Figure \ref{fig:LISA_SNR} shows the amplitude spectral density vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the top and bottom rows show results for models FZ and F50 respectively for the fiducial parameter variation.
-For comparison, we also show the LISA sensitivity curve, including the
-modeled confusion foreground from each population in black, and the the entire population for each model in grey.
-Plots for our three parameter variations can be found in Appendix \ref{appendix:ASD_vars}.
+For comparison, we also show the LISA sensitivity curve, including the modeled confusion foreground from each population in black, and the the entire population for each model in grey.
+Plots for our three parameter variations \textbf{and discussion on the impact of each varation on the resolved populations} can be found in Appendix \ref{appendix:ASD_vars}.
 Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models.
@@
 While the distance to any one DWD strongly influences its ASD, DWD populations without a He WD component have, on average, higher ASDs due to their more massive WD components.
-
-We \textbf{highlight} that the height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 2 for model FZ relative to model F50 for variations $\alpha5$ and $q3$, the number of resolved sources is not reduced to an equal degree.
-This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.
-For the fiducial and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ are reduced by \textbf{$\sim 17$\%} and increased by \textbf{$\sim3\%$} respectively\textbf{, with relatively unchanged overall LISA population sizes}.
-For $\alpha5$ the number of resolvable DWDs is reduced by only \textbf{$\sim 22\%$}, and the number of resolvable DWDs $q3$ remains almost \emph{unchanged}, with a \textbf{$\sim 5\%$} reduction even though the overall LISA population of both variations is halved.
-\textbf{The majority of systems which become resolvable with a lower foreground (in model FZ) are non-chirping systems.
-This is because both chirping and non-chirping systems have their populations halved, but the lower foreground allows a relative increase in the number of resolved non-chirping sources.
-Thus, the incorporation of a metallicity-dependent binary fraction reduces the number of chirping binaries relative to non-chirping binaries by a factor of two for variations $\alpha5$ and $q3$.
-The number of chirping systems in the fiducial and $\alpha25$ variations remain unchanged between models F50 and FZ.}
 
@@
 This suggests that assuming a metallicity-dependent binary fraction may change the size of the Galactic close DWD population by a factor of $\sim$ two and the strength of the Galactic DWD GW foreground for LISA depending on the chosen binary evolution model.
+\textbf{We highlight, however, that for variations where the height of the confusion foreground is reduced, the number of resolved sources is not reduced to an equal degree.
+This is because an absence of fewer competing GW signals from DWDs in the LISA frequency band leads to individually resolved DWDs.
+See Appendix \ref{appendix:ASD_vars} for more details.}
 
@@
 
-The height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of \textbf{two} for model FZ relative to model F50 for variations $\alpha5$ and $q3$, however the number of resolved\textbf{, i.e.
-observable,} sources is not reduced to an equal degree.
-The number of observable systems with SNR $>7$ increases by 3\% for $\alpha25$\textbf{, mimicking the LISA-band population remaining relatively unchanged}.
-\textbf{However, }the number of \textbf{observable} DWDs is reduced by only 26\% for $\alpha5$, and \textbf{by only 1\% for $q3$}, even though the overall LISA population of both variations is halved.
-\textbf{Maintaining} the number of DWDs in parameter variation $q3$ is contributed to \textbf{largely} by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).
+\textbf{The height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ affects the number of resolvable systems in each parameter variation.
+For the fiducial and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ are reduced by $\sim 17$\% and increased by $\sim3\%$ respectively, with relatively unchanged overall LISA population sizes.
+For $\alpha5$ the number of resolvable DWDs is reduced by only $\sim 22\%$, and the number of resolvable DWDs $q3$ remains almost \emph{unchanged}, with a $\sim 5\%$ reduction even though the overall LISA population of both variations is halved.
+The majority of systems which become resolvable with a lower foreground (in model FZ) are non-chirping systems.
+This is because both chirping and non-chirping systems have their populations halved, but the lower foreground allows a relative increase in the number of resolved non-chirping sources.
+Thus, the incorporation of a metallicity-dependent binary fraction reduces the number of chirping binaries relative to non-chirping binaries by a factor of two for variations $\alpha5$ and $q3$.
+The number of chirping systems in the fiducial and $\alpha25$ variations remain unchanged between models F50 and FZ.}
 

### 2022-11-18 src/scripts/Mc_vs_dist.py

@@ -156,10 +156,10 @@ for model, model_Z, model_label in zip(models, model_Zs, model_labels):
         
     if "alpha25" in model:
         ax[0].set_yticks(np.arange(0.2, 0.42, 0.05))
-        ax[0].set_ylim(0.23, 0.4)
+        ax[0].set_ylim(0.23, 0.41)
         
         #ax[1].set_yticks([0.25, 0.3, 0.35, 0.4, 0.45, 0.5])
-        ax[1].set_ylim(0.25, 0.6)
+        ax[1].set_ylim(0.26, 0.62)
         
         ax[2].set_yticks(np.arange(0.25, 1.05, 0.15))
         ax[2].set_ylim(0.345, 1.05)
@@ -168,8 +168,13 @@ for model, model_Z, model_label in zip(models, model_Zs, model_labels):
         ax[3].set_yticklabels(['0.30', '0.60', '0.90', '1.20', '1.50'])
         ax[3].set_ylim(0.175, 1.55)
     
-    if ("q3" in model) or ("alpha5" in model):
+    if "q3" in model:
         ax[3].set_ylim(0.175, 1.55)
+    
+    if "alpha5" in model:
+        ax[0].set_ylim(0.16, 0.32)
+        ax[1].set_ylim(top=0.55)
+        ax[3].set_yticks([0.2, 0.6, 1.0, 1.4])
     plt.tight_layout()    
     plt.subplots_adjust(wspace=0.25)
     plt.savefig(paths.figures / "Mc_vs_dist_{}.pdf".format(model), dpi=100)

### 2022-11-22 src/scripts/CEsep.py
figure script edits

@@ -4,6 +4,9 @@ import pandas as pd
 import matplotlib.pyplot as plt
 import matplotlib as mpl
 import paths
+
+plt.rcParams["font.family"] = "serif"
+plt.rcParams["font.size"] = 14
 plt.rcParams['mathtext.fontset'] = 'dejavuserif'
 
 models = ["fiducial", "alpha25", "alpha5", "q3"]
@@ -20,7 +23,7 @@ whichsep = "CEsep"
 
 fig, ax = plt.subplots(4, 4, figsize=(16, 15))
 
-for m, model in enumerate(models):
+for m, model in enumerate(models):        
     if "Z" in model:
         Heinter = pd.read_hdf(paths.data / "results.hdf", key = 'intersep_{}_{}_{}_{}'.format(10, 10, "FZ", model))
         COHeinter = pd.read_hdf(paths.data / "results.hdf", key='intersep_{}_{}_{}_{}'.format(11, 10,  "FZ", model))
@@ -148,54 +151,71 @@ for m, model in enumerate(models):
                 loc='lower left', bbox_to_anchor= (0.0, 1.01), ncol=2, 
                 borderaxespad=0, frameon=False, fontsize=15, markerscale=0.5)
         ax[m, i].xaxis.set_minor_locator(AutoMinorLocator())
-        ax[m, i].yaxis.set_minor_locator(AutoMinorLocator())
+        ax[m, i].yaxis.set_minor_locator(AutoMinorLocator(5))
         
     if whichsep == 'CEsep':
         ax[m, 0].set_ylabel(r'$\overline{\mathit{a}}_{\rm{CE}}$  [10$^3$ R$_\odot$]', fontsize=16)
     else:
         ax[m, 0].set_ylabel(r'$\overline{\mathit{a}}_{\rm{RLO}}$  [10$^3$ R$_\odot$]', fontsize=16)
-    
+        
     if "fiducial" in model:
         ax[m, 0].set_yticks(np.arange(0.1, 0.6, 0.1))
-        ax[m, 0].set_ylim(0.09, 0.51)
+        ax[m, 0].set_ylim(0.08, 0.52)
         ax[m, 0].set_yticklabels(['0.10', '0.20', '0.30', '0.40', '0.50'])
+        
[…]

### 2022-11-22 src/scripts/Mc_vs_dist.py

@@ -8,6 +8,10 @@ import seaborn as sns
 import paths
 from matplotlib import patches
 
+plt.rcParams["font.family"] = "serif"
+plt.rcParams["mathtext.fontset"] = "dejavuserif"
+plt.rcParams["font.size"] = 14
+
 models = ["fiducial", "alpha25", "alpha5", "q3"]
 model_Zs = ["fiducial_Z", "alpha25_Z", "alpha5_Z", "q3_Z"]
 model_labels = ["fiducial", r"$\alpha25$", r"$\alpha5$", r"$q3$"]
@@ -17,19 +21,19 @@ label_y = [0.35, 0.49, 0.95, 1.6]
 colors = ['#add0ed', '#2b5d87', '#4288c2', '#17334a']
 figlabels = ['He + He', 'CO + He', 'CO + CO', 'ONe + X']
 
-for model, model_Z, model_label in zip(models, model_Zs, model_labels):
+for model, model_Z, model_label in zip(models, model_Zs, model_labels):  
     fig, ax = plt.subplots(1, 4, figsize=(16,4.5))
 
     resolved_dat_FZ = pd.read_hdf(
        paths.data / "results.hdf", key="resolved_DWDs_{}_{}".format("FZ", model_Z)
-    
+
     )
     resolved_dat_FZ = resolved_dat_FZ.loc[resolved_dat_FZ.resolved_chirp == 1.0]
     resolved_dat_F50 = pd.read_hdf(
         paths.data / "results.hdf", key="resolved_DWDs_{}_{}".format("F50", model)
     )
     resolved_dat_F50 = resolved_dat_F50.loc[resolved_dat_F50.resolved_chirp == 1.0]
-    
+
     Heplot = resolved_dat_FZ.loc[
         (resolved_dat_FZ.kstar_1 == 10) & (resolved_dat_FZ.kstar_2 == 10)
     ]
@@ -44,8 +48,8 @@ for model, model_Z, model_label in zip(models, model_Zs, model_labels):
         ((resolved_dat_FZ.kstar_1 == 12) & (resolved_dat_FZ.kstar_2.isin([10, 11, 12]))) |
         ((resolved_dat_FZ.kstar_2 == 12) & (resolved_dat_FZ.kstar_1.isin([10, 11, 12])))
     ]
-    
-    
+
+
     Heplot_F50 = resolved_dat_F50.loc[
         (resolved_dat_F50.kstar_1 == 10) & (resolved_dat_F50.kstar_2 == 10)
     ]
[…]

### 2022-11-22 src/scripts/form_eff.py

@@ -20,6 +20,10 @@ RETURNS
 No direct function outputs, but saves formation efficiency data for all
 DWD types and metallicity bins to files contained in pathtosave.
 '''
+
+plt.rcParams["font.family"] = "serif"
+plt.rcParams["mathtext.fontset"] = "dejavuserif"
+
 met_arr = np.logspace(np.log10(1e-4), np.log10(0.03), 15)
 met_arr = np.round(met_arr, 8)
 met_arr = np.append(0.0, met_arr)
@@ -152,41 +156,56 @@ for m, model_F50 in enumerate(models):
         if ii == 3:
             ax[ii, i].set_xlabel('Log$_{10}$(Z/Z$_\odot$)', fontsize=18)
         ax[ii, i].xaxis.set_minor_locator(AutoMinorLocator())
-        ax[ii, i].yaxis.set_minor_locator(AutoMinorLocator())
+        ax[ii, i].yaxis.set_minor_locator(AutoMinorLocator(5))
         ax[ii, i].tick_params(labelsize=15)
     
     if "fiducial" in model_F50:
+        ax[ii, 0].set_yticks(np.arange(0.5, 3.0, 0.5))
+        ax[ii, 0].set_yticklabels(['0.50', '1.00', '1.50', '2.00', '2.50'])
         ax[ii, 0].set_ylim(top=2.6)
-        ax[ii, 1].set_yticks(np.arange(1.5, 10.0, 1.))
-        ax[ii, 1].set_ylim(1.35, 5.7)
+        
+        ax[ii, 1].set_yticks(np.arange(1.5, 6.0, 1.))
+        ax[ii, 1].set_yticklabels(['1.50', '2.50', '3.50', '4.50', '5.50'])
+        ax[ii, 1].set_ylim(1.3, 5.7)
+
+        ax[ii, 2].set_yticks(np.arange(0.75, 3.0, 0.5))
         ax[ii, 2].set_ylim(top=2.9)
-        ax[ii, 3].set_yticks(np.arange(0.1, 0.5, 0.1))
-        ax[ii, 3].set_ylim(top=0.33)
+        ax[ii, 3].set_yticks(np.arange(0.08, 0.5, 0.06))
+        ax[ii, 3].set_ylim(0.07, 0.33)
         
     if "alpha25" in model_F50:
[…]

### 2022-11-22 src/scripts/lisa_nums.py

@@ -9,6 +9,11 @@ FIREmax = 13.346
 Z_sun = 0.02
 num = 30
 
+plt.rcParams["font.family"] = "serif"
+plt.rcParams["mathtext.fontset"] = "dejavuserif"
+plt.rcParams["font.size"] = 14
+
+
 met_bins = np.logspace(np.log10(FIREmin), np.log10(FIREmax), num) * Z_sun
     
 models = ["fiducial",  "alpha25", "alpha5", "q3"]

### 2022-11-22 src/scripts/met_dep_porb.py

@@ -110,9 +110,8 @@ for Z in met_arr:
     
     
 rcParams["font.family"] = "serif"
+rcParams["mathtext.fontset"] = "dejavuserif"
 rcParams["font.size"] = 14
-rcParams["mathtext.default"] = "regular"
-
 
 logP_lo_lim=0
 logP_hi_lim=9
@@ -142,8 +141,8 @@ for norm_wide, norm_close, Z, FeH, color in zip(norm_wide_list, norm_close_list,
 
 plt.legend(ncol=2, loc=[0, 1.01], frameon=False, prop={'size':16})
 plt.tick_params(labelsize=15)
-plt.xlabel(r'log$_{10}(P_{\rm{orb}}/day)$', size=18)
-plt.ylabel(r'$f_{\rm{logP}}$', size=18)
+plt.xlabel(r'Log$_{10}(P_{\rm{orb}}/\rm{day})$', size=18)
+plt.ylabel(r'f$_{\rm{logP}}$', size=18)
 plt.xlim(0, 8.5)
 plt.ylim(0, 0.23)
 plt.tight_layout()

### 2022-11-23 src/scripts/lisa_nums.py
fig edit

@@ -145,47 +145,73 @@ for m, model in enumerate(models):
                 fontsize=15
             )
         ax[m, i].xaxis.set_minor_locator(AutoMinorLocator())
-        ax[m, i].yaxis.set_minor_locator(AutoMinorLocator())
+        ax[m, i].yaxis.set_minor_locator(AutoMinorLocator(5))
         ax[m, i].tick_params(labelsize=15)
 
     ax[m, 0].set_ylabel(r'N$_{f_{\rm{GW}} \geq 10^{-4} \rm{Hz}}$ (Z) [10$^5$]', fontsize=18)
     
     if "fiducial" in model:
         ax[m, 0].set_yticks(np.arange(0.0, 2.5, 0.5))
+        ax[m, 0].set_yticklabels(['0.00', '0.50', '1.00', '1.50', '2.00'])
         ax[m, 0].set_ylim(top=2.05)
+        
         ax[m, 1].set_yticks(np.arange(0, 20, 4))
         ax[m, 1].set_ylim(top=17.25)
         ax[m, 1].set_yticklabels(np.arange(0, 20, 4).astype(float).astype(str))
-        ax[m, 3].set_ylim(top=0.81)
+        
+        ax[m, 2].set_yticks(np.arange(0.0, 3.0, 0.75))
+        #ax[m, 2].set_yticklabels(['0.00', '0.50', '1.00', '1.50', '2.00', '2.50'])
+        
+        ax[m, 3].set_yticks(np.arange(0., 1.0, 0.2))
+        ax[m, 3].set_yticklabels(['0.00', '0.20', '0.40', '0.60', '0.80'])
+        ax[m, 3].set_ylim(top=0.82)
     
     if "alpha25" in model:
         ax[m, 0].set_yticks(np.arange(0.0, 0.015, 0.003))
+        ax[m, 0].set_ylim(top=0.0123)
+        
         ax[m, 1].set_yticks(np.arange(0.0, 1.0, 0.2))
-        ax[m, 1].set_ylim(top=0.82)
+        ax[m, 1].set_yticklabels(['0.00', '0.20', '0.40', '0.60', '0.80'])
+        ax[m, 1].set_ylim(top=0.83)
+        
+        ax[m, 2].set_yticks(np.arange(0.0, 0.4, 0.1))
+        ax[m, 2].set_yticklabels(['0.00', '0.10', '0.20', '0.30'])
+        
[…]

### 2022-11-23 src/scripts/CEsep.py
figure edits

@@ -161,7 +161,6 @@ for m, model in enumerate(models):
     if "fiducial" in model:
         ax[m, 0].set_yticks(np.arange(0.1, 0.6, 0.1))
         ax[m, 0].set_ylim(0.08, 0.52)
-        ax[m, 0].set_yticklabels(['0.10', '0.20', '0.30', '0.40', '0.50'])
         
         ax[m, 1].set_yticks(np.arange(0.25, 1.5, 0.25))
         ax[m, 1].set_ylim(0.2, 1.3)
@@ -170,41 +169,37 @@ for m, model in enumerate(models):
         ax[m, 2].set_ylim(top=2.35)
         
         ax[m, 3].set_yticks(np.arange(1.0, 3.5, 0.5))
-        ax[m, 3].set_yticklabels(['1.00', '1.50', '2.00', '2.50', '3.00'])
         ax[m, 3].set_ylim(0.9, 3.1)
         
     if "alpha25" in model:
         ax[m, 0].set_yticks(np.arange(0.15, 0.55, 0.1))
-        ax[m, 0].set_yticklabels(['0.15', '0.25', '0.35', '0.45'])
         ax[m, 0].set_ylim(top=0.49)
         
         ax[m, 1].set_yticks(np.arange(0.5, 3.0, 0.75))
         ax[m, 1].set_ylim(top=3.05)
         
         ax[m, 2].set_yticks(np.arange(0.8, 4.0, 0.8))
-        ax[m, 2].set_yticklabels(['0.80', '1.60', '2.40', '3.20'])
         ax[m, 2].set_ylim(0.15, 3.52)
         
         ax[m, 3].set_yticks([1., 2., 3., 4.])
-        ax[m, 3].set_yticklabels(['1.00', '2.00', '3.00', '4.00'])
+        ax[m, 3].set_yticklabels(['1.0', '2.0', '3.0', '4.0'])
         ax[m, 3].set_ylim(top=4.4)
         
     if "alpha5" in model:
-        ax[m, 0].set_yticks(np.arange(0.02, 2.5, 0.07))
-        ax[m, 0].set_ylim(top=0.258)
+        ax[m, 0].set_yticks(np.arange(0.0, 2.5, 0.05))
+        ax[m, 0].set_ylim(top=0.235)
         
         ax[m, 1].set_yticks([0.0, 0.1, 0.2, 0.3])
[…]

### 2022-11-23 src/scripts/Mc_vs_dist.py

@@ -135,7 +135,7 @@ for model, model_Z, model_label in zip(models, model_Zs, model_labels):
             ax[i].text(0.05, 0.9, name, fontsize=18, horizontalalignment='left',
                        transform=ax[i].transAxes)
         ax[i].xaxis.set_minor_locator(AutoMinorLocator())
-        ax[i].yaxis.set_minor_locator(AutoMinorLocator(5))
+        ax[i].yaxis.set_minor_locator(AutoMinorLocator())
         ax[i].tick_params(labelsize=15)
 
 
@@ -147,62 +147,52 @@ for model, model_Z, model_label in zip(models, model_Zs, model_labels):
         ax[0].set_ylim(0.168, 0.36)
 
         ax[1].set_yticks(np.arange(0.20, 0.6, 0.1))
-        ax[1].set_yticklabels(['0.20', '0.30', '0.40', '0.50'])
         ax[1].set_ylim(0.23, 0.516)
         ax[1].yaxis.set_minor_locator(AutoMinorLocator(6))
 
         ax[2].set_yticks(np.arange(0.45, 1.0, 0.15))
         ax[2].set_ylim(0.35, 0.93)
 
-        ax[3].set_yticks(np.arange(0.4, 1.4, 0.3))
-        ax[3].set_yticklabels(['0.40', '0.70', '1.00', '1.30'])
-        ax[3].set_ylim(0.20, 1.36)
+        ax[3].set_yticks(np.arange(0.3, 1.4, 0.3))
+        ax[3].set_ylim(0.20, 1.35)
         
     if "alpha25" in model:
         ax[0].set_yticks(np.arange(0.2, 0.42, 0.05))
         ax[0].set_ylim(0.23, 0.41)
 
         ax[1].set_yticks(np.arange(0.3, 0.7, 0.1))
-        ax[1].set_yticklabels(['0.30', '0.40', '0.50', '0.60'])
         ax[1].set_ylim(0.26, 0.62)
 
         ax[2].set_yticks(np.arange(0.4, 1.05, 0.2))
-        ax[2].set_yticklabels(['0.40', '0.60', '0.80', '1.00'])
         ax[2].set_ylim(0.345, 1.04)
 
-        ax[3].set_yticks(np.arange(0.3, 1.6, 0.4))
-        ax[3].set_yticklabels(['0.30', '0.70', '1.10', '1.50'])
-        ax[3].set_ylim(0.2, 1.58)
[…]

### 2022-11-23 src/scripts/form_eff.py

@@ -161,51 +161,46 @@ for m, model_F50 in enumerate(models):
     
     if "fiducial" in model_F50:
         ax[ii, 0].set_yticks(np.arange(0.5, 3.0, 0.5))
-        ax[ii, 0].set_yticklabels(['0.50', '1.00', '1.50', '2.00', '2.50'])
         ax[ii, 0].set_ylim(top=2.6)
         
         ax[ii, 1].set_yticks(np.arange(1.5, 6.0, 1.))
-        ax[ii, 1].set_yticklabels(['1.50', '2.50', '3.50', '4.50', '5.50'])
         ax[ii, 1].set_ylim(1.3, 5.7)
 
         ax[ii, 2].set_yticks(np.arange(0.75, 3.0, 0.5))
         ax[ii, 2].set_ylim(top=2.9)
-        ax[ii, 3].set_yticks(np.arange(0.08, 0.5, 0.06))
-        ax[ii, 3].set_ylim(0.07, 0.33)
+        
+        ax[ii, 3].set_yticks(np.arange(0.08, 0.5, 0.08))
+        ax[ii, 3].set_ylim(0.07, 0.335)
         
     if "alpha25" in model_F50:
-        ax[ii, 0].set_yticks(np.arange(0.01, 0.15, 0.03))
+        ax[ii, 0].set_yticks(np.arange(0.03, 0.15, 0.03))
         ax[ii, 1].set_yticks(np.arange(0.2, 1.2, 0.2))
-        ax[ii, 1].set_yticklabels(['0.20', '0.40', '0.60', '0.80', '1.00'])
         ax[ii, 2].set_yticks(np.arange(0.5, 2.5, 0.5))
-        ax[ii, 2].set_yticklabels(['0.50', '1.00', '1.50', '2.00'])
         ax[ii, 2].set_ylim(top=2.15)
 
     if "alpha5" in model_F50:
         ax[ii, 0].set_yticks([1, 2, 3, 4, 5])
-        ax[ii, 0].set_yticklabels(['1.00', '2.00', '3.00', '4.00', '5.00']) 
+        ax[ii, 0].set_yticklabels(['1.0', '2.0', '3.0', '4.0', '5.0']) 
         ax[ii, 0].set_ylim(bottom=0.8)
         ax[ii, 1].set_yticks([3, 4, 5, 6])
-        ax[ii, 1].set_yticklabels(['3.00', '4.00', '5.00', '6.00'])
[…]

### 2022-11-23 src/scripts/lisa_nums.py

@@ -152,18 +152,16 @@ for m, model in enumerate(models):
     
     if "fiducial" in model:
         ax[m, 0].set_yticks(np.arange(0.0, 2.5, 0.5))
-        ax[m, 0].set_yticklabels(['0.00', '0.50', '1.00', '1.50', '2.00'])
+        ax[m, 0].set_yticklabels(['0.0', '0.5', '1.0', '1.5', '2.0'])
         ax[m, 0].set_ylim(top=2.05)
         
         ax[m, 1].set_yticks(np.arange(0, 20, 4))
         ax[m, 1].set_ylim(top=17.25)
         ax[m, 1].set_yticklabels(np.arange(0, 20, 4).astype(float).astype(str))
         
-        ax[m, 2].set_yticks(np.arange(0.0, 3.0, 0.75))
-        #ax[m, 2].set_yticklabels(['0.00', '0.50', '1.00', '1.50', '2.00', '2.50'])
+        ax[m, 2].set_yticks(np.arange(0.0, 3., 0.8))
         
         ax[m, 3].set_yticks(np.arange(0., 1.0, 0.2))
-        ax[m, 3].set_yticklabels(['0.00', '0.20', '0.40', '0.60', '0.80'])
         ax[m, 3].set_ylim(top=0.82)
     
     if "alpha25" in model:
@@ -171,11 +169,9 @@ for m, model in enumerate(models):
         ax[m, 0].set_ylim(top=0.0123)
         
         ax[m, 1].set_yticks(np.arange(0.0, 1.0, 0.2))
-        ax[m, 1].set_yticklabels(['0.00', '0.20', '0.40', '0.60', '0.80'])
         ax[m, 1].set_ylim(top=0.83)
         
         ax[m, 2].set_yticks(np.arange(0.0, 0.4, 0.1))
-        ax[m, 2].set_yticklabels(['0.00', '0.10', '0.20', '0.30'])
         
         ax[m, 3].yaxis.set_minor_locator(AutoMinorLocator(4))
         
@@ -187,14 +183,12 @@ for m, model in enumerate(models):
         ax[m, 1].set_yticklabels(['0.0', '20.0', '40.0', '60.0'])
         
         ax[m, 2].set_yticks(np.arange(0, 30, 7.5))
-        #ax[m, 2].set_yticklabels(['0.0', '5.0', '10.0', 
-        #                          '15.0', '20.0', '25.0'])
[…]

### 2022-11-25 src/tex/ms.tex
potentially final text edits

@@
 
-We count all higher-order companions as secondary, or binary, components.
+We count all higher-order companions as secondary (i.e.
+binary) components.
 We show curves for all 15 of our metallicity bins, increasing in metallicity from darkest to lightest curve colour.
@@
 The amount of mass accepted by the accretor is limited to $10$ times the accretor's mass divided by the accretor's thermal timescale.
-Finally, for RLO mass loss which becomes unstable and leads to common envelope evolution (CEE) we assume that the donor's binding energy is calculated according to the fits detailed in Appendix B of \citet{Claeys2014} and that orbital energy is deposited with $100\%$ efficiency into unbinding the common envelope ($\alpha=1$).
+Finally, for RLO mass loss which becomes unstable and leads to common envelope \textbf{(CE)} evolution we assume that the donor's binding energy is calculated according to the fits detailed in Appendix B of \citet{Claeys2014} and that orbital energy is deposited with $100\%$ efficiency into unbinding the common envelope ($\alpha=1$).
 
@@
 	\includegraphics[width=\columnwidth]{figures/sfh_vs_fb.pdf}
-    \caption{The metallicity-dependent binary fraction for close solar-type binaries with P $< 10^4$ days (black) plotted against the logarithm of $Z/Z_\odot$, with scatter points denoting the location of the metallicity grid used in our \cosmic\ simulations.
+    \caption{The metallicity-dependent binary fraction for close solar-type binaries with \textbf{$P_{\rm{orb}}< 10^4$} days (black) plotted against the logarithm of $Z/Z_\odot$, with scatter points denoting the location of the metallicity grid used in our \cosmic\ simulations.
 The secondary axis shows the amount of mass in stars formed within each metallicity bin from galaxy \textbf{m12i} of the ``Latte" suite in the FIRE-2 simulations as a red histogram.
@@
 The metallicity-dependent close binary fraction for solar-type binaries ($P_{\rm{orb}} < 10^4$ days), or simply the close binary fraction from here on, is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid.
-The close binary fraction, $f_{\rm{b}}$, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly.
+The close binary fraction, \textbf{$f_{\rm{b}}(Z)$}, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly.
 These two opposing trends compete throughout this study along with the impact of metallicity on single star evolution to form the final numerical distribution of systems in our DWD populations.
@@
 \end{equation}
-where $a_i$ is the DWD separation at formation, and 
+where $a_i$ \textbf{and $a_f$ are} the DWD separations at formation\textbf{ and present day respectively}, and 
 \begin{equation}
@@
 Instead, they originate through interactions in close binary systems or binaries with large eccentricities.
-Because of this, He WDs are able to form with low component masses on order $\sim 0.1\,M_\odot$, with the majority of He WDs in our simulations having masses between 0.2-0.5 $M_\odot$.
+Because of this, He WDs are able to form with low component masses on order $\sim 0.1\,M_\odot$, with the majority of He WDs in our simulations having masses between $0.2$--$0.5$ $M_\odot$.
 He + He DWDs form through evolution of close binary systems, during which their envelopes are both stripped through RLO and CE phase interactions before Helium ignition occurs.
@@
 When these systems enter a CE phase, it thus requires more orbital energy to eject the CE than for a low-metallicity star at the same point in its evolution, causing a large amount of orbital shrinking.
-These effects often leads{\sout{s}} to a stellar merger at higher metallicities for a system that would have survived the CE phase at a lower metallicity, thus causing a decrease in formation efficiency with metallicity.}
+These effects often lead to a stellar merger at higher metallicities for a system that would have survived the CE phase at a lower metallicity, thus causing a decrease in formation efficiency with metallicity.}
 
@@
     \caption{Average interaction separation, $\overline{a}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type and variation from model F50.
-Solid lines show the average separation at the first RLO for binaries in each metallicity bin.
+Solid lines show the average separation at the first \textbf{CE} for binaries in each metallicity bin.
 The shaded regions show the $1\sigma$ spread around the mean within each metallicity bin.
@@
 The LISA population of DWDs is dominated by stars with super-solar metallicities.
-This is true even for model FZ, which drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond $Z\simeq Z_\odot$.
+This is true even for model FZ, \textbf{where $f_{\rm{b}}(Z)$} drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond $Z\simeq Z_\odot$.
 There is a double peak in the fiducial and $\alpha25$ He + He populations; the first peak is caused by the sharp drop in formation efficiency past $Z\simeq0.1\,Z_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
@@
 All systems that end up radiating GWs in the LISA band have undergone at least one phase of CE evolution.
-For systems which experience a stable RLO mass transfer in the first interaction, the CE phase plays a key role in shrinking systems with initially wide separations to bring them into the LISA band.
+For systems which experience a stable RLO mass transfer as the first interaction, the CE phase plays a key role in shrinking systems with initially wide separations to bring them into the LISA band.
 
@@
 There is still a slight increasing trend in CO + He (as well as CO + CO and a more pronounced trend in He + He) for $q3$ that stems from the metallicity-dependent convective envelope discussion above.
-We also see that the average interaction separation are overall lower for variations $q3$ and $\alpha5$ than for the other two due to the orbital shrinkage that has already occurred from stable mass transfer and the efficient CE phase that will lead to minimal orbital shrinkage respectively.
+We also see that the average interaction separations are overall lower for variations $q3$ and $\alpha5$ than for the other two due to the orbital shrinkage that has already occurred from stable mass transfer and the efficient CE phase that will lead to minimal orbital shrinkage respectively.
 
@@
 The dashed lines show fits to the rolling boxcar median of width 1000 bins for each PSD (see Section \ref{sec:LISA_obs} for a discussion).
-A metallicity-dependent binary fraction (model FZ) yields fewer DWDs across all frequencies than a $50\%$ binary fraction (model F50) by roughly a factor of $2$ for the $\alpha5$ and $q3$ parameter variations.
-This produces a lower GW confusion foreground for frequencies with f$_{\rm{GW}}\leq\sim10^{-3}$ Hz.
+A metallicity-dependent binary fraction (model FZ) yields fewer DWDs across all frequencies than a $50\%$ binary fraction (model F50) by roughly a factor of \textbf{two} for the $\alpha5$ and $q3$ parameter variations.
+This produces a lower GW confusion foreground for frequencies with $f_{\rm{GW}}\lesssim 10^{-3}$ Hz.
 In contrast, the fiducial and $\alpha25$ parameter variations show very similar confusion foregrounds.}
@@
 The $\alpha5$ and $q3$ variations produce a higher number of F50 systems than FZ when summed over all DWD types.
-This is due to the log-uniform P$_{\rm{orb}}$ distribution of model F50 having more of the shortest-period binaries than the tails of the log-normal distribution of FZ; a discrepancy which becomes more significant with increasing metallicity as the FZ distribution moves from a peak of log$_{10}$($P_{\rm{orb}}\rm{/day})\simeq 3-4$ to log$_{10}$($P_{\rm{orb}}\rm{/day})\simeq 4-6$.
+This is due to the log-uniform $P_{\rm{orb}}$ distribution of model F50 having more of the shortest-period binaries than the tails of the log-normal distribution of FZ; a discrepancy which becomes more significant with increasing metallicity as the FZ distribution moves from a peak of log$_{10}$($P_{\rm{orb}}\rm{/day})\simeq 3-4$ to log$_{10}$($P_{\rm{orb}}\rm{/day})\simeq 4-6$.
 This tail is less likely to survive to the LISA band at present for the fiducial and $\alpha25$ variations due to the increased propensity for mergers of DWD progenitors.
@@
 Contours are shown at the $5^{\rm{th}}$, 25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$, and 95$^{\rm{th}}$ percentiles.
-Despite intrinsic changes to population properties induced by a metallicity-dependent binary fraction, and a reduction in the height of the DWD Galactic foreground the distributions are very similar.}
+Despite intrinsic changes to population properties induced by a metallicity-dependent binary fraction and a reduction in the height of the DWD Galactic foreground, the distributions are very similar.}
     \label{fig:Mc_vs_dist}
@@
 We show the GW PSD of each model, as well as the confusion forground estimate, in Figure~\ref{fig:PSD}.
-We downsample the PSD frequencies by a factor of 10 for plotting purposes.
+We downsample the PSD frequencies by a factor of \textbf{20} for plotting purposes.
 While model F50 (dark blue) and model FZ (light blue) produce several thousand large spikes in the PSD across LISA's frequency band, the overall foreground height, including the confusion, is larger for model F50 for parameter variations $\alpha5$ and $q3$.
@@
 Figure \ref{fig:LISA_SNR} shows the amplitude spectral density vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the top and bottom rows show results for models FZ and F50 respectively for the fiducial parameter variation.
-For comparison, we also show the LISA sensitivity curve, including the modeled confusion foreground from each population in black, and the the entire population for each model in grey.
+For comparison, we also show the LISA sensitivity curve, including the modeled confusion foreground from each population in black, and the entire population for each model in grey.
 Plots for our three parameter variations \textbf{and discussion on the impact of each varation on the resolved populations} can be found in Appendix \ref{appendix:ASD_vars}.
@@
 Figure \ref{fig:Mc_vs_dist} shows the chirp mass vs the luminosity distance for each DWD type in this selected population for the fiducial variation.
-The same figure for our other three parameter variations is shown in Appendix \ref{appendix:Mc_dist_vars}.
+The same figure for our other three parameter variations \textbf{and accompanying discussion} is shown in Appendix \ref{appendix:Mc_dist_vars}.
 The contours show the $5^{\rm{th}}$, $25^{\rm{th}}$, $50^{\rm{th}}$, $75^{\rm{th}}$, and $95^{\rm{th}}$ percentiles for models FZ (light blue) and F50 (dark blue, dashed).
@@
 In each parameter variation, changing the binary evolution assumptions dramatically changes the formation and evolution of the DWD populations.
-These changes lead to large shifts in the overall number of close DWDs in our synthetic present-day Milky-Way-like galaxies.
+These changes lead to large shifts in the overall number of close DWDs in our synthetic present-day Milky Way-like galaxies.
 We find that the total number of DWDs with $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$ increases for both variations $q3$ and $\alpha5$ \textbf{with respect to the fiducial case}.
@@
 This is illustrated in Figure \ref{fig:model_comp}.
-The top panel shows the confusion foreground fits for each binary evolution variation (different colored lines) and for each binary fraction model where the solid lines show FZ models and dotted lines show F50 models.
+The top panel shows the confusion foreground fits for each binary evolution variation (different colored lines) and for each binary fraction model where the solid lines show FZ models and \textbf{dashed} lines show F50 models.
 The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for the FZ models vs the F50 models for each variation.
@@
 \textbf{We highlight, however, that for variations where the height of the confusion foreground is reduced, the number of resolved sources is not reduced to an equal degree.
-This is because an absence of fewer competing GW signals from DWDs in the LISA frequency band leads to individually resolved DWDs.
+This is because fewer competing GW signals from DWDs in the LISA frequency band leads to more individually resolved DWDs.
 See Appendix \ref{appendix:ASD_vars} for more details.}
@@
 An important consequence of a lower Galactic DWD confusion foreground is that relative to the total DWD population, more DWDs can be individually resolved because of the reduction in competing GW signals.
-While the number of DWDs radiating GWs in the LISA frequency band is reduced by a factor of two for model FZ relative to model F50 for variations $\alpha25$ and $q3$, the number of resolved sources is less affected with a population-wide reduction of $26\%$ for the former, and surprisingly only by 1\% for the latter.
+While the number of DWDs radiating GWs in the LISA frequency band is reduced by a factor of two for model FZ relative to model F50 for variations $\alpha25$ and $q3$, the number of resolved sources is less affected with a population-wide reduction of \textbf{$22\%$} for the former, and surprisingly only by \textbf{5\%} for the latter.
 These results are far-reaching since the strength of the Galactic DWD confusion foreground has direct consequences on the detectability of all other LISA sources with small SNRs.
@@
 The distinction between the various scenarios in this intermediate orbital period range depends on the combination of their ZAMS masses and orbital periods.
-Finally, at wider initial periods $\log_{10}(\rm{P}) > 2.5$, the decrease in formation efficiency is dominated by systems which never interact and thus do not form a DWD before the present day.
+Finally, at wider initial periods \textbf{$\log_{10}(P_{\rm{orb}}/\rm{day}) > 2.5$}, the decrease in formation efficiency is dominated by systems which never interact and thus do not form a DWD before the present day.
 
@@
 \subsubsection{\textbf{CO + CO}}\label{formeff_COCO}
-The decrease in the CO + CO DWD formation efficiency with increasing metallicity stems from different evolutionary channels which arise at the ZAMS orbital period boundary of $\log_{10}(P_{\rm{orb}}/\rm{day})\simeq3$.
+The decrease in the CO + CO DWD formation efficiency with increasing metallicity stems from different evolutionary channels which arise at the ZAMS orbital period boundary of $\log_{10}(P_{\rm{orb}}/\rm{day})\sim3$.
 We find that for binaries with orbital periods below this boundary, the most common way that CO + CO DWDs form at lower metallicities but not at higher metallicities is through stellar mergers during a CE phase with a donor that is still on the giant branch.
@@
 This is also apparent for the $q3$ variation, and to a lesser extent in the fiducial case.
-In $q3$, for any given orbital period we find that lower-mass DWDs originate from lower metallicities, thus leading to an approximately constant formation efficiency.
+In $q3$, for any given orbital period we find that lower-mass DWDs originate from lower metallicities, thus leading to an approximately constant formation efficiency \textbf{for model F50}.
 
@@
 For both the $\alpha5$ and $q3$ variations, the majority of CO + CO DWDs originate in wide enough orbits that they do not interact before DWD formation.
-This leads to an approximately constant formation efficiency across metallicity in both cases.
+This leads to an approximately constant formation efficiency across metallicity in both cases \textbf{for model F50}.
 
@@
 The main difference between each parameter variation is only in the number of sources produced since the number of stellar mergers that occur before DWD formation increases with decreasing common envelope efficiency.
-In model F50, the formation efficiency is decreased significantly for parameter variation $\alpha25$ because the log-uniform orbital period distribution produces many ZAMS binaries with very short orbital periods which lead to stellar mergers during the CE phases.
+In model F50, the formation efficiency is decreased \textbf{with respect to FZ} for parameter variation $\alpha25$ because the log-uniform orbital period distribution produces many ZAMS binaries with very short orbital periods which lead to stellar mergers during the CE phases.
+\textbf{The F50 formation efficiency distributions are slightly flattened compared to model FZ for variations $\alpha5$ and $q3$, similar to CO + CO as discussed above.}
 
@@
     \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for each DWD type and parameter variation.
-The rows alternate between model F50 and from model FZ.
+The rows alternate between model F50 and model FZ.
 In each panel, the LISA sensitivity curve, including the confusion foreground for each model, is shown in black and the total population for each model is shown in grey.

### 2022-11-29 src/tex/ms.tex
Update ms.tex

@@
 The companion frequency differs from the binary fraction: the companion frequency is the probability of a star having a companion at a given orbital period, and the integration of this probability over all periods results in the binary fraction of the population.
-The metallicity dependence of the companion frequency is observed only below $P_{\rm{orb}}=10^6$ days, above which there are not sufficient observational data of binary systems to infer a metallicity dependence.
+The metallicity dependence of the companion frequency is \textbf{strongly identified} only below $P_{\rm{orb}}=10^4$ days\textbf{, whereas for $P_{\rm{orb}}>10^6$ it appears to be metallicity-invariant \citep{Moe2019}.
+We follow \citet{Moe2019}'s choice to linearly interpolate between the two regimes due to a dearth of observational data in this range.}
 
@@
 Each curve is coloured by metallicity, with the darkest curve corresponding to the lowest-metallicity bin in our simulations at [Fe/H] $=-2.3$ and the lightest curve corresponding to our highest-metallicity bin at [Fe/H] $=0.18$.
-Above $\log_{10}(P_{\rm{orb}}/\rm{day})\sim 4$, the companion frequency distribution \textbf{converges to} the same \textbf{curve} for all metallicity bins as no identified metallicity dependence at those periods exists in current literature.}
+Above \textbf{Between $\log_{10}(P_{\rm{orb}}/\rm{day})\sim 4$}, the companion frequency distribution \textbf{converges to} the same \textbf{curve} for all metallicity bins as no \textbf{identified} metallicity dependence at those periods exists in current literature.}
     \label{fig:met_dep_porb}
@@
 
-We count all higher-order companions as secondary (i.e.
-binary) components.
+We count all higher-order companions as secondary, or binary, components.
 We show curves for all 15 of our metallicity bins, increasing in metallicity from darkest to lightest curve colour.

### 2022-11-29 src/tex/ms.tex
Update ms.tex

@@
 Each curve is coloured by metallicity, with the darkest curve corresponding to the lowest-metallicity bin in our simulations at [Fe/H] $=-2.3$ and the lightest curve corresponding to our highest-metallicity bin at [Fe/H] $=0.18$.
-Above \textbf{Between $\log_{10}(P_{\rm{orb}}/\rm{day})\sim 4$}, the companion frequency distribution \textbf{converges to} the same \textbf{curve} for all metallicity bins as no \textbf{identified} metallicity dependence at those periods exists in current literature.}
+Above $\log_{10}(P_{\rm{orb}}/\rm{day})\sim 4$, the companion frequency distribution \textbf{converges to} the same \textbf{curve} for all metallicity bins as no \textbf{identified} metallicity dependence at those periods exists in current literature.}
     \label{fig:met_dep_porb}

### 2022-11-29 src/tex/ms.tex

@@
 Each curve is coloured by metallicity, with the darkest curve corresponding to the lowest-metallicity bin in our simulations at [Fe/H] $=-2.3$ and the lightest curve corresponding to our highest-metallicity bin at [Fe/H] $=0.18$.
-Above $\log_{10}(P_{\rm{orb}}/\rm{day})\sim 4$, the companion frequency distribution \textbf{converges to} the same \textbf{curve} for all metallicity bins as no \textbf{identified} metallicity dependence at those periods exists in current literature.}
+Above $\log_{10}(P_{\rm{orb}}/\rm{day})\sim 4$, the companion frequency distribution \textbf{converges to} the same \textbf{curve} for all metallicity bins as no identified metallicity dependence at those periods exists in current literature.}
     \label{fig:met_dep_porb}

### 2022-12-02 src/tex/ms.tex
remove bolding and line numbers

@@
 % Define document class
-\documentclass[twocolumn, linenumbers]{aastex631}
+\documentclass[twocolumn]{aastex631}
 %\documentclass[twocolumn]{aastex631}
@@
 The companion frequency differs from the binary fraction: the companion frequency is the probability of a star having a companion at a given orbital period, and the integration of this probability over all periods results in the binary fraction of the population.
-The metallicity dependence of the companion frequency is \textbf{strongly identified} only below $P_{\rm{orb}}=10^4$ days\textbf{, whereas for $P_{\rm{orb}}>10^6$ it appears to be metallicity-invariant \citep{Moe2019}.
-We follow \citet{Moe2019}'s choice to linearly interpolate between the two regimes due to a dearth of observational data in this range.}
+The metallicity dependence of the companion frequency is strongly identified only below $P_{\rm{orb}}=10^4$ days, whereas for $P_{\rm{orb}}>10^6$ it appears to be metallicity-invariant \citep{Moe2019}.
+We follow \citet{Moe2019}'s choice to linearly interpolate between the two regimes due to a dearth of observational data in this range.
 
@@
 Each curve is coloured by metallicity, with the darkest curve corresponding to the lowest-metallicity bin in our simulations at [Fe/H] $=-2.3$ and the lightest curve corresponding to our highest-metallicity bin at [Fe/H] $=0.18$.
-Above $\log_{10}(P_{\rm{orb}}/\rm{day})\sim 4$, the companion frequency distribution \textbf{converges to} the same \textbf{curve} for all metallicity bins as no identified metallicity dependence at those periods exists in current literature.}
+Above $\log_{10}(P_{\rm{orb}}/\rm{day})\sim 4$, the companion frequency distribution converges to the same curve for all metallicity bins as no identified metallicity dependence at those periods exists in current literature.}
     \label{fig:met_dep_porb}
@@
 Figure \ref{fig:met_dep_porb} shows the companion frequency f$_{\rm{logP}}$ for solar-type stars as a function of the logarithm of orbital period, mirroring the inner binaries curve of Figure 2 in \citet{Moe2021} and scaling to an overall multiplicity frequency of 0.67 (equivalent to an integrated binary fraction of 50\%) at solar metallicity.
-To obtain the normalization of the companion frequency for close binaries ($P_{\rm{orb}}<10^4$), we fit the results presented in \citet{Moe2019} using linear regression to obtain a piecewise relation between the metallicity, [Fe/H] and \textbf{close} binary fraction $f_{\rm{b}}$ as
+To obtain the normalization of the companion frequency for close binaries ($P_{\rm{orb}}<10^4$), we fit the results presented in \citet{Moe2019} using linear regression to obtain a piecewise relation between the metallicity, [Fe/H] and close binary fraction $f_{\rm{b}}$ as
 
@@
 The amount of mass accepted by the accretor is limited to $10$ times the accretor's mass divided by the accretor's thermal timescale.
-Finally, for RLO mass loss which becomes unstable and leads to common envelope \textbf{(CE)} evolution we assume that the donor's binding energy is calculated according to the fits detailed in Appendix B of \citet{Claeys2014} and that orbital energy is deposited with $100\%$ efficiency into unbinding the common envelope ($\alpha=1$).
+Finally, for RLO mass loss which becomes unstable and leads to common envelope (CE) evolution we assume that the donor's binding energy is calculated according to the fits detailed in Appendix B of \citet{Claeys2014} and that orbital energy is deposited with $100\%$ efficiency into unbinding the common envelope ($\alpha=1$).
 
@@
 Between all variations, all other prescriptions for binary evolution remain identical besides the one varied parameter.
-\textbf{A summary of all models and variations explored in this work is given in Table \ref{tbl:models}.} We delve in depth into the fiducial results in each section, and then give a brief overview of how the results change for each parameter variation.
+A summary of all models and variations explored in this work is given in Table \ref{tbl:models}.
+We delve in depth into the fiducial results in each section, and then give a brief overview of how the results change for each parameter variation.
 
@@
     \end{tabular}
-    \caption{\textbf{Summary of the models and binary evolution assumption variation simulations that are explored in this study.}}
+    \caption{Summary of the models and binary evolution assumption variation simulations that are explored in this study.}
     \label{tbl:models}
@@
 	\includegraphics[width=\columnwidth]{figures/sfh_vs_fb.pdf}
-    \caption{The metallicity-dependent binary fraction for close solar-type binaries with \textbf{$P_{\rm{orb}}< 10^4$} days (black) plotted against the logarithm of $Z/Z_\odot$, with scatter points denoting the location of the metallicity grid used in our \cosmic\ simulations.
+    \caption{The metallicity-dependent binary fraction for close solar-type binaries with $P_{\rm{orb}}< 10^4$ days (black) plotted against the logarithm of $Z/Z_\odot$, with scatter points denoting the location of the metallicity grid used in our \cosmic\ simulations.
 The secondary axis shows the amount of mass in stars formed within each metallicity bin from galaxy \textbf{m12i} of the ``Latte" suite in the FIRE-2 simulations as a red histogram.
@@
 The metallicity-dependent close binary fraction for solar-type binaries ($P_{\rm{orb}} < 10^4$ days), or simply the close binary fraction from here on, is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid.
-The close binary fraction, \textbf{$f_{\rm{b}}(Z)$}, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly.
+The close binary fraction, $f_{\rm{b}}(Z)$, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly.
 These two opposing trends compete throughout this study along with the impact of metallicity on single star evolution to form the final numerical distribution of systems in our DWD populations.
@@
 \end{equation}
-where $a_i$ \textbf{and $a_f$ are} the DWD separations at formation\textbf{ and present day respectively}, and 
+where $a_i$ and $a_f$ are the DWD separations at formation and present day respectively, and 
 \begin{equation}
@@
 This effect is exaggerated for model FZ which assumes a close binary fraction which also decreases with increasing metallicity.
-In \textbf{this section}, we \textbf{give a brief overview of the general trends observed in formation efficiency and their underlying causes.
-For a detailed description for each DWD type and binary evolution parameter variation, see Appendix \ref{appendix:form_eff}.}
+In this section, we give a brief overview of the general trends observed in formation efficiency and their underlying causes.
+For a detailed description for each DWD type and binary evolution parameter variation, see Appendix \ref{appendix:form_eff}.
 
-\textbf{There are two common ways that the formation of DWDs from stellar progenitors is inhibited.
+There are two common ways that the formation of DWDs from stellar progenitors is inhibited.
 The first is through stellar mergers, where the binary merges before both components become WDs.
 The second is due to evolutionary outcomes like forming a different DWD type, or not forming a DWD by the present day.
-For all DWD types except ONe + X, which has other dominating \textbf{effects} hindering formation efficiency like metallicity-dependent stellar winds, we find that different regimes of ZAMS orbital period leads to different specific evolutionary channels.}
+For all DWD types except ONe + X, which has other dominating effects hindering formation efficiency like metallicity-dependent stellar winds, we find that different regimes of ZAMS orbital period leads to different specific evolutionary channels.
 
-\textbf{In our \cosmic\ models, lower-metallicity stars evolve faster than high-metallicity stars and have larger radii near the end of the MS.
+In our \cosmic\ models, lower-metallicity stars evolve faster than high-metallicity stars and have larger radii near the end of the MS.
 This changes the timescales of RLO: low-metallicity stars tend to fill their Roche lobes while still on the MS, meaning mass transfer can remain stable which serves to widen the binary.
@@
 When these systems enter a CE phase, it thus requires more orbital energy to eject the CE than for a low-metallicity star at the same point in its evolution, causing a large amount of orbital shrinking.
-These effects often lead to a stellar merger at higher metallicities for a system that would have survived the CE phase at a lower metallicity, thus causing a decrease in formation efficiency with metallicity.}
+These effects often lead to a stellar merger at higher metallicities for a system that would have survived the CE phase at a lower metallicity, thus causing a decrease in formation efficiency with metallicity.
 
@@
 
-\textbf{Our binary evolution parameter variations emphasizes the interplay of the aforementioned effects of the distributions of F50 and FZ with the physics of binary evolution.
+Our binary evolution parameter variations emphasizes the interplay of the aforementioned effects of the distributions of F50 and FZ with the physics of binary evolution.
 For example, the lower CE efficiency of variation $\alpha25$ is the dominating formation efficiency inhibitor since it induces a higher merger rate.
@@
 We thus find less mergers overall in both cases, and that the effect of the metallicity-dependent $P_{\rm{orb}}$ distribution dominates the formation efficiency trends rather than restrictions imposed by binary evolution prescriptions.
-}
 
@@
     \caption{Average interaction separation, $\overline{a}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type and variation from model F50.
-Solid lines show the average separation at the first \textbf{CE} for binaries in each metallicity bin.
+Solid lines show the average separation at the first CE for binaries in each metallicity bin.
 The shaded regions show the $1\sigma$ spread around the mean within each metallicity bin.
@@
 The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts.
-The sharp drop of the CO + CO average at the highest-metallicity bin of the fiducial variation is due to binning effects of the figure: it only contains \textbf{304} systems, of which the majority stem from a single low-separation system which was sampled \textbf{258} times times during the simulation.
+The sharp drop of the CO + CO average at the highest-metallicity bin of the fiducial variation is due to binning effects of the figure: it only contains 304 systems, of which the majority stem from a single low-separation system which was sampled 258 times times during the simulation.
 The regions of metallicity where there is not shading beyond the mean trend are also due to low numbers of DWDs in each bin.}
@@
 The LISA population of DWDs is dominated by stars with super-solar metallicities.
-This is true even for model FZ, \textbf{where $f_{\rm{b}}(Z)$} drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond $Z\simeq Z_\odot$.
+This is true even for model FZ, where $f_{\rm{b}}(Z)$ drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond $Z\simeq Z_\odot$.
 There is a double peak in the fiducial and $\alpha25$ He + He populations; the first peak is caused by the sharp drop in formation efficiency past $Z\simeq0.1\,Z_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
@@
 The slope of the increase for these three models is dictated by the CE efficiency $\alpha$.
-\textbf{As discussed in Section \ref{sec:formeff}, with} increasing metallicity there is a deepening of the convective envelope of the star \textbf{compared to its lower metallicity counterpart}, requiring more orbital energy to be available in order to eject the CE.
+As discussed in Section \ref{sec:formeff}, with increasing metallicity there is a deepening of the convective envelope of the star compared to its lower metallicity counterpart, requiring more orbital energy to be available in order to eject the CE.
 Thus the high-metallicity binaries must have even wider separations for lower $\alpha$ values to ensure the binary does not merge before the envelope is ejected.
@@
 
-While metallicity impacts the intrinsic properties of our simulated DWD populations as described in Sections~\ref{sec:formeff} and \ref{sec:CEsep}, when we consider the present-day Galactic close DWDs we find that the population detectable by LISA largely only changes \textbf{in total number, but not in frequency distribution}.
+While metallicity impacts the intrinsic properties of our simulated DWD populations as described in Sections~\ref{sec:formeff} and \ref{sec:CEsep}, when we consider the present-day Galactic close DWDs we find that the population detectable by LISA largely only changes in total number, but not in frequency distribution.
 The number of DWDs in the LISA frequency band decreases by $\sim50\%$ when comparing model F50 to model FZ for variations $\alpha5$ and $q3$, but remains approximately unchanged for our fiducial and $\alpha25$ variations.
@@
 	\includegraphics[width=\textwidth]{figures/PSD.pdf}
-    \caption{The PSD of the entire Galactic DWD GW foreground, summed over all metallicities and DWD types vs GW frequency for models FZ and F50, where the PSD is downsampled by a factor of \textbf{$20$} for plotting purposes.
+    \caption{The PSD of the entire Galactic DWD GW foreground, summed over all metallicities and DWD types vs GW frequency for models FZ and F50, where the PSD is downsampled by a factor of $20$ for plotting purposes.
 Each panel shows a different parameter variation.
@@
 The dashed lines show fits to the rolling boxcar median of width 1000 bins for each PSD (see Section \ref{sec:LISA_obs} for a discussion).
-A metallicity-dependent binary fraction (model FZ) yields fewer DWDs across all frequencies than a $50\%$ binary fraction (model F50) by roughly a factor of \textbf{two} for the $\alpha5$ and $q3$ parameter variations.
+A metallicity-dependent binary fraction (model FZ) yields fewer DWDs across all frequencies than a $50\%$ binary fraction (model F50) by roughly a factor of two for the $\alpha5$ and $q3$ parameter variations.
 This produces a lower GW confusion foreground for frequencies with $f_{\rm{GW}}\lesssim 10^{-3}$ Hz.
@@
 We show the GW PSD of each model, as well as the confusion forground estimate, in Figure~\ref{fig:PSD}.
-We downsample the PSD frequencies by a factor of \textbf{20} for plotting purposes.
+We downsample the PSD frequencies by a factor of 20 for plotting purposes.
 While model F50 (dark blue) and model FZ (light blue) produce several thousand large spikes in the PSD across LISA's frequency band, the overall foreground height, including the confusion, is larger for model F50 for parameter variations $\alpha5$ and $q3$.
@@
 For comparison, we also show the LISA sensitivity curve, including the modeled confusion foreground from each population in black, and the entire population for each model in grey.
-Plots for our three parameter variations \textbf{and discussion on the impact of each varation on the resolved populations} can be found in Appendix \ref{appendix:ASD_vars}.
+Plots for our three parameter variations and discussion on the impact of each varation on the resolved populations can be found in Appendix \ref{appendix:ASD_vars}.
 Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models.
@@
 Figure \ref{fig:Mc_vs_dist} shows the chirp mass vs the luminosity distance for each DWD type in this selected population for the fiducial variation.
-The same figure for our other three parameter variations \textbf{and accompanying discussion} is shown in Appendix \ref{appendix:Mc_dist_vars}.
+The same figure for our other three parameter variations and accompanying discussion is shown in Appendix \ref{appendix:Mc_dist_vars}.
 The contours show the $5^{\rm{th}}$, $25^{\rm{th}}$, $50^{\rm{th}}$, $75^{\rm{th}}$, and $95^{\rm{th}}$ percentiles for models FZ (light blue) and F50 (dark blue, dashed).
@@
 These changes lead to large shifts in the overall number of close DWDs in our synthetic present-day Milky Way-like galaxies.
-We find that the total number of DWDs with $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$ increases for both variations $q3$ and $\alpha5$ \textbf{with respect to the fiducial case}.
+We find that the total number of DWDs with $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$ increases for both variations $q3$ and $\alpha5$ with respect to the fiducial case.
 This is because there are fewer stellar mergers which occur before the formation of a DWD, thus allowing more systems to evolve due to GW emission and orbit in the LISA frequency band at present.
 Conversely, for variation $\alpha25$, we find that the number of DWDs orbiting with frequencies in the LISA band is drastically reduced.
-This is because of the highly inefficient use of orbital energy to eject the common envelope, \textbf{which produces} more stellar mergers, or closer binaries which are more prone to future mergers.
+This is because of the highly inefficient use of orbital energy to eject the common envelope, which produces more stellar mergers, or closer binaries which are more prone to future mergers.
 
@@
 This is illustrated in Figure \ref{fig:model_comp}.
-The top panel shows the confusion foreground fits for each binary evolution variation (different colored lines) and for each binary fraction model where the solid lines show FZ models and \textbf{dashed} lines show F50 models.
+The top panel shows the confusion foreground fits for each binary evolution variation (different colored lines) and for each binary fraction model where the solid lines show FZ models and dashed lines show F50 models.
 The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for the FZ models vs the F50 models for each variation.
-The number of DWDs in the LISA band spans over two orders of magnitude, \textbf{but} the ratio of FZ to F50, as well as the spectral shape of the confusion fit, is either relatively unchanged or reduced by a factor of approximately two.
+The number of DWDs in the LISA band spans over two orders of magnitude, but the ratio of FZ to F50, as well as the spectral shape of the confusion fit, is either relatively unchanged or reduced by a factor of approximately two.
 This suggests that assuming a metallicity-dependent binary fraction may change the size of the Galactic close DWD population by a factor of $\sim$ two and the strength of the Galactic DWD GW foreground for LISA depending on the chosen binary evolution model.
-\textbf{We highlight, however, that for variations where the height of the confusion foreground is reduced, the number of resolved sources is not reduced to an equal degree.
+We highlight, however, that for variations where the height of the confusion foreground is reduced, the number of resolved sources is not reduced to an equal degree.
 This is because fewer competing GW signals from DWDs in the LISA frequency band leads to more individually resolved DWDs.
-See Appendix \ref{appendix:ASD_vars} for more details.}
+See Appendix \ref{appendix:ASD_vars} for more details.
 
@@
 An important consequence of a lower Galactic DWD confusion foreground is that relative to the total DWD population, more DWDs can be individually resolved because of the reduction in competing GW signals.
-While the number of DWDs radiating GWs in the LISA frequency band is reduced by a factor of two for model FZ relative to model F50 for variations $\alpha25$ and $q3$, the number of resolved sources is less affected with a population-wide reduction of \textbf{$22\%$} for the former, and surprisingly only by \textbf{5\%} for the latter.
+While the number of DWDs radiating GWs in the LISA frequency band is reduced by a factor of two for model FZ relative to model F50 for variations $\alpha25$ and $q3$, the number of resolved sources is less affected with a population-wide reduction of $22\%$ for the former, and surprisingly only by 5\% for the latter.
 These results are far-reaching since the strength of the Galactic DWD confusion foreground has direct consequences on the detectability of all other LISA sources with small SNRs.
@@
 \appendix
-\section{\textbf{Formation efficiency trends}}\label{appendix:form_eff}
-\textbf{As discussed in Section \ref{sec:formeff}, the formation efficiency of DWDs exhibits a metallicity dependence.
-This is due to the impact of metallicity on \textbf{both} stellar evolution, and the ZAMS orbital period distribution of model F50 vs.
+\section{Formation efficiency trends}\label{appendix:form_eff}
+As discussed in Section \ref{sec:formeff}, the formation efficiency of DWDs exhibits a metallicity dependence.
+This is due to the impact of metallicity on both stellar evolution, and the ZAMS orbital period distribution of model F50 vs.
 FZ.
 Each DWD type and binary evolution parameter variation exhibits unique trends in efficiency and in their evolutionary channel.
-In the following subsections we go through each DWD type in detail, first for our fiducial simulations and then for our variations.}
+In the following subsections we go through each DWD type in detail, first for our fiducial simulations and then for our variations.
 
@@
 
-\subsubsection{\textbf{He + He}}\label{formeff_HeHe}
-For He + He DWDs, the sudden drop in formation efficiency near $\log(Z/Z_{\odot})=-1.0$ \textbf{(see Figure \ref{fig:form_eff})} is generally caused by the timescale for which the initially more massive star in the DWD progenitor overflows it's Roche lobe.
-\textbf{As discussed in Section \ref{sec:formeff}, at} lower metallicities, donors tend to fill their Roche lobes while they are still on the MS and the mass transfer remains stable and serves to widen the binary.
+\subsubsection{He + He}\label{formeff_HeHe}
+For He + He DWDs, the sudden drop in formation efficiency near $\log(Z/Z_{\odot})=-1.0$ (see Figure \ref{fig:form_eff}) is generally caused by the timescale for which the initially more massive star in the DWD progenitor overflows it's Roche lobe.
+As discussed in Section \ref{sec:formeff}, at lower metallicities, donors tend to fill their Roche lobes while they are still on the MS and the mass transfer remains stable and serves to widen the binary.
 At higher metallicities, mass transfer is initiated when the donor has left the main sequence, and the binary enters a common envelope evolution.
 
-The ZAMS orbital period leads to different specific \textbf{He + He} evolutionary channels.
-For short-period systems with periods below $10~\rm{days}$, \textbf{a CE phase} leads to a stellar merger due to insufficient orbital energy to eject the envelope.
+The ZAMS orbital period leads to different specific He + He evolutionary channels.
+For short-period systems with periods below $10~\rm{days}$, a CE phase leads to a stellar merger due to insufficient orbital energy to eject the envelope.
 Stellar mergers continue to dominate the evolutionary pathways of systems with intermediate orbital periods ($1 < \log_{10}(P_{\rm{orb}}/\rm{day}) < 2.5$).
-However, an additional growing number of merging systems arises with one WD component and one stellar companion, and \textbf{surviving} systems which don't interact at all and thus do not form a He + He DWD.
+However, an additional growing number of merging systems arises with one WD component and one stellar companion, and surviving systems which don't interact at all and thus do not form a He + He DWD.
 The distinction between the various scenarios in this intermediate orbital period range depends on the combination of their ZAMS masses and orbital periods.
-Finally, at wider initial periods \textbf{$\log_{10}(P_{\rm{orb}}/\rm{day}) > 2.5$}, the decrease in formation efficiency is dominated by systems which never interact and thus do not form a DWD before the present day.
+Finally, at wider initial periods $\log_{10}(P_{\rm{orb}}/\rm{day}) > 2.5$, the decrease in formation efficiency is dominated by systems which never interact and thus do not form a DWD before the present day.
 
-\subsubsection{\textbf{CO + He}}\label{formeff_COHe}
-\textbf{In general, a CO + He DWD fails to form because either a stellar merger occurs before DWD formation, or a CO + CO or He + He DWD is formed instead.
+\subsubsection{CO + He}\label{formeff_COHe}
+In general, a CO + He DWD fails to form because either a stellar merger occurs before DWD formation, or a CO + CO or He + He DWD is formed instead.
 We discuss the specifics of these effects for three ZAMS orbital period regimes below.
-Model FZ yields higher formation efficiencies than F50 because CO + He DWDs prefer to form from progenitor binaries with orbital periods near $\log_{10}(P_{\rm{orb}}/~\rm{day})\sim2-4$, which is where the orbital period distribution of FZ peaks.}
+Model FZ yields higher formation efficiencies than F50 because CO + He DWDs prefer to form from progenitor binaries with orbital periods near $\log_{10}(P_{\rm{orb}}/~\rm{day})\sim2-4$, which is where the orbital period distribution of FZ peaks.
 
@@
 At higher metallicities, the CO WD merges with its companion.
-\textbf{As discussed in Section \ref{sec:formeff}, h}igher-metallicity progenitors have a larger fraction of their mass in the convective envelope when compared to lower-metallicity stars of the same mass.
+As discussed in Section \ref{sec:formeff}, higher-metallicity progenitors have a larger fraction of their mass in the convective envelope when compared to lower-metallicity stars of the same mass.
 Thus a CE phase with a higher-metallicity progenitor requires more orbital energy to eject the common envelope, causing a larger amount of orbital shrinking which results in a merger later in its binary evolution.
@@
 For CO + He DWD progenitor systems with intermediate orbital periods ($1.5\leq \log_{10}(P_{\rm{orb}}/\rm{day})< 2.5$) the mechanisms which impact formation efficiency are complex.
-The dominant way CO + He DWDs \textbf{fail to form} is stellar mergers that occur during the second CE phase.
-\textbf{Low-metallicity systems survive this second CE phase whereas high-metallicity systems do not.} \textbf{Similar to the short-period systems, there is increased orbital shrinkage for high-metallicity progenitor binaries due to the deeper convective envelope of the CE evolution donor.
-This creates shorter post-CE orbital periods which leads to mergers during the second \textbf{CE} phase.}
+The dominant way CO + He DWDs fail to form is stellar mergers that occur during the second CE phase.
+Low-metallicity systems survive this second CE phase whereas high-metallicity systems do not.
+Similar to the short-period systems, there is increased orbital shrinkage for high-metallicity progenitor binaries due to the deeper convective envelope of the CE evolution donor.
+This creates shorter post-CE orbital periods which leads to mergers during the second CE phase.
 
-If a lower-metallicity system forms a CO + He DWD and a higher-metallicity system does not, this \textbf{could also be} because the initially more massive binary component initiates a CE while on the giant branch instead of the asymptotic giant branch.
-This leaves behind a He WD with a stellar companion \textbf{instead of a CO + He}, which is the dominating scenario that restricts formation efficiency.
+If a lower-metallicity system forms a CO + He DWD and a higher-metallicity system does not, this could also be because the initially more massive binary component initiates a CE while on the giant branch instead of the asymptotic giant branch.
+This leaves behind a He WD with a stellar companion instead of a CO + He, which is the dominating scenario that restricts formation efficiency.
 There are a few edge cases where either a He + He DWD is formed instead, or a CO WD and a stellar companion is formed and there has been very nearly but not quite enough time for a CO + He DWD to form.
@@
 At these orbital periods, stellar mergers always occur with a CE phase between a stellar companion and a CO or He WD.
-\textbf{Again}, the mergers occur because of increased CE donor envelope masses at higher metallicities.
+Again, the mergers occur because of increased CE donor envelope masses at higher metallicities.
 A subdominant channel of stable He + He DWDs can also occur when a high-metallicity primary overflows it's Roche lobe while still on the giant branch and thus forms a He WD.
 
-\subsubsection{\textbf{CO + CO}}\label{formeff_COCO}
+\subsubsection{CO + CO}\label{formeff_COCO}
 The decrease in the CO + CO DWD formation efficiency with increasing metallicity stems from different evolutionary channels which arise at the ZAMS orbital period boundary of $\log_{10}(P_{\rm{orb}}/\rm{day})\sim3$.
@@
 For binaries with orbital periods above the boundary, the vast majority of systems with wide initial orbits end up as stable binaries.
-The \textbf{wide} systems which don’t form a CO DWD at high metallicity do so because one or both of the binary components initiate a CE phase while still on the giant branch, thus producing a CO + He or He + He DWD.
+The wide systems which don’t form a CO DWD at high metallicity do so because one or both of the binary components initiate a CE phase while still on the giant branch, thus producing a CO + He or He + He DWD.
 
-\subsubsection{\textbf{ONe + X}}\label{formeff_ONe}
+\subsubsection{ONe + X}\label{formeff_ONe}
 The strongest effect which hinders formations of higher-metallicity ONe + X DWDs is the strength of metallicity-dependent stellar winds assumed in our model \citep{Vink2001}.
@@
 
-\textbf{As discussed in Section \ref{sec:formeff},} our simulations with binary evolution parameter variations \textbf{show competition between} the physics of binary evolution \textbf{and} skews introduced by the metallicity-dependent orbital period distribution and binary fraction.
-Two important features of our FZ and F50 models drive the differences in \textbf{formation efficiency for} our binary evolution parameter variations.
-First, the log-normal metallicity-dependent ZAMS orbital period distribution increasingly skews towards \textbf{$P_{\rm{orb}}\lesssim 10^4$ days} for decreasing metallicity.
-However, second, the log-uniform $P_{\rm{orb}}$ distribution of F50 produces a higher number of the shortest-period systems (\textbf{$P_{\rm{orb}}\lesssim 100$ days}) than for FZ as the tail of the FZ distribution falls \textbf{below F50 in this regime.} \textbf{Because there are more ZAMS binaries with $P_{\rm{orb}} \lesssim 10^4$ days in F50, as the population evolves there are more likely to be binary interactions in the population for F50 than FZ.
+As discussed in Section \ref{sec:formeff}, our simulations with binary evolution parameter variations show competition between the physics of binary evolution and skews introduced by the metallicity-dependent orbital period distribution and binary fraction.
+Two important features of our FZ and F50 models drive the differences in formation efficiency for our binary evolution parameter variations.
+First, the log-normal metallicity-dependent ZAMS orbital period distribution increasingly skews towards $P_{\rm{orb}}\lesssim 10^4$ days for decreasing metallicity.
+However, second, the log-uniform $P_{\rm{orb}}$ distribution of F50 produces a higher number of the shortest-period systems ($P_{\rm{orb}}\lesssim 100$ days) than for FZ as the tail of the FZ distribution falls below F50 in this regime.
+Because there are more ZAMS binaries with $P_{\rm{orb}} \lesssim 10^4$ days in F50, as the population evolves there are more likely to be binary interactions in the population for F50 than FZ.
 This leads to more mergers in $\alpha25$ occurring for F50 before formation of the DWD, and thus a lower $\alpha25$ formation efficiency overall for F50 in contrast to FZ.
@@
 Across all DWD types, we find that there are more mergers for variation $\alpha25$ compared with the fiducial variation, and fewer for $\alpha5$, due to the CE efficiency's impact on CE phase orbital energy requirements.
-We also find fewer mergers for $q3$, because of the ability for binaries to maintain stable mass transfer, thus increasing their chance of survival.}
+We also find fewer mergers for $q3$, because of the ability for binaries to maintain stable mass transfer, thus increasing their chance of survival.
 
-\subsubsection{\textbf{Parameter variations: He + He}}\label{formeff_HeHe_vars}
-For binary systems leading to He + He DWDs, \textbf{as stated above} there are many more mergers for $\alpha25$ than for the fiducial variation.
+\subsubsection{Parameter variations: He + He}\label{formeff_HeHe_vars}
+For binary systems leading to He + He DWDs, as stated above there are many more mergers for $\alpha25$ than for the fiducial variation.
 The lower CE efficiency leads to more DWD progenitor mergers from a failed CE ejection, or the CE shrinking the orbit such that it then merges on the second CE phase.
-\textbf{As discussed above, there are also more close binaries in the orbital period distribution of F50 than FZ, creating a higher propensity for binary interactions and thus mergers for $\alpha25$.} This is illustrated in the $\alpha25$ He + He plot of Figure \ref{fig:form_eff}.
+As discussed above, there are also more close binaries in the orbital period distribution of F50 than FZ, creating a higher propensity for binary interactions and thus mergers for $\alpha25$.
+This is illustrated in the $\alpha25$ He + He plot of Figure \ref{fig:form_eff}.
 Similar to the fiducial parameter variation, a binary that becomes a He + He DWD at lower metallicities would merge before becoming one at higher metallicities because of the longer evolution timescales.
 These later interactions lead to closer post-CE separations and thus more mergers.
-The dip at [Fe/H] $\simeq -1.5$ \textbf{(see Figure \ref{fig:form_eff})} stems from mergers before the DWD forms, again similar to the fiducial parameter variation.
+The dip at [Fe/H] $\simeq -1.5$ (see Figure \ref{fig:form_eff}) stems from mergers before the DWD forms, again similar to the fiducial parameter variation.
 The peak that occurs in $\alpha25$ at $\sim 10\%\,Z_\odot$ arises from binaries evolving faster, and thus interacting earlier, as metallicity increases.
 This means that equivalent binaries that would have merged or formed a CO + He DWD instead at lower metallicities now survive to produce a He + He DWD.
-At higher metallicities, there are also a higher proportion of wide ZAMS binaries, which evolve off the Main Sequence too slowly to form a He + He DWD, \textbf{adding to} the efficiency drop.
+At higher metallicities, there are also a higher proportion of wide ZAMS binaries, which evolve off the Main Sequence too slowly to form a He + He DWD, adding to the efficiency drop.
 
@@
 Beyond the effects described above, the efficiency drop across metallicity is similar to the fiducial parameter variation in that it depends on the metallicity-dependent ZAMS orbital period distribution emphasizing short-period systems at low metallicities, and on the change of formation channel for different period ranges across metallicity.
-We find \textbf{that} variation $q3$ yields the highest formation efficiency.
-Only the shortest-period binaries do not form a DWD\textbf{, which are lost} through mergers at higher metallicities.
+We find that variation $q3$ yields the highest formation efficiency.
+Only the shortest-period binaries do not form a DWD, which are lost through mergers at higher metallicities.
 At low metallicities, even binaries with ZAMS orbital periods $P_{\rm{orb}}\lesssim 100$ days form He + He DWDs, with binaries in model FZ reaching ZAMS orbital periods less than a day in length.
@@
 
-\subsubsection{\textbf{Parameter variations: CO + He}}\label{formeff_COHe_vars}
+\subsubsection{Parameter variations: CO + He}\label{formeff_COHe_vars}
 For CO + He binaries, there are again many more mergers for parameter variation $\alpha25$ relative to the fiducial case.
-This is the dominant \textbf{reason} that progenitors do not evolve to produce DWDs at higher metallicities.
+This is the dominant reason that progenitors do not evolve to produce DWDs at higher metallicities.
 At low metallicities, a number of progenitor binaries form CO + CO DWDs instead of He + CO DWDs.
-This is especially the case near $\log_{10}(Z/Z_\odot)\sim -2$, where RLO occurs late enough in a binary's evolution that mass transfer remains stable and CO + CO's are formed rather than CO + He, hence producing a dip in the formation efficiency \textbf{(see Figure \ref{fig:form_eff})}.
+This is especially the case near $\log_{10}(Z/Z_\odot)\sim -2$, where RLO occurs late enough in a binary's evolution that mass transfer remains stable and CO + CO's are formed rather than CO + He, hence producing a dip in the formation efficiency (see Figure \ref{fig:form_eff}).
 
-Because parameter variation $\alpha5$ \textbf{yields fewer} mergers, the formation efficiency is mostly governed by the metallicity-dependent ZAMS orbital period distribution.
+Because parameter variation $\alpha5$ yields fewer mergers, the formation efficiency is mostly governed by the metallicity-dependent ZAMS orbital period distribution.
 At higher metallicities, the majority of cases in model FZ where progenitors do not produce a CO + He DWD are from progenitor mergers, or from He + He DWDs forming instead of CO + He DWDs.
@@
 This is also apparent for the $q3$ variation, and to a lesser extent in the fiducial case.
-In $q3$, for any given orbital period we find that lower-mass DWDs originate from lower metallicities, thus leading to an approximately constant formation efficiency \textbf{for model F50}.
+In $q3$, for any given orbital period we find that lower-mass DWDs originate from lower metallicities, thus leading to an approximately constant formation efficiency for model F50.
 
-\subsubsection{\textbf{Parameter variations: CO + CO}}\label{formeff_CO_vars}
+\subsubsection{Parameter variations: CO + CO}\label{formeff_CO_vars}
 For CO + CO, across all variations, very close ZAMS binaries ($P_{\rm{orb}}\sim\mathcal{O}(100$ days)) at high metallicities form a CO + He or He + He DWD instead of a CO + CO because the binary interacts before core Helium burning of one or both components.
@@
 Due to the high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods survive to become CO + CO DWDs rather than merging or becoming CO + He or He + He DWDs.
-There are \textbf{fewer} mergers overall for $q3$ than all the $\alpha$ variations because the first RLO occurrence leads to stable mass transfer from the primary to the secondary rather than multiple CE phases.
+There are fewer mergers overall for $q3$ than all the $\alpha$ variations because the first RLO occurrence leads to stable mass transfer from the primary to the secondary rather than multiple CE phases.
 For both the $\alpha5$ and $q3$ variations, the majority of CO + CO DWDs originate in wide enough orbits that they do not interact before DWD formation.
-This leads to an approximately constant formation efficiency across metallicity in both cases \textbf{for model F50}.
+This leads to an approximately constant formation efficiency across metallicity in both cases for model F50.
 
-\subsubsection{\textbf{Parameter variations: ONe + X}}\label{formeff_ONe_vars}
+\subsubsection{Parameter variations: ONe + X}\label{formeff_ONe_vars}
 For model FZ, the ONe + X formation efficiencies follow similar trends aross each parameter variation.
-Their formation scenarios are similar to those described \textbf{in Section \ref{sec:formeff}} for ONe + X DWDs in the fiducial binary evolution parameter set.
+Their formation scenarios are similar to those described in Section \ref{sec:formeff} for ONe + X DWDs in the fiducial binary evolution parameter set.
 The main difference between each parameter variation is only in the number of sources produced since the number of stellar mergers that occur before DWD formation increases with decreasing common envelope efficiency.
-In model F50, the formation efficiency is decreased \textbf{with respect to FZ} for parameter variation $\alpha25$ because the log-uniform orbital period distribution produces many ZAMS binaries with very short orbital periods which lead to stellar mergers during the CE phases.
-\textbf{The F50 formation efficiency distributions are slightly flattened compared to model FZ for variations $\alpha5$ and $q3$, similar to CO + CO as discussed above.}
+In model F50, the formation efficiency is decreased with respect to FZ for parameter variation $\alpha25$ because the log-uniform orbital period distribution produces many ZAMS binaries with very short orbital periods which lead to stellar mergers during the CE phases.
+The F50 formation efficiency distributions are slightly flattened compared to model FZ for variations $\alpha5$ and $q3$, similar to CO + CO as discussed above.
 
@@
 Figure \ref{fig:LISA_SNR_vars} shows the ASD vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the rows alternate between models F50 and FZ for the $\alpha25$, $\alpha5$, and $q3$ parameter variations.
-The LISA sensitivity curve is also shown in black, which includes the modeled confusion foreground \textbf{(see Section \ref{sec:LISA_met} for details on fitting the foreground) for the given variation}.
+The LISA sensitivity curve is also shown in black, which includes the modeled confusion foreground (see Section \ref{sec:LISA_met} for details on fitting the foreground) for the given variation.
 The entire population is shown as grey scatter points.
@@
 
-\textbf{The height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ affects the number of resolvable systems in each parameter variation.
+The height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ affects the number of resolvable systems in each parameter variation.
 For the fiducial and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ are reduced by $\sim 17$\% and increased by $\sim3\%$ respectively, with relatively unchanged overall LISA population sizes.
@@
 Thus, the incorporation of a metallicity-dependent binary fraction reduces the number of chirping binaries relative to non-chirping binaries by a factor of two for variations $\alpha5$ and $q3$.
-The number of chirping systems in the fiducial and $\alpha25$ variations remain unchanged between models F50 and FZ.}
+The number of chirping systems in the fiducial and $\alpha25$ variations remain unchanged between models F50 and FZ.
 
@@
 For $\alpha25$ we plot scatter plots for He + He and ONe + X due to low statistics; there are too few binaries in this selected population to produce reliable kernel density estimates.
-The only population with a significant change between \textbf{binary fraction models} is for ONe + X DWDs\textbf{, variation} $\alpha5$.
-Here, we find a skew to lower \textbf{chirp} masses because a higher fraction of the binaries are ONe + He for FZ \textbf{compared to} F50: a Helium companion makes up \textbf{38\%} of this selected population for FZ, compared with \textbf{12\%} for F50.
+The only population with a significant change between binary fraction models is for ONe + X DWDs, variation $\alpha5$.
+Here, we find a skew to lower chirp masses because a higher fraction of the binaries are ONe + He for FZ compared to F50: a Helium companion makes up 38\% of this selected population for FZ, compared with 12\% for F50.
 This leads to lower average chirp masses for the ONe + X distribution.
-Furthermore, \textbf{$\sim6$\%} of the F50 measurable systems are ONe + ONe binaries, versus 0\% for FZ.
-Because ONe WDs have larger masses, this also creates the high-mass concentration we \textbf{find} in the F50 contours.
+Furthermore, $\sim6$\% of the F50 measurable systems are ONe + ONe binaries, versus 0\% for FZ.
+Because ONe WDs have larger masses, this also creates the high-mass concentration we find in the F50 contours.
 \begin{figure*}[h]
